### 2017-11-15 Latex/meeting1Nov.tex
Adding figures, literature and latex folders

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper,top=1.5cm,bottom=1.5cm,left=1.5cm,right=1.5cm,%
bindingoffset=0mm]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.75em depth0em\fi}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{float}
\linespread{1.3}
\raggedbottom

%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\R}{\mathbb{R}}
\DeclareMathOperator{\E}{\mathbb{E}}
%

\begin{document}

\Large{

\section*{Results}

\begin{itemize}
	\item Implemented Barsky\&Sims' strategy $\Rightarrow$ Results are in line with the paper. In this case, we can just recover the news shock so we cannot say anything about IT productivity shocks.
	\item Implemented Ryan's strategy $\Rightarrow$ The news shock is in line with B\&S (despite imposing the zero long-run restriction on relative IT prices). However the IT shock explain a minuscule amount of TFP variation and IRFs are largely insignificant.
	\item Implemented a variant of Ryan's strategy ("one step" maximization)
	$$
	\max_{\gamma_{news},\gamma_{IT}} FEV_{TFP,news} + FEV_{TFP,IT}
	$$ s.t. same long-run restriction on news. $\Rightarrow$ Now all the explanation power goes to IT shocks and none is left to news. 
\end{itemize}

\section*{Problems}

\begin{itemize}
	\item The comparison between the two Ryan's strategy variants shows that the data attribute all the variation to either i) the shock that is less restricted or ii) the shock that comes first in the maximization. Our takeaway is that the long-run constraint is not really affecting the result of B\&S. There are two possible explanations: 1) no room for IT shocks. 2) The long-run constraint is not able to disentangle IT from news.
\end{itemize}

\section*{Where to go}

\begin{itemize}
\item An additional constraint?

\item Other thoughts?
\end{itemize}

}
\end{document}

### 2017-11-15 Forni/aic_bic_hq.m

@@ -1,24 +1,0 @@
-function [AIC,BIC,HQ] = aic_bic_hq(dataset,max_lags)
-
-%These criteria minimize the following objective functions:
-%AIC(p) = T ln detOmega_hat + 2(n^2*p)
-%BIC(p) = T ln detOmega_hat + (n^2*p)lnT
-%HQ(p)  = T ln detOmega_hat + 2(n^2*p)lnlnT
-%where n is the number of variables, T is the length of the dataset, and p
-%is the number of lags
-
-T = size(dataset,1);
-nvar = size(dataset,2);
-for nlags = 1:max_lags
-      [~,~,~,sigma] = sr_var(dataset,nlags);
-      
-      AIC(nlags)      = T*log(det(sigma)) + 2*(nvar^2*nlags);
-      BIC(nlags)      = T*log(det(sigma)) + (nvar^2*nlags)*log(T);
-      HQ(nlags)       = T*log(det(sigma)) + 2*(nvar^2*nlags)*log(log(T));
-end
-
-[AIC_minvalue, AIC]    = min(AIC);
-[BIC_minvalue, BIC]    = min(BIC);
-[HQ_minvalue, HQ]      = min(HQ);
-
-end

### 2017-11-15 produce_IT_prices_graphs.m

@@ -3,6 +3,9 @@ close all
 
 
 %Data Reading and Transformation
+base_path = pwd;
+addpath([base_path '\Data']) %for Microsoft
+addpath([base_path '/Data']) %for Mac
 filename = 'dataset_IT_prices';
 sheet    = 'Sheet1';
 range    = 'B1:F324';

### 2017-11-15 read_data.m

@@ -2,8 +2,8 @@ function [data_levels, shocknames, varnames, which_shock, q] = read_data(filenam
 % A file for reading in data specifically for this project. TO DO: Make
 % this general and clean up data reading in general.
 base_path = pwd;
-addpath([base_path '\Data'])
-addpath([base_path '/Data'])
+addpath([base_path '\Data']) %for Microsoft
+addpath([base_path '/Data']) %for Mac
 data = xlsread(filename,sheet,range);
 % Cumulate growth variables to levels (log levels to be precise, b/c growth
 % rates are calculated as log diffs)

### 2017-11-15 trendbreaks.m

@@ -12,6 +12,9 @@ clear all
 close all
 
 %Technical name
+base_path = pwd;
+addpath([base_path '\Data']) %for Microsoft
+addpath([base_path '/Data']) %for Mac
 file = 'data_trendbreaks.xlsx';
 sheet ='Sheet1';
 range = 'B2:E333';

### 2017-11-15 Latex/First_draft/first_draft.tex
adding all the latex documents

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper,top=3.5cm,bottom=3.5cm,left=3.5cm,right=3.5cm,%
bindingoffset=0mm]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\qed}{\nobreak \ifvmode \relax \else
	\ifdim\lastskip<1.5em \hskip-\lastskip
	\hskip1.5em plus0em minus0.5em \fi \nobreak
	\vrule height0.75em width0.75em depth0em\fi}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{float}
\linespread{1.3}
\raggedbottom

%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\R}{\mathbb{R}}
\DeclareMathOperator{\E}{\mathbb{E}}
%

\title{First Draft}
\author{Marco Brianti\\Laura Gati}
\date{August 2017}

\begin{document}

	\maketitle

	\section{Introduction}

	The basic idea is to rationalize a setting where incorrect information implies fundamental changes in the economy. To this end, we rely on the model proposed by Comin and Gertler (2006) which we enhance with a particular information structure derived from Lorenzoni (2009) in order to show how noisy signals can affect the real structure of the economy. In particular, Comin and Gertler (2006) propose a setting where TFP can be endogenously affected due to R\&D expenditure. After a negative shock, due to lack of resources, agents will decrease (among other variables) R\&D expenditure and thus affect the endogenous component of TFP. As a result, the lower level of TFP will trigger a negative spiral causing a much slower recovery than with a simple negative TFP shock.

	In order to introduce imperfect information appropriately, we consider the main structure of the model. In this economy, the final good can be either consumed, invested in physical capital, or spent as R\&D. The marginal benefit of allocating the final good into one or another sector will depend on the utility function, the price of investment and the efficiency of research sector, respectively. It is obvious that differently from the first two variables, the efficiency of the R\&D sector is much more difficult to observe. Indeed, this process is related to a huge amount of variables such as the probability of succeeding, the demand for this new technology, the existence of prospective competitors, and so on and so forth. Since many of these factors are unobserved or pertain to the future, we thus assume that R\&D efficiency is not fully observed and the optimal level of research expenditure will be decided as the outcome of agents' inference problem concerning this variable.

	To understand the main mechanism of the model, consider a simple example. Assume that for some reason, agents wrongly perceive a lower level of R\&D efficiency. The optimal response will be to allocate less resources to R\&D due to its low productivity. However, the choice to invest less in R\&D leads to lower productivity in the future, so that the economy will in fact experience a negative productivity shock. In other words, in this theoretical exercise a shock to beliefs is able to trigger a future fundamental shock, analogously to a self-fulfilling prophecy.

	The goal of this paper, then, is to exploit a simple but well-accepted model to show how wrong information may affect the structure of the economy beyond the business cycle effects well documented in the literature. In particular, the effects of imperfect information here are starkly different than in Lorenzoni (2009). The account in Lorenzoni (2009) documents how noisy information leads to business cycle fluctuations that resemble demand shocks. Instead our objective is to demonstrate how similar information imperfections can also imply future supply shocks and thus affectively alter the fundamental structure of the economy.

	\section{Two-Period Model}

	An agent seeks to maximize her utility,
	\begin{equation}
	U(C_0) + \beta^t U(C_1)
	\end{equation}
	where $C_i$ represents the level of consumption at period $i$, $\beta \in [0 \ 1]$ is the deterministic discount factor, and the time separable utility function provides the standard property $U'(\cdot)>0$ and  $U''(\cdot) < 0$.

	The budget constraints are represented by
	\begin{equation}
	C_0 \leq Y_0 - I_0 - S_0
	\end{equation}
	and
	\begin{equation}
	C_1 \leq Y_1
	\end{equation}
	where $Y_0$ is the level of production of consumption good in period $0$ which can be either consumed, invested in physical capital ($I_0$ ), or spent in research and development ($S_0$). While $Y_1$ is the level of output in the second period and will be fully consumed. The level of output is defined by the following production function
	\begin{equation}
	Y_i \leq A Z_i F(K_i) \ \ \ \text{for} \ i = 1,2
	\end{equation}
	where $A$ represents the exogenous level of technology, $Z_i$ represents the endogenous level of technology which is given in the first period and chosen in the second. Similarly, $K_i$ represents the level of capital which is given in the first period and chosen in the second. $F(\cdot)$ is the production function which uses capital $K_i$ as unique input factor and it displays the standard assumptions $F'(\cdot) > 0$ and $F''(\cdot) < 0$.

	The level of endogenous technology and capital is defined respectively by the following laws of motion
	\begin{equation}
	Z_{1} \leq \lambda S_0 + Z_0
	\end{equation}
	\begin{equation}
	K_{1} \leq I_0 + (1 - \delta)K_0
	\end{equation}
	where $\lambda \in [0 \ 1]$ represents the exogenous efficiency of the $R\&D$ sector. It can be interpreted as the probability of producing a new technology by spending a unit of consumption good in the research sector.

	In compact form the agent seeks to solve the following problem
	\begin{equation}
	\begin{split}
	\max_{\{ C_0,C_1,Y_0,Y_1,I_0,S_0,K_{1},Z_{1} \}} &U(C_0) + \beta U(C_1) \\
	\text{s.t.} \ \ \ C_0 &\leq Y_0 - I_0 - S_0 \\
	C_1 &\leq Y_1 \\
	Y_i &\leq A Z_i F(K_i) \ \ \ \text{for} \ i = 1,2 \\
	Z_{1} &\leq \lambda S_0 + Z_0 \\
	K_{1} &\leq I_0 + (1 - \delta)K_0 \\
	\end{split}
	\end{equation}

	Set up the Lagrangian
	\begin{equation}
	\begin{split}
	L =  U(C_0) + \beta U(C_1)  + &\mu_{1}\big[ Y_0 - I_0 - S_0 - C_0   \big]  + \mu_{2}\big[  A Z_0 F(K_0) - Y_0  \big]  \\
	+ &\mu_{3}\big[ \lambda S_0 + Z_0 -  Z_{1}  \big]   + \mu_{4}\big[ I_0 + (1 - \delta)K_0 -  K_{1}  \big]  \\
	+ &\beta \mu_5 \big[  AZ_1 K_1^{\alpha} - Y_1  \big] + \beta \mu_6 \big[  Y_1 - C_1   \big]
	\end{split}
	\end{equation}
	and the derive the first order conditions
	\begin{equation}
	U'(C_0) = \mu_{1}
	\end{equation}
	\begin{equation}
	U'(C_1) = \mu_{6}
	\end{equation}
	\begin{equation}
	\mu_{1} = \mu_{2}
	\end{equation}
	\begin{equation}
	\mu_{1} = \mu_{4}
	\end{equation}
	\begin{equation}
	\mu_{1} = \lambda \mu_{3}
	\end{equation}
	\begin{equation}
	\mu_{3} = \beta  \mu_{5} A F(K_{1})
	\end{equation}
	\begin{equation}
	\mu_4 = \beta  \mu_{5} A Z_{1} F'(K_{1})
	\end{equation}
	\begin{equation}
	\mu_5 = \mu_{6}
	\end{equation}
	\begin{equation}
	C_0 = Y_0 - I_0 - S_0
	\end{equation}
	\begin{equation}
	C_1 = Y_1
	\end{equation}
	\begin{equation}
	Y_i = A Z_i F(K_i) \ \ \ \text{for} \ i = 1,2
	\end{equation}
	\begin{equation}
	Z_{1} = \lambda S_0 + Z_0
	\end{equation}
	\begin{equation}
	K_{1} = I_0 + (1 - \delta)K_0
	\end{equation}

	Combining (9), (10), (12), (15), and (16) yields
	\begin{equation}
	1 =  \beta \frac{U'(C_{1})}{U'(C_0)}  A Z_{1} F'(K_{1}) 
	\end{equation}
	Moreover, combining (9), (10), and (12)-(15) yields
	\begin{equation}
	1 =  \beta \frac{U'(C_{1})}{U'(C_0)} \lambda  A F(K_{1}) 
	\end{equation}

	Notice that Equations (17)-(23) form a system of eight Equations in eight unknowns: $C_0$, $C_1$ $Y_0$, $Y_1$ $I_0$, $S_0$, $Z_{1}$, and $K_{1}$.

	\subsection*{Further Assumptions}

	Without loss of generality assume that the $U(C_i) = \log(C_i)$ and $F(K_i) = K_i^{\alpha}$ for $i = 1,2$. The model then yields

	\begin{equation}
	C_0 = Y_0 - I_0 - S_0
	\end{equation}
	\begin{equation}
	C_1 = Y_1
	\end{equation}
	\begin{equation}
	Y_0 = A Z_0 K_0^{\alpha}
	\end{equation}
	\begin{equation}
	Y_1 = A Z_1 K_1^{\alpha}
	\end{equation}
	\begin{equation}
	Z_{1} = \lambda S_0 + Z_0
	\end{equation}
	\begin{equation}
	K_{1} = I_0 + (1 - \delta)K_0
	\end{equation}
	\begin{equation}
	1 =  \beta \frac{C_{0}}{C_1}  \alpha A Z_{1} K_{1}^{\alpha - 1}
	\end{equation}
	\begin{equation}
	1 =  \beta  \frac{C_{0}}{C_1} \lambda  A K_{1}^{\alpha} 
	\end{equation}

	\subsection*{Solution}

	Substitute (26) into (24) and obtain
	\begin{equation}
	C_0 = A Z_0 K_0^{\alpha} - I_0 - S_0
	\end{equation}
	Substitute (28) and (29) into (27) and use (25) to obtain
	\begin{equation}
	C_1 = A (\lambda S_0 + Z_0) (I_0 + (1 - \delta)K_0)^{\alpha}
	\end{equation}
	Substitute (28), (29), (32), and (33) into (30) and (31) and obtain
	\begin{equation}
	1 = \alpha \beta \frac{A Z_0 K_0^{\alpha} - I_0 - S_0}{I_0 + (1 - \delta)K_0}
	\end{equation}
	and
	\begin{equation}
	1 = \lambda \beta \frac{A Z_0 K_0^{\alpha} - I_0 - S_0}{\lambda S_0 + Z_0}
	\end{equation}

	This is a system of two equations (34) and (35) in two unknowns $S_0$ and $I_0$ and its solution is
	\begin{equation}
	\begin{split}
	S_0 &= \frac{\beta}{1 + \beta+ \alpha \beta}[AZ_0 K_0^{\alpha} + (1-\delta)K_0] - \Bigg( \frac{1 + \alpha \beta}{1 + \beta + \alpha \beta} \Bigg) \lambda^{-1} Z_0 \\
	I_0 &= \alpha S_0 - (1-\delta)K_0 + \alpha \lambda^{-1} Z_0  \\
	\end{split}
	\end{equation}
	\begin{prop}
		$S_0$ is increasing in $\lambda$
	\end{prop}
	\begin{proof}
		\begin{equation}
		\frac{\partial S_0}{\partial \lambda} = \Bigg( \frac{1 + \alpha \beta}{1 + \beta + \alpha \beta} \Bigg) \lambda^{-2} Z_0 > 0   \qed
		\end{equation}
	\end{proof}

	\subsection*{Imperfect Information}

	Assume that $\lambda$, the efficiency of the R\&D sector, cannot be directly observable and takes the form
	\begin{equation}
	\lambda = \lambda_m + \varepsilon,
	\end{equation}
	where $\varepsilon$ is a mean zero and finite variance shock which deviate the value of $\lambda$ from the known expected value $\lambda_m$. The agent is instead able to observe the following signal
	\begin{equation}
	\lambda_s = \lambda + \eta
	\end{equation}
	where $\eta$ is a second mean zero and finite variance shock fully independent from $\varepsilon$ which prevents the agent to have access to a complete information setup.

	\subsection*{Inference}

	Agent seeks to minimize the error between $\lambda$ and $\lambda_s$ using standard Kalman filter techniques.
	\begin{equation}
	\begin{split}
	\beta_k &= \frac{Cov(\lambda,\lambda_s)}{Var(\lambda_s)} \\
	&= \frac{Cov(\lambda_m + \varepsilon, \lambda_m + \varepsilon + \eta)}{Var(\lambda_m + \varepsilon + \eta)} \\
	&= \frac{\sigma_{\varepsilon}}{\sigma_{\eta} + \sigma_{\varepsilon}}
	\end{split}
	\end{equation}
	and
	\begin{equation}
	\begin{split}
	\alpha_k &= \E[\lambda] - \beta_k \E[\lambda_s] \\
	&= (1 - \beta_k) \lambda_m \\
	&= \frac{\sigma_{\eta}}{\sigma_{\eta} + \sigma_{\varepsilon}} \lambda_m
	\end{split}
	\end{equation}
	which implies that
	\begin{equation}
	\begin{split}
	\E[\lambda|\lambda_s] &= \alpha_k + \beta_k \lambda_s \\
	&=  \frac{\sigma_{\eta}}{\sigma_{\eta} + \sigma_{\varepsilon}} \lambda_m + \frac{\sigma_{\varepsilon}}{\sigma_{\eta} + \sigma_{\varepsilon}} \lambda_s \\
	&=  \frac{\sigma_{\eta}}{\sigma_{\eta} + \sigma_{\varepsilon}} \lambda_m + \frac{\sigma_{\varepsilon}}{\sigma_{\eta} + \sigma_{\varepsilon}} (\lambda_m + \lambda_s  - \lambda_m) \\
	&= \lambda_m + \frac{\sigma_{\varepsilon}}{\sigma_{\eta} + \sigma_{\varepsilon}} (\lambda_s  - \lambda_m) \\
	\end{split}
	\end{equation}

	\subsection*{Noise Shocks}

	Assume $\varepsilon = 0$ and $\eta = \tilde{\eta} > 0$.  It is clear that even if $\lambda = \lambda_m$, agent is just able to observe $\lambda_s = \lambda_m + \tilde{\eta}$. This implies that the perceived value of $\lambda$ is
	\begin{equation}
	\E[\lambda | \lambda_s] = \lambda_p = \lambda_m + \frac{\sigma_{\varepsilon}}{\sigma_{\eta} + \sigma_{\varepsilon}} \tilde{\eta}
	\end{equation}
	This implies that the R\&D expenditure will be strictly higher even if the level of $\lambda$ is completely unaffected which entails a greater level of technology due to a noise shock.

	\section{The Analytical Model - To be completed}

	An agent seeks to maximize her life-time utility,
	\begin{equation}
	\sum_{t=0}^{\infty} \beta^t U(C_t)
	\end{equation}
	where $C_t$ represents the level of consumption at period $t$, $\beta \in [0 \ 1]$ is the deterministic discount factor, and the time separable utility function provides the standard property $U'(\cdot)>0$ and  $U''(\cdot) < 0$.

	The budget constraint is represented by
	\begin{equation}
	C_t \leq Y_t - I_t - S_t
	\end{equation}
	where $Y_t$ is the level of production of consumption good which can be either consumed, invested in physical capital ($I_t$ ), or spent in research and development ($S_t$). The level of output is endogenously defined by the following production function
	\begin{equation}
	Y_t \leq A_t Z_t F(K_t)
	\end{equation}
	where $A_t$ and $Z_t$ represent respectively the exogenous and endogenous level of technology in the economy. $F(\cdot)$ is the production function which uses capital $K_t$ as unique input factor and it displays the standard assumptions $F'(\cdot) > 0$ and $F'(\cdot) < 0$.

	The level of endogenous technology and capital is defined respectively by the following laws of motion
	\begin{equation}
	Z_{t+1} \leq \lambda_t S_t + Z_t
	\end{equation}
	\begin{equation}
	K_{t+1} \leq I_t + (1 - \delta)K_t
	\end{equation}
	where $\lambda_t \in [0 \ 1]$ represents the exogenous efficiency of the $R\&D$ sector. It can be interpreted as the probability of producing a new technology by spending a unit of consumption good in the research sector.

	In compact form the agent seeks to solve the following problem
	\begin{equation}
	\begin{split}
	\max_{\{ C_t,Y_t,I_t,S_t,K_{t+1},Z_{t+1} \}_{t=0}^{\infty}} &\sum_{t=0}^{\infty} \beta^t U(C_t) \\
	\text{s.t.} \ \ \ C_t &\leq Y_t - I_t - S_t \\
	Y_t &\leq A_t Z_t F(K_t) \\
	Z_{t+1} &\leq \lambda_t S_t + Z_t \\
	K_{t+1} &\leq I_t + (1 - \delta)K_t \\
	\end{split}
	\end{equation}

	Set up the Lagrangian
	\begin{equation}
	\begin{split}
	L = \sum_{t=0}^{\infty} \beta^t \Big\{ U(C_t)  + &\mu_{1,t}\big[ Y_t - I_t - S_t - C_t   \big]  + \mu_{2,t}\big[  A_t Z_t F(K_t) - Y_t  \big]  \\
	+ &\mu_{3,t}\big[ \lambda_t S_t + Z_t -  Z_{t+1}  \big]   + \mu_{4,t}\big[ I_t + (1 - \delta)K_t -  K_{t+1}  \big]  \Big\}
	\end{split}
	\end{equation}
	and the derive the first order conditions
	\begin{equation}
	U'(C_t) = \mu_{1,t}
	\end{equation}
	\begin{equation}
	\mu_{1,t} = \mu_{2,t}
	\end{equation}
	\begin{equation}
	\mu_{1,t} = \mu_{4,t}
	\end{equation}
	\begin{equation}
	\mu_{1,t} = \lambda_t \mu_{3,t}
	\end{equation}
	\begin{equation}
	\beta \E_t [ \mu_{2,t+1} A_{t+1} Z_{t+1} F'(K_{t+1}) + \mu_{4,t+1}(1-\delta) ] = \mu_{4,t}
	\end{equation}
	\begin{equation}
	\beta \E_t [ \mu_{2,t+1} A_{t+1} F(K_{t+1}) + \mu_{3,t+1} ] = \mu_{3,t}
	\end{equation}
	\begin{equation}
	C_t = Y_t - I_t - S_t
	\end{equation}
	\begin{equation}
	Y_t = A_t Z_t F(K_t)
	\end{equation}
	\begin{equation}
	Z_{t+1} = \lambda_t S_t + Z_t
	\end{equation}
	\begin{equation}
	K_{t+1} = I_t + (1 - \delta)K_t
	\end{equation}

	Combining (8)-(10) and (12) yields
	\begin{equation}
	1 = \E_t \Bigg\{ \beta \frac{U'(C_{t+1})}{U'(C_t)} \big[   1  + A_{t+1} Z_{t+1} F'(K_{t+1}) - \delta \big]   \Bigg\}
	\end{equation}
	Moreover, combining (8), (9), (11), and (13) yields
	\begin{equation}
	1 = \E_t \Bigg\{ \beta \frac{U'(C_{t+1})}{U'(C_t)} \frac{\lambda_t}{\lambda_{t+1}} \Bigg[ 1 + \lambda_{t+1}  A_{t+1}F(K_{t+1}) \Bigg]   \Bigg\}
	\end{equation}

	Notice that Equations (14)-(19) form a system of six Equations in six unknowns: $C_t$, $Y_t$, $I_t$, $S_t$, $Z_{t+1}$, and $K_{t+1}$.

	\subsection*{Further Assumption}

	For simplicity assume the $U(C_t) = \log(C_t)$ and $F(K_t) = K_t^{\alpha}$. The model becomes
	\begin{equation}
	C_t = Y_t - I_t - S_t
	\end{equation}
	\begin{equation}
	Y_t = A_t Z_t K_t^{\alpha}
	\end{equation}
	\begin{equation}
	Z_{t+1} = \lambda_t S_t + Z_t
	\end{equation}
	\begin{equation}
	K_{t+1} = I_t + (1 - \delta)K_t
	\end{equation}
	\begin{equation}
	1 = \E_t \Bigg\{ \beta \frac{C_t}{C_{t+1}} \big[   1  + \alpha A_{t+1} Z_{t+1} K_{t+1}^{\alpha - 1} - \delta \big]   \Bigg\}
	\end{equation}
	\begin{equation}
	1 = \E_t \Bigg\{ \beta \frac{C_t}{C_{t+1}} \frac{\lambda_t}{\lambda_{t+1}} \big[ 1 + \lambda_{t+1}  A_{t+1} K_{t+1}^{\alpha} \big]   \Bigg\}
	\end{equation}

\section{Dynamic Model}

\subsection{Household}

A representative household seeks to maximize her life-time utility,
\begin{equation}
\sum_{t=0}^{\infty} \beta^t [ log(C_t) - \chi L_t^{\theta}]
\end{equation}
The budget constraint is represented by
\begin{equation}
C_t + K_{t+1} + S_t = W_tL_t + (1- \delta + R_{t})K_t + \Pi_t
\end{equation}
where $S_t$ is the investment in R\&D and $\Pi_t$ is a lump-sum transfer from the profits of the intermediate-good sector.

First order conditions over $C_t$, $L_t$, and $K_{t+1}$ yield
\begin{equation}
\frac{1}{C_t} = \chi \frac{L_t^{\theta - 1} }{W_t}
\end{equation}
\begin{equation}
1 = \beta \E_t \bigg[\frac{C_t}{C_{t+1}} (1 - \delta + R_{t+1})  \bigg]
\end{equation}

\subsection{Final-good producer}

A representative final-good producer maximizes its own profits using the following production function
\begin{equation}
\begin{aligned}
Y_t &= A_t[K_t^{\alpha}L_t^{1 - \alpha}]^{1 - \gamma} \bigg[ \bigg( \int_0^{Z_t} M_{j,t}^{\frac{1}{\nu}} dj \bigg)^{\nu} \bigg]^{\gamma} \\
    &= A_t[K_t^{\alpha}L_t^{1 - \alpha}]^{1 - \gamma} M_t^{\gamma} Z_t^{\gamma \nu} \\
    &= A_t Z_t^{\nu}[K_t^{\alpha}L_t^{1 - \alpha}]^{1 - \gamma} [M_t Z_t]^{\gamma}
\end{aligned}
\end{equation}
where $Z_t^{\nu}$ represents the endogenous component of productivity and $M_{j,t}$ is an intermediate good. It will be shown that all $M_{j,t}$ are equal to each other on the equilibrium path.

Firm's first order conditions over $K_t$, $L_t$, and $M_{j,t}$ yield
\begin{equation}
W_t = (1 - \gamma)(1 - \alpha) \frac{Y_t}{L_t}
\end{equation}
\begin{equation}
R_t = (1 - \gamma)\alpha \frac{Y_t}{K_t}
\end{equation}
\begin{equation}
P^M_t = \gamma \frac{Y_t}{Z_t M_t}
\end{equation}
where $W_t$, $R_t$, and $P^M_t$ are the price of each respective factor.

\subsection{Intermediate-good producer}

Intermediate-good producers compete in a imperfect monopolistic market. Due to absence of any frictions, the Dixit–Stiglitz aggregator provides an optimal price equal to
\begin{equation}
P_t^M = \nu
\end{equation}
For each monopolist, profits will then be
\begin{equation}
\Pi_t = (P_t^M - 1)M_t
\end{equation}

\subsection{R\&D Sector}

The value of being a monopolist is
\begin{equation}
V_t = \Pi_t + \phi \beta \E \bigg[ \frac{C_t}{C_{t+1}}  V_{t+1} \bigg]
\end{equation}
However, to became a monopolist, innovator needs to meet a free entry condition that implies
\begin{equation}
\frac{1}{\lambda_t} = \phi \beta \E \bigg[ \frac{C_t}{C_{t+1}}  V_{t+1} \bigg]
\end{equation}
where the law of motion of endogenous TFP is
\begin{equation}
Z_{t+1} = \lambda_t S_t + \phi Z_t
\end{equation}
and
\begin{equation}
\lambda_t = \lambda_x \frac{1}{K_t^{\rho}S_t^{1 - \rho}}
\end{equation}

\subsection{System of equations}

We have 13 variables: $C_t$, $K_{t+1}$, $L_t$, $W_t$, $R_t$, $P_t$, $Y_t$, $\Pi_t$, $V_t$, $Z_{t+1}$, $S_t$, $\lambda_t$, and $M_t$ in 13 equations:

\begin{equation}
\frac{1}{C_t} = \chi \frac{L_t^{\theta - 1} }{W_t}
\end{equation}
\begin{equation}
1 = \beta \E_t \bigg[\frac{C_t}{C_{t+1}} (1 - \delta + R_{t+1})  \bigg]
\end{equation}
\begin{equation}
C_t + K_{t+1} + S_t = W_tL_t + (1- \delta + R_{t})K_t + \Pi_t
\end{equation}
\begin{equation}
W_t = (1 - \gamma)(1 - \alpha) \frac{Y_t}{L_t}
\end{equation}
\begin{equation}
R_t = (1 - \gamma)\alpha \frac{Y_t}{K_t}
\end{equation}
\begin{equation}
P^M_t = \gamma \frac{Y_t}{Z_t M_t}
\end{equation}
\begin{equation}
P_t^M = \nu
\end{equation}
\begin{equation}
\Pi_t = (P_t^M - 1)M_t
\end{equation}
\begin{equation}
V_t = \Pi_t + \phi \beta \E \bigg[ \frac{C_t}{C_{t+1}}  V_{t+1} \bigg]
\end{equation}
\begin{equation}
Z_{t+1} = \lambda_t S_t + \phi Z_t
\end{equation}
\begin{equation}
\frac{1}{\lambda_t} = \phi \beta \E \bigg[ \frac{C_t}{C_{t+1}}  V_{t+1} \bigg]
\end{equation}
\begin{equation}
Y_t = A_t[K_t^{\alpha}L_t^{1 - \alpha}]^{1 - \gamma}Z_tM_t^{\gamma}
\end{equation}
\begin{equation}
\lambda_t = \lambda_x \frac{1}{K_t^{\rho}S_t^{1 - \rho}}
\end{equation}

\end{document}

### 2017-11-15 Latex/Forni_first_draft/first_draft.tex
adding all the latex documents

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper,top=3.5cm,bottom=3.5cm,left=3.5cm,right=3.5cm,%
bindingoffset=0mm]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\qed}{\nobreak \ifvmode \relax \else
	\ifdim\lastskip<1.5em \hskip-\lastskip
	\hskip1.5em plus0em minus0.5em \fi \nobreak
	\vrule height0.75em width0.75em depth0em\fi}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{float}
\linespread{1.3}
\raggedbottom

%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\R}{\mathbb{R}}
\DeclareMathOperator{\E}{\mathbb{E}}
%

\title{First Draft}
\author{Marco Brianti\\Laura Gati}
\date{October 2017}

\begin{document}

	\maketitle

	\tableofcontents

	\section{Introduction}

	A hotly discussed current issue in the economics profession is the slow recovery of TFP after the Great Recession. A strand of literature in the wake of Comin and Gertler (2006) is highlighting that this slow recovery may be due to the endogenous component of TFP.\footnote{Such models capture a setting where TFP can be endogenously affected through R\&D expenditure. In this setting, a standard negative shock in exogenous TFP will imply not only a decrease in TFP itself via the exogenous component, but also a decrease in R\&D investment, due to the lack of resources in the economy. This decrease in R\&D investment leads to a decrease in the endogenous component of TFP. As a result, TFP overall will not only be lower than without the endogenous mechanism, but its lower level will start this process anew, thus triggering a negative spiral. Therefore the same negative technology shock will have both higher level and propagation effects.} Among these papers are Anzoategui et al. (2016), Bianchi et al. (2016) and Moran and Queralto (2017). However,  macroeconomic literature has expressed two major concerns with this interpretation: 1.) As clearly explored by Fernald, Hall, Stock and Watson (2017), the slowdown in TFP started in 2006, that is \emph{before} the financial crisis. 2.) R\&D triggers significant effects on TFP only after a remarkable amount of time, so it is hard to rationalize a decrease in R\&D at the time of the crisis as immediately leading to a slowdown in TFP. For these reasons, an explanation of the TFP slowdown merely based on lower R\&D investment cannot successfully explain how to relate these empirical facts to the models proposed in this literature, since in such models, the decrease in R\&D is due to a weak demand triggered by the financial crisis.

	In this project we aim to explain the slowdown in TFP using an endogenous growth model \`a la Comin and Gertler (2006), but, crucially, we aim to address the two main critiques pointed out above. Our model, therefore, shifts the focus from R\&D solely, to the role of expectations on more broad concepts of investment in endogenous TFP.

	As suggested by empirical papers such as Hall, Lotti, and Mairesse (2012), R\&D is not the only variable able to affect the endogenous component of TFP. In particular, investment in Information and Communication Techonlogy (hereafter IT investment) seems to be able to play an important role in driving the endogenous component of TFP. As an empirical motivation, in Figure 1 we show the log-levels of IT investment and the value of manufacturers new orders for IT industries (hereafter IT orders). Differently from R\&D expenditure, the slowdown of IT-related variables took place slightly before 2001 due to the burst of the IT bubble. Independently from the crisis, these variables never came back to the original trend and our aim is to assess the role of IT investment in the slowdown in TFP.

	\begin{figure}
		\centering
		\includegraphics[scale=0.5, angle =270]{motivation}
		\caption{Data source is Federal Reserve Economic Data (FRED). IT investment is quarterly data and IT orders is monthly. Both variables are in log-levels.}
	\end{figure}

A model that is postulating an endogenous determinant of TFP in the long run needs to take a stand on what sense this endogenous determinant differs from a news shock - the type of shock that in general is thought to be the driver of TFP in the long run. In particular, both of the shocks can be thought to happen contemporaneously but to be related to a future increase in TFP. Therefore, in order to be able to analyze these shocks separately we need to discipline our empirical and theoretical models to pin down a dimension of difference between them.

The project is split into an empirical and theoretical part. The empirical part performs a structural VAR where we aim to identify news shocks as well as IT productivity shocks in a setting where TFP is endogenous. The theoretical part aims to provide a mechanism for the intuition that a news shock have a self-enforcing flavor through the endogenous component of TFP. As an example, assume that agents are hit by the exogenous signal that future TFP will be considerably higher. In this setting, due to fact that new ideas are more profitable when TFP is higher, a news shock will imply an increase in the perceived profitability of the IT sector, leading to a contemporaneous jump in this variable.\footnote{In particular, we subscribe to the interpretation of the IT investment process as a long-term investment whose results materialize with a lag. Following this logic, it is reasonable to believe that agents start to invest today in order to have new ideas ready to be sold when the expected jump in productivity actually arises.} Thus, a news shock implies a higher level of IT investment today which eventually will entail also a higher level of endogenous TFP in the future, confirming agents' expectations. Importantly, this mechanism does not rule out the existence of a completely exogenous news shock regarding the exogenous component of TFP but it considers the possibility that such a shock will naturally embody a mechanism of self-enforcing expectations.

\section{Empirical Evidence}

In this section, we follow a two-step procedure to investigate whether the mechanism outlined above is at work in the data. As a first step, we impose minimal discipline to simply bring together SVARs studied in the news shocks literature and in the endogenous TFP literature. Thus, the first VAR we run will be one that features both news shocks and IT productivity shocks, and we will impose only a minimal set of restrictions. This will be useful to get a first sense of the data and of how the system behaves when variables capturing news and endogenous TFP enter the system simultaneously. However, as we will explore in further detail below, this specification does not offer an adequate identification of news shocks in the presence of endogenous TFP, and thus also our IT productivity shocks may be poorly identified. Therefore, in a second step, we introduce an additional variable and impose a richer set of restrictions motivated by basic supply-demand theory to identify our shocks of interest.

\subsection{First Set of Results}

\subsubsection{Specification and Identification Strategy}

Our first-step specification is the following 6-variable VAR 
\begin{equation}
\begin{pmatrix}
TFP_t \\ 
H_t \\
MI_{t+5|t} \\
IT_t \\
GDP_t \\
C_t \\
\end{pmatrix} = B(L) \begin{pmatrix}
TFP_{t-1} \\ 
H_{t-1} \\
MI_{t-1+5|t-1} \\
IT_{t-1} \\
GDP_{t-1} \\
C_{t-1} \\
\end{pmatrix} + i_t
\end{equation}
where $TFP_t$ is the log-level of Fernald total factor productivity, $H_{t}$ is the level of total number of hours worked, $MI_{t+5|t}$ is the level of Michigan Index of business confidence over 5 years, $IT_t$ is the log-level of IT investment, $GDP_t$ is the log-level of real gross domestic product, and $C_t$ is the log-level of real consumption. All the variables refer to the U.S. economy. $B(L)$ is a ($6\times 6$) matrix of lag-operator functions of the same order. In our favorite specification the order of the lag operator functions is two which implies that we regress variables at time $t$ with their own lagged values at $t-1$ and $t-2$. Finally, $i_t$ is a ($6\times 1$) vector of correlated innovations where $\Omega = i'_t i_t$.

In order to derive structural shocks $s_t$ from innovations $i_t$ we use a standard Cholesky identification strategy which imposes 15 zero-impact restrictions. Our identification strategy aims to identify a news shock and a IT productivity shock. In particular, we adhere to the following definitions of our shocks of interest. In line with the news shock literature, a news shock is defined as a signal regarding the future exogenous component of TFP.\footnote{In much of the news shock literature, this definition is not explicit in terms of \emph{exogenous} TFP, because in the absence of an endogenous TFP mechanism, exogenous TFP and total TFP are by definition the same object. Thus, defining a news shock as the shock that moves TFP over the long horizon implicitly amounts to saying that news move exogenous TFP.} The IT productivity shock (also IT shock) is by definition an increase in the sector-specific productivity that should lead to a natural increase in the IT level of investment. %Can we speak here about substitution effect?
The reason why we seek to identify also this second shock is because we want to disentangle the rise in IT investment given by an increase in the sector-specific productivity to the rise in IT investment due to future signals on exogenous TFP. %In other words, in order to size the self-enforcement effect of a news shock we need to disentangle the endogenous component embodied by an IT productivity shock, and, on the other hand, to correctly size the pure effect of an IT productivity shock we need to disentangle from IT its expectational component.

In line with both strands of literature, we assume that both news shocks and IT productivity shocks have zero-impact effect on TFP. However, in order to distinguish these two, we impose a zero impact response of the Michigan Index to IT productivity shocks. We are using this last restriction in order to clean out any expectational effect from IT productivity shocks. In other words, an IT productivity shock should just show the effects of an unexpected and orthogonal increase in IT investment due to a contemporaneous shift in the sector-specific IT productivity, without embodying any hidden information regarding the future states of exogenous TFP. Failing to impose such a restriction will lead to upward-biased results on the effect of IT shocks on future TFP since we will not be able to distinguish between the exogenous news and the endogenous mechanism. However, on the other hand, we are not restricting the response of IT expenditure to news shocks since we are open to the idea that agents in response to a future increase in TFP will opt for a contemporaneous increase in IT investment. In particular, this is the self-enforcing behavior of the news shock that we are seeking to test.\footnote{As already argued, new technologies may be more profitable when TFP is higher, implying that a news shock would trigger an increase in the perceived profitability of the IT sector, leading to a contemporaneous jump in this variable.}

\subsection{Results}

In this subsection we present impulse response functions and variance decomposition of news shocks and IT productivity shocks.

\begin{figure}[h!]
	\centering
	\includegraphics[scale=0.5]{figure(1)_IT}
	\caption{Impulse responses of aggregate macroeconomic variables to a news shock. Red solid line is point estimation and dashed lines are 90\% confidence intervals.}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[scale=0.5]{figure(2)_IT}
	\caption{Impulse responses of aggregate macroeconomic variables to a IT shock. Red solid line is point estimation and dashed lines are 90\% confidence intervals.}
\end{figure}

\begin{table}[h!]
	\centering
	\begin{tabular}{ c c c }
		&       News shock     &      IT shock \\
		TFP              &       [    0.1733]   &      [  0.0990] \\
		H                &       [    0.0931]   &      [  0.2311] \\
		Mich index       &       [    0.5234]   &      [  0.2048] \\
		IT investment    &       [    0.0430]   &      [  0.6416] \\
		GDP              &       [    0.1406]   &      [  0.4178] \\
		C                &       [    0.1766]   &      [  0.4118] \\
	\end{tabular}
	%		\caption{Percentage variance explained by news shocks and IT shocks on TFP, hours worked, business confidence, information and technology investment, GDP, and consumption. The horizon is set to be 10 years.}\\
\end{table}

Our results from this specification are broadly in line with the two strands of literature we're bringing together. Considering first the impulse responses following a news shock, we see a delayed positive effect on TFP. In particular, it is significant after five quarters and, although diminishing, its effect is still positive after 10 years. As expected, news have a significant impact effect on agents' expectations as proxied by the Michigan index of business confidence over 5 years. In addition, news have a small but positive impact effect on consumption, investment in IT and economic outcome.

This effect gradually gets larger for all the variables, mirroring the response of TFP. Specifically, we are interested in the positive and prolonged response of IT investment which suggests a self-enforcing behavior of news in the economy.

Interestingly, an IT shock has a even more delayed effect on TFP. In line with the related empirical literature, an improvement in the IT sector takes almost 5 years to trigger an effect on TFP. Additionally, IT shocks have a sharp and positive effect on agents' confidence after the zero-impact restriction.\footnote{This sharp response of agents' expectations after the zero-impact restriction is a fair critique to our identification strategy, as it suggests a problem of reverse causality between news and IT efficiency. This is the reason we attempt a more disciplined identification strategy in the next section.} Due to the shift in IT productivity, IT investment has a positive response for a prolonged period of time confirming the importance of this shock on economic activity. Moreover, consumption and GDP have a slightly delayed positive response which increases over time and remains high even after 10 years.

Finally, focusing on Table 1, news explain almost 20\% of the variance of TFP over a 10-year horizon. Alternatively, a IT productivity shock is able to explain almost the 10\% over the same horizon. Although, news shocks seem to be able to better explain TFP in the long run, IT shocks have a more important effect on real variables like hours worked, consumption, and GDP over 10 years.

\subsubsection{Concerns}

As discussed in the previous sections, there are several reasons to be concerned that our first specification does not adequately disentangle news shocks from IT shocks. The short-run identification strategy followed in the previous section assumes the same zero impact effect on TFP both from news and IT shocks. The only restriction that imposes any difference between the two shocks is that the variable capturing news, the Michigan index, should not react on impact to an IT shock. The entire validity of the procedure hinges on whether this assumption is sufficient to neatly disentangle the two shocks.

However, there are ample reasons for why this might not be the case. First of all, as noted above, the response of the Michigan index to an IT shock shoots into significant territory immediately after impact. Potentially, this reflects that the zero-impact restriction may be not enough to clean out expectational effects from the IT shock which is suggestive of the fact that identified IT shocks may embody a part of news biasing the effects and relevance of an IT shock. In other words, an IT shock identified using the Cholesky procedure cannot pin down an \emph{exogenous} sector-specific IT productivity shock, but a convex combination between itself and news. Then, it means that with these procedure we are also biasing the effects and relevance of news since a part of it is incorrectly shifted to IT shocks. As a result,  zero-impact restrictions are not sufficient to distinguish between news and IT suggesting the need for an improved identification strategy.

\subsection{A Second Identification Strategy}

%Attempt to fully cleaning a sector-specific IT productivity shock from a signal on the exogenous component of TFP.
In order to tackle the challenges presented above, we propose a second identification strategy that relies on basic supply-demand theory from macroeconomics to pin down other observable differences between news and IT shocks. The idea is the following.

Inside the specific IT sector, a news shock resembles the same effects of a demand shock. In particular, IT productivity is completely unchanged but its demand is now stronger for the novel information that future TFP will be higher. This shift in the demand for IT items is likely due to a spillover effect that new technologies are more profitable when TFP is higher. Thus, in terms of nominal quantities, since news shocks look like sectoral demand shocks, we expect a contemporaneous increase in the sectoral prices. On the other hand, IT shocks imply supply-side changes in the IT sector, since the sector becomes more productive on impact. Thus, within the IT sector, the IT shock resembles supply shocks, involving sinking sectoral prices. Thus simple supply-demand theory gives us a dimension along which news shocks and IT shocks differ: they move prices in the IT sector in opposite directions.

In particular, in order to avoid having to deal with the general effect of both shocks on inflation, we will consider the relative price of IT, as given by the ratio $\frac{P^{IT}}{P}$, where $P$ is simply the CPI.\footnote{The reason we consider the relative price of IT is in general to avoid having to take a stance on the direction of price movements per se. In particular, a robust empirical finding of the news literature is that prices tend to decrease after a news shock. Thus, the prediction of supply-demand theory would be annulled in a framework where we only consider prices, while it remains operative if we take into account that prices across the board may be going down, but IT prices move less than prices of other items in the CPI.}

To spell out the identification strategy we derive from this line of thought, it is useful to consider a simple, reduced-form decomposition of the channels that determine productivity:

\begin{equation}
TFP_t =  \underbrace{\varepsilon_t}_\text{surprise tech shock}  + \underbrace{\underbrace{V_{t-1}}_\text{news shock} + \underbrace{IT_{t-1}}_\text{\text{IT shock}}}_\text{$N_{t-1}$}  \\
\end{equation}

Equation (2) illustrates that in the model we have in mind, the productivity of the economy is governed by three forces: contemporaneous shocks to exogenous TFP, news shocks that exogenously affect productivity with a lag, and IT shocks that endogenously affect productivity with a lag. Note that defining $N_{t-1} = V_{t-1} + IT_{t-1}$ would yield the specification of Barsky \& Sims, where productivity is thought of as driven by surprise shocks to technology and a news shock, $N_{t-1}$. Barsky and Sims (2011) identify $N_{t-1}$ as the shock that maximizes the forecast error variance (FEV) of TFP in the long run, thus capturing all the fluctuations in future TFP related to contemporaneous shocks. %$\varepsilon_t$ is simply considered as a reduced-form residual. 
This suggests that we can rely on a combination of the Barsky and Sims (2011) strategy and the implications of supply-demand theory to simultaneously identify our news shock, $V_{t-1}$, and our IT shock, $IT_{t-1}$. In particular, our second identification strategy can be summarized as the following algorithm:

\begin{enumerate}
	\item The news shock $V_{t-1}$ maximizes the FEV of future TFP subject to the restriction that it has no effect on the relative price $\frac{P^{IT}}{P}$ in the long run;
	\item The IT shock maximizes the remaining FEV of future TFP.
    \item The tech shock $\varepsilon_t$ is considered as a residual shock and is left unrestricted;
\end{enumerate}

\subsection{Second Set of Results}

We still need to implement this identification strategy.

\end{document}

### 2017-11-15 Latex/Macro_Lunch_Proposal/comments.tex
adding all the latex documents

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper,top=3.5cm,bottom=3.5cm,left=3.5cm,right=3.5cm,%
bindingoffset=0mm]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.75em depth0em\fi}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{float}
\linespread{1.3}
\raggedbottom

%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\R}{\mathbb{R}}
\DeclareMathOperator{\E}{\mathbb{E}}
%

\title{Innovation and Productivity Growth Slowdown}
\author{Moran and Queralto}
\date{2017}

\begin{document}

\maketitle

\section{Introduction}

Growth in TFP has slowed dramatically in recent years. Weak productivity growth has been widespread across advanced economies. This development has caused concern for policymakers, and at the same time has sparked an intense debate on its possible causes. A recent but growing literature in macroeconomics incorporates endogenous TFP growth mechanism within the modern quantitative frameworks, following the lead of Comin and Gertler (2006). The first goal of this paper is to shed light on the empirical role of innovation in driving productivity growth. To this end, we use SVAR methods to investigate such hypothesis. Our measure of innovation is business-sector R\&D expenditure. Our goal is to develop a baseline macroeconomic model with endogenous innovation and adoption to use the findings from the VAR abalysis to discipline the effects of innovation on TFP in the model.

The VAR analysis suggests that a rise in R\&D induces a gradual, persistent increase in TFP. We also find that in more R\&D-intensive countries, the effect of R\&D on TFP is stronger. Interestingly, we also find that stock prices tend to immediately jump in response to the R\&D shocks we identify. This result reminds the new shock introduced by Beaudry and Portier (2006).

Turning to the model analysis, we find that the endogenous growth mechanism accounts for a significant share of the recent TFP slowdown. We also consider the question of how much of the productivity slowdown is due to the Great Recession, relative to factors that predate it. We find that the sharp decline in R\&D during the crisis likely contributed significantly to the subsequent low TFP growth. Finally, the model suggests large adverse effects due to the ZLB.

\section{Evidence}

The basic approach consists in identifying shocks in private R\&D expenditure, and then tracing out their dynamic effect on TFP.

\subsection*{United States}

They begin with a small-scale empirical model for the US. Our reduced-form empirical specification is a first-order VAR:
\begin{equation}
\begin{bmatrix}
GDP_t^{us} \\
TFP_t^{us} \\
R\&D_t^{us} \\
\end{bmatrix} = c^{us} + B^{us} \begin{bmatrix}
GDP_{t-1}^{us} \\
TFP_{t-1}^{us} \\
R\&D_{t-1}^{us} \\ 
\end{bmatrix} + u_t^{us}
\end{equation}
all the variables are in logs, the frequency is annual, and the observations start in 1953.

To identify structural shocks to R\&D they rely on a Choleski identification procedure. Restrictions are: (1) zero-impact effect of R\&D on TFP, (2) zero-impact effect of R\&D on GDP, and (3) zero-impact effect of TFP on GDP. Results are not affected if GDP is contemporaneously affected by R\&D and TFP.\footnote{In other words, GDP is third in the VAR.}

A rise in R\&D for reasons unrelated to current fundamentals accelerates the development of technological innovations which after some time become implemented in production and eventually improve firms' productivity. There is however the risk of reverse causality. If firms can foresee the future rise in TFP, they could respond by increasing R\&D expenditure because they believe that the new technologies will now be more profitable. One way to test for this possibility is to repeat the analysis reported above, but using aggregate investment in place of R\&D. The idea is that just a R\&D shock should trigger an increase in TFP and not an investment shock. Performing the same analysis using investment, they obtain that an investment shock does not trigger any significant increase in TFP (supporting their causality argument).

\subsection*{Panel of advanced economies}

We next explore if such a result holds in a sample of advanced economies (AE). The data consists of a panel of 21 AEs (not including the US) in the post-1980 period. Data on business-sector R\&D expenditure is from the OECD. We evaluate
\begin{equation}
\begin{bmatrix}
GDP_{i,t}^{us} \\
TFP_{i,t}^{us} \\
R\&D_{i,t}^{us} \\
\end{bmatrix} = c_i^{us} + B^{us} \begin{bmatrix}
GDP_{i,t-1}^{us} \\
TFP_{i,t-1}^{us} \\
R\&D_{i,t-1}^{us} \\ 
\end{bmatrix} + u_{i,t}^{us}
\end{equation}
The system contains a vector of country fixed effects $c_i$, thus allowing estimation of the country-specific intercept term for each country in the sample. The model, however, imposes the matrix B as well as the variance-covariance matrix of the residual $u_{i,t}$ to be common across countries.\footnote{The identification assumption is that the relation of R\&D and TFP is the same across countries.}

As in the case of the US, a rise in R\&D induces a gradual, persistent rise in TFP. The main difference is that the effect seems to be much weaker and the peak happens to be much later. They conclude that R\&D is less powerful in affecting TFP in the AEs.

Finally, we have found a degree of heterogeneity across countries. The effect of TFP tends to be stronger in countries with higher ratios of private R\&D to GDP.

\subsection*{Spillover from the US R\&D to foreign TFP}

A natural question to ask when analyzing TFP development across countries is whether there are cross-country R\&D spillovers, i.e. if R\&D expenditure in one given country may benefit productivity in other countries. To this end, we next specify a VAR which allows for spillovers from US variables to foreign-economy variables. We suppose that foreign variables cannot affect US variables (neither contemporaneous nor with one lag). Our focus is on whether foreign TFP responds to US R\&D shocks. They do not find spillovers for the full sample but they do find it focusing on high research intensity countries.

\subsection*{A large-scale US VAR}

For robustness, we next estimate a higher-dimensional VAR for the US, including a standard set of macroeconomic variables. The estimated model provides interesting information on the effects of R\&D shocks on a large number of variables. We additionally include the logs of investment, consumption, and stock prices and the levels of federal fund rate and inflation. All these added variables are free to respond contemporaneously to R\&D shocks.

The pattern of responses of R\&D and TFP is largely unchanged relative to the tree-variable VAR. The effect on GDP, consumption, and investment is weak but it mimics the TFP one. Inflation declines significantly as TFP rises.

Interestingly, stock prices immediately jump in response to R\&D shock. This dynamic pattern is reminiscent of the findings by Beaudry and Portier (2006) and related literature of news shocks.

\section{Model}

\section{Estimation of the Model}

\section{Experiments}

\section{Conclusions}

\end{document}

### 2017-11-15 Latex/Ryan_first_meeting/our_exposition.tex
adding all the latex documents

--- 2017-11-15 Latex/First_draft/first_draft.tex
@@
 
-\title{First Draft}
+\title{Presentation}
 \author{Marco Brianti\\Laura Gati}
-\date{August 2017}
+\date{Fall 2017}
 
@@
 
-	\section{Introduction}
+\subsection*{Related Literature}
 
-	The basic idea is to rationalize a setting where incorrect information implies fundamental changes in the economy.
-To this end, we rely on the model proposed by Comin and Gertler (2006) which we enhance with a particular information structure derived from Lorenzoni (2009) in order to show how noisy signals can affect the real structure of the economy.
-In particular, Comin and Gertler (2006) propose a setting where TFP can be endogenously affected due to R\&D expenditure.
-After a negative shock, due to lack of resources, agents will decrease (among other variables) R\&D expenditure and thus affect the endogenous component of TFP.
-As a result, the lower level of TFP will trigger a negative spiral causing a much slower recovery than with a simple negative TFP shock.
+\
 
-	In order to introduce imperfect information appropriately, we consider the main structure of the model.
-In this economy, the final good can be either consumed, invested in physical capital, or spent as R\&D.
-The marginal benefit of allocating the final good into one or another sector will depend on the utility function, the price of investment and the efficiency of research sector, respectively.
-It is obvious that differently from the first two variables, the efficiency of the R\&D sector is much more difficult to observe.
-Indeed, this process is related to a huge amount of variables such as the probability of succeeding, the demand for this new technology, the existence of prospective competitors, and so on and so forth.
-Since many of these factors are unobserved or pertain to the future, we thus assume that R\&D efficiency is not fully observed and the optimal level of research expenditure will be decided as the outcome of agents' inference problem concerning this variable.
+Comin and Gertler (2006) - Endogenous TFP component
 
+\
+
+Lorenzoni (2009) - Noise shocks
+
+\subsection*{Main Contribution}
+
+\
+
+The basic idea is to rationalize a setting where incorrect information (noise a la Lorenzoni, 2009) implies fundamental changes in the economy.
+The account in Lorenzoni (2009) documents how noisy information leads to business cycle fluctuations that resemble demand shocks.
+Instead our objective is to demonstrate how similar information imperfections can also imply future supply shocks and thus affectively alter the fundamental structure of the economy.
+
+\subsection*{Implementation}
+
+\
+
+To this end, we rely on the model proposed by Comin and Gertler (2006) which we enhance with a particular information structure derived from Lorenzoni (2009).
 To understand the main mechanism of the model, consider a simple example.
@@
 However, the choice to invest less in R\&D leads to lower productivity in the future, so that the economy will in fact experience a negative productivity shock.
-In other words, in this theoretical exercise a shock to beliefs is able to trigger a future fundamental shock, analogously to a self-fulfilling prophecy.
-
-	The goal of this paper, then, is to exploit a simple but well-accepted model to show how wrong information may affect the structure of the economy beyond the business cycle effects well documented in the literature.
-In particular, the effects of imperfect information here are starkly different than in Lorenzoni (2009).
-The account in Lorenzoni (2009) documents how noisy information leads to business cycle fluctuations that resemble demand shocks.
-Instead our objective is to demonstrate how similar information imperfections can also imply future supply shocks and thus affectively alter the fundamental structure of the economy.
-
-	\section{Two-Period Model}
-
-	An agent seeks to maximize her utility,
-	\begin{equation}
-	U(C_0) + \beta^t U(C_1)
-	\end{equation}
-	where $C_i$ represents the level of consumption at period $i$, $\beta \in [0 \ 1]$ is the deterministic discount factor, and the time separable utility function provides the standard property $U'(\cdot)>0$ and  $U''(\cdot) < 0$.
-
-	The budget constraints are represented by
-	\begin{equation}
-	C_0 \leq Y_0 - I_0 - S_0
-	\end{equation}
-	and
-	\begin{equation}
-	C_1 \leq Y_1
-	\end{equation}
-	where $Y_0$ is the level of production of consumption good in period $0$ which can be either consumed, invested in physical capital ($I_0$ ), or spent in research and development ($S_0$).
-While $Y_1$ is the level of output in the second period and will be fully consumed.
-The level of output is defined by the following production function
-	\begin{equation}
-	Y_i \leq A Z_i F(K_i) \ \ \ \text{for} \ i = 1,2
-	\end{equation}
-	where $A$ represents the exogenous level of technology, $Z_i$ represents the endogenous level of technology which is given in the first period and chosen in the second.
-Similarly, $K_i$ represents the level of capital which is given in the first period and chosen in the second.
-$F(\cdot)$ is the production function which uses capital $K_i$ as unique input factor and it displays the standard assumptions $F'(\cdot) > 0$ and $F''(\cdot) < 0$.
-
-	The level of endogenous technology and capital is defined respectively by the following laws of motion
-	\begin{equation}
-	Z_{1} \leq \lambda S_0 + Z_0
-	\end{equation}
-	\begin{equation}
-	K_{1} \leq I_0 + (1 - \delta)K_0
-	\end{equation}
-	where $\lambda \in [0 \ 1]$ represents the exogenous efficiency of the $R\&D$ sector.
-It can be interpreted as the probability of producing a new technology by spending a unit of consumption good in the research sector.
-
-	In compact form the agent seeks to solve the following problem
-	\begin{equation}
-	\begin{split}
-	\max_{\{ C_0,C_1,Y_0,Y_1,I_0,S_0,K_{1},Z_{1} \}} &U(C_0) + \beta U(C_1) \\
-	\text{s.t.} \ \ \ C_0 &\leq Y_0 - I_0 - S_0 \\
-	C_1 &\leq Y_1 \\
-	Y_i &\leq A Z_i F(K_i) \ \ \ \text{for} \ i = 1,2 \\
-	Z_{1} &\leq \lambda S_0 + Z_0 \\
-	K_{1} &\leq I_0 + (1 - \delta)K_0 \\
-	\end{split}
-	\end{equation}
-
-	Set up the Lagrangian
-	\begin{equation}
-	\begin{split}
-	L =  U(C_0) + \beta U(C_1)  + &\mu_{1}\big[ Y_0 - I_0 - S_0 - C_0   \big]  + \mu_{2}\big[  A Z_0 F(K_0) - Y_0  \big]  \\
-	+ &\mu_{3}\big[ \lambda S_0 + Z_0 -  Z_{1}  \big]   + \mu_{4}\big[ I_0 + (1 - \delta)K_0 -  K_{1}  \big]  \\
-	+ &\beta \mu_5 \big[  AZ_1 K_1^{\alpha} - Y_1  \big] + \beta \mu_6 \big[  Y_1 - C_1   \big]
-	\end{split}
-	\end{equation}
-	and the derive the first order conditions
-	\begin{equation}
-	U'(C_0) = \mu_{1}
-	\end{equation}
-	\begin{equation}
-	U'(C_1) = \mu_{6}
-	\end{equation}
-	\begin{equation}
-	\mu_{1} = \mu_{2}
-	\end{equation}
-	\begin{equation}
-	\mu_{1} = \mu_{4}
-	\end{equation}
-	\begin{equation}
-	\mu_{1} = \lambda \mu_{3}
-	\end{equation}
-	\begin{equation}
-	\mu_{3} = \beta  \mu_{5} A F(K_{1})
-	\end{equation}
-	\begin{equation}
-	\mu_4 = \beta  \mu_{5} A Z_{1} F'(K_{1})
-	\end{equation}
-	\begin{equation}
-	\mu_5 = \mu_{6}
-	\end{equation}
-	\begin{equation}
-	C_0 = Y_0 - I_0 - S_0
-	\end{equation}
-	\begin{equation}
-	C_1 = Y_1
-	\end{equation}
-	\begin{equation}
-	Y_i = A Z_i F(K_i) \ \ \ \text{for} \ i = 1,2
-	\end{equation}
-	\begin{equation}
-	Z_{1} = \lambda S_0 + Z_0
-	\end{equation}
-	\begin{equation}
-	K_{1} = I_0 + (1 - \delta)K_0
-	\end{equation}
-
-	Combining (9), (10), (12), (15), and (16) yields
-	\begin{equation}
-	1 =  \beta \frac{U'(C_{1})}{U'(C_0)}  A Z_{1} F'(K_{1}) 
-	\end{equation}
-	Moreover, combining (9), (10), and (12)-(15) yields
-	\begin{equation}
-	1 =  \beta \frac{U'(C_{1})}{U'(C_0)} \lambda  A F(K_{1}) 
-	\end{equation}
-
-	Notice that Equations (17)-(23) form a system of eight Equations in eight unknowns: $C_0$, $C_1$ $Y_0$, $Y_1$ $I_0$, $S_0$, $Z_{1}$, and $K_{1}$.
-
-	\subsection*{Further Assumptions}
-
-	Without loss of generality assume that the $U(C_i) = \log(C_i)$ and $F(K_i) = K_i^{\alpha}$ for $i = 1,2$. The model then yields
-
-	\begin{equation}
-	C_0 = Y_0 - I_0 - S_0
-	\end{equation}
-	\begin{equation}
-	C_1 = Y_1
-	\end{equation}
-	\begin{equation}
-	Y_0 = A Z_0 K_0^{\alpha}
-	\end{equation}
-	\begin{equation}
-	Y_1 = A Z_1 K_1^{\alpha}
-	\end{equation}
-	\begin{equation}
-	Z_{1} = \lambda S_0 + Z_0
-	\end{equation}
-	\begin{equation}
-	K_{1} = I_0 + (1 - \delta)K_0
-	\end{equation}
-	\begin{equation}
-	1 =  \beta \frac{C_{0}}{C_1}  \alpha A Z_{1} K_{1}^{\alpha - 1}
-	\end{equation}
-	\begin{equation}
-	1 =  \beta  \frac{C_{0}}{C_1} \lambda  A K_{1}^{\alpha} 
-	\end{equation}
-
-	\subsection*{Solution}
-
-	Substitute (26) into (24) and obtain
-	\begin{equation}
-	C_0 = A Z_0 K_0^{\alpha} - I_0 - S_0
-	\end{equation}
-	Substitute (28) and (29) into (27) and use (25) to obtain
-	\begin{equation}
-	C_1 = A (\lambda S_0 + Z_0) (I_0 + (1 - \delta)K_0)^{\alpha}
-	\end{equation}
-	Substitute (28), (29), (32), and (33) into (30) and (31) and obtain
-	\begin{equation}
-	1 = \alpha \beta \frac{A Z_0 K_0^{\alpha} - I_0 - S_0}{I_0 + (1 - \delta)K_0}
-	\end{equation}
-	and
-	\begin{equation}
-	1 = \lambda \beta \frac{A Z_0 K_0^{\alpha} - I_0 - S_0}{\lambda S_0 + Z_0}
-	\end{equation}
-
-	This is a system of two equations (34) and (35) in two unknowns $S_0$ and $I_0$ and its solution is
-	\begin{equation}
-	\begin{split}
-	S_0 &= \frac{\beta}{1 + \beta+ \alpha \beta}[AZ_0 K_0^{\alpha} + (1-\delta)K_0] - \Bigg( \frac{1 + \alpha \beta}{1 + \beta + \alpha \beta} \Bigg) \lambda^{-1} Z_0 \\
-	I_0 &= \alpha S_0 - (1-\delta)K_0 + \alpha \lambda^{-1} Z_0  \\
-	\end{split}
-	\end{equation}
-	\begin{prop}
-		$S_0$ is increasing in $\lambda$
-	\end{prop}
-	\begin{proof}
-		\begin{equation}
-		\frac{\partial S_0}{\partial \lambda} = \Bigg( \frac{1 + \alpha \beta}{1 + \beta + \alpha \beta} \Bigg) \lambda^{-2} Z_0 > 0   \qed
-		\end{equation}
-	\end{proof}
-
-	\subsection*{Imperfect Information}
-
-	Assume that $\lambda$, the efficiency of the R\&D sector, cannot be directly observable and takes the form
-	\begin{equation}
-	\lambda = \lambda_m + \varepsilon,
-	\end{equation}
-	where $\varepsilon$ is a mean zero and finite variance shock which deviate the value of $\lambda$ from the known expected value $\lambda_m$. The agent is instead able to observe the following signal
-	\begin{equation}
-	\lambda_s = \lambda + \eta
-	\end{equation}
-	where $\eta$ is a second mean zero and finite variance shock fully independent from $\varepsilon$ which prevents the agent to have access to a complete information setup.
-
-	\subsection*{Inference}
-
-	Agent seeks to minimize the error between $\lambda$ and $\lambda_s$ using standard Kalman filter techniques.
-	\begin{equation}
-	\begin{split}
-	\beta_k &= \frac{Cov(\lambda,\lambda_s)}{Var(\lambda_s)} \\
-	&= \frac{Cov(\lambda_m + \varepsilon, \lambda_m + \varepsilon + \eta)}{Var(\lambda_m + \varepsilon + \eta)} \\
-	&= \frac{\sigma_{\varepsilon}}{\sigma_{\eta} + \sigma_{\varepsilon}}
-	\end{split}
-	\end{equation}
-	and
-	\begin{equation}
-	\begin{split}
-	\alpha_k &= \E[\lambda] - \beta_k \E[\lambda_s] \\
-	&= (1 - \beta_k) \lambda_m \\
-	&= \frac{\sigma_{\eta}}{\sigma_{\eta} + \sigma_{\varepsilon}} \lambda_m
-	\end{split}
-	\end{equation}
-	which implies that
-	\begin{equation}
-	\begin{split}
-	\E[\lambda|\lambda_s] &= \alpha_k + \beta_k \lambda_s \\
-	&=  \frac{\sigma_{\eta}}{\sigma_{\eta} + \sigma_{\varepsilon}} \lambda_m + \frac{\sigma_{\varepsilon}}{\sigma_{\eta} + \sigma_{\varepsilon}} \lambda_s \\
-	&=  \frac{\sigma_{\eta}}{\sigma_{\eta} + \sigma_{\varepsilon}} \lambda_m + \frac{\sigma_{\varepsilon}}{\sigma_{\eta} + \sigma_{\varepsilon}} (\lambda_m + \lambda_s  - \lambda_m) \\
-	&= \lambda_m + \frac{\sigma_{\varepsilon}}{\sigma_{\eta} + \sigma_{\varepsilon}} (\lambda_s  - \lambda_m) \\
-	\end{split}
-	\end{equation}
-
-	\subsection*{Noise Shocks}
-
-	Assume $\varepsilon = 0$ and $\eta = \tilde{\eta} > 0$.
-It is clear that even if $\lambda = \lambda_m$, agent is just able to observe $\lambda_s = \lambda_m + \tilde{\eta}$.
-This implies that the perceived value of $\lambda$ is
-	\begin{equation}
-	\E[\lambda | \lambda_s] = \lambda_p = \lambda_m + \frac{\sigma_{\varepsilon}}{\sigma_{\eta} + \sigma_{\varepsilon}} \tilde{\eta}
-	\end{equation}
-	This implies that the R\&D expenditure will be strictly higher even if the level of $\lambda$ is completely unaffected which entails a greater level of technology due to a noise shock.
-
-	\section{The Analytical Model - To be completed}
-
-	An agent seeks to maximize her life-time utility,
-	\begin{equation}
-	\sum_{t=0}^{\infty} \beta^t U(C_t)
-	\end{equation}
-	where $C_t$ represents the level of consumption at period $t$, $\beta \in [0 \ 1]$ is the deterministic discount factor, and the time separable utility function provides the standard property $U'(\cdot)>0$ and  $U''(\cdot) < 0$.
-
-	The budget constraint is represented by
-	\begin{equation}
-	C_t \leq Y_t - I_t - S_t
-	\end{equation}
-	where $Y_t$ is the level of production of consumption good which can be either consumed, invested in physical capital ($I_t$ ), or spent in research and development ($S_t$).
-The level of output is endogenously defined by the following production function
-	\begin{equation}
-	Y_t \leq A_t Z_t F(K_t)
-	\end{equation}
-	where $A_t$ and $Z_t$ represent respectively the exogenous and endogenous level of technology in the economy.
-$F(\cdot)$ is the production function which uses capital $K_t$ as unique input factor and it displays the standard assumptions $F'(\cdot) > 0$ and $F'(\cdot) < 0$.
-
-	The level of endogenous technology and capital is defined respectively by the following laws of motion
-	\begin{equation}
-	Z_{t+1} \leq \lambda_t S_t + Z_t
-	\end{equation}
-	\begin{equation}
-	K_{t+1} \leq I_t + (1 - \delta)K_t
-	\end{equation}
-	where $\lambda_t \in [0 \ 1]$ represents the exogenous efficiency of the $R\&D$ sector.
-It can be interpreted as the probability of producing a new technology by spending a unit of consumption good in the research sector.
-
-	In compact form the agent seeks to solve the following problem
-	\begin{equation}
-	\begin{split}
-	\max_{\{ C_t,Y_t,I_t,S_t,K_{t+1},Z_{t+1} \}_{t=0}^{\infty}} &\sum_{t=0}^{\infty} \beta^t U(C_t) \\
-	\text{s.t.} \ \ \ C_t &\leq Y_t - I_t - S_t \\
-	Y_t &\leq A_t Z_t F(K_t) \\
-	Z_{t+1} &\leq \lambda_t S_t + Z_t \\
-	K_{t+1} &\leq I_t + (1 - \delta)K_t \\
-	\end{split}
-	\end{equation}
-
-	Set up the Lagrangian
-	\begin{equation}
-	\begin{split}
-	L = \sum_{t=0}^{\infty} \beta^t \Big\{ U(C_t)  + &\mu_{1,t}\big[ Y_t - I_t - S_t - C_t   \big]  + \mu_{2,t}\big[  A_t Z_t F(K_t) - Y_t  \big]  \\
-	+ &\mu_{3,t}\big[ \lambda_t S_t + Z_t -  Z_{t+1}  \big]   + \mu_{4,t}\big[ I_t + (1 - \delta)K_t -  K_{t+1}  \big]  \Big\}
-	\end{split}
-	\end{equation}
-	and the derive the first order conditions
-	\begin{equation}
-	U'(C_t) = \mu_{1,t}
-	\end{equation}
-	\begin{equation}
-	\mu_{1,t} = \mu_{2,t}
-	\end{equation}
-	\begin{equation}
-	\mu_{1,t} = \mu_{4,t}
-	\end{equation}
-	\begin{equation}
-	\mu_{1,t} = \lambda_t \mu_{3,t}
-	\end{equation}
-	\begin{equation}
-	\beta \E_t [ \mu_{2,t+1} A_{t+1} Z_{t+1} F'(K_{t+1}) + \mu_{4,t+1}(1-\delta) ] = \mu_{4,t}
-	\end{equation}
-	\begin{equation}
-	\beta \E_t [ \mu_{2,t+1} A_{t+1} F(K_{t+1}) + \mu_{3,t+1} ] = \mu_{3,t}
-	\end{equation}
-	\begin{equation}
-	C_t = Y_t - I_t - S_t
-	\end{equation}
-	\begin{equation}
-	Y_t = A_t Z_t F(K_t)
-	\end{equation}
-	\begin{equation}
-	Z_{t+1} = \lambda_t S_t + Z_t
-	\end{equation}
-	\begin{equation}
-	K_{t+1} = I_t + (1 - \delta)K_t
-	\end{equation}
-
-	Combining (8)-(10) and (12) yields
-	\begin{equation}
-	1 = \E_t \Bigg\{ \beta \frac{U'(C_{t+1})}{U'(C_t)} \big[   1  + A_{t+1} Z_{t+1} F'(K_{t+1}) - \delta \big]   \Bigg\}
-	\end{equation}
-	Moreover, combining (8), (9), (11), and (13) yields
-	\begin{equation}
-	1 = \E_t \Bigg\{ \beta \frac{U'(C_{t+1})}{U'(C_t)} \frac{\lambda_t}{\lambda_{t+1}} \Bigg[ 1 + \lambda_{t+1}  A_{t+1}F(K_{t+1}) \Bigg]   \Bigg\}
-	\end{equation}
-
-	Notice that Equations (14)-(19) form a system of six Equations in six unknowns: $C_t$, $Y_t$, $I_t$, $S_t$, $Z_{t+1}$, and $K_{t+1}$.
-
-	\subsection*{Further Assumption}
-
-	For simplicity assume the $U(C_t) = \log(C_t)$ and $F(K_t) = K_t^{\alpha}$. The model becomes
-	\begin{equation}
-	C_t = Y_t - I_t - S_t
-	\end{equation}
-	\begin{equation}
-	Y_t = A_t Z_t K_t^{\alpha}
-	\end{equation}
-	\begin{equation}
-	Z_{t+1} = \lambda_t S_t + Z_t
-	\end{equation}
-	\begin{equation}
-	K_{t+1} = I_t + (1 - \delta)K_t
-	\end{equation}
-	\begin{equation}
-	1 = \E_t \Bigg\{ \beta \frac{C_t}{C_{t+1}} \big[   1  + \alpha A_{t+1} Z_{t+1} K_{t+1}^{\alpha - 1} - \delta \big]   \Bigg\}
-	\end{equation}
-	\begin{equation}
-	1 = \E_t \Bigg\{ \beta \frac{C_t}{C_{t+1}} \frac{\lambda_t}{\lambda_{t+1}} \big[ 1 + \lambda_{t+1}  A_{t+1} K_{t+1}^{\alpha} \big]   \Bigg\}
-	\end{equation}
-
-\section{Dynamic Model}
-
-\subsection{Household}
-
-A representative household seeks to maximize her life-time utility,
-\begin{equation}
-\sum_{t=0}^{\infty} \beta^t [ log(C_t) - \chi L_t^{\theta}]
-\end{equation}
-The budget constraint is represented by
-\begin{equation}
-C_t + K_{t+1} + S_t = W_tL_t + (1- \delta + R_{t})K_t + \Pi_t
-\end{equation}
-where $S_t$ is the investment in R\&D and $\Pi_t$ is a lump-sum transfer from the profits of the intermediate-good sector.
-
-First order conditions over $C_t$, $L_t$, and $K_{t+1}$ yield
-\begin{equation}
-\frac{1}{C_t} = \chi \frac{L_t^{\theta - 1} }{W_t}
-\end{equation}
-\begin{equation}
-1 = \beta \E_t \bigg[\frac{C_t}{C_{t+1}} (1 - \delta + R_{t+1})  \bigg]
-\end{equation}
-
-\subsection{Final-good producer}
-
-A representative final-good producer maximizes its own profits using the following production function
-\begin{equation}
-\begin{aligned}
-Y_t &= A_t[K_t^{\alpha}L_t^{1 - \alpha}]^{1 - \gamma} \bigg[ \bigg( \int_0^{Z_t} M_{j,t}^{\frac{1}{\nu}} dj \bigg)^{\nu} \bigg]^{\gamma} \\
-    &= A_t[K_t^{\alpha}L_t^{1 - \alpha}]^{1 - \gamma} M_t^{\gamma} Z_t^{\gamma \nu} \\
-    &= A_t Z_t^{\nu}[K_t^{\alpha}L_t^{1 - \alpha}]^{1 - \gamma} [M_t Z_t]^{\gamma}
-\end{aligned}
-\end{equation}
-where $Z_t^{\nu}$ represents the endogenous component of productivity and $M_{j,t}$ is an intermediate good. It will be shown that all $M_{j,t}$ are equal to each other on the equilibrium path.
-
-Firm's first order conditions over $K_t$, $L_t$, and $M_{j,t}$ yield
-\begin{equation}
-W_t = (1 - \gamma)(1 - \alpha) \frac{Y_t}{L_t}
-\end{equation}
-\begin{equation}
-R_t = (1 - \gamma)\alpha \frac{Y_t}{K_t}
-\end{equation}
-\begin{equation}
-P^M_t = \gamma \frac{Y_t}{Z_t M_t}
-\end{equation}
-where $W_t$, $R_t$, and $P^M_t$ are the price of each respective factor.
-
-\subsection{Intermediate-good producer}
-
-Intermediate-good producers compete in a imperfect monopolistic market. Due to absence of any frictions, the Dixit–Stiglitz aggregator provides an optimal price equal to
-\begin{equation}
-P_t^M = \nu
-\end{equation}
-For each monopolist, profits will then be
-\begin{equation}
-\Pi_t = (P_t^M - 1)M_t
-\end{equation}
-
-\subsection{R\&D Sector}
-
-The value of being a monopolist is
-\begin{equation}
-V_t = \Pi_t + \phi \beta \E \bigg[ \frac{C_t}{C_{t+1}}  V_{t+1} \bigg]
-\end{equation}
-However, to became a monopolist, innovator needs to meet a free entry condition that implies
-\begin{equation}
-\frac{1}{\lambda_t} = \phi \beta \E \bigg[ \frac{C_t}{C_{t+1}}  V_{t+1} \bigg]
-\end{equation}
-where the law of motion of endogenous TFP is
-\begin{equation}
-Z_{t+1} = \lambda_t S_t + \phi Z_t
-\end{equation}
-and
-\begin{equation}
-\lambda_t = \lambda_x \frac{1}{K_t^{\rho}S_t^{1 - \rho}}
-\end{equation}
-
-\subsection{System of equations}
-
-We have 13 variables: $C_t$, $K_{t+1}$, $L_t$, $W_t$, $R_t$, $P_t$, $Y_t$, $\Pi_t$, $V_t$, $Z_{t+1}$, $S_t$, $\lambda_t$, and $M_t$ in 13 equations:
-
-\begin{equation}
-\frac{1}{C_t} = \chi \frac{L_t^{\theta - 1} }{W_t}
-\end{equation}
-\begin{equation}
-1 = \beta \E_t \bigg[\frac{C_t}{C_{t+1}} (1 - \delta + R_{t+1})  \bigg]
-\end{equation}
-\begin{equation}
-C_t + K_{t+1} + S_t = W_tL_t + (1- \delta + R_{t})K_t + \Pi_t
-\end{equation}
-\begin{equation}
-W_t = (1 - \gamma)(1 - \alpha) \frac{Y_t}{L_t}
-\end{equation}
-\begin{equation}
-R_t = (1 - \gamma)\alpha \frac{Y_t}{K_t}
-\end{equation}
-\begin{equation}
-P^M_t = \gamma \frac{Y_t}{Z_t M_t}
-\end{equation}
-\begin{equation}
-P_t^M = \nu
-\end{equation}
-\begin{equation}
-\Pi_t = (P_t^M - 1)M_t
-\end{equation}
-\begin{equation}
-V_t = \Pi_t + \phi \beta \E \bigg[ \frac{C_t}{C_{t+1}}  V_{t+1} \bigg]
-\end{equation}
-\begin{equation}
-Z_{t+1} = \lambda_t S_t + \phi Z_t
-\end{equation}
-\begin{equation}
-\frac{1}{\lambda_t} = \phi \beta \E \bigg[ \frac{C_t}{C_{t+1}}  V_{t+1} \bigg]
-\end{equation}
-\begin{equation}
-Y_t = A_t[K_t^{\alpha}L_t^{1 - \alpha}]^{1 - \gamma}Z_tM_t^{\gamma}
-\end{equation}
-\begin{equation}
-\lambda_t = \lambda_x \frac{1}{K_t^{\rho}S_t^{1 - \rho}}
-\end{equation}
 

### 2017-11-21 Latex/Meeting_Ryan_22_Nov_2017/meeting22Nov2017.tex
wrote latex file for meeting Ryan on Nov 22, 2017

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper,top=1.5cm,bottom=1.5cm,left=1.5cm,right=1.5cm,%
bindingoffset=0mm]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.75em depth0em\fi}
\usepackage{tikz}
\usepackage{graphicx}
%\graphicspath{{./Figures/}}
\def \ourFigPath {../../} % this should move up two steps but it isn't working 
% . = current directory
 % .. = parent directory
\usepackage{rotating}
\usepackage{float}
\linespread{1.3}
\raggedbottom

%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\R}{\mathbb{R}}
\DeclareMathOperator{\E}{\mathbb{E}}
%

\title{Discussion of Results}
\author{Marco Brianti\\Laura Gati}
\date{22 Nov 2017}

\begin{document}

\maketitle

\subsection*{Shares of FEV of TFP}

\

\textbf{Differenced relative prices (inflation of IT price index over CPI-inflation)}

IT: 51.60\%

\noindent News: 19.63\%

\

 \textbf{Log level of capital prices (differencing here seems to overdo it)}

IT: 28.47\%

\noindent News: 28.31\%

\newpage
\subsection*{IRFs - ratio of inflations (i.e relative prices)}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_shock_Ryan_two_stepsID_20-Nov-2017_12_24_34}
\caption{News shock - ratio of inflations}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_shock_Ryan_two_stepsID_20-Nov-2017_12_24_39}
\caption{IT shock - ratio of inflations}
\end{figure}

%%%%%
\newpage
\subsection*{IRFs - log level of capital prices}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_21-Nov-2017_11_35_24}
\caption{News shock - log level of capital prices}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_21-Nov-2017_11_35_27}
\caption{IT shock - log level of capital prices}
\end{figure}

\newpage
\subsection*{Recap and interpretation}

\begin{itemize}
\item One big motivation for the entire research project is the puzzling decrease in TFP growth, which - as we have also documented - started \emph{before} the Great Recession.
\item The sudden decrease in IT investment after the burst of the IT bubble around 2000-2002 coincides with this slowdown in TFP growth, which led us to investigate the effect of IT investment on TFP. 
\item We run a structural VAR to estimate the effect of an IT productivity shock on TFP and other main macroeconomic variables.
\item This identification poses a challenge because we need to confront the view that there is an endogenous channel in the evolution of TFP with the widely accepted view that TFP is driven by news. Since both are similar in the way they affect TFP only with lags, we need an additional restriction to disentangle the two.
\item The additional restriction we use is that news shocks should have no effect on relative IT prices at a certain (long) horizon, because they behave like demand shocks.
\item [] \textbf{What the results seem to suggest:}
\item [1)] News and IT shocks together explain more of the FEV of TFP than news does alone in Barsky \& Sims (around 70\% vs approximately 40\% in Barsky \& Sims). (Compare with capital prices specification too.)
\item [2)] News still explains a considerable fraction, but IT shocks explain more. (Compare with capital prices specification too.)
\item [] $\rightarrow$ we read this as evidence that both news and the endogenous channel via IT investment plays an important role in explaining TFP  over the business cycle and the medium run. 
\end{itemize}

\subsection*{Comments? Thoughts? Does this make sense to you? Is it presentable in its current form?}

\end{document}

### 2017-11-21 main_file_SVAR_RyansID.m

@@ -82,11 +82,13 @@ for i_simul = 1:nsimul
 end
 
 %Creating and Printing figures
-print_figs = 'no';
+print_figs = 'yes';
 [IRFs, ub, lb] = genIRFs(fake_impact,fake_impact_boot,B,beta_tilde_star,H,sig);
 plotIRFs(IRFs,ub,lb,40,which_shocks,shocknames,varnames, which_ID,print_figs)
 
-save('capital_price_workspace')
+
+
+%save('capital_price_workspace')
 
 % %%%%%%% Saved work from before really implementing Kilian, uncomment all
 % %%%%%%% of this if the real Kilian stuff are superbad - although the two

### 2017-11-24 Latex/general_writeup.tex
Playing around with different specifications
In order to do that, I’ve also changed some things:
1.) Written a code called invoke_matrix_outputting.m, which generates a
table containing the FEVs.
2.) implemented inputting the stuff to the server, so that we can run 2
things at the same time.

--- 2017-11-21 Latex/Meeting_Ryan_22_Nov_2017/meeting22Nov2017.tex
@@
 \usepackage{graphicx}
-%\graphicspath{{./Figures/}}
-\def \ourFigPath {../../} % this should move up two steps but it isn't working 
-% . = current directory
- % .. = parent directory
+\def \ourFigPath {../} 
+\usepackage{subfigure}
 \usepackage{rotating}
@@
 
-\title{Discussion of Results}
+\title{General writeup}
 \author{Marco Brianti\\Laura Gati}
-\date{22 Nov 2017}
+\date{August 2017}
 
@@
 
-\subsection*{Shares of FEV of TFP}
+	\section{VAR Results - Comparison of different specifications}
 
-\
+	\subsection{Relative prices LR horizon 8}
+	\noindent Time it took, for 500 bootstrap, Mac: 61 min
 
-\textbf{Differenced relative prices (inflation of IT price index over CPI-inflation)}
+	\noindent  Time it took, for 500 bootstrap, server (w/o parpool): 140 min
 
-IT: 51.60\%
+	\noindent  Time it took, for 500 bootstrap, server (w/ parpool): ? min
 
-\noindent News: 19.63\%
+	\noindent  'News'       'IT'        'Total'
 
-\
+         \noindent  '0.17231'    '0.5386'    '0.7109'
 
- \textbf{Log level of capital prices (differencing here seems to overdo it)}
-
-IT: 28.47\%
-
-\noindent News: 28.31\%
-
-\newpage
-\subsection*{IRFs - ratio of inflations (i.e relative prices)}
+         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_8_24-Nov-2017_15_14_15}
 
@@
 \centering
-\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_shock_Ryan_two_stepsID_20-Nov-2017_12_24_34}
-\caption{News shock - ratio of inflations}
+\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_shock_Ryan_two_stepsID_20-Nov-2017_12_24_34}} \hspace{.2in%
+} 
+\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_shock_Ryan_two_stepsID_20-Nov-2017_12_24_39}}
 \end{figure}
 
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_shock_Ryan_two_stepsID_20-Nov-2017_12_24_39}
-\caption{IT shock - ratio of inflations}
-\end{figure}
-
-%%%%%
-\newpage
-\subsection*{IRFs - log level of capital prices}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_21-Nov-2017_11_35_24}
-\caption{News shock - log level of capital prices}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_21-Nov-2017_11_35_27}
-\caption{IT shock - log level of capital prices}
-\end{figure}
-
-\newpage
-\subsection*{Recap and interpretation}
-
-\begin{itemize}
-\item One big motivation for the entire research project is the puzzling decrease in TFP growth, which - as we have also documented - started \emph{before} the Great Recession.
-\item The sudden decrease in IT investment after the burst of the IT bubble around 2000-2002 coincides with this slowdown in TFP growth, which led us to investigate the effect of IT investment on TFP.
-\item We run a structural VAR to estimate the effect of an IT productivity shock on TFP and other main macroeconomic variables.
-\item This identification poses a challenge because we need to confront the view that there is an endogenous channel in the evolution of TFP with the widely accepted view that TFP is driven by news.
-Since both are similar in the way they affect TFP only with lags, we need an additional restriction to disentangle the two.
-\item The additional restriction we use is that news shocks should have no effect on relative IT prices at a certain (long) horizon, because they behave like demand shocks.
-\item [] \textbf{What the results seem to suggest:}
-\item [1)] News and IT shocks together explain more of the FEV of TFP than news does alone in Barsky \& Sims (around 70\% vs approximately 40\% in Barsky \& Sims).
-(Compare with capital prices specification too.)
-\item [2)] News still explains a considerable fraction, but IT shocks explain more. (Compare with capital prices specification too.)
-\item [] $\rightarrow$ we read this as evidence that both news and the endogenous channel via IT investment plays an important role in explaining TFP  over the business cycle and the medium run. 
-\end{itemize}
-
-\subsection*{Comments? Thoughts? Does this make sense to you? Is it presentable in its current form?}
+%%%%%%%%	
+	\subsection{Capital prices LR horizon 8}
+	\input{FEVs_Ryan_two_stepsID_P_capital_LR_hor_8_24-Nov-2017_12_26_07}
 

### 2017-11-24 Ryan_two_stepsID.m

@@ -1,5 +1,5 @@
 function [impact, FEV_opt, IRFs, gam, FEV_news, FEV_IT] ...
-        = Ryan_two_stepsID(which_variable,which_shocks,H,B,A,q)
+        = Ryan_two_stepsID(which_variable,which_shocks,H,LR_hor,B,A,q)
 %which_variable: variable we want to max the response for a specific shock (TFP)
 %which_shocks: the shock is maximizing the FEV of which_variable (--> news and IT shocks)
 %H: horizon of the maximization
@@ -31,7 +31,7 @@ options  = optimset(options, 'TolFun', 1e-9, 'display', 'none');
 
 % Instead of Blanchard Quah, impose that IR(rel_prices, news) = 0 at some
 % finite long horizon.
-LR_hor = 8; % 100
+% LR_hor = 8; % 100
 sig = 0.9; % not used, but we need to input something not to get error
 [IR, ~, ~] = genIRFs(A,0,vertcat(ones(1,size(B,2)), B),0,LR_hor, sig);
 % R = zeros(nvar,nvar); 

### 2017-11-24 genIRFs.m

@@ -15,6 +15,7 @@ perc_low = floor(nsimul*(1-sig)); % the lower percentile of bootstrapped respons
 B = B(2:end,:);
 B_boot = B_boot(2:end,:,:);
 
+
 % Preallocate IRs
 IRFs = zeros(nvar,H,nshocks);
 IRFs_boot = zeros(nvar,H,nshocks,nsimul);
@@ -48,6 +49,7 @@ for i_shock=1:nshocks
                         IRFs_boot(:,k,i_shock,i_sim) = F_boot*B_boot(:,:,i_sim);
                         F_boot = [IRFs_boot(:,k,i_shock,i_sim)' F_boot(1:end-nvar)];
                   end
+                  % If bootstraps go the wrong way, flip them
                   if sum(sum(abs(IRFs_boot(:,:,i_shock,i_sim) - IRFs(:,:,i_shock)))) ...
                               >= sum(sum(abs(IRFs_boot(:,:,i_shock,i_sim) + IRFs(:,:,i_shock))))
                         IRFs_boot(:,:,i_shock,i_sim) = - IRFs_boot(:,:,i_shock,i_sim);

### 2017-11-24 invoke_matrix_outputting.m

@@ -1,0 +1,22 @@
+function invoke_matrix_outputting(matrix, matrixname, rowLabels, columnLabels, some_comment)
+
+base_path = pwd;
+
+current_time = datestr(now);
+ct1 = strrep(current_time,':','_'); % substitute : with _
+ct2 = strrep(ct1,' ','_'); % substitute spaces with _
+some_comment = strrep(some_comment,':','_');
+some_comment = strrep(some_comment,' ','_');
+
+final_name = [matrixname '_' some_comment '_' ct2 '.tex'];
+
+if exist([base_path '\Latex'], 'dir')
+   addpath([base_path '\Latex']) 
+   path.out = ['Latex\' final_name]; %for Microsoft
+else
+    addpath([base_path '/Latex'])
+    path.out = ['Latex/' final_name]; %for Mac    
+end
+
+
+matrix2latex_black(matrix, path.out, 'rowLabels', rowLabels, 'columnLabels', columnLabels, 'alignment', 'c', 'format', '%-6.1f', 'size', 'small'); 

### 2017-11-24 main_file_SVAR_RyansID.m

@@ -3,9 +3,10 @@
 
 % Marco Brianti, Laura Gáti, Oct 28 2017
 
-% TOOK 72.1348 MIN TO RUN!!
+% 500 bootstrap: Mac takes ? min
+% 500 bootstrap: Server takes 30 min
 
-clear 
+clear
 close all
 
 tic
@@ -47,30 +48,42 @@ test_stationarity(B');
 % dbstop in Ryan_two_stepsID at 74
 
 % Implement Ryan's ID strategy
+LR_hor = 8; % at what horizon to impose the LR restriction
 % [impact, FEV_opt, IRFs, gamma_opt, FEV_news, FEV_IT] = ryansID(which_variable,which_shocks,H,B,A,q);
 [impact, FEV_opt, ~, gam_opt, FEV_news, FEV_IT] ...
-    = Ryan_two_stepsID(which_variable,which_shocks,H,B,A,pos_rel_prices);
+    = Ryan_two_stepsID(which_variable,which_shocks,H,LR_hor,B,A,pos_rel_prices);
 % impact is the nvar x 2 impact matrix of news and IT.
 
-% TO DO: check info sufficiency (Forni's orthogonality test)
+% With Barsky & Sims-type ID, since you do a abs max, there are two
+% solutions: gam and -gam. So choose the one that makes sense. I'm doing
+% that so that news and IT have + effects on TFP.
+if gam_opt(1,1) < 0 % If news have - effects on TFP
+   impact(:,1) = -impact(:,1); 
+end
+if gam_opt(1,2) < 0 % if IT has - effects on TFP
+    impact(:,2) = -impact(:,2);
+end
 
-[s, obj_opt] = get_structral_shocks_alternative(A,gam_opt,res);
-s3 = s(3,:)';
-s4 = s(4,:)';
-% [s_old, obj_opt] = get_structural_shocks(A,gam_opt,res); % this old way
-% didn't work well, cancel it completely after a while
-% s1 = s_old(1,:)';
-% s2 = s_old(2,:)';
 
-pc = get_principal_components(data);
-pc = pc(1+nlags:end,:); % adjust because due to the lags, the structural shocks are shorter
 
-[B, yhat, res] = quick_ols(s3,pc);
-[B, yhat, res] = quick_ols(s4,pc);
-
-signi = f_test(s4,res, nvar,156,nvar)
-
-return
[…]

### 2017-11-24 matrix2latex_black.m

@@ -1,0 +1,229 @@
+function matrix2latex_black(matrix, filename, varargin)
+
+% PURPOSE:  Export of a matlab array object for LaTeX, so that it can be
+%           icluded as a tabular object with \input{out.tex}.
+% ------------------------------------------------------------------------
+% USAGE:    matrix2late(matrix, filename, varargs)
+%
+% WHERE:    matrix      = 2 dimensional numerical or cell array
+%           filename    = valid filename, in which the resulting latex 
+%                         code will be stored
+%           varargs     = one ore more of the following (denominator, 
+%                         value) combinations
+%                       + 'rowLabels', array -> Can be used to label the 
+%                       rows of the resulting latex table
+%                       + 'columnLabels', array -> Can be used to label 
+%                       the columns of the resulting latex table
+%                           '...\\' = tile without any further cell content
+%                           '\\'    = like \skip or \\ in text area
+%                           '$..$'  = any math commands
+%                       + 'alignment', 'value' -> Can be used to specify 
+%                       the alginment of the table within the latex 
+%                       document. Valid arguments are: 'l', 'c', and 'r' 
+%                       for left, center, and right, respectively
+%                       + 'format', 'value' -> Can be used to format the 
+%                       input data. 'value' has to be a valid format 
+%                       string, similar to the ones used in 
+%                       fprintf('format', value);
+%                       + 'size', 'value' -> One of latex' recognized 
+%                       font-sizes, e.g. tiny, HUGE, Large, large, LARGE..
+%
+% NOTES:    Base programm was written by:
+%           Author:   M. Koehler
+%           Contact:  koehler@in.tum.de
+%           Version:  1.1
+%           Date:     May 09, 2004
+% ------------------------------------------------------------------------
+% RETURNS:  nothing since syntax is correct
+% ------------------------------------------------------------------------
+% EXAMPLE:
+% matrix          = wfs;
+% rowLabels       = {'Wald-F (lik)' 'P-Value' 'Wald-F (core)' 'P-Value'};
+% columnLabels    = {'ltGap' 'hpGap' 'mvhpGap' 'stpGap' 'bpfoptGap' ...
+%         'HKFGap' 'pfGap'};
[…]

### 2017-11-25 Latex/general_writeup.tex
Documented that the longer the LR restriction, the more is attributed to IT and less to news

@@
 
+	\
+
 	\noindent  'News'       'IT'        'Total'
@@
 
+         \
+
          \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_8_24-Nov-2017_15_14_15}
+
+         \
 
@@
 %%%%%%%%
+% LR hor of 16 
+\newpage
+\subsection{Relative prices LR horizon 16}
+	\noindent Time it took, for 500 bootstrap, Mac: 61 min
+
+	\
+
+	\noindent  'News'       'IT'        'Total'
+
+         \noindent  '0.10054'    '0.60847'    '0.70901'
+
+         \
+
+         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_16_24-Nov-2017_18_56_26}
+
+         \
+
+\begin{figure}[h!]
+\centering
+\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_24-Nov-2017_18_56_19}} \hspace{.2in%
+} 
+\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_24-Nov-2017_18_56_23}}
+\end{figure}
+
+%%%%%%%%
+% LR hor of 80 - 
+\newpage
+\subsection{Relative prices LR horizon 80}
+	\noindent Time it took, for 500 bootstrap, Mac: 81 min
+
+	\
+
+	\noindent  'News'       'IT'        'Total'
+
+         \noindent  '0.044546'    '0.69612'    '0.74067'
+
+         \
+
+         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_80_24-Nov-2017_21_59_17}
+
+         \
+
+\begin{figure}[h!]
+\centering
+\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_24-Nov-2017_21_59_10}} \hspace{.2in%
+} 
+\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_24-Nov-2017_21_59_14}}
+\end{figure}
+
+%%%%%%%%
+%two lags instead of one (back to LR hor = 8)
+
+%%%%%%%%
+% adding stock prices
+
+%%%%%%%%
+% removing consumption
+
+%%%%%%%%
+% and/or adding investment
+
+%%%%%%%%
+% Capital prices
+\newpage
 	\subsection{Capital prices LR horizon 8}
+	\noindent Time it took, for 500 bootstrap, Mac: 12 min
+
+	\noindent  Time it took, for 500 bootstrap, server (w/o parpool): 30 min
+
+	\noindent  'News'       'IT'        'Total'
+
+         \noindent  '0.40843'    '0.23982'    '0.64824'
+
 	\input{FEVs_Ryan_two_stepsID_P_capital_LR_hor_8_24-Nov-2017_12_26_07}
 
+	\begin{figure}[h!]
+\centering
+\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_24-Nov-2017_16_17_15}} \hspace{.2in%
+} 
+\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_24-Nov-2017_16_17_19}}
+\end{figure}
+
 \end{document}

### 2017-11-25 main_file_SVAR_RyansID.m

@@ -3,9 +3,6 @@
 
 % Marco Brianti, Laura Gáti, Oct 28 2017
 
-% 500 bootstrap: Mac takes ? min
-% 500 bootstrap: Server takes 30 min
-
 clear
 close all
 
@@ -110,7 +107,7 @@ end
 %Creating and Printing figures
 comment = [which_ID '_' char(varnames(6)) '_LR_hor_' num2str(LR_hor)];
 
-print_figs = 'no';
+print_figs = 'yes';
 [IRFs, ub, lb] = genIRFs(fake_impact,fake_impact_boot,B,beta_tilde_star,H,sig);
 
 % % With Barsky & Sims-type ID, since you do a abs max, there are two

### 2017-11-25 Latex/general_writeup.tex
New Nice specification
I run the following specification:

TFP (log)
Real SP500 (log)
MichIndex (level)
IT Investment (log)
Real Cons (log)
Relative Prices (log-diff)

One lag, zero restriction in 8 quarters.

The result is super nice. In my opinion is even better than the one we showed Ryan.

I had the result to the Latex file you made.

@@
 %%%%%%%%
-%two lags instead of one (back to LR hor = 8)
+%two lags instead of one (back to LR hor = 8), adding real stock prices 500, removing GDP, with relative price
+\newpage
+	\subsection{Capital prices LR horizon 8}
+	\noindent one lag, LR hor = 8, adding real stock prices 500, removing GDP, with relative price
+
+	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_25-Nov-2017_11_39_14}
+
+	\begin{figure}[h!]
+\centering
+\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_25-Nov-2017_11_30_49}} \hspace{.2in%
+} 
+\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_25-Nov-2017_11_30_52}}
+\end{figure}
 
 %%%%%%%%
-% adding stock prices
+%one lag (back to LR hor = 8)
+
+%%%%%%%%
+% adding real SP
 

### 2017-11-25 bootstrap_with_kilian.m

@@ -2,7 +2,7 @@ function [beta_tilde, data_boot2, beta_tilde_star,nonstationarities] = bootstrap
 
 % This function does the entire bootstrap procedure using Kilian's
 % correction, see Kilian 1998, p. 220.
-% Inputs: 
+% Inputs:
 % beta_hat = the point estimate of beta from reduform_var
 % Outputs:
 % beta_tilde        = the corrected point estimate (nvar*nlags +1, nvar)
@@ -23,7 +23,7 @@ nlags = (size(beta_hat,1)-1)/nvar;
 
 beta_hat_star1 = zeros(nvar*nlags+1, nvar, nsimul);
 for i_simul = 1:nsimul
-    [beta_hat_star1(:,:,i_simul),~,~] = reduform_var(data_boot1(:,:, i_simul), nlags);
+      [beta_hat_star1(:,:,i_simul),~,~] = reduform_var(data_boot1(:,:, i_simul), nlags);
 end
 
 psi_hat1 = mean(beta_hat_star1,3) - beta_hat;
@@ -32,14 +32,14 @@ psi_hat1 = mean(beta_hat_star1,3) - beta_hat;
 disp('Step 1b')
 flag = test_stationarity(beta_hat');
 if  flag == 0
-    beta_tilde = beta_hat - psi_hat1;
+      beta_tilde = beta_hat - psi_hat1;
 else % nonstationary
-    delt = 1;
-    while flag == 1
-        delt = delt- 0.01;
-        beta_tilde = beta_hat - delt*psi_hat1;
-        flag = test_stationarity(beta_tilde');
-    end
+      delt = 1;
+      while flag == 1
+            delt = delt - 0.01;
+            beta_tilde = beta_hat - delt*psi_hat1;
+            flag = test_stationarity(beta_tilde');
+      end
 end
 
 %% 2nd bootstrap loop
@@ -49,11 +49,11 @@ disp('Step 2a')
 % Generate bootstrapped data samples
 data_boot2 = data_boot(beta_tilde, nburn, res, nsimul, which_correction, blocksize);
 
-beta_hat_star2  = zeros(nvar*nlags+1, nvar, nsimul); 
+beta_hat_star2  = zeros(nvar*nlags+1, nvar, nsimul);
 beta_tilde_star = zeros(nvar*nlags+1, nvar, nsimul);
 
 for i_simul = 1:nsimul
[…]

### 2017-11-25 main_file_SVAR_RyansID.m

@@ -41,16 +41,16 @@ end
 
 %Checking if the VAR is stationary
 test_stationarity(B');
-
-% dbstop in Ryan_two_stepsID at 74
+disp('Line 44')
 
 % Implement Ryan's ID strategy
 LR_hor = 8; % at what horizon to impose the LR restriction
 % [impact, FEV_opt, IRFs, gamma_opt, FEV_news, FEV_IT] = ryansID(which_variable,which_shocks,H,B,A,q);
 [impact, FEV_opt, ~, gam_opt, FEV_news, FEV_IT] ...
     = Ryan_two_stepsID(which_variable,which_shocks,H,LR_hor,B,A,pos_rel_prices);
-% impact is the nvar x 2 impact matrix of news and IT.
 
+disp('Line 52')
+% impact is the nvar x 2 impact matrix of news and IT.
 
 % % TO DO: check info sufficiency (Forni's orthogonality test)
 % [s, obj_opt] = get_structral_shocks_alternative(A,gam_opt,res);
@@ -68,12 +68,6 @@ LR_hor = 8; % at what horizon to impose the LR restriction
 % [B, yhat, res] = quick_ols(s4,pc);
 %
 % signi = f_test(s4,res, nvar,156,nvar)
-%
-% return
-
-
-
-
 
 % Bootstrap
 which_ID = 'Ryan_two_stepsID';
@@ -82,6 +76,8 @@ blocksize = 5; % size of block for drawing in blocks
 
 [beta_tilde, data_boot2, beta_tilde_star, nonstationarities] = bootstrap_with_kilian( ...
     B, nburn, res, nsimul, which_correction, blocksize);
+
+disp('Line 80')
 
 % Get "bootstrapped A" nsimul times
 for i_simul=1:nsimul
@@ -114,20 +110,19 @@ print_figs = 'yes';
 % % solutions: gam and -gam. So choose the one that makes sense. I'm doing
 % % that so that news and IT have + effects on TFP.
 if sum(IRFs(1,:,3)) < 0 % if the majority of TFP response is negative
-    IRFs(:,:,3) = -IRFs(:,:,3);
-    ub(:,:,3) = - ub(:,:,3);
-    lb(:,:,3) = - lb(:,:,3);
+    IRFs(:,:,3)   = -IRFs(:,:,3);
[…]

### 2017-11-26 Latex/general_writeup.tex
more playing around with specifications
updated the same latex file, general_writeup

@@
 %%%%%%%%
-%two lags instead of one (back to LR hor = 8), adding real stock prices 500, removing GDP, with relative price
+%one lag (back to LR hor = 8), adding real stock prices 500, removing GDP, with relative price
 \newpage
-	\subsection{Capital prices LR horizon 8}
+	\subsection{Relative prices LR horizon 8, adding SP 500}
 	\noindent one lag, LR hor = 8, adding real stock prices 500, removing GDP, with relative price
@@
 %%%%%%%%
-%one lag (back to LR hor = 8)
+% adding real SP500, but with GDP
+\newpage
+	\subsection{Relative prices LR horizon 8, adding SP 500 and leaving in GDP}
+	\noindent one lag, LR hor = 8, adding real stock prices 500, leaving in GDP, with relative price; only 30 bootstrap
+
+	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_09_31_50}
+
+	\begin{figure}[h!]
+\centering
+\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_26-Nov-2017_09_36_04}} \hspace{.2in%
+} 
+\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_26-Nov-2017_09_36_11}}
+\end{figure}
+
+\
+
+I wanted to do this to see if in the previous spec, it was adding SP500 that made things nicer or if it was removing GDP.
+Clearly, if you keep GDP in, things aren't so nice anymore, but they're not too bad.
+Things don't move so much anymore; it seems like we have too many variables for the VAR to contain.
+At the same time, overall they move in the right directions.
 
 %%%%%%%%
-% adding real SP
+%SP500 instead of Mich
+\newpage
+	\subsection{Relative prices LR horizon 8, adding SP 500 instead of Mich}
+	\noindent one lag, LR hor = 8, adding real stock prices 500 instead of Mich, leaving in GDP, with relative price; only 30 bootstrap
+
+	\
+
+	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_01_19}
+
+	\begin{figure}[h!]
+\centering
+\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_26-Nov-2017_10_02_09}} \hspace{.2in%
+} 
+\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_26-Nov-2017_10_02_14}}
+\end{figure}
+
+\
+
+I wanted to do this one to see how well SP500 can replace Mich. Results are fairly in line, that's great, contribution of news and IT is \emph{identical}. VERY nice!
+%%%%%%%%
+%two lags (back to LR hor = 8, back to no SP500 i.e. default setup)
+\newpage
+	\subsection{Default spec, 2 lags}
+	\noindent two lags, LR hor = 8, Mich is back, with relative price; only 30 bootstrap
+
+	\
+
+	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_12_18}
+
+	\begin{figure}[h!]
+\centering
+\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_26-Nov-2017_10_12_10}} \hspace{.2in%
+} 
+\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_26-Nov-2017_10_12_14}}
+\end{figure}
+
+\
+A little too much uncertainty here on the news shock side. Doing this with a 500 bootstrap might make sense. % Running on server, expected to be ready around 16.00
 
@@
 % removing consumption 
+\newpage
+	\subsection{Default spec, removing consumption}
+	\noindent one lag, LR hor = 8, no consumption, with relative price; only 30 bootstrap
+
+	\
+
+	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_24_22}
+
+	\begin{figure}[h!]
+\centering
+\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_26-Nov-2017_10_24_15}} \hspace{.2in%
+} 
+\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_26-Nov-2017_10_24_19}}
+\end{figure}
+
+\
+
+Not too bad, but wiggly - strangely enough, something seems to be missing.
+
+%%%%%%%%
+% adding hours 
+\newpage
+	\subsection{Default spec, adding hours}
+	\noindent one lag, LR hor = 8, adding hours, with relative price; only 30 bootstrap
+
+	\
+
+	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_24_22}
+
+	\begin{figure}[h!]
+\centering
+\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_26-Nov-2017_10_43_48}} \hspace{.2in%
+} 
+\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_26-Nov-2017_10_43_51}}
+\end{figure}
+
+\
+As usual, it screws up the news shock, leaving the IT shock very nice.
 
@@
 %%%%%%%%
-% Capital prices
+% Capital prices instead of relative prices
 \newpage

### 2017-11-26 main_file_SVAR_RyansID.m

@@ -14,13 +14,14 @@ sheet    = 'Data';
 range    = 'B1:M286';
 [data, varnames] = read_data2(filename, sheet, range);
 shocknames = {'News Shock','IT Shock'};
-which_shocks = [3 4];
+% which_shocks = [3 4];
+which_shocks = [2 3];
 pos_rel_prices = 6;
 
 %Technical Parameters
 max_lags        = 10;
 nburn           = 0; %with the Kilian correction better not burning!!!
-nsimul          = 20; %5000
+nsimul          = 30; %5000
 nvar            = size(data,2);
 sig             = 0.90; % significance level
 H               = 100; %40; % horizon for generation of IRFs
@@ -76,9 +77,9 @@ for i_simul = 1:nsimul
 end
 
 %Creating and Printing figures
-comment = [which_ID '_' char(varnames(6)) '_LR_hor_' num2str(LR_hor)];
+comment = [which_ID '_' char(varnames(5)) '_LR_hor_' num2str(LR_hor)];
 
-print_figs = 'no';
+print_figs = 'yes';
 [IRFs, ub, lb] = genIRFs(fake_impact,fake_impact_boot,...
       B,beta_tilde_star,H,sig);
 
@@ -101,6 +102,9 @@ plotIRFs(IRFs,ub,lb,40,which_shocks,shocknames,varnames, ...
       which_ID,print_figs)
 
 %Forni&Gambetti Orthogonality Test
+do_FG_test = 'no';
+switch do_FG_test
+    case 'yes'
 filename_PC       = 'Dataset_test_PC';
 sheet_PC          = 'Quarterly';
 range_PC          = 'B2:DC287';
@@ -108,6 +112,7 @@ first_n_PCs       = 10;
 [pvalue_news_shock, pvalue_IT_shock] = ...
       Forni_Gambetti_orthogonality_test(filename_PC,...
       sheet_PC,range_PC,first_n_PCs,A,gam_opt,res);
+end
 
 %Saving in Tex format the Variance Decomposition Matrix
 fev_matrix = {'News', 'IT', 'Total'};

### 2017-11-27 Latex/general_writeup.tex
In latex file 1.4 and 1.6 are two great specifications in line amopng them!

@@
 
-	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_01_19}
+	\input{FEVs_Ryan_two_stepsID_real_consumption_LR_hor_8_27-Nov-2017_12_27_33}
 
@@
 \centering
-\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_26-Nov-2017_10_02_09}} \hspace{.2in%
+\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_27-Nov-2017_12_27_25}} \hspace{.2in%
 } 
-\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_26-Nov-2017_10_02_14}}
+\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_27-Nov-2017_12_27_30}}
 \end{figure}

### 2017-11-27 main_file_SVAR_RyansID.m

@@ -21,7 +21,7 @@ pos_rel_prices = 6;
 %Technical Parameters
 max_lags        = 10;
 nburn           = 0; %with the Kilian correction better not burning!!!
-nsimul          = 30; %5000
+nsimul          = 500; %5000
 nvar            = size(data,2);
 sig             = 0.90; % significance level
 H               = 100; %40; % horizon for generation of IRFs
@@ -31,7 +31,7 @@ which_variable  = 1; % select TFP as the variable whose FEV we wanna max
 %%Checking the number of lags over BIC, AIC, and HQ (see 'Lecture2M' in our folder)
 [AIC,BIC,HQ] = aic_bic_hq(data,max_lags);
 if AIC >= 4
-    nlags = 1; % 1
+    nlags = 1; % 2;
     warning(['AIC > 4, setting nlags to ', num2str(nlags) ])
 else
     nlags = AIC;

### 2017-11-27 Latex/general_writeup.tex
1.11 Another specification in line with 1.4 and 1.6
 in line with 1.4 and 1.6. Also impact of relative prices is significan for both shocks

@@
 
+\newpage
+\subsection{Relative prices LR horizon 8}
+
+\input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_8_27-Nov-2017_14_42_35}
+
+\begin{figure}[h!]
+	\centering
+	\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_27-Nov-2017_14_42_29}} \hspace{.2in%
+	} 
+	\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_27-Nov-2017_14_42_32}}
+\end{figure}
+
 \end{document}

### 2017-11-27 main_file_SVAR_RyansID.m

@@ -11,12 +11,16 @@ tic
 %Data Reading and Transformation
 filename = 'dataset_main';
 sheet    = 'Data';
-range    = 'B1:M286';
+range    = 'B1:N286';
 [data, varnames] = read_data2(filename, sheet, range);
 shocknames = {'News Shock','IT Shock'};
 % which_shocks = [3 4];
 which_shocks = [2 3];
-pos_rel_prices = 6;
+pos_rel_prices = 5;
+if pos_rel_prices == 6
+else
+      warning('Position of Relative Price is not anymore 6.')
+end
 
 %Technical Parameters
 max_lags        = 10;

### 2017-11-28 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
deleted some old figures and started doing macro lunch presentation

--- 2017-11-26 Latex/general_writeup.tex
@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
+\documentclass{beamer}
 \usepackage[english]{babel}
-\usepackage[a4paper,top=1.5cm,bottom=1.5cm,left=1.5cm,right=1.5cm,%
-bindingoffset=0mm]{geometry}
+\usepackage[latin1]{inputenc}
+\usepackage[T1]{fontenc}
 \usepackage{amssymb}
 \usepackage{amsmath}
-\newtheorem{prop}{Proposition}
-\newtheorem{lemma}{Lemma}
-\newenvironment{proof}[1][Proof]{\begin{trivlist}
-		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
-\newcommand{\qed}{\nobreak \ifvmode \relax \else
-	\ifdim\lastskip<1.5em \hskip-\lastskip
-	\hskip1.5em plus0em minus0.5em \fi \nobreak
-	\vrule height0.75em width0.75em depth0em\fi}
-\usepackage{tikz}
-\usepackage{graphicx}
-\def \ourFigPath {../} 
-\usepackage{subfigure}
-\usepackage{rotating}
-\usepackage{float}
-\linespread{1.3}
-\raggedbottom
+\usepackage{booktabs}
+\usepackage{verbatim}
 
@@
 % subsets of real numbers
+\newcommand{\numberset}{\mathbb}
 \newcommand{\real}{\hbox{\reali R}}
+\newcommand{\N}{\numberset{N}}
 \newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
 \newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
-\newcommand{\R}{\mathbb{R}}
-\DeclareMathOperator{\E}{\mathbb{E}}
+\newcommand{\virgolette}[1]{``#1''}
 %
 
-\title{General writeup}
-\author{Marco Brianti\\Laura Gati}
-\date{August 2017}
+\author[Brianti, Gati]{\\Marco Brianti and Laura Gati}
+
+\institute[Boston College]{Boston College}
+
+\title{Title}
+
+\date{December 13, 2017}
+
+\usetheme{Warsaw}
 
@@
 
+\begin{frame}
+
 \maketitle
 
-	\section{VAR Results - Comparison of different specifications}
+\end{frame}
 
-	\subsection{Relative prices LR horizon 8}
-	\noindent Time it took, for 500 bootstrap, Mac: 61 min
-
-	\noindent  Time it took, for 500 bootstrap, server (w/o parpool): 140 min
-
-	\noindent  Time it took, for 500 bootstrap, server (w/ parpool): ? min
+%% Slide 1 / Comments I
+\begin{frame}
+	\frametitle{A primitive question}
 
@@
 
-	\noindent  'News'       'IT'        'Total'
-
-         \noindent  '0.17231'    '0.5386'    '0.7109'
-
 	\
 
-         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_8_24-Nov-2017_15_14_15}
+	Why has TFP slowed down?
 
-         \
-
-\begin{figure}[h!]
-\centering
-\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_shock_Ryan_two_stepsID_20-Nov-2017_12_24_34}} \hspace{.2in%
-} 
-\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_shock_Ryan_two_stepsID_20-Nov-2017_12_24_39}}
-\end{figure}
-
-%%%%%%%%
-% LR hor of 16 
-\newpage
-\subsection{Relative prices LR horizon 16}
-	\noindent Time it took, for 500 bootstrap, Mac: 61 min
-
-	\
-
-	\noindent  'News'       'IT'        'Total'
-
-         \noindent  '0.10054'    '0.60847'    '0.70901'
-
-         \
-
-         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_16_24-Nov-2017_18_56_26}
-
-         \
-
-\begin{figure}[h!]
-\centering
-\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_24-Nov-2017_18_56_19}} \hspace{.2in%
-} 
-\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_24-Nov-2017_18_56_23}}
-\end{figure}
-
-%%%%%%%%
-% LR hor of 80 - 
-\newpage
-\subsection{Relative prices LR horizon 80}
-	\noindent Time it took, for 500 bootstrap, Mac: 81 min
-
-	\
-
-	\noindent  'News'       'IT'        'Total'
-
-         \noindent  '0.044546'    '0.69612'    '0.74067'
-
-         \
-
-         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_80_24-Nov-2017_21_59_17}
-
-         \
-
-\begin{figure}[h!]
-\centering
-\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_24-Nov-2017_21_59_10}} \hspace{.2in%
-} 
-\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_24-Nov-2017_21_59_14}}
-\end{figure}
-
-%%%%%%%%
-%one lag (back to LR hor = 8), adding real stock prices 500, removing GDP, with relative price
-\newpage
-	\subsection{Relative prices LR horizon 8, adding SP 500}
-	\noindent one lag, LR hor = 8, adding real stock prices 500, removing GDP, with relative price
-
-	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_25-Nov-2017_11_39_14}
-
-	\begin{figure}[h!]
-\centering
-\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_25-Nov-2017_11_30_49}} \hspace{.2in%
-} 
-\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_25-Nov-2017_11_30_52}}
-\end{figure}
-
-%%%%%%%%
-% adding real SP500, but with GDP
-\newpage
-	\subsection{Relative prices LR horizon 8, adding SP 500 and leaving in GDP}
-	\noindent one lag, LR hor = 8, adding real stock prices 500, leaving in GDP, with relative price; only 30 bootstrap
-
-	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_09_31_50}
-
-	\begin{figure}[h!]
-\centering
-\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_26-Nov-2017_09_36_04}} \hspace{.2in%
-} 
-\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_26-Nov-2017_09_36_11}}
-\end{figure}
-
-\
-
-I wanted to do this to see if in the previous spec, it was adding SP500 that made things nicer or if it was removing GDP.
-Clearly, if you keep GDP in, things aren't so nice anymore, but they're not too bad.
-Things don't move so much anymore; it seems like we have too many variables for the VAR to contain.
-At the same time, overall they move in the right directions.
-
-%%%%%%%%
-%SP500 instead of Mich
-\newpage
-	\subsection{Relative prices LR horizon 8, adding SP 500 instead of Mich}
-	\noindent one lag, LR hor = 8, adding real stock prices 500 instead of Mich, leaving in GDP, with relative price; only 30 bootstrap
-
-	\
-
-	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_01_19}
-
-	\begin{figure}[h!]
-\centering
-\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_26-Nov-2017_10_02_09}} \hspace{.2in%
-} 
-\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_26-Nov-2017_10_02_14}}
-\end{figure}
-
-\
-
-I wanted to do this one to see how well SP500 can replace Mich. Results are fairly in line, that's great, contribution of news and IT is \emph{identical}. VERY nice!
-%%%%%%%%
-%two lags (back to LR hor = 8, back to no SP500 i.e. default setup)
-\newpage
-	\subsection{Default spec, 2 lags}
-	\noindent two lags, LR hor = 8, Mich is back, with relative price; only 30 bootstrap
-
-	\
-
-	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_12_18}
-
-	\begin{figure}[h!]
-\centering
-\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_26-Nov-2017_10_12_10}} \hspace{.2in%
-} 
-\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_26-Nov-2017_10_12_14}}
-\end{figure}
-
-\
-A little too much uncertainty here on the news shock side. Doing this with a 500 bootstrap might make sense. % Running on server, expected to be ready around 16.00
-
-%%%%%%%%
-% removing consumption 
-\newpage
-	\subsection{Default spec, removing consumption}
-	\noindent one lag, LR hor = 8, no consumption, with relative price; only 30 bootstrap
-
-	\
-
-	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_24_22}
-
-	\begin{figure}[h!]
-\centering
-\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_26-Nov-2017_10_24_15}} \hspace{.2in%
-} 
-\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_26-Nov-2017_10_24_19}}
-\end{figure}
-
-\
-
-Not too bad, but wiggly - strangely enough, something seems to be missing.
-
-%%%%%%%%
-% adding hours 
-\newpage
-	\subsection{Default spec, adding hours}
-	\noindent one lag, LR hor = 8, adding hours, with relative price; only 30 bootstrap
-
-	\
-
-	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_24_22}
-
-	\begin{figure}[h!]
-\centering
-\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_26-Nov-2017_10_43_48}} \hspace{.2in%
-} 
-\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_26-Nov-2017_10_43_51}}
-\end{figure}
-
-\
-As usual, it screws up the news shock, leaving the IT shock very nice.
-
-%%%%%%%%
-% and/or adding investment
-
-%%%%%%%%
-% Capital prices instead of relative prices
-\newpage
-\subsection{Capital prices LR horizon 8}
-\noindent Time it took, for 500 bootstrap, Mac: 12 min
-
-\noindent  Time it took, for 500 bootstrap, server (w/o parpool): 30 min
-
-\noindent  'News'       'IT'        'Total'
-
-\noindent  '0.40843'    '0.23982'    '0.64824'
-
-\input{FEVs_Ryan_two_stepsID_P_capital_LR_hor_8_24-Nov-2017_12_26_07}
-
-\begin{figure}[h!]
-	\centering
-	\subfigure[News]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_24-Nov-2017_16_17_15}} \hspace{.2in%
-	} 
-	\subfigure[IT]{\includegraphics[width=8.5cm]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_24-Nov-2017_16_17_19}}
-\end{figure}
+\end{frame}
 

### 2017-11-28 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
more work on presentation

@@
 \usepackage{verbatim}
+\usepackage{csquotes}
 
@@
 
-%% Slide 1 / Comments I
+%%%%%%% Slide %%%%%%
 \begin{frame}
-	\frametitle{A primitive question}
+	\frametitle{A very big question}
+
+Broad consensus on secular stagnation.
+
+\
+
+The literature has agreed that there are two main factors driving this:
+\begin{itemize}
+\item decreasing labor force participation
+\item decreasing TFP growth
+\end{itemize}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{A smaller, but still big question}
 
@@
 
-	Why has TFP slowed down?
+	Why has TFP slowed down? % show TFP graph here
 
 \end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Two possible mechanisms}
+
+\begin{itemize}
+\item a permanent, or very persistent exogenous shock to TFP
+
+\
+
+\item an endogenous mechanism
+\end{itemize}
+
+\
+
+\
+
+$\rightarrow$ What we do in a nutshell: test for the endogenous mechanism (main analysis will be a SVAR)
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Related literatures}
+	\label{related_lit}
+\begin{itemize}
+\item One strand of literature: Exogenous TFP and news shocks
+	\begin{itemize}
+	\item Beaudry \& Portier (2006)
+	\item Barsky \& Sims (2011)
+
+	\end{itemize}
+\item [] \textbf{Our contribution: allow in this setting the existence of an endogenous mechanism that affects future TFP}
+
+\hyperlink{BS_quote}{\beamergotobutton{Barsky \& Sims quote}}
+
+	\
+
+	\
+
+\item Another strand of literature: Endogenous TFP with R\&D investment as the key variable
+	\begin{itemize}
+	\item Comin \& Gertler (2006)
+	\item Moran \& Queralto (2017)
+
+	\end{itemize}
+
+\item []  \textbf{Our contribution: provide what we think is a more convincing test for the endogenous mechanism}
+
+\end{itemize}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Why more convincing?}
+	\label{convincing}
+
+	Because the endogenous TFP literature faces a big problem: The endogenous mechanism is rationalized entirely using R\&D investment.
+
+	\
+
+\begin{enumerate}
+\item  But R\&D in the data is almost acyclical.... $\rightarrow$ hard to rationalize as a driver of business cycle fluctuations % hyperlink to graph: growth rate of RD vs. growth rate of TFP and GDP
+ \hyperlink{growth_rates}{\beamergotobutton{Graph of acyclical R\&D}}
+
+\
+
+\item Timing issue: the TFP slowdown begins around 2006, i.e.
+\emph{before} the Great Recession and thus \emph{before} the marked drop in R\&D  % hyperlink to graph: level of RD and TFP, so we see that TFP drops in 2006, while RD only during the recession.
+\hyperlink{timing}{\beamergotobutton{Graph of timing}}
+
+\end{enumerate}
+
+\
+
+$\Rightarrow$ Following the suggestion of Fernald, Hall, Stock \& Watson (2009), we propose to use investment in information technology (IT)  % hyperlink to our own graph motivation.pdf: the top graph.
+\hyperlink{it_investment}{\beamergotobutton{Graph of IT investment}}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Empirical analysis}
+
+	We run a SVAR using aggregate, quarterly US data. The data vector is:
+
+	\begin{equation}
+	\mathbf{X_t} = 
+	\begin{bmatrix}
+    TFP_t      \\
+
+   SP_t   \\
+
+   IT_t \\
+
+   GDP_t \\
+
+   C_t \\
+
+   RP_t
+\end{bmatrix}
+	\end{equation}
+
+\
+
+\
+
+\begin{itemize}
+\item $RP = \pi^{IT}/\pi^{CPI}$. 
+\item All variables are in log levels except for RP, which is in growth rates. 
+\item The dataset ranges from 1989:q1 - 2017:q1.
+\end{itemize}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{From reduced form to structural form}
+\begin{equation}
+(\mathbf{AD})^{-1}
+    \mathbf{X_{t}}
+= \mathbf{C(L)} 
+\mathbf{X_{t-1}}
++ \mathbf{S_t}
+\end{equation}
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Identification strategy}
+
+\begin{equation}
+TFP_t =  \underbrace{\varepsilon_t}_\text{surprise tech shock}  + \underbrace{V_{t-k}}_\text{news shock} + \underbrace{IT_{t-k}}_\text{IT shock}  
+\end{equation}
+
+\
+
+    \begin{enumerate}
+    	\item The news shock $V_{t-k}$ maximizes the FEV of future TFP subject to the restriction that it has no effect on the relative price $RP$ in the long run;
+
+	\
+
+    \item The IT shock maximizes the remaining FEV of future TFP;
+
+    \
+
+    \item The tech shock $\varepsilon_t$ is considered as a residual shock and is left unrestricted.
+   \end{enumerate}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%                     APPENDIX  
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Barsky \& Sims say:}
+	\label{BS_quote}
+
+\blockquote{\emph{A more general objection to our empirical approach would be that a number of structural shocks, which are not really ``news'' in the sense defined by the literature, might affect a measure of TFP in the future without impacting it immediately.
+Among these shocks might be research and development shocks, investment specific shocks, and reallocative shocks.
+Our identification (and any other existing VAR identifications) would obviously confound any true news shock with these shocks.}}
+
+\
+
+\hspace{5cm} Barsky \& Sims (2011), p. 278.
+
+\
+
+\
+
+\
+
+\hyperlink{related_lit}{\beamerreturnbutton{Return}}	
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Growth rate of RD vs growth rate of TFP}
+	\label{growth_rates}
+
+\hyperlink{convincing}{\beamerreturnbutton{Return}}	
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Timing: RD drop vs TFP drop}
+	\label{timing}
+
+\hyperlink{convincing}{\beamerreturnbutton{Return}}	
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{IT investment: a break at the right time}
+	\label{it_investment}
+
+\hyperlink{convincing}{\beamerreturnbutton{Return}}	
+\end{frame}
+%%%%%%%%%%%%%%%%%
 

### 2017-11-29 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
Keep going with presentation + Real IT inv good results

@@
 \usepackage{csquotes}
+\usepackage{sansmathaccent}
+\pdfmapfile{+sansmathaccent.map}
 
@@
 
-\author[Brianti, Gati]{\\Marco Brianti and Laura Gati}
+\author[Brianti, Gati]{Marco Brianti and Laura Gati}
 
@@
 	\frametitle{From reduced form to structural form}
+	\label{identification}
+
+Structural Form	
 \begin{equation}
@@
 \mathbf{X_{t-1}}
-+ \mathbf{S_t}
++ \mathbf{s_t}
 \end{equation}
+
+\
+
+\
+
+Reduced Form
+\begin{equation}
+\mathbf{X_{t}}
+= \underbrace{\mathbf{AD} \mathbf{C(L)}}_\text{$\mathbf{B(L)}$} 
+\mathbf{X_{t-1}}
++ \underbrace{\mathbf{AD} \mathbf{_t}}_\text{$\mathbf{i_t}$}
+\end{equation}
+
+\
+
+\
+
+\begin{itemize}
+	\item $AD$ is the impact matrix
+	\item $A$ is s.t. $As_t s_t' A' = i_t i_t' = \Sigma$ and $s_t s_t' = I$
+	\item $D$ is a rotation matrix s.t. $DD' = I$ $\Rightarrow$ $AD(AD)' = \Sigma$
+\end{itemize}
+
+$D$ will be a tool to impose our identification assumptions \hyperlink{Technicalities}{\beamergotobutton{Technicalities}}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+\frametitle{Identified Shocks}
+
+\begin{itemize}
+	\item We impose restrictions on $D$ in order to identify two shocks:
+	\begin{enumerate}
+		\item News Shock
+		\item IT Productivity Shock
+	\end{enumerate}
+
+\
+
+	\item Econometric challenge is to disentangle two shocks with very similar features 
+		\begin{enumerate}
+		\item No impact effect on TFP
+		\item Persistent positive effect over time on TFP
+		\item Most likely both shocks have positive impact effects on forward-looking variables
+	\end{enumerate}
+
+\
+
+	\item Barsky \& Sims' identification strategy is not sufficient to disentangle the two
+	\begin{itemize}
+		\item We need a further assumption (restriction) to find a dimension of difference between the shocks
+	\end{itemize}
+\end{itemize}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+\frametitle{Additional Restriction}
+
+\begin{itemize}
+	\item We rely in simple demand ans supply theory
+	\begin{enumerate}
+		\item 
+		\item 
+	\end{enumerate}
+
+	\
+
+	\item 
+	\begin{enumerate}
+		\item 
+		\item 
+	\end{enumerate}
+
+	\
+
+	\item 
+	\begin{itemize}
+		\item 
+	\end{itemize}
+\end{itemize}
+
 \end{frame}
@@
 
+%%%%%%% Slide %%%%%%
+\begin{frame}
+\frametitle{Identification Strategy}
+\label{Technicalities}
+
+\begin{equation}
+D = \begin{bmatrix}
+d_{11} & \gamma_{12} & \gamma_{13} & d_{14} & \cdots \\
+d_{21} & \gamma_{22} & \gamma_{23} & d_{24} & \cdots \\
+\vdots & \vdots & \vdots & \ddots & \vdots 
+\end{bmatrix}
+\end{equation}
+
+\begin{itemize}
+	\item Indifferent over $d_{ij}$ as long as $D$ is orthogonal
+	\item $A \gamma_{2}$ is the impact response to a news shock
+	\item $A \gamma_{3}$ is the impact response to a IT productivity shock
+	\item First element of both $A \gamma_{2}$ and $A \gamma_{3}$ is zero due to the no-contemporaneous effect of both shocks on TFP
+	\item $A \gamma_2$ is such that the FEV of TFP is maximized subject to zero long-run effect on $RP$
+	\item $A \gamma_3$ is maximizing the remaining FEV of TFP 
+\end{itemize}
+
+\hyperlink{identification}{\beamerreturnbutton{Return}}	
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2017-11-29 main_file_SVAR_RyansID.m

@@ -11,12 +11,12 @@ tic
 %Data Reading and Transformation
 filename = 'dataset_main';
 sheet    = 'Data';
-range    = 'B1:N286';
+range    = 'B1:P286';
 [data, varnames] = read_data2(filename, sheet, range);
 shocknames = {'News Shock','IT Shock'};
 % which_shocks = [3 4];
 which_shocks = [2 3];
-pos_rel_prices = 5;
+pos_rel_prices = 6;
 if pos_rel_prices == 6
 else
       warning('Position of Relative Price is not anymore 6.')
@@ -25,7 +25,7 @@ end
 %Technical Parameters
 max_lags        = 10;
 nburn           = 0; %with the Kilian correction better not burning!!!
-nsimul          = 20; %5000
+nsimul          = 500; %5000
 nvar            = size(data,2);
 sig             = 0.90; % significance level
 H               = 100; %40; % horizon for generation of IRFs

### 2017-11-29 main_file_SVAR_RyansID.m
results to check figures

@@ -25,7 +25,7 @@ end
 %Technical Parameters
 max_lags        = 10;
 nburn           = 0; %with the Kilian correction better not burning!!!
-nsimul          = 500; %5000
+nsimul          = 20; %5000
 nvar            = size(data,2);
 sig             = 0.90; % significance level
 H               = 100; %40; % horizon for generation of IRFs

### 2017-11-29 plotIRFs.m

@@ -26,7 +26,8 @@ function plotIRFs(IRFs,ub,lb,h,which_shock, names, varnames, which_ID_strat, pri
             plot(periods,ub(i_var,1:h,which_shock(i_shock)),'--','linewidth',1,'Color','k')
             plot(periods,lb(i_var,1:h,which_shock(i_shock)),'--','linewidth',1,'Color','k')
             plot(zeros(1,h), 'Color','b')
-            title([name, ' on ' , varname])
+            %title([name, ' on ' , varname],'fontsize',18)
+            title([varname],'fontsize',18)
             hold off
             grid on
         end

### 2017-11-29 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
kept going with the presentation

@@
 \begin{frame}
-\frametitle{Identified Shocks}
+\frametitle{Identified shocks}
 
@@
 \begin{frame}
-\frametitle{Additional Restriction}
+\frametitle{Additional restriction}
 
 \begin{itemize}
-	\item We rely in simple demand ans supply theory
+	\item We rely on simple demand and supply theory
+
+	\
+
 	\begin{enumerate}
-		\item 
-		\item 
+		\item The IT shock is a \emph{sectoral} shock $\rightarrow$ we expect it to move relative prices
+		\item The news shock is \emph{not} a sectoral shock $\rightarrow$ we have no a priori sense of what it should do to relative prices on impact, but after some time relative prices should go back to their initial value
 	\end{enumerate}
@@
 
-	\item 
-	\begin{enumerate}
-		\item 
-		\item 
-	\end{enumerate}
+\end{itemize}
 
-	\
+	$\rightarrow$ add the restriction that a news shock should have no effect on relative prices after a reasonable time
 
-	\item 
-	\begin{itemize}
-		\item 
-	\end{itemize}
-\end{itemize}
+\hspace{4cm} $\hookrightarrow$ enough for prices to adjust, so
+
+\hspace{4cm}   between 6 -12 quarters
 
@@
 \begin{frame}
-	\frametitle{Identification strategy}
+	\frametitle{Identification strategy overall}
 
@@
     \begin{enumerate}
-    	\item The news shock $V_{t-k}$ maximizes the FEV of future TFP subject to the restriction that it has no effect on the relative price $RP$ in the long run;
+    	\item The news shock $V_{t-k}$ maximizes the FEV of future TFP subject to the restriction that it has no effect on the relative price $RP$ at a small number of quarters;
 
@@
 
-    \item The tech shock $\varepsilon_t$ is considered as a residual shock and is left unrestricted.
+    \item The tech shock $\varepsilon_t$ is considered as a residual shock and is left unrestricted (unidentified).
    \end{enumerate}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Our favorite specification}
+
+	\begin{itemize}
+	\item Recall: dataset is quarterly and covers 1989:q1-2017-q1.
+
+	\
+
+	\item One lag (as suggested by BIC and HQ).
+
+	\
+
+	\item Horizon of FEV-maximization: 100 quarters.
+
+	\
+
+	\item Restriction on relative prices after a news shock is imposed at 8 quarters.
+
+	\end{itemize}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Results - Impulse responses to a news shock}
+
+\includegraphics[scale=0.5]{}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Results - Impulse responses to an IT shock}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Results - FEV of TFP explained by the two shocks}
+
+    \hspace{2.25cm}
+\begin{large}
+	\begin{tabular}{lccc}
+	\hline
+		& News & IT & Total \\
+		\hline
+		 & 0.37195 & 0.43944 & 0.81138 \\
+		\hline
+	\end{tabular}
+\end{large}
 

### 2017-11-29 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
more work on the presentation

@@
 \pdfmapfile{+sansmathaccent.map}
-
+\def \ourFigPath {../../} 
+\setbeamersize{text margin left=5mm,text margin right=12mm} 
 %
@@
 \item $RP = \pi^{IT}/\pi^{CPI}$. 
-\item All variables are in log levels except for RP, which is in growth rates. 
+\item All variables are real (except price indexes) and in log levels (except for RP, which is in growth rates). 
 \item The dataset ranges from 1989:q1 - 2017:q1.
@@
 \begin{frame}
-	\frametitle{Results - Impulse responses to a news shock}
+	\frametitle{Impulse responses to a news shock}
 
-\includegraphics[scale=0.5]{}
+\vspace{-1cm}
+\noindent
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_29-Nov-2017_15_06_45}
+\end{figure}
 
@@
 \begin{frame}
-	\frametitle{Results - Impulse responses to an IT shock}
+	\frametitle{Impulse responses to an IT shock}
+
+\vspace{-1cm}
+\noindent
+\begin{figure}
+\centering
+\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_29-Nov-2017_15_06_52}
+\end{figure}
 
@@
 \begin{frame}
-	\frametitle{Results - FEV of TFP explained by the two shocks}
+	\frametitle{FEV of TFP explained by the two shocks at 40 periods}
 
@@
 \end{large}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Interpretation}
+
+\begin{enumerate}
+ \item Shape and timing of the responses reflect ...
+
+ %\
+
+	\begin{itemize}
+	\item both the Barsky \& Sims result ...
+
+	\
+
+	\item ... as well as the the conjecture that the IT shock looks similar to news along certain dimensions,
+
+	\
+
+	\item ... but relative prices do indeed introduce a margin of difference between the two shocks.
+	\end{itemize}
+
+\
+
+\item Shares of FEV of TFP explained ...
+	\begin{itemize}
+	\item ... are also in line with the Barsky \& Sims result ...
+	\item [] For BS, news explains around 45\%, compared to 37\% here
+
+	\
+
+	\item ... yet suggest that the IT shock plays an important role as well
+	\end{itemize}
+
+\end{enumerate}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Robustness checks}
+
+\begin{itemize}
+\item Different variables
+	\begin{itemize}
+	\item Add the Michigan index of consumer confidence (expected business conditions 5 years ahead)
+
+	\
+
+	\item Replace IT prices with capital prices (following Comin \& Gertler)
+	\end{itemize}
+
+	\
+
+\item Different horizons at which we impose the restriction on relative prices for the news shock
+\item[] $\rightarrow$ ran  6, 8, 10, 12 and 16 quarters.
+
+\
+
+\item Increase the number of lags (2)
+\end{itemize}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Conclusion}
+
+\begin{itemize}
+\item Provided what we think (and we hope you do too) a careful and more general test for the endogenous mechanism in TFP.
+\begin{itemize}
+\item While the literature focuses exclusively on R\&D, we show that IT is a better variable to focus on.
+\end{itemize}
+
+\
+
+\item The results show that by controlling for the presence of news shocks, the endogenous component of TFP is an important driver of TFP fluctuations at long horizons.
+
+\
+
+\item This result does not contrast however with the findings of the news shock literature since we still find that news also play a significant role in explaining TFP.
+
+\end{itemize}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Work ahead}
+
+\begin{itemize}
+\item Rationalize this setting using a theoretical model
+\item [] $\hookrightarrow$ what we have in mind: an endogenous TFP model (in the vein of Comin \& Gertler) augmented with news shocks
+
+\
+
+\item Estimate the model (IR-matching)
+
+\
+
+\item Perform a counterfactual for the Great Recession \emph{and} the period prior, shutting down the negative IT shocks around 2000
+% assuming the IT bubble, i.e. the negative shock to IT productivity around 2000, did not happen.
+
+\
+
+\item See if we can find interesting interactions between the two shocks?
+\item [] $\hookrightarrow$ In particular, we're thinking of noise shocks on IT productivity
+	\begin{itemize}
+	\item [] news shock: shock to expected future value
+	\item [] noise shock: shock to expected current value (``perceptions'')
+	\end{itemize}
+\end{itemize}
 
@@
 \
+
+\hyperlink{related_lit}{\beamerreturnbutton{Return}}	
+\hyperlink{BS_FEV}{\beamerbutton{Barsky \& Sims' FEV-table}}	
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Barsky \& Sims FEV of TFP explained}
+	\label{BS_FEV}
+
+\vspace{-1cm}
+\noindent
+\begin{figure}
+\centering
+\includegraphics[scale=0.3]{fig_BS_fevtable}
+\end{figure}
 

### 2017-11-29 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
Adding to the tex presentation new figures

@@
 
-\hspace{4cm}   between 6 -12 quarters
+\hspace{4cm}   between 6-12 quarters
 
@@
 \centering
-\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_29-Nov-2017_15_06_45}
+\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_29-Nov-2017_16_43_36}
 \end{figure}
@@
 \centering
-\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_29-Nov-2017_15_06_52}
+\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_29-Nov-2017_16_43_47}
 \end{figure}
@@
 \begin{frame}
-	\frametitle{FEV of TFP explained by the two shocks at 40 periods}
+	\frametitle{FEV explained by the two shocks at 40 periods}
 
@@
 		\hline
-		 & 0.37195 & 0.43944 & 0.81138 \\
+	TFP	           & 0.4081  & 0.4026 & 0.8107  \\
+	GDP            &         &        &         \\
+	Cons           &         &        &         \\
 		\hline

### 2017-11-29 main_file_SVAR_RyansID.m
Doing the figures for macrolunch presentation
Not completed yet

@@ -22,6 +22,8 @@ else
       warning('Position of Relative Price is not anymore 6.')
 end
 
+return
+
 %Technical Parameters
 max_lags        = 10;
 nburn           = 0; %with the Kilian correction better not burning!!!

### 2017-11-29 work_space_to_create_figures.m

@@ -1,0 +1,118 @@
+clear
+close all
+
+%Data Reading and Transformation
+filename = 'dataset_main';
+sheet    = 'Data';
+range    = 'B1:P286';
+[data, varnames] = read_data2(filename, sheet, range);
+
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%% PLOTTING TFP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+time_TFP = datetime(1989,4,1) + calquarters(0:size(data,1)-1);
+gcf = figure(1);
+set(gcf,'color','w');
+set(gcf,'position',[1 41 1920 963])
+hold on
+plot(time_TFP,data(:,1),'linewidth',1.5)
+xt = get(gca, 'XTick');
+set(gca, 'FontSize', 24)
+brk = time_TFP(68);
+y1 = get(gca,'ylim');
+plot([brk brk],y1)
+txt1 = '2006:q1';
+xtx = brk + 70;
+ytx = 345;
+text(xtx,ytx,txt1,'fontsize',24)
+leg = legend('Utilization-adjusted TFP');
+set(leg,'fontsize',28)
+grid on
+hold off
+%invoke_export_fig('TFP','macrolunch')
+
+clear
+close all
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%% PLOTTING R&D GROWTH %%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+filename = 'dataset_main';
+sheet    = 'Data';
+range    = 'B1:C286';
+[data, varnames] = read_data2(filename, sheet, range);
+data2 = [NaN NaN ; diff(log(data))];
+time_RD = datetime(1947,4,1) + calquarters(0:size(data,1)-1);
[…]

### 2017-11-30 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
Doing the figures for macrolunch presentation
Not completed yet
added the last plot to macro lunch presentation

@@
 
-	\
+	Why has TFP slowed down?
 
@@
 
-	Why has TFP slowed down? % show TFP graph here
+	\vspace{-1cm}
+	\noindent
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_TFP_macrolunch_29-Nov-2017_17_41_17}
+	\end{figure}
 
@@
 
+		\vspace{-1cm}
+	\noindent
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_RD_macrolunch_29-Nov-2017_18_12_20}
+	\end{figure}
+
 \hyperlink{convincing}{\beamerreturnbutton{Return}}	
@@
 
+	\vspace{-1cm}
+	\noindent
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_RD_level_macrolunch_29-Nov-2017_18_28_54}
+	\end{figure}
+
 \hyperlink{convincing}{\beamerreturnbutton{Return}}	
@@
 \begin{frame}
-	\frametitle{IT investment: a break at the right time}
+	\frametitle{IT investment: a drop at the right time}
 	\label{it_investment}
+
+%	\vspace{-1cm}
+	\noindent
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.31]{\ourFigPath Figures/fig_IT_level_macrolunch_30-Nov-2017_10_06_45}
+	\end{figure}
 

### 2017-11-30 work_space_to_create_figures.m

@@ -7,7 +7,6 @@ sheet    = 'Data';
 range    = 'B1:P286';
 [data, varnames] = read_data2(filename, sheet, range);
 
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%% PLOTTING TFP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@ -104,9 +103,45 @@ invoke_export_fig('RD_level','macrolunch')
 %corr(data(80:end,1),data(80:end,2))
 
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%% PLOTTING IT INVESTMENT %%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+clear
+close all
+
+filename = 'dataset_main';
+sheet    = 'Data';
+range    = 'B1:P286';
+[data, varnames] = read_data2(filename, sheet, range);
+data3 = log(data); % Marco?
+time_IT = datetime(1989,1,1) + calquarters(0:size(data,1)-1);
+time_IT = time_IT';
+IT = data3(:,3);
+[m, i] = max(IT);
+breaktime = datestr(time_IT(i),'yyyy-qq');
 
 
+gcf = figure(1);
+set(gcf,'color','w');
+set(gcf,'position',[1 41 1920 963])
+hold on
+plot(time_IT,IT,'linewidth',1.5)
+xt = get(gca, 'XTick');
+set(gca, 'FontSize', 24)
+brk = time_IT(i);
+y1 = get(gca,'ylim');
+plot([brk brk],y1, 'r--')
+txt1 = breaktime;
+xtx = brk + 200;
+ytx = 0.58;
+text(xtx,ytx,txt1,'fontsize',24)
+leg = legend('Real IT Investment','Location','East');
[…]

### 2017-11-30 Latex/general_writeups/general_writeup.tex
cleaned up the FEV tables and general_writeup a bit

--- 2017-11-27 Latex/general_writeup.tex
@@
 \usepackage{graphicx}
-\def \ourFigPath {../} 
+\def \ourFigPath {../../} 
 \usepackage{subfigure}
@@
 
-         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_8_24-Nov-2017_15_14_15}
+         \input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_8_24-Nov-2017_15_14_15}
 
@@
 
-         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_16_24-Nov-2017_18_56_26}
+         \input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_16_24-Nov-2017_18_56_26}
 
@@
 
-         \input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_80_24-Nov-2017_21_59_17}
+         \input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_80_24-Nov-2017_21_59_17}
 
@@
 
-	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_25-Nov-2017_11_39_14}
+	\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_25-Nov-2017_11_39_14}
 
@@
 
-	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_09_31_50}
+	\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_09_31_50}
 
@@
 
-	\input{FEVs_Ryan_two_stepsID_real_consumption_LR_hor_8_27-Nov-2017_12_27_33}
+	\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_real_consumption_LR_hor_8_27-Nov-2017_12_27_33}
 
@@
 
-	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_12_18}
+	\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_12_18}
 
@@
 
-	\input{FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_24_22}
+	\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_RelPrice_LR_hor_8_26-Nov-2017_10_24_22}
 
@@
 
-\input{FEVs_Ryan_two_stepsID_P_capital_LR_hor_8_24-Nov-2017_12_26_07}
+\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_P_capital_LR_hor_8_24-Nov-2017_12_26_07}
 
@@
 
-\input{FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_8_27-Nov-2017_14_42_35}
+\input{\ourFigPath Tables/FEVs_Ryan_two_stepsID_Rel_Price_LR_hor_8_27-Nov-2017_14_42_35}
 

### 2017-11-30 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
added forni gambetti test to presentation
Finishing presentation

--- 2017-11-29 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
@@
 
-\title{Title}
+\title{The Slowdown of TFP \\ Exogenous and Endogenous Mechanisms}
 
@@
 \item  But R\&D in the data is almost acyclical.... $\rightarrow$ hard to rationalize as a driver of business cycle fluctuations % hyperlink to graph: growth rate of RD vs. growth rate of TFP and GDP
- \hyperlink{growth_rates}{\beamergotobutton{Graph of acyclical R\&D}}
 
@@
 \emph{before} the Great Recession and thus \emph{before} the marked drop in R\&D  % hyperlink to graph: level of RD and TFP, so we see that TFP drops in 2006, while RD only during the recession.
-\hyperlink{timing}{\beamergotobutton{Graph of timing}}
+\hyperlink{timing}{\beamergotobutton{Graph of R\&D}}
 
@@
 	TFP	           & 0.4081  & 0.4026 & 0.8107  \\
-	GDP            &         &        &         \\
-	Cons           &         &        &         \\
 		\hline
@@
 \item Increase the number of lags (2)
+
+\
+
+\item Check whether VAR is information-sufficient to identify the two shocks (Forni-Gambetti test)
 \end{itemize}
@@
 \begin{frame}
-	\frametitle{Growth rate of RD vs growth rate of TFP}
-	\label{growth_rates}
+	\frametitle{Timing: RD drop vs TFP drop}
+	\label{timing}
+
+	\vspace{-1cm}
+	\noindent
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_RD_level_macrolunch_30-Nov-2017_11_31_04}
+	\end{figure}
 
@@
 \begin{frame}
-	\frametitle{Timing: RD drop vs TFP drop}
-	\label{timing}
+	\frametitle{IT investment: a drop at the right time}
+	\label{it_investment}
 
-\hyperlink{convincing}{\beamerreturnbutton{Return}}	
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{IT investment: a break at the right time}
-	\label{it_investment}
+%	\vspace{-1cm}
+	\noindent
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.29]{\ourFigPath Figures/fig_IT_level_macrolunch_30-Nov-2017_11_37_26}
+	\end{figure}
 

### 2017-11-30 read_data2.m

@@ -12,12 +12,12 @@ function [data, var_names] = read_data2(filename, sheet, range)
 % Row 5: Position: the position of the series in the dataset to be used (could play a role for Cholesky VARs for ex.)
 
 
-% Create the correct path 
+% Create the correct path
 base_path = pwd;
 if exist([base_path '\Data'], 'dir')
-    addpath([base_path '\Data']) %for Microsoft
+      addpath([base_path '\Data']) %for Microsoft
 else
-    addpath([base_path '/Data']) %for Mac
+      addpath([base_path '/Data']) %for Mac
 end
 
 % Reading Excel
@@ -36,21 +36,24 @@ nvar = size(variables,2);
 % if 3: take the log
 % if 4: take the difference
 % if 5: take the growth rate (diff after logs)
+% if 6: take the cumulative and then log
 % else: keep the level but warning
 for i_var = 1:nvar
       if     transformations(i_var) == 1
             full_data(:,i_var) = cumsum(full_data(:,i_var));
-      elseif transformations(i_var) == 2 
+      elseif transformations(i_var) == 2
             full_data(:,i_var) = full_data(:,i_var);
       elseif transformations(i_var) == 3
             full_data(:,i_var) = log(full_data(:,i_var));
-      elseif transformations(i_var) == 4 
+      elseif transformations(i_var) == 4
             full_data(:,i_var) = vertcat(nan, diff(full_data(:,i_var)));
       elseif transformations(:,i_var) == 5
             full_data(:,i_var) = vertcat(nan, diff(log(full_data(:,i_var))));
+      elseif transformations(:,i_var) == 6
+            full_data(:,i_var) = log(cumsum(full_data(:,i_var)));
       else
             warning('Some variables may have a mispecified transformation')
-      end     
+      end
 end
 
 % Selecting the VAR system we want to work with
@@ -64,7 +67,7 @@ for i_var = 1:nvar
             % keep variable out of VAR
       else
             warning('The selection procedure of the system may be mispecified')
-      end    
+      end
 end
 
 % Generalized Truncation

### 2017-11-30 work_space_to_create_figures.m

@@ -31,37 +31,34 @@ grid on
 hold off
 %invoke_export_fig('TFP','macrolunch')
 
-clear
-close all
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%% PLOTTING R&D GROWTH %%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-filename = 'dataset_main';
-sheet    = 'Data';
-range    = 'B1:C286';
-[data, varnames] = read_data2(filename, sheet, range);
-data2 = [NaN NaN ; diff(log(data))];
-time_RD = datetime(1947,4,1) + calquarters(0:size(data,1)-1);
-time_RD = time_RD';
-
-
-figure(1)
-gcf = figure(1);
-set(gcf,'color','w');
-set(gcf,'position',[1 41 1920 963])
-hold on
-plot(time_RD(80:end),data2(80:end,:),'linewidth',1.5)
-leg = legend('Utilization-adjusted TFP','Real R&D expenditure');
-set(leg,'fontsize',28)
-xt = get(gca, 'XTick');
-set(gca, 'FontSize', 24)
-grid on
-hold off
+% filename = 'dataset_main';
+% sheet    = 'Data';
+% range    = 'B1:C286';
+% [data, varnames] = read_data2(filename, sheet, range);
+% data2(:,1) = data(:,1)./4; 
+% data2(:,2) = [NaN ; diff(data(:,2)).*100];
+% time_RD = datetime(1947,4,1) + calquarters(0:size(data,1)-1);
+% time_RD = time_RD';
+% 
+% 
+% figure(1)
+% gcf = figure(1);
+% set(gcf,'color','w');
+% set(gcf,'position',[1 41 1920 963])
+% hold on
+% plot(time_RD(80:end),data2(80:end,:),'linewidth',1.5)
+% leg = legend('Utilization-adjusted TFP','Real R&D expenditure');
+% set(leg,'fontsize',28)
+% xt = get(gca, 'XTick');
+% set(gca, 'FontSize', 24)
+% grid on
+% hold off
 %invoke_export_fig('RD','macrolunch')
[…]

### 2017-12-05 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
Adding single_plot_IRF

@@
 \usepackage{verbatim}
+\usepackage{caption}
+\usepackage{float}
 \usepackage{csquotes}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{TFP response to both shocks}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_TFP_Ryan_two_stepsID_05-Dec-2017_10_53_04}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_TFP_Ryan_two_stepsID_05-Dec-2017_10_53_13}
+\end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Real SP500 response to both shocks}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_SP_Ryan_two_stepsID_05-Dec-2017_10_53_06}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_SP_Ryan_two_stepsID_05-Dec-2017_10_53_14}
+\end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Real IT investment response to both shocks}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_IT_Investment_Ryan_two_stepsID_05-Dec-2017_10_53_07}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_IT_Investment_Ryan_two_stepsID_05-Dec-2017_10_53_15}
+\end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Real GDP response to both shocks}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_GDP_Ryan_two_stepsID_05-Dec-2017_10_53_09}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_GDP_Ryan_two_stepsID_05-Dec-2017_10_53_16}
+\end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Real Consumption response to both shocks}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_Consumption_Ryan_two_stepsID_05-Dec-2017_10_53_10}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_Consumption_Ryan_two_stepsID_05-Dec-2017_10_53_17}
+\end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%% Slide %%%%%%

### 2017-12-05 invoke_export_fig.m

@@ -17,7 +17,7 @@ figname = strrep(figname,' ','_');
 some_comment = strrep(some_comment,':','_');
 some_comment = strrep(some_comment,' ','_');
 
-final_name = ['fig_' figname '_' some_comment '_' ct2 '.pdf'];
+final_name = ['fig_' figname '_' some_comment '_' ct2 '.png'];
 
 base_path = pwd;
 if exist([base_path '\Figures'], 'dir')

### 2017-12-05 main_file_SVAR_RyansID.m

@@ -84,8 +84,8 @@ end
 
 %Creating and Printing figures
 comment = [which_ID '_' char(varnames(5)) '_LR_hor_' num2str(LR_hor)];
-
 print_figs = 'yes';
+
 [IRFs, ub, lb] = genIRFs(fake_impact,fake_impact_boot,...
       B,beta_tilde_star,H,sig);
 
@@ -104,8 +104,10 @@ if sum(IRFs(1,:,4)) < 0 % if the majority of TFP response is negative
 end
 
 %Printing/Showing IRFs
-plotIRFs(IRFs,ub,lb,40,which_shocks,shocknames,varnames, ...
-      which_ID,print_figs)
+h = 40;
+% plotIRFs(IRFs,ub,lb,40,which_shocks,shocknames,varnames, ...
+%       which_ID,print_figs)
+plot_single_IRFs(IRFs,ub,lb,h,which_shocks,shocknames, varnames, which_ID, print_figs)
 
 %Forni&Gambetti Orthogonality Test
 do_FG_test = 'no';

### 2017-12-05 plot_since_IRFs.m

@@ -1,0 +1,46 @@
+function plot_single_IRFs(IRFs,ub,lb,h,which_shock,names, varnames, which_ID_strat, print_figs)
+% h = IR horizon for figures
+% ub and lb are the bootstrapped CI
+% names = cell vector of shock names
+% varnames = cell vector of variable names
+% which_ID_strat = a string describing which identification strategy we used
+% print_figs = 'yes' --> saves the figures; else if 'no' -- > just
+% shows the figures.
+
+nvar = size(IRFs,1);
+nshocks = size(which_shock,2);
+periods = 1:h;
+
+% Draw pretty pictures
+for i_shock=1:nshocks
+      for i_var=1:nvar
+            figure(i_shock*nvar - nvar + i_var)
+            set(gcf,'color','w'); % sets white background color
+            set(gcf, 'Position', get(0, 'Screensize')); % sets the figure fullscreen (hopefully)
+            varname = varnames{i_var};
+            name = names{i_shock};
+            hold on
+            x2 = [periods, fliplr(periods)];
+            inBetween = [lb(i_var,1:h,which_shock(i_shock)), ...
+                  fliplr(ub(i_var,1:h,which_shock(i_shock)))];
+            fill(x2, inBetween, [0.75 0.75 0.75],'LineStyle','none');
+            plot(zeros(1,h), 'Color','b')
+            plot(periods,IRFs(i_var,1:h,which_shock(i_shock)),'linewidth',1,'Color','r')
+            title([name, ' on ' , varname],'fontsize',18)
+            %title([varname],'fontsize',18)
+            xt = get(gca, 'XTick');
+            set(gca, 'FontSize', 14)
+            hold off
+            grid on
+            
+            % Save figures if you want to
+            if strcmp(print_figs, 'yes')
+                  invoke_export_fig(name, which_ID_strat)
+                  close all
+                  pause(1)
+            end
+      end
+end
+
+
+end

### 2017-12-05 plot_single_IRFs.m

@@ -1,0 +1,46 @@
+function plot_single_IRFs(IRFs,ub,lb,h,which_shock,names, varnames, which_ID_strat, print_figs)
+% h = IR horizon for figures
+% ub and lb are the bootstrapped CI
+% names = cell vector of shock names
+% varnames = cell vector of variable names
+% which_ID_strat = a string describing which identification strategy we used
+% print_figs = 'yes' --> saves the figures; else if 'no' -- > just
+% shows the figures.
+
+nvar = size(IRFs,1);
+nshocks = size(which_shock,2);
+periods = 1:h;
+
+% Draw pretty pictures
+for i_shock=1:nshocks
+      for i_var=1:nvar
+            figure(i_shock*nvar - nvar + i_var)
+            set(gcf,'color','w'); % sets white background color
+            set(gcf, 'Position', get(0, 'Screensize')); % sets the figure fullscreen (hopefully)
+            varname = varnames{i_var};
+            name = names{i_shock};
+            hold on
+            x2 = [periods, fliplr(periods)];
+            inBetween = [lb(i_var,1:h,which_shock(i_shock)), ...
+                  fliplr(ub(i_var,1:h,which_shock(i_shock)))];
+            fill(x2, inBetween, [0.75 0.75 0.75],'LineStyle','none');
+            plot(zeros(1,h), 'Color','b')
+            plot(periods,IRFs(i_var,1:h,which_shock(i_shock)),'linewidth',1,'Color','r')
+            %title([varname],'fontsize',18)
+            xt = get(gca, 'XTick');
+            set(gca, 'FontSize', 14)
+            title([name, ' on ' , varname],'fontsize',60)
+            hold off
+            grid on
+            
+            % Save figures if you want to
+            if strcmp(print_figs, 'yes')
+                  invoke_export_fig([name, ' on ' , varname], which_ID_strat)
+                  close all
+                  pause(0.5)
+            end
+      end
+end
+
+
+end

### 2017-12-06 Ryan_two_stepsID.m
correct_favourite_macrolunch
A lot of things are going on.

1. I have updated the figures in order to allow 2 confidence intervals (90% and 95% for example)

2. Very inelegantly I have fixed the scale of the IRFs across shocks. You will see how I have done looking at plot_single_IRF

3. I run 1000 bootstraps of the new corrected specification (Real SP500 are now in logs), 1 lag, 8 is the horizon contraint.

Problems.

For some obscure reasons I do not know why the point estimate is not anymore perfectly inside the confidence intervals. You can see such results on figures that I run todat at 2p

@@ -32,8 +32,9 @@ options  = optimset(options, 'TolFun', 1e-9, 'display', 'none');
 % Instead of Blanchard Quah, impose that IR(rel_prices, news) = 0 at some
 % finite long horizon.
 % LR_hor = 8; % 100
-sig = 0.9; % not used, but we need to input something not to get error
-[IR, ~, ~] = genIRFs(A,0,vertcat(ones(1,size(B,2)), B),0,LR_hor, sig);
+sig1 = 0.9; % not used, but we need to input something not to get error
+sig2 = 0.95; % not used, but we need to input something not to get error
+[IR, ~, ~, ~, ~] = genIRFs(A,0,vertcat(ones(1,size(B,2)), B),0,LR_hor, sig1,sig2);
 % R = zeros(nvar,nvar); 
 R = squeeze(IR(:,end,:)); % comment this out if you wanna not impose the LR-restriction
 

### 2017-12-06 genIRFs.m

@@ -1,15 +1,19 @@
-function [IRFs, ub, lb] = genIRFs(A_IRF,A_boot,B,B_boot,H, sig)
+function [IRFs, ub1, lb1, ub2, lb2] = genIRFs(A_IRF,A_boot,B,B_boot,H, sig1, sig2)
 % Generate IRFs and bootstrapped IRF confidence intervals for ALL shocks
 % H = IR horizon for the generation of IRFs (to be used in variance decomposition)
-% sig = CI significance level (enter as 0.9 for example)
+% sig1 = CI significance level (enter as 0.9 for example)
+% sig2 = CI significance level (enter as 0.95 for example)
+% sig1 should be smaller to sig2 as an informal rule
 % Can choose not to do bootstrapping by setting A_boot to 0.
 
 nvar = size(A_IRF,1);
 nlag = (size(B,1)-1)/nvar;
 nshocks = nvar;
 nsimul = size(A_boot,3);
-perc_up = ceil(nsimul*sig); % the upper percentile of bootstrapped responses for CI
-perc_low = floor(nsimul*(1-sig)); % the lower percentile of bootstrapped responses for CI
+perc_up1 = ceil(nsimul*sig1); % the upper percentile of bootstrapped responses for CI
+perc_low1 = floor(nsimul*(1-sig1)); % the lower percentile of bootstrapped responses for CI
+perc_up2 = ceil(nsimul*sig2); % the upper percentile of bootstrapped responses for CI
+perc_low2 = floor(nsimul*(1-sig2)); % the lower percentile of bootstrapped responses for CI
 
 % Remove constant
 B = B(2:end,:);
@@ -20,8 +24,10 @@ B_boot = B_boot(2:end,:,:);
 IRFs = zeros(nvar,H,nshocks);
 IRFs_boot = zeros(nvar,H,nshocks,nsimul);
 IRFs_boot_sorted = zeros(nvar,H,nshocks,nsimul);
-ub = zeros(nvar,H,nshocks);
-lb = zeros(nvar,H,nshocks);
+ub1 = zeros(nvar,H,nshocks);
+lb1 = zeros(nvar,H,nshocks);
+ub2 = zeros(nvar,H,nshocks);
+lb2 = zeros(nvar,H,nshocks);
 
 for i_shock=1:nshocks
       shocks = zeros(nvar,1);
@@ -61,13 +67,10 @@ for i_shock=1:nshocks
[…]

### 2017-12-06 main_file_SVAR_RyansID.m

@@ -22,14 +22,13 @@ else
       warning('Position of Relative Price is not anymore 6.')
 end
 
-return
-
 %Technical Parameters
 max_lags        = 10;
 nburn           = 0; %with the Kilian correction better not burning!!!
-nsimul          = 500; %5000
+nsimul          = 20; %5000
 nvar            = size(data,2);
-sig             = 0.90; % significance level
+sig1            = 0.90; % significance level
+sig2            = 0.90; % significance level
 H               = 100; %40; % horizon for generation of IRFs
 h               = H; %40; % horizon for IRF plots
 which_variable  = 1; % select TFP as the variable whose FEV we wanna max
@@ -50,7 +49,7 @@ end
 test_stationarity(B');
 
 % Implement Ryan's ID strategy
-LR_hor = 8; % at what horizon to impose the LR restriction
+LR_hor = 10; % at what horizon to impose the LR restriction
 % [impact, FEV_opt, IRFs, gamma_opt, FEV_news, FEV_IT] = ryansID(which_variable,which_shocks,H,B,A,q);
 [impact, FEV_opt, ~, gam_opt, FEV_news, FEV_IT] ...
     = Ryan_two_stepsID(which_variable,which_shocks,H,...
@@ -84,30 +83,34 @@ end
 
 %Creating and Printing figures
 comment = [which_ID '_' char(varnames(5)) '_LR_hor_' num2str(LR_hor)];
-print_figs = 'yes';
+print_figs = 'no';
 
-[IRFs, ub, lb] = genIRFs(fake_impact,fake_impact_boot,...
-      B,beta_tilde_star,H,sig);
+[IRFs, ub1, lb1, ub2, lb2] = genIRFs(fake_impact,fake_impact_boot,...
+      B,beta_tilde_star,H,sig1,sig2);
 
 % % With Barsky & Sims-type ID, since you do a abs max, there are two
 % % solutions: gam and -gam. So choose the one that makes sense. I'm doing
 % % that so that news and IT have + effects on TFP.
 if sum(IRFs(1,:,3)) < 0 % if the majority of TFP response is negative
     IRFs(:,:,3)   = -IRFs(:,:,3);
-    ub(:,:,3)     = - ub(:,:,3);
[…]

### 2017-12-06 plot_single_IRFs.m

@@ -1,4 +1,4 @@
-function plot_single_IRFs(IRFs,ub,lb,h,which_shock,names, varnames, which_ID_strat, print_figs)
+function plot_single_IRFs(IRFs,ub1,lb1,ub2,lb2,h,which_shock,names, varnames, which_ID_strat, print_figs)
 % h = IR horizon for figures
 % ub and lb are the bootstrapped CI
 % names = cell vector of shock names
@@ -12,8 +12,8 @@ nshocks = size(which_shock,2);
 periods = 1:h;
 
 %Ylim
-min_y_lim = [-0.5    -0.1     -0.01     0        0        -0.012];
-max_y_lim = [2.5      0.8      0.03     0.012    0.012     0.006];
+min_y_lim = [-0.5      0       -0.015     0        0        -0.012];
+max_y_lim = [4       0.09      0.05     0.025    0.025     0.006];
 
 % Draw pretty pictures
 for i_shock=1:nshocks
@@ -25,9 +25,13 @@ for i_shock=1:nshocks
             name = names{i_shock};
             hold on
             x2 = [periods, fliplr(periods)];
-            inBetween = [lb(i_var,1:h,which_shock(i_shock)), ...
-                  fliplr(ub(i_var,1:h,which_shock(i_shock)))];
+            inBetween = [lb2(i_var,1:h,which_shock(i_shock)), ...
+                  fliplr(ub2(i_var,1:h,which_shock(i_shock)))];
             fill(x2, inBetween, [0.75 0.75 0.75],'LineStyle','none');
+            x1 = [periods, fliplr(periods)];
+            inBetween = [lb1(i_var,1:h,which_shock(i_shock)), ...
+                  fliplr(ub1(i_var,1:h,which_shock(i_shock)))];
+            fill(x1, inBetween, [0.5 0.5 0.5],'LineStyle','none');
             plot(zeros(1,h), 'Color','b')
             plot(periods,IRFs(i_var,1:h,which_shock(i_shock)),'linewidth',1,'Color','r')
             xt = get(gca, 'XTick');

### 2017-12-07 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
added new figures and new FEV to presentation

--- 2017-11-30 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
@@
 \usepackage{verbatim}
+\usepackage{caption}
+\usepackage{float}
 \usepackage{csquotes}
 \usepackage{sansmathaccent}
+\usepackage{subfigure}
+\usepackage{multicol}
 \pdfmapfile{+sansmathaccent.map}
@@
 	\end{itemize}
-\item [] \textbf{Our contribution: allow in this setting the existence of an endogenous mechanism that affects future TFP}
+\item [] \textbf{Our contribution: allow in this setting for the existence of an endogenous mechanism that affects future TFP}
 
@@
 
-%%%%%%% Slide %%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}
-	\frametitle{Impulse responses to a news shock}
-
-\vspace{-1cm}
-\noindent
+\frametitle{TFP response to both shocks}
 \begin{figure}
 	\centering
-\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_29-Nov-2017_16_43_36}
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_TFP_Ryan_two_stepsID_06-Dec-2017_14_00_39}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_TFP_Ryan_two_stepsID_06-Dec-2017_14_00_47}
+\end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Real SP500 response to both shocks}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_SP_Ryan_two_stepsID_06-Dec-2017_14_00_40}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_SP_Ryan_two_stepsID_06-Dec-2017_14_00_48}
+\end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Other responses to  both shocks}
+
+\begin{figure}
+\begin{multicols}{2}
+\centering
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_IT_Investment_Ryan_two_stepsID_06-Dec-2017_14_00_41}\\  
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_GDP_Ryan_two_stepsID_06-Dec-2017_14_00_43}\\ 
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_Consumption_Ryan_two_stepsID_06-Dec-2017_14_00_44}\\ 
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Relative_Price_Ryan_two_stepsID_06-Dec-2017_14_00_45}\\
+
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_IT_Investment_Ryan_two_stepsID_06-Dec-2017_14_00_49}\\
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_GDP_Ryan_two_stepsID_06-Dec-2017_14_00_51}\\
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_Consumption_Ryan_two_stepsID_06-Dec-2017_14_00_52}\\ 
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Relative_Price_Ryan_two_stepsID_06-Dec-2017_14_00_53}\\
+
+\end{multicols}
 \end{figure}
@@
 \end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Impulse responses to an IT shock}
-
-\vspace{-1cm}
-\noindent
-\begin{figure}
-\centering
-\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_29-Nov-2017_16_43_47}
-\end{figure}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 		\hline
-	TFP	           & 0.4081  & 0.4026 & 0.8107  \\
+	TFP	           & 0.2060  & 0.5776 & 0.7836  \\
 		\hline
@@
 
-	\item ... as well as the the conjecture that the IT shock looks similar to news along certain dimensions,
+	\item ... as well as the conjecture that the IT shock looks similar to news along certain dimensions,
 
@@
 
-\
+\vspace{0.1cm}
 
@@
 	\begin{itemize}
-	\item ... are also in line with the Barsky \& Sims result ...
-	\item [] For BS, news explains around 45\%, compared to 37\% here
+	\item ... also reflect the Barsky \& Sims result in that the contribution of the news shock is still significant...
+
+	\item [] (For BS, news explains around 45\%, compared to 20\% here)
 
@@
 
-	\item ... yet suggest that the IT shock plays an important role as well
+	\item ... yet suggest that the IT shock plays a very important role as well (nearly 60\%)
+
+	\
+
+	\item ... and was previously - as anticipated by BS - partly counfounded with news!
 	\end{itemize}
@@
 
-\item Check whether VAR is information-sufficient to identify the two shocks (Forni-Gambetti test)
+\item Check whether VAR is information-sufficient to identify the news shock (Forni-Gambetti test) (p-val of 12\%)
 \end{itemize}
@@
 \begin{itemize}
-\item Provided what we think (and we hope you do too) a careful and more general test for the endogenous mechanism in TFP.
+\item We provided what we think (and we hope you do too) a careful and more general test for the endogenous mechanism in TFP.
 \begin{itemize}

### 2017-12-08 main_file_SVAR_RyansID.m
did some diagnostics on the CI not even problem
To me it’s not a specification problem. It’s either a bootstrap
calculation problem or a plotting problem.

@@ -15,13 +15,24 @@ range    = 'B1:P286';
 [data, varnames] = read_data2(filename, sheet, range);
 shocknames = {'News Shock','IT Shock'};
 % which_shocks = [3 4];
-which_shocks = [2 3];
+which_shocks   = [2 3];
 pos_rel_prices = 6;
+pos_news       = 2;
+pos_IT         = 3;
 if pos_rel_prices == 6
 else
       warning('Position of Relative Price is not anymore 6.')
 end
-
+if strcmp(varnames(pos_news),'Real SP') == 1
+    % good
+else
+    warning('Position of News is not anymore 2.')
+end
+if strcmp(varnames(pos_IT),'Real IT Investment') == 1
+    % good
+else
+    warning('Position of IT is not anymore 3.')
+end
 %Technical Parameters
 max_lags        = 10;
 nburn           = 0; %with the Kilian correction better not burning!!!
@@ -49,7 +60,7 @@ end
 test_stationarity(B');
 
 % Implement Ryan's ID strategy
-LR_hor = 10; % at what horizon to impose the LR restriction
+LR_hor = 8; % at what horizon to impose the LR restriction
 % [impact, FEV_opt, IRFs, gamma_opt, FEV_news, FEV_IT] = ryansID(which_variable,which_shocks,H,B,A,q);
 [impact, FEV_opt, ~, gam_opt, FEV_news, FEV_IT] ...
     = Ryan_two_stepsID(which_variable,which_shocks,H,...
@@ -91,20 +102,22 @@ print_figs = 'no';
 % % With Barsky & Sims-type ID, since you do a abs max, there are two
 % % solutions: gam and -gam. So choose the one that makes sense. I'm doing
 % % that so that news and IT have + effects on TFP.
-if sum(IRFs(1,:,3)) < 0 % if the majority of TFP response is negative
-    IRFs(:,:,3)   = -IRFs(:,:,3);
-    ub1(:,:,3)     = - ub1(:,:,3);
-    lb1(:,:,3)     = - lb1(:,:,3);
-    ub2(:,:,3)     = - ub2(:,:,3);
-    lb2(:,:,3)     = - lb2(:,:,3);
[…]

### 2017-12-09 main_file_SVAR_RyansID.m
Revert "did some diagnostics on the CI not even problem"
This reverts commit 1b9009d1134c4f0afde3d3bb1eff50e50577e52f.

@@ -15,24 +15,13 @@ range    = 'B1:P286';
 [data, varnames] = read_data2(filename, sheet, range);
 shocknames = {'News Shock','IT Shock'};
 % which_shocks = [3 4];
-which_shocks   = [2 3];
+which_shocks = [2 3];
 pos_rel_prices = 6;
-pos_news       = 2;
-pos_IT         = 3;
 if pos_rel_prices == 6
 else
       warning('Position of Relative Price is not anymore 6.')
 end
-if strcmp(varnames(pos_news),'Real SP') == 1
-    % good
-else
-    warning('Position of News is not anymore 2.')
-end
-if strcmp(varnames(pos_IT),'Real IT Investment') == 1
-    % good
-else
-    warning('Position of IT is not anymore 3.')
-end
+
 %Technical Parameters
 max_lags        = 10;
 nburn           = 0; %with the Kilian correction better not burning!!!
@@ -60,7 +49,7 @@ end
 test_stationarity(B');
 
 % Implement Ryan's ID strategy
-LR_hor = 8; % at what horizon to impose the LR restriction
+LR_hor = 10; % at what horizon to impose the LR restriction
 % [impact, FEV_opt, IRFs, gamma_opt, FEV_news, FEV_IT] = ryansID(which_variable,which_shocks,H,B,A,q);
 [impact, FEV_opt, ~, gam_opt, FEV_news, FEV_IT] ...
     = Ryan_two_stepsID(which_variable,which_shocks,H,...
@@ -102,22 +91,20 @@ print_figs = 'no';
 % % With Barsky & Sims-type ID, since you do a abs max, there are two
 % % solutions: gam and -gam. So choose the one that makes sense. I'm doing
 % % that so that news and IT have + effects on TFP.
-if sum(IRFs(1,:,pos_news)) < 0 % if the majority of TFP response is negative (news)
-    IRFs(:,:,pos_news)   = -IRFs(:,:,pos_news);
-    ub1(:,:,pos_news)    = - ub1(:,:,pos_news);
-    lb1(:,:,pos_news)    = - lb1(:,:,pos_news);
-    ub2(:,:,pos_news)    = - ub2(:,:,pos_news);
[…]

### 2017-12-09 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
did some diagnostics on the CI not even problem
To me it’s not a specification problem. It’s either a bootstrap
calculation problem or a plotting problem.
Revert "added new figures and new FEV to presentation"
This reverts commit ecb61e558c0db68064b3e62886e566b729a7b87e.

--- 2017-11-30 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
@@
 
-%%%%%%% Slide %%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}
-	\frametitle{Impulse responses to a news shock}
-
-\vspace{-1cm}
-\noindent
+\frametitle{TFP response to both shocks}
 \begin{figure}
 	\centering
-\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_29-Nov-2017_16_43_36}
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_TFP_Ryan_two_stepsID_05-Dec-2017_10_53_04}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_TFP_Ryan_two_stepsID_05-Dec-2017_10_53_13}
+\end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Real SP500 response to both shocks}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_SP_Ryan_two_stepsID_05-Dec-2017_10_53_06}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_SP_Ryan_two_stepsID_05-Dec-2017_10_53_14}
+\end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{Other responses to  both shocks}
+
+\begin{figure}
+\begin{multicols}{2}
+\centering
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_IT_Investment_Ryan_two_stepsID_05-Dec-2017_10_53_07}\\  
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_GDP_Ryan_two_stepsID_05-Dec-2017_10_53_09}\\ 
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_Consumption_Ryan_two_stepsID_05-Dec-2017_10_53_10}\\ 
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Relative_Price_Ryan_two_stepsID_05-Dec-2017_10_53_11}\\
+
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_IT_Investment_Ryan_two_stepsID_05-Dec-2017_10_53_15}\\
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_GDP_Ryan_two_stepsID_05-Dec-2017_10_53_16}\\
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_Consumption_Ryan_two_stepsID_05-Dec-2017_10_53_17}\\ 
+\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Relative_Price_Ryan_two_stepsID_05-Dec-2017_10_53_19}\\
+
+\end{multicols}
 \end{figure}

### 2017-12-10 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
added figures from the new nice specification and FEV-table, and also added FEVs in the presentation

@@
 		\hline
-	TFP	           & 0.4081  & 0.4026 & 0.8107  \\
+	TFP	           & 0.20384  & 0.52596 & 0.72981  \\
 		\hline
@@
 
-	\
+	\vspace{0.1cm}
 
@@
 	\item ... are also in line with the Barsky \& Sims result ...
-	\item [] For BS, news explains around 45\%, compared to 37\% here
+	\item [] For BS, news explains around 45\%, compared to 20\% here
 
-	\
+	\vspace{0.1cm}
 
-	\item ... yet suggest that the IT shock plays an important role as well
+	\item ... yet suggest that the IT shock plays an important role as well (around 52\%)
+
+	\vspace{0.1cm}
+
+	\item ... and indeed the IT shock \emph{complements} the news shock, instead of substituting for it
+	\item [] For BS, the single identified shock explains around 45\%, while our two identified shocks explain around 73\%
 	\end{itemize}

### 2017-12-10 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
saved more figures, updated presentation and added an option for export_fig where we don't save the time
The latter should be useful for creating and updating figures for a
latex document, so we don’t need to rename the figures in the latex
document, because they overwrite the old figures.

@@
 	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_TFP_Ryan_two_stepsID_05-Dec-2017_10_53_04}
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_TFP__}
 \end{figure}
@@
 	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_TFP_Ryan_two_stepsID_05-Dec-2017_10_53_13}
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_TFP__}
 \end{figure}
@@
 	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_SP_Ryan_two_stepsID_05-Dec-2017_10_53_06}
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_SP__}
 \end{figure}
@@
 	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_SP_Ryan_two_stepsID_05-Dec-2017_10_53_14}
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_SP__}
+\end{figure}
+\end{frame}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{frame}
+\frametitle{IT investment response to both shocks}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_IT_Investment__}
+\end{figure}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_IT_Investment__}
 \end{figure}
@@
 
+\vspace{-0.2cm}
 \begin{figure}
@@
 \centering 
-\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_IT_Investment_Ryan_two_stepsID_05-Dec-2017_10_53_07}\\  
-\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_GDP_Ryan_two_stepsID_05-Dec-2017_10_53_09}\\ 
-\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Real_Consumption_Ryan_two_stepsID_05-Dec-2017_10_53_10}\\ 
-\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_News_Shock_on_Relative_Price_Ryan_two_stepsID_05-Dec-2017_10_53_11}\\
+\includegraphics[scale = 0.1]{\ourFigPath Figures/fig_News_Shock_on_Real_GDP_Ryan_two_stepsID_10-Dec-2017_17_34_47}\\ 
+\vspace{0.3cm}
+\includegraphics[scale = 0.1]{\ourFigPath Figures/fig_News_Shock_on_Real_Consumption_Ryan_two_stepsID_10-Dec-2017_17_34_50}\\ 
+\vspace{0.3cm}
+\includegraphics[scale = 0.1]{\ourFigPath Figures/fig_News_Shock_on_Relative_Price_Ryan_two_stepsID_10-Dec-2017_17_34_52}\\
 
-\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_IT_Investment_Ryan_two_stepsID_05-Dec-2017_10_53_15}\\
-\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_GDP_Ryan_two_stepsID_05-Dec-2017_10_53_16}\\
-\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Real_Consumption_Ryan_two_stepsID_05-Dec-2017_10_53_17}\\ 
-\includegraphics[scale = 0.08]{\ourFigPath Figures/fig_IT_Shock_on_Relative_Price_Ryan_two_stepsID_05-Dec-2017_10_53_19}\\
+\includegraphics[scale = 0.1]{\ourFigPath Figures/fig_IT_Shock_on_Real_GDP_Ryan_two_stepsID_10-Dec-2017_17_35_00}\\
+\vspace{0.3cm}
+\includegraphics[scale = 0.1]{\ourFigPath Figures/fig_IT_Shock_on_Real_Consumption_Ryan_two_stepsID_10-Dec-2017_17_35_02}\\ 
+\vspace{0.3cm}
+\includegraphics[scale = 0.1]{\ourFigPath Figures/fig_IT_Shock_on_Relative_Price_Ryan_two_stepsID_10-Dec-2017_17_35_04}\\
 

### 2017-12-10 invoke_export_fig.m

@@ -1,4 +1,4 @@
-function invoke_export_fig(figname, some_comment)
+function invoke_export_fig(figname, some_comment,use_current_time)
 % This file invokes the export_fig command which requires the figure to be saved to be open
 % Inputs:
 % figname      = what you want the figure to be called
@@ -6,18 +6,22 @@ function invoke_export_fig(figname, some_comment)
 % Outputs: a figure saved as a pdf with the name
 % fig_figname_some_comment_time.pdf
 
-
-current_time = datestr(now);
-ct1 = strrep(current_time,':','_'); % substitute : with _
-ct2 = strrep(ct1,' ','_'); % substitute spaces with _
-
 % Make sure there are no spaces or : in any of the strings
 figname = strrep(figname,':','_');
 figname = strrep(figname,' ','_');
 some_comment = strrep(some_comment,':','_');
 some_comment = strrep(some_comment,' ','_');
 
-final_name = ['fig_' figname '_' some_comment '_' ct2 '.png'];
+if use_current_time==1
+    current_time = datestr(now);
+    ct1 = strrep(current_time,':','_'); % substitute : with _
+    ct2 = strrep(ct1,' ','_'); % substitute spaces with _
+    
+    final_name = ['fig_' figname '_' some_comment '_' ct2 '.png'];
+    
+else
+    final_name = ['fig_' figname '_' some_comment '.png'];
+end
 
 base_path = pwd;
 if exist([base_path '\Figures'], 'dir')

### 2017-12-10 main_file_SVAR_RyansID.m

@@ -119,7 +119,8 @@ end
 h = 40;
 % plotIRFs(IRFs,ub,lb,40,which_shocks,shocknames,varnames,which_ID,print_figs)
 % plot_single_IRFs(IRFs,ub1,lb1,h,which_shocks,shocknames, varnames, which_ID, print_figs)
-plot_single_IRFs_2CIs(IRFs,ub1,lb1,ub2,lb2,h,which_shocks,shocknames, varnames, which_ID, print_figs)
+use_current_time = 0; % don't save the time
+plot_single_IRFs_2CIs(IRFs,ub1,lb1,ub2,lb2,h,which_shocks,shocknames, varnames, '_', print_figs, use_current_time)
 
 %Forni&Gambetti Orthogonality Test
 do_FG_test = 'no';

### 2017-12-10 plot_single_IRFs.m

@@ -1,4 +1,4 @@
-function plot_single_IRFs(IRFs,ub,lb,h,which_shock,names, varnames, which_ID_strat, print_figs)
+function plot_single_IRFs(IRFs,ub,lb,h,which_shock,names, varnames, which_ID_strat, print_figs, use_current_time)
 % h = IR horizon for figures
 % ub and lb are the bootstrapped CI
 % names = cell vector of shock names
@@ -39,7 +39,7 @@ for i_shock=1:nshocks
             
             % Save figures if you want to
             if strcmp(print_figs, 'yes')
-                  invoke_export_fig([name, ' on ' , varname], which_ID_strat)
+                  invoke_export_fig([name, ' on ' , varname], which_ID_strat,use_current_time)
                   close all
                   pause(0.5)
             end

### 2017-12-10 plot_single_IRFs_2CIs.m

@@ -1,4 +1,4 @@
-function plot_single_IRFs_2CIs(IRFs,ub1,lb1,ub2, lb2, h,which_shock,names, varnames, which_ID_strat, print_figs)
+function plot_single_IRFs_2CIs(IRFs,ub1,lb1,ub2, lb2, h,which_shock,names, varnames, which_ID_strat, print_figs, use_current_time)
 % h = IR horizon for figures
 % ub1 and lb1 are the bootstrapped CI for the 1st significance level
 % ub2 and lb2 are the bootstrapped CI for the 2nd significance level
@@ -13,10 +13,8 @@ nshocks = size(which_shock,2);
 periods = 1:h;
 
 %Ylim
-% min_y_lim = [-0.5    -0.1     -0.01     0        0        -0.012];
-% max_y_lim = [2.5      0.8      0.03     0.012    0.012     0.006];
-min_y_lim = [-3    -0.1     -0.05     -0.02       -0.02     -0.02];
-max_y_lim = [3      0.1      0.05     0.02        0.02       0.02];
+min_y_lim = [-1   -0.01     -0.02     -0.02       -0.02     -0.02];
+max_y_lim = [4        0.1      0.05      0.02        0.02      0.02];
 
 % Draw pretty pictures
 for i_shock=1:nshocks
@@ -39,7 +37,7 @@ for i_shock=1:nshocks
         plot(zeros(1,h), 'Color','b')
         plot(periods,IRFs(i_var,1:h,which_shock(i_shock)),'linewidth',1,'Color','r')
         xt = get(gca, 'XTick');
-        set(gca, 'FontSize', 22)
+        set(gca, 'FontSize', 28)
         title([name, ' on ' , varname],'fontsize',72)
           ylim([min_y_lim(i_var) max_y_lim(i_var)]);
         hold off
@@ -47,7 +45,7 @@ for i_shock=1:nshocks
         
         % Save figures if you want to
         if strcmp(print_figs, 'yes')
-            invoke_export_fig([name, ' on ' , varname], which_ID_strat)
+            invoke_export_fig([name, ' on ' , varname], which_ID_strat,use_current_time)
             close all
             pause(0.5)
         end

### 2017-12-11 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
updated the presentation

@@
 	\item Moran \& Queralto (2017)
+	\item  Guerron \& Jinnai (2014)
 
@@
 \mathbf{X_{t-1}}
-+ \underbrace{\mathbf{AD} \mathbf{_t}}_\text{$\mathbf{i_t}$}
++ \underbrace{\mathbf{AD} \mathbf{s_t}}_\text{$\mathbf{i_t}$}
 \end{equation}
@@
 \begin{equation}
-TFP_t =  \underbrace{\varepsilon_t}_\text{surprise tech shock}  + \underbrace{V_{t-k}}_\text{news shock} + \underbrace{IT_{t-k}}_\text{IT shock}  
+TFP_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{IT_{t-k}}_\text{IT shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
 \end{equation}
@@
 
-	\item Horizon of FEV-maximization: 100 quarters.
+	\item Horizon of FEV-maximization: 60 quarters.
 
@@
 \begin{frame}
-	\frametitle{FEV explained by the two shocks at 40 periods}
+	\frametitle{FEV explained by the two shocks at 60 periods}
 
@@
 \end{large}
+
+\vspace{2cm}
+
+For BS, FEV of news was 45\%.
 

### 2018-01-09 Latex/Meeting_Ryan_10Jan_2018/meeting10Jan2018.tex
some work on counterfactual

--- 2017-11-21 Latex/Meeting_Ryan_22_Nov_2017/meeting22Nov2017.tex
@@
 %\graphicspath{{./Figures/}}
-\def \ourFigPath {../../} % this should move up two steps but it isn't working 
+\def \ourFigPath {../../} % this should move up two steps 
 % . = current directory
@@
 
-\title{Discussion of Results}
+\title{Counterfactuals from SVARs - Questions}
 \author{Marco Brianti\\Laura Gati}
-\date{22 Nov 2017}
+\date{10 Jan 2018}
 
@@
 
-\subsection*{Shares of FEV of TFP}
+\
+
+\section{What we have done so far:}
+\begin{enumerate}
+\item Recovered structural shocks from our identified VAR
+\item Used them together with the impulse responses to generate what Kilian calls ``cumulative contribution of a shock $j$" to TFP.
+These are historical decompositions of TFP in the sense that, relative to the trend of our TFP series, we can see the percent deviations caused by the shocks - together with the responses to them - in our sample.
+Mathematically, the cumulative effect of a shock $j$ on TFP is:
+
+\begin{equation}
+\hat{y}^{j}_{TFP, t} = \sum^{t-1}_{i=0} B(L)^i A s_{j, t-i}
+\end{equation}
+
+where $j = \{IT, news\}$ and $s$ is the structural shock. Then, the overall cumulative effect of all shocks is
+
+\begin{equation}
+\hat{y}_{TFP, t} = \sum_{j= IT,news} \hat{y}^{j}_{TFP, t}
+\end{equation}
+
+\item The object we're interested in is
+\begin{equation}
+TFP - f\big( \hat{y}^{IT}_{TFP, t} \big)
+\end{equation}
+
+and our question is: what is $f$?
 
@@
 
-\textbf{Differenced relative prices (inflation of IT price index over CPI-inflation)}
+In other words: the problem comes from the fact that $\hat{y}^{IT}_{TFP, t}$ is in percentage deviations from the trend of TFP.
+What we're interested in, however, is how TFP would have evolved (in levels) absent the shocks to IT starting in 2000-Q3.
 
-IT: 51.60\%
-
-\noindent News: 19.63\%
-
-\
-
- \textbf{Log level of capital prices (differencing here seems to overdo it)}
-
-IT: 28.47\%
-
-\noindent News: 28.31\%
-
-\newpage
-\subsection*{IRFs - ratio of inflations (i.e relative prices)}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_shock_Ryan_two_stepsID_20-Nov-2017_12_24_34}
-\caption{News shock - ratio of inflations}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_shock_Ryan_two_stepsID_20-Nov-2017_12_24_39}
-\caption{IT shock - ratio of inflations}
-\end{figure}
-
-%%%%%
-\newpage
-\subsection*{IRFs - log level of capital prices}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=0.4]{\ourFigPath Figures/fig_News_Shock_Ryan_two_stepsID_21-Nov-2017_11_35_24}
-\caption{News shock - log level of capital prices}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[scale=0.4]{\ourFigPath Figures/fig_IT_Shock_Ryan_two_stepsID_21-Nov-2017_11_35_27}
-\caption{IT shock - log level of capital prices}
-\end{figure}
-
-\newpage
-\subsection*{Recap and interpretation}
-
-\begin{itemize}
-\item One big motivation for the entire research project is the puzzling decrease in TFP growth, which - as we have also documented - started \emph{before} the Great Recession.
-\item The sudden decrease in IT investment after the burst of the IT bubble around 2000-2002 coincides with this slowdown in TFP growth, which led us to investigate the effect of IT investment on TFP.
-\item We run a structural VAR to estimate the effect of an IT productivity shock on TFP and other main macroeconomic variables.
-\item This identification poses a challenge because we need to confront the view that there is an endogenous channel in the evolution of TFP with the widely accepted view that TFP is driven by news.
-Since both are similar in the way they affect TFP only with lags, we need an additional restriction to disentangle the two.
-\item The additional restriction we use is that news shocks should have no effect on relative IT prices at a certain (long) horizon, because they behave like demand shocks.
-\item [] \textbf{What the results seem to suggest:}
-\item [1)] News and IT shocks together explain more of the FEV of TFP than news does alone in Barsky \& Sims (around 70\% vs approximately 40\% in Barsky \& Sims).
-(Compare with capital prices specification too.)
-\item [2)] News still explains a considerable fraction, but IT shocks explain more. (Compare with capital prices specification too.)
-\item [] $\rightarrow$ we read this as evidence that both news and the endogenous channel via IT investment plays an important role in explaining TFP  over the business cycle and the medium run. 
-\end{itemize}
-
-\subsection*{Comments? Thoughts? Does this make sense to you? Is it presentable in its current form?}
+\end{enumerate}
 

### 2018-01-09 main_file_SVAR_RyansID.m

@@ -11,7 +11,7 @@ tic
 %Data Reading and Transformation
 filename = 'dataset_main';
 sheet    = 'Data';
-range    = 'B1:W286';
+range    = 'B1:W287';
 [data, varnames] = read_data2(filename, sheet, range);
 shocknames = {'News Shock','IT Shock'};
 varnames
@@ -159,4 +159,54 @@ end
 toc
 disp(varnames)
 disp(datestr(now))
+
+% Counterfactual
+s = get_structural_shocks_Forni(A,gam_opt,res);
+
+% Historical decompositions of TFP from the 2 structral shocks
+% IT:
+hd_IT = historical_decomposition(s(:,pos_IT),fake_impact,B, pos_IT, 1);
+% News:
+hd_news = historical_decomposition(s(:,pos_news),fake_impact,B, pos_news, 1);
+% sum of the two:
+hd = hd_IT + hd_news;
+
+% Get counterfactual when shutting off IT shocks 2000-Q3 onward
+IT_bubble = find(time=='01-Jul-2000');
+s_alternative = s;
+s_alternative(IT_bubble:end,3) = 0;
+% Redo counterfactuals for alternative scenario
+% IT:
+hd_IT_alt = historical_decomposition(s_alternative(:,pos_IT),fake_impact,B, pos_IT, 1);
+% News:
+hd_news_alt = historical_decomposition(s_alternative(:,pos_news),fake_impact,B, pos_news, 1);
+% sum of the two:
+hd_alt = hd_IT_alt + hd_news_alt;
+
+
+time = datetime(1989,7,1) + calquarters(0:size(s,1)-1); %ALWAYS CHECK IF THE INITIAL PERIOD IS THE SAME
+
+figure
+plot(time,hd); hold on
+plot(time, hd_alt)
+legend('original', 'alternative')
+title('Hd total')
+
+figure
+plot(time,hd_IT); hold on
+plot(time, hd_IT_alt)
+legend('original', 'alternative')
+title('Hd IT')
+
+figure
+plot(time,hd_IT); hold on
+plot(time, hd_news)
+legend('hd IT', 'hd news')
+title('Hd IT vs Hd news')
+
+figure
+plot(time,hd_IT_alt); hold on
+plot(time, hd_news_alt)
+legend('hd IT', 'hd news')
+title('Hd IT vs Hd news in alternative world')
 

### 2018-01-11 main_file_SVAR_RyansID.m
did the counterfactual figure nicely and created the dissertation workshop presentation
… but the prezzy still needs to be reworked a lot

@@ -163,52 +163,50 @@ disp(datestr(now))
 % Counterfactual
 [s, IR] = get_structural_shocks_Forni(A,gam_opt,res);
 
+which_shock_zero = 3; % set negative realizations of the IT shock to 0
+y0 = data(1,:); % initial values of data
+counterfactuals = counterfactual(s,IR,B,y0,which_shock_zero);
 
-
-% Historical decompositions of TFP from the 2 structral shocks
-% IT:
-hd_IT = historical_decomposition(s(:,pos_IT),fake_impact,B, pos_IT, 1);
-% News:
-hd_news = historical_decomposition(s(:,pos_news),fake_impact,B, pos_news, 1);
-% sum of the two:
-hd = hd_IT + hd_news;
-
-% Get counterfactual when shutting off IT shocks 2000-Q3 onward
-IT_bubble = find(time=='01-Jul-2000');
-s_alternative = s;
-s_alternative(IT_bubble:end,3) = 0;
-% Redo counterfactuals for alternative scenario
-% IT:
-hd_IT_alt = historical_decomposition(s_alternative(:,pos_IT),fake_impact,B, pos_IT, 1);
-% News:
-hd_news_alt = historical_decomposition(s_alternative(:,pos_news),fake_impact,B, pos_news, 1);
-% sum of the two:
-hd_alt = hd_IT_alt + hd_news_alt;
-
-
-time = datetime(1989,7,1) + calquarters(0:size(s,1)-1); %ALWAYS CHECK IF THE INITIAL PERIOD IS THE SAME
+time = datetime(1989,7,1) + calquarters(0:size(s,1)); %ALWAYS CHECK IF THE INITIAL PERIOD IS THE SAME
 
 figure
-plot(time,hd); hold on
-plot(time, hd_alt)
-legend('original', 'alternative')
-title('Hd total')
+set(gcf,'color','w'); % sets white background color
+set(gcf, 'Position', get(0, 'Screensize')); % sets the figure fullscreen (hopefully)
+plot(time, data(:,1), 'b', 'linewidth', 2)
+hold on
+plot(time, counterfactuals(:,1), 'r', 'linewidth', 2)
+legend('Original TFP series', 'Counterfactual TFP','Location','Southeast')
+title('Shutting off negative IT productivity shocks')
+set(gca, 'FontSize', 28)
+grid on
 
-figure
-plot(time,hd_IT); hold on
-plot(time, hd_IT_alt)
[…]

### 2018-01-18 Latex/Dissertation_Workshop_23Jan2018/dw23jan2018.tex
did the counterfactual figure nicely and created the dissertation workshop presentation
… but the prezzy still needs to be reworked a lot
added acemoglu book

--- 2017-12-11 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
@@
 \def \ourFigPath {../../} 
+\def \ourTablePath {../../Tables/}
+
 \setbeamersize{text margin left=5mm,text margin right=12mm} 
@@
 
-\date{December 13, 2017}
+\date{January 23, 2018}
 
@@
 \end{frame}
+
+%%%%%  OLD STUFF
+%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Our starting point: Barsky \& Sims (2011)}
+	\label{BS_quote}
+
+\blockquote{\emph{A more general objection to our empirical approach would be that a number of structural shocks, which are not really ``news'' in the sense defined by the literature, might affect a measure of TFP in the future without impacting it immediately.
+Among these shocks might be research and development shocks, investment specific shocks, and reallocative shocks.
+Our identification (and any other existing VAR identifications) would obviously confound any true news shock with these shocks.}}
+
+\
+
+\hspace{5cm} Barsky \& Sims (2011), p. 278.
+
+\
+
+\
+
+\
+
+\hyperlink{related_lit}{\beamerreturnbutton{Return}}	
+\hyperlink{BS_FEV}{\beamerbutton{Barsky \& Sims' FEV-table}}	
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{What we do}
+
+\begin{itemize}
+\item We pick a particular shock out of this class of news-resembling shocks
+
+\
+
+\item We lay out a simple model of the role of this shock in explaining TFP fluctuations
+
+\
+
+\item Main analysis: Using a structural VAR, we test empirically for the contribution of this shock to TFP fluctuations against that of a classical news shock
+\end{itemize}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Theoretical model}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Theoretical model}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Theoretical model}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Theoretical model}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
 
@@
 \begin{frame}
-	\frametitle{Barsky \& Sims say:}
-	\label{BS_quote}
-
-\blockquote{\emph{A more general objection to our empirical approach would be that a number of structural shocks, which are not really ``news'' in the sense defined by the literature, might affect a measure of TFP in the future without impacting it immediately.
-Among these shocks might be research and development shocks, investment specific shocks, and reallocative shocks.
-Our identification (and any other existing VAR identifications) would obviously confound any true news shock with these shocks.}}
-
-\
-
-\hspace{5cm} Barsky \& Sims (2011), p. 278.
-
-\
-
-\
-
-\
-
-\hyperlink{related_lit}{\beamerreturnbutton{Return}}	
-\hyperlink{BS_FEV}{\beamerbutton{Barsky \& Sims' FEV-table}}	
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
 	\frametitle{Barsky \& Sims FEV of TFP explained}
@@
 \centering
-\includegraphics[scale=0.3]{fig_BS_fevtable}
+\includegraphics[scale=0.3]{\ourTablePath fig_BS_fevtable}
 \end{figure}

### 2018-01-19 Latex/Dissertation_Workshop_23Jan2018/dw23jan2018.tex
dissertation workshop presentation and a workspace with nsimul =500 and right TFP magnitude, as well as new figs

--- 2017-12-11 Latex/MacroLunch_Dec2017/macrolunch_dec2017.tex
@@
 \begin{frame}
-	\frametitle{A very big question}
+	\frametitle{Motivation}
 
-Broad consensus on secular stagnation.
+	\begin{itemize}
+	\item The neoclassical tradition (RBC literature) in macro has treated total factor productivity (TFP) as exogenous.
+
+	(King \& Rebelo 1999, Christiano, Eichenbaum \& Trabandt 2014, 2018)
 
@@
 
-The literature has agreed that there are two main factors driving this:
-\begin{itemize}
-\item decreasing labor force participation
-\item decreasing TFP growth
+	\item The Great Recession 2008 revived interest in endogenous components in TFP for explaining long-run TFP fluctuations.
+
+	\
+
+	\item[] $\rightarrow$ We explore the possibility that general-purpose technologies (GPT), in particular for the last 30 years information technologies (IT), play a role in explaining TFP fluctuations at long horizons.
+
+	\
+
 	\end{itemize}
@@
 \begin{frame}
-	\frametitle{A smaller, but still big question}
+	\frametitle{Motivation II}
 
-	Why has TFP slowed down?
+	\begin{itemize}
+	\item Our main analysis is estimating a structural VAR in which we identify a shock to the exogenous component of future TFP (a news shock) and a shock to the endogenous component of TFP (a shock to IT productivity, hereafter ``IT shock").
 
@@
 
-	\vspace{-1cm}
-	\noindent
-	\begin{figure}
-		\centering
-		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_TFP_macrolunch_29-Nov-2017_17_41_17}
-	\end{figure}
+	\
+
+	\item Along the way, we provide a solution to an econometric challenge in the literature on long-run productivity.
+
+	\end{itemize}
 
@@
 \begin{frame}
-	\frametitle{Two possible mechanisms}
+	\frametitle{Our starting point: Barsky \& Sims (2011)}
+	\label{BS_quote}
 
-\begin{itemize}
-\item a permanent, or very persistent exogenous shock to TFP
+BS identify news shocks as shocks that maximize future fluctuations in TFP. But they warn:
 
@@
 
-\item an endogenous mechanism
-\end{itemize}
+\blockquote{\emph{A more general objection to our empirical approach would be that a number of structural shocks, which are not really ``news'' in the sense defined by the literature, might affect a measure of TFP in the future without impacting it immediately.
+Among these shocks might be research and development shocks, investment specific shocks, and reallocative shocks.
+Our identification (and any other existing VAR identifications) would obviously confound any true news shock with these shocks.}}
 
@@
 
+\hspace{5cm} Barsky \& Sims (2011), p. 278.
+
 \
 
-$\rightarrow$ What we do in a nutshell: test for the endogenous mechanism (main analysis will be a SVAR)
+$\rightarrow$ We focus on a specific subset of shocks which are ``not really `news''': shocks to the productivity of the sector that produces IT goods.
 
+%\hyperlink{BS_FEV}{\beamerbutton{Barsky \& Sims' FEV-table}}	
 \end{frame}
@@
 \item [] \textbf{Our contribution: allow in this setting the existence of an endogenous mechanism that affects future TFP}
-
-\hyperlink{BS_quote}{\beamergotobutton{Barsky \& Sims quote}}
 
@@
 \begin{frame}
-	\frametitle{Why more convincing?}
-	\label{convincing}
+	\frametitle{A toy model}
 
-	Because the endogenous TFP literature faces a big problem: The endogenous mechanism is rationalized entirely using R\&D investment.
+	How should we think of this IT productivity shock?
 
@@
 
-\begin{enumerate}
-\item  But R\&D in the data is almost acyclical.... $\rightarrow$ hard to rationalize as a driver of business cycle fluctuations % hyperlink to graph: growth rate of RD vs. growth rate of TFP and GDP
+	\
 
@@
 
-\item Timing issue: the TFP slowdown begins around 2006, i.e.
-\emph{before} the Great Recession and thus \emph{before} the marked drop in R\&D  % hyperlink to graph: level of RD and TFP, so we see that TFP drops in 2006, while RD only during the recession.
-\hyperlink{timing}{\beamergotobutton{Graph of R\&D}}
+	Contextualize using a simple expanding variety model (Romer 1990)
 
-\end{enumerate}
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Expanding variety model}
+	\label{expanding_variety}
+
+Final good $Y_t$ is the CES aggregate of a number $A_t$ intermediate goods $Y_t^M(s)$:	% theta is between 0 and infinity
+	\begin{equation}
+	Y_t = \Big[ \int_{0}^{A_t} Y_t^M(s)^{\frac{\theta-1}{\theta} } ds \Big]^{\frac{\theta}{\theta-1}}
+	\end{equation}
+
+\pause
+
+Intermediate good $s$ is Cobb-Douglas with exogenous TFP $\Psi_t$:
+\begin{equation}
+Y_t(s) = \Psi_t K_t(s)^{\alpha}L_t(s)^{1-\alpha}
+\end{equation}
+
+\pause
+
+$\rightarrow$ letting $K_t$ and $L_t$ be aggregate capital and labor, final output is:
+\begin{equation}
+Y_t = A_t^{\frac{1}{\theta-1}} \Psi_t K_t^{\alpha}L_t^{1-\alpha}
+\end{equation}
+
+\pause
+
+The IT sector is a separate sector that uses IT investment $S_{i,t}$ to expand $A_t$.
+Importantly, we assume that the IT sector is also augmented by $\Psi_t$, as well as by the sector-specific productivity $\lambda_t$.
+
+\begin{equation}
+V_{i,t} = \lambda_t \Psi_t f(S_{i,t}) 
+\end{equation}
+
+\hyperlink{it_sector}{\beamergotobutton{IT sector in detail}}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{The shocks}
+
+\begin{equation*}
+Y_t \; = \underbrace{A_t^{\frac{1}{\theta-1}}}_\text{endogenous TFP} \; \; \underbrace{\Psi_t}_\text{exogenous TFP} \; K_t^{\alpha}L_t^{1-\alpha}
+\end{equation*}
 
@@
 
-$\Rightarrow$ Following the suggestion of Fernald, Hall, Stock \& Watson (2009), we propose to use investment in information technology (IT)  % hyperlink to our own graph motivation.pdf: the top graph.
-\hyperlink{it_investment}{\beamergotobutton{Graph of IT investment}}
+\
+
+$\hookrightarrow$ A news shock is $\Psi_{t+k} \uparrow$ for some $k>0$
+
+\
+
+$\hookrightarrow$ An IT productivity shock is $\lambda_t \uparrow$, which shows up in $A_{t+j} \uparrow$ with a lag $j>0$
+
+\
+
+Crucially, both lead to an increase in future TFP, with no effect on impact.
+
+\
+
+ $\rightarrow$ to a Barsky \& Sims-type identification, the two shocks are observationally equivalent!
+
+ $\Rightarrow$ econometric challenge is to disentangle the two!
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Identification: relative prices}
+
+The price level $P$ is an aggregate of the prices intermediate goods. These are determined as an FOC to 
+\begin{equation*}
+Y_t(s) = \Psi_t K_t(s)^{\alpha}L_t(s)^{1-\alpha}
+\end{equation*}
+
+\hspace{5cm} $\hookrightarrow P$ is a function of $\Psi_t$
+
+\
+
+The price of IT good, $P^{IT}$, is determined as an FOC to
+
+\begin{equation}
+V_{i,t} = \lambda_t \Psi_t f(S_{i,t})
+\end{equation}
+
+\hspace{5cm}  $\hookrightarrow P^{IT}$ is a function of $\Psi_t$ \textbf{and} $\lambda_t$
+
+\
+
+$\Rightarrow$ The two shocks imply different responses of relative prices $\frac{P^{IT}}{P}$!
+
+\begin{itemize}
+\item A news shock moves both $P$ and $P^{IT}$, leaving relative prices unchanged.
+\item An IT productivity shock moves only $P^{IT}$, thus changing relative prices.
+\end{itemize}
 
@@
 \item All variables are real (except price indexes) and in log levels (except for RP, which is in growth rates). 
-\item The dataset ranges from 1989:q1 - 2017:q1.
+\item The dataset ranges from 1989:q1 - 2017:q2.
 \end{itemize}
@@
 
-$D$ will be a tool to impose our identification assumptions \hyperlink{Technicalities}{\beamergotobutton{Technicalities}}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-\frametitle{Identified shocks}
-
-\begin{itemize}
-	\item We impose restrictions on $D$ in order to identify two shocks:
-	\begin{enumerate}
-		\item News Shock
-		\item IT Productivity Shock
-	\end{enumerate}
-
-\
-
-	\item Econometric challenge is to disentangle two shocks with very similar features 
-		\begin{enumerate}
-		\item No impact effect on TFP
-		\item Persistent positive effect over time on TFP
-		\item Most likely both shocks have positive impact effects on forward-looking variables
-	\end{enumerate}
-
-\
-
-	\item Barsky \& Sims' identification strategy is not sufficient to disentangle the two
-	\begin{itemize}
-		\item We need a further assumption (restriction) to find a dimension of difference between the shocks
-	\end{itemize}
-\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-\frametitle{Additional restriction}
-
-\begin{itemize}
-	\item We rely on simple demand and supply theory
-
-	\
-
-	\begin{enumerate}
-		\item The IT shock is a \emph{sectoral} shock $\rightarrow$ we expect it to move relative prices
-		\item The news shock is \emph{not} a sectoral shock $\rightarrow$ we have no a priori sense of what it should do to relative prices on impact, but after some time relative prices should go back to their initial value
-	\end{enumerate}
-
-	\
-
-\end{itemize}
-
-	$\rightarrow$ add the restriction that a news shock should have no effect on relative prices after a reasonable time
-
-\hspace{4cm} $\hookrightarrow$ enough for prices to adjust, so
-
-\hspace{4cm}   between 6-12 quarters
+We impose our identifying assumptions on the matrix $D$. \hyperlink{Technicalities}{\beamergotobutton{Technicalities}}
 
@@
 \begin{equation}
-TFP_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{IT_{t-k}}_\text{IT shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
+\epsilon^{TFP}_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{IT_{t-k}}_\text{IT productivity shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
 \end{equation}
@@
     \begin{enumerate}
-    	\item The news shock $V_{t-k}$ maximizes the FEV of future TFP subject to the restriction that it has no effect on the relative price $RP$ at a small number of quarters;
+    	\item The news shock $V_{t-k}$ maximizes the FEV of future TFP subject to the restriction that it has no effect on the relative price $RP$ at a small number of quarters (enough for prices to adjust, so 6-12);
 
@@
 	\begin{itemize}
-	\item Recall: dataset is quarterly and covers 1989:q1-2017-q1.
+	\item Recall: dataset is quarterly and covers 1989:q1-2017-q2.
 
@@
 	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_TFP__}
+	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_TFP__} % REGENERATE TFP SHOCKS FIGURES WITH RIGHT SCALES!!
 \end{figure}
@@
 	\begin{itemize}
-	\item both the Barsky \& Sims result ...
+	\item both the Barsky \& Sims result;
 
@@
 
-	\item ... as well as the the conjecture that the IT shock looks similar to news along certain dimensions,
+	\item as well as the the conjecture that the IT shock looks similar to news along certain dimensions;
 
@@
 
-	\item ... but relative prices do indeed introduce a margin of difference between the two shocks.
+	\item but relative prices do indeed introduce a margin of difference between the two shocks.
 	\end{itemize}
@@
 	\begin{itemize}
-	\item ... are also in line with the Barsky \& Sims result ...
-	\item [] For BS, news explains around 45\%, compared to 20\% here
+	\item are also in line with the Barsky \& Sims result;
+	\item [] (for BS, news explains around 45\%, compared to 20\% here)
 
@@
 
-	\item ... yet suggest that the IT shock plays an important role as well (around 52\%)
+	\item  yet suggest that the IT shock plays an important role as well (around 52\%).
 
@@
 
-	\item ... and indeed the IT shock \emph{complements} the news shock, instead of substituting for it
-	\item [] For BS, the single identified shock explains around 45\%, while our two identified shocks explain around 73\%
+	\item And indeed the IT shock \emph{complements} the news shock, instead of substituting for it.
+	\item [] For BS, the single identified shock explains around 45\%, while our two identified shocks explain around 73\%.
 	\end{itemize}
@@
 \begin{frame}
+	\frametitle{A counterfactual}
+
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_counterfactual_}
+	\end{figure}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
 	\frametitle{Conclusion}
@@
 \begin{itemize}
-\item Provided what we think (and we hope you do too) a careful and more general test for the endogenous mechanism in TFP.
-\begin{itemize}
-\item While the literature focuses exclusively on R\&D, we show that IT is a better variable to focus on.
-\end{itemize}
+\item Provided a test for the role of IT as an example of GPTs in explaining fluctuations in long-run TFP, and in doing so, overcame an econometric challenge prevalent in the literature on long-run productivity.
 
@@
 
-\item The results show that by controlling for the presence of news shocks, the endogenous component of TFP is an important driver of TFP fluctuations at long horizons.
+\item The results show that by controlling for the presence of news shocks, IT productivity shocks are important drivers of TFP fluctuations at long horizons.
 
@@
 \item This result does not contrast however with the findings of the news shock literature since we still find that news also play a significant role in explaining TFP.
+
+\
+
+\item Moreover, IT productivity shocks can be thought of as giving more microfoundations to what classical news shocks carry information on.
 
@@
 \begin{itemize}
-\item Rationalize this setting using a theoretical model
-\item [] $\hookrightarrow$ what we have in mind: an endogenous TFP model (in the vein of Comin \& Gertler) augmented with news shocks
+
+\item Technically, should do a VECM due to cointegration and wanting to have variables in the VAR as growth rates rather than levels...
 
@@
 
-\item Estimate the model (IR-matching)
+\item Dig deeper: IT is just an example of GPTs for the last 30 years
+\item[] $\hookrightarrow$ could redo analysis for different time periods with different GPTs (electricity in 1920s, airplane industry in 1960s ...)
 
@@
 
-\item Perform a counterfactual for the Great Recession \emph{and} the period prior, shutting down the negative IT shocks around 2000
-% assuming the IT bubble, i.e. the negative shock to IT productivity around 2000, did not happen.
+\item Use a fully structural model to see if we can find interesting interactions between the two shocks?
+\item [] $\hookrightarrow$ In particular, we're thinking of noise shocks on IT productivity
 
@@
 
-\item See if we can find interesting interactions between the two shocks?
-\item [] $\hookrightarrow$ In particular, we're thinking of noise shocks on IT productivity
-	\begin{itemize}
-	\item [] news shock: shock to expected future value
-	\item [] noise shock: shock to expected current value (``perceptions'')
-	\end{itemize}
+\item But there are also other shocks that are similar to news shocks and yet not news shocks in the Barsky \& Sims sense: reallocative shocks, shocks to inventories, etc...  
 \end{itemize}
@@
 \begin{frame}
-	\frametitle{Barsky \& Sims say:}
-	\label{BS_quote}
+	\frametitle{The current TFP slowdown}
 
-\blockquote{\emph{A more general objection to our empirical approach would be that a number of structural shocks, which are not really ``news'' in the sense defined by the literature, might affect a measure of TFP in the future without impacting it immediately.
-Among these shocks might be research and development shocks, investment specific shocks, and reallocative shocks.
-Our identification (and any other existing VAR identifications) would obviously confound any true news shock with these shocks.}}
+	\vspace{-1cm}
+	\noindent
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_TFP_macrolunch_29-Nov-2017_17_41_17}
+	\end{figure}
 
-\
-
-\hspace{5cm} Barsky \& Sims (2011), p. 278.
-
-\
-
-\
-
-\
-
-\hyperlink{related_lit}{\beamerreturnbutton{Return}}	
-\hyperlink{BS_FEV}{\beamerbutton{Barsky \& Sims' FEV-table}}	
 \end{frame}
@@
 \hyperlink{related_lit}{\beamerreturnbutton{Return}}	
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Production of IT goods}
+	\label{it_sector}
+
+Production function for IT goods:
+
+\begin{equation}
+V_{i,t} = \lambda_t \Psi_t f(S_{i,t}) 
+\end{equation}
+where $S_{i,t}$ is investment by producer $i$ in IT goods and $\lambda$ is the productivity of the IT sector.
+
+\
+
+The IT producer's problem is to max discounted profits $J_{i,t+1}$
+
+\begin{equation}
+\max_{S_{i,t}} \; \mathbb{E}(\Lambda_{t,t+1},J_{i,t+1})\lambda_t \Psi_t f(S_{i,t}) - P^{IT}_t S_{i,t}
+\end{equation}
+
+\
+FOC:
+
+\begin{equation}
+P^{IT}_t = \mathbb{E}(\Lambda_{t,t+1},J_{i,t+1})\lambda \Psi_t f_1
+\end{equation}
+
+\hyperlink{expanding_variety}{\beamerreturnbutton{Return}}	
 \end{frame}

### 2018-01-21 Latex/Dissertation_Workshop_23Jan2018/dw23jan2018.tex
update of presentation

@@
 
-\title{The Slowdown of TFP \\ Exogenous and Endogenous Mechanisms}
+\title{IT Spillovers in Long-Run TFP \\ A SVAR Approach}
 
@@
 	\begin{itemize}
-	\item The neoclassical tradition (RBC literature) in macro has treated total factor productivity (TFP) as exogenous.
+	\item The neoclassical tradition (RBC literature) in macro has treated total factor productivity (TFP) as exogenous, working against endogenous growth models
 
-	(King \& Rebelo 1999, Christiano, Eichenbaum \& Trabandt 2014, 2018)
+	(King \& Rebelo 1999, Christiano, Eichenbaum \& Trabandt 2014, 2018, vs. e.g. Romer 1990)
 
@@
 
-The IT sector is a separate sector that uses IT investment $S_{i,t}$ to expand $A_t$.
-Importantly, we assume that the IT sector is also augmented by $\Psi_t$, as well as by the sector-specific productivity $\lambda_t$.
+IT sector is a separate sector that uses IT investment and its own sectoral productivity $\lambda_t$ to expand $A_t$.  \hyperlink{it_sector}{\beamergotobutton{IT sector in detail}}
 
-\begin{equation}
-V_{i,t} = \lambda_t \Psi_t f(S_{i,t}) 
-\end{equation}
-
-\hyperlink{it_sector}{\beamergotobutton{IT sector in detail}}
+$\rightarrow$ IT sector is driven by profits from selling the IT good, but its advances spill over to aggregate TFP.
 
@@
 
-The price level $P$ is an aggregate of the prices intermediate goods. These are determined as an FOC to 
-\begin{equation*}
-Y_t(s) = \Psi_t K_t(s)^{\alpha}L_t(s)^{1-\alpha}
-\end{equation*}
-
-\hspace{5cm} $\hookrightarrow P$ is a function of $\Psi_t$
+Let $P$ be the price level (price of final good), $P^{IT}$ the price of the IT good and relative prices be $P^{IT}/P$.
 
@@
 
-The price of IT good, $P^{IT}$, is determined as an FOC to
-
-\begin{equation}
-V_{i,t} = \lambda_t \Psi_t f(S_{i,t})
-\end{equation}
-
-\hspace{5cm}  $\hookrightarrow P^{IT}$ is a function of $\Psi_t$ \textbf{and} $\lambda_t$
+Intuition:
+\begin{itemize}
+\item News shock makes all sectors of the economy more productive $\rightarrow$ impacts the sectoral price $P^IT$ as well as P $\Rightarrow$ relative prices do not move.
+\item IT productivity shock makes only the IT sector more productive $\rightarrow$ impacts the sectoral price $P^{IT}$ \textbf{only} $\Rightarrow$ relative prices move! 
+\end{itemize}
 
@@
 
-$\Rightarrow$ The two shocks imply different responses of relative prices $\frac{P^{IT}}{P}$!
+$\Rightarrow$ identifying restriction: news shock does not move relative prices.
+\newline Accounting for price rigidities: news shock does not move relative prices after price adjustment has taken place (6-12 quarters).
 
-\begin{itemize}
-\item A news shock moves both $P$ and $P^{IT}$, leaving relative prices unchanged.
-\item An IT productivity shock moves only $P^{IT}$, thus changing relative prices.
-\end{itemize}
+\
+
+Similar identification scheme: Fisher 2006.
+
+%The price level $P$ is an aggregate of the prices intermediate goods. These are determined as an FOC to 
+%\begin{equation*}
+%Y_t(s) = \Psi_t K_t(s)^{\alpha}L_t(s)^{1-\alpha}
+%\end{equation*}
+%
+%\hspace{5cm} $\hookrightarrow P$ is a function of $\Psi_t$ 
+%
+%\
+%
+%The price of IT good, $P^{IT}$, is determined as an FOC to
+%
+%\begin{equation}
+%V_{i,t} = \lambda_t \Psi_t f(S_{i,t})
+%\end{equation}
+%
+%
+%\hspace{5cm}  $\hookrightarrow P^{IT}$ is a function of $\Psi_t$ \textbf{and} $\lambda_t$	
+%
+%\
+%
+%$\Rightarrow$ The two shocks imply different responses of relative prices $\frac{P^{IT}}{P}$!
+%
+%\begin{itemize}
+%\item A news shock moves both $P$ and $P^{IT}$, leaving relative prices unchanged.
+%\item An IT productivity shock moves only $P^{IT}$, thus changing relative prices.
+%\end{itemize}
 
@@
 
+Innovation in TFP at time $t$ can be decomposed as:
+
 \begin{equation}
-\epsilon^{TFP}_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{IT_{t-k}}_\text{IT productivity shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
+\epsilon^{TFP}_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{f(IT_{t-j})}_\text{IT productivity shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
 \end{equation}
@@
 
-    \item The IT shock maximizes the remaining FEV of future TFP;
+    \item The IT productivity shock maximizes the remaining FEV of future TFP;
 
@@
 
+\item Show the identification assumption in the structural model.
+
+\
+
 \item Technically, should do a VECM due to cointegration and wanting to have variables in the VAR as growth rates rather than levels...

### 2018-01-30 Latex/Basu_propositions/propositions.tex
basu presentation and some literature note-taking

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{float}
\usepackage{csquotes}
\usepackage{sansmathaccent}
\usepackage{subfigure}
\usepackage{multicol}
\pdfmapfile{+sansmathaccent.map}
\def \ourFigPath {../../} 
\def \ourTablePath {../../Tables/}

\setbeamersize{text margin left=5mm,text margin right=12mm} 
%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\numberset}{\mathbb}
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\N}{\numberset{N}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\virgolette}[1]{``#1''}
%

\author[Brianti, Gati]{Marco Brianti and Laura Gati}

\institute[Boston College]{Boston College}

\title{3 slides to convince you that it's endogenous TFP}

\date{\today}

\usetheme{Warsaw}

\begin{document}

\begin{frame}

\maketitle

\end{frame}

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{A two-sector model}

Final goods firm (GE)
\begin{align*}
\max_{K^f_t(s), L^f_t(s), K^{IT}_t(s) } Y_t(s) =  & K^f_t(s)^{\alpha}L^f_t(s)^{\beta}K^{IT}_t(s)^{1-\alpha - \beta}A_t \\
 & - w_t L_t(s) -R_tK^f_t(s) -P^{IT}_t I^{IT}_t(s) \\
 & \text{where} \; K^{IT}_t(s) =  (1-\delta^{IT})K^{IT}_{t-1} + I^{IT}_t \\
 & \text{and} \; A_t =  S_t \Psi_t (K^{IT}_t)^{\gamma}
\end{align*}

IT-producing firm (Google)
\begin{align*}
\max_{K^{I}_t(s), L^{I}_t(s)} I^{IT}_t(s) = P^{IT}_t S_t \lambda_t F(K^I_t(s), L^I_t(s)) -w_t L^I_t(s) - R_t K^I_t(s)
\end{align*}

\

A news shock is $S_{t+k} \uparrow$ for some positive $k$.

An IT productivity shock is $\lambda_{t+j}$ for some positive $j$.

$\Psi$ is a final-good-specific exogenous technology process.

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{Proposition 1 - the Solow-residual in this model}

\begin{align*}
\frac{\dot{A}}{A} = & \frac{\dot{Y}}{Y} - \alpha \frac{\dot{K^f}}{K^f} - \beta \frac{\dot{L^f}}{L^f} - (1-\alpha - \beta) \frac{\dot{K^{IT}}}{K^{IT}} \\
= & \frac{\dot{S}}{S} + \frac{\dot{\Psi}}{\Psi} + \gamma \frac{\dot{K^{IT}}}{K^{IT}}
\end{align*}

TFP consists of an exogenous, common technology process $S$, a final-good-specific exogenous technology process $\Psi$ and an endogenous component coming as a spillover from the aggregate stock of IT technology. 
\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{Proposition 2 - when a news shock leaves relative prices constant}

Since the rate of return on the input factors have to equal in the two sectors, we can set the FOCs from GE and Google equal. Let's do this for capital:

\begin{align*}
R_t = & \alpha \frac{Y_t(s)}{K^f_t(s)} P^C_t = S_t \lambda_t F_k P^{IT}_t \\
\Leftrightarrow \frac{P^{IT}_t }{P^{C}_t } = & \alpha \frac{K^f_t(s)^{\alpha}L^f_t(s)^{\beta}K^{IT}_t(s)^{1-\alpha - \beta}S_t \Psi_t (K^{IT}_t)^{\gamma} }{K^f_t(s)} \frac{1}{S_t \lambda_t F_k}
\end{align*}

A news shock doesn't move relative prices if 
\begin{itemize}
\item No other exogenous shock hits the economy ($\Psi_t$ and $\lambda_t$ do not move);
\item the news shock doesn't change the relative marginal productivities of the two inputs in the two sectors, so that labor and capital are not reallocated from one sector to another.
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%

\end{document}

### 2018-01-30 Latex/Dissertation_Workshop_23Jan2018/dw23jan2018.tex
basu presentation and some literature note-taking

@@
 \begin{frame}
+	\frametitle{VARs - A quick recap}
+	\label{identification}
+
+Structural Form	
+\begin{equation}
+(\mathbf{AD})^{-1}
+    \mathbf{X_{t}}
+= \mathbf{C(L)} 
+\mathbf{X_{t-1}}
++ \mathbf{s_t}
+\end{equation}
+
+\
+
+\
+
+Reduced Form
+\begin{equation}
+\mathbf{X_{t}}
+= \underbrace{\mathbf{AD} \mathbf{C(L)}}_\text{$\mathbf{B(L)}$} 
+\mathbf{X_{t-1}}
++ \underbrace{\mathbf{AD} \mathbf{s_t}}_\text{$\mathbf{i_t}$}
+\end{equation}
+
+\
+
+\
+
+\begin{itemize}
+	\item $AD$ is the impact matrix
+	\item $A$ is s.t. $As_t s_t' A' = i_t i_t' = \Sigma$ and $s_t s_t' = I$
+	\item $D$ is a rotation matrix s.t. $DD' = I$ $\Rightarrow$ $AD(AD)' = \Sigma$
+\end{itemize}
+
+We impose our identifying assumptions on the matrix $D$. \hyperlink{Technicalities}{\beamergotobutton{Technicalities}}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
 	\frametitle{Our starting point: Barsky \& Sims (2011)}
@@
 \begin{equation}
-Y_t(s) = \Psi_t K_t(s)^{\alpha}L_t(s)^{1-\alpha}
+Y^M_t(s) = \Psi_t K_t(s)^{\alpha}L_t(s)^{1-\alpha}
 \end{equation}
@@
 
+So in this model, the innovation to TFP at period $t$ is:
+\begin{equation}
+\epsilon^{TFP}_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{f(IT_{t-j})}_\text{IT productivity shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
+\end{equation}
+
 Crucially, both lead to an increase in future TFP, with no effect on impact.
-
-\
-
- $\rightarrow$ to a Barsky \& Sims-type identification, the two shocks are observationally equivalent!
-
- $\Rightarrow$ econometric challenge is to disentangle the two!
 
@@
 \begin{itemize}
-\item News shock makes all sectors of the economy more productive $\rightarrow$ impacts the sectoral price $P^IT$ as well as P $\Rightarrow$ relative prices do not move.
+\item News shock makes all sectors of the economy more productive $\rightarrow$ impacts the sectoral price $P^{IT}$ as well as P $\Rightarrow$ relative prices do not move.
 \item IT productivity shock makes only the IT sector more productive $\rightarrow$ impacts the sectoral price $P^{IT}$ \textbf{only} $\Rightarrow$ relative prices move! 
@@
 \begin{frame}
+	\frametitle{Identification strategy overall}
+
+Recall that the innovation in TFP at time $t$ is:
+
+\begin{equation*}
+\epsilon^{TFP}_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{f(IT_{t-j})}_\text{IT productivity shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
+\end{equation*}
+
+\
+
+    \begin{enumerate}
+    	\item The news shock $V_{t-k}$ maximizes the FEV of future TFP, with a zero impact effect, subject to the restriction that it has no effect on the relative price $RP$ at a small number of quarters;
+
+	\
+
+    \item The IT productivity shock maximizes the remaining FEV of future TFP, with a zero impact effect;
+
+    \
+
+    \item The tech shock $\varepsilon_t$ is considered as a residual shock and is left unrestricted (unidentified).
+   \end{enumerate}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
 	\frametitle{Empirical analysis}
@@
 \end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{From reduced form to structural form}
-	\label{identification}
-
-Structural Form	
-\begin{equation}
-(\mathbf{AD})^{-1}
-    \mathbf{X_{t}}
-= \mathbf{C(L)} 
-\mathbf{X_{t-1}}
-+ \mathbf{s_t}
-\end{equation}
-
-\
-
-\
-
-Reduced Form
-\begin{equation}
-\mathbf{X_{t}}
-= \underbrace{\mathbf{AD} \mathbf{C(L)}}_\text{$\mathbf{B(L)}$} 
-\mathbf{X_{t-1}}
-+ \underbrace{\mathbf{AD} \mathbf{s_t}}_\text{$\mathbf{i_t}$}
-\end{equation}
-
-\
-
-\
-
-\begin{itemize}
-	\item $AD$ is the impact matrix
-	\item $A$ is s.t. $As_t s_t' A' = i_t i_t' = \Sigma$ and $s_t s_t' = I$
-	\item $D$ is a rotation matrix s.t. $DD' = I$ $\Rightarrow$ $AD(AD)' = \Sigma$
-\end{itemize}
-
-We impose our identifying assumptions on the matrix $D$. \hyperlink{Technicalities}{\beamergotobutton{Technicalities}}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Identification strategy overall}
-
-Innovation in TFP at time $t$ can be decomposed as:
-
-\begin{equation}
-\epsilon^{TFP}_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{f(IT_{t-j})}_\text{IT productivity shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
-\end{equation}
-
-\
-
-    \begin{enumerate}
-    	\item The news shock $V_{t-k}$ maximizes the FEV of future TFP subject to the restriction that it has no effect on the relative price $RP$ at a small number of quarters (enough for prices to adjust, so 6-12);
-
-	\
-
-    \item The IT productivity shock maximizes the remaining FEV of future TFP;
-
-    \
-
-    \item The tech shock $\varepsilon_t$ is considered as a residual shock and is left unrestricted (unidentified).
-   \end{enumerate}
 
@@
 	\item Replace IT prices with capital prices (following Comin \& Gertler)
+
+	\
+
+	\item Replace CPI inflation with PCE inflation
 	\end{itemize}

### 2018-01-31 Latex/Basu_propositions/propositions.tex
edited Basu presentation to include empirical evidence

@@
 
-An IT productivity shock is $\lambda_{t+j}$ for some positive $j$.
+An IT productivity shock is $\lambda_{t} \uparrow$, i.e. an increase in IT productivity today.
 
@@
 \begin{itemize}
-\item No other exogenous shock hits the economy ($\Psi_t$ and $\lambda_t$ do not move);
 \item the news shock doesn't change the relative marginal productivities of the two inputs in the two sectors, so that labor and capital are not reallocated from one sector to another.
@@
 
+%%%%%%% Slide %%%%%%
+\begin{frame}
+\frametitle{+1 slide: evidence that $\gamma \neq 0$, i.e. that GPTs show up as spillovers}
+
+Theoretical evidence
+\begin{itemize}
+\item Brynjolfsson, e.g. in Bloom et al. (2014): theory of IT as a GPT changing management practices.
+\item Mokyr (1990):  an economic history account of how GPTs (electricity, computers) change the organization of production as a whole, so it's not just the firm's individual use of them that matters, but that of the economy as a whole.
+\item Romer (1986): a production function with spillovers from human capital.
+\end{itemize}
+
+Empirical evidence
+\begin{itemize}
+\item Stiroh (2002 AER): industry-level data show that productivity gains from IT are not confined to industries producing IT.
+\item Oliner \& Sichel (2000 JEP): growth accounting.
+\item Black \& Lynch (2004, EJ), Doms, Dunn \& Troske (1997 QJE): plant-level data.
+\end{itemize}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2018-01-31 Latex/Basu_propositions/propositions.tex
updated Basu presentation
another little change to Basu presentation

@@
  & - w_t L_t(s) -R_tK^f_t(s) -P^{IT}_t I^{IT}_t(s) \\
- & \text{where} \; K^{IT}_t(s) =  (1-\delta^{IT})K^{IT}_{t-1} + I^{IT}_t \\
- & \text{and} \; A_t =  S_t \Psi_t (K^{IT}_t)^{\gamma}
+ & \text{s.t.} \; K^{IT}_t(s) =  (1-\delta^{IT})K^{IT}_{t-1} + I^{IT}_t \\
+ & \text{but not internalizing} \; A_t =  S_t \Psi_t (K^{IT}_t)^{\gamma}
 \end{align*}
@@
 
-$\Psi$ is a final-good-specific exogenous technology process.
+$\Psi$ is a final-good-specific exogenous deterministic technology process.
 

### 2018-02-01 Latex/Basu_propositions/propositions.tex
Rolling averagen in basu's Presentation

--- 2018-01-31 Latex/Basu_propositions/propositions.tex
@@
  & \text{where} \; K^{IT}_t(s) =  (1-\delta^{IT})K^{IT}_{t-1} + I^{IT}_t \\
- & \text{and} \; A_t =  S_t \Psi_t (K^{IT}_t)^{\gamma}
+ &  \; A_t =  S_t \Psi_t (G(K^{IT}_t,K^{IT}_{t-1},\dots))^{\gamma} \\
+ &  \; G(K^{IT}_t,K^{IT}_{t-1},\dots) = \zeta_1 K_t^{IT} + \zeta_2 K^{IT}_{t-1} + \dots \\
+  & \text{and} \; \sum_{i=1}^{N} \zeta_i = 1
 \end{align*}
+
+\end{frame}
+
+\begin{frame}
 

### 2018-02-01 Latex/Basu_propositions/propositions.tex
updated basu slides
updated basu presentation with new notation

--- 2018-01-31 Latex/Basu_propositions/propositions.tex
@@
 
-\title{3 slides to convince you that it's endogenous TFP}
+\title{5 slides to convince you that it's endogenous TFP}
 
@@
 \begin{align*}
-\max_{K^f_t(s), L^f_t(s), K^{IT}_t(s) } Y_t(s) =  & K^f_t(s)^{\alpha}L^f_t(s)^{\beta}K^{IT}_t(s)^{1-\alpha - \beta}A_t \\
- & - w_t L_t(s) -R_tK^f_t(s) -P^{IT}_t I^{IT}_t(s) \\
- & \text{where} \; K^{IT}_t(s) =  (1-\delta^{IT})K^{IT}_{t-1} + I^{IT}_t \\
- & \text{and} \; A_t =  S_t \Psi_t (K^{IT}_t)^{\gamma}
+\max_{K_{1,t}(s), L_{1,t}(s), S^{IT}_t(s) } Y_t(s) =  & K_{1,t}(s)^{\alpha}L_{1,t}(s)^{\beta}S^{IT}_t(s)^{1-\alpha - \beta}A_t \\
+ & - w_t L_{1,t}(s) -R_tK_{1,t}(s) -P^{IT}_t IT_t(s) \\
+ & \text{where} \; S^{IT}_t(s) =  (1-\delta^{IT})S^{IT}_{t-1} + IT_t \\
+ &  \; A_t =  \eta_t \Psi_t (G(S^{IT}_t,S^{IT}_{t-1},\dots))^{\gamma} \\
+ &  \; G(S^{IT}_t,S^{IT}_{t-1},\dots) = \zeta_1 S_t^{IT} + \zeta_2 S^{IT}_{t-1} + \dots \\
+  & \text{and} \; \sum_{i=1}^{N} \zeta_i = 1
 \end{align*}
+
+\end{frame}
+
+\begin{frame}
 
@@
 \begin{align*}
-\max_{K^{I}_t(s), L^{I}_t(s)} I^{IT}_t(s) = P^{IT}_t S_t \lambda_t F(K^I_t(s), L^I_t(s)) -w_t L^I_t(s) - R_t K^I_t(s)
+\max_{K_{2,t}(s), L_{2,t}(s)} IT_t(s) = P^{IT}_t \eta_t \lambda_t F(K_{2,t}(s), L_{2,t}(s)) -w_t L_{2,t}(s) - R_t K_{2,t}(s)
 \end{align*}
@@
 
-A news shock is $S_{t+k} \uparrow$ for some positive $k$.
+A news shock is $\eta_{t+k} \uparrow$ for some positive $k$.
 
@@
 \begin{align*}
-\frac{\dot{A}}{A} = & \frac{\dot{Y}}{Y} - \alpha \frac{\dot{K^f}}{K^f} - \beta \frac{\dot{L^f}}{L^f} - (1-\alpha - \beta) \frac{\dot{K^{IT}}}{K^{IT}} \\
-= & \frac{\dot{S}}{S} + \frac{\dot{\Psi}}{\Psi} + \gamma \frac{\dot{K^{IT}}}{K^{IT}}
+\frac{\dot{A}}{A} = & \frac{\dot{Y}}{Y} - \alpha \frac{\dot{K_1}}{K_1} - \beta \frac{\dot{L_1}}{L_1} - (1-\alpha - \beta) \frac{\dot{S^{IT}}}{S^{IT}} \\
+= & \frac{\dot{\eta}}{\eta} + \frac{\dot{\Psi}}{\Psi} + \gamma \frac{\dot{G}(S^{IT},\dots)}{G(S^{IT},\dots)}
 \end{align*}
 
-TFP consists of an exogenous, common technology process $S$, a final-good-specific exogenous technology process $\Psi$ and an endogenous component coming as a spillover from the aggregate stock of IT technology.
+TFP consists of an exogenous, common technology process $\eta$, a final-good-specific exogenous technology process $\Psi$ and an endogenous component coming as a spillover from the aggregate stock of IT technology.
 \end{frame}
@@
 \begin{align*}
-R_t = & \alpha \frac{Y_t(s)}{K^f_t(s)} P^C_t = S_t \lambda_t F_k P^{IT}_t \\
-\Leftrightarrow \frac{P^{IT}_t }{P^{C}_t } = & \alpha \frac{K^f_t(s)^{\alpha}L^f_t(s)^{\beta}K^{IT}_t(s)^{1-\alpha - \beta}S_t \Psi_t (K^{IT}_t)^{\gamma} }{K^f_t(s)} \frac{1}{S_t \lambda_t F_k}
+R_t = & \alpha \frac{Y_t(s)}{K_{1,t}(s)} P^C_t = \eta_t \lambda_t F_k P^{IT}_t \\
+\Leftrightarrow \frac{P^{IT}_t }{P^{C}_t } = & \alpha \frac{K_{1,t}(s)^{\alpha}L_{1,t}(s)^{\beta}S^{IT}_t(s)^{1-\alpha - \beta}\eta_t \Psi_t (S^{IT}_t)^{\gamma} }{K_{1,t}(s)} \frac{1}{\eta_t \lambda_t F_k}
 \end{align*}
@@
 \begin{frame}
-\frametitle{+1 slide: evidence that $\gamma \neq 0$, i.e. that GPTs show up as spillovers}
+\frametitle{Evidence that $\gamma \neq 0$; GPTs show up as spillovers}
 

### 2018-02-02 Latex/Basu_propositions/propositions.tex
another update to basu presentation
updated the presentation once more with another reference

@@
 \begin{itemize}
+\item Whelan (2001): a two-sector model with IT relative prices.
 \item Brynjolfsson, e.g. in Bloom et al. (2014): theory of IT as a GPT changing management practices.
-\item Mokyr (1990):  an economic history account of how GPTs (electricity, computers) change the organization of production as a whole, so it's not just the firm's individual use of them that matters, but that of the economy as a whole.
+\item Mokyr (1990):  an economic history account of how GPTs (electricity, computers) change the \textbf{organization} of production $\rightarrow$ neither use, nor output value of IT, but \textbf{indirect} effect
 \item Romer (1986): a production function with spillovers from human capital.
@@
 \begin{itemize}
+\item Basu, Fernald, Oulton \& Srinivasan (2004 Macro Annuals)
 \item Stiroh (2002 AER): industry-level data show that productivity gains from IT are not confined to industries producing IT.
 \item Oliner \& Sichel (2000 JEP): growth accounting.
-\item Black \& Lynch (2004, EJ), Doms, Dunn \& Troske (1997 QJE): plant-level data.
+\item Black \& Lynch (2004 EJ), Doms, Dunn \& Troske (1997 QJE): plant-level data.
 \end{itemize}

### 2018-02-06 Latex/Basu_propositions/propositions.tex
Just added a neutral title...you never know...
Some modifications on the presentation

@@
 
-\title{5 slides to convince you that it's endogenous TFP}
+\title{Title}
 
@@
 
-Final goods firm (GE)
+Final goods firm $s$ (GE)
 \begin{align*}
-\max_{K_{1,t}(s), L_{1,t}(s), S^{IT}_t(s) } Y_t(s) =  & K_{1,t}(s)^{\alpha}L_{1,t}(s)^{\beta}S^{IT}_t(s)^{1-\alpha - \beta}A_t \\
- & - w_t L_{1,t}(s) -R_tK_{1,t}(s) -P^{IT}_t IT_t(s) \\
- & \text{where} \; S^{IT}_t(s) =  (1-\delta^{IT})S^{IT}_{t-1} + IT_t \\
- &  \; A_t =  \eta_t \Psi_t (G(S^{IT}_t,S^{IT}_{t-1},\dots))^{\gamma} \\
- &  \; G(S^{IT}_t,S^{IT}_{t-1},\dots) = \zeta_1 S_t^{IT} + \zeta_2 S^{IT}_{t-1} + \dots \\
-  & \text{and} \; \sum_{i=1}^{N} \zeta_i = 1
+\max_{K_{1,t}(s), L_{1,t}(s), S^{IT}_t(s) }  & \sum_{t=0}^{\infty} \beta^t \Big[ P_t^C A_t K_{1,t}(s)^{\alpha_1}L_{1,t}(s)^{\alpha_2}S^{IT}_t(s)^{1-\alpha_1 - \alpha_2} \\
+& - W_t L_{1,t}(s) -R_tK_{1,t}(s) -P^{IT}_t IT_t(s) \Big] \\
 \end{align*}
+where
+\begin{itemize} 
+	\item $A_t =  \eta_t \Psi_t (G(S^{IT}_t,S^{IT}_{t-1},\dots))^{\gamma}$   
+	\item $S^{IT}_t(s) =  (1-\delta^{IT})S^{IT}_{t-1} + IT_t$
+	\item $G(S^{IT}_t,S^{IT}_{t-1},\dots) = \zeta_1 S_t^{IT} + \zeta_2 S^{IT}_{t-1} + \dots$
+	\item $\sum_{i=1}^{N} \zeta_i = 1$
+  \end{itemize}
 
@@
 \begin{align*}
-\max_{K_{2,t}(s), L_{2,t}(s)} IT_t(s) = P^{IT}_t \eta_t \lambda_t F(K_{2,t}(s), L_{2,t}(s)) -w_t L_{2,t}(s) - R_t K_{2,t}(s)
+\max_{K_{2,t}(s), L_{2,t}(s)} IT_t(s) = P^{IT}_t \eta_t \lambda_t F(K_{2,t}(s), L_{2,t}(s)) -W_t L_{2,t}(s) - R_t K_{2,t}(s)
 \end{align*}
@@
 
-A news shock is $\eta_{t+k} \uparrow$ for some positive $k$.
+\
 
-An IT productivity shock is $\lambda_{t} \uparrow$, i.e. an increase in IT productivity today.
+\begin{itemize}
+\item A news shock is $\eta_{t+k} \uparrow$ for some positive $k$.
 
-$\Psi$ is a final-good-specific exogenous technology process.
+\
+
+\item An IT productivity shock is $\lambda_{t} \uparrow$, i.e. an increase in IT productivity today. 
+\end{itemize}
 
@@
 
-TFP consists of an exogenous, common technology process $\eta$, a final-good-specific exogenous technology process $\Psi$ and an endogenous component coming as a spillover from the aggregate stock of IT technology.
+\
+
+where
+\begin{itemize}
+	\item $\eta$ is a economy-wide exogenous technology process.
+	\item $\Psi$ is a final-good exogenous technology process.
+	\item The third element is a spillover from the aggregate stock of IT.
+	\end{itemize}
+
 \end{frame}

### 2018-02-14 Latex/Drafts/draft_13feb2018.tex
steady state in mathematica, a bibliography and the frame of a paper-style draft for Peter Ireland

\documentclass[11pt]{article}
\usepackage{amsmath, amsthm, amssymb,lscape, natbib}
\usepackage{graphicx}
\usepackage{colortbl}
\usepackage{hhline}
\usepackage{multirow}
\usepackage{setspace}
\usepackage[final]{pdfpages}
\usepackage[left=2.5cm,top=2.5cm,right=2.5cm, bottom=2.5cm]{geometry}
\usepackage{natbib} 
\usepackage{bibentry} 
\newcommand{\bibverse}[1]{\begin{verse} \bibentry{#1} \end{verse}}
\newcommand{\vs}{\vspace{.3in}}
\renewcommand{\ni}{\noindent}
\usepackage{xr-hyper}
\usepackage[]{hyperref}

\definecolor{citec}{rgb}{0,0,.5}
\definecolor{linkc}{rgb}{0,0,.6}
\definecolor{bcolor}{rgb}{1,1,1}
\hypersetup{
%hidelinks = true
  colorlinks = true,
  urlcolor=linkc,
  linkcolor=linkc,
  citecolor = citec,
  filecolor = linkc,
  pdfauthor={Laura G\'ati},
}

% A first draft in a paper-format

\geometry{left=.97in,right=1in,top=1in,
bottom=1in}
\linespread{1.5}
\renewcommand{\[}{\begin{equation}}
\renewcommand{\]}{\end{equation}}

\begin{document}

\linespread{1.0}

\title{Title}
\author{Marco Brianti, Laura G\'ati\thanks{%
Department of Economics, Boston College, Chestnut Hill, MA 02467, U.S.A. Email: gati@bc.edu} \\
%EndAName
 Boston College \\
%EndAName
}
\date{Preliminary and Incomplete \\ \today}
\maketitle

%%%%%%%%%%%%%%%%%%%%             ABSTRACT           %%%%%%%%%%%%%%%%%% 
%\begin{abstract}

%\end{abstract}

\newpage
%%%%%%%%%%%%%%%%%%%%               INTRODUCTION                 %%%%%%%%%%%%%%%%%% 
\section{Introduction}

%%%%%%%%%%%%%%%%%%%%               MODEL                 %%%%%%%%%%%%%%%%%% 
\section{Model}

%%%%%%%%%%%%%%%%%%%%               EMPIRICS                 %%%%%%%%%%%%%%%%%% 
\section{Empirics}
\subsection{Data and specification}
\subsection{Results}

%%%%%%%%%%%%%%%%%%%%               CONCLUSION                 %%%%%%%%%%%%%%%%%% 
\section{Conclusion}

 %%%%%%%%%%%%%%%%%%           BIBLIOGRAPHY            %%%%%%%%%%%%%%%%%% 
\newpage
\nocite{*}
\bibliography{itgpt} % try one from BibDesk -- it works!!! 
\bibliographystyle{cell} % cell is the best so far, acm 2nd best

\end{document}

### 2018-02-15 Latex/Drafts/draft_13feb2018.tex
more work on the draft

@@
 \definecolor{bcolor}{rgb}{1,1,1}
+\def \ourFigPath {../../Figures/} 
+\def \ourTablePath {../../Tables/} 
 \hypersetup{
@@
 \section{Introduction}
+The sluggish recovery of productivity after the Great Recession of 2008 has reignited interest in the factors behind long-run productivity growth.
+On the one hand, the literature in the wake of the seminal contribution of \cite{comin_gertler2006} interprets productivity fluctuations as medium-run business cycle phenomena, thus inviting the interpretation of the current productivity slowdown as a persistent, but transitory slump due to procyclical R\&D investment contracting during the bust.
+On the other hand, a glance at Fig.
+\ref{fig_slowdowns} reveals that total factor productivity (TFP) dropped already before the 2008 recession.
+Motivated by this observation, a large literature has turned to alternative potential drivers of productivity.\footnote{Another reason to be skeptical concerning the extent to which R\&D can play a major rule in current productivity developments is that R\&D investment only started decreasing after the decrease in TFP materialized, contrary to the conventional wisdom that R\&D leads TFP.
+See for example \cite{guerron_jinnai2013}.} In particular, this literature reexamines the question of what the main forces behind productivity growth are in the economy in general.
+
+\begin{figure}[h!]
+\centering
+\caption{The Slowdown of TFP and R\&D (levels)}
+\includegraphics[scale = 0.3]{\ourFigPath fig_RD_level_macrolunch_30-Nov-2017_11_31_04}
+\label{fig_slowdowns}
+\end{figure}
+
+The particular channel of productivity growth this paper focuses on is general purpose technology (GPT).
+GPTs are technologies whose main effect on productivity comes through changing the organization and the process of production.
+Thus they may be inputs to production themselves, but their fundamental contribution is as spillovers to aggregate production.\footnote{See for example \cite{bresnahan_trajtenberg1992}.} More specifically, we consider information technologies (IT), which has widely been claimed to be the main GPT since the 1990s.\footnote{See \cite{basu_etal2004}, \cite{brynjolfsson_etal1994} and \cite{allstar_paper} among many others.} Our main contribution is quantifying the extent to which IT productivity can explain long-run fluctuations in TFP.
+We use SVAR approach in which we identify a shock to IT productivity and examine how much of the forecast error variance (FEV) of TFP our identified shock can account for.
+Our second contribution is providing an identification scheme for the IT productivity shock in the presence of other shocks that at first glance seem observationally equivalent.
+Since our shock of interest contemporaneously effects the productivity of the IT sector and shows up in aggregate TFP with a lag\footnote{See \cite{david1989}.}, it bears strong resemblance to classical news shocks, which by definition have no contemporaneous effect on TFP, yet affect it over time.\footnote{This is the classical definition of the news shock literature in the wake of \cite{beaudry_portier2006}.} In order to make sure that our IT productivity shock is not picking up the effects of news shocks, we propose an identification approach that identifies both shocks, thus disentangling them.
+Applying our methodology to aggregate US data from 1989 to 2017, we obtain that IT productivity shocks explain around 50\% of TFP fluctuations at long horizons, while news shocks account for around 20\%.
+We interpret these findings as evidence that IT as a general purpose technology is indeed an important factor behind the evolution of long-run TFP, while still maintaining a considerable role for news shocks.
+
+The paper is organized as follows.
+Section \ref{sec_related_lit} reviews the related literature.
+Section \ref{sec_model} lays out a simple two-sector model which we use to work out our identifying restrictions.
+Section \ref{sec_empirics} presents the data, the SVAR we run and discusses the results.
+Section \ref{sec_conclusion} concludes.
+
+%%%%%%%%%%%%%%%%%%%%               RELATED LITERATURE                 %%%%%%%%%%%%%%%%%% 
+\section{Related literature}
+\label{sec_related_lit}
+
+This paper is situated at the intersection of three literatures.
+The first is the medium-run business cycles literature which emphasizes the role of R\&D investment for productivity growth.
+Here the seminal paper is \cite{comin_gertler2006}, which first set up the structural framework to analyze endogenous growth phenomena with the tools of business cycle analysis.
+Many papers rely on Comin \& Gertler's framework to attempt to quantify the importance of R\&D investment for TFP shocks.
+These papers include \cite{anzo_etal2016}, \cite{comin_etal2016} and \cite{moran_queralto2017}.
+Our paper is most closely related to \cite{moran_queralto2017}, since that paper also uses SVAR analysis to assess the role of R\&D investment.
+However, while Moran \& Queralto focus on R\&D, our interest here is IT productivity because of its role as a general purpose technology.
+Additionally, while Moran and Queralto recognize the identification problem that arises due to the similarity between their shock of interest and news shocks, they refrain from attempting to identify both shocks.
+
+The second literature our paper is related to is the literature on GPTs.
+It is difficult to trace this literature back to a single paper, but one of the early, important contributions is \cite{bresnahan_trajtenberg1992}, which first suggests the possibility of GPTs being the engines behind productivity growth.
+Bresnahan \& Trajtenberg are also among the first to interpret electricity and IT to have been the most important GPTs, electricity being seminal in the early 20\textsuperscript{th} century up to the 1930s, and IT gaining prominence in the 1990s.
+The literature on GPTs has subsequently identified a number of characteristics of GPTs.
+\cite{david1990} and \cite{jov_rous2005} pinpoint that GPTs do not tend to increase productivity contemporaneously but only affect it after considerable time.
+Based on this observation, \cite{atkeson_kehoe2007} build a model which captures the slow diffusion of GPTs.
+A number of papers, most notably \cite{oliner_sichel2000} and \cite{oulton2010}, use neoclassical growth accounting techniques to conclude that both IT production but in particular IT use contributed significantly to the US productivity surge in the 1990s.
+\cite{basu_etal2004} conduct a case study between the US and the UK to compare why the UK did not experience the productivity uptake the US enjoyed in the 1990s, and find that differences in IT productivity explain a large fraction.
+Finally, to our knowledge \cite{allstar_paper} carries out the most thorough analysis of a vast arsenal of possible causes for the sluggish recovery of productivity after the 2008 recession.
+A clear reason remains elusive, yet the authors conclude that IT is a strong potential candidate.
+
+The third and last literature that our work relates to is the news shocks literature.
 
@@
 \section{Model}
+\label{sec_model}
 
@@
 \section{Empirics}
+\label{sec_empirics}
 \subsection{Data and specification}
@@
 \section{Conclusion}
+\label{sec_conclusion}
 
@@
 \nocite{*}
-\bibliography{itgpt} % try one from BibDesk -- it works!!! 
-\bibliographystyle{cell} % cell is the best so far, acm 2nd best
+\bibliography{itgpt} 
+\bibliographystyle{cell}
 

### 2018-02-15 Latex/Drafts/draft_13feb2018.tex
some more work on the draft
i’ve written a rough version with everything except for the structural
model and appendix.

@@
 \usepackage{multirow}
+\usepackage{multicol}
 \usepackage{setspace}
@@
 \section{Introduction}
-The sluggish recovery of productivity after the Great Recession of 2008 has reignited interest in the factors behind long-run productivity growth.
+The sluggish recovery of productivity after the Great Recession of 2008 has reignited interest in the factors behind long-run productivity.
 On the one hand, the literature in the wake of the seminal contribution of \cite{comin_gertler2006} interprets productivity fluctuations as medium-run business cycle phenomena, thus inviting the interpretation of the current productivity slowdown as a persistent, but transitory slump due to procyclical R\&D investment contracting during the bust.
-On the other hand, a glance at Fig.
-\ref{fig_slowdowns} reveals that total factor productivity (TFP) dropped already before the 2008 recession.
-Motivated by this observation, a large literature has turned to alternative potential drivers of productivity.\footnote{Another reason to be skeptical concerning the extent to which R\&D can play a major rule in current productivity developments is that R\&D investment only started decreasing after the decrease in TFP materialized, contrary to the conventional wisdom that R\&D leads TFP.
-See for example \cite{guerron_jinnai2013}.} In particular, this literature reexamines the question of what the main forces behind productivity growth are in the economy in general.
+On the other hand, a glance at Figure \ref{fig_slowdowns} reveals that total factor productivity (TFP) dropped already before the 2008 recession.
+Motivated by this observation, a large literature has turned to potential drivers of productivity other than R\&D.\footnote{Another reason to be skeptical concerning the extent to which R\&D can play a major rule in current productivity developments is that R\&D investment only started decreasing after the decrease in TFP materialized, contrary to the conventional wisdom that R\&D leads TFP.
+See for example \cite{guerron_jinnai2013}.}
 
@@
 GPTs are technologies whose main effect on productivity comes through changing the organization and the process of production.
-Thus they may be inputs to production themselves, but their fundamental contribution is as spillovers to aggregate production.\footnote{See for example \cite{bresnahan_trajtenberg1992}.} More specifically, we consider information technologies (IT), which has widely been claimed to be the main GPT since the 1990s.\footnote{See \cite{basu_etal2004}, \cite{brynjolfsson_etal1994} and \cite{allstar_paper} among many others.} Our main contribution is quantifying the extent to which IT productivity can explain long-run fluctuations in TFP.
-We use SVAR approach in which we identify a shock to IT productivity and examine how much of the forecast error variance (FEV) of TFP our identified shock can account for.
-Our second contribution is providing an identification scheme for the IT productivity shock in the presence of other shocks that at first glance seem observationally equivalent.
-Since our shock of interest contemporaneously effects the productivity of the IT sector and shows up in aggregate TFP with a lag\footnote{See \cite{david1989}.}, it bears strong resemblance to classical news shocks, which by definition have no contemporaneous effect on TFP, yet affect it over time.\footnote{This is the classical definition of the news shock literature in the wake of \cite{beaudry_portier2006}.} In order to make sure that our IT productivity shock is not picking up the effects of news shocks, we propose an identification approach that identifies both shocks, thus disentangling them.
-Applying our methodology to aggregate US data from 1989 to 2017, we obtain that IT productivity shocks explain around 50\% of TFP fluctuations at long horizons, while news shocks account for around 20\%.
+Thus they may be inputs to production themselves, but their fundamental contribution is as spillovers to aggregate production.\footnote{See for example \cite{bresnahan_trajtenberg1992}.} More specifically, we consider information technologies (IT), which has widely been claimed to be the main GPT since the 1990s.\footnote{See \cite{basu_etal2004}, \cite{brynjolfsson_etal1994} and \cite{allstar_paper} among many others.} Our main contribution is quantifying the extent to which IT investment can explain long-run fluctuations in TFP.
+We use a SVAR approach in which we identify a shock to IT investment and examine how much of the forecast error variance (FEV) of TFP our identified shock can account for.
+Our second contribution is providing an identification scheme for the IT investment shock in the presence of other shocks that at first glance seem observationally equivalent.
+Since our shock of interest contemporaneously effects the productivity of the IT sector and shows up in aggregate TFP with a lag\footnote{See \cite{david1989}.}, it bears strong resemblance to classical news shocks, which by definition have no contemporaneous effect on TFP, yet affect it over time.\footnote{This is the classical definition of the news shock literature in the wake of \cite{beaudry_portier2006}.} In order to make sure that our IT investment shock is not picking up the effects of news shocks, we propose an identification approach that identifies both shocks, thus disentangling them.
+Applying our methodology to aggregate US data from 1989 to 2017, we obtain that IT investment shocks explain around 50\% of TFP fluctuations at long horizons, while news shocks account for around 20\%.
 We interpret these findings as evidence that IT as a general purpose technology is indeed an important factor behind the evolution of long-run TFP, while still maintaining a considerable role for news shocks.
-
-The paper is organized as follows.
-Section \ref{sec_related_lit} reviews the related literature.
-Section \ref{sec_model} lays out a simple two-sector model which we use to work out our identifying restrictions.
-Section \ref{sec_empirics} presents the data, the SVAR we run and discusses the results.
-Section \ref{sec_conclusion} concludes.
 
@@
 Our paper is most closely related to \cite{moran_queralto2017}, since that paper also uses SVAR analysis to assess the role of R\&D investment.
-However, while Moran \& Queralto focus on R\&D, our interest here is IT productivity because of its role as a general purpose technology.
+However, while Moran \& Queralto focus on R\&D, our interest here is IT investment because of its role as a general purpose technology.
 Additionally, while Moran and Queralto recognize the identification problem that arises due to the similarity between their shock of interest and news shocks, they refrain from attempting to identify both shocks.
@@
 A number of papers, most notably \cite{oliner_sichel2000} and \cite{oulton2010}, use neoclassical growth accounting techniques to conclude that both IT production but in particular IT use contributed significantly to the US productivity surge in the 1990s.
-\cite{basu_etal2004} conduct a case study between the US and the UK to compare why the UK did not experience the productivity uptake the US enjoyed in the 1990s, and find that differences in IT productivity explain a large fraction.
+\cite{stiroh2002} uses industry-level data to reach the same findings.
+\cite{basu_etal2004} conduct a case study between the US and the UK to compare why the UK did not experience the productivity uptake the US enjoyed in the 1990s, and find that differences in IT investment explain a large fraction.
 Finally, to our knowledge \cite{allstar_paper} carries out the most thorough analysis of a vast arsenal of possible causes for the sluggish recovery of productivity after the 2008 recession.
@@
 
-The third and last literature that our work relates to is the news shocks literature.
+The third and last literature that our work relates to is the news shocks literature started by  \cite{beaudry_portier2006}.
+Our work is most closely related to \cite{barsky_sims2011}, because we augment their identification strategy to identify an additional shock.
+\cite{bouakez_kemoe2017} and \cite{kurmann_sims2017} are similar to our paper in spirit because they argue that news shocks are not properly identified if there are measurement errors in TFP.
+Along these lines, \cite{crouzet_oh2014} consider fluctuations in inventories as variation that needs to purged from TFP in order to properly identify news shocks.
+Instead of measurement errors or inventories, we attribute the misidentification of news shocks to a general purpose technology, IT, spilling over into TFP.
+A large fraction of the literature has chosen to focus on investment-specific shocks, most notably \cite{greenwood_etal1997}, \cite{fisher2006}, \cite{chen_wemy2015} and \cite{cummins_violante2002}.
+While these papers, in particular \cite{fisher2006}, resemble our work in that they identify a news shock and a sector-specific shock, they also deviate from what we do here in a crucial way.
+Importantly, all of these papers essentially postulate two separate news shocks: one to aggregate TFP, and one to sector-specific TFPs.
+Our IT investment shock is, however, not a classical news shock in the sense that it affects the demand for IT goods contemporaneously; it is not information that productivity will increase in the future.
+Instead, the reason that this shock ends up impacting aggregate TFP in the future is the slow diffusion of GPTs documented by the GPT literature.
+Thus, our IT investment shock has a very different interpretation than the reduced-form shocks identified in this strand of literature.
+
+The rest of the paper is organized as follows.
+Section \ref{sec_model} lays out a simple two-sector model which we use to work out our identifying restrictions.
+Section \ref{sec_empirics} presents the data, the SVAR we run and discusses the results.
+Section \ref{sec_conclusion} concludes.
 
@@
 \label{sec_empirics}
+Having rationalized our identification restriction, we now summarize our overall identification scheme and present the VAR that we run.
+In order to identify the IT investment shock as well as a classical news shock, we proceed sequentially as follows.
+First, we identify the news as the shock that maximizes the FEV of future TFP subject to our additional identification restriction developed in Section \ref{sec_model} that the news shock has no effect on relative prices after a small number of periods.
+Second, we let the IT investment shock maximize the remaining FEV of future TFP.
+Lastly, whatever FEV of future TFP remains unexplained we attribute to surprise shocks to technology.
+
+It is apparent that this overall strategy relies heavily on \cite{barsky_sims2011}, since they are the first to propose a FEV-maximization strategy in order to identify news shocks.
+The novelty here is adding a second shock, the IT investment shock, that is observationally equivalent to a news shock in data, and relying on the additional restriction on relative prices in order to disentangle the two shocks.
+As stated in Section \ref{sec_related_lit}, a similar identification scheme relying on relative prices has been proposed by \cite{fisher2006}, but the shock that Fisher identifies has a completely different interpretation than our shock.
+Fisher's additional shock is indeed a sector-specific news shock, while our IT investment shock is a surprise shock to IT investment today.
+Thus, while Fisher disentangles two types of news shocks, we here disentangle a news shock from a shock that captures endogenous growth in TFP.
+We therefore believe that understanding the importance of our shock to the evolution of TFP is especially of interest to economists, because it can shed light on the contribution of one channel of endogenous growth.
+
 \subsection{Data and specification}
+We run a VAR on a vector of aggregate variables $\mathbf{X_t}$, using quarterly data from the US for the time period of 1989:q1 - 2017:q2. The data vector is:
+
+	\begin{equation*}
+	\mathbf{X_t} = 
+	\begin{bmatrix}
+    TFP_t      \\
+
+   SP_t   \\
+
+   IT_t \\
+
+   GDP_t \\
+
+   C_t \\
+
+   RP_t
+\end{bmatrix}
+	\end{equation*}
+
+	\
+
+$TFP$ is the log of Fernald's constructed TFP series, utilization-adjusted.
+$SP$ is the log of the S\&P 500 stock price index.
+$IT$ is private fixed investment in information processing equipment and software, deflated using the price index for IT goods from the CPI.
+$GDP$ and $C$ are the logs of GDP and personal consumption expenditures respectively.
+$RP$ is the ratio of two inflation rates: IT price inflation divided by overall CPI inflation.\footnote{Redoing the analysis with PCE instead of CPI inflation yields very similar results.} All relevant variables are real.
+
+We choose one lag for our VAR as suggested by the BIC and HQ lag selection criteria.
+In our preferred specification, we set the horizon of FEV-maximization at 60 quarters, but the results are robust to different long horizons.
+The restriction on relative prices after a news shock is imposed at 8 quarters, but numbers between 6 and 12 quarters yield similar results.
+
 \subsection{Results}
+
+Turning to the results, we first examine the impulse responses to our two identified shocks to see whether the responses are in line with our expectations and the predictions of our structural model.
+We then proceed to the heart of the results, the variance decompositions.
+
+\begin{figure}
+\caption{Impulse responses to our news and IT investment shocks}
+\begin{multicols}{2}
+\centering 
+\includegraphics[scale=0.14]{\ourFigPath fig_News_Shock_on_TFP__} \\
+\vspace{0.7cm}
+\includegraphics[scale=0.14]{\ourFigPath fig_News_Shock_on_Real_SP__}\\
+\vspace{0.7cm}
+\includegraphics[scale=0.14]{\ourFigPath fig_News_Shock_on_Real_IT_Investment__}\\
+\vspace{0.7cm}
+\includegraphics[scale = 0.14]{\ourFigPath fig_News_Shock_on_Real_GDP_Ryan_two_stepsID_10-Dec-2017_17_34_47}\\ 
+\vspace{0.7cm}
+\includegraphics[scale = 0.14]{\ourFigPath fig_News_Shock_on_Real_Consumption_Ryan_two_stepsID_10-Dec-2017_17_34_50}\\ 
+\vspace{0.7cm}
+\includegraphics[scale = 0.14]{\ourFigPath fig_News_Shock_on_Relative_Price_Ryan_two_stepsID_10-Dec-2017_17_34_52}\\
+
+\includegraphics[scale=0.14]{\ourFigPath fig_IT_Shock_on_TFP__} \\
+\vspace{0.7cm}
+\includegraphics[scale=0.14]{\ourFigPath fig_IT_Shock_on_Real_SP__} \\
+\vspace{0.7cm}
+\includegraphics[scale=0.14]{\ourFigPath fig_IT_Shock_on_Real_IT_Investment__} \\
+\vspace{0.7cm}
+\includegraphics[scale = 0.14]{\ourFigPath fig_IT_Shock_on_Real_GDP_Ryan_two_stepsID_10-Dec-2017_17_35_00}\\
+\vspace{0.7cm}
+\includegraphics[scale = 0.14]{\ourFigPath fig_IT_Shock_on_Real_Consumption_Ryan_two_stepsID_10-Dec-2017_17_35_02}\\ 
+\vspace{0.7cm}
+\includegraphics[scale = 0.14]{\ourFigPath fig_IT_Shock_on_Relative_Price_Ryan_two_stepsID_10-Dec-2017_17_35_04}\\
+
+\end{multicols}
+\label{fig_irfs}
+\end{figure}
+
+Figure \ref{fig_irfs} displays the impulse responses of all the variables in the VAR to the news shock and to the IT investment shock.
+The first row depicts the response of TFP.
+In line with the expectation that the two shocks look very similar with respect to the way they affect TFP, this impulse response indeed looks very similar for both shocks.
+TFP does not react on impact, but moves into positive territory after 10-15 quarters, and remains above its steady state value for an extended period of time.
+The similarity of the two shocks is also seen in the response of stock prices in the second row.
+For both the news shock and the IT investment shock, stock prices jump up on impact because both shocks will eventually entail higher future TFP.\footnote{While we here emphasize the sign of the responses because we seek to validate our identification approach, it should be noted that the magnitude of the responses is in line with the literature, in particular with \cite{barsky_sims2011}.}
+
+The first variable where the difference between the two shocks starts kicking in is IT investment in the third row.
+Of course, the IT investment shock is by default an increase in the IT investment residual, so we have a positive response there.
+After the news shock, however, IT investment decreases significantly on impact.
+This response can be rationalized with consumption smoothing.
+When news about increases in TFP in the future hit, consumers know that their future consumption will increase.
+Therefore they seek to raise consumption already today, and to do so, they decrease savings.
+Thus, all investment variables decrease.
+
+GDP and consumption in the fourth and fifth rows respond very similarly to each other and across the two shocks.
+This is because both are a function of productivity and expectations, and as we have highlighted above, both TFP and stock prices react similarly to both shocks, thus inducing similar GDP and consumption responses.
+
+A very comforting feature of these results are the impulse responses of relative prices, seen in the last row.
+On the one hand, one can see our identification restriction imposed on the response to the news shock at 8 quarters.
+On the other hand, even though we do not impose anything on the response of relative prices to the IT investment shock, we get a significantly negative response on impact which remains significant for about 20 quarters.
+This seems to confirm the validity of our identification restriction, since relative prices indeed move more following an IT investment shock than they do after a news shock.
+
+Overall the impulse responses are in line with our expectations and suggest that our identification approach is performing well.
+We therefore now turn to the core of our results and investigate what fraction of TFP volatility can be attributed to our two shocks at a long horizon.
+Table \ref{tab_vardecomp} portrays the share of forecast error variance of TFP that the two identified shocks account for.
+To put the numbers in perspective, the news shock identified by \cite{barsky_sims2011} explains about 45\% of the FEV of TFP at 40 quarters.
+
+\begin{table}[h!]
+\centering
+\caption{Share of FEV of TFP at 60 quarters explained by the identified shocks}
+\label{tab_vardecomp}
+\
+
+\begin{large}
+	\begin{tabular}{lccc}
+	\hline
+		& News & IT & Total \\
+		\hline
+	TFP	           & 0.20384  & 0.52596 & 0.72981  \\
+		\hline
+	\end{tabular}
+\end{large}
+\end{table}
+
+The striking result is that the IT investment shock alone is able to explain almost 53\% of long-run TFP variation!
+One the one hand, this means that some of the explanatory power of the news shock should actually be attributed to the IT shock, so we are indeed doing a correct cleaning of the news shock from elements that come from a different channel.
+On the other hand, the IT investment shock is also picking up explanatory power above and beyond that purged from the news shock.
+Thus, it is not the case that the news shock is really just an IT investment shock; the two are indeed two different sources of TFP fluctuations.
+By extension, the news shock still retains a significant explanatory power of about 20\%.
+All in all, the IT investment shock does not discredit the news shock in explaining long-run TFP, but it seems to play a far more important role itself.
+
+\subsection{A counterfactual for the Dotcom bubble}
+Returning to our motivating example, we now address the question what our VAR predicts for the evolution of TFP had the negative IT investment shocks of the Dotcom bubble not happened.
+Therefore, using the time series of structural IT investment shocks recovered from our SVAR, we construct a counterfactual TFP series in which we shut off all negative shocks in our sample.
+This counterfactual series is plotted against the original series in Figure \ref{fig_counter}.
+
+\begin{figure}[h!]
+\caption{A counterfactual TFP series}
+\label{fig_counter}
+
+\vspace{0.5cm}
+	\centering
+	\includegraphics[scale=0.28]{\ourFigPath fig_counterfactual_}
+\end{figure}
+
+By definition, since we have shut off negative IT investment shocks, the counterfactual TFP series, represented by the red line, are above the original blue series.
+The notable feature of this graph, however, is that the two lines really start to diverge around 2005, around 12 quarters after the Dotcom bubble burst in 2002.
+As the impulse responses from the VAR indicate, it takes about 10 quarters for the IT investment shock to show up as significant response in TFP.
+Thus the counterfactual is suggesting that the large divergence between original and constructed series come from the sizable negative IT investment shock that hit during the Dotcom crash.
 
@@
 \label{sec_conclusion}
+This paper has proposed spillovers from the stock of IT as an important driver for TFP fluctuations in the long run.
+Our main contribution is presenting empirical evidence in a SVAR context that quantifies the role of IT.
+The results indicate that since IT investment shocks explain almost 53\% of long-run TFP fluctuations, they are indeed an important factor for the evolution of TFP.
+At the same time, news shocks still explain about 20\%, losing some, but not all of their explanatory power found in previous studies.
+
+Our second contribution is developing an identification strategy to properly disentangle news shocks from IT investment shocks.
+Our procedure augments FEV-maximization \`a la \cite{barsky_sims2011} with a restriction on the relative price of IT goods.
+The identification scheme is intuitive and simple to implement, and can be generalized to a whole class of shocks that bear resemblance to news shocks, yet have an entirely different structural interpretation.
 

### 2018-03-07 Latex/Meeting_Ryan_5March_2018/meeting5March2018.tex
work on model. only one tiny mistake now in steady state, otherwise growth model works

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper,top=1.5cm,bottom=1.5cm,left=1.5cm,right=1.5cm,%
bindingoffset=0mm]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\qed}{\nobreak \ifvmode \relax \else
      \ifdim\lastskip<1.5em \hskip-\lastskip
      \hskip1.5em plus0em minus0.5em \fi \nobreak
      \vrule height0.75em width0.75em depth0em\fi}
\usepackage{tikz}
\usepackage{graphicx}
%\graphicspath{{./Figures/}}
\def \ourFigPath {../../} % this should move up two steps 
% . = current directory
 % .. = parent directory
\usepackage{rotating}
\usepackage{float}
\linespread{1.3}
\raggedbottom

%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\R}{\mathbb{R}}
\DeclareMathOperator{\E}{\mathbb{E}}
%

\title{Steady state of two-sector models - Questions}
\author{Marco Brianti\\Laura Gati}
\date{5 March 2018}

\begin{document}

\maketitle

\

\section{A two-sector model \`a la Oulton (2010)}
Why look at this model? Because the one we have laid out maps to this, but here the formulation is simpler because the HH accumulates all kinds of capital. Also, I'm shutting off spillovers to TFP from the IT stock for now.

\begin{align*}
& yc_t = bc_t \; h1^{1-a-b} kc1_t^aki1_t^b \\
 & yi_t = bi_t  \; h2^{1-a-b} kc2_t^a kci1_t^b \\
& kc_t  = kc1_t + kc2_t \\
& ki_t = ki1_t + ki2_t \\
& h_t  = h1_t + h2_t \\
& kc_{t+1}  = (1-\delta_c )kc_t + ic_t \\
& ki_{t+1}  = (1-\delta_i)ki_t + it_t \\
& yc_t = c_t + ic_t \\
& yi_t = it_t \\
& p_t  = pi_t / pc_t  \; \; \; \text{Normalizing} \; pc = 1 \; \text{we have} \; p \; \text{as only price variable left.}\\
& bc_t, bi_t \; \text{grow with exogenous growth rates} \; \gamma_c \; \text{and} \; \gamma_i \\
& w_t / c_t = \chi \\
& 1 = \beta \mathbb{E}_t\frac{c_t}{c_{t+1}}(rc_{t+1} + 1- \delta_c ) \\
& 1 = \beta \mathbb{E}_t\frac{c_t}{c_{t+1}} (\frac{1}{p_{t+1}}ri_{t+1} + 1-\delta_i) \\
& w_t = (1-a-b)bc_t \; h1_t^{-a-b} kc1_t^a ki1_t^b \\
& rc_t = a \; bc_t \; h1_t^{1-a-b} kc1_t^{a-1} ki1_t^b \\
& ri_t = b \; bc_t \; h1_t^{1-a-b} kc1_t^a ki1_t^{b-1} \\
& \frac{1}{p_t}w_t = (1-a-b)bc_t \; h1_t^{-a-b} kc1_t^a ki1_t^b \\
& \frac{1}{p_t}rc_t = a \; bc_t \; h1_t^{1-a-b} kc1_t^{a-1} ki1_t^b \\
& \frac{1}{p_t}ri_t = b \; bc_t \; h1_t^{1-a-b} kc1_t^a ki1_t^{b-1} 
\end{align*}

\section{Steady state with growth}
BGP: Following Oulton, let's assume that $\gamma_i > \gamma_c$. It can be shown that $g_p = \gamma_c - \gamma_i < 0$, i.e. relative prices are falling.
Furthermore it can be shown (from LOMs, GDP equations) that $yc, c, ic$ and $kc$ grow at a shared rate $g$, while $yi, it$ and $ki$ grow at the rate $g_i$ which is faster than $g$. (Something like $g_i = g - g_p$.) From the EEs, we also see that $rc$ is constant while $ri$ is falling at the rate $g_p$. So at this point I have things growing at 3 different rates ($g, g_i$ and $g_p$) and how to connect these rates with the exogenous growth rates is tough, especially since I begin to get confused about gross and net growth rates too. But what I find the most challenging is to stationarize. Suppose I just divide the variables by the appropriate variable. For example since I know that $yc, c, ic$ and $kc$ grow at a shared rate $g$, I can divide all those variables by for example $yc_{t-1}$. So let's divide the final goods production function by $yc_{t-1}$ and denote by tilde the stationary variables:

\begin{equation*}
\tilde{yc}_t = bc_t \; h1^{1-a-b} \tilde{kc}_t^a \; ki_t^b \; yc_{t-1}^{-(1+b)}
\end{equation*}

What makes me confused here is that to get $ki$ to be stationary, we need to divide by additional stuff: the difference between the growth rates of the standard capital sector and the IT sector. But because of the exponents things don't seem to work out. And then we haven't even dealt with $bc$ which is merrily growing at its own rate and I don't see how to connect that with the $g, g_i$ and $g_p$.

\section{Shutting off growth - steady state is still tough}
 To shut off growth, I let $bc, bi$ be constants for a moment so that nothing grows. Then the steady state is given by the following set of equations (once I've done a couple of substitutions):

\begin{equation}
\frac{w}{\chi}  +\delta_c kc1 + \delta_c  kc2 = bc \; h1^{1-a-b} \; kc1^{a} \; ki1^{b}
\end{equation}

\begin{equation}
\delta_i ki1 + \delta_i ki2 = bi \; h2^{1-a-b} \; kc2^{a} \; ki2^{b}
\end{equation}

\begin{equation}
rc =1/\beta -(1-\delta_c)
\end{equation}

\begin{equation}
ri =(1/\beta -(1-\delta_i))p
\end{equation}

\begin{equation}
w = (1-a-b) \; bc \; h1^{-a-b} \; kc1^{a} \; ki1^{b}
\end{equation}

\begin{equation}
rc =  a \; bc \; h1^{1-a-b} \; kc1^{a-1} \; ki1^{b}
\end{equation}

\begin{equation}
ri =  b \; bc \; h1^{1-a-b} \; kc1^{a} \; ki1^{b-1}
\end{equation}

\begin{equation}
\frac{1}{p} w = (1-a-b) \; bi \; h2^{-a-b} \; kc2^{a} \; ki2^{b}
\end{equation}

\begin{equation}
\frac{1}{p} rc  = a \; bi \; h2^{1-a-b} \; kc2^{a-1} \; ki2^{b}
\end{equation}

\begin{equation}
\frac{1}{p} ri= b \; bi \; h2^{1-a-b} \; kc2^{a} \; ki2^{b-1}
\end{equation}

Even this one is tricky because so much seems redundant. I've been able to solve it, but it's not a 100\% correct.

%Taking ratios of (5)-(10), I get that $p = bc/bi$, which makes sense. I also get $\frac{h1}{h2} = \frac{kc1}{kc2} = \frac{ki1}{ki2}$. Then from (4) I get $ri$, and from (2) and (10) I get $\frac{ki1}{ki2}$. From (1) I get $\frac{w}{kc1}$, which I can use in (5) to get $h1$. The problem is, now I'm stuck. There doesn't seem to be a way to pin down the levels of standard capital and IT capital in any of the two sectors.

\end{document}

### 2018-03-07 Code/oulton2010/model.m

@@ -1,0 +1,104 @@
+% MODEL_LINEAR - Linearized version of the simple RBC model example from 
+% EC860.
+%
+% usage:
+%
+% [fy, fx, fyp, fxp] = model(param)
+%
+% where
+%
+% param = a parameters object, created in parmeters.m
+%
+% NOTES: This program, which generates the model matrices in cannonical form,
+%        requires the MATLAB symbolic toolbox! The algorithm used to solve 
+%        the model, however, is numerical and requires no m-files
+%        beyond those that appear in this directory.
+%
+% Code by Ryan Chahrour, Boston College, 2014
+ 
+% This is OULTON 2010 WITH GROWTH
+
+function [fyn, fxn, fypn, fxpn] = model(param)
+
+%Steady State
+[ss, param] = model_ss(param);
+
+%Declare parameters
+bet      = param.bet;  %Never call anything beta...it's a matlab function
+a        = param.a; % share of standard capital
+b        = param.b; % share of IT capital
+gami     = param.gami; % growth rate of equipment productivity
+gamc     = param.gamc;    % growth rate of neutral technology
+di       = param.di; % depreciation rate of capital IT
+dc       = param.dc; % depreciation rate of capital standard
+chi      = param.chi; % preference parameter.
+
+%Declare Needed Symbols
+syms KC KI KC1 KC2 KI1 KI2 % 6 vars
+syms KC_p KI_p KC1_p KC2_p KI1_p KI2_p 
+syms GAMC GAMI G GI GP % 5 vars
+syms GAMC_p GAMI_p G_p GI_p GP_p
+syms YC YI C IC IT W RC RI H H1 H2 % 11 vars
+syms YC_p YI_p C_p IC_p IT_p W_p RC_p RI_p H_p H1_p H2_p  % -> 22 vars
+
+%Declare X and Y vectors
+% KC KI GAMC GAMI
[…]

### 2018-03-07 Code/oulton2010/model_no_growth.m

@@ -1,0 +1,107 @@
+% MODEL_LINEAR - Linearized version of the simple RBC model example from 
+% EC860.
+%
+% usage:
+%
+% [fy, fx, fyp, fxp] = model(param)
+%
+% where
+%
+% param = a parameters object, created in parmeters.m
+%
+% NOTES: This program, which generates the model matrices in cannonical form,
+%        requires the MATLAB symbolic toolbox! The algorithm used to solve 
+%        the model, however, is numerical and requires no m-files
+%        beyond those that appear in this directory.
+%
+% Code by Ryan Chahrour, Boston College, 2014
+ 
+% This is OULTON 2010 W/O GROWTH
+
+function [fyn, fxn, fypn, fxpn] = model_no_growth(param)
+
+%Steady State
+[ss, param] = model_ss_no_growth(param);
+
+%Declare parameters
+bet      = param.bet;  %Never call anything beta...it's a matlab function
+a        = param.a; % share of standard capital
+b        = param.b; % share of IT capital
+gamq     = param.gamq; % growth rate of equipment productivity
+gamz     = param.gamz;    % growth rate of neutral technology
+g        = param.g; % growth rate of the rest of the model
+di       = param.di; % depreciation rate of capital IT
+dc       = param.dc; % depreciation rate of capital standard
+chi      = param.chi; % preference parameter.
+bc       = param.bc; % treating final goods technology as a param
+bi       = param.bi; % treating IT goods technology as a param
+
+%Declare Needed Symbols
+syms KC KI KC1 KC2 KI1 KI2 BC BI % 8 vars
+syms KC_p KI_p KC1_p KC2_p KI1_p KI2_p BC_p BI_p
+syms YC YI C IC IT W RC RI P H H1 H2 % 12 vars
+syms YC_p YI_p C_p IC_p IT_p W_p RC_p RI_p P_p H_p H1_p H2_p % 12 vars -> 20 vars -2 = 18 vars
+
+%Declare X and Y vectors
+% KC KI 
+X  = [KC KI]; % vector of state variables  
+XP = [KC_p KI_p]; % p signifies t+1 
+
+% YC YI C IC IT W RC RI P H H1 H2 KC1 KC2 KI1 KI2
[…]

### 2018-03-07 Code/oulton2010/model_ss.m

@@ -1,0 +1,62 @@
+% MODEL_SS - Return the steady state of the model (computed analytically)
+%
+% usage:
+% 
+% [ss, param] = model_ss(param)
+% STEADY STATE OF OULTON 2010 WITH GROWTH
+
+function [ss,param] = model_ss(param)
+
+%Parameters from param object
+bet      = param.bet;  %Never call anything beta...it's a matlab function
+a        = param.a; % share of standard capital
+b        = param.b; % share of IT capital
+gami     = param.gami; % growth rate of equipment productivity
+gamc     = param.gamc;    % growth rate of neutral technology
+di       = param.di; % depreciation rate of capital IT
+dc       = param.dc; % depreciation rate of capital standard
+chi      = param.chi; % preference parameter.
+
+%Use closed form expressions for the ss values. 
+% starting at my notes p. 231, green equations.
+gp = gamc - gami; % eq. I p. 222
+g = ((1-b)*gamc + b*gami)/(1-a-b);  % eq. II
+gi = ((a)*gamc + (1-a)*gami)/(1-a-b);  % eq. III
+rc = (1+g)/bet - (1-dc); % green 1
+ri = ((1+g)/bet - (1-di))*(1+gp); % green 2
+% ri = ((1+g)/bet - (1-di)); % brown option 2
+
+
+% Purple suggestion instead of orange one
+ki1_h1  = (b/ri)^((1-a)/(1-a-b)) *(a/rc)^(a/(1-a-b)) * (1+gamc)^(1/(1-a-b)); %purple 1
+kc1_h1  = (a*(1+gamc)/rc)^(1/(1-a)) *ki1_h1^(b/(1-a)); % purple 2
+w       = (1-a-b)*(1+gamc)*kc1_h1^(a) * ki1_h1^(b); % purple 3
+kc2_h2  = (a/rc)^((1-b)/(1-a-b)) * (b/ri)^(b/(1-a-b)) *((1+gami)*(1+gp))^(1/(1-a-b)); % purple 4 = orange 1
+ki2_h2  = (b/ri * (1+gami)*(1+gp))^(1/(1-b))*(kc2_h2)^(a/(1-b)); % purple 5 = orange 2
[…]

### 2018-03-07 Code/oulton2010/model_ss_no_growth.m

@@ -1,0 +1,85 @@
+% MODEL_SS - Return the steady state of the model (computed analytically)
+%
+% usage:
+% 
+% [ss, param] = model_ss(param)
+
+
+function [ss,param] = model_ss_no_growth(param)
+
+%Parameters from param object
+bet      = param.bet;  %Never call anything beta...it's a matlab function
+a        = param.a; % share of standard capital
+b        = param.b; % share of IT capital
+gamq     = param.gamq; % growth rate of equipment productivity
+gamz     = param.gamz;    % growth rate of neutral technology
+g        = param.g; % growth rate of the rest of the model
+di       = param.di; % depreciation rate of capital IT
+dc       = param.dc; % depreciation rate of capital standard
+chi      = param.chi; % preference parameter.
+bc       = param.bc; % treating final goods technology as a param
+bi       = param.bi; % treating IT goods technology as a param
+
+%Use closed form expressions for the ss values. 
+
+% % Version 1. Assume P given. (copied from steadystate_no_growth.nb, based on my notes p. 196.)
+% p = 1;
+% rc     = 1/bet - (1 - dc);
+% ri     = (1/bet - (1 - di))*p;
+% ki1ki2 = (bc/bi)^((1 - 2*a*b)/b) * p^((1 - 2*(a + b) - 2*a*(a + b))/(a + b));
+% kc1kc2 = p^(-1/b)*(bc/bi)^(1/b)*(ki1ki2)^(-1);
+% h1h2   = (1/p * bc/bi * kc1kc2^a * ki1ki2^b)^(1/(a+b));
+% h1     = ((1-a-b)/(chi)* rc/a) / (rc/a - dc - dc*kc1kc2^-1); % p. 204
+% h2     = h1/h1h2;
+% kc2ki2 = (di*ki1ki2 + di) / (bi *rc/(a*bi*p));
+% ki2    = (rc/(a*bc)* kc1kc2^(1-a)* ki1ki2^(-b) * h1^(a+b-1) * kc2ki2^(a-1) )^(1/(1-a-b));
+% kc2    = kc2ki2 * ki2;
+% ki1    = ki1ki2 * ki2;
+% kc1    = kc1kc2 * kc2;
[…]

### 2018-03-07 Code/oulton2010/parameters.m

@@ -1,0 +1,19 @@
+% PARAMETETRS - This function returns a parameter structure to use in the model solution.
+% Object is used for easier passsing of many input values to function. 
+%
+% usage
+%
+% param = parameters
+%
+% (No input arguments, file is just for storing values and creating object)
+
+function param = parameters()
+param.bet      = 0.95;  %Never call anything beta...it's a matlab function
+param.a        = 0.13;  % share of standard capital
+param.b        = 0.17; % share of IT capital
+param.gami     = 1.032; % growth rate of IT productivity
+param.gamc     = 1.00328;    % growth rate of cons. productivity
+param.di       = 0.124; %0.124; % depreciation rate of IT capital (Some work suggests 0.1830)
+param.dc       = 0.056; % depreciation rate of standard capital
+param.chi      = 1; % preference parameter in labor disutility.
+

### 2018-03-07 Code/oulton2010/stationarized.m

@@ -1,0 +1,44 @@
+%stationarized System. My notes p. 228
+f(1)    = -YC + (1+GAMC)*H1^(1-a-b)*KC1^(a)*KI1^(b);
+f(end+1)= -YI + (1+GAMI)*H2^(1-a-b)*KC2^(a)*KI2^(b);
+f(end+1)= -KC + KC1 + KC2;
+f(end+1)= -KI + KI1 + KI2;
+f(end+1)= -H + H1 + H2;
+f(end+1)= -KC_p*(1+G) + (1-dc)*KC + IC;
+f(end+1)= -KI_p*(1+GI)+ (1-di)*KI + IT; 
+f(end+1)= -YC + C + IC;
+f(end+1)= -YI + IT;
+f(end+1)= -W + C*chi;
+f(end+1)= -1 + bet*C/C_p*1/(1+G)*(RC_p + 1-dc);
+f(end+1)= -1 + bet*C/C_p*1/(1+G)*(RI_p/(1+GI_p) + 1-di);
+f(end+1)= -W + (1-a-b)*(1+GAMC)*H1^(-a-b)*KC1^(a)*KI1^(b);
+f(end+1)= -RC + a*(1+GAMC)*H1^(1-a-b)*KC1^(a-1)*KI1^(b);
+f(end+1)= -RI + b*(1+GAMC)*H1^(1-a-b)*KC1^(a)*KI1^(b-1);
+f(end+1)= -W + (1-a-b)*(1+GAMI)*(1+GP)*H2^(-a-b)*KC2^(a)*KI2^(b);
+f(end+1)= -RC + a*(1+GAMI)*(1+GP)*H2^(1-a-b)*KC2^(a-1)*KI2^(b);
+f(end+1)= -RI + b*(1+GAMI)*(1+GP)*H2^(1-a-b)*KC2^(a)*KI2^(b-1);
+f(end+1)= % GAMC
+f(end+1)= % GAMI
+f(end+1)= -GP + GAMC -GAMI; % eq. I p. 222
+f(end+1)= -G + ((1-b)*GAMC + b*GAMI)/(1-a-b);  % eq. II
+f(end+1)= -GI + ((a)*GAMC + (1-a)*GAMI)/(1-a-b);  % eq. III
+
+% steady state, starting at my notes p. 231, green equations.
+% need gamc and gami
+gp = gamc - gami; % eq. I p. 222
+g = ((1-b)*gamc + b*gami)/(1-a-b);  % eq. II
[…]

### 2018-03-09 Latex/Drafts/draft_13feb2018.tex
some work on the draft
for my Fed application… but at least the paper looks really neat :P

@@
 
-\title{Title}
+\title{IT as a GPT - Working Paper}
 \author{Marco Brianti, Laura G\'ati\thanks{%
@@
 The sluggish recovery of productivity after the Great Recession of 2008 has reignited interest in the factors behind long-run productivity.
-On the one hand, the literature in the wake of the seminal contribution of \cite{comin_gertler2006} interprets productivity fluctuations as medium-run business cycle phenomena, thus inviting the interpretation of the current productivity slowdown as a persistent, but transitory slump due to procyclical R\&D investment contracting during the bust.
+On the one hand, the literature in the wake of \cite{comin_gertler2006} interprets productivity fluctuations as medium-run business cycle phenomena.
+This reading invites thinking of the current productivity slowdown as a persistent, but transitory slump due to procyclical R\&D investment contracting during the bust.
 On the other hand, a glance at Figure \ref{fig_slowdowns} reveals that total factor productivity (TFP) dropped already before the 2008 recession.
@@
 GPTs are technologies whose main effect on productivity comes through changing the organization and the process of production.
-Thus they may be inputs to production themselves, but their fundamental contribution is as spillovers to aggregate production.\footnote{See for example \cite{bresnahan_trajtenberg1992}.} More specifically, we consider information technologies (IT), which has widely been claimed to be the main GPT since the 1990s.\footnote{See \cite{basu_etal2004}, \cite{brynjolfsson_etal1994} and \cite{allstar_paper} among many others.} Our main contribution is quantifying the extent to which IT investment can explain long-run fluctuations in TFP.
+Thus they may be inputs to production themselves, but their fundamental contribution is as spillovers to aggregate production.\footnote{This definition echoes that of \cite{bresnahan_trajtenberg1992}.} More specifically, we consider the information technologies (IT) sector, which has been widely claimed to be the main GPT since the 1990s.\footnote{See \cite{basu_etal2004}, \cite{brynjolfsson_etal1994} and \cite{allstar_paper} among many others.} Our main contribution is quantifying the extent to which IT investment can explain long-run fluctuations in TFP.
 We use a SVAR approach in which we identify a shock to IT investment and examine how much of the forecast error variance (FEV) of TFP our identified shock can account for.
 Our second contribution is providing an identification scheme for the IT investment shock in the presence of other shocks that at first glance seem observationally equivalent.
-Since our shock of interest contemporaneously effects the productivity of the IT sector and shows up in aggregate TFP with a lag\footnote{See \cite{david1989}.}, it bears strong resemblance to classical news shocks, which by definition have no contemporaneous effect on TFP, yet affect it over time.\footnote{This is the classical definition of the news shock literature in the wake of \cite{beaudry_portier2006}.} In order to make sure that our IT investment shock is not picking up the effects of news shocks, we propose an identification approach that identifies both shocks, thus disentangling them.
+Since our shock of interest contemporaneously effects the productivity of the IT sector and shows up in aggregate TFP with a lag\footnote{See \cite{david1989}.}, it bears strong resemblance to classical news shocks, which by definition have no contemporaneous effect on TFP, yet affect it over time.\footnote{This is the classical definition of news shocks prevalent in the news shocks literature, for example in \cite{beaudry_portier2006}.} In order to make sure that our IT investment shock is not picking up the effects of news shocks, we propose an identification approach that identifies both shocks, thus disentangling them.
 Applying our methodology to aggregate US data from 1989 to 2017, we obtain that IT investment shocks explain around 50\% of TFP fluctuations at long horizons, while news shocks account for around 20\%.
@@
 Our paper is most closely related to \cite{moran_queralto2017}, since that paper also uses SVAR analysis to assess the role of R\&D investment.
-However, while Moran \& Queralto focus on R\&D, our interest here is IT investment because of its role as a general purpose technology.
-Additionally, while Moran and Queralto recognize the identification problem that arises due to the similarity between their shock of interest and news shocks, they refrain from attempting to identify both shocks.
+However, while \cite{moran_queralto2017} focus on R\&D, our interest here is IT investment because of its role as a general purpose technology.
+Additionally, while \cite{moran_queralto2017} recognize the identification problem that arises due to the similarity between their shock of interest and news shocks, they refrain from attempting to identify both shocks.
 
@@
 \cite{bouakez_kemoe2017} and \cite{kurmann_sims2017} are similar to our paper in spirit because they argue that news shocks are not properly identified if there are measurement errors in TFP.
-Along these lines, \cite{crouzet_oh2014} consider fluctuations in inventories as variation that needs to purged from TFP in order to properly identify news shocks.
+Along these lines, \cite{crouzet_oh2016} consider fluctuations in inventories as variation that needs to purged from TFP in order to properly identify news shocks.
 Instead of measurement errors or inventories, we attribute the misidentification of news shocks to a general purpose technology, IT, spilling over into TFP.
@@
 \section{Model}
+The structural model used to illustrate our identification procedure displays two key features.
+The first one is that it is a two-sector model.
+This is obviously crucial in order to allow the IT sector to differ in meaningful ways from the rest of the economy.
+The second key element is that the production function of the final good incorporates a spillover effect from the stock of IT goods in the economy.
+Thus, essentially our theoretical model is a combination of a two-sector neoclassical growth model and an endogenous growth model \`a la \cite{romer1986}.
+The modeling of the two-sector element follows closely the approach taken in \cite{oulton2010}.
+
+There are two sectors in the economy.
+Sector 1 produces the final consumption good, $yc$, while sector 2 produces the IT good, $yi$.
+Both sectors employ labor, capital and IT goods to produce output using an identical production technology.
+The production functions are constant returns to scale of the standard Cobb-Douglas form:
+
+\begin{align}
+& yc_t = bc_t \; h1^{1-a-b} k1_t^a s1_t^b \\
+ & yi_t = bi_t  \; h2^{1-a-b} k2_t^a si1_t^b 
+\end{align}
+
+where $k$ signifies the capital stock, $s$ the stock of IT goods and the numbers denote in which sector the factor is employed in.
+$bc$ and $bi$ are the Solow-residuals of the two sectors.
+The assumption of spillovers from the stock of IT goods shows up in $bc$ as
+
+\begin{equation}
+bc_t  = \psi_t  s_t^\gamma
+\end{equation}
+
+where $\psi$ is a final-good specific exogenous technology process and $\gamma$ will be specified in more detail below. Market clearing requires
+
+\begin{align}
+& kc_t  = kc1_t + kc2_t \\
+& ki_t = ki1_t + ki2_t \\
+& h_t  = h1_t + h2_t 
+\end{align}
+
+The capital stock and the stock of IT goods evolve according to
+
+\begin{align}
+& kc_{t+1}  = (1-\delta_c )kc_t + ic_t \\
+& ki_{t+1}  = (1-\delta_i)ki_t + it_t 
+\end{align}
+
+where $\delta_j$ with $j = \{c,i\}$ are the rates of depreciation and $ic$ and $it$ are the respective flows. The income-expenditure equations are given by
+
+\begin{align}
+& yc_t = c_t + ic_t \\
+& yi_t = it_t 
+\end{align}
+
+signifying that the final good can be used for consumption and investment in capital, while all of the IT output is used as input in the accumulation of the IT stock.
+Thus, in this setting the IT good is a pure intermediate good.
+
+Firms in both sectors choose labor, capital and the amount of IT stock to use to maximize profits.
+Thus, in both sectors we obtain three first order conditions that are completely standard, The only difference between the two sectors is that their output is denominated using different prices.
+Therefore we now define the relative price of IT goods as $p_t = p^i_t / p^c_t$.
+Normalizing $p^c_t = 1$ allows us to consider only $p_t$ in what follows.
+
+To close the model, we consider a standard household that maximizes log utility from consumption and leisure subject to a budget constraint. The household problem then is
+
+\begin{align}
+& \max_{c_t, h_t, k_{t+1}, s_{t+1}} \sum_j \beta^j \left[ \text{ln} \;  c_{t+j} - \chi h_{t+j} \right] \\
+& \text{s.t.} \; \; c_t + k_{t+1} + p_t s_{t+1} = w_t h_t + rc_t k_t + ri_t s_t + (1-\delta_c)k_t + (1+ \delta_i)p_t s_t
+\end{align}
+
+where $rc$ and $ri$ are the rental rates of capital and of the IT good., and $w$ is the wage.
+This problem yields three first order conditions, where in relative prices again constitute a difference between the Euler equations of capital and IT goods.
+
+Let us now consider the behavior of this model in response to the following shocks: 1) classical news shocks 2) and IT investment shocks.
+The goal of the exercise here is to analyze how the model responds to these shocks and use those observations to work out our identification restriction.
+
 \label{sec_model}
@@
 \label{sec_empirics}
-Having rationalized our identification restriction, we now summarize our overall identification scheme and present the VAR that we run.
+Having rationalized our identification restriction, we now summarize our overall identification scheme and present the VAR.
 In order to identify the IT investment shock as well as a classical news shock, we proceed sequentially as follows.
@@
 On the other hand, even though we do not impose anything on the response of relative prices to the IT investment shock, we get a significantly negative response on impact which remains significant for about 20 quarters.
-This seems to confirm the validity of our identification restriction, since relative prices indeed move more following an IT investment shock than they do after a news shock.
+This seems to confirm the validity of our identification restriction, since relative prices indeed move more following an IT investment shock than they do after a news shock in the unrestricted domain.
 
@@
 The striking result is that the IT investment shock alone is able to explain almost 53\% of long-run TFP variation!
-One the one hand, this means that some of the explanatory power of the news shock should actually be attributed to the IT shock, so we are indeed doing a correct cleaning of the news shock from elements that come from a different channel.
+On the one hand, this means that some of the explanatory power of the news shock should actually be attributed to the IT shock, so we are indeed doing a correct cleaning of the news shock from elements that come from a different channel.
 On the other hand, the IT investment shock is also picking up explanatory power above and beyond that purged from the news shock.
@@
 
-By definition, since we have shut off negative IT investment shocks, the counterfactual TFP series, represented by the red line, are above the original blue series.
+By definition, since we have shut off negative IT investment shocks, the counterfactual TFP series, represented by the red line, is above the original blue series.
 The notable feature of this graph, however, is that the two lines really start to diverge around 2005, around 12 quarters after the Dotcom bubble burst in 2002.
-As the impulse responses from the VAR indicate, it takes about 10 quarters for the IT investment shock to show up as significant response in TFP.
+As the impulse responses from the VAR indicate, it takes about 10 quarters for the IT investment shock to show up as a significant response in TFP.
 Thus the counterfactual is suggesting that the large divergence between original and constructed series come from the sizable negative IT investment shock that hit during the Dotcom crash.

### 2018-03-14 Latex/Drafts/draft_13feb2018.tex
work on spillover in model

@@
 This is obviously crucial in order to allow the IT sector to differ in meaningful ways from the rest of the economy.
-The second key element is that the production function of the final good incorporates a spillover effect from the stock of IT goods in the economy.
+The second key element is that the production function of the final good incorporates a spillover effect from the stock of IT goods in the final goods production.
 Thus, essentially our theoretical model is a combination of a two-sector neoclassical growth model and an endogenous growth model \`a la \cite{romer1986}.
@@
 There are two sectors in the economy.
-Sector 1 produces the final consumption good, $yc$, while sector 2 produces the IT good, $yi$.
+Sector 1 consists of a unity mass of firms producing the final consumption good, $yc(j)$, where $j$ indexes each firm.
+Sector 2 produces the IT good, $yi$.
 Both sectors employ labor, capital and IT goods to produce output using an identical production technology.
@@
 \begin{align}
-& yc_t = bc_t \; h1^{1-a-b} k1_t^a s1_t^b \\
- & yi_t = bi_t  \; h2^{1-a-b} k2_t^a si1_t^b 
+& yc_t(j) = BC_t(j) \; h_1(j)^{1-a-b} k_{1,t}(j)^a s_{1,t}(j)^b \\
+ & yi_t = bi_t  \; h_2^{1-a-b} k_{2,t}^a si_{2,t}^b 
 \end{align}
@@
 where $k$ signifies the capital stock, $s$ the stock of IT goods and the numbers denote in which sector the factor is employed in.
-$bc$ and $bi$ are the Solow-residuals of the two sectors.
-The assumption of spillovers from the stock of IT goods shows up in $bc$ as
+$BC$ and $bi$ are the Solow-residuals of the two sectors.
+The assumption of spillovers from the stock of IT goods shows up in $BC$ as
 
 \begin{equation}
-bc_t  = \psi_t  s_t^\gamma
+BC_t  = bc_t  s_{1,t}^\gamma
 \end{equation}
 
-where $\psi$ is a final-good specific exogenous technology process and $\gamma$ will be specified in more detail below. Market clearing requires
+where $bc$ is a final-good specific exogenous technology process (the analogy of $bi$ for the final-good sector) and $\gamma$ captures the intensity of the spillover.
+Key here is that while an individual final-goods firm $j$ considers $BC_t$ to be exogenous when optimizing over $ki_{1,t}$, aggregating the final-goods production function over $j$ and substituting in for $BC_t$ yields
+
+\begin{equation}
+yc_t = bc_t \; s_{1,t}^\gamma \; h_1^{1-a-b} k_{1,t}^a s_{1,t}^b 
+\end{equation}
+
+This is the sense in which the stock of IT capital employed in final goods production spills over to aggregate productivity.
+A balanced growth path requires $\gamma \leq 1-b$, so that the production function does not exhibit increasing returns to scale.
+The interesting case that we investigate here is when $\gamma = 1-b$, because then the production function assumes an AK-form in the stock of IT capital in the final-goods sector.
+Thus, the spillover from the IT stock generates endogenous growth here, in line with the interpretation of IT goods as general purpose technologies.
+
+Market clearing in the two-sector economy requires
 
 \begin{align}
-& kc_t  = kc1_t + kc2_t \\
-& ki_t = ki1_t + ki2_t \\
-& h_t  = h1_t + h2_t 
+& kc_t  = kc_{1,t} + kc_{2,t} \\
+& ki_t = ki_{1,t} + ki_{2,t} \\
+& h_t  = h_{1,t} + h_{2,t} 
 \end{align}
@@
 Firms in both sectors choose labor, capital and the amount of IT stock to use to maximize profits.
-Thus, in both sectors we obtain three first order conditions that are completely standard, The only difference between the two sectors is that their output is denominated using different prices.
-Therefore we now define the relative price of IT goods as $p_t = p^i_t / p^c_t$.
-Normalizing $p^c_t = 1$ allows us to consider only $p_t$ in what follows.
+Thus, in both sectors we obtain three first order conditions that are completely standard.
+The only difference between the two sectors is that their output is denominated using different prices.
+Therefore we now define the relative price of IT goods as $p_t = pi_t / pc_t$.
+Normalizing $pc_t = 1$ allows us to consider only $p_t$ in what follows.
 
@@
 
-where $rc$ and $ri$ are the rental rates of capital and of the IT good., and $w$ is the wage.
-This problem yields three first order conditions, where in relative prices again constitute a difference between the Euler equations of capital and IT goods.
+where $rc$ and $ri$ are the rental rates of capital and of the IT good, and $w$ is the wage.
+This problem yields three first order conditions, where relative prices again constitute a difference between the Euler equations of capital and IT goods.
 

### 2018-03-14 Code/oulton2010/model_spillover.m

@@ -1,0 +1,103 @@
+% MODEL_LINEAR - Linearized version of the simple RBC model example from 
+% EC860.
+%
+% usage:
+%
+% [fy, fx, fyp, fxp] = model(param)
+%
+% where
+%
+% param = a parameters object, created in parmeters.m
+%
+% NOTES: This program, which generates the model matrices in cannonical form,
+%        requires the MATLAB symbolic toolbox! The algorithm used to solve 
+%        the model, however, is numerical and requires no m-files
+%        beyond those that appear in this directory.
+%
+% Code by Ryan Chahrour, Boston College, 2014
+ 
+% This is OULTON 2010 WITH GROWTH
+
+function [fyn, fxn, fypn, fxpn] = model_spillover(param)
+
+%Steady State
+[ss, param] = model_spillover_ss(param);
+
+%Declare parameters
+bet      = param.bet;  %Never call anything beta...it's a matlab function
+a        = param.a; % share of standard capital
+b        = param.b; % share of IT capital
+gami     = param.gami; % growth rate of equipment productivity
+gamc     = param.gamc;    % growth rate of neutral technology
+di       = param.di; % depreciation rate of capital IT
+dc       = param.dc; % depreciation rate of capital standard
+chi      = param.chi; % preference parameter.
+gam      = param.gam; % spillover elasticity
+
+%Declare Needed Symbols
+syms KC KI KC1 KC2 KI1 KI2 % 6 vars
+syms KC_p KI_p KC1_p KC2_p KI1_p KI2_p 
+syms GAMC GAMI G GI GP % 5 vars
+syms GAMC_p GAMI_p G_p GI_p GP_p
+syms YC YI C IC IT W RC RI H H1 H2 % 11 vars
+syms YC_p YI_p C_p IC_p IT_p W_p RC_p RI_p H_p H1_p H2_p  % -> 22 vars
+
+%Declare X and Y vectors
[…]

### 2018-03-14 Code/oulton2010/model_spillover_ss.m

@@ -1,0 +1,61 @@
+% MODEL_SS - Return the steady state of the model (computed analytically)
+%
+% usage:
+% 
+% [ss, param] = model_ss(param)
+% STEADY STATE OF OULTON 2010 WITH GROWTH
+
+function [ss,param] = model_spillover_ss(param)
+
+%Parameters from param object
+bet      = param.bet;  %Never call anything beta...it's a matlab function
+a        = param.a; % share of standard capital
+b        = param.b; % share of IT capital
+gami     = param.gami; % growth rate of equipment productivity
+gamc     = param.gamc;    % growth rate of neutral technology
+di       = param.di; % depreciation rate of capital IT
+dc       = param.dc; % depreciation rate of capital standard
+chi      = param.chi; % preference parameter.
+gam      = param.gam; % spillover elasticity
+
+%Use closed form expressions for the ss values. 
+% starting at my notes p. 231, green equations.
+gp = gamc - gami; % eq. I p. 222
+g = ((1-b -gam)*gamc + (gam+b)*gami)/(1-a-b -gam);  % eq. Ialt
+gi = ((a)*gamc + (1-a)*gami)/(1-a-b -gam);  % eq. IIIalt
+
+rc = (1+g)/bet - (1-dc); % green 1
+ri = ((1+g)/bet -(1-di)*(1+gp)); % yellow 2
+
+% Purple suggestion instead of orange one
+ki1_h1  = (b/ri)^((1-a)/(1-a-b)) *(a/rc)^(a/(1-a-b)) * (1+gamc)^(1/(1-a-b)); %purple 1
+kc1_h1  = (a*(1+gamc)/rc)^(1/(1-a)) *ki1_h1^(b/(1-a)); % purple 2
+w       = (1-a-b)*(1+gamc)*kc1_h1^(a) * ki1_h1^(b); % purple 3
+kc2_h2  = (a/rc)^((1-b)/(1-a-b)) * (b/ri)^(b/(1-a-b)) *((1+gami)*(1+gp))^(1/(1-a-b)); % purple 4 = orange 1
+ki2_h2  = (b/ri * (1+gami)*(1+gp))^(1/(1-b))*(kc2_h2)^(a/(1-b)); % purple 5 = orange 2
[…]

### 2018-03-14 Code/oulton2010/parameters.m

@@ -16,4 +16,5 @@ param.gamc     = 1.00328-1; %1.00328;    % growth rate of cons. productivity
 param.di       = 0.124; %0.124; % depreciation rate of IT capital (Some work suggests 0.1830)
 param.dc       = 0.056; %0.056 depreciation rate of standard capital
 param.chi      = 1; % preference parameter in labor disutility. (From Ryan)
+param.gam      = 1; % spillover elasticity (only used in model_spillover.m and model_spillover_ss.m)
 

### 2018-04-03 Latex/Interpretation_Theoretical_IRFs/Interpretation_Theoretical_IRFs.tex
starting a document for the interpretation of theoretical IRFs

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[a4paper,top=3.5cm,bottom=3.5cm,left=3.5cm,right=3.5cm,%
bindingoffset=0mm]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newenvironment{proof}[1][Proof]{\begin{trivlist}
		\item[\hskip \labelsep {\bfseries #1}]}{\end{trivlist}}
\newcommand{\qed}{\nobreak \ifvmode \relax \else
	\ifdim\lastskip<1.5em \hskip-\lastskip
	\hskip1.5em plus0em minus0.5em \fi \nobreak
	\vrule height0.75em width0.75em depth0em\fi}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{rotating}
\usepackage{float}
\linespread{1.3}
\raggedbottom

%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\R}{\mathbb{R}}
\DeclareMathOperator{\E}{\mathbb{E}}
%

\title{Theoretical Impulse Response Functions}
\author{Marco Brianti\\Laura Gati}
\date{October 2017}

\begin{document}

	\maketitle

	\section{Zero Balanced-Growth Path}

	Define $x_t$ as the value of variable $x$ at time $t$. Define $\overline{x}$ as the value of variable $x$ in steady state. Impulse response functions are percentage deviation of $x$ from its steady state value $\overline{x}$. Formally,
$$
IRF(x_t | \varepsilon) = \log \bigg( \frac{x_t}{\overline{x}}  \bigg)
$$
where $\varepsilon$ is a general perturbation from the steady state level of the system. As long as $\varepsilon$ has a transitory nature, we expect IRFs to converge to zero asymptotically. In other words, we expect that the system will naturally converge to the steady state level once the perturbation ceases.

\section{Positive Balanced-Growth Path - Temporary Shock}

Define $x_t$ as the value of variable $x$ at time $t$. Define $\tilde{x}_t$ as the value of $x$ when divide by the value of an exogenous process which is growing at the same rate of $x$. Formally,
$$
\tilde{x}_t = \frac{x_t}{G_{t-1}}
$$
where $G_{t-1}$ may represent the value of the exogenous productivity process which is growing at the same rate of $x$. Define $\tilde{x}$ as the value of $\tilde{x_t}$ when the system is growing at the balanced growth at the BGP without any past or present source of perturbation. In this case, impulse response functions are percentage deviation of $\tilde{x}_t$ from its steady state value $\tilde{x}$. Formally,
\begin{eqnarray}
\begin{aligned}
IRF(\tilde{x}_t | \varepsilon) &= \log \bigg( \frac{\tilde{x}_t}{\tilde{x}}  \bigg)  \\
                               &= \log \bigg( \frac{\frac{x_t(\varepsilon)}{G_{t-1}}}{\frac{x_t}{G_{t-1}}}  \bigg)  \\
                               &= \log \bigg( \frac{x_t(\varepsilon)}{x_t} \bigg)  \\
\end{aligned}
\end{eqnarray}
In other words, we can interpret $IRF(\tilde{x}_t | \varepsilon)$ as percentage deviation of $x_t$ from the value it should have had without $\varepsilon$. Also in this case we expect IRFs to converge to zero asymptotically. In other words, we expect $x_t(\varepsilon)$ to converge back to $x_t$ once the perturbation ceases.

\section{Positive Balanced-Growth Path - Permanent Shock}

\end{document}

### 2018-04-03 Latex/Interpretation_Theoretical_IRFs/Interpretation_Theoretical_IRFs.tex
More work on IRFs latex

@@
 
-\section{Positive Balanced-Growth Path - Temporary Shock}
+\section{Positive Balanced-Growth Path - Level Shock}
 
@@
 
-\section{Positive Balanced-Growth Path - Permanent Shock}
+\section{Positive Balanced-Growth Path - Trend Shock}
+
+Define $x_t$ as the value of variable $x$ at time $t$. Define $\tilde{x}_t$ as the value of $x$ when divide by the value of an exogenous process which is growing at the same rate of $x$. Formally,
+$$
+\tilde{x}_t = \frac{x_t}{G_{t-1}}
+$$
+where $G_{t-1}$ may represent the value of the exogenous productivity process which is growing at the same rate of $x$.
+Define $\tilde{x}$ as the value of $\tilde{x}_t$ when the system is growing at the balanced growth at the BGP without any past or present source of perturbation.
+In this case, impulse response functions are percentage deviation of $\tilde{x}_t$ from its steady state value $\tilde{x}$.
+Formally,
+\begin{eqnarray}
+\begin{aligned}
+IRF(\tilde{x}_{t+h} | \varepsilon) &= \log \bigg[ \Pi_{i=0}^h \bigg( \frac{\tilde{x}_{t+i}(\varepsilon)}{\tilde{x}_{t+i-1}(\varepsilon)}  \frac{G_{t+i-1}}{G_{t+i-2}}  \bigg) \bigg]  \\
+&= \log \Bigg[ \Pi_{i=0}^h \Bigg( \frac{\frac{x_{t+i}(\varepsilon)}{G_{t+i-1}(\varepsilon)}}{\frac{x_{t+i-1}(\varepsilon)}{G_{t+i-2}(\varepsilon)}}  \frac{G_{t+i-1}(\varepsilon)}{G_{t+i-2}(\varepsilon)}  \Bigg) \Bigg]  \\
+&= \log \Bigg[ \Pi_{i=0}^h \Bigg( \frac{x_{t+i}(\varepsilon)}{x_{t+i-1}(\varepsilon)}   \Bigg) \Bigg]  \\
+&= \log \bigg( \frac{x_{t+h}(\varepsilon)}{x_{t-1}}  \bigg)  \\
+\end{aligned}
+\end{eqnarray}
 

### 2018-04-03 Code/oulton2010/main_prog.m

@@ -16,7 +16,6 @@ addpath(base_path)
 %Load Parameters
 param = parameters;
 
-return
 %% Correctly stationarized model w/o spillover
 %Compute the first-order coefficiencients of the model
 [fyn, fxn, fypn, fxpn] = model_exog_stat(param);
@@ -54,7 +53,7 @@ end
 IRFs = IRFs_all(gamc_idx:njumps,:,:);
 IRFs_some = IRFs_all([c_idx, gamc_idx],:,:);
 
-which_shock = [pos_KI];
+which_shock = [pos_BIGGAMC];
 shocknames = {'Hard capital shock', 'IT capital shock', 'Growth rate of Final', 'Growth rate of IT'};
 % GAMC_p GAMKI_p GAMYC_p GAMYI_p GAMH_p GAMP_p GAMKC2_p GAMKI2_p
 varnames = {'Logdev C', 'Logdev KI', 'Logdev YC', 'Logdev YI', 'Logdev H', 'Logdev P', 'Logdev KC2', 'Logdev KI2' };
@@ -81,6 +80,8 @@ save('gxhx.mat', 'gx', 'hx')
 %Eigenvalues of hx
 disp('Computing eigenvalues of hx');
 disp(eig(hx))
+
+fghjk
 
 return
 

### 2018-04-12 Code/oulton2010/model_exog_stat_ss.m
s.s. with spillover has been implemented. Error are to the -8/-9. it should be just a numerical issue...no more than that

@@ -76,4 +76,6 @@ xx  = [kc ki biggamc biggami c ki biggamc biggami yc yi h p kc2 ki2];
 yy  = [yc yi c ic it w rc ri h h1 h2 kc1 kc2 ki1 ki2 p expg expgi expg expgi 1 p expg expgi];
 % YC YI C IC IT W RC RI H H1 H2 KC1 KC2 KI1 KI2 P
 
+
+
 ss  = [yy xx];

### 2018-04-12 Code/oulton2010/model_spillover.m

@@ -55,10 +55,10 @@ Y  = [YC YI C IC IT W RC RI H H1 H2 KC1 KC2 KI1 KI2 P EXPGC EXPGI]; % vector of 
 YP = [YC_p YI_p C_p IC_p IT_p W_p RC_p RI_p H_p H1_p H2_p KC1_p KC2_p KI1_p KI2_p P_p EXPGC_p EXPGI_p] ;
 
 % Model Equations 
-f(1)    = -YC + KI^gam * (BIGGAMC)*H1^(1-a-b)*KC1^(a)*KI1^(b); %
-f(end+1)= -YI + KI^gam *(BIGGAMI)*H2^(1-a-b)*KC2^(a)*KI2^(b); %
+f(1)    = -YC + KI^gam * (BIGGAMC)*H1^(1-a-b)*KC1^(a)*KI1^(b); 
+f(end+1)= -YI + KI^gam *(BIGGAMI)*H2^(1-a-b)*KC2^(a)*KI2^(b); 
 f(end+1)= -KC + KC1 + KC2;
-f(end+1)= -KI + KI1 + KI2;
+f(end+1)= -KI + KI1 + KI2; %
 f(end+1)= -H + H1 + H2;
 f(end+1)= -EXPGC + BIGGAMC^((1-b-gam)/(1-a-b-gam))*BIGGAMI^((b+gam)/(1-a-b-gam));
 f(end+1)= -EXPGI + BIGGAMC^(a/(1-a-b-gam))*BIGGAMI^((1-a)/(1-a-b-gam));

### 2018-04-12 Code/oulton2010/model_spillover_ss.m

@@ -19,50 +19,104 @@ chi      = param.chi; % preference parameter.
 gam      = param.gam; % spillover elasticity
 
 %Use closed form expressions for the ss values. 
-% My notes p. 289-292
-p  = (biggamc)/(biggami); % p. 291
-expgc = biggamc^((1-b-gam)/(1-a-b-gam))*biggami^((b+gam)/(1-a-b-gam));
-expgi = biggamc^(a/(1-a-b-gam))*biggami^((1-a)/(1-a-b-gam));
-gc  = expgc - (1-dc); 
-gi = expgi - (1-di);
-rc = 1/bet * expgc - (1-dc); % p. 289
-ri = (1/bet* expgi -(1-di))*p; 
 
-% What we do know: from Marco's notes and from FOCs simply.
-ki_kc = b/a*rc/ri;
-w_ki = (1-a-b)/b*ri;
+%Step 0 - always run it!
+p        = (biggamc)/(biggami); 
+expgc    = biggamc^((1-b-gam)/(1-a-b-gam))*biggami^((b+gam)/(1-a-b-gam));
+expgi    = biggamc^(a/(1-a-b-gam))*biggami^((1-a)/(1-a-b-gam));
+gc       = expgc - (1-dc); 
+gi       = expgi - (1-di);
+rc       = 1/bet * expgc - (1-dc); 
+ri       = (1/bet* expgi -(1-di))*p; 
 
+%Step 1
+kc          = @(wx) wx/rc*a/(1-a-b); %kc = kc1 = kc2 = Kc/h = Kc1/h1 = Kc2/h2
+ki          = @(wx) wx/ri*b/(1-a-b); %ki = ki1 = ki2 = Ki/h = Ki1/h1 = Ki2/h2
+Ki          = @(wx) (rc/(a*biggamc)*kc(wx)^(1-a)*ki(wx)^(-b))^(1/gam);
+Ki_check    = @(wx) (ri/(b*biggamc)*kc(wx)^(-a)*ki(wx)^(1-b))^(1/gam); %check 
+Ki_check2   = @(wx) (wx/((1-a-b)*biggamc)*kc(wx)^(-a)*ki(wx)^(-b))^(1/gam); %check
[…]

### 2018-04-12 Code/oulton2010/main_prog.m
Formally added the s.s. solution procedure

@@ -99,8 +99,8 @@ disp(eig(hx_v))
 
 % IRFs
 % Positions of the shocks in shock vector:
-nvar = size(gx_v,1) + size(gx_v,2);
-nshocks = size(hx_v,1);
+nvar = size(gx,1) + size(gx,2);
+nshocks = size(hx,1);
 pos_KC = 1; % shock to K stock
 pos_KI = 2; % shock to IT stock
 pos_GAMC = 3; % a shock to TFP in final goods prod (= surprise tech shock)

### 2018-04-12 Code/oulton2010/model_spillover_ss.m

@@ -56,8 +56,6 @@ end
 Ki1 = @(wx) ki(wx)*h1(wx);
 Kc1 = @(wx) kc(wx)*h1(wx);
 
-%Error is above this point
-
 %Step 4
 h = @(wx) h1(wx) + h2(wx);
 Kc = @(wx) Kc1(wx) + Kc2(wx);

### 2018-04-26 Latex/Slides_Presenter_April2018/dw23jan2018.tex
Preparing slides for the macro reading presenter

--- 2018-01-30 Latex/Dissertation_Workshop_23Jan2018/dw23jan2018.tex
@@
 
-\date{January 23, 2018}
+\date{April 26, 2018}
 
@@
 	\begin{itemize}
-	\item The neoclassical tradition (RBC literature) in macro has treated total factor productivity (TFP) as exogenous, working against endogenous growth models
-
-	(King \& Rebelo 1999, Christiano, Eichenbaum \& Trabandt 2014, 2018, vs. e.g. Romer 1990)
-
-	\
 
@@
 
+	\item However, an increase in IT investment affects TFP with some delays. Therefore this shock is likely to look very similar to a standard news shock.
+
 	\end{itemize}
@@
 \begin{frame}
-	\frametitle{Motivation II}
+	\frametitle{Motivation}
 
 	\begin{itemize}
-	\item Our main analysis is estimating a structural VAR in which we identify a shock to the exogenous component of future TFP (a news shock) and a shock to the endogenous component of TFP (a shock to IT productivity, hereafter ``IT shock").
+	\item Our main analysis is estimating a structural VAR in which we identify a shock to the exogenous component of future TFP (hereafter \textit{news shock}) and a contemporaneous shock which incentivizes investment in information and technology stock (hereafter \textit{IT shock}).
 
@@
 
-	\item Along the way, we provide a solution to an econometric challenge in the literature on long-run productivity.
+    \item As a support for our identification we design a 2-sector general equilibrium model which features both investment in IT and news shocks.
+
+	\end{itemize}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+\frametitle{Preview of the Results}
+
+\begin{itemize}
+	\item IT shocks drive about half of long-run TFP fluctuations in our sample.
+
+	\
+
+	\item News shocks drive approximately one fifth $\Rightarrow$ Still relevant but - once appropriately cleaned from IT shocks - less important then found previously in the literature.
+
+	\
+
+	\item Our structural model points out that relative prices can be used to disentangle the two.
 
@@
 \begin{frame}
-	\frametitle{Our starting point: Barsky \& Sims (2011)}
-	\label{BS_quote}
-
-BS identify news shocks as shocks that maximize future fluctuations in TFP. But they warn:
-
-	\
-
-\blockquote{\emph{A more general objection to our empirical approach would be that a number of structural shocks, which are not really ``news'' in the sense defined by the literature, might affect a measure of TFP in the future without impacting it immediately.
-Among these shocks might be research and development shocks, investment specific shocks, and reallocative shocks.
-Our identification (and any other existing VAR identifications) would obviously confound any true news shock with these shocks.}}
-
-\
-
-\hspace{5cm} Barsky \& Sims (2011), p. 278.
-
-\
-
-$\rightarrow$ We focus on a specific subset of shocks which are ``not really `news''': shocks to the productivity of the sector that produces IT goods.
-
-%\hyperlink{BS_FEV}{\beamerbutton{Barsky \& Sims' FEV-table}}	
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
 	\frametitle{Related literatures}
@@
 \begin{frame}
-	\frametitle{A toy model}
-
-	How should we think of this IT productivity shock?
-
-	\
-
-	\
-
-	\
-
-	Contextualize using a simple expanding variety model (Romer 1990)
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Expanding variety model}
-	\label{expanding_variety}
-
-Final good $Y_t$ is the CES aggregate of a number $A_t$ intermediate goods $Y_t^M(s)$:	% theta is between 0 and infinity
-	\begin{equation}
-	Y_t = \Big[ \int_{0}^{A_t} Y_t^M(s)^{\frac{\theta-1}{\theta} } ds \Big]^{\frac{\theta}{\theta-1}}
-	\end{equation}
-
-\pause
-
-Intermediate good $s$ is Cobb-Douglas with exogenous TFP $\Psi_t$:
-\begin{equation}
-Y^M_t(s) = \Psi_t K_t(s)^{\alpha}L_t(s)^{1-\alpha}
-\end{equation}
-
-\pause
-
-$\rightarrow$ letting $K_t$ and $L_t$ be aggregate capital and labor, final output is:
-\begin{equation}
-Y_t = A_t^{\frac{1}{\theta-1}} \Psi_t K_t^{\alpha}L_t^{1-\alpha}
-\end{equation}
-
-\pause
-
-IT sector is a separate sector that uses IT investment and its own sectoral productivity $\lambda_t$ to expand $A_t$.  \hyperlink{it_sector}{\beamergotobutton{IT sector in detail}}
-
-$\rightarrow$ IT sector is driven by profits from selling the IT good, but its advances spill over to aggregate TFP.
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{The shocks}
-
-\begin{equation*}
-Y_t \; = \underbrace{A_t^{\frac{1}{\theta-1}}}_\text{endogenous TFP} \; \; \underbrace{\Psi_t}_\text{exogenous TFP} \; K_t^{\alpha}L_t^{1-\alpha}
-\end{equation*}
-
-\
-
-\
-
-$\hookrightarrow$ A news shock is $\Psi_{t+k} \uparrow$ for some $k>0$
-
-\
-
-$\hookrightarrow$ An IT productivity shock is $\lambda_t \uparrow$, which shows up in $A_{t+j} \uparrow$ with a lag $j>0$
-
-\
-
-So in this model, the innovation to TFP at period $t$ is:
-\begin{equation}
-\epsilon^{TFP}_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{f(IT_{t-j})}_\text{IT productivity shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
-\end{equation}
-
-Crucially, both lead to an increase in future TFP, with no effect on impact.
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
 	\frametitle{Identification: relative prices}
@@
 \begin{itemize}
-\item News shock makes all sectors of the economy more productive $\rightarrow$ impacts the sectoral price $P^{IT}$ as well as P $\Rightarrow$ relative prices do not move.
-\item IT productivity shock makes only the IT sector more productive $\rightarrow$ impacts the sectoral price $P^{IT}$ \textbf{only} $\Rightarrow$ relative prices move! 
+\item As long as the technology improvement heralded by the news shock does not realize, relative prices should not move.
+\item An increase in IT productivity shock makes only the IT sector more productive $\rightarrow$ impacts the sectoral price $P^{IT}$ \textbf{only} $\Rightarrow$ relative prices move! 
 \end{itemize}

### 2018-05-12 Latex/Meeting_Ryan_14May_2018/Meeting.tex
Creating figures for our meeting with Ryan of May 14
Figures we created:
1. IRFs from the “just IT” VAR
2. IRFs from the structural model for the noise shock
We also added base_path as an argument for the figure generation in
both cases, just so you know.

--- 2018-04-26 Latex/Slides_Presenter_April2018/dw23jan2018.tex
@@
 
-\title{IT Spillovers in Long-Run TFP \\ A SVAR Approach}
+\title{IT Spillovers in TFP }
 
-\date{April 26, 2018}
+\date{\today}
 
@@
 \begin{frame}
-	\frametitle{Motivation}
+\frametitle{Topics of today's discussion}
 
-	\begin{itemize}
-
-	\item The Great Recession 2008 revived interest in endogenous components in TFP for explaining long-run TFP fluctuations.
+\begin{enumerate}
+\item L'Huillier's structure-related comment: disentangling news shocks is just a robustness check
 
@@
 
-	\item[] $\rightarrow$ We explore the possibility that general-purpose technologies (GPT), in particular for the last 30 years information technologies (IT), play a role in explaining TFP fluctuations at long horizons.
+\item $\hookrightarrow$ taking up on that, a ``just IT'' identification in the VAR
 
@@
 
-	\item However, an increase in IT investment affects TFP with some delays. Therefore this shock is likely to look very similar to a standard news shock.
-
-	\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Motivation}
-
-	\begin{itemize}
-	\item Our main analysis is estimating a structural VAR in which we identify a shock to the exogenous component of future TFP (hereafter \textit{news shock}) and a contemporaneous shock which incentivizes investment in information and technology stock (hereafter \textit{IT shock}).
-
-	\
-
-	\
-
-    \item As a support for our identification we design a 2-sector general equilibrium model which features both investment in IT and news shocks.
-
-	\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-\frametitle{Preview of the Results}
-
-\begin{itemize}
-	\item IT shocks drive about half of long-run TFP fluctuations in our sample.
-
-	\
-
-	\item News shocks drive approximately one fifth $\Rightarrow$ Still relevant but - once appropriately cleaned from IT shocks - less important then found previously in the literature.
-
-	\
-
-	\item Our structural model points out that relative prices can be used to disentangle the two.
-
-\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{VARs - A quick recap}
-	\label{identification}
-
-Structural Form	
-\begin{equation}
-(\mathbf{AD})^{-1}
-    \mathbf{X_{t}}
-= \mathbf{C(L)} 
-\mathbf{X_{t-1}}
-+ \mathbf{s_t}
-\end{equation}
-
-\
-
-\
-
-Reduced Form
-\begin{equation}
-\mathbf{X_{t}}
-= \underbrace{\mathbf{AD} \mathbf{C(L)}}_\text{$\mathbf{B(L)}$} 
-\mathbf{X_{t-1}}
-+ \underbrace{\mathbf{AD} \mathbf{s_t}}_\text{$\mathbf{i_t}$}
-\end{equation}
-
-\
-
-\
-
-\begin{itemize}
-	\item $AD$ is the impact matrix
-	\item $A$ is s.t. $As_t s_t' A' = i_t i_t' = \Sigma$ and $s_t s_t' = I$
-	\item $D$ is a rotation matrix s.t. $DD' = I$ $\Rightarrow$ $AD(AD)' = \Sigma$
-\end{itemize}
-
-We impose our identifying assumptions on the matrix $D$. \hyperlink{Technicalities}{\beamergotobutton{Technicalities}}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Related literatures}
-	\label{related_lit}
-\begin{itemize}
-\item One strand of literature: Exogenous TFP and news shocks
-	\begin{itemize}
-	\item Beaudry \& Portier (2006)
-	\item Barsky \& Sims (2011)
-
-	\end{itemize}
-\item [] \textbf{Our contribution: allow in this setting the existence of an endogenous mechanism that affects future TFP}
-
-	\
-
-	\
-
-\item Another strand of literature: Endogenous TFP with R\&D investment as the key variable
-	\begin{itemize}
-	\item Comin \& Gertler (2006)
-	\item Moran \& Queralto (2017)
-	\item Guerron \& Jinnai (2014)
-
-	\end{itemize}
-
-\item []  \textbf{Our contribution: provide what we think is a more convincing test for the endogenous mechanism}
-
-\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Identification: relative prices}
-
-Let $P$ be the price level (price of final good), $P^{IT}$ the price of the IT good and relative prices be $P^{IT}/P$.
-
-\
-
-Intuition:
-\begin{itemize}
-\item As long as the technology improvement heralded by the news shock does not realize, relative prices should not move.
-\item An increase in IT productivity shock makes only the IT sector more productive $\rightarrow$ impacts the sectoral price $P^{IT}$ \textbf{only} $\Rightarrow$ relative prices move! 
-\end{itemize}
-
-\
-
-$\Rightarrow$ identifying restriction: news shock does not move relative prices.
-\newline Accounting for price rigidities: news shock does not move relative prices after price adjustment has taken place (6-12 quarters).
-
-\
-
-Similar identification scheme: Fisher 2006.
-
-%The price level $P$ is an aggregate of the prices intermediate goods. These are determined as an FOC to 
-%\begin{equation*}
-%Y_t(s) = \Psi_t K_t(s)^{\alpha}L_t(s)^{1-\alpha}
-%\end{equation*}
-%
-%\hspace{5cm} $\hookrightarrow P$ is a function of $\Psi_t$ 
-%
-%\
-%
-%The price of IT good, $P^{IT}$, is determined as an FOC to
-%
-%\begin{equation}
-%V_{i,t} = \lambda_t \Psi_t f(S_{i,t})
-%\end{equation}
-%
-%
-%\hspace{5cm}  $\hookrightarrow P^{IT}$ is a function of $\Psi_t$ \textbf{and} $\lambda_t$	
-%
-%\
-%
-%$\Rightarrow$ The two shocks imply different responses of relative prices $\frac{P^{IT}}{P}$!
-%
-%\begin{itemize}
-%\item A news shock moves both $P$ and $P^{IT}$, leaving relative prices unchanged.
-%\item An IT productivity shock moves only $P^{IT}$, thus changing relative prices.
-%\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Identification strategy overall}
-
-Recall that the innovation in TFP at time $t$ is:
-
-\begin{equation*}
-\epsilon^{TFP}_t =   \underbrace{V_{t-k}}_\text{news shock} + \underbrace{f(IT_{t-j})}_\text{IT productivity shock}  + \underbrace{\varepsilon_t}_\text{surprise tech shock} 
-\end{equation*}
-
-\
-
-    \begin{enumerate}
-    	\item The news shock $V_{t-k}$ maximizes the FEV of future TFP, with a zero impact effect, subject to the restriction that it has no effect on the relative price $RP$ at a small number of quarters;
-
-	\
-
-    \item The IT productivity shock maximizes the remaining FEV of future TFP, with a zero impact effect;
-
-    \
-
-    \item The tech shock $\varepsilon_t$ is considered as a residual shock and is left unrestricted (unidentified).
+\item the structural model: implementing a noise shock
 \end{enumerate}
@@
 \begin{frame}
-	\frametitle{Empirical analysis}
+\frametitle{2) ``Just IT'' identification}
 
-	We run a SVAR using aggregate, quarterly US data. The data vector is:
+A rotation of shocks that maximizes the impact effect on IT investment s.t. a 0 impact response on TFP.
+\end{frame}
 
-	\begin{equation}
-	\mathbf{X_t} = 
-	\begin{bmatrix}
-    TFP_t      \\
-
-   SP_t   \\
-
-   IT_t \\
-
-   GDP_t \\
-
-   C_t \\
-
-   RP_t
-\end{bmatrix}
-	\end{equation}
-
-\
-
-\
-
-\begin{itemize}
-\item $RP = \pi^{IT}/\pi^{CPI}$. 
-\item All variables are real (except price indexes) and in log levels (except for RP, which is in growth rates). 
-\item The dataset ranges from 1989:q1 - 2017:q2.
-\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Our favorite specification}
-
-	\begin{itemize}
-	\item Recall: dataset is quarterly and covers 1989:q1-2017-q2.
-
-	\
-
-	\item One lag (as suggested by BIC and HQ).
-
-	\
-
-	\item Horizon of FEV-maximization: 60 quarters.
-
-	\
-
-	\item Restriction on relative prices after a news shock is imposed at 8 quarters.
-
-	\end{itemize}
-
-\end{frame}
 %%%%%%%%%%%%%%%%%
@@
 \begin{frame}
-\frametitle{TFP response to both shocks}
+\frametitle{ VAR Responses}
+
+\vspace{-0.2cm}
 \begin{figure}
+\begin{multicols}{2}
 \centering 
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_TFP__} % REGENERATE TFP SHOCKS FIGURES WITH RIGHT SCALES!!
+\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_IT_Shock_on_TFP__}\\
+\vspace{0.3cm}
+\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_IT_Shock_on_Real_Consumption__}\\ 
+\vspace{0.3cm}
+\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_IT_Shock_on_Relative_Price__}\\
+
+\end{multicols}
 \end{figure}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_TFP__}
-\end{figure}
+
 \end{frame}
@@
 \begin{frame}
-\frametitle{Real SP500 response to both shocks}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_SP__}
-\end{figure}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_SP__}
-\end{figure}
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{IT investment response to both shocks}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_IT_Investment__}
-\end{figure}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_IT_Investment__}
-\end{figure}
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{Other responses to both shocks}
+\frametitle{More VAR responses}
 
@@
 \centering 
-\includegraphics[scale = 0.1]{\ourFigPath Figures/fig_News_Shock_on_Real_GDP_Ryan_two_stepsID_10-Dec-2017_17_34_47}\\ 
+\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_IT_Shock_on_Real_IT_Investment__}\\
 \vspace{0.3cm}
-\includegraphics[scale = 0.1]{\ourFigPath Figures/fig_News_Shock_on_Real_Consumption_Ryan_two_stepsID_10-Dec-2017_17_34_50}\\ 
+\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_IT_Shock_on_Real_GDP__}\\ 
 \vspace{0.3cm}
-\includegraphics[scale = 0.1]{\ourFigPath Figures/fig_News_Shock_on_Relative_Price_Ryan_two_stepsID_10-Dec-2017_17_34_52}\\
-
-\includegraphics[scale = 0.1]{\ourFigPath Figures/fig_IT_Shock_on_Real_GDP_Ryan_two_stepsID_10-Dec-2017_17_35_00}\\
-\vspace{0.3cm}
-\includegraphics[scale = 0.1]{\ourFigPath Figures/fig_IT_Shock_on_Real_Consumption_Ryan_two_stepsID_10-Dec-2017_17_35_02}\\ 
-\vspace{0.3cm}
-\includegraphics[scale = 0.1]{\ourFigPath Figures/fig_IT_Shock_on_Relative_Price_Ryan_two_stepsID_10-Dec-2017_17_35_04}\\
+\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_IT_Shock_on_Real_SP__}\\
 
@@
 \begin{frame}
-	\frametitle{FEV explained by the two shocks at 60 periods}
+	\frametitle{3) Model}
 
-    \hspace{2.25cm}
-\begin{large}
-	\begin{tabular}{lccc}
-	\hline
-		& News & IT & Total \\
-		\hline
-	TFP	           & 0.20384  & 0.52596 & 0.72981  \\
-		\hline
-	\end{tabular}
-\end{large}
-
-\vspace{2cm}
-
-For BS, FEV of news was 45\%.
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Interpretation}
-
-\begin{enumerate}
- \item Shape and timing of the responses reflect ...
-
- %\
-
-	\begin{itemize}
-	\item both the Barsky \& Sims result;
-
-	\vspace{0.1cm}
-
-	\item as well as the the conjecture that the IT shock looks similar to news along certain dimensions;
-
-	\vspace{0.1cm}
-
-	\item but relative prices do indeed introduce a margin of difference between the two shocks.
-	\end{itemize}
+\begin{equation}\label{eq:prodfuncfinal}
+y_{c,t} = N_t  \  \ \Gamma_{c,t}  \  \ k_{i,t}^{\gamma} \ \  h_{1,t}^{1 - a- b} k_{c,1,t}^a k_{i,1,t}^b
+\end{equation}
 
@@
 
-\item Shares of FEV of TFP explained ...
-	\begin{itemize}
-	\item are also in line with the Barsky \& Sims result;
-	\item [] (for BS, news explains around 45\%, compared to 20\% here)
-
-	\vspace{0.1cm}
-
-	\item  yet suggest that the IT shock plays an important role as well (around 52\%).
-
-	\vspace{0.1cm}
-
-	\item And indeed the IT shock \emph{complements} the news shock, instead of substituting for it.
-	\item [] For BS, the single identified shock explains around 45\%, while our two identified shocks explain around 73\%.
-	\end{itemize}
-
-\end{enumerate}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Robustness checks}
-
-\begin{itemize}
-\item Different variables
-	\begin{itemize}
-	\item Add the Michigan index of consumer confidence (expected business conditions 5 years ahead)
+\begin{equation}\label{eq:prodfuncinter}
+y_{i,t} = N_t \ \ \Gamma_{i,t} \ \ k_{i,t}^{\gamma} \ \  h_{2,t}^{1 - a- b} k_{c,2,t}^a k_{i,2,t}^b
+\end{equation}
 
@@
 
-	\item Replace IT prices with capital prices (following Comin \& Gertler)
+The uses of the outputs are
+$$
+y_{c,t} = c_t + i_{c,t} \ \ \text{and} \ \ y_{i,t} = i_{i,t}
+$$
 
@@
 
-	\item Replace CPI inflation with PCE inflation
-	\end{itemize}
-
-	\
-
-\item Different horizons at which we impose the restriction on relative prices for the news shock
-\item[] $\rightarrow$ ran  6, 8, 10, 12 and 16 quarters.
-
-\
-
-\item Increase the number of lags (2)
-
-\
-
-\item Check whether VAR is information-sufficient to identify the news shock (Forni-Gambetti test) (p-val of 12\%)
+\begin{itemize}
+%\item News shock is $\varepsilon$, $N_{t} = \rho_N N_{t-1} + \varepsilon_{t-k}$
+\item Noise shock (contemporaneous) is $\eta$, $E_t \Gamma_{i,t} = \Gamma_{i,t} + \eta_t$
 \end{itemize}
@@
 
-%%%%%%% Slide %%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{frame}
-	\frametitle{A counterfactual}
+\frametitle{Model responses}
 
+\vspace{-0.2cm}
 \begin{figure}
+\begin{multicols}{2}
 \centering 
-		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_counterfactual_}
+\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_Noise_on_C__}\\
+\vspace{0.3cm}
+\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_Noise_on_P__}\\ 
+\vspace{0.3cm}
+\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_Noise_on_KI__}\\ 
+\vspace{0.3cm}
+\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_Noise_on_YC__}\\ 
+\end{multicols}
 \end{figure}
@@
 \end{frame}
-%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%%%%%%% Slide %%%%%%
+%%%%%%%        Slide    %%%%%%%%%%%%%%%%%%
 \begin{frame}
-	\frametitle{Conclusion}
+\frametitle{Next steps}
 
 \begin{itemize}
-\item Provided a test for the role of IT as an example of GPTs in explaining fluctuations in long-run TFP, and in doing so, overcame an econometric challenge prevalent in the literature on long-run productivity.
+\item Estimate the spillover parameter $\gamma$ through IR-matching
 
@@
 
-\item The results show that by controlling for the presence of news shocks, IT productivity shocks are important drivers of TFP fluctuations at long horizons.
+\item Robustness checks / improving the VAR / completing the VECM
 
@@
 
-\item This result does not contrast however with the findings of the news shock literature since we still find that news also play a significant role in explaining TFP.
-
-\
-
-\item Moreover, IT productivity shocks can be thought of as giving more microfoundations to what classical news shocks carry information on.
-
+\item Your thoughts?
 \end{itemize}
@@
 \end{frame}
-%%%%%%%%%%%%%%%%%
 
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Work ahead}
-
-\begin{itemize}
-
-\item Show the identification assumption in the structural model.
-
-\
-
-\item Technically, should do a VECM due to cointegration and wanting to have variables in the VAR as growth rates rather than levels...
-
-\
-
-\item Dig deeper: IT is just an example of GPTs for the last 30 years
-\item[] $\hookrightarrow$ could redo analysis for different time periods with different GPTs (electricity in 1920s, airplane industry in 1960s ...)
-
-\
-
-\item Use a fully structural model to see if we can find interesting interactions between the two shocks?
-\item [] $\hookrightarrow$ In particular, we're thinking of noise shocks on IT productivity
-
-\
-
-\item But there are also other shocks that are similar to news shocks and yet not news shocks in the Barsky \& Sims sense: reallocative shocks, shocks to inventories, etc...  
-\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%                     APPENDIX  
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{The current TFP slowdown}
-
-	\vspace{-1cm}
-	\noindent
-	\begin{figure}
-		\centering
-		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_TFP_macrolunch_29-Nov-2017_17_41_17}
-	\end{figure}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Barsky \& Sims FEV of TFP explained}
-	\label{BS_FEV}
-
-\vspace{-1cm}
-\noindent
-\begin{figure}
-\centering
-\includegraphics[scale=0.3]{\ourTablePath fig_BS_fevtable}
-\end{figure}
-
-\hyperlink{related_lit}{\beamerreturnbutton{Return}}	
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Production of IT goods}
-	\label{it_sector}
-
-Production function for IT goods:
-
-\begin{equation}
-V_{i,t} = \lambda_t \Psi_t f(S_{i,t}) 
-\end{equation}
-where $S_{i,t}$ is investment by producer $i$ in IT goods and $\lambda$ is the productivity of the IT sector.
-
-\
-
-The IT producer's problem is to max discounted profits $J_{i,t+1}$
-
-\begin{equation}
-\max_{S_{i,t}} \; \mathbb{E}(\Lambda_{t,t+1},J_{i,t+1})\lambda_t \Psi_t f(S_{i,t}) - P^{IT}_t S_{i,t}
-\end{equation}
-
-\
-FOC:
-
-\begin{equation}
-P^{IT}_t = \mathbb{E}(\Lambda_{t,t+1},J_{i,t+1})\lambda \Psi_t f_1
-\end{equation}
-
-\hyperlink{expanding_variety}{\beamerreturnbutton{Return}}	
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Timing: RD drop vs TFP drop}
-	\label{timing}
-
-	\vspace{-1cm}
-	\noindent
-	\begin{figure}
-		\centering
-		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_RD_level_macrolunch_30-Nov-2017_11_31_04}
-	\end{figure}
-
-\hyperlink{convincing}{\beamerreturnbutton{Return}}	
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{IT investment: a drop at the right time}
-	\label{it_investment}
-
-%	\vspace{-1cm}
-	\noindent
-	\begin{figure}
-		\centering
-		\includegraphics[scale=0.29]{\ourFigPath Figures/fig_IT_level_macrolunch_30-Nov-2017_11_37_26}
-	\end{figure}
-
-\hyperlink{convincing}{\beamerreturnbutton{Return}}	
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-\frametitle{Identification Strategy}
-\label{Technicalities}
-
-\begin{equation}
-D = \begin{bmatrix}
-d_{11} & \gamma_{12} & \gamma_{13} & d_{14} & \cdots \\
-d_{21} & \gamma_{22} & \gamma_{23} & d_{24} & \cdots \\
-\vdots & \vdots & \vdots & \ddots & \vdots 
-\end{bmatrix}
-\end{equation}
-
-\begin{itemize}
-	\item Indifferent over $d_{ij}$ as long as $D$ is orthogonal
-	\item $A \gamma_{2}$ is the impact response to a news shock
-	\item $A \gamma_{3}$ is the impact response to a IT productivity shock
-	\item First element of both $A \gamma_{2}$ and $A \gamma_{3}$ is zero due to the no-contemporaneous effect of both shocks on TFP
-	\item $A \gamma_2$ is such that the FEV of TFP is maximized subject to zero long-run effect on $RP$
-	\item $A \gamma_3$ is maximizing the remaining FEV of TFP 
-\end{itemize}
-
-\hyperlink{identification}{\beamerreturnbutton{Return}}	
-\end{frame}
-%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2018-05-12 Code/just_IT_vecm/main_file_just_IT.m

@@ -57,8 +57,8 @@ nsimul          = 200; %5000
 nvar            = size(data,2);
 sig1            = 0.9; % significance level
 sig2            = 0.95; % a 2nd sig. level
-H               = 40; %40; % horizon for generation of IRFs
-h               = H; %40; % horizon for IRF plots
+H               = 100; %40; % horizon for generation of IRFs
+h               = 40; %40; % horizon for IRF plots
 which_variable  = pos_IT; % select IT as the variable whose FEV we wanna max
 
 
@@ -130,7 +130,7 @@ end
 
 %Creating and Printing figures
 comment = [which_ID '_' char(varnames(5))];
-print_figs = 'no';
+print_figs = 'yes';
 
 [IRFs, ub1, lb1, ub2, lb2] = genIRFs(fake_impact,fake_impact_boot,...
       B,beta_tilde_star,H,sig1, sig2);
@@ -146,13 +146,11 @@ if IRFs(pos_IT,1,pos_IT) < 0 % if the impact effect on IT is negative
       lb2(:,:,pos_IT)     = - lb2(:,:,pos_IT);
 end
 
-
 %Printing/Showing IRFs
-h = 40;
 % plotIRFs(IRFs,ub,lb,40,which_shocks,shocknames,varnames,which_ID,print_figs)
 % plot_single_IRFs(IRFs,ub1,lb1,h,which_shocks,shocknames, varnames, which_ID, print_figs)
 use_current_time = 0; % don't save the time
-plot_single_IRFs_2CIs(IRFs,ub1,lb1,ub2,lb2,h,which_shock,shocknames, varnames, '_', print_figs, use_current_time)
+plot_single_IRFs_2CIs(IRFs,ub1,lb1,ub2,lb2,h,which_shock,shocknames, varnames, '_', print_figs, use_current_time, base_path)
 
 %Forni&Gambetti Orthogonality Test
 do_FG_test = 'no';

### 2018-05-12 Code/oulton2010/main_prog_spillover_news.m

@@ -49,7 +49,7 @@ pos_BIGGAMI = biggami_idx-njumps; % IT productivity shock
 pos_news    = v8_idx - njumps;
 pos_N       = n_idx - njumps;
 pos_noise   = biggamitt_idx - njumps; %preliminary noise shock
-T = 60;
+T = 0;
 IRFs_all = zeros(nvar, T, nshocks);
 for s=1:nshocks
     x0 = zeros(nshocks,1); % impulse vector
@@ -75,5 +75,5 @@ shocknames(1, pos_noise)   = {'Noise'};
 
 % GAMC_p GAMKI_p GAMYC_p GAMYI_p GAMH_p GAMP_p GAMKC2_p GAMKI2_p
 varnames = {'Biggamc', 'C', 'KI', 'YC', 'YI', 'H', 'P', 'KC2', 'KI2' };
-print_figs = 'no';
-plot_single_simple_IRFs(IRFs,T,which_shock,shocknames, varnames, print_figs)
+print_figs = 'yes';
+plot_single_simple_IRFs(IRFs,T,which_shock,shocknames, varnames, print_figs, base_path)

### 2018-05-12 Code/oulton2010/parameters.m

@@ -13,10 +13,11 @@ param.a        = 0.13;  %0.13 share of standard capital
 param.b        = 0.17; %0.17 share of IT capital
 param.biggami  = 1.032; %1.032; % growth rate of IT productivity
 param.biggamc  = 1.00328; %1.00328;    % growth rate of cons. productivity
-param.di       = 0.3; %0.124; % depreciation rate of IT capital (Some work suggests 0.1830)
-param.dc       = 0.3; %0.056 depreciation rate of standard capital
+param.di       = 0.124; %0.124; % depreciation rate of IT capital (Some work suggests 0.1830)
+param.dc       = 0.056; %0.056 depreciation rate of standard capital
 param.chi      = 1; % preference parameter of preference for leisure. (From Ryan)
 param.gam      = 0.2; %0.2 spillover elasticity (only used in model_spillover.m and model_spillover_ss.m)
 param.siggami  = 1; % variance of BIGGAMI
-param.sige     = 1; % variance of signal on BIGGAMI
+param.sige     = 2; % variance of signal on BIGGAMI
 
+end

### 2018-05-12 invoke_export_fig.m

@@ -1,4 +1,4 @@
-function invoke_export_fig(figname, some_comment,use_current_time)
+function invoke_export_fig(figname, some_comment,use_current_time, base_path)
 % This file invokes the export_fig command which requires the figure to be saved to be open
 % Inputs:
 % figname      = what you want the figure to be called
@@ -23,21 +23,24 @@ else
     final_name = ['fig_' figname '_' some_comment '.png'];
 end
 
-base_path = pwd;
-if exist([base_path '\Figures'], 'dir')
-    cd([base_path '\Figures']) %for Microsoft
+if nargin < 4
+    base_path = pwd;
 else
-    cd([base_path '/Figures']) %for Mac
+    if exist([base_path '\Figures'], 'dir')
+        cd([base_path '\Figures']) %for Microsoft
+    else
+        cd([base_path '/Figures']) %for Mac
+    end
+    
+    if exist([base_path '\Export_Fig'], 'dir')
+        addpath([base_path '\Export_Fig']) %for Microsoft
+    else
+        addpath([base_path '/Export_Fig']) %for Mac
+    end
+    
+    
+    export_fig(final_name)
+    
+    cd(base_path)
 end
-
-if exist([base_path '\Export_Fig'], 'dir')
-    addpath([base_path '\Export_Fig']) %for Microsoft
-else
-    addpath([base_path '/Export_Fig']) %for Mac
-end
-
-export_fig(final_name)
-
-cd(base_path)
-
 end

### 2018-05-12 main_file_VECM.m

@@ -21,7 +21,7 @@ nvar            = size(data,2);
 %%Checking the number of lags over BIC, AIC, and HQ (see 'Lecture2M' in our folder)
 [AIC,BIC,HQ] = aic_bic_hq(data,max_lags);
 if AIC >= 4
-    nlags = 3; % 2;
+    nlags = 1; % 2;
     warning(['AIC > 4, setting nlags to ', num2str(nlags) ])
 else
     nlags = AIC;

### 2018-05-12 plot_single_IRFs_2CIs.m

@@ -1,4 +1,5 @@
-function plot_single_IRFs_2CIs(IRFs,ub1,lb1,ub2, lb2, h,which_shock,names, varnames, which_ID_strat, print_figs, use_current_time)
+function plot_single_IRFs_2CIs(IRFs,ub1,lb1,ub2, lb2, h,which_shock,names, varnames, which_ID_strat, print_figs, ...
+    use_current_time, base_path)
 % h = IR horizon for figures
 % ub1 and lb1 are the bootstrapped CI for the 1st significance level
 % ub2 and lb2 are the bootstrapped CI for the 2nd significance level
@@ -39,13 +40,13 @@ for i_shock=1:nshocks
         xt = get(gca, 'XTick');
         set(gca, 'FontSize', 28)
         title([name, ' on ' , varname],'fontsize',72)
-          ylim([min_y_lim(i_var) max_y_lim(i_var)]);
+          %ylim([min_y_lim(i_var) max_y_lim(i_var)]);
         hold off
         grid on
         
         % Save figures if you want to
         if strcmp(print_figs, 'yes')
-            invoke_export_fig([name, ' on ' , varname], which_ID_strat,use_current_time)
+            invoke_export_fig([name, ' on ' , varname], which_ID_strat,use_current_time, base_path)
             close all
             pause(0.5)
         end

### 2018-05-12 plot_single_simple_IRFs.m

@@ -1,4 +1,4 @@
-function plot_single_simple_IRFs(IRFs,h,which_shock,names, varnames, print_figs, ub, lb)
+function plot_single_simple_IRFs(IRFs,h,which_shock,names, varnames, print_figs, base_path)
 % A simplified function for plotting IRFs in particular when there are no
 % bells and whistles. You only need to input IRFs, h, shocknames, varnames
 % and 'no' for printing figures.
@@ -28,13 +28,6 @@ for i_shock=1:nshocks
         varname = varnames{i_var};
         name = names{which_shock(i_shock)};
         hold on
-        if nargin > 6
-            % if ub, lb given, do shaded confidence intervals
-            x2 = [periods, fliplr(periods)];
-            inBetween = [lb(i_var,1:h,which_shock(i_shock)), ...
-                fliplr(ub(i_var,1:h,which_shock(i_shock)))];
-            fill(x2, inBetween, [0.75 0.75 0.75],'LineStyle','none');
-        end
         plot(zeros(1,h), 'Color','b')
         plot(periods,IRFs(i_var,1:h,which_shock(i_shock)),'linewidth',1,'Color','r')
         xt = get(gca, 'XTick');
@@ -48,7 +41,7 @@ for i_shock=1:nshocks
         if strcmp(print_figs, 'yes')
             which_ID_strat = '_';
             use_current_time = 'no';
-            invoke_export_fig([name, ' on ' , varname], which_ID_strat,use_current_time)
+            invoke_export_fig([name, ' on ' , varname], which_ID_strat,use_current_time, base_path)
             close all
             pause(0.5)
         end

### 2018-05-17 Code/just_IT_vecm/main_file_just_IT.m
We tried to fix VECM (still problems with fmincon) and we saved important results

@@ -130,7 +130,7 @@ end
 
 %Creating and Printing figures
 comment = [which_ID '_' char(varnames(5))];
-print_figs = 'yes';
+print_figs = 'no';
 
 [IRFs, ub1, lb1, ub2, lb2] = genIRFs(fake_impact,fake_impact_boot,...
       B,beta_tilde_star,H,sig1, sig2);
@@ -176,6 +176,10 @@ impact_vardec = A*D_null; % where A is the chol.
 vardec = gen_vardecomp(IRF_vardec,h,h);
 shareIT_on_TFP = vardec(1,end); % "end" b/c we put gam_opt as last.
 
+%Get Structural Shocks
+[s_shock_just_IT, ~] = ...
+      get_structural_shocks_general(A,gam_opt,res,which_shock);
+
 disp('stopping here')
 return
 %Saving in Tex format the Variance Decomposition Matrix
@@ -197,10 +201,3 @@ end
 toc
 disp(varnames)
 disp(datestr(now))
-
-
-
-
-
-
-

### 2018-05-17 LL_VECM.m

@@ -1,4 +1,4 @@
 function obj = LL_VECM(T,B,sigma)    
-    %obj = T/2*log(det(B)^2) + sum(sum(abs(T/2*trace((B')^(-1)*B^(-1)*sigma))));
-    obj = sum(sum(abs(B*B' - sigma)));
+    obj = T/2*log(det(B)^2) + sum(sum(abs(T/2*trace((B')^(-1)*B^(-1)*sigma))));
+    %obj = sum(sum((B*B'-sigma).^2));
 end

### 2018-05-17 RRR.m

@@ -76,7 +76,7 @@ sorted_eig = sort(eigv,'descend');
 %eigenvectors so that A*V = B*V*D.
 check = A*V - B*V*D;
 check = sum(sum(abs(check)));
-if check > 10^(-14)
+if check > 10^(-12)
       warning('Eigenvalues and eigenvectors are not solving the generalized eigenvalue problem.')
 end
 

### 2018-05-17 genIRFs_VECM.m

@@ -32,13 +32,6 @@ lb1 = zeros(nvar,H,nshocks);
 ub2 = zeros(nvar,H,nshocks);
 lb2 = zeros(nvar,H,nshocks);
 
-
-% Phi_zero = eye(nvar);
-% Phi_one = Phi_zero*A(:,1:nvar);
-% Phi_two = Phi_one*A(:,1:nvar) + Phi_zero*A(:,1:nvar);
-% % and so on and so forth ...
-
-
 for i_shock=1:nshocks
     shocks = zeros(nvar,1);
     shocks(i_shock,1) = 1;

### 2018-05-17 get_structural_shocks_general.m

@@ -1,0 +1,9 @@
+function [structural_shocks, IR] = get_structural_shocks_general(A,gamma,resid,which_shocks)
+
+D = [gamma null(gamma')]; % building D, the only orthogonal matrix
+%D = [D_step1(:,1:which_shocks(1)-1) gamma D_step1(:,which_shocks(end)+1:end)]; % rearranging so the identified shocks are still in the right place
+IR = A*D; 
+s = IR^(-1)*resid';
+s = s'; % to make it (T,nshocks_recovered)
+structural_shocks = s(:,1:length(which_shocks));
+end

### 2018-05-17 main_file_SVAR_RyansID.m

@@ -37,10 +37,10 @@ which_shocks = [pos_news pos_IT];
 %Technical Parameters
 max_lags        = 10;
 nburn           = 0; %with the Kilian correction better not burning!!!
-nsimul          = 30; %5000
+nsimul          = 10; %5000
 nvar            = size(data,2);
-sig1            = 0.9; % significance level
-sig2            = 0.95; % a 2nd sig. level
+sig1            = 0.6; % significance level
+sig2            = 0.4; % a 2nd sig. level
 H               = 100; %40; % horizon for generation of IRFs
 h               = H; %40; % horizon for IRF plots
 which_variable  = 1; % select TFP as the variable whose FEV we wanna max
@@ -54,25 +54,15 @@ else
       nlags = AIC;
 end
 
-switch 'VECM'
-      case 'VAR'
-            %Run VAR imposing Cholesky
-            [A,B,res,sigma] = sr_var(data, nlags);
-            %Checking if the VAR is stationary
-            test_stationarity(B');
-            
-      case 'VECM'
-            %Run VECM
-            constant = 0;
-            [Pi,B,res,sigma] = VECM(data, nlags, constant);
-            %Static rotation matrix
-            A = chol(sigma)';
-end
+%Run VAR imposing Cholesky
+[A,B,res,sigma] = sr_var(data, nlags);
+%Checking if the VAR is stationary
+test_stationarity(B');
 
 % Implement Ryan's ID strategy
 LR_hor = 8; % at what horizon to impose the LR restriction
 % [impact, FEV_opt, IRFs, gamma_opt, FEV_news, FEV_IT] = ryansID(which_variable,which_shocks,H,B,A,q);
-H_max = 60;
+H_max = 100;
 [impact, FEV_opt, ~, gam_opt, FEV_news, FEV_IT] ...
       = Ryan_two_stepsID(which_variable,which_shocks,H_max,...
       LR_hor,B,A,pos_rel_prices);
@@ -223,6 +213,8 @@ end
 % % sum of the two:
 % hd_alt = hd_IT_alt + hd_news_alt;
 
+[structural_shock_RyanID, ~] = ...
+      get_structural_shocks_general(A,gam_opt,res,which_shocks);
 
 
 

### 2018-05-17 main_file_VECM.m

@@ -21,7 +21,7 @@ nvar            = size(data,2);
 %%Checking the number of lags over BIC, AIC, and HQ (see 'Lecture2M' in our folder)
 [AIC,BIC,HQ] = aic_bic_hq(data,max_lags);
 if AIC >= 4
-    nlags = 1; % 2;
+    nlags = 2; % 2;
     warning(['AIC > 4, setting nlags to ', num2str(nlags) ])
 else
     nlags = AIC;
@@ -29,15 +29,18 @@ end
 
 %Run reduced form VECM
 r = nvar-1; %number of cointegrating vectors
-%[alph_hat, bet_hat,Gam_hat,sigma] = RRR(data, nlags, r);
-[alph_hat,bet_hat,Pi,Gam_hat,res,sigma] = redu_VECM(data, nlags, r);
+%[alph_hat2, bet_hat2,Gam_hat2,sigma2] = RRR(data, nlags, r);
+[alph_hat,bet_hat,Pi,Gam_hat,res,sigma] = redu_VECM(data, nlags, r); %It seems to be correct...
+%compared to a different method.
+
+return
 
 %Run structural VECM
 [B, Xi, A] = structural_VECM(alph_hat,bet_hat,Gam_hat,res,sigma,nlags,r);
 
 return
 
-H = 40;
+H = 1000;
 sig1 = 0;
 sig2 = 0;
 [IRFs, ub1, lb1, ub2, lb2] = genIRFs_VECM(B,0,A',0,H,sig1,sig2);

### 2018-05-17 structural_VECM.m

@@ -36,8 +36,7 @@ end
 % Xi = bet*(alp'*G*bet)^(-1)*alp'; %(nvar,nvar)
 betT = null(bet','r');
 alpT = null(alp','r');
-Xi = betT*(alpT'*G*betT)^(-1)*alpT'; %(nvar,nvar) % This line is based on Chiawa et al. 
-
+Xi = betT*(alpT'*G*betT)^(-1)*alpT'; %(nvar,nvar) % This line is based on Chiawa et al.
 
 % Objective function to minimize - See Lutkepohl (2005) - EUI, working paper
 obj = @(B) LL_VECM(T,B,sigma);
@@ -63,23 +62,23 @@ end
 
 %Optimization Parameters
 options  = optimset('fmincon');
-options  = optimset(options, 'TolFun', 1e-19, 'display', 'none');
+options  = optimset(options, 'display', 'iter','TolFun', 1e-7);
+%'TolFun', 1e-19, 'FinDiffRelStep', 1
 warning off
 %Minimization
-B_zero = rand(nvar);
+B_zero = randn(nvar,nvar);
 if r > 1
       %B_opt = fmincon(obj, B_zero,[],[],Aeq,Beq,[],[],[],options);
       B_opt  = fmincon(obj, B_zero,[],[],Aeq,Beq,[],[],@(B) ...
-          constraint_long(B,Xi,r,nvar),options);
+            constraint_long(B,Xi,r,nvar),options);
       %fmincon(FUN,X0,A,B,Aeq,Beq,LB,UB,NONLCON,OPTIONS)
 else
       B_opt = fmincon(obj, B_zero,[],[],[],[],[],[],@(B) constraint_long(B,Xi,r,nvar),options);
 end
 %Temporary tools to visualize the correctness of restrictions
-obj_min = obj(B_opt);
-obj_zero = obj(B_zero);
-B_opt;
-long_restr = Xi*B_opt;
+diff_BBp_sigma = B_opt'*B_opt - sigma
+long_restr = Xi*B_opt
+B_opt
 warning on
 
 %Setting the A matrix to obtain a SVAR functional form as follows

### 2018-05-29 Latex/Meeting_Ryan_30May_2018/Meeting.tex
Presentation for Ryan's meeting

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{float}
\usepackage{csquotes}
\usepackage{sansmathaccent}
\usepackage{subfigure}
\usepackage{multicol}
\pdfmapfile{+sansmathaccent.map}
\def \ourFigPath {../../} 
\def \ourTablePath {../../Tables/}

\setbeamersize{text margin left=5mm,text margin right=12mm} 
%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\numberset}{\mathbb}
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\N}{\numberset{N}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\virgolette}[1]{``#1''}
%

\author[Brianti, Gati]{Marco Brianti and Laura Gati}

\institute[Boston College]{Boston College}

\title{IT Spillovers in TFP }

\date{\today}

\usetheme{Warsaw}

\begin{document}

\begin{frame}

\maketitle

\end{frame}

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{Topics of today's discussion}

\begin{enumerate}
\item Model solution related questions.

\begin{itemize}
	\item How should be $Ef_x$?
	\item Is the first partial derivative times the related state or just the first partial derivative?
	\end{itemize}

\

\item Constructing a conceptually correct GDP and TFP.

\

\item Initial results for the VECM.

\

\item Different identification procedures and their correlations.
\end{enumerate}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{(2) Constructing a conceptually correct GDP and TFP}

Oulton (2010) defines GDP as follows
$$
\hat{GDP} = (1 - w) \hat{y_c} + w \hat{y_i} \ \ \ \text{where} \ \ \ w = \frac{p y_i}{y_c + p y_i}
$$
\begin{itemize}
	\item Can we use $w$ in s.s.?
\end{itemize}

\

\

Moreover,

$$
\hat{TFP} = (1 - w) \hat{TFP_c} + w \hat{TFP_i} 
$$

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{(3) VECM}

Number of cointegrating vectors is 1 as indicated by Johansen's trace test.

\

\

Identification strategy: rotation of shocks that maximizes the impact effect on IT investment s.t. a 0 impact response on TFP.

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{(3) VECM}

\vspace{-0.2cm}
\begin{figure}
	\begin{multicols}{2}
		\centering 
		\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_IT_Shock_on_TFP__JustIT_VECM}\\
		\vspace{0.3cm}
		\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_IT_Shock_on_Real_IT_Investment__JustIT_VECM}\\ 
		\vspace{0.3cm}
		\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_IT_Shock_on_Real_Consumption__JustIT_VECM}\\ 
		\vspace{0.3cm}
		\includegraphics[scale = 0.13]{\ourFigPath Figures/fig_IT_Shock_on_Real_GDP__JustIT_VECM}\\

	\end{multicols}
\end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%%        Slide    %%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{(4) Different identification procedures and their correlations.}

Two step-identification procedure.

\

\begin{enumerate}
\item Identify the news shock a la Barsky-Sims subject to some constraint suggested by the theoretical model.

\begin{itemize}
	\item Limiting the response of relative prices to a news shock.
	\item Zero-impact response of IT to a news shock.
\end{itemize}

\

\item Identify the IT shock as the one that maximizes the impact effect on IT investment s.t. a 0 impact response on TFP.
\end{enumerate}

\

\textbf{Note.} This is the only identification procedure you have not seen so far.

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%        Slide    %%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Quick overview of identification procedures}
	\begin{enumerate}
		\item ``Old news" identification: Identify news shock and IT shock a la Barsky \& Sims, s.t. a 0 on relative prices.
		\item ``just IT" identification: identify an IT shock only as a rotation of shocks that maximizes the impact effect on IT investment s.t. a 0 impact effect on TFP.
		\item ``two-step just IT'': the new one presented above. 
	\end{enumerate}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%        Slide    %%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Structural shock series}
\begin{center}
\begin{tabular}{ccc}
	S.1 & S.2 & S.3 \\
	1.0000   & 0.6392 &   0.6180 \\
	0.6392  &  1.0000 &   0.8359 \\
	0.6180  &  0.8359 &   1.0000 \\
\end{tabular}
\end{center}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%        Slide    %%%%%%%%%%%%%%%%%%
\begin{frame}
\frametitle{Correlations}

\begin{center}
\includegraphics[scale = 0.3]{\ourFigPath Figures/structural_shocks_together}\\
\end{center}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

### 2018-05-29 Code/corr_structural_shocks.m

@@ -1,0 +1,23 @@
+% Investigate correlations between structural shock time series obtained
+% from different identification strategies
+
+clear
+load 'correct_favourite_macrolunch_structural_shocks.mat'
+
+s_old_news = structural_shock_RyanID(:,2);
+
+load 's_shock_just_IT.mat'
+
+s_justIT = s_shock_just_IT(1:end-1);
+
+load 'structural_shocks_justIT_controllingNEWS.mat'
+
+s_justIT_controlling_news = structural_shock_RyanID(1:end-1,2);
+
+size(s_old_news)
+size(s_justIT)
+size(s_justIT_controlling_news)
+
+structural_shocks = [s_old_news s_justIT s_justIT_controlling_news];
+
+corr(structural_shocks)

### 2018-05-29 Code/oulton2010/model_IRmatching_spillover_news.m

@@ -135,7 +135,7 @@ f(end+1) = S_p - BIGGAMI_p;
 %Log-linear approx
 xlog = 1:length(X);
 ylog = 1:length(Y);
-% log_var = [X(xlog) Y(ylog) XP(xlog) YP(ylog)];
+%log_var = [X(xlog) Y(ylog) XP(xlog) YP(ylog)];
 log_var = [];
 
 disp(['neq: ' num2str(length(f))]);

### 2018-05-29 Code/oulton2010/model_prog.m

@@ -3,6 +3,7 @@ function [f fx fy fxp fyp eta R set dgam_dtheta deta_dtheta dR_dtheta xlag ylag]
 param = param_trans(param);
 %Assign parameter values to named variables.
 gam = param(1);
+sige = param(2);
 
 %Assign set values to named variables.
 bet = set(1);
@@ -14,8 +15,7 @@ di = set(6);
 dc = set(7);
 chi = set(8);
 siggami = set(9);
-sige = set(10);
-adiff = set(11);
+adiff = set(10);
 
 %BEGIN_EXTRACT_HERE
 

### 2018-05-29 Code/oulton2010/model_spillover_news.m

@@ -166,9 +166,9 @@ wi = p*yc/(yc+p*yi);
 % wi = P*YC/(YC+P*YI);
 f(end+1) = GAMGDP - (1-wi)*GAMYC - wi*GAMYI;
 f(end+1) = -GAMTFP + gam*GAMKI + (1-wi)*BIGGAMC + wi*BIGGAMI; % A correct formulation for TFP growth
-f(end+1) = -GAMTFP + GAMGDP ...
-    - (1-wi)*((1-a-b)*GAMH1 + a*GAMKC1 + b*GAMKI1) ...
-    -    wi *((1-a-b)*GAMH2 + a*GAMKC2 + b*GAMKI2); % An alternative formulation for TFP growth - should be equivalent but isn't?
+% f(end+1) = -GAMTFP + GAMGDP ...
+%     - (1-wi)*((1-a-b)*GAMH1 + a*GAMKC1 + b*GAMKI1) ...
+%     -    wi *((1-a-b)*GAMH2 + a*GAMKC2 + b*GAMKI2); % An alternative formulation for TFP growth - should be equivalent but isn't?
 % A stationary IT productivity level shock:
 f(end+1) = log(ITLEV_p) -0.8*log(ITLEV);
 

### 2018-05-29 Code/oulton2010/param_unpacker.m

@@ -1,5 +1,6 @@
 %Assign parameter values to named variables.
 gam = param(1);
+sige = param(2);
 
 %Assign set values to named variables.
 bet = set(1);
@@ -11,6 +12,5 @@ di = set(6);
 dc = set(7);
 chi = set(8);
 siggami = set(9);
-sige = set(10);
-adiff = set(11);
+adiff = set(10);
 

### 2018-05-31 Latex/Slides_for_Final_Draft_June_2018/Slides_June2018.tex
Starting final slides draft

--- 2018-04-26 Latex/Slides_Presenter_April2018/dw23jan2018.tex
@@
 
-\title{IT Spillovers in Long-Run TFP \\ A SVAR Approach}
+\title{Spillover Effects of Information and Communication Technology on Future TFP using a Structural VAR Approach}
 
-\date{April 26, 2018}
+\date{June 2018}
 
@@
 	\begin{itemize}
+
+		\item Literature agrees on the importance of Total Factor Productivity (TFP) in driving long-run economic performance.
+
+		\item However, less agreement on the underlying driver of TFP.
 
@@
 \begin{frame}
-\frametitle{TFP response to both shocks}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_TFP__} % REGENERATE TFP SHOCKS FIGURES WITH RIGHT SCALES!!
-\end{figure}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_TFP__}
-\end{figure}
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
 \frametitle{Real SP500 response to both shocks}
@@
 	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_SP__}
-\end{figure}
-\end{frame}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{frame}
-\frametitle{IT investment response to both shocks}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_News_Shock_on_Real_IT_Investment__}
-\end{figure}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.15]{\ourFigPath Figures/fig_IT_Shock_on_Real_IT_Investment__}
 \end{figure}

### 2018-06-02 Latex/Draft_Summer2018/Summer2018.tex
Final Draft - Abstract and 5 lines of introduction

\documentclass[14pt]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[top=3cm,bottom=3cm,left=3cm,right=3cm,bindingoffset=0mm]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{comment}
\usepackage{rotating}
\usepackage{float}
\usepackage{natbib}
\usepackage{amsthm}
\usepackage{bbm}
\usepackage{thmtools,thm-restate}
\usepackage{hyperref}
\usepackage{extsizes}
\usepackage[font=footnotesize,labelfont=bf]{caption}

% New Options
\newtheorem{prop}{Proposition}
\newtheorem{definition}{Definition}[section]
\newtheorem*{remark}{Remark}
\newtheorem{lemma}{Lemma}
\declaretheorem{proposition}
\linespread{1.3}
\raggedbottom
\font\reali=msbm10 at 12pt

% New Commands
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\R}{\mathbb{R}}
\DeclareMathOperator{\E}{\mathbb{E}}

\title{ICT and Future Productivity:\\Evidence and Theory of a GPT\thanks{Correspondence: Department of Economics, Boston College, 140 Commonwealth Avenue, Chestnut Hill, MA 02467. Email: brianti@bc.edu (Marco Brianti) and gati@bc.edu (Laura Gati).}}
\author{Marco Brianti \\ {\small Boston College} \and Laura Gati \\ {\small Boston College}}
\date{\today}

\begin{document}

\maketitle
%%%%%%%%%%%%%%%%%%%%             ABSTRACT           %%%%%%%%%%%%%%%%%% 
\small{
\abstract{Information and Communication technology (ICT) is able to explain accelerations in productivity in sectors that are ICT users. We employ Structural VARs to investigate the effects of ICT supply shocks on Total Factor Productivity (TFP) and other macroeconomic variables. In response to this sector-specific supply shock relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a delayed significant and persistent increase. In line with theories of ICT as a general-purpose technology, we analyze a two-sector general equilibrium model in order to rigorously rationalize previous results and estimate key parameters via impulse-response matching. We conclude that ICT accumulation is able to enhance productivity through a positive spillover effect which takes into account the overall level of diffusion of ICT capital in the economy.}
}
\newpage

\newpage
%%%%%%%%%%%%%%%%%%%%               INTRODUCTION                 %%%%%%%%%%%%%%%%%% 
\section{Introduction}

Although there is large consensus on the importance of productivity as a driver of economic performances, less agreement is on the underlying sources that enhance its growth. For several years, most of the business-cycle literature purposely decided to avoid such a question by proxying movements in productivity as random shocks.\footnote{\cite{kydland1982time} and \cite{long1983real} are among the first papers which consider productivity shocks on a general equilibrium model.}

However, the robust empirical evidence of the slowdown in productivity right before the great recession is summoning the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.

%%%%%%%%%%%%%%%%%%%%%%            EMPIRICS                     %%%%%%%%%%%%%%%%%%%
\section{Empirics}

%%%%%%%%%%%%%%%%%%%%               MODEL                 %%%%%%%%%%%%%%%%%% 
\section{Model}

%%%%%%%%%%%%%%%%%%%%               CONCLUSION                 %%%%%%%%%%%%%%%%%% 
\section{Conclusion}

\bibliographystyle{chicago}
\bibliography{literature}

 %%%%%%%%%%%%%%%%%%           BIBLIOGRAPHY            %%%%%%%%%%%%%%%%%%

\end{document}

### 2018-06-04 Latex/Draft_Summer2018/Summer2018.tex
Writing the introduction

@@
 
-However, the robust empirical evidence of the slowdown in productivity right before the great recession is summoning the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.
+However, the robust empirical evidence of the slowdown in productivity right before the great recession is summoning the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
 
+In the spirit of \cite{comin2006medium}, a part of literature endogenizes productivity by adapting features of endogenous growth models into DSGE models.
+Following \cite{romer1990endogenous}, most of those models augment final-good production functions with an expanding composite of intermediate goods produced by the R\&D sector in order to allow for an endogenous rate of adoption of new technologies.\footnote{\cite{bianchi2014growth}, \cite{anzoategui2016endogenous}, and \cite{moran2017innovation} use similar techniques to endogenize growth.
+In particular, \cite{bianchi2014growth} augment a DSGE  model using a quality ladders model in the vein of \cite{grossman1991quality}.
+Moreover, \cite{anzoategui2016endogenous} and \cite{moran2017innovation}, similarly to \cite{comin2006medium}, use a model of expanding variety in the vein of \cite{romer1990endogenous}.}
 %%%%%%%%%%%%%%%%%%%%%%            EMPIRICS                     %%%%%%%%%%%%%%%%%%%
@@
 \section{Conclusion}
+hjklbhjkl
 

### 2018-06-04 Latex/Draft_Summer2018/Summer2018.tex
Keep writing

--- 2018-06-02 Latex/Draft_Summer2018/Summer2018.tex
@@
 
-However, the robust empirical evidence of the slowdown in productivity right before the great recession is summoning the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.
+However, the robust empirical evidence of the slowdown in productivity right before the great recession is summoning the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
+
+Along \cite{comin2006medium}, some theoretical contributions rationalize endogenous productivity dynamics by adapting features of endogenous growth models into DSGE models.
+Following \cite{romer1990endogenous}, most of those papers augment final-good production functions with an expanding composite of intermediate goods produced by the R\&D sector in order to allow for an endogenous rate of adoption of new technologies.\footnote{\cite{bianchi2014growth}, \cite{anzoategui2016endogenous}, and \cite{moran2017innovation} use similar techniques to endogenize growth.
+In particular, \cite{bianchi2014growth} augment a DSGE  model using a quality ladders model in the vein of \cite{grossman1991quality}.
+Moreover, \cite{anzoategui2016endogenous} and \cite{moran2017innovation}, similarly to \cite{comin2006medium}, use a model of expanding variety in the vein of \cite{romer1990endogenous}.} Consistent with those previous models, some other papers are exerting effort to show that although research effort is rising, the productivity of the research sector is slowing down.\footnote{\cite{jones2009burden} and \cite{bloom2017ideas} are two important contributions that highlight those facts.}
+
+Motivated by this wave of research, in this paper we empirically investigate which has been one of the main driver of total factor productivity (hereafter TFP) in the last 30 years and how our results can be theoretically rationalized.
+
+We employ Structural VARs to investigate the effects of ICT supply shocks on Total Factor Productivity (TFP) and other macroeconomic variables.
+In response to this sector-specific supply shock relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a delayed significant and persistent increase.
+In line with theories of ICT as a general-purpose technology, we analyze a two-sector general equilibrium model in order to rigorously rationalize previous results and estimate key parameters via impulse-response matching.
+We conclude that ICT accumulation is able to enhance productivity through a positive spillover effect which takes into account the overall level of diffusion of ICT capital in the economy.
 

### 2018-06-05 Latex/Draft_Summer2018/Summer2018.tex
Few details

@@
 We employ Structural VARs to investigate the effects of ICT supply shocks on Total Factor Productivity (TFP) and other macroeconomic variables.
-In response to this sector-specific supply shock relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a delayed significant and persistent increase.
-In line with theories of ICT as a general-purpose technology, we analyze a two-sector general equilibrium model in order to rigorously rationalize previous results and estimate key parameters via impulse-response matching.
+In response to this sector-specific supply shock relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a significant delayed and persistent increase.
+In line with theories of ICT as a general-purpose technology, we analyze a two-sector general equilibrium model in order to rationalize previous results and estimate key parameters via impulse-response matching.
 We conclude that ICT accumulation is able to enhance productivity through a positive spillover effect which takes into account the overall level of diffusion of ICT capital in the economy.}

### 2018-06-07 Latex/Draft_Summer2018/Summer2018.tex
keep writing the intro

@@
 Although there is large consensus on the importance of productivity as a driver of economic performances, less agreement is on the underlying sources that enhance its growth.
-For several years, most of the business-cycle literature purposely decided to avoid such a question by proxying movements in productivity as random shocks.\footnote{\cite{kydland1982time} and \cite{long1983real} are among the first papers which consider productivity shocks on a general equilibrium model.}
-
-However, the robust empirical evidence of the slowdown in productivity right before the great recession is summoning the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
+For several years, most of the business-cycle literature purposely decided to avoid such a question by proxying movements in productivity as random shocks.\footnote{\cite{kydland1982time} and \cite{long1983real} are among the first papers which consider productivity shocks on a general equilibrium model.} However, the robust empirical evidence of the slowdown in productivity right before the great recession is summoning the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
 
@@
 In particular, \cite{bianchi2014growth} augment a DSGE  model using a quality ladders model in the vein of \cite{grossman1991quality}.
-Moreover, \cite{anzoategui2016endogenous} and \cite{moran2017innovation}, similarly to \cite{comin2006medium}, use a model of expanding variety in the vein of \cite{romer1990endogenous}.} Consistent with those previous models, some other papers are exerting effort to show that although research effort is rising, the productivity of the research sector is slowing down.\footnote{\cite{jones2009burden} and \cite{bloom2017ideas} are two important contributions that highlight those facts.}
+Moreover, \cite{anzoategui2016endogenous} and \cite{moran2017innovation}, similarly to \cite{comin2006medium}, use a model of expanding variety in the vein of \cite{romer1990endogenous}.} Consistent with those previous models, some other papers provide some empirical evidence of a slowdown in the productivity of the R\&D sector.
+Specifically, they show that although research effort is rising, the rate of new ideas and discoveries is slowing down.\footnote{\cite{jones2009burden} and \cite{bloom2017ideas} are two important contributions that highlight those facts.}
 
-Motivated by this wave of research, in this paper we empirically investigate which has been one of the main driver of total factor productivity (hereafter TFP) in the last 30 years and how our results can be theoretically rationalized.
+Motivated by this wave of research, this paper follows a different path and argue that Information and Communication Technology (ICT) plays an important role in driving medium-term productivity in sectors that are ICT users.
+Our contribution is twofold.
+First, we provide a robust empirical evidence to show that ICT-investment is positively related with future TFP.
+Second, we analyze a standard theoretical framework in order to both motivate and explain our empirical results.
+
+Regarding the empirical section, the idea is to identify supply (technological) shocks which are only specific to the ICT sector in a standard Structural VAR.\footnote{An interesting paper which are somehow related to our empirical part is \cite{jafari2012impact}.
+The authors identify ICT shocks as a potential driver of the Iranian business cycle using a completely different identification strategy and obtaining qualitatively different results.} In a multivariate system where TFP and ICT investment are ordered respectively first and second, we look for a shock which does not affect TFP on impact but that maximize the impact effect on ICT investment.
 

### 2018-06-07 Latex/Draft_Summer2018/Summer2018.tex
Keeeeep writing

@@
 Regarding the empirical section, the idea is to identify supply (technological) shocks which are only specific to the ICT sector in a standard Structural VAR.\footnote{An interesting paper which are somehow related to our empirical part is \cite{jafari2012impact}.
-The authors identify ICT shocks as a potential driver of the Iranian business cycle using a completely different identification strategy and obtaining qualitatively different results.} In a multivariate system where TFP and ICT investment are ordered respectively first and second, we look for a shock which does not affect TFP on impact but that maximize the impact effect on ICT investment.
+The authors identify ICT shocks as a potential driver of the Iranian business cycle using a completely different identification strategy and obtaining qualitatively different results.} In order to have a reliable identification procedure our multivariate system needs to embody three key variables: TFP, ICT investment (hereafter ICTI), and relative prices (hereafter RP).
+Importantly, ICTI is defined as the total expenditure in equipment and computer software meant to be used in production for more than an year.
+Thus, an increase in ICTI has to be though as an ICT capital deepening.
+Moreover RP is simply the ration between prices in the ICT sector over prices in the overall economy.
+As pointed out by
+
+In other words, In order to identify a ICT supply shock, we expect it to be orthogonal to current TFP because the ICT sector accounts for a negligible part in the whole economy.
+In addition, ICT supply shocks should enhance the usage of this ICT goods and services
+
+ we seek a shock which are ordered respectively first and second, we look for a shock which does not affect TFP on impact but that maximize the impact effect on ICT investment.
 

### 2018-06-07 Latex/Draft_Summer2018/Summer2018.tex
moooore writing

@@
 Although there is large consensus on the importance of productivity as a driver of economic performances, less agreement is on the underlying sources that enhance its growth.
-For several years, most of the business-cycle literature purposely decided to avoid such a question by proxying movements in productivity as random shocks.\footnote{\cite{kydland1982time} and \cite{long1983real} are among the first papers which consider productivity shocks on a general equilibrium model.} However, the robust empirical evidence of the slowdown in productivity right before the great recession is summoning the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
+For several years, most of the business-cycle literature purposely decided to avoid such a question by proxying movements in productivity as random shocks.\footnote{\cite{kydland1982time} and \cite{long1983real} are among the first papers which consider productivity shocks on general equilibrium models.} However, the robust empirical evidence of the slowdown in productivity right before the great recession is summoning the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
 
@@
 In particular, \cite{bianchi2014growth} augment a DSGE  model using a quality ladders model in the vein of \cite{grossman1991quality}.
-Moreover, \cite{anzoategui2016endogenous} and \cite{moran2017innovation}, similarly to \cite{comin2006medium}, use a model of expanding variety in the vein of \cite{romer1990endogenous}.} Consistent with those previous models, some other papers provide some empirical evidence of a slowdown in the productivity of the R\&D sector.
-Specifically, they show that although research effort is rising, the rate of new ideas and discoveries is slowing down.\footnote{\cite{jones2009burden} and \cite{bloom2017ideas} are two important contributions that highlight those facts.}
+Moreover, \cite{anzoategui2016endogenous} and \cite{moran2017innovation}, similarly to \cite{comin2006medium}, use a model of expanding variety in the vein of \cite{romer1990endogenous}.} Consistent with those previous models, other papers attempt to provide empirical evidence of a slowdown in the productivity of the R\&D sector.
+Specifically, they show that although research effort is keeping rising, the rate of new ideas and discoveries is slowing down.\footnote{\cite{jones2009burden} and \cite{bloom2017ideas} are two important contributions that highlight those facts.}
 
@@
 Our contribution is twofold.
-First, we provide a robust empirical evidence to show that ICT-investment is positively related with future TFP.
+First, we provide a robust empirical evidence to show that current rises in ICT-investment explains significant and persistent increases in future Total Factor Productivity (hereafter TFP).
 Second, we analyze a standard theoretical framework in order to both motivate and explain our empirical results.
 
-Regarding the empirical section, the idea is to identify supply (technological) shocks which are only specific to the ICT sector in a standard Structural VAR.\footnote{An interesting paper which are somehow related to our empirical part is \cite{jafari2012impact}.
+Regarding the empirical section, the idea is to identify supply (technological) shocks which are only specific to the ICT sector in a Structural VAR context.\footnote{An interesting paper which is somehow related to our empirical part is \cite{jafari2012impact}.
 The authors identify ICT shocks as a potential driver of the Iranian business cycle using a completely different identification strategy and obtaining qualitatively different results.} In order to have a reliable identification procedure our multivariate system needs to embody three key variables: TFP, ICT investment (hereafter ICTI), and relative prices (hereafter RP).

### 2018-06-08 Latex/Draft_Summer2018/Summer2018.tex
writing

@@
 
-Motivated by this wave of research, this paper follows a different path and argue that Information and Communication Technology (ICT) plays an important role in driving medium-term productivity in sectors that are ICT users.
+Motivated by this wave of research, this paper follows a different path and argue that Information and Communication Technology (hereafter ICT) plays an important role in driving medium-term productivity in sectors that are ICT users.
 Our contribution is twofold.
-First, we provide a robust empirical evidence to show that current rises in ICT-investment explains significant and persistent increases in future Total Factor Productivity (hereafter TFP).
+First, we provide a robust empirical evidence to show that current rises in ICT investment explains significant and persistent increases in future Total Factor Productivity (hereafter TFP).
 Second, we analyze a standard theoretical framework in order to both motivate and explain our empirical results.
@@
 Thus, an increase in ICTI has to be though as an ICT capital deepening.
-Moreover RP is simply the ration between prices in the ICT sector over prices in the overall economy.
-As pointed out by
+Moreover RP is the ratio between prices in the ICT sector over prices in the overall economy.
+To verify that we are correctly identifying an ICT technology shock, we firstly expect it to be orthogonal to the productivity of all the other sectors.
+Since the share of the ICT sector accounts for a negligible part in the whole economy we expect it should have an approximately zero effect on TFP.
+Moreover, as pointed out by \cite{greenwood1997long} and \cite{fisher2006dynamic}, embodying RP and ICTI is important because we expect that a sectoral supply shock should decrease its relative prices and enhance expenditure in the underlying sector.\footnote{However, as suggested by both \cite{greenwood2000role} and \cite{basu2010sector}, we are aware that conditioning our identifying restrictions only on the direction of RP does not properly measure for technological changes between sectors.
+This is the main reason why we never impose the direction of RP as an direct identifying condition.}
 
-In other words, In order to identify a ICT supply shock, we expect it to be orthogonal to current TFP because the ICT sector accounts for a negligible part in the whole economy.
-In addition, ICT supply shocks should enhance the usage of this ICT goods and services
+\
 

### 2018-06-09 Latex/Draft_Summer2018/Summer2018.tex
another bit of the presentation

@@
 Although there is large consensus on the importance of productivity as a driver of economic performances, less agreement is on the underlying sources that enhance its growth.
-For several years, most of the business-cycle literature purposely decided to avoid such a question by proxying movements in productivity as random shocks.\footnote{\cite{kydland1982time} and \cite{long1983real} are among the first papers which consider productivity shocks on general equilibrium models.} However, the robust empirical evidence of the slowdown in productivity right before the great recession is summoning the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
+For several years most of the business-cycle literature purposely decided to avoid such a question by proxying movements in productivity as random shocks.\footnote{\cite{kydland1982time} and \cite{long1983real} are among the first papers which consider productivity shocks on general equilibrium models.} However, the robust empirical evidence of the slowdown in productivity right before the great recession is summoning the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
 
@@
 First, we provide a robust empirical evidence to show that current rises in ICT investment explains significant and persistent increases in future Total Factor Productivity (hereafter TFP).
-Second, we analyze a standard theoretical framework in order to both motivate and explain our empirical results.
+Second, we analyze a standard theoretical framework in order to both motivate and rationalize our empirical results.
 
-Regarding the empirical section, the idea is to identify supply (technological) shocks which are only specific to the ICT sector in a Structural VAR context.\footnote{An interesting paper which is somehow related to our empirical part is \cite{jafari2012impact}.
+Regarding the empirical section, the idea is to identify technological shocks which are only specific to the ICT sector in a Structural VAR context.\footnote{An interesting paper which is somehow related to our empirical part is \cite{jafari2012impact}.
 The authors identify ICT shocks as a potential driver of the Iranian business cycle using a completely different identification strategy and obtaining qualitatively different results.} In order to have a reliable identification procedure our multivariate system needs to embody three key variables: TFP, ICT investment (hereafter ICTI), and relative prices (hereafter RP).
@@
 Since the share of the ICT sector accounts for a negligible part in the whole economy we expect it should have an approximately zero effect on TFP.
-Moreover, as pointed out by \cite{greenwood1997long} and \cite{fisher2006dynamic}, embodying RP and ICTI is important because we expect that a sectoral supply shock should decrease its relative prices and enhance expenditure in the underlying sector.\footnote{However, as suggested by both \cite{greenwood2000role} and \cite{basu2010sector}, we are aware that conditioning our identifying restrictions only on the direction of RP does not properly measure for technological changes between sectors.
-This is the main reason why we never impose the direction of RP as an direct identifying condition.}
+Moreover, as pointed out by \cite{greenwood1997long} and \cite{fisher2006dynamic}, embodying RP and ICTI is important because we expect that a sectoral technology shock should decrease its relative prices and enhance expenditure in the underlying sector.\footnote{However, as suggested by both \cite{greenwood2000role} and \cite{basu2010sector}, we are aware that conditioning our identifying restrictions only on the direction of RP does not properly measure for technological changes between sectors.
+This is the main reason why we never impose the direction of RP as an direct identifying condition.} In response to this shock, ICTI rises on impact and remains significant for several quarters.
+RP persistently and significantly declines for more than two years and TFP, which does not react on impact, rises after few quarters and remains significant and stable for at least 5 years.
+
+Although our results are robust over different specifications, there is an important critique that our empirical strategy had to carefully take into account, which is the reverse causality due to news on future TFP.
+A well-taken concern motivated my the news-shock literature is that the positive reaction of ICTI on impact may be triggered to signals related future increases in TFP and not to contemporaneous ICT technological improvements.
+In other words, our identification strategy may confound a news shock which contemporaneously enhances investment in ICT capital goods.
+In order to take into account this potential issue, we provide a series of robustness check where sequentially we firstly identify a news shock in the spirit of \cite{barsky2011news} and subsequently we identify our sectoral ICT shock using the previous identification strategy.
+Encouragingly, controlling for signals regarding future movements in TFP does not affect any conclusion drown so far.
+In particular, we can now state even more strongly the causality relation from movements in current ICT technological changes to future TFP.
+
+In order to formally explain which mechanism links current ICT to future TFP, we analyze a 2-sector DSGE model which allows ICT to be the general purpose technology of the whole economy.
 
@@
 We employ Structural VARs to investigate the effects of ICT supply shocks on Total Factor Productivity (TFP) and other macroeconomic variables.
-In response to this sector-specific supply shock relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a delayed significant and persistent increase.
+In response to this sector-specific technology shock relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a delayed significant and persistent increase.
 In line with theories of ICT as a general-purpose technology, we analyze a two-sector general equilibrium model in order to rigorously rationalize previous results and estimate key parameters via impulse-response matching.

### 2018-06-09 Latex/Draft_Summer2018/Summer2018.tex
not much

@@
 
- we seek a shock which are ordered respectively first and second, we look for a shock which does not affect TFP on impact but that maximize the impact effect on ICT investment.
-
-We employ Structural VARs to investigate the effects of ICT supply shocks on Total Factor Productivity (TFP) and other macroeconomic variables.
-In response to this sector-specific technology shock relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a delayed significant and persistent increase.
 In line with theories of ICT as a general-purpose technology, we analyze a two-sector general equilibrium model in order to rigorously rationalize previous results and estimate key parameters via impulse-response matching.

### 2018-06-09 Latex/Draft_Summer2018/Summer2018.tex
Writing the introduction

@@
 
-Along \cite{comin2006medium}, some theoretical contributions rationalize endogenous productivity dynamics by adapting features of endogenous growth models into DSGE models.
+Along with \cite{comin2006medium}, some theoretical contributions rationalize endogenous productivity dynamics by adapting features of endogenous growth models into DSGE models.
 Following \cite{romer1990endogenous}, most of those papers augment final-good production functions with an expanding composite of intermediate goods produced by the R\&D sector in order to allow for an endogenous rate of adoption of new technologies.\footnote{\cite{bianchi2014growth}, \cite{anzoategui2016endogenous}, and \cite{moran2017innovation} use similar techniques to endogenize growth.
@@
 
-In order to formally explain which mechanism links current ICT to future TFP, we analyze a 2-sector DSGE model which allows ICT to be the general purpose technology of the whole economy.
+In order to formally explain which mechanism links current ICT to future TFP, we analyze a 2-sector DSGE model which allows ICT to be the general purpose technology (hereafter GPT) of the whole economy.
+Both sectoral production functions are fed with three inputs: (i) labor, supplied by households, (ii) hard capital, produced by the final sector, and (iii) ICT capital, produced by the ICT sector.
+Along with \cite{basu2007information}, we interpret the nature of ICT as a GPT in a neoclassical essence since we assume exogenous technological changes in the ICT sector.
+When an ICT technology shock arrives, both sectors accumulate ICT capital since it is easier to produce and cheaper to buy.
+We then assume that an ICT capital deepening positively affects the production function of both sectors through a spillover effect.
+This positive diffusion effect is intrinsically related to the nature of ICT capital, that is, improving the quality and the speed of communication among economic agents.
+However, this quality and speed strongly depends on how many economic agents own this technologies.
+As a simple example, owning a mobile phone enables to contact someone instantaneously if the person you want to reach is endowed by the same technology.
+As a result, the effectiveness of ICT capital is intrinsically related to its own diffusion.
+We rationalize this simple line of thought augmenting the production function of each sector in the economy with a spillover effect driven by the diffusion of ICT capital.
 
@@
 
-In line with theories of ICT as a general-purpose technology, we analyze a two-sector general equilibrium model in order to rigorously rationalize previous results and estimate key parameters via impulse-response matching.
-We conclude that ICT accumulation is able to enhance productivity through a positive spillover effect which takes into account the overall level of diffusion of ICT capital in the economy.
+Allora ecco perche ICT cresce TFP with some lags...
+
+\
+
+Matching parameters and results
+
+\
+
+related literature
+
+\
+
+structure of the paper
+
+\
 

### 2018-06-15 Latex/Draft_Summer2018/Summer2018.tex
Writing + function to find SS numerically (find_SS_numerically.m)

@@
 Both sectoral production functions are fed with three inputs: (i) labor, supplied by households, (ii) hard capital, produced by the final sector, and (iii) ICT capital, produced by the ICT sector.
-Along with \cite{basu2007information}, we interpret the nature of ICT as a GPT in a neoclassical essence since we assume exogenous technological changes in the ICT sector.
-When an ICT technology shock arrives, both sectors accumulate ICT capital since it is easier to produce and cheaper to buy.
-We then assume that an ICT capital deepening positively affects the production function of both sectors through a spillover effect.
-This positive diffusion effect is intrinsically related to the nature of ICT capital, that is, improving the quality and the speed of communication among economic agents.
-However, this quality and speed strongly depends on how many economic agents own this technologies.
-As a simple example, owning a mobile phone enables to contact someone instantaneously if the person you want to reach is endowed by the same technology.
+Along with \cite{basu2007information}, we interpret the nature of ICT as a GPT in a neoclassical essence since we assume that exogenous technological changes in the ICT sector are able to affect economy-wide productivity.
+In particular, when an ICT technology shock arrives, both sectors accumulate ICT capital since it is easier to produce and cheaper to buy.
+This ICT capital deepening consequently enhances the productivity of both sectors by means of a spillover.
+Since the purpose of ICT capital is to improve information sharing, the quality and speed of communication must mainly depend on the diffusion of these technologies among agents.
+As a simple example, owning a mobile phone enables to contact someone instantaneously if the person you want to reach is endowed with the same technology.
 As a result, the effectiveness of ICT capital is intrinsically related to its own diffusion.
-We rationalize this simple line of thought augmenting the production function of each sector in the economy with a spillover effect driven by the diffusion of ICT capital.
+We rationalize this line of thought augmenting the production function of each sector with a spillover effect driven by the diffusion of ICT capital.
+Consistently with the related literature and our empirical results, the accumulation of ICT capital is a slow process and the benefits of an ICT technology shock show up in the production functions of ICT-users with lags.
 
-\
-
-Allora ecco perche ICT cresce TFP with some lags...
-
-\
-
-Matching parameters and results
+As a last step, we use both our empirical and theoretical results to estimate the key parameters of the model via impulse-response function matching to an ICT technology shock.
+The key parameters within this set are (i) the effectiveness of the spillover effect on the production functions, and (ii) the standard deviation and (iii) persistence of ICT technology shocks.
 

### 2018-06-15 Code/oulton2010/find_SS_numerically.m

@@ -1,0 +1,84 @@
+function output = find_SS_numerically(params)
+
+global h chi xi del k bet A rho sigma_z psi_c tau b
+global uu p q qp pp c cp
+global fun1 fun2 fun3 fun4 fun5
+
+bla = structvars(params);
+for i1 = 1:size(bla,1)
+    eval(bla(i1,:));
+end
+
+uu           = log(h+b);
+p            = @(thet) thet/(1+thet^chi)^(1/chi);
+q            = @(thet) 1/((1+thet^chi)^(1/chi));
+qp           = @(thet) -thet^(chi-1)/((1+thet^chi)^(1/chi+1));
+pp           = @(thet) q(thet) + thet*qp(thet);
+c            = @(s) A*((1/(1-s))^(1+psi_c)-1)/(1+psi_c) - A*s;
+cp           = @(s) A*(1/(1-s))^(2+psi_c)- A;
+
+fun1 = @(s,phimax,phimin,L,thet) log(h+b) - log(phimin) - ...
+    bet*( c(s) + (1 - s*p(thet) - del) *  cp(s)/p(thet) ); %same of latex
+
+fun2 = @(s,phimax,phimin,L,thet) - k/q(thet) + 1/2*(1-phimax)^2 + ...
+    (1-phimin)*bet*(1-del)*k/q(thet) ; %same of latex
+
+fun3 = @(s,phimax,phimin,L,thet) - cp(s)/p(thet) + log(phimax) + phimin*(1-log(phimin)) ...
+    - phimax + (1-phimin)*(- uu + bet*(c(s) +  (1 - s*p(thet) - del) *  cp(s)/p(thet)));
+
+fun4 = @(s,phimax,phimin,L,thet) - L + ( (1-del)*L + p(thet)*s*(1-L) )*(1-phimin);
+
+fun5 = @(s,phimax,phimin,L,thet) - xi*k*thet/phimax + (1-xi)*cp(s);
+
+%Evaluate the steady state for a simplified version of Mitman and
+%Rabinovich
+OPTIONS = optimoptions('lsqnonlin');
+OPTIONS.OptimalityTolerance = 1e-10;
+OPTIONS.StepTolerance = 1e-10;
+OPTIONS.FunctionTolerance = 1e-10;
+
+x0 = [0.1,0.9,0.1,0.9,10];
+lb = [0,0,0,0,0.00001];
+ub = [1,1,1,1,1000000];
+[x,res] = lsqnonlin(@problem,x0,lb,ub,OPTIONS);
+
[…]

### 2018-06-19 Latex/Draft_Summer2018/Summer2018.tex
more writing

@@
 As a last step, we use both our empirical and theoretical results to estimate the key parameters of the model via impulse-response function matching to an ICT technology shock.
-The key parameters within this set are (i) the effectiveness of the spillover effect on the production functions, and (ii) the standard deviation and (iii) persistence of ICT technology shocks.
+The key parameters within this set are (i) the elasticity of productivity to ICT capital diffusion, namely the parameter which governs the spillover effect, and (ii) the standard deviation and (iii) persistence of ICT technology shocks.
+Results consistently point out a positive spillover effect of ICT capital deepening on TFP suggesting that the assumptions made in the theoretical model are supported by our empirical results.
+We confirm that ICT is a general-purpose technology which enhance productivity of ICT capital users through a spillover effect related to its own diffusion.
 
-\
+Our paper is mainly related to three strands of literature.
+First of all, we link to the literature that investigates the recent slowdown in TFP growth.
+Our project is motivated by papers such as \cite{oliner2007explaining}, \cite{jorgenson2008retrospective}, \cite{byrne2016does}, \cite{cette2016pre}, and \cite{fernald2017disappointing} who document that the slowdown in TFP growth occurred before the recession implying that the financial crisis per se cannot be its cause.\footnote{In particular, in line with our results, also \cite{fernald2017disappointing} conclude that the pause in the information technology revolution is the main candidate explanation.} Secondly, our project is related to the literature that investigate the effects of investment-specific technology shocks in a multi-sector economy.
+In particular, throughout the paper our main references will be \cite{greenwood1997long}, \cite{oulton2007investment}, and \cite{fisher2006dynamic}.
+However, both the empirical exercise and the theoretical model are strictly related to \cite{greenwood2000role}, \cite{basu2010sector}, and \cite{justiniano2011investment}.
+Finally, this paper is also related to papers that argue that information and communication technology is the current general-purpose technology.
+Main references will be \cite{bresnahan1992general}, and \cite{basu2007information}.
 
-related literature
-
-\
-
-structure of the paper
-
-\
+The paper is structured as follows.
+We present empirical results and robustness checks in Section \ref{section:empirics}.
+We then present and analyze the 2-sector DSGE model in Section \ref{section:theory}.
+We estimate via impulse-response matching key parameters of the model and run a series of related experiment in Section \ref{section:experiments}.
+Concluding remarks, caveats and prospective future research are discussed in Section \ref{section:conclusions}.
 
 %%%%%%%%%%%%%%%%%%%%%%            EMPIRICS                     %%%%%%%%%%%%%%%%%%%
-\section{Empirics}
+\section{Empirics}\label{section:empirics}
 
 %%%%%%%%%%%%%%%%%%%%               MODEL                 %%%%%%%%%%%%%%%%%% 
-\section{Model}
+\section{Model}\label{section:theory}
+
+%%%%%%%%%%%%%%%%%%%%               MODEL                 %%%%%%%%%%%%%%%%%% 
+\section{Model}\label{section:experiments}
 
 %%%%%%%%%%%%%%%%%%%%               CONCLUSION                 %%%%%%%%%%%%%%%%%% 
-\section{Conclusion}
+\section{Conclusion}\label{section:conclusions}
 hjklbhjkl

### 2018-06-23 Latex/Draft_Summer2018/Summer2018.tex
Introduction complete + new specification with hours

@@
-\documentclass[14pt]{article}
+\documentclass[12pt]{article}
 
@@
 \usepackage{hyperref}
-\usepackage{extsizes}
+%\usepackage{extsizes}
 \usepackage[font=footnotesize,labelfont=bf]{caption}
@@
 \maketitle
+
+\
+
+\
+
+\
 %%%%%%%%%%%%%%%%%%%%             ABSTRACT           %%%%%%%%%%%%%%%%%% 
@@
 
+\begin{comment}
 Our paper is mainly related to three strands of literature.
@@
 Finally, this paper is also related to papers that argue that information and communication technology is the current general-purpose technology.
-Main references will be \cite{bresnahan1992general}, and \cite{basu2007information}.
+Main references will be bresnan, and \cite{basu2007information}.
+\end{comment}
 
 The paper is structured as follows.
-We present empirical results and robustness checks in Section \ref{section:empirics}.
+We present empirical results and main robustness checks in Section \ref{section:empirics}.
 We then present and analyze the 2-sector DSGE model in Section \ref{section:theory}.

### 2018-06-23 Code/just_IT_vecm/main_file_just_IT.m

@@ -5,7 +5,7 @@
 % Code by Marco Brianti and Laura Gati, Boston College, 2018
 %**************************************************************
 
-clear 
+clear
 close all
 
 current_dir = pwd;
@@ -25,7 +25,7 @@ tic
 %Data Reading and Transformation
 filename = 'dataset_main';
 sheet    = 'Data';
-range    = 'B1:W287';
+range    = 'B1:Z287';
 warning off
 [data, varnames] = read_data2(filename, sheet, range);
 warning on
@@ -53,7 +53,7 @@ which_shock = 2; %[pos_IT];
 %Technical Parameters
 max_lags        = 10;
 nburn           = 0; %with the Kilian correction better not burning!!!
-nsimul          = 200; %5000
+nsimul          = 2000; %5000
 nvar            = size(data,2);
 sig1            = 0.9; % significance level
 sig2            = 0.95; % a 2nd sig. level
@@ -64,27 +64,16 @@ which_variable  = which_shock; % select IT as the variable whose FEV we wanna ma
 %%Checking the number of lags over BIC, AIC, and HQ (see 'Lecture2M' in our folder)
 [AIC,BIC,HQ] = aic_bic_hq(data,max_lags);
 if AIC >= 4
-      nlags = 1; % 2;
+      nlags = 2; % 2;
       warning(['AIC > 4, setting nlags to ', num2str(nlags) ])
 else
       nlags = AIC;
 end
 
-procedure = 'VAR';
-switch procedure
-      case 'VAR'
-            %Run VAR imposing Cholesky
-            [A,B,res,sigma] = sr_var(data, nlags);
-            %Checking if the VAR is stationary
-            test_stationarity(B');
-            
-      case 'VECM'
-            %Run VECM
-            constant = 0;
-            [Pi,B,res,sigma] = VECM(data, nlags, constant);
-            %Static rotation matrix
-            A = chol(sigma)';
-end
+%Run VAR imposing Cholesky
+[A,B,res,sigma] = sr_var(data, nlags);
+%Checking if the VAR is stationary
+test_stationarity(B');
 
 % Implement the "just IT" ID strategy in a VAR
 H_max = 40;
@@ -93,26 +82,18 @@ H_max = 40;
 % Bootstrap
[…]

### 2018-06-23 invoke_export_fig.m

@@ -17,10 +17,10 @@ if use_current_time==1
     ct1 = strrep(current_time,':','_'); % substitute : with _
     ct2 = strrep(ct1,' ','_'); % substitute spaces with _
     
-    final_name = ['fig_' figname '_' some_comment '_' ct2 '.png'];
+    final_name = ['fig_' figname '_' some_comment '_' ct2 '.pdf'];
     
 else
-    final_name = ['fig_' figname '_' some_comment '.png'];
+    final_name = ['fig_' figname '_' some_comment '.pdf'];
 end
 
 if nargin < 4

### 2018-06-26 Latex/Draft_Summer2018/Summer2018.tex
Some writing + empirical exercises

@@
 
+In this section, we present our main empirical set of results.
+Our attempt is to properly identify technological shocks which are only specific to the ICT sector in a Structural VAR context and analyze their impact on key macroeconomic variables.
+At the best of our knowledge, there is only another paper that attempts a similar exercise: \cite{jafari2012impact}.
+Although also this paper identifies ICT shocks, the authors use Iranian data and both identification strategy and main results are qualitatively different.
+
+\section{Main Specification}
+
+In this section we present our main specification where we impose minimal discipline on the identification strategy.
+It turns out that those set of results presented here are consistent with different robustness checks.
+Our first-step specification is the following 6-variable VAR
+\begin{equation}
+\begin{pmatrix}
+TFP_t \\ 
+IT_t \\
+GDP_t \\
+C_t \\
+H_t \\
+RP_t \\
+\end{pmatrix} = B(L) \begin{pmatrix}
+TFP_{t-1} \\ 
+IT_{t-1} \\
+GDP_{t-1+5|t-1} \\
+C_{t-1} \\
+H_{t-1} \\
+RP_{t-1} \\
+\end{pmatrix} + i_t
+\end{equation}
+where $TFP_t$ is the log-level of Fernald total factor productivity, $H_{t}$ is the level of total number of hours worked per person, $MI_{t+5|t}$ is the level of Michigan Index of business confidence over 5 years, $IT_t$ is the log-level of IT investment, $GDP_t$ is the log-level of real gross domestic product, and $C_t$ is the log-level of real consumption.
+All the variables refer to the U.S.
+economy.
+$B(L)$ is a ($6\times 6$) matrix of lag-operator functions of the same order.
+In our favorite specification the order of the lag operator functions is two which implies that we regress variables at time $t$ with their own lagged values at $t-1$ and $t-2$.
+Finally, $i_t$ is a ($6\times 1$) vector of correlated innovations where $\Omega = i'_t i_t$.
+
+In order to derive structural shocks $s_t$ from innovations $i_t$ we use a standard Cholesky identification strategy which imposes 15 zero-impact restrictions.
+Our identification strategy aims to identify a news shock and a IT productivity shock.
+In particular, we adhere to the following definitions of our shocks of interest.
+In line with the news shock literature, a news shock is defined as a signal regarding the future exogenous component of TFP.\footnote{In much of the news shock literature, this definition is not explicit in terms of \emph{exogenous} TFP, because in the absence of an endogenous TFP mechanism, exogenous TFP and total TFP are by definition the same object.
+Thus, defining a news shock as the shock that moves TFP over the long horizon implicitly amounts to saying that news move exogenous TFP.} The IT productivity shock (also IT shock) is by definition an increase in the sector-specific productivity that should lead to a natural increase in the IT level of investment.
+%Can we speak here about substitution effect?
+The reason why we seek to identify also this second shock is because we want to disentangle the rise in IT investment given by an increase in the sector-specific productivity to the rise in IT investment due to future signals on exogenous TFP.
+%In other words, in order to size the self-enforcement effect of a news shock we need to disentangle the endogenous component embodied by an IT productivity shock, and, on the other hand, to correctly size the pure effect of an IT productivity shock we need to disentangle from IT its expectational component.
+
 %%%%%%%%%%%%%%%%%%%%               MODEL                 %%%%%%%%%%%%%%%%%% 

### 2018-06-26 Code/just_IT_vecm/main_file_just_IT.m

@@ -53,7 +53,7 @@ which_shock = 2; %[pos_IT];
 %Technical Parameters
 max_lags        = 10;
 nburn           = 0; %with the Kilian correction better not burning!!!
-nsimul          = 2000; %5000
+nsimul          = 1000; %5000
 nvar            = size(data,2);
 sig1            = 0.9; % significance level
 sig2            = 0.95; % a 2nd sig. level
@@ -64,7 +64,7 @@ which_variable  = which_shock; % select IT as the variable whose FEV we wanna ma
 %%Checking the number of lags over BIC, AIC, and HQ (see 'Lecture2M' in our folder)
 [AIC,BIC,HQ] = aic_bic_hq(data,max_lags);
 if AIC >= 4
-      nlags = 2; % 2;
+      nlags = 1; % 2;
       warning(['AIC > 4, setting nlags to ', num2str(nlags) ])
 else
       nlags = AIC;
@@ -81,8 +81,8 @@ H_max = 40;
 
 % Bootstrap
 which_ID = 'just_IT';
-which_correction = 'blocks'; % [none, blocks] --> Choose whether to draws residuals in blocks or not.
-blocksize = 10; % size of block for drawing in blocks
+which_correction = 'none'; % [none, blocks] --> Choose whether to draws residuals in blocks or not.
+blocksize = 30; % size of block for drawing in blocks
 [beta_tilde, data_boot2, beta_tilde_star, nonstationarities] = ...
       bootstrap_with_kilian(B, nburn, res, ...
       nsimul, which_correction, blocksize);
@@ -108,7 +108,7 @@ end
 
 %Creating and Printing figures
 comment = [which_ID '_' char(varnames(pos_IT))];
-print_figs = 'yes';
+print_figs = 'no';
 
 [IRFs, ub1, lb1, ub2, lb2] = genIRFs(fake_impact,fake_impact_boot,...
       B,beta_tilde_star,H,sig1, sig2);

### 2018-06-26 Latex/Draft_Summer2018/Summer2018.tex
moire work

@@
 To verify that we are correctly identifying an ICT technology shock, we firstly expect it to be orthogonal to the productivity of all the other sectors.
-Since the share of the ICT sector accounts for a negligible part in the whole economy we expect it should have an approximately zero effect on TFP.
+Since the share of the ICT sector accounts for a negligible part in the whole economy we expect it should have an approximately zero effect on TFP on impact.
 Moreover, as pointed out by \cite{greenwood1997long} and \cite{fisher2006dynamic}, embodying RP and ICTI is important because we expect that a sectoral technology shock should decrease its relative prices and enhance expenditure in the underlying sector.\footnote{However, as suggested by both \cite{greenwood2000role} and \cite{basu2010sector}, we are aware that conditioning our identifying restrictions only on the direction of RP does not properly measure for technological changes between sectors.
@@
 In other words, our identification strategy may confound a news shock which contemporaneously enhances investment in ICT capital goods.
-In order to take into account this potential issue, we provide a series of robustness check where sequentially we firstly identify a news shock in the spirit of \cite{barsky2011news} and subsequently we identify our sectoral ICT shock using the previous identification strategy.
+In order to take into account this potential issue, we provide a series of robustness checks where sequentially we firstly identify a news shock in the spirit of \cite{barsky2011news} and subsequently we identify our sectoral ICT shock using the previous identification strategy.
 Encouragingly, controlling for signals regarding future movements in TFP does not affect any conclusion drown so far.
@@
 
-In order to formally explain which mechanism links current ICT to future TFP, we analyze a 2-sector DSGE model which allows ICT to be the general purpose technology (hereafter GPT) of the whole economy.
+Motivated by papers in line with \cite{oliner2000resurgence} and \cite{stiroh2002information}, in order to formally explain which mechanism links current ICT to future TFP, we analyze a 2-sector DSGE model which allows ICT to be the general purpose technology (hereafter GPT) of the whole economy.
 Both sectoral production functions are fed with three inputs: (i) labor, supplied by households, (ii) hard capital, produced by the final sector, and (iii) ICT capital, produced by the ICT sector.
-Along with \cite{basu2007information}, we interpret the nature of ICT as a GPT in a neoclassical essence since we assume that exogenous technological changes in the ICT sector are able to affect economy-wide productivity.
+As well-explained by both \cite{basu2003case} and \cite{basu2007information}, a GPT should be able to enhance accelerations in productivity in sectors that are users of the underlying technology.
+We then interpret ICT as the GPT of the last 30 years of the U.S.
+economy assuming that exogenous technological changes in the ICT sector are able to affect economy-wide productivity.
 In particular, when an ICT technology shock arrives, both sectors accumulate ICT capital since it is easier to produce and cheaper to buy.
@@
 We rationalize this line of thought augmenting the production function of each sector with a spillover effect driven by the diffusion of ICT capital.
-Consistently with the related literature and our empirical results, the accumulation of ICT capital is a slow process and the benefits of an ICT technology shock show up in the production functions of ICT-users with lags.
+Consistently with this literature and our empirical results, the accumulation of ICT capital is a slow process and the benefits of an ICT technology shock show up in the production functions of ICT-users with lags.\footnote{Notice that differently to \cite{basu2003case} and \cite{basu2007information}, we interpret the general-purpose nature of ICT in the spirit of an endogenous growth model.}
 
@@
 
-In this section, we present our main empirical set of results.
+In this section we present our main empirical set of results.
 Our attempt is to properly identify technological shocks which are only specific to the ICT sector in a Structural VAR context and analyze their impact on key macroeconomic variables.
@@
 Our first-step specification is the following 6-variable VAR
+
+\
+
+DO NOT READ
+
+\
+
 \begin{equation}

### 2018-06-26 Code/just_IT_vecm/main_file_just_IT.m

@@ -64,7 +64,7 @@ which_variable  = which_shock; % select IT as the variable whose FEV we wanna ma
 %%Checking the number of lags over BIC, AIC, and HQ (see 'Lecture2M' in our folder)
 [AIC,BIC,HQ] = aic_bic_hq(data,max_lags);
 if AIC >= 4
-      nlags = 1; % 2;
+      nlags = 2; % 2;
       warning(['AIC > 4, setting nlags to ', num2str(nlags) ])
 else
       nlags = AIC;

### 2018-06-28 Latex/Draft_Summer2018/Summer2018.tex
Empirical part - beginning

@@
 Moreover RP is the ratio between prices in the ICT sector over prices in the overall economy.
-To verify that we are correctly identifying an ICT technology shock, we firstly expect it to be orthogonal to the productivity of all the other sectors.
+To verify that we are correctly identifying an ICT technology shock, we firstly expect it to be orthogonal to the current productivity of all the other sectors.
 Since the share of the ICT sector accounts for a negligible part in the whole economy we expect it should have an approximately zero effect on TFP on impact.
@@
 Our attempt is to properly identify technological shocks which are only specific to the ICT sector in a Structural VAR context and analyze their impact on key macroeconomic variables.
-At the best of our knowledge, there is only another paper that attempts a similar exercise: \cite{jafari2012impact}.
-Although also this paper identifies ICT shocks, the authors use Iranian data and both identification strategy and main results are qualitatively different.
 
@@
 In this section we present our main specification where we impose minimal discipline on the identification strategy.
-It turns out that those set of results presented here are consistent with different robustness checks.
-Our first-step specification is the following 6-variable VAR
-
-\
-
-DO NOT READ
-
-\
-
+It turns out that the set of results presented here are consistent with different robustness checks.
+Our first-step specification is the following 5-variable VAR
 \begin{equation}
@@
 TFP_t \\ 
-IT_t \\
+ICT_t \\
 GDP_t \\
 C_t \\
-H_t \\
 RP_t \\
@@
 TFP_{t-1} \\ 
-IT_{t-1} \\
-GDP_{t-1+5|t-1} \\
+ICT_{t-1} \\
+GDP_{t-1} \\
 C_{t-1} \\
-H_{t-1} \\
 RP_{t-1} \\
@@
 \end{equation}
-where $TFP_t$ is the log-level of Fernald total factor productivity, $H_{t}$ is the level of total number of hours worked per person, $MI_{t+5|t}$ is the level of Michigan Index of business confidence over 5 years, $IT_t$ is the log-level of IT investment, $GDP_t$ is the log-level of real gross domestic product, and $C_t$ is the log-level of real consumption.
+where $TFP_t$ is the log-level of Fernald total factor productivity at time $t$, $ICT_{t}$ is the log-level of real information and communication technology investment at time $t$,\footnote{Notice that $ICTI_t$ is defined as the total expenditure at time $t$ in equipment and computer software meant to be used in production for more than an year.} $GDP_t$ is the log-level of real gross domestic product at time $t$, $C_t$ is the log-level of real consumption at time $t$, and $RP_t$ is the log-deviation of ratio between prices of ICT goods and services and the consumer price index (CPI).
 All the variables refer to the U.S.
 economy.
-$B(L)$ is a ($6\times 6$) matrix of lag-operator functions of the same order.
-In our favorite specification the order of the lag operator functions is two which implies that we regress variables at time $t$ with their own lagged values at $t-1$ and $t-2$.
-Finally, $i_t$ is a ($6\times 1$) vector of correlated innovations where $\Omega = i'_t i_t$.
+$B(L)$ is a ($5\times 5$) matrix of lag-operator functions of the same order.
+Following the Bayesian Information Criterion (BIC), the lag operator functions is one which implies that we regress variables at time $t$ with their own lagged values at $t-1$.\footnote{The Hannan-Quinn Criterion (HQ) suggests to use two lags.
+Results remains consistent following this second criterion.} Finally, $i_t$ is a ($6\times 1$) vector of correlated innovations where $\Omega = i'_t i_t$.
 
-In order to derive structural shocks $s_t$ from innovations $i_t$ we use a standard Cholesky identification strategy which imposes 15 zero-impact restrictions.
-Our identification strategy aims to identify a news shock and a IT productivity shock.
-In particular, we adhere to the following definitions of our shocks of interest.
-In line with the news shock literature, a news shock is defined as a signal regarding the future exogenous component of TFP.\footnote{In much of the news shock literature, this definition is not explicit in terms of \emph{exogenous} TFP, because in the absence of an endogenous TFP mechanism, exogenous TFP and total TFP are by definition the same object.
-Thus, defining a news shock as the shock that moves TFP over the long horizon implicitly amounts to saying that news move exogenous TFP.} The IT productivity shock (also IT shock) is by definition an increase in the sector-specific productivity that should lead to a natural increase in the IT level of investment.
-%Can we speak here about substitution effect?
-The reason why we seek to identify also this second shock is because we want to disentangle the rise in IT investment given by an increase in the sector-specific productivity to the rise in IT investment due to future signals on exogenous TFP.
-%In other words, in order to size the self-enforcement effect of a news shock we need to disentangle the endogenous component embodied by an IT productivity shock, and, on the other hand, to correctly size the pure effect of an IT productivity shock we need to disentangle from IT its expectational component.
+Using data released on April, 2018 by the Bureau of Economic Analysis (BEA) the real value added of the information sector on real GDP is slightly below $5$\% for the current quarter.
+Thus, since the share of this sector accounts for a negligible part in the whole economy, as an identification strategy, we assume that an ICT-investment technological change (hereafter ICT shock) is fully orthogonal to current TFP.
+In addition, in line with theoretical results firstly presented by \cite{greenwood1997long}, we expect that an ICT shock should incentivize sector-specific investment since ICT goods are now easier to produce and cheaper to buy.
+We transpose this theoretical argument in our empirical VAR by assuming that an ICT shock has a maximal impact effect on ICT investment.
 

### 2018-06-28 Latex/Draft_Summer2018/Summer2018.tex
Keep writing the empirical part

@@
 
-\section{Main Specification}
+\subsection{Main Specification}
 
@@
 Our first-step specification is the following 5-variable VAR
-\begin{equation}
+\begin{equation}\label{eq:mainSpecification}
 \begin{pmatrix}
@@
 \end{equation}
-where $TFP_t$ is the log-level of Fernald total factor productivity at time $t$, $ICT_{t}$ is the log-level of real information and communication technology investment at time $t$,\footnote{Notice that $ICTI_t$ is defined as the total expenditure at time $t$ in equipment and computer software meant to be used in production for more than an year.} $GDP_t$ is the log-level of real gross domestic product at time $t$, $C_t$ is the log-level of real consumption at time $t$, and $RP_t$ is the log-deviation of ratio between prices of ICT goods and services and the consumer price index (CPI).
-All the variables refer to the U.S.
+where $TFP_t$ is the log-level of Fernald total factor productivity at time $t$, $ICT_{t}$ is the log-level of real information and communication technology investment at time $t$,\footnote{Notice that $ICTI_t$ is defined as the total expenditure at time $t$ in equipment and computer software meant to be used in production for more than an year.} $GDP_t$ is the log-level of real gross domestic product at time $t$, $C_t$ is the log-level of real consumption at time $t$, and $RP_t$ is the log-deviation of ratio between prices of ICT goods and services and the consumer price index (CPI).\footnote{Except for $RP_t$ that is not cointegrated with the remaining variables, we opt for estimating the VAR in levels since it produces consistent estimates of the impulse responses and is robust to cointegration of unknown forms.
+In particular, as suggested by \cite{hamilton1994time} when there is uncertainty regarding the nature of common trends, estimating the system in levels is considered the conservative approach.
+In any case our results are very similar when estimating a vector error correction model (VECM).} All the variables have a quarterly frequency from 1989:Q1 to 2017:Q1 and refer to the U.S.
 economy.
@@
 Following the Bayesian Information Criterion (BIC), the lag operator functions is one which implies that we regress variables at time $t$ with their own lagged values at $t-1$.\footnote{The Hannan-Quinn Criterion (HQ) suggests to use two lags.
-Results remains consistent following this second criterion.} Finally, $i_t$ is a ($6\times 1$) vector of correlated innovations where $\Omega = i'_t i_t$.
+Results remains consistent following this second criterion.} Finally, $i_t$ is a ($6\times 1$) vector of correlated innovations where $\Sigma = i'_t i_t$.
 
-Using data released on April, 2018 by the Bureau of Economic Analysis (BEA) the real value added of the information sector on real GDP is slightly below $5$\% for the current quarter.
-Thus, since the share of this sector accounts for a negligible part in the whole economy, as an identification strategy, we assume that an ICT-investment technological change (hereafter ICT shock) is fully orthogonal to current TFP.
-In addition, in line with theoretical results firstly presented by \cite{greenwood1997long}, we expect that an ICT shock should incentivize sector-specific investment since ICT goods are now easier to produce and cheaper to buy.
-We transpose this theoretical argument in our empirical VAR by assuming that an ICT shock has a maximal impact effect on ICT investment.
+\subsection{Empirical Strategy}
+
+Our simples identification strategy implies that an ICT-investment technological shock (hereafter ICT shock) has no impact effect on TFP and maximal impact effect on ICT investment.
+We justify these assumptions with both empirical and theoretical argument.
+First of all, using data released on April, 2018 by the Bureau of Economic Analysis (BEA) the real value added of the information sector on real GDP is slightly below $5$\% for the underlying quarter.
+Thus, since the share of this sector accounts for a negligible part in the whole economy, we assume that an ICT shock is orthogonal to current TFP.
+In addition, in line with theoretical results firstly presented by \cite{greenwood1997long}, we expect that an ICT shock should enhance sector-specific investment since ICT goods are now easier to produce and cheaper to buy.
+As a result, we expect an ICT shock to have a maximal impact effect on ICT investment.
+
+Following a similar notation of \cite{barsky2011news}, we implement our identification strategy as follows.
+Let $y_t$ be the $(5 \times 1)$ vector of observables of length $T$.
+Once can form the reduced form moving average representation:
+$$
+y_t = \bar{B}(L)y_{t} + i_t \ \ \Rightarrow \ \ y_t = A(L)i_t
+$$
+where $A(L) = [I - \bar{B}(L)]^{-1}$ and $\bar{B}(L)$ has no constant terms. Assume now there exists a linear combination that maps innovations $i_t$ to structural shocks $s_t$:
+$$
+s_t = A_0 i_t
+$$
+This entails the structural moving average representation:
+$$
+y_t = C(L)i_t
+$$
+where $C(L) = A(L) A_0$ and $i_t = A_0^{-1} s_t$.
+The impact matrix $A_0$ must be such that $\Sigma = A_0 A_0'$.
+Notice that $A_0$ is not unique since for any $D$ such that $DD' = I$, $\tilde{A}_0 = A_0 D$ satisfies $\Sigma = \tilde{A}_0 \tilde{A}_0'$.
+
+The matrix of impact responses to a all shocks is:
+$$
+\Omega = \tilde{A}_0 D
+$$
+and 
+$$
+\Omega_{i,j} = e_i' \tilde{A}_0 D e_j
+$$
+where $e_k$ is a selection column vector of the same dimension of $\tilde{A}_0$ with $1$ in the $k$th element and zero elsewhere.
+In particular, notice that $e_j$ is selecting a specific column of $D$, which will be denoted by $\gamma_j$.
+As a result, $\tilde{A}_0\gamma_j$ denotes the vector of impact responses of all the variable to shock $j$.
+
+Let observe from System \ref{eq:mainSpecification} that $TFP_t$ is ordered first and $ICT_t$ second.
+In order to implement our identification strategy, we need to mathematically solve the following problem:
+\begin{equation}\label{eq:mainObjective}
+\max_{\gamma_j} \Omega_{2,j} = e_2' \tilde{A}_0 \gamma_j
+\end{equation}
+subject to
+\begin{equation}\label{eq:mainZeroTFP}
+\Omega_{1,j} = e_1' \tilde{A}_0 \gamma_j = 0, \ \ \text{and}
+\end{equation}
+\begin{equation}\label{eq:mainOrtho}
+\gamma_j' \gamma_j = 1
+\end{equation}
+where $j$ represents the arbitrary position of the ICT shock.
+Then, in order to ensure that this identification belongs to the space of possible orthogonalizations of $\Sigma$, the problem is denoted in terms of choosing $\gamma_j$ conditional on any orthogonalization, $\tilde{A}_0$.
+Objective function \ref{eq:mainObjective} imposes that an ICT shock as a maximal impact effect on ICT investment.
+Constraint \ref{eq:mainZeroTFP} orthogonalizes current TFP to ICT shocks and Constraint \ref{eq:mainOrtho} satisfies the condition that $\gamma_j$ is derived from an orthogonal matrix $D$.
+
+\subsection{Main Set of Results}
+
+Appendix \ref{section:mainSetResults} shows the estimated impulse responses of System \ref{eq:mainSpecification} to the identified ICT shock.
+The shaded gray areas are the $90$\% and $95$\% confidence bands from 2000 bias-corrected bootstrap procedure of \cite{kilian1998small}.
 
@@
 %%%%%%%%%%%%%%%%%%%%               MODEL                 %%%%%%%%%%%%%%%%%% 
-\section{Model}\label{section:experiments}
+\section{Experiments}\label{section:experiments}
 
@@
 
+\newpage
+
+ %%%%%%%%%%%%%%%%%%           Appendices            %%%%%%%%%%%%%%%%%%
+
+\appendix
+
+\section{Main Set of Results}\label{section:mainSetResults}
+
+\
+
+\
+
+\
+
+\
+
+\
+
+\
+
+\
+
+\
+
+	\begin{figure}[h!]
+		\begin{center}
+\includegraphics[scale=0.35]{MainFigures/fig_ICT_Shock_on_TFP_empirical_noH}
+		\caption{Empirical impulse response of TFP to an ICT shock.
+The red solid lines are the estimated impulse responses to our ICT shock.
+The shaded dark gray area and the shaded light gray area are the $90$\% and $95$\% confidence intervals, respectively, from 2000 bias-corrected bootstrap replications of the reduced-form VAR.
+The horizontal axes refer to forecast horizon and the units of the vertical axes are percentage deviations.}
+		\label{fig:TFP_main}
+	\end{center}
+\end{figure}
+
+	\begin{figure}[h!]
+		\begin{center}
+		\includegraphics[scale=0.35]{MainFigures/fig_ICT_Shock_on_Real_ICT_Investment_empirical_noH}
+		\caption{Empirical impulse response of real ICT investment to an ICT shock.
+The red solid lines are the estimated impulse responses to our ICT shock.
+The shaded dark gray area and the shaded light gray area are the $90$\% and $95$\% confidence intervals, respectively, from 2000 bias-corrected bootstrap replications of the reduced-form VAR.
+The horizontal axes refer to forecast horizon and the units of the vertical axes are percentage deviations.}
+		\label{fig:ICT_main}
+	\end{center} 
+	\end{figure}
+
+	\begin{figure}[h!]
+	\begin{center}
+		\includegraphics[scale=0.35]{MainFigures/fig_ICT_Shock_on_Real_GDP_empirical_noH}
+		\caption{Empirical impulse response of real Gross Domestic Product to an ICT shock.
+The red solid lines are the estimated impulse responses to our ICT shock.
+The shaded dark gray area and the shaded light gray area are the $90$\% and $95$\% confidence intervals, respectively, from 2000 bias-corrected bootstrap replications of the reduced-form VAR.
+The horizontal axes refer to forecast horizon and the units of the vertical axes are percentage deviations.}
+		\label{fig:GDP_main}
+	\end{center} 
+\end{figure}
+
+	\begin{figure}[h!]
+	\begin{center}
+		\includegraphics[scale=0.35]{MainFigures/fig_ICT_Shock_on_Real_Consumption_empirical_noH}
+		\caption{Empirical impulse response of real consumption to an ICT shock.
+The red solid lines are the estimated impulse responses to our ICT shock.
+The shaded dark gray area and the shaded light gray area are the $90$\% and $95$\% confidence intervals, respectively, from 2000 bias-corrected bootstrap replications of the reduced-form VAR.
+The horizontal axes refer to forecast horizon and the units of the vertical axes are percentage deviations.}
+		\label{fig:C_main}
+	\end{center} 
+\end{figure}
+
+	\begin{figure}[h!]
+	\begin{center}
+		\includegraphics[scale=0.35]{MainFigures/fig_ICT_Shock_on_Relative_Price_empirical_noH}
+		\caption{Empirical impulse response of relative price to an ICT shock.
+The red solid lines are the estimated impulse responses to our ICT shock.
+The shaded dark gray area and the shaded light gray area are the $90$\% and $95$\% confidence intervals, respectively, from 2000 bias-corrected bootstrap replications of the reduced-form VAR.
+The horizontal axes refer to forecast horizon and the units of the vertical axes are percentage deviations.}
+		\label{fig:RP_main}
+	\end{center} 
+\end{figure}
+
 \end{document}

### 2018-06-28 Code/just_IT_vecm/main_file_just_IT.m

@@ -29,7 +29,7 @@ range    = 'B1:Z287';
 warning off
 [data, varnames] = read_data2(filename, sheet, range);
 warning on
-shocknames = {'IT Shock'};
+shocknames = {'ICT Shock'};
 varnames
 
 % Find positions of shocks and of relative prices in a correct way
@@ -42,7 +42,7 @@ elseif sum(strcmp('SP deflated', varnames))==1 % i.e. we use SP deflated by GDPD
 elseif sum(strcmp('SP deflated per capita', varnames))==1 % i.e. we use SP deflated by GDPDEF for news
       pos_news = find(strcmp('SP deflated per capita', varnames));
 end
-pos_IT = find(strcmp('Real IT Investment', varnames));
+pos_IT = find(strcmp('Real ICT Investment', varnames));
 if find(strcmp('Relative Price', varnames)) > 0
       pos_rel_prices = find(strcmp('Relative Price', varnames));
 elseif find(strcmp('Relative price PCE', varnames))
@@ -108,7 +108,7 @@ end
 
 %Creating and Printing figures
 comment = [which_ID '_' char(varnames(pos_IT))];
-print_figs = 'no';
+print_figs = 'yes';
 
 [IRFs, ub1, lb1, ub2, lb2] = genIRFs(fake_impact,fake_impact_boot,...
       B,beta_tilde_star,H,sig1, sig2);
@@ -124,11 +124,8 @@ print_figs = 'no';
 %       lb2(:,:,pos_IT)     = - lb2(:,:,pos_IT);
 % end
 
-%Printing/Showing IRFs
-% plotIRFs(IRFs,ub,lb,40,which_shocks,shocknames,varnames,which_ID,print_figs)
-% plot_single_IRFs(IRFs,ub1,lb1,h,which_shocks,shocknames, varnames, which_ID, print_figs)
 use_current_time = 0; % don't save the time
-plot_single_IRFs_2CIs(IRFs,ub1,lb1,ub2,lb2,h,which_shock,shocknames, varnames, 'empirical', print_figs, use_current_time, base_path)
+plot_single_IRFs_2CIs(IRFs,ub1,lb1,ub2,lb2,h,which_shock,shocknames, varnames, 'empirical_noH', print_figs, use_current_time, base_path)
 
 %Forni&Gambetti Orthogonality Test
 do_FG_test = 'no';

### 2018-06-28 invoke_export_fig.m

@@ -17,10 +17,10 @@ if use_current_time==1
     ct1 = strrep(current_time,':','_'); % substitute : with _
     ct2 = strrep(ct1,' ','_'); % substitute spaces with _
     
-    final_name = ['fig_' figname '_' some_comment '_' ct2 '.pdf'];
+    final_name = ['fig_' figname '_' some_comment '_' ct2 '.png'];
     
 else
-    final_name = ['fig_' figname '_' some_comment '.pdf'];
+    final_name = ['fig_' figname '_' some_comment '.png'];
 end
 
 if nargin < 4

### 2018-06-29 Latex/Draft_Summer2018/Summer2018.tex
more writing on robustness checks

@@
 
-Our simples identification strategy implies that an ICT-investment technological shock (hereafter ICT shock) has no impact effect on TFP and maximal impact effect on ICT investment.
+Our simplest identification strategy implies that an ICT-investment technological shock (hereafter ICT shock) has no impact effect on TFP and maximal impact effect on ICT investment.
 We justify these assumptions with both empirical and theoretical argument.
@@
 The shaded gray areas are the $90$\% and $95$\% confidence bands from 2000 bias-corrected bootstrap procedure of \cite{kilian1998small}.
+In particular, Figure \ref{fig:TFP_main} shows impulse response of TFP to an ICT shock.
+TFP takes around $4$ quarters before displaying a positive and significant effect and reaches its peak of $1.2$\% after $24$ quarters.
+In Figure \ref{fig:ICT_main}, real ICT investment has a large and positive impact response of almost $2$\% that gets even larger after a quarter.
+Then, it slowly starts to decay remaining significant for more than $40$ quarters.
+In Figures \ref{fig:GDP_main} and \ref{fig:C_main}, we present responses of real GDP and real consumption, respectively.
+Real GDP has a significant impact response of $0.3$\%, starts to increase and finally reaches its peak of almost $0.5$\% approximately at the same time of TFP.
+Similarly, real consumption has an impact effect of $0.2$\% with a delayed peak of $0.5$\%.
+Finally, in Figure \ref{fig:RP_main}, relative prices has a significant and negative impact response of $0.4$\% and remain persistently below their own steady state value for almost $9$ years.
 

### 2018-06-29 Code/just_IT_vecm/loading_structural_shocks.m

@@ -1,0 +1,21 @@
+clear
+close all
+
+load main_just_IT_noHOURS_1LAG.mat
+sICT1 = s_shock_just_IT;
+
+load Workspace_Just_IT_SVAR_1LAG.mat
+sICT2 = s_shock_just_IT;
+
+%just for Microsoft (for now)
+addpath('C:\Users\th3\Documents\BG_2017\Code\just_IT_controlling_NEWS') 
+
+load Workspace_Just_IT_controllingNEWS_shortrunimpactsRP_maxNEWS_maxIT_1LAG.mat
+sICT3      = structural_shock_RyanID(:,2);
+sNEWS1     = structural_shock_RyanID(:,1);
+
+load Workspace_Just_IT_controllingNEWS_zeroimpactIT_maxNEWS_maxIT_1LAG.mat
+sICT4      = s_shock_just_IT(:,2);
+sNEWS2     = s_shock_just_IT(:,1);
+
+

### 2018-06-30 Latex/Draft_Summer2018/Summer2018.tex
reading through the introduction

@@
 \title{ICT and Future Productivity:\\Evidence and Theory of a GPT\thanks{Correspondence: Department of Economics, Boston College, 140 Commonwealth Avenue, Chestnut Hill, MA 02467.
-Email: brianti@bc.edu (Marco Brianti) and gati@bc.edu (Laura Gati).}}
-\author{Marco Brianti \\ {\small Boston College} \and Laura Gati \\ {\small Boston College}}
+Email: brianti@bc.edu (Marco Brianti) and gati@bc.edu (Laura G\'ati).}}
+\author{Marco Brianti \\ {\small Boston College} \and Laura G\'ati \\ {\small Boston College}}
 \date{\today}
@@
 \small{
-\abstract{Information and Communication technology (ICT) is able to explain accelerations in productivity in sectors that are ICT users.
+\abstract{Information and Communication Technology (ICT) is able to explain accelerations in productivity in sectors that are ICT users.
 We employ Structural VARs to investigate the effects of ICT supply shocks on Total Factor Productivity (TFP) and other macroeconomic variables.
-In response to this sector-specific supply shock relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a significant delayed and persistent increase.
-In line with theories of ICT as a general-purpose technology, we analyze a two-sector general equilibrium model in order to rationalize previous results and estimate key parameters via impulse-response matching.
+In response to this sector-specific supply shock, relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a significant delayed and persistent increase.
+Taking up the view of theories of ICT as a general-purpose technology, we analyze a two-sector general equilibrium model in order to rationalize previous results and estimate spillovers from the stock of ICT via impulse-response matching.
 We conclude that ICT accumulation is able to enhance productivity through a positive spillover effect which takes into account the overall level of diffusion of ICT capital in the economy.}
@@
 
-Although there is large consensus on the importance of productivity as a driver of economic performances, less agreement is on the underlying sources that enhance its growth.
-For several years most of the business-cycle literature purposely decided to avoid such a question by proxying movements in productivity as random shocks.\footnote{\cite{kydland1982time} and \cite{long1983real} are among the first papers which consider productivity shocks on general equilibrium models.} However, the robust empirical evidence of the slowdown in productivity right before the great recession is summoning the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
+Although there is large consensus on the importance of productivity as a driver of economic performance, there is less agreement on the underlying sources of productivity growth.
+For several years most of the business-cycle literature purposely decided to avoid such a question by proxying movements in productivity as exogenous shocks.\footnote{\cite{kydland1982time} and \cite{long1983real} are among the first papers which consider productivity shocks on general equilibrium models.} However, the robust empirical evidence of the slowdown in productivity right before the Great Recession is urging the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
 
-Along with \cite{comin2006medium}, some theoretical contributions rationalize endogenous productivity dynamics by adapting features of endogenous growth models into DSGE models.
-Following \cite{romer1990endogenous}, most of those papers augment final-good production functions with an expanding composite of intermediate goods produced by the R\&D sector in order to allow for an endogenous rate of adoption of new technologies.\footnote{\cite{bianchi2014growth}, \cite{anzoategui2016endogenous}, and \cite{moran2017innovation} use similar techniques to endogenize growth.
+Along with \cite{comin2006medium}, some theoretical contributions rationalize endogenous productivity dynamics by incorporating features of endogenous growth models into standard models of business cycles.
+Following \cite{romer1990endogenous}, most of these papers augment final-good production functions with an expanding composite of intermediate goods produced by the Research \& Development (R\&D) sector in order to allow for an endogenous rate of adoption of new technologies.\footnote{\cite{bianchi2014growth}, \cite{anzoategui2016endogenous}, and \cite{moran2017innovation} use similar techniques to endogenize growth.
 In particular, \cite{bianchi2014growth} augment a DSGE  model using a quality ladders model in the vein of \cite{grossman1991quality}.
-Moreover, \cite{anzoategui2016endogenous} and \cite{moran2017innovation}, similarly to \cite{comin2006medium}, use a model of expanding variety in the vein of \cite{romer1990endogenous}.} Consistent with those previous models, other papers attempt to provide empirical evidence of a slowdown in the productivity of the R\&D sector.
-Specifically, they show that although research effort is keeping rising, the rate of new ideas and discoveries is slowing down.\footnote{\cite{jones2009burden} and \cite{bloom2017ideas} are two important contributions that highlight those facts.}
+Moreover, \cite{anzoategui2016endogenous} and \cite{moran2017innovation}, similarly to \cite{comin2006medium}, use a model of expanding variety in the vein of \cite{romer1990endogenous}.} Guided by the prediction of such theoretical work that R\&D developments matter for growth, other papers attempt to provide empirical evidence of a slowdown in the productivity of the R\&D sector.
+Specifically, they show that although research effort keeps rising, the rate of new ideas and discoveries is slowing down.\footnote{\cite{jones2009burden} and \cite{bloom2017ideas} are two important contributions that highlight these facts.}
 
-Motivated by this wave of research, this paper follows a different path and argue that Information and Communication Technology (hereafter ICT) plays an important role in driving medium-term productivity in sectors that are ICT users.
+Motivated by this wave of research, this paper follows a different path and argues that Information and Communication Technology (hereafter ICT) plays an important role in driving medium-term productivity in sectors that are ICT users.
 Our contribution is twofold.
-First, we provide a robust empirical evidence to show that current rises in ICT investment explains significant and persistent increases in future Total Factor Productivity (hereafter TFP).
+First, we provide robust empirical evidence to show that current rises in ICT investment explains significant and persistent increases in future Total Factor Productivity (hereafter TFP).
 Second, we analyze a standard theoretical framework in order to both motivate and rationalize our empirical results.
 
-Regarding the empirical section, the idea is to identify technological shocks which are only specific to the ICT sector in a Structural VAR context.\footnote{An interesting paper which is somehow related to our empirical part is \cite{jafari2012impact}.
-The authors identify ICT shocks as a potential driver of the Iranian business cycle using a completely different identification strategy and obtaining qualitatively different results.} In order to have a reliable identification procedure our multivariate system needs to embody three key variables: TFP, ICT investment (hereafter ICTI), and relative prices (hereafter RP).
-Importantly, ICTI is defined as the total expenditure in equipment and computer software meant to be used in production for more than an year.
-Thus, an increase in ICTI has to be though as an ICT capital deepening.
-Moreover RP is the ratio between prices in the ICT sector over prices in the overall economy.
-To verify that we are correctly identifying an ICT technology shock, we firstly expect it to be orthogonal to the current productivity of all the other sectors.
-Since the share of the ICT sector accounts for a negligible part in the whole economy we expect it should have an approximately zero effect on TFP on impact.
-Moreover, as pointed out by \cite{greenwood1997long} and \cite{fisher2006dynamic}, embodying RP and ICTI is important because we expect that a sectoral technology shock should decrease its relative prices and enhance expenditure in the underlying sector.\footnote{However, as suggested by both \cite{greenwood2000role} and \cite{basu2010sector}, we are aware that conditioning our identifying restrictions only on the direction of RP does not properly measure for technological changes between sectors.
+In the empirical section, we identify technological shocks specific to the ICT sector in a Structural VAR context.\footnote{An interesting paper related to our empirical work is \cite{jafari2012impact}.
+The authors identify ICT shocks as a potential driver of the Iranian business cycle using a completely different identification strategy and obtaining qualitatively different results.} In order to have a reliable identification procedure our multivariate system needs to include three key variables: TFP, ICT investment (hereafter ICTI), and relative prices (hereafter RP).
+ICTI is defined as the total expenditure in equipment and computer software meant to be used in production for more than an year.
+Thus, an increase in ICTI is ICT capital deepening.
+RP is the ratio between the price of the ICT good and the price level in the overall economy.
+We use two identifying restrictions in order to back out an ICT technology shock.
+First, we expect it to be orthogonal to the current productivity of all the other sectors.
+Since the share of the ICT sector accounts for a negligible part in the whole economy, ICT shocks should have an approximately zero effect on TFP on impact.
+Thus, our first restriction will be a zero-impact restriction on TFP after an ICT shock.
+Moreover, following \cite{greenwood1997long} and \cite{fisher2006dynamic}, we rely on RP and ICTI because we expect that a sectoral technology shock should decrease its relative prices and enhance expenditure in the underlying sector.
+For theoretical reasons discussed in more detail below, we do not impose any restriction on RP; instead, we let the ICT shock maximize the impact response of ICTI.\footnote{However, as suggested by both \cite{greenwood2000role} and \cite{basu2010sector}, we are aware that conditioning our identifying restrictions only on the direction of RP does not properly measure for technological changes between sectors.
 This is the main reason why we never impose the direction of RP as an direct identifying condition.} In response to this shock, ICTI rises on impact and remains significant for several quarters.
-RP persistently and significantly declines for more than two years and TFP, which does not react on impact, rises after few quarters and remains significant and stable for at least 5 years.
+RP persistently and significantly declines for more than two years, suggesting that we are indeed identifying the correct sectoral shock.
+Our main result is that TFP, restricted not to respond on impact, rises after few quarters and remains significant and stable for at least 5 years, despite the tiny size of the ICT sector relative to the economy.
 
-Although our results are robust over different specifications, there is an important critique that our empirical strategy had to carefully take into account, which is the reverse causality due to news on future TFP.
-A well-taken concern motivated my the news-shock literature is that the positive reaction of ICTI on impact may be triggered to signals related future increases in TFP and not to contemporaneous ICT technological improvements.
-In other words, our identification strategy may confound a news shock which contemporaneously enhances investment in ICT capital goods.
-In order to take into account this potential issue, we provide a series of robustness checks where sequentially we firstly identify a news shock in the spirit of \cite{barsky2011news} and subsequently we identify our sectoral ICT shock using the previous identification strategy.
-Encouragingly, controlling for signals regarding future movements in TFP does not affect any conclusion drown so far.
-In particular, we can now state even more strongly the causality relation from movements in current ICT technological changes to future TFP.
+Although our results are robust over different specifications, an important critique to our empirical strategy is reverse causality coming from news on future TFP.
+As suggested by the news-shock literature, the positive reaction of ICTI on impact may be triggered by signals related future increases in TFP and not to contemporaneous ICT technological improvements.
+In other words, our identification strategy may confound our shock of interest with a news shock which contemporaneously enhances investment in ICT capital goods.
+We address this issue by providing a series of alternative identification strategies which we show deliver the same time series of ICT innovations as our initial specification.
+The heart of these robustness checks is sequential identification of news and ICT shocks: we firstly identify a news shock in the spirit of \cite{barsky2011news}, and subsequently we identify our sectoral ICT shock using the previous identification strategy.
+Encouragingly, controlling for signals regarding future movements in TFP does not affect our results.
+We view this as strengthening our statement relating movements in current ICT technology to future TFP.
 
-Motivated by papers in line with \cite{oliner2000resurgence} and \cite{stiroh2002information}, in order to formally explain which mechanism links current ICT to future TFP, we analyze a 2-sector DSGE model which allows ICT to be the general purpose technology (hereafter GPT) of the whole economy.
+In order to formally explain which mechanism links current ICT to future TFP, we analyze a two-sector DSGE model which allows ICT to be the general purpose technology (hereafter GPT) of the whole economy.
+There are two main justifications for interpreting ICT as a GPT.
+On the one hand, there is a vast literature starting with  that makes a case for the general-purpose nature of ICT capital.\footnote{See for example \cite{oliner2000resurgence} and \cite{stiroh2002information} amongst others.} On the other hand, the small size of ICT sector share both in overall investment and overall output makes our results of a strong and persistent TFP increase hard to interpret in absence of an additional force such as general-purpose externality.
+
 Both sectoral production functions are fed with three inputs: (i) labor, supplied by households, (ii) hard capital, produced by the final sector, and (iii) ICT capital, produced by the ICT sector.

### 2018-06-30 Latex/Draft_Summer2018/Summer2018.tex
more reading of intro

@@
 There are two main justifications for interpreting ICT as a GPT.
-On the one hand, there is a vast literature starting with  that makes a case for the general-purpose nature of ICT capital.\footnote{See for example \cite{oliner2000resurgence} and \cite{stiroh2002information} amongst others.} On the other hand, the small size of ICT sector share both in overall investment and overall output makes our results of a strong and persistent TFP increase hard to interpret in absence of an additional force such as general-purpose externality.
+On the one hand, there is a vast literature that makes a case for the general-purpose nature of ICT capital.\footnote{See for example \cite{oliner2000resurgence} and \cite{stiroh2002information} amongst others.} On the other hand, the small size of ICT sector share both in overall investment and overall output makes our results of a strong and persistent TFP increase after an ICT shock hard to interpret in absence of an additional force such as an externality coming from the general-purpose property of ICT capital.
 
-Both sectoral production functions are fed with three inputs: (i) labor, supplied by households, (ii) hard capital, produced by the final sector, and (iii) ICT capital, produced by the ICT sector.
-As well-explained by both \cite{basu2003case} and \cite{basu2007information}, a GPT should be able to enhance accelerations in productivity in sectors that are users of the underlying technology.
+In our model, both sectoral production functions are fed with three inputs: (i) labor, supplied by households, (ii) hard capital, produced by the final sector, and (iii) ICT capital, produced by the ICT sector.
+As explained by both \cite{basu2003case} and \cite{basu2007information}, a GPT should be able to enhance accelerations in productivity in sectors that are users of the underlying technology.
 We then interpret ICT as the GPT of the last 30 years of the U.S.
-economy assuming that exogenous technological changes in the ICT sector are able to affect economy-wide productivity.
-In particular, when an ICT technology shock arrives, both sectors accumulate ICT capital since it is easier to produce and cheaper to buy.
+economy assuming that exogenous technological changes in the ICT sector are able to affect economy-wide productivity above the direct effect coming from the technology increase itself.\footnote{A clarification is in place here.
+In a two-sector model, the overall residual productivity is a convolution of the two exogenous productivities.
+Thus sectoral productivity changes trivially show up in overall productivity.
+Our assumption of ICT capital being a GPT means that overall productivity responds more to an ICT-sector-specific technology shock than warranted by this shock directly.
+We address this question in detail in the main text in Section \ref{section:empirics}.} In particular, when an ICT technology shock arrives, both sectors accumulate ICT capital since it is easier to produce and cheaper to buy.
 This ICT capital deepening consequently enhances the productivity of both sectors by means of a spillover.
-Since the purpose of ICT capital is to improve information sharing, the quality and speed of communication must mainly depend on the diffusion of these technologies among agents.
-As a simple example, owning a mobile phone enables to contact someone instantaneously if the person you want to reach is endowed with the same technology.
+
+Since the purpose of ICT capital is to improve information sharing, the quality and speed of communication mainly depends on the diffusion of these technologies among agents.
+As a simple example, owning a mobile phone enables one to contact another person instantaneously only if the other person is also endowed with the same technology.
 As a result, the effectiveness of ICT capital is intrinsically related to its own diffusion.
 We rationalize this line of thought augmenting the production function of each sector with a spillover effect driven by the diffusion of ICT capital.
-Consistently with this literature and our empirical results, the accumulation of ICT capital is a slow process and the benefits of an ICT technology shock show up in the production functions of ICT-users with lags.\footnote{Notice that differently to \cite{basu2003case} and \cite{basu2007information}, we interpret the general-purpose nature of ICT in the spirit of an endogenous growth model.}
+Consistently with the GPT literature above and our empirical results, the accumulation of ICT capital is a slow process and the benefits of an ICT technology shock show up in the production functions of ICT-users with lags.\footnote{Notice that differently to \cite{basu2003case} and \cite{basu2007information}, we interpret the general-purpose nature of ICT in the spirit of an endogenous growth model.}
 
@@
 We present empirical results and main robustness checks in Section \ref{section:empirics}.
-We then present and analyze the 2-sector DSGE model in Section \ref{section:theory}.
+We then present and analyze the two-sector DSGE model in Section \ref{section:theory}.
 We estimate via impulse-response matching key parameters of the model and run a series of related experiment in Section \ref{section:experiments}.

### 2018-06-30 Latex/Draft_Summer2018/Summer2018.tex
Robustness checks + a little bit of code

@@
 
-\subsection{Main Specification}
+\subsection{Main Specification}\label{section:mainSpec}
 
@@
 It turns out that the set of results presented here are consistent with different robustness checks.
+
+\subsubsection{Data}
+
 Our first-step specification is the following 5-variable VAR 
@@
 TFP_t \\ 
-ICT_t \\
+ICTI_t \\
 GDP_t \\
@@
 TFP_{t-1} \\ 
-ICT_{t-1} \\
+ICTI_{t-1} \\
 GDP_{t-1} \\
@@
 \end{equation}
-where $TFP_t$ is the log-level of Fernald total factor productivity at time $t$, $ICT_{t}$ is the log-level of real information and communication technology investment at time $t$,\footnote{Notice that $ICTI_t$ is defined as the total expenditure at time $t$ in equipment and computer software meant to be used in production for more than an year.} $GDP_t$ is the log-level of real gross domestic product at time $t$, $C_t$ is the log-level of real consumption at time $t$, and $RP_t$ is the log-deviation of ratio between prices of ICT goods and services and the consumer price index (CPI).\footnote{Except for $RP_t$ that is not cointegrated with the remaining variables, we opt for estimating the VAR in levels since it produces consistent estimates of the impulse responses and is robust to cointegration of unknown forms.
+where $TFP_t$ is the log-level of Fernald total factor productivity at time $t$, $ICTI_{t}$ is the log-level of real information and communication technology investment at time $t$,\footnote{Notice that $ICTI_t$ is defined as the total expenditure at time $t$ in equipment and computer software meant to be used in production for more than an year.} $GDP_t$ is the log-level of real gross domestic product at time $t$, $C_t$ is the log-level of real consumption at time $t$, and $RP_t$ is the log-deviation of ratio between prices of ICT goods and services and the consumer price index (CPI).\footnote{Except for $RP_t$ that is not cointegrated with the remaining variables, we opt for estimating the VAR in levels since it produces consistent estimates of the impulse responses and is robust to cointegration of unknown forms.
 In particular, as suggested by \cite{hamilton1994time} when there is uncertainty regarding the nature of common trends, estimating the system in levels is considered the conservative approach.
@@
 Following the Bayesian Information Criterion (BIC), the lag operator functions is one which implies that we regress variables at time $t$ with their own lagged values at $t-1$.\footnote{The Hannan-Quinn Criterion (HQ) suggests to use two lags.
-Results remains consistent following this second criterion.} Finally, $i_t$ is a ($6\times 1$) vector of correlated innovations where $\Sigma = i'_t i_t$.
+Results remains consistent following this second criterion.} Finally, $i_t$ is a ($5 \times 1$) vector of correlated innovations where $\Sigma = i'_t i_t$.
 
-\subsection{Empirical Strategy}
+\subsubsection{Empirical Strategy}
 
-Our simplest identification strategy implies that an ICT-investment technological shock (hereafter ICT shock) has no impact effect on TFP and maximal impact effect on ICT investment.
+Our simplest identification strategy implies that an ICT-investment technological shock (hereafter ICT shock) has no impact effect on TFP and maximal impact effect on ICTI.
 We justify these assumptions with both empirical and theoretical argument.
@@
 In addition, in line with theoretical results firstly presented by \cite{greenwood1997long}, we expect that an ICT shock should enhance sector-specific investment since ICT goods are now easier to produce and cheaper to buy.
-As a result, we expect an ICT shock to have a maximal impact effect on ICT investment.
+As a result, we expect an ICT shock to have a maximal impact effect on ICTI.
 
 Following a similar notation of \cite{barsky2011news}, we implement our identification strategy as follows.
-Let $y_t$ be the $(5 \times 1)$ vector of observables of length $T$.
+Let $y_t$ be the $(5 \times 1)$ vector of observables of length $T$ presented above.
 Once can form the reduced form moving average representation:
@@
 
-The matrix of impact responses to a all shocks is:
+The matrix of impact responses to all shocks is:
 $$
@@
 $$
-and 
+and is specifically formed by the following elements,
 $$
@@
 
-Let observe from System \ref{eq:mainSpecification} that $TFP_t$ is ordered first and $ICT_t$ second.
+Let observe from System \ref{eq:mainSpecification} that $TFP_t$ is ordered first and $ICTI_t$ second.
 In order to implement our identification strategy, we need to mathematically solve the following problem:
@@
 
-\subsection{Main Set of Results}
+\subsubsection{Main Set of Results}
 
@@
 In Figures \ref{fig:GDP_main} and \ref{fig:C_main}, we present responses of real GDP and real consumption, respectively.
-Real GDP has a significant impact response of $0.3$\%, starts to increase and finally reaches its peak of almost $0.5$\% approximately at the same time of TFP.
+Real GDP has a significant impact response of $0.3$\% and reaches its peak of almost $0.5$\% approximately at the same time of TFP.
 Similarly, real consumption has an impact effect of $0.2$\% with a delayed peak of $0.5$\%.
 Finally, in Figure \ref{fig:RP_main}, relative prices has a significant and negative impact response of $0.4$\% and remain persistently below their own steady state value for almost $9$ years.
+
+In addition, Table \ref{table:vardec} in Appendix \ref{section:vardec} presents forecast error variance of each variable on impact, and after one-, two-, four-, six-, and ten-year horizon.
+In line with impulse responses, ICT shocks, which are orthogonal to current productivity, explain a third of TFP fluctuations over ten-year horizon.
+On the other hand, ICT shocks drive almost the whole variation in ICT investment on impact but this effect tends to decay over time getting below the $50$\% after 10 years.
+Interestingly, both output and consumption has a remarkable reaction on impact: $26$\% and $19$\%, respectively.
+Moreover, this effect tends to increase reaching $40$\% in both cases over the maximal horizon.
+Finally, ICT shocks do not have a remarkable effect on relative prices.
+The fraction of fluctuations explained on impact is only $6$\% with a peak of $14$\% between four and six years.
+
+\subsection{Controlling for News Shocks}
+
+In this section, we show a set of robustness checks aimed to show that our previous results are not driven by future signals regarding exogenous productivity.
+Although our results are robust when we purposely change the main specification presented in Subsection \ref{section:mainSpec}, an important critique to our empirical strategy is reverse causality coming from news on future TFP.
+As suggested by the news-shock literature, the positive reaction of ICTI on impact may be triggered by signals related future increases in productivity and not to a contemporaneous ICT shock.
+In other words, our identification strategy may confound our shock of interest with a news shock which contemporaneously enhances investment in ICT capital goods.
+We address this issue by providing two main alternative identification strategies which we show deliver the same time series of ICT shocks as our initial specification.
+Firstly, we test if our result is robust once removed all the forward looking variables which fluctuations may be unrelated to sector-specific technological changes: consumption and output.
+Technically speaking, consumption and output may granger-cause future TFP for reasons which are orthogonal to ICT shocks.
+For example, the forward-looking nature of consumption may provide to the VAR unnecessary information regarding future changes in TFP not related to an ICT shock which our identification strategy is not able to filter it out.
+Secondly, we apply a sequential identification where we firstly identify a news shock in the spirit of \cite{barsky2011news}, and subsequently we identify our sectoral ICT shock using the previous identification strategy.
+This second strategy has the specific purpose of filtering out all the current movements in forward-looking variables related to future fluctuations of TFP which are not related to current ICT shocks.
+
+Encouragingly, controlling for signals regarding future movements in productivity does not affect our identified ICT shocks suggesting a causal relation which goes from current ICT investment to future TFP.
+
+\subsubsection{Removing Forward-Looking Variables}
+
+Three-variables one lag, just show the structural shocks and their correlation. Responses very similar.
+
+\subsubsection{Sequential Identification Strategy}
 
@@
 
-\
-
-\
-
-\
-
-\
-
-\
-
-\
-
-\
-
-\
-
 	\begin{figure}[h!]
@@
 \end{figure}
+
+\newpage
 
@@
 
+\newpage
+
 	\begin{figure}[h!]
@@
 
+\newpage
+
+ \section{Variance Decomposition}\label{section:vardec}
+
+ 	\begin{table}[h!]
+ 		\begin{center}
+ \begin{tabular}{lcccccccccc}
+\hline
+ 	& $h = 1$ & $h = 4$ & $h = 8$ & $h = 16$ & $h = 24$ & $h = 40$ \\
+ 	\hline
+TFP &  0       &  0.0023  &  0.0194 &   0.1088 &   0.2273  &  0.3382 \\
+ICT Investment &  0.9997  &  0.9038  &  0.7964 &   0.6320 &   0.5310  &  0.4371 \\
+Real GDP &  0.2620  &  0.3061  &  0.3486 &   0.3936 &   0.4046  &  0.3881 \\
+Real Consumption &  0.1952  &  0.2638  &  0.3219 &   0.3931 &   0.4188  &  0.4064 \\
+Relative Prices &  0.0618  &  0.0967  &  0.1276 &   0.1511 &   0.1516  &  0.1467 \\	
+\hline
+ 	\end{tabular}
+  		\caption{The letter $h$ denotes the forecast horizon. The numbers refer to the fraction of the forecast error variance of each variable at various forecast horizons to the identified ICT shock}
+  \label{table:vardec}
+  \end{center}
+ \end{table}
+
 \end{document}

### 2018-06-30 Code/just_IT_vecm/loading_structural_shocks.m

@@ -18,4 +18,15 @@ load Workspace_Just_IT_controllingNEWS_zeroimpactIT_maxNEWS_maxIT_1LAG.mat
 sICT4      = s_shock_just_IT(:,2);
 sNEWS2     = s_shock_just_IT(:,1);
 
+load Workspace_Just_IT_SVAR_2Variables_1LAG.mat
+sICT5      = s_shock_just_IT;
+
+load Workspace_Just_IT_SVAR_3Variables_1LAG.mat
+sICT6      = s_shock_just_IT;
+
+corr(sICT1,sICT6)
+plot(sICT1)
+hold on
+plot(sICT6)
+
 

### 2018-06-30 Code/just_IT_vecm/main_file_just_IT.m

@@ -69,6 +69,7 @@ if AIC >= 4
 else
       nlags = AIC;
 end
+nlags = 1
 
 %Run VAR imposing Cholesky
 [A,B,res,sigma] = sr_var(data, nlags);
@@ -89,7 +90,7 @@ blocksize = 30; % size of block for drawing in blocks
 
 
 % Get "bootstrapped A" nsimul times
-for i_simul=1:nsimul      
+for i_simul=1:nsimul
       [A_boot, ~,~,~] = sr_var(data_boot2(:,:,i_simul), nlags);
       % Get bootstrapped confidence intervals nsimul times
       disp(['Iteration ' num2str(i_simul) ' out of ' num2str(nsimul)])
@@ -108,7 +109,7 @@ end
 
 %Creating and Printing figures
 comment = [which_ID '_' char(varnames(pos_IT))];
-print_figs = 'yes';
+print_figs = 'no';
 
 [IRFs, ub1, lb1, ub2, lb2] = genIRFs(fake_impact,fake_impact_boot,...
       B,beta_tilde_star,H,sig1, sig2);
@@ -150,6 +151,18 @@ impact_vardec = A*D_null; % where A is the chol.
 
 vardec = gen_vardecomp(IRF_vardec,h,h);
 shareIT_on_TFP = vardec(1,end); % "end" b/c we put gam_opt as last.
+h1     = 1;
+h4     = 4;
+h8     = 8;
+h16    = 16;
+h24    = 24;
+h40    = 40;
+h_vec  = [h1 h4 h8 h16 h24 h40];
+for ih = 1:length(h_vec)
+      vardec = gen_vardecomp(IRF_vardec,h_vec(ih),h);
+      table_vardec(:,ih) = vardec(:,end);
+end
+
 
 %Get Structural Shocks
 [s_shock_just_IT, ~] = ...

### 2018-07-01 Latex/Draft_Summer2018/Summer2018.tex
did some more rewriting of the introduction

@@
 \small{
-\abstract{Information and Communication Technology (ICT) is able to explain accelerations in productivity in sectors that are ICT users.
-We employ Structural VARs to investigate the effects of ICT supply shocks on Total Factor Productivity (TFP) and other macroeconomic variables.
+\abstract{We employ Structural VARs to investigate the effects of ICT supply shocks on Total Factor Productivity (TFP) and other macroeconomic variables.
 In response to this sector-specific supply shock, relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a significant delayed and persistent increase.
@@
 Although there is large consensus on the importance of productivity as a driver of economic performance, there is less agreement on the underlying sources of productivity growth.
-For several years most of the business-cycle literature purposely decided to avoid such a question by proxying movements in productivity as exogenous shocks.\footnote{\cite{kydland1982time} and \cite{long1983real} are among the first papers which consider productivity shocks on general equilibrium models.} However, the robust empirical evidence of the slowdown in productivity right before the Great Recession is urging the literature to take a step back and devote more attention on the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
+For several years most of the business-cycle literature purposely decided to avoid such a question by proxying movements in productivity as exogenous shocks.\footnote{\cite{kydland1982time} and \cite{long1983real} are among the first papers which consider productivity shocks on general equilibrium models.} However, the robust empirical evidence of the slowdown in productivity right before the Great Recession has led recent literature to take a step back and devote more attention to the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
 
-Along with \cite{comin2006medium}, some theoretical contributions rationalize endogenous productivity dynamics by incorporating features of endogenous growth models into standard models of business cycles.
-Following \cite{romer1990endogenous}, most of these papers augment final-good production functions with an expanding composite of intermediate goods produced by the Research \& Development (R\&D) sector in order to allow for an endogenous rate of adoption of new technologies.\footnote{\cite{bianchi2014growth}, \cite{anzoategui2016endogenous}, and \cite{moran2017innovation} use similar techniques to endogenize growth.
+Along with \cite{comin2006medium}, theoretical contributions rationalize endogenous productivity dynamics by incorporating features of endogenous growth models in standard models of business cycles.
+Following \cite{romer1990endogenous}, most of these papers augment final-good production functions with an expanding composite of intermediate goods invented by the Research \& Development (R\&D) sector in order to allow for an endogenous rate of adoption of new technologies.\footnote{\cite{bianchi2014growth}, \cite{anzoategui2016endogenous}, and \cite{moran2017innovation} use similar techniques to endogenize growth.
 In particular, \cite{bianchi2014growth} augment a DSGE  model using a quality ladders model in the vein of \cite{grossman1991quality}.
@@
 Our contribution is twofold.
-First, we provide robust empirical evidence to show that current rises in ICT investment explains significant and persistent increases in future Total Factor Productivity (hereafter TFP).
-Second, we analyze a standard theoretical framework in order to both motivate and rationalize our empirical results.
+First, we provide robust empirical evidence to show that current rises in ICT investment explain significant and persistent increases in future Total Factor Productivity (hereafter TFP).
+Second, we analyze a standard theoretical framework in order to both rationalize and draw conclusions from our empirical results.
 
 In the empirical section, we identify technological shocks specific to the ICT sector in a Structural VAR context.\footnote{An interesting paper related to our empirical work is \cite{jafari2012impact}.
-The authors identify ICT shocks as a potential driver of the Iranian business cycle using a completely different identification strategy and obtaining qualitatively different results.} In order to have a reliable identification procedure our multivariate system needs to include three key variables: TFP, ICT investment (hereafter ICTI), and relative prices (hereafter RP).
+The authors identify ICT shocks as a potential driver of the Iranian business cycle using a completely different identification strategy and obtaining qualitatively different results.} Our multivariate system includes three key variables: TFP, ICT investment (hereafter ICTI), and relative prices (hereafter RP).
 ICTI is defined as the total expenditure in equipment and computer software meant to be used in production for more than an year.
@@
 RP is the ratio between the price of the ICT good and the price level in the overall economy.
+
 We use two identifying restrictions in order to back out an ICT technology shock.
@@
 
-In order to formally explain which mechanism links current ICT to future TFP, we analyze a two-sector DSGE model which allows ICT to be the general purpose technology (hereafter GPT) of the whole economy.
+In order to understand the economics behind our empirical results, we then analyze a two-sector DSGE model which allows ICT to be the general purpose technology (hereafter GPT) of the whole economy.
 There are two main justifications for interpreting ICT as a GPT.
-On the one hand, there is a vast literature that makes a case for the general-purpose nature of ICT capital.\footnote{See for example \cite{oliner2000resurgence} and \cite{stiroh2002information} amongst others.} On the other hand, the small size of ICT sector share both in overall investment and overall output makes our results of a strong and persistent TFP increase after an ICT shock hard to interpret in absence of an additional force such as an externality coming from the general-purpose property of ICT capital.
+On the one hand, there is a vast literature that makes a case for the general-purpose nature of ICT capital.\footnote{See for example \cite{oliner2000resurgence} and \cite{stiroh2002information} amongst others.} On the other hand, the small size of the share of the ICT sector both in overall investment and overall output makes our results of a strong and persistent TFP increase after an ICT shock hard to interpret in absence of an additional force such as an externality coming from the general-purpose property of ICT capital.
 
@@
 We address this question in detail in the main text in Section \ref{section:empirics}.} In particular, when an ICT technology shock arrives, both sectors accumulate ICT capital since it is easier to produce and cheaper to buy.
-This ICT capital deepening consequently enhances the productivity of both sectors by means of a spillover.
+This ICT capital deepening consequently enhances the productivity of both sectors by means of a spillover coming from the accumulated ICT capital stock.
 
@@
 As a result, the effectiveness of ICT capital is intrinsically related to its own diffusion.
-We rationalize this line of thought augmenting the production function of each sector with a spillover effect driven by the diffusion of ICT capital.
-Consistently with the GPT literature above and our empirical results, the accumulation of ICT capital is a slow process and the benefits of an ICT technology shock show up in the production functions of ICT-users with lags.\footnote{Notice that differently to \cite{basu2003case} and \cite{basu2007information}, we interpret the general-purpose nature of ICT in the spirit of an endogenous growth model.}
+This line of thought is what leads us to augment the production function of each sector with a spillover effect capturing the diffusion of ICT capital.
+Having a spillover arise from a state variable is also consistent with both the GPT literature above and with our empirical results, since it also leads to model dynamics in which the accumulation of ICT capital is a slow process and the benefits of an ICT technology shock show up in the production functions of ICT-users with lags.\footnote{Notice that differently to \cite{basu2003case} and \cite{basu2007information}, we interpret the general-purpose nature of ICT in the spirit of an endogenous growth model.}
 
@@
 The key parameters within this set are (i) the elasticity of productivity to ICT capital diffusion, namely the parameter which governs the spillover effect, and (ii) the standard deviation and (iii) persistence of ICT technology shocks.
-Results consistently point out a positive spillover effect of ICT capital deepening on TFP suggesting that the assumptions made in the theoretical model are supported by our empirical results.
-We confirm that ICT is a general-purpose technology which enhance productivity of ICT capital users through a spillover effect related to its own diffusion.
+Results consistently point out a positive spillover effect of ICT capital deepening on TFP, confirming that within this class of theoretical models, data supports the existence of spillovers from ICT capital.
+Thus, our theoretical model suggests to interpret the responses obtained in the empirical section in light of ICT as a general-purpose technology which enhances productivity of ICT capital users through a spillover effect related to its own diffusion.
 
@@
 We then present and analyze the two-sector DSGE model in Section \ref{section:theory}.
-We estimate via impulse-response matching key parameters of the model and run a series of related experiment in Section \ref{section:experiments}.
+We estimate via impulse-response matching key parameters of the model and run a series of related experiments in Section \ref{section:experiments}.
 Concluding remarks, caveats and prospective future research are discussed in Section \ref{section:conclusions}.

### 2018-07-01 Latex/Draft_Summer2018/Summer2018.tex
some work on the empirical part

@@
 
-In this section we present our main empirical set of results.
-Our attempt is to properly identify technological shocks which are only specific to the ICT sector in a Structural VAR context and analyze their impact on key macroeconomic variables.
+In this section we present our main empirical results.
+Our attempt is to properly identify technological shocks which are specific to the ICT sector in a Structural VAR context and analyze their impact on key macroeconomic variables.
 
@@
 
-In this section we present our main specification where we impose minimal discipline on the identification strategy.
-It turns out that the set of results presented here are consistent with different robustness checks.
+We start by illustrating our main specification where we impose minimal discipline on the identification strategy.
+In subsequent sections, we try vastly different alternative empirical strategies.
+It turns out that the set of results presented here are consistent with the different robustness checks.
 
@@
 \end{equation}
-where $TFP_t$ is the log-level of Fernald total factor productivity at time $t$, $ICTI_{t}$ is the log-level of real information and communication technology investment at time $t$,\footnote{Notice that $ICTI_t$ is defined as the total expenditure at time $t$ in equipment and computer software meant to be used in production for more than an year.} $GDP_t$ is the log-level of real gross domestic product at time $t$, $C_t$ is the log-level of real consumption at time $t$, and $RP_t$ is the log-deviation of ratio between prices of ICT goods and services and the consumer price index (CPI).\footnote{Except for $RP_t$ that is not cointegrated with the remaining variables, we opt for estimating the VAR in levels since it produces consistent estimates of the impulse responses and is robust to cointegration of unknown forms.
+where $TFP_t$ is the log-level of Fernald total factor productivity at time $t$, $ICTI_{t}$ is the log-level of real information and communication technology investment at time $t$,\footnote{$ICTI_t$ is defined as the total expenditure at time $t$ in equipment and computer software meant to be used in production for more than an year.} $GDP_t$ is the log-level of real gross domestic product at time $t$, $C_t$ is the log-level of real consumption at time $t$, and $RP_t$ is the log-deviation of the ratio between prices of ICT goods and services and the consumer price index (CPI).\footnote{Except for $RP_t$ that is not cointegrated with the remaining variables, we opt for estimating the VAR in levels since it produces consistent estimates of the impulse responses and is robust to cointegration of unknown forms.
 In particular, as suggested by \cite{hamilton1994time} when there is uncertainty regarding the nature of common trends, estimating the system in levels is considered the conservative approach.
-In any case our results are very similar when estimating a vector error correction model (VECM).} All the variables have a quarterly frequency from 1989:Q1 to 2017:Q1 and refer to the U.S.
-economy.
-$B(L)$ is a ($5\times 5$) matrix of lag-operator functions of the same order.
-Following the Bayesian Information Criterion (BIC), the lag operator functions is one which implies that we regress variables at time $t$ with their own lagged values at $t-1$.\footnote{The Hannan-Quinn Criterion (HQ) suggests to use two lags.
+The alternative approach is to estimate the system as a vector error correction model (VECM); our results remain very similar also in this case.} Our dataset is quarterly and covers the U.S.
+economy from 1989:Q1 to 2017:Q1.\footnote{All data are from the BEA except for TFP, which is the series constructed by John Fernald, available on his website.} $B(L)$ is a ($5\times 5$) matrix of lag-operator functions of the same order.
+Following the Bayesian Information Criterion (BIC), we set choose one lag, which implies that we regress variables at time $t$ with their own lagged values at $t-1$.\footnote{The Hannan-Quinn Criterion (HQ) suggests to use two lags.
 Results remains consistent following this second criterion.} Finally, $i_t$ is a ($5 \times 1$) vector of correlated innovations where $\Sigma = i'_t i_t$.

### 2018-07-01 Latex/Draft_Summer2018/Summer2018.tex
more work on the empirical part

@@
 
-Our simplest identification strategy implies that an ICT-investment technological shock (hereafter ICT shock) has no impact effect on TFP and maximal impact effect on ICTI.
-We justify these assumptions with both empirical and theoretical argument.
-First of all, using data released on April, 2018 by the Bureau of Economic Analysis (BEA) the real value added of the information sector on real GDP is slightly below $5$\% for the underlying quarter.
-Thus, since the share of this sector accounts for a negligible part in the whole economy, we assume that an ICT shock is orthogonal to current TFP.
-In addition, in line with theoretical results firstly presented by \cite{greenwood1997long}, we expect that an ICT shock should enhance sector-specific investment since ICT goods are now easier to produce and cheaper to buy.
+Our simplest identification strategy assumes that an ICT-investment technological shock (hereafter ICT shock) has no impact effect on TFP and maximal impact effect on ICTI.
+We justify these assumptions with both empirical and theoretical arguments.
+First of all, using data released in April, 2018 by the Bureau of Economic Analysis (BEA) the real value added of the information sector on real GDP is slightly below $5$\% for the underlying quarter.\footnote{There are many ways to quantify the size of the ICT sector, both in terms of what share one considers and how one defines the ICT sector.
+The number presented in the text refers to the value added share of the ICT sector, defined as in Section \ref{eq:mainSpecification}.
+The statement that the ICT sector is tiny is however not sensitive to the definition of the sector or to the choice of share.
+Even with broader definitions, one obtains numbers in the range of 5\%.} Thus, since the share of this sector accounts for a negligible part in the whole economy, we think it safe to assume that an ICT shock is orthogonal to current TFP.
+In addition, the theory of multi-sector models, firstly presented by \cite{greenwood1997long}, predicts that a productivity increase in one sector should lead to sectoral output becoming cheaper.
+Thus, we expect that an ICT shock should enhance sector-specific investment since ICT goods are now easier to produce and cheaper to buy.
 As a result, we expect an ICT shock to have a maximal impact effect on ICTI.
 
-Following a similar notation of \cite{barsky2011news}, we implement our identification strategy as follows.
+Using a notation similar to \cite{barsky2011news}, we implement our identification strategy as follows.
 Let $y_t$ be the $(5 \times 1)$ vector of observables of length $T$ presented above.
-Once can form the reduced form moving average representation:
+One can form the reduced form moving average representation:
 $$
@@
 $$
-where $A(L) = [I - \bar{B}(L)]^{-1}$ and $\bar{B}(L)$ has no constant terms. Assume now there exists a linear combination that maps innovations $i_t$ to structural shocks $s_t$:
+where $A(L) = [I - \bar{B}(L)]^{-1}$ and $\bar{B}(L)$ has no constant terms. Assume now that there exists a linear combination that maps innovations $i_t$ to structural shocks $s_t$:
 $$
@@
 
-The matrix of impact responses to all shocks is:
+The matrix of impact responses to all shocks is: % TYPO HERE? either Atilde or A0 D. Checked Barsky, this seems correct but I'm confused. 
 $$
@@
 $$
-and is specifically formed by the following elements,
+and is specifically formed by the following elements, denoting the responses of variable $i$ to shock $j$, % same here
 $$
@@
 $$
-where $e_k$ is a selection column vector of the same dimension of $\tilde{A}_0$ with $1$ in the $k$th element and zero elsewhere.
-In particular, notice that $e_j$ is selecting a specific column of $D$, which will be denoted by $\gamma_j$.
-As a result, $\tilde{A}_0\gamma_j$ denotes the vector of impact responses of all the variable to shock $j$.
+where $e_k$ is a selector column vector of the same dimension as $\tilde{A}_0$ with $1$ in the $k$th element and zero elsewhere.
+In particular, notice that $e_j$ is selecting a specific column of $D$.
+Let this column be denoted by $\gamma_j$.
+Using this notation, $\tilde{A}_0\gamma_j$ is the vector of impact responses of all the variable to shock $j$.
 
-Let observe from System \ref{eq:mainSpecification} that $TFP_t$ is ordered first and $ICTI_t$ second.
-In order to implement our identification strategy, we need to mathematically solve the following problem:
+Observe from System \ref{eq:mainSpecification} that $TFP_t$ is ordered first and $ICTI_t$ second. Our identification strategy is then the solution to the following problem:
 \begin{equation}\label{eq:mainObjective}
@@
 where $j$ represents the arbitrary position of the ICT shock.
-Then, in order to ensure that this identification belongs to the space of possible orthogonalizations of $\Sigma$, the problem is denoted in terms of choosing $\gamma_j$ conditional on any orthogonalization, $\tilde{A}_0$.
-Objective function \ref{eq:mainObjective} imposes that an ICT shock as a maximal impact effect on ICT investment.
+Then, in order to ensure that this identification belongs to the space of possible orthogonalizations of $\Sigma$, the problem is formulated in terms of choosing $\gamma_j$ conditional on any orthogonalization, $\tilde{A}_0$.
+Objective function \ref{eq:mainObjective} imposes that an ICT shock has a maximal impact effect on ICT investment.
 Constraint \ref{eq:mainZeroTFP} orthogonalizes current TFP to ICT shocks and Constraint \ref{eq:mainOrtho} satisfies the condition that $\gamma_j$ is derived from an orthogonal matrix $D$.
@@
 Appendix \ref{section:mainSetResults} shows the estimated impulse responses of System \ref{eq:mainSpecification} to the identified ICT shock.
-The shaded gray areas are the $90$\% and $95$\% confidence bands from 2000 bias-corrected bootstrap procedure of \cite{kilian1998small}.
-In particular, Figure \ref{fig:TFP_main} shows impulse response of TFP to an ICT shock.
+The shaded gray areas are the $90$\% and $95$\% confidence bands from a bias-corrected bootstrap procedure of \cite{kilian1998small} using 2000 simulations.
+Our main interest, Figure \ref{fig:TFP_main}, shows the impulse response of TFP to an ICT shock.
 TFP takes around $4$ quarters before displaying a positive and significant effect and reaches its peak of $1.2$\% after $24$ quarters.
@@
 In Figures \ref{fig:GDP_main} and \ref{fig:C_main}, we present responses of real GDP and real consumption, respectively.
-Real GDP has a significant impact response of $0.3$\% and reaches its peak of almost $0.5$\% approximately at the same time of TFP.
+Real GDP has a significant impact response of $0.3$\% and reaches its peak of almost $0.5$\% approximately at the same time as TFP.
 Similarly, real consumption has an impact effect of $0.2$\% with a delayed peak of $0.5$\%.
-Finally, in Figure \ref{fig:RP_main}, relative prices has a significant and negative impact response of $0.4$\% and remain persistently below their own steady state value for almost $9$ years.
+Finally,  Figure \ref{fig:RP_main} depicts that response of relative prices.
+Despite imposing no restriction here, the response of RP is broadly in line with multi-sector theory.
+Relative prices drop significantly on impact by $0.4$\% and remain persistently below their own steady state value for almost $9$ years.
 
-In addition, Table \ref{table:vardec} in Appendix \ref{section:vardec} presents forecast error variance of each variable on impact, and after one-, two-, four-, six-, and ten-year horizon.
-In line with impulse responses, ICT shocks, which are orthogonal to current productivity, explain a third of TFP fluctuations over ten-year horizon.
+In addition, Table \ref{table:vardec} in Appendix \ref{section:vardec} presents forecast error variance decompositions for the ICT shock on each variable.
+The table shows decompositions on impact, and at a one-, two-, four-, six-, and ten-year horizon.
+In line with the impulse responses, ICT shocks, which are orthogonal to current productivity, explain nothing of current TFP fluctuations.
+At a ten-year horizon, however, this fraction is over a third!
 On the other hand, ICT shocks drive almost the whole variation in ICT investment on impact but this effect tends to decay over time getting below the $50$\% after 10 years.

### 2018-07-01 Latex/Draft_Summer2018/Summer2018.tex
read up to the empirical part that you have written
I think this paper will be great! I’m very enthusiastic! :)

@@
 The table shows decompositions on impact, and at a one-, two-, four-, six-, and ten-year horizon.
+These results are very interesting in their own right, as they hint that the ICT sector may have a particular role for the overall productivity of the economy.
+
 In line with the impulse responses, ICT shocks, which are orthogonal to current productivity, explain nothing of current TFP fluctuations.
 At a ten-year horizon, however, this fraction is over a third!
-On the other hand, ICT shocks drive almost the whole variation in ICT investment on impact but this effect tends to decay over time getting below the $50$\% after 10 years.
-Interestingly, both output and consumption has a remarkable reaction on impact: $26$\% and $19$\%, respectively.
-Moreover, this effect tends to increase reaching $40$\% in both cases over the maximal horizon.
-Finally, ICT shocks do not have a remarkable effect on relative prices.
+This crucial result is a strong sign that the ICT sector matters for overall productivity over and beyond the direct contribution of its sectoral productivity (which, as we have seen, is marginal).
+At the same time, ICT shocks drive almost the whole variation in ICT investment on impact, with a slow decay over time to below $50$\% after 10 years.
+Interestingly, both output and consumption have a remarkable reaction on impact: $26$\% and $19$\%, respectively.
+Moreover, this effect tends to increase reaching $40$\% in both cases at the maximal horizon.
+Finally, ICT shocks only account for a small fraction of movements in relative prices.
 The fraction of fluctuations explained on impact is only $6$\% with a peak of $14$\% between four and six years.
+Overall, these variance decompositions all seem to suggest that the ICT shock leads to complex forms of reallocation and accumulation that take place over the medium run in the economy.
+Our structural model of Section \ref{section:theory} provides a theoretical framework to think about these dynamics and to give them an economic interpretation.
 
@@
 
-In this section, we show a set of robustness checks aimed to show that our previous results are not driven by future signals regarding exogenous productivity.
-Although our results are robust when we purposely change the main specification presented in Subsection \ref{section:mainSpec}, an important critique to our empirical strategy is reverse causality coming from news on future TFP.
-As suggested by the news-shock literature, the positive reaction of ICTI on impact may be triggered by signals related future increases in productivity and not to a contemporaneous ICT shock.
+In this section, we present a set of robustness checks aimed to show that our previous results are not driven by future signals regarding exogenous productivity.
+The main concern against the specification of \ref{section:mainSpec} is reverse causality coming from the presence of news about future TFP that is not accounted for.
+Indeed, the news-shock literature warns that the positive reaction of ICTI on impact may be triggered by signals related to future increases in productivity and not to a contemporaneous ICT shock.
 In other words, our identification strategy may confound our shock of interest with a news shock which contemporaneously enhances investment in ICT capital goods.
 We address this issue by providing two main alternative identification strategies which we show deliver the same time series of ICT shocks as our initial specification.
-Firstly, we test if our result is robust once removed all the forward looking variables which fluctuations may be unrelated to sector-specific technological changes: consumption and output.
-Technically speaking, consumption and output may granger-cause future TFP for reasons which are orthogonal to ICT shocks.
-For example, the forward-looking nature of consumption may provide to the VAR unnecessary information regarding future changes in TFP not related to an ICT shock which our identification strategy is not able to filter it out.
-Secondly, we apply a sequential identification where we firstly identify a news shock in the spirit of \cite{barsky2011news}, and subsequently we identify our sectoral ICT shock using the previous identification strategy.
-This second strategy has the specific purpose of filtering out all the current movements in forward-looking variables related to future fluctuations of TFP which are not related to current ICT shocks.
 
-Encouragingly, controlling for signals regarding future movements in productivity does not affect our identified ICT shocks suggesting a causal relation which goes from current ICT investment to future TFP.
+As a first-pass test, % cite Barsky Basu Lee and Forni or whatevs
+we check if our results are robust once we remove all the forward looking variables whose fluctuations may be unrelated to sector-specific technological changes: consumption and output.
+Technically speaking, consumption and output may Granger-cause future TFP for reasons which are orthogonal to ICT shocks.
+For example, the forward-looking nature of consumption may provide the VAR with information regarding future changes in TFP not related to an ICT shock, which our identification strategy is not able to filter out.
+Our second test is running a VAR in which we identify both ICT shocks and news shocks.
+In particular, we apply a sequential identification where we first identify a news shock in the spirit of \cite{barsky2011news}, and subsequently we identify our sectoral ICT shock using our original identification strategy.
+This second strategy has the specific purpose of filtering out all the current movements in forward-looking variables related to future fluctuations of TFP which are not related to current ICT shocks, as such fluctuations are all captured by the identified news shock.
+
+As is illustrated in the rest of this section, both our robustness checks recover the same series for structural ICT shocks as our initial specification, and thus leave our results unaffected.
+We therefore conclude that controlling for signals regarding future movements in productivity does not affect our identified ICT shocks, and thus confirm the causal relation between current ICT investment and future TFP.
 

### 2018-07-02 Latex/Draft_Summer2018/Summer2018.tex
Starting to write the second alternative to control for news

@@
 economy from 1989:Q1 to 2017:Q1.\footnote{All data are from the BEA except for TFP, which is the series constructed by John Fernald, available on his website.} $B(L)$ is a ($5\times 5$) matrix of lag-operator functions of the same order.
-Following the Bayesian Information Criterion (BIC), we set choose one lag, which implies that we regress variables at time $t$ with their own lagged values at $t-1$.\footnote{The Hannan-Quinn Criterion (HQ) suggests to use two lags.
+Following the Bayesian Information Criterion (BIC), we choose one lag, which implies that we regress variables at time $t$ with their own lagged values at $t-1$.\footnote{The Hannan-Quinn Criterion (HQ) suggests to use two lags.
 Results remains consistent following this second criterion.} Finally, $i_t$ is a ($5 \times 1$) vector of correlated innovations where $\Sigma = i'_t i_t$.
 
-\subsubsection{Empirical Strategy}
+\subsubsection{Empirical Strategy}\label{section:empiricalstrategy_simple}
 
@@
 
-Three-variables one lag, just show the structural shocks and their correlation. Responses very similar.
+In this part of the paper, we employ a first-pass test where we attempt to show that our ICT shock is not confounded with future signals of TFP unrelated to the ICT sector.
+
+As discussed by \cite{sims2012news}, \cite{forni2014sufficient}, and \cite{barsky2015whither} the presence of forward-looking variables in the VAR is a necessary condition to correctly identify a news shock.
+In particular, since the univariate TFP process cannot predict future TFP,\footnote{It is well-accepted that TFP growth can be approximated as a white noise.} a news shock can be identified if there are variables that granger-cause TFP inside the VAR.
+For example, \cite{beaudry2006stock} use current movements in stock prices to predict future productivity, but also contemporary fluctuations in consumption, hours, investment, may implicitly reflect information regarding future technical change.
+
+Thus, as a simple test we propose to redo the exercise described in Section \ref{section:mainSpec} without two forward-looking macroeconomic variables not directly related with the ICT sector: consumption and output.\footnote{Notice that output implicitly reflect the behavior of hours and investment once we control for consumption.} If we are actually confounding news shocks with our ICT shock series then we would expect to see some differences in this second estimate.
+In other words, once our VAR is deprived by a source of information useful to recover a news shock, then the confounded part should either decreases or cancels out.
+
+As hinted above, in this section we estimate the following 3-dimensional system
+\begin{equation}\label{eq:noForVariables}
+\begin{pmatrix}
+TFP_t \\ 
+ICTI_t \\
+RP_t \\
+\end{pmatrix} = B(L) \begin{pmatrix}
+TFP_{t-1} \\ 
+ICTI_{t-1} \\
+RP_{t-1} \\
+\end{pmatrix} + i_t
+\end{equation}
+where  $TFP_t$, $ICTI_{t}$, and $RP_t$ have the same meaning and transformation as in System \ref{eq:mainSpecification}.
+As before, dataset is quarterly and covers the U.S.
+economy from 1989:Q1 to 2017:Q1.
+Finally, according to the Bayesian Information Criterion (BIC), we choose one lag.\footnote{The Hannan-Quinn Criterion (HQ) suggests to use two lags.
+Results remains consistent following this second criterion.} Using the same identification strategy presented in \ref{section:empiricalstrategy_simple}, we recover a series of ICT shocks which is correlated at $95$\% with the one estimated in 5-dimensional system.
+In particular, in Appendix \ref{section:removing_FL_Var}, Figure \ref{fig:shockSeries_removing} shows ICT shock series for both the 3-dimensional system and 5-dimensional one.
+In line with the correlation coefficient, the two series almost overlap each others suggesting that our initial result is not driven by the forward-looking power of consumption and output on TFP.
+
+However, although this result is encouraging, this first-pass test has obviously a weak power because the jump of ICTI on impact may be triggered by future exogenous signal of TFP.
+In this case, ICTI would be itself the source to granger-cause TFP and our ICT shock would be upward biased by news.
+To amend this deeper concern, we then need to employ a more complicated strategy presented in the next section.
 
 \subsubsection{Sequential Identification Strategy}
+
+In this part, we present an alternative procedure to rule out the presence of news from our empirical result.
+In this second test we run a VAR where we identify both ICT shocks and news shocks.
+We apply a sequential identification where we first identify a news shocks in the spirit of \cite{barsky2011news}, and subsequently we identify ICT shocks using our original identification strategy.
+Here we are seriously attempting to filter out future signals unrelated to current ICT shocks.
+Specifically, in the first step the news shock is identified as the shock orthogonal to current TFP that best explains its future movements.
+Then, as a second step, the ICT shock is identified as the shock orthogonal to current TFP that maximizes the impact effect on ICT investment.
+
+However, we need to clarify that in order to correctly employ this procedure, we need to take care to a second issue.
+As mentioned by \cite{barsky2011news}, \textit{``A general objection to our emprical approach would be that a number of structural shocks, which are not really news in the sense defined in the literature, might affect a measure of TFP in the future without impacting it immediately.
+Among these shocks might be research and development shocks, investment specific shocks, and reallocative shocks.
+Our identification (and any other existing VAR identifications) would obviously confound any true news shock with these shocks.''} In other words, by naively employing the procedure presented above, any ICT shocks would be fully captured as a news shock since it is orthogonal to current TFP and explains its future movements.
+
+Thus, in order to avoid the opposite mistake, namely confounding ICT shocks into news shocks, we need to augment the first step with a sort of control ad hoc for our case.
 
@@
 
+\newpage
+
+ \section{Removing Forward-Looking Variables}\label{section:removing_FL_Var}
+
+ 	\begin{figure}[h!]
+ 	\begin{center}
+ 		\includegraphics[scale=0.35]{MainFigures/Removing_FLVariables}
+ 		\caption{ICT shock series using the empirical strategy presented in \ref{section:empiricalstrategy_simple}.
+Blue solid line represents shock series for the 5-dimension system \ref{eq:mainSpecification} presented in \ref{section:mainSpec}.
+Red dotted line represents shock series for the 3-dimensional system presented in \ref{section:removing_FL_Var}.}
+ 		\label{fig:shockSeries_removing}
+ 	\end{center} 
+ \end{figure}
+
 \end{document}

### 2018-07-02 Code/just_IT_vecm/loading_structural_shocks.m

@@ -24,9 +24,18 @@ sICT5      = s_shock_just_IT;
 load Workspace_Just_IT_SVAR_3Variables_1LAG.mat
 sICT6      = s_shock_just_IT;
 
+quarter = 1989.25:0.25:2017;
+quarter = quarter';
 corr(sICT1,sICT6)
-plot(sICT1)
+plot(quarter,sICT1,'linewidth',1.8)
 hold on
-plot(sICT6)
+plot(quarter,sICT6,'--','linewidth',2.3)
+set(gcf,'color','w');
+grid on
+LEG = legend('5-dimensional system','3-dimesional system');
+LEG.FontSize = 20;
+legend boxoff
+title('Series of ICT shocks for different specifications','fontsize',40)
+axis tight
 
 

### 2018-07-03 Latex/Draft_Summer2018/Summer2018.tex
More writing on controlling for news

@@
 
-However, we need to clarify that in order to correctly employ this procedure, we need to take care to a second issue.
-As mentioned by \cite{barsky2011news}, \textit{``A general objection to our emprical approach would be that a number of structural shocks, which are not really news in the sense defined in the literature, might affect a measure of TFP in the future without impacting it immediately.
+However, we need to clarify that in order to correctly employ this procedure, we need to take care of a second issue.
+As correctly mentioned by \cite{barsky2011news}, \textit{``A general objection to our emprical approach would be that a number of structural shocks, which are not really news in the sense defined in the literature, might affect a measure of TFP in the future without impacting it immediately.
 Among these shocks might be research and development shocks, investment specific shocks, and reallocative shocks.
@@
 Thus, in order to avoid the opposite mistake, namely confounding ICT shocks into news shocks, we need to augment the first step with a sort of control ad hoc for our case.
+To formally discipline this additional identification assumption we need to design a two-sector model in the spirit of \cite{greenwood1997long}.\footnote{In particular, the model presented in Section \ref{section:theory} is closely related to \cite{oulton2007investment}.} In particular, we will mostly rely on the effect of an sector-neutral technology shock on relative prices to constraint the first step in order to avoid to capture an ICT shock into a news shock.
+
+\begin{prop}\label{prop:priceRestriction}
+In a two-sector economy, if both production functions are identical then any economy-wide productivity shocks do not affect relative prices between the two sectors.
+\end{prop}
+\begin{proof}
+	See Appendix \ref{section:proofpriceRestriction}.
+\end{proof}
+
+Proposition \ref{prop:priceRestriction} implies that a future sector-neutral technological change (the so-called news shock) never affects relative prices between sectors.
+Obviously, this statement is correct under the extreme assumptions that (i) the shock is expected to have the same impact on the two sectors and (ii) production functions are identical to each others.
+If those assumptions hold in the data, then the correct additional restriction would be to shut down to zero the impulse response of relative prices to a news shock.
+However, this restriction would obviously penalize the identification of news shocks since it is unlikely that assumptions (i) and (ii) perfectly hold in the data.
+We then opt for a more moderate strategy where we basically impose that the response of relative prices to a news shock should be relatively much smaller than the response observed by an ICT shock.
+Practically speaking, we arbitrarily set the impulse response of relative prices to be zero on some specific horizon rather than always.
+In particular, although results are robust to different horizon restrictions, our favorite specification is the one which set relative prices to have zero effect in the first two periods.
+
+In this case, our specification is the following 6-variable VAR,
+\begin{equation}\label{eq:newsSpecification}
+\begin{pmatrix}
+TFP_t \\ 
+SP_t \\
+ICTI_t \\
+GDP_t \\
+C_t \\
+RP_t \\
+\end{pmatrix} = B(L) \begin{pmatrix}
+TFP_{t-1} \\ 
+SP_{t-1} \\
+ICTI_{t-1} \\
+GDP_{t-1} \\
+C_{t-1} \\
+RP_{t-1} \\
+\end{pmatrix} + i_t
+\end{equation}
+where $TFP_t$, $ICTI_t$, $GDP_t$, $C_t$, and $RP_t$ have the same meaning and transformation as in System \ref{eq:mainSpecification}.
+Moreover, $SP_t$ represents the log-transformation of Standard \& Poor's 500 stock prices added to provide an additional forward-looking variable to the system.\footnote{As mentioned before, following \cite{sims2012news}, \cite{forni2014sufficient}, and \cite{barsky2015whither} the presence of forward-looking variables in the VAR is a necessary condition to correctly identify a news shock.} As before, dataset is quarterly and covers the U.S.
+economy from 1989:Q1 to 2017:Q1 and following the BIC and HQ criteria we opt for one lag.
+
+Using the same notation in Section \ref{section:empiricalstrategy_simple}, our identification strategy can be presented as follows,\footnote{Also in this case we keep following the same notation of \cite{barsky2011news}.}
+
+\
+
+\textbf{Step 1 - Identification of $\gamma_{news}$}
+$$
+\max_{\gamma_{news}} \sum_{h = 0}^{H} \Sigma
+$$
 
@@
 
+\newpage
+
+\section{Proof of Proposition \ref{prop:priceRestriction}}\label{section:proofpriceRestriction}
+
+Prova
+
 \end{document}

### 2018-07-03 Latex/Draft_Summer2018/Summer2018.tex
keep writing, reviewing some technicalities

@@
 Let $y_t$ be the $(5 \times 1)$ vector of observables of length $T$ presented above.
-One can form the reduced form moving average representation:
+The reduced-form VAR takes the following form,
 $$
-y_t = \bar{B}(L)y_{t} + i_t \ \ \Rightarrow \ \ y_t = A(L)i_t
+y_t = B(L)y_{t-1} + i_t 
 $$
-where $A(L) = [I - \bar{B}(L)]^{-1}$ and $\bar{B}(L)$ has no constant terms. Assume now that there exists a linear combination that maps innovations $i_t$ to structural shocks $s_t$:
+Assume now that there exists a linear combination that maps innovations $i_t$ to structural shocks $s_t$,
 $$
-s_t = A_0 i_t
+A_0 s_t = i_t
 $$
-This entails the structural moving average representation:
+which implies the structural-form VAR
 $$
-y_t = C(L)i_t
+A_0^{-1}y_t = C(L) y_{t-1} + s_t
 $$
-where $C(L) = A(L) A_0$ and $i_t = A_0^{-1} s_t$.
+where $C(L) = A_0^{-1} B(L)$ and $s_t = A_0^{-1} i_t$.
 The impact matrix $A_0$ must be such that $\Sigma = A_0 A_0'$.
@@
 
-Using the same notation in Section \ref{section:empiricalstrategy_simple}, our identification strategy can be presented as follows,\footnote{Also in this case we keep following the same notation of \cite{barsky2011news}.}
+Using a similar notation in Section \ref{section:empiricalstrategy_simple}, assume for simplicity  that $B(L)$ allows only of one lag
 
@@
 $$
-\max_{\gamma_{news}} \sum_{h = 0}^{H} \Sigma
+\max_{\gamma_{news}} \frac{\sum_{\tau = 0}^H B_{}}{}
 $$

### 2018-07-04 Latex/Draft_Summer2018/Summer2018.tex
closing the document
more notations to empirical

@@
 $$
-\Omega = \tilde{A}_0 D
+\Pi(0) = \tilde{A}_0 D
 $$
@@
 $$
-\Omega_{i,j} = e_i' \tilde{A}_0 D e_j
+\Pi_{i,j}(0) = e_i' \tilde{A}_0 D e_j
 $$
@@
 \begin{equation}\label{eq:mainObjective}
-\max_{\gamma_j} \Omega_{2,j} = e_2' \tilde{A}_0 \gamma_j
+\max_{\gamma_j} \Pi_{2,j}(0) = e_2' \tilde{A}_0 \gamma_j
 \end{equation}
@@
 \begin{equation}\label{eq:mainZeroTFP}
-\Omega_{1,j} = e_1' \tilde{A}_0 \gamma_j = 0, \ \ \text{and}
+\Pi_{1,j}(0) = e_1' \tilde{A}_0 \gamma_j = 0, \ \ \text{and}
 \end{equation}
@@
 
-Using a similar notation in Section \ref{section:empiricalstrategy_simple}, assume for simplicity  that $B(L)$ allows only of one lag
-
+Using a similar notation in Section \ref{section:empiricalstrategy_simple}, assume for notation simplicity that $B(L) = B$ allows only of one lag.
+Define the impulse response of variable $i$ to the identified shock $j$ at time $t$ as,\footnote{We also suppress the constant to simplify the notation.
+Identification strategy can obviously be applied for $B(L)$ allowing for more than one lag and with the constant.}
+$$
+\Pi_{i,j}(t) = e_i'B^t \tilde{A}_0 D e_j
+$$
+and its variance decomposition up to time $h$
+$$
+\Omega_{i,j}(h) = \frac{ \sum_{t=0}^h e_i'B^t \tilde{A}_0 D e_j e_j' D' \tilde{A}_0' B'^t e_i } { }
+$$
 \
@@
 $$
-\max_{\gamma_{news}} \frac{\sum_{\tau = 0}^H B_{}}{}
+\max_{\gamma_{news}} \frac{\sum_{\tau = 0}^H B \tilde{A}_0 \tilde{A}_0 }{}
 $$

### 2018-07-04 Latex/Draft_Summer2018/Summer2018.tex
More stuff
More writing and running some stuff

@@
 
+\subsubsection*{Data}
+
 In this case, our specification is the following 6-variable VAR,
@@
 
+\subsubsection*{Empirical Strategy}
+
 Using a similar notation in Section \ref{section:empiricalstrategy_simple}, assume for notation simplicity that $B(L) = B$ allows only of one lag.
@@
 $$
-\Pi_{i,j}(t) = e_i'B^t \tilde{A}_0 D e_j
+\Pi_{i,j}(t) = e_i' B^t \tilde{A}_0 D e_j = e_i' B^t \tilde{A}_0 \gamma_j
 $$
@@
 $$
-\Omega_{i,j}(h) = \frac{ \sum_{t=0}^h e_i'B^t \tilde{A}_0 D e_j e_j' D' \tilde{A}_0' B'^t e_i } { }
+\Omega_{i,j}(h) = \frac{ \sum_{t=0}^h e_i' B^t \tilde{A}_0 D e_j e_j' D' \tilde{A}_0' B'^t e_i } {e_i'( \sum_{\tau = 0}^H B^t \Sigma B'^t )e_i} = \frac{ \sum_{t=0}^h e_i' B^t \tilde{A}_0 \gamma_j \gamma_j' \tilde{A}_0' B'^t e_i } {e_i'( \sum_{\tau = 0}^H B^t \Sigma B'^t )e_i}
 $$
-\
+Given the following notation and let notice that TFP is ordered first and ICTI second, the identification strategy can be summarized as follows,
 
-\textbf{Step 1 - Identification of $\gamma_{news}$}
+\subsubsection*{Step 1 - Identification of $\gamma_{news}$}
 $$
-\max_{\gamma_{news}} \frac{\sum_{\tau = 0}^H B \tilde{A}_0 \tilde{A}_0 }{}
+\max_{\gamma_{news}} \Omega_{1,news}(h) = \frac{ \sum_{t=0}^h e_1' B^t \tilde{A}_0 \gamma_{news} \gamma_{news}' \tilde{A}_0' B'^t e_1 } {e_1' ( \sum_{\tau = 0}^H B^t \Sigma B'^t )e_1}
 $$
+subject to
+$$
+\Pi_{1,news}(0) = 0,
+$$
+$$
+\Pi_{6,news}(0) = \Pi_{6,news}(1) = 0, \ \ \text{and}
+$$
+$$
+\gamma_{news} \gamma_{news}' = 1.
+$$
+where the first constraint represents the zero-impact restriction of news on TFP.
+Moreover, the second constraint represents the arbitrary restriction to have a response of relative prices to news relatively small.\footnote{Our identification strategy is robust over different restrictions to relative prices.
+Results hold even if we set the zero restriction on other horizons.} Finally, the last constraint imposes that $\gamma_{news}$ should be a column derived from the orthogonal matrix $D$.
+
+\subsubsection*{Step 2 - Identification of $\gamma_{ICT}$}
+$$
+\max_{\gamma_{ICT}} \Pi_{2,ICT}(0) =  e_2' \tilde{A}_0 \gamma_{ICT} 
+$$
+subject to
+$$
+\Pi_{1,ICT}(0) = 0,
+$$
+$$
+\gamma_{news} \gamma_{ICT}' = 0, \ \ \text{and} \ \ \gamma_{ICT} \gamma_{ICT}' = 1.
+$$
+where the first constraint represents the zero-impact restriction of news on TFP and the last constraint imposes that both $\gamma_{news}$ and $\gamma_{ICT}$ should be two different columns derived from the orthogonal matrix $D$.
+
+\subsubsection*{Results}
 

### 2018-07-04 Code/just_IT_controlling_NEWS/main_file_SVAR_just_IT_controllingNEWS.m

@@ -38,7 +38,7 @@ elseif sum(strcmp('SP deflated', varnames))==1 % i.e. we use SP deflated by GDPD
 elseif sum(strcmp('SP deflated per capita', varnames))==1 % i.e. we use SP deflated by GDPDEF for news
       pos_news = find(strcmp('SP deflated per capita', varnames));
 end
-pos_IT = find(strcmp('Real IT Investment', varnames));
+pos_IT = find(strcmp('Real ICT Investment', varnames));
 if find(strcmp('Relative Price', varnames)) > 0
       pos_rel_prices = find(strcmp('Relative Price', varnames));
 elseif find(strcmp('Relative price PCE', varnames))
@@ -49,7 +49,7 @@ which_shocks = [pos_news pos_IT];
 %Technical Parameters
 max_lags        = 10;
 nburn           = 0; %with the Kilian correction better not burning!!!
-nsimul          = 100; %5000
+nsimul          = 2000; %5000
 nvar            = size(data,2);
 sig1            = 0.9; % significance level
 sig2            = 0.95; % a 2nd sig. level

### 2018-07-04 Code/just_IT_controlling_NEWS/two_steps_controllingNEWS.m

@@ -1,5 +1,5 @@
 function [impact, gam] = ...
-      two_steps_controllingNEWS(which_variable,which_shocks,H,LR_hor,B,A,q,pos_IT)
+      two_steps_controllingNEWS(which_variable,which_shocks,H,LR_hor,B,A,var_restricted,pos_IT)
 %which_variable: variable we want to max the response for a specific shock (TFP)
 %which_shocks: the shock is maximizing the FEV of which_variable (--> news and IT shocks)
 %H: horizon of the maximization
@@ -34,10 +34,10 @@ sig = 0.9; % not used, but we need to input something not to get error
 hor_IRF = 40;
 [IR, ~, ~, ~, ~] = genIRFs(A,0,vertcat(ones(1,size(B,2)), B),0,hor_IRF, sig, sig);
 relaxing_impact = 1;
-relaxing_longrun = 1;
+relaxing_longrun = 2;
 R = IR(:,relaxing_impact:relaxing_longrun,:);
 %R = squeeze(IR(:,LR_hor,:)); % comment this out if you wanna not impose the LR-restriction
-q = 3;
+var_restricted = 6;
 %Constraint that News and IT have no contemporaneous effect on TFP
 Me3       = 1; %  Me = no. of equality constraints
 Beq3      = zeros(Me3,1); % Beq is (Me x 1) where
@@ -46,7 +46,7 @@ Aeq3(1,1) = 1; %zero-impact of news on TFP
 
 % dbstop constraint_ryan at 12
 % [gam3_opt] = fmincon(obj, gam3_zero,[],[],Aeq3,Beq3,[],[],@(gam3) constraint_barskysims11(gam3),options);
-[gam3_opt] = fmincon(obj, gam3_zero,[],[],Aeq3,Beq3,[],[],@(gam3) constraint_theory(gam3,R,q),options);
+[gam3_opt] = fmincon(obj, gam3_zero,[],[],Aeq3,Beq3,[],[],@(gam3) constraint_theory(gam3,R,var_restricted),options);
 %fmincon(FUN,X0,A,B,Aeq,Beq,LB,UB,NONLCON,OPTIONS)
 
 % Recover FEV from the step 1 minimization

### 2018-07-05 Code/just_IT_controlling_NEWS/main_file_SVAR_just_IT_controllingNEWS.m
Revert "More writing and running some stuff"
This reverts commit c9524e5b17fba094c2b44d328d5a318eb17bbbfb.

@@ -38,7 +38,7 @@ elseif sum(strcmp('SP deflated', varnames))==1 % i.e. we use SP deflated by GDPD
 elseif sum(strcmp('SP deflated per capita', varnames))==1 % i.e. we use SP deflated by GDPDEF for news
       pos_news = find(strcmp('SP deflated per capita', varnames));
 end
-pos_IT = find(strcmp('Real ICT Investment', varnames));
+pos_IT = find(strcmp('Real IT Investment', varnames));
 if find(strcmp('Relative Price', varnames)) > 0
       pos_rel_prices = find(strcmp('Relative Price', varnames));
 elseif find(strcmp('Relative price PCE', varnames))
@@ -49,7 +49,7 @@ which_shocks = [pos_news pos_IT];
 %Technical Parameters
 max_lags        = 10;
 nburn           = 0; %with the Kilian correction better not burning!!!
-nsimul          = 2000; %5000
+nsimul          = 100; %5000
 nvar            = size(data,2);
 sig1            = 0.9; % significance level
 sig2            = 0.95; % a 2nd sig. level

### 2018-07-05 Code/just_IT_controlling_NEWS/two_steps_controllingNEWS.m

@@ -1,5 +1,5 @@
 function [impact, gam] = ...
-      two_steps_controllingNEWS(which_variable,which_shocks,H,LR_hor,B,A,var_restricted,pos_IT)
+      two_steps_controllingNEWS(which_variable,which_shocks,H,LR_hor,B,A,q,pos_IT)
 %which_variable: variable we want to max the response for a specific shock (TFP)
 %which_shocks: the shock is maximizing the FEV of which_variable (--> news and IT shocks)
 %H: horizon of the maximization
@@ -34,10 +34,10 @@ sig = 0.9; % not used, but we need to input something not to get error
 hor_IRF = 40;
 [IR, ~, ~, ~, ~] = genIRFs(A,0,vertcat(ones(1,size(B,2)), B),0,hor_IRF, sig, sig);
 relaxing_impact = 1;
-relaxing_longrun = 2;
+relaxing_longrun = 1;
 R = IR(:,relaxing_impact:relaxing_longrun,:);
 %R = squeeze(IR(:,LR_hor,:)); % comment this out if you wanna not impose the LR-restriction
-var_restricted = 6;
+q = 3;
 %Constraint that News and IT have no contemporaneous effect on TFP
 Me3       = 1; %  Me = no. of equality constraints
 Beq3      = zeros(Me3,1); % Beq is (Me x 1) where
@@ -46,7 +46,7 @@ Aeq3(1,1) = 1; %zero-impact of news on TFP
 
 % dbstop constraint_ryan at 12
 % [gam3_opt] = fmincon(obj, gam3_zero,[],[],Aeq3,Beq3,[],[],@(gam3) constraint_barskysims11(gam3),options);
-[gam3_opt] = fmincon(obj, gam3_zero,[],[],Aeq3,Beq3,[],[],@(gam3) constraint_theory(gam3,R,var_restricted),options);
+[gam3_opt] = fmincon(obj, gam3_zero,[],[],Aeq3,Beq3,[],[],@(gam3) constraint_theory(gam3,R,q),options);
 %fmincon(FUN,X0,A,B,Aeq,Beq,LB,UB,NONLCON,OPTIONS)
 
 % Recover FEV from the step 1 minimization

### 2018-07-05 Latex/Draft_Summer2018/Summer2018.tex
Revert "More writing and running some stuff"
This reverts commit c9524e5b17fba094c2b44d328d5a318eb17bbbfb.
Good progress for controlling for news - More writing

@@
 \usepackage{amsmath}
+\usepackage{subcaption}
 \usepackage{tikz}
@@
 
-\subsubsection{Sequential Identification Strategy}
+\subsubsection{Sequential Identification Strategy}\label{section:twosteps}
 
@@
 Practically speaking, we arbitrarily set the impulse response of relative prices to be zero on some specific horizon rather than always.
-In particular, although results are robust to different horizon restrictions, our favorite specification is the one which set relative prices to have zero effect in the first two periods.
+In particular, although results are robust to different horizon restrictions, our favorite specification is the one which set relative prices to have zero effect in the first three periods.
 
@@
 $$
-\Pi_{6,news}(0) = \Pi_{6,news}(1) = 0, \ \ \text{and}
+\Pi_{6,news}(0) = \Pi_{6,news}(1) = \Pi_{6,news}(2) = 0, \ \ \text{and}
 $$
@@
 
+\newpage
+
+\section{Controlling for News Shocks - Two-Step Identification Strategy}
+
+\subsection{Impulse Responses}\label{section:IRF_2step}
+
+\begin{figure}[h!]
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{MainFigures/fig_News_Shock_on_TFP__controllinNEWS_}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{MainFigures/fig_ICT_Shock_on_TFP__controllinNEWS_}
+	\end{subfigure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=1\linewidth]{MainFigures/fig_News_Shock_on_Real_SP__controllinNEWS_}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=1\linewidth]{MainFigures/fig_ICT_Shock_on_Real_SP__controllinNEWS_}
+\end{subfigure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=1\linewidth]{MainFigures/fig_News_Shock_on_Real_ICT_Investment__controllinNEWS_}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=1\linewidth]{MainFigures/fig_ICT_Shock_on_Real_ICT_Investment__controllinNEWS_}
+\end{subfigure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\caption{Empirical impulse responses of TFP, Real Stock Prices, and Real ICT Investment to a news shock and an ICT shock.
+The red solid lines are the estimated impulse responses to our ICT shock.
+The shaded dark gray area and the shaded light gray area are the $90$\% and $95$\% confidence intervals, respectively, from 2000 bias-corrected bootstrap replications of the reduced-form VAR.
+The horizontal axes refer to forecast horizon and the units of the vertical axes are percentage deviations.}
+	\label{fig:2stepIRF_first}
+\end{figure}
+
+\newpage
+
+\begin{figure}[h!]
+\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=1\linewidth]{MainFigures/fig_News_Shock_on_Real_GDP__controllinNEWS_}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=1\linewidth]{MainFigures/fig_ICT_Shock_on_Real_GDP__controllinNEWS_}
+\end{subfigure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=1\linewidth]{MainFigures/fig_News_Shock_on_Real_Consumption__controllinNEWS_}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=1\linewidth]{MainFigures/fig_ICT_Shock_on_Real_Consumption__controllinNEWS_}
+\end{subfigure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=1\linewidth]{MainFigures/fig_News_Shock_on_Relative_Price__controllinNEWS_}
+\end{subfigure}%
+\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=1\linewidth]{MainFigures/fig_ICT_Shock_on_Relative_Price__controllinNEWS_}
+\end{subfigure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\caption{Empirical impulse responses of Real GDP, Real Consumption, and Relative Prices to a news shock and an ICT shock.
+The red solid lines are the estimated impulse responses to our ICT shock.
+The shaded dark gray area and the shaded light gray area are the $90$\% and $95$\% confidence intervals, respectively, from 2000 bias-corrected bootstrap replications of the reduced-form VAR.
+The horizontal axes refer to forecast horizon and the units of the vertical axes are percentage deviations.}
+\label{fig:2stepIRF_second}
+\end{figure}
+
+\newpage
+
+\subsection{ICT Shock Series}\label{section:ICTshockseries_2step}
+
+ 	\begin{figure}[h!]
+	\begin{center}
+		\includegraphics[scale=0.35]{MainFigures/ICTshocksSeries_ControllingforNEWS}
+		\caption{ICT shock series using two different empirical strategy.
+Blue solid line represents shock series for the 5-dimension system \ref{eq:mainSpecification} presented in \ref{section:mainSpec}.
+Red dotted line represents shock series for the 6-dimensional system \ref{eq:newsSpecification} presented in \ref{section:twosteps} where we employ a 2-step identification strategy in order to control for news shocks.}
+		\label{fig:shockSeries_2steps}
+	\end{center} 
+\end{figure}
+
 \end{document}

### 2018-07-05 Code/just_IT_controlling_NEWS/check_different_specifications.m

@@ -1,0 +1,57 @@
+clear all
+
+%load twotousandbootstrap_controllingNews_RPzero.mat
+load Workspace_Just_IT_controllingNEWS_shortrunimpactsRP_maxNEWS_maxIT_1LAG.mat
+
+data1 = data;
+B1 = B;
+A1 = A;
+res1 = res;
+imp1 = impact;
+IRFs1 = IRFs;
+gam1  = gam_opt;
+
+
+%load Workspace_Just_IT_controllingNEWS_shortrunimpactsRP_maxNEWS_maxIT_1LAG.mat
+load checkcheck3
+data2 = data;
+B2 = B;
+A2 = A;
+res2 = res;
+imp2 = impact;
+IRFs2 = IRFs;
+gam2 = gam;
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+
+
+check_data = sum(sum((data1 - data2).^2));
+check_B = sum(sum((B1 - B2).^2))
+check_A = sum(sum((A1 - A2).^2))
+check_res = sum(sum((res1 - res2).^2))
+check_imp = sum(sum((imp1 - imp2).^2))
+check_IRFs = sum(sum(sum((IRFs1 - IRFs2).^2)))
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2018-07-05 Code/just_IT_controlling_NEWS/constraint_theory.m

@@ -1,4 +1,4 @@
-   function [c,ceq] = constraint_ryan(gam,R,q) 
+   function [c,ceq] = constraint_theory(gam,R,q) 
        % gam is for this exercise gam3, 6x1
        % R = PA, the LR effect before multiplying with gam3. (nvar x nshocks)
        % q = position of relative prices

### 2018-07-05 Code/just_IT_controlling_NEWS/main_file_SVAR_just_IT_controllingNEWS.m

@@ -25,7 +25,7 @@ filename = 'dataset_main';
 sheet    = 'Data';
 range    = 'B1:W287';
 [data, varnames] = read_data2(filename, sheet, range);
-shocknames = {'News Shock','IT Shock'};
+shocknames = {'News Shock','ICT Shock'};
 varnames
 
 % Find positions of shocks and of relative prices in a correct way
@@ -106,11 +106,9 @@ end
 
 %Creating and Printing figures
 comment = [which_ID '_' char(varnames(5)) '_LR_hor_' num2str(LR_hor)];
-print_figs = 'no';
-
+print_figs = 'yes';
 [IRFs, ub1, lb1, ub2, lb2] = genIRFs(fake_impact,fake_impact_boot,...
       B,beta_tilde_star,H,sig1, sig2);
-
 % % With Barsky & Sims-type ID, since you do a abs max, there are two
 % % solutions: gam and -gam. So choose the one that makes sense. I'm doing
 % % that so that news and IT have + effects on TFP.
@@ -123,18 +121,17 @@ if sum(IRFs(1,:,pos_IT)) < 0 % if the majority of TFP response is negative
 end
 if sum(IRFs(1,:,pos_news)) < 0 % if the majority of TFP response is negative
       IRFs(:,:,pos_news)   = -IRFs(:,:,pos_news);
-      ub1(:,:,pos_news)     = - ub1(:,:,pos_news);
+      ub1(:,:,pos_news)     = - ub1(:,:,pos_news);c
       lb1(:,:,pos_news)     = - lb1(:,:,pos_news);
       ub2(:,:,pos_news)     = - ub2(:,:,pos_news);
       lb2(:,:,pos_news)     = - lb2(:,:,pos_news);
 end
-
 %Printing/Showing IRFs
 h = 40;
 % plotIRFs(IRFs,ub,lb,40,which_shocks,shocknames,varnames,which_ID,print_figs)
 % plot_single_IRFs(IRFs,ub1,lb1,h,which_shocks,shocknames, varnames, which_ID, print_figs)
 use_current_time = 0; % don't save the time
-plot_single_IRFs_2CIs(IRFs,ub1,lb1,ub2,lb2,h,which_shocks,shocknames, varnames, '_', print_figs, use_current_time)
[…]

### 2018-07-05 Code/just_IT_controlling_NEWS/two_steps_controllingNEWS.m

@@ -34,7 +34,7 @@ sig = 0.9; % not used, but we need to input something not to get error
 hor_IRF = 40;
 [IR, ~, ~, ~, ~] = genIRFs(A,0,vertcat(ones(1,size(B,2)), B),0,hor_IRF, sig, sig);
 relaxing_impact = 1;
-relaxing_longrun = 2;
+relaxing_longrun = 3;
 R = IR(:,relaxing_impact:relaxing_longrun,:);
 %R = squeeze(IR(:,LR_hor,:)); % comment this out if you wanna not impose the LR-restriction
 var_restricted = 6;
@@ -51,7 +51,7 @@ Aeq3(1,1) = 1; %zero-impact of news on TFP
 
 % Recover FEV from the step 1 minimization
 [FEV3_opt, ~, ~]     = objective_barskysims(which_variable,H,B,A,gam3_opt);
-FEV3_opt     = - FEV3_opt;
+FEV3_opt             = - FEV3_opt;
 
 if FEV3_opt > 1 || (gam3_opt'*gam3_opt - 1)^2 > 10^(-10) || gam3_opt(1)^2 > 10^(-12)
       warning('The problem is not consistent with the constraints.')
@@ -84,14 +84,15 @@ if max_again == 1
       if FEV_opt > 1 || (gam4_opt'*gam4_opt - 1)^2 > 10^(-10) || gam4_opt(1)^2 > 10^(-12)
             warning('The problem is not consistent with the constraints.')
       end
-      
-elseif max_again == 0
-      disp('In the second step we max impact effect on IT investment')
+end     
+if max_again == 0
+      disp('In the second step we max impact effect on ICT investment')
       D = eye(nvar);
       gam4_zero = D(:,which_shocks(2)); %IT shock impact vector (initial value)
       % Identifying gam4 - Max impact FEV_IT s.t. impact on TFP = 0
       %
       % Setting the objective function of Step2
+      which_variable = 3; %Position of ICT Investment! Be careful!
       obj2 = @(gam4) objective_just_IT(which_variable,A,gam4);
       %
       %Constraint that News and IT have no contemporaneous effect on TFP

### 2018-07-05 Code/just_IT_vecm/loading_structural_shocks.m

@@ -24,18 +24,28 @@ sICT5      = s_shock_just_IT;
 load Workspace_Just_IT_SVAR_3Variables_1LAG.mat
 sICT6      = s_shock_just_IT;
 
+load mainControllingforNews_2000boot_RPzeros1to3_MaxTFP_MaxITimpact_1Lag_6variables
+sICT7      = s_shock_just_IT(:,2);
+sNEWS3     = s_shock_just_IT(:,1);
+
+corr(sICT7,sICT1)
+
+%corr(sICT1,sICT6)
+
+
+
 quarter = 1989.25:0.25:2017;
 quarter = quarter';
-corr(sICT1,sICT6)
+corr(sICT1,sICT7)
 plot(quarter,sICT1,'linewidth',1.8)
 hold on
-plot(quarter,sICT6,'--','linewidth',2.3)
+plot(quarter,sICT7,'--','linewidth',2.3)
 set(gcf,'color','w');
 grid on
-LEG = legend('5-dimensional system','3-dimesional system');
+LEG = legend('Main Specification','Controlling for News Shocks');
 LEG.FontSize = 20;
 legend boxoff
-title('Series of ICT shocks for different specifications','fontsize',40)
+title('Series of ICT shocks for different identification strategies','fontsize',40)
 axis tight
 
 

### 2018-07-05 plot_single_IRFs_2CIs.m

@@ -15,8 +15,8 @@ nshocks = size(which_shock,2);
 periods = 1:h;
 
 %Ylim
-% min_y_lim = [-0.01   -0.01     -0.02     -0.02       -0.02     -0.02];
-% max_y_lim = [0.04        0.1      0.05      0.02        0.02      0.02];
+min_y_lim = [-0.005   -0.01     -0.01     -0.01       -0.01     -0.008];
+max_y_lim = [0.03        0.07      0.035      0.02        0.02      0.001];
 
 % Draw pretty pictures
 for i_shock=1:nshocks
@@ -41,7 +41,7 @@ for i_shock=1:nshocks
         xt = get(gca, 'XTick');
         set(gca, 'FontSize', 28)
         title([name, ' on ' , varname],'fontsize',72)
-          %ylim([min_y_lim(i_var) max_y_lim(i_var)]);
+        ylim([min_y_lim(i_var) max_y_lim(i_var)]);
         hold off
         grid on
         

### 2018-07-07 Latex/Draft_Summer2018/Summer2018.tex
starting the model

@@
 
+Figures \ref{fig:2stepIRF_first} and \ref{fig:2stepIRF_second} in Appendix \ref{section:IRF_2step} shows estimated impulse responses to both news and ICT shocks.
+In particular, Figure \ref{fig:2stepIRF_first} shows dynamic responses of TFP, stock prices, and ICT investment to both shocks and Figure \ref{fig:2stepIRF_second} shows dynamic responses of GDP, consumption and relative prices to both shocks as well.
+The shaded gray areas are the $90$\% and $95$\% confidence bands from a bias-corrected bootstrap procedure of \cite{kilian1998small} using 2000 simulations.
+
+Dynamic responses to an ICT shock are almost identical to the ones presented in the main identification in Section \ref{section:mainSpec}.
+After few lags, TFP displays a positive and significant effect and reaches its peak of $1.2$\% after $6$ years.
+Interestingly, stock prices jump on impact and the effect remain significant over the medium run.
+Real ICT investment has a large and positive impact response and it slowly starts to decay remaining significant for a long period of time.
+Both real GDP and real consumption have a significant impact response and reaches its peak approximately after $6$ years.
+Finally, the response of relative prices is negative and persistent as we have previously discussed.
+
+In addition, we show dynamic responses to a news shock to confirm the reliability of our identification strategy.
+Constraining fluctuations of relative prices to news does not qualitatively affect what has been already found in the literature.
+In line with \cite{barsky2011news}, it takes more that 2 years for TFP to display a positive, significant and strongly persistent effect.
+Stock prices have a strong forecasting power and show a $4$\% impact effect which is persistent and significant in the long run.
+Real ICT investment does not show a positive impact response but it slowly starts to increase getting significant after almost $2$ years.
+As found by \cite{barsky2011news} in their main specification, real GDP has a non-significant impact effect and it fast rises with all the variables of the system.
+Moreover, as expected by its forward looking nature, real consumption have a significant impact response and reaches its peak once TFP displays a significant effect.
+Finally, relative prices are initially constrained to have a zero response and then shows a small, negative and persistent deviation for at least five years which eventually dies out.
+
+Finally, we recover a series of ICT shocks which is correlated at $94$\% with the one estimated in System \ref{eq:mainSpecification} using the simple identification strategy presented in Section \ref{section:empiricalstrategy_simple}.
+In particular, in Appendix \ref{section:ICTshockseries_2step}, Figure \ref{fig:shockSeries_2steps} shows ICT shock series for both the 5-dimensional system and 6-dimensional presented in this section.
+In line with the correlation coefficient, the two series almost overlap each others suggesting that our initial result is not confounding any signal regarding future TFP with our estimated ICT shock.
+
+%Here there is room for further comments:
+%Variance explained by a news shock is only 20% -> smaller than the one in the literature.
+Maybe we should explain that news literature is confounding ICT shock into news shocks.
+However this is not really the target of our paper.
+Is it necessary to do?
+We need to think about that.
+
 %%%%%%%%%%%%%%%%%%%%               MODEL                 %%%%%%%%%%%%%%%%%% 
 \section{Model}\label{section:theory}
+
+In the previous section, we have documented results regarding the relation of current ICT investment and future productivity.
+Clearly, to rationalize empirical dynamic responses of aggregate macroeconomic variables to ICT shocks, we need a two-sector approach that distinguishes ICT goods from other output.
+In this section, we present a simple two-sector model that rationalizes our structural VAR estimates.
+The model presented has several common features with \cite{greenwood1997long} that design a two-sector economy where one sector displays a faster technology than the other.
+One different is that we focus specifically on ICT capital sector, rather than equipment, as the sector with faster technological improvements.
+This assumption will be necessary if we want to fit the fact that relative prices between the ICT investment and overall economy display a downward sloping trend.\footnote{In addition, we also rely on the results of \cite{whelan2003two} and \cite{oulton2007investment} to correctly define productivity and output share in our setting.}
+
+\subsubsection*{Household}
+
+Consider an economy inhabitated by a representative agent whi maximizes the expect values of his lifetime utility as given by
+$$
+\E \Bigg[  \sum_{t=0}^{\infty} \beta^t U(c_t,l_t)  \Bigg]
+$$
+with 
+$$
+U(c_t,l_t) = \log(c_t) - \frac{1}{1+\eta} l_t^{1+\eta}
+$$
+where $c_t$ and $l_t$ represent consumption and labor at time $t$.
+
+\subsection*{Final-Good Sector}
+
+In each period, the production of final output $y^c_t$ requires the services of labor $l_{1,t}$, and two types of capital: hard capital, $k^c_{1,t}$ and ICT capital, $k^i_{1,t}$.\footnote{Notice that $x_{1,t}$ has to be interpret as the part of overall input $x_t$ which is allocated to the final-output sector, i.e.
+sector $1$.} In addition, production function is augmented with (i) sector-specific productivity, $\Gamma^c_t$ and (ii) a positive spillover effect related to the diffusion of ICT capital in the whole economy, $k^i_t$.\footnote{Notice that differently to $k^i_{1,t}$, $k^i_t$ represents the total amount of ICT capital in the whole economy at time $t$.} Production of final output is undertaken in accordance with
+$$
+y^c_t = A^c_t \ (k^c_{1,t})^a \ (k^i_{1,t})^b \ (l_{1,t})^{1-a-b}
+$$
+$\Gamma^c_t k^i_{t} $
 

### 2018-07-09 Latex/Draft_Summer2018/Summer2018.tex
Description of the model

@@
 Both real GDP and real consumption have a significant impact response and reaches its peak approximately after $6$ years.
-Finally, the response of relative prices is negative and persistent as we have previously discussed.
+Thus, the response of relative prices is negative and persistent as we have previously discussed.
+Finally, even if to formally shown, ICT shocks explains $27$\% of TFP fluctuations over $10$-year horizon.
+Also this result, is completely in line with previous results presented in Table \ref{table:vardec} in Appendix \ref{section:vardec}.
 
@@
 
-\subsubsection*{Household}
+\subsubsection{Household}
 
-Consider an economy inhabitated by a representative agent whi maximizes the expect values of his lifetime utility as given by
-$$
+Consider an economy inhabited by a representative agent which maximizes the expect values of his lifetime utility as given by
+\begin{eqnarray}\label{equation:utilFunc}
 \E \Bigg[  \sum_{t=0}^{\infty} \beta^t U(c_t,l_t)  \Bigg]
-$$
+\end{eqnarray}
 with 
-$$
+\begin{eqnarray*}
 U(c_t,l_t) = \log(c_t) - \frac{1}{1+\eta} l_t^{1+\eta}
-$$
+\end{eqnarray*}
 where $c_t$ and $l_t$ represent consumption and labor at time $t$.
 
-\subsection*{Final-Good Sector}
+\subsection{Final-Good Sector}
 
-In each period, the production of final output $y^c_t$ requires the services of labor $l_{1,t}$, and two types of capital: hard capital, $k^c_{1,t}$ and ICT capital, $k^i_{1,t}$.\footnote{Notice that $x_{1,t}$ has to be interpret as the part of overall input $x_t$ which is allocated to the final-output sector, i.e.
-sector $1$.} In addition, production function is augmented with (i) sector-specific productivity, $\Gamma^c_t$ and (ii) a positive spillover effect related to the diffusion of ICT capital in the whole economy, $k^i_t$.\footnote{Notice that differently to $k^i_{1,t}$, $k^i_t$ represents the total amount of ICT capital in the whole economy at time $t$.} Production of final output is undertaken in accordance with
-$$
-y^c_t = A^c_t \ (k^c_{1,t})^a \ (k^i_{1,t})^b \ (l_{1,t})^{1-a-b}
-$$
-$\Gamma^c_t k^i_{t} $
+In each period, the production of final output $y^c_t$ requires the services of labor $l_{t}$, and two types of capital: hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$.
+In addition, production function is augmented with (i) neutral productivity common across sectors, (ii) sector-specific productivity, and (iii) a positive spillover effect related to the diffusion of ICT capital in the whole economy.
+Production of final output is undertaken in accordance with
+\begin{eqnarray}\label{equation:production_FINAL}
+y^c_t = A^c_t \ (k^c_{1,t})^a \ (k^i_{1,t})^b \ (l_{1,t})^{1-a-b}, \ \ 0 < a,b < 1
+\end{eqnarray}
+where total factor productivity is equal to $ A_t^c = \eta_t \ \theta^c_t \ (k^i_{t})^{\gamma} $.
+$\eta_t$ is the neutral technological component, $\theta^c_t$ is the sector-specific technological component, and $\gamma$ represents the parameter that governs the size of the spillover effect of ICT capital in the production function.
+Moreover, $k^c_{1,t}$ is the part of hard capital $k^c_t$ devoted to the final-good sector, i.e.
+sector 1.
+Similarly, $k^i_{1,t}$ and $l_{1,t}$ are the parts of ICT capital $k^i_t$ and labor $l_t$ devoted to the final-good sector, respectively.
+
+Final output $y^c_t$ can be used for two purposes: consumption, $c_t$ and investment in hard capital, $i^c_t$,
+\begin{eqnarray}\label{equation:resourceFINAL}
+y^c_t = c_t + i^c_t
+\end{eqnarray}
+Notice that elements in the equation above are normalized such that both output and investment are measured in units of consumption.
+Moreover, hard structures can be produced from final output on a one-to-one basis.
+The stock of hard capital evolves according to
+\begin{eqnarray}\label{equation:LOM_Hard}
+k^c_{t+1} = (1 - \delta^c) k^c_t + i^c_t
+\end{eqnarray}
+where $0 < \delta^c < 1$ represents the period depreciation of hard capital.
+
+\subsection{ICT-Good Sector}
+
+Similar to final-output production function, the creation of ICT output $y^i_t$ requires the services of labor $l_{t}$, and two types of capital: hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$.
+In addition, production function is augmented with (i) neutral productivity common across sectors, (ii) sector-specific productivity, and (iii) a positive spillover effect related to the diffusion of ICT capital in the whole economy.
+Production of ICT output is undertaken in accordance with
+\begin{eqnarray}\label{equation:productionICT}
+y^i_t = A^i_t \ (k^c_{2,t})^a \ (k^i_{2,t})^b \ (l_{2,t})^{1-a-b} , \ \ 0 < a,b < 1
+\end{eqnarray}
+where total factor productivity is equal to $ A_t^i = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma} $.
+$\eta_t$ is the same neutral technological component, $\theta^i_t$ is the ICT-specific technological component, and $\gamma$ represents the same parameter that governs the size of the spillover effect of ICT capital also in this production function.
+Similarly, $k^c_{2,t}$ is the part of hard capital $k^c_t$ devoted to the ICT-good sector, i.e.
+sector 2 and $k^i_{2,t}$ and $l_{2,t}$ are the parts of ICT capital $k^c_t$ and labor $l_t$ devoted to the ICT-good sector, respectively.
+
+ICT output $y^i_t$ can be only investment in ICT capital, $i^i_t$,
+\begin{eqnarray}\label{equation:resourceICT}
+y^i_t = i^i_t
+\end{eqnarray}
+Notice that elements in the equation above are normalized such that both output and investment are measured in the same units.
+Moreover, ICT goods can be produced from ICT output on a one-to-one basis.
+The stock of ICT capital evolves according to
+\begin{eqnarray}\label{equation:LOM_ICT}
+k^i_{t+1} = (1 - \delta^i) k^i_t + i^i_t
+\end{eqnarray}
+where $0 < \delta^i < 1$ represents the period depreciation of ICT capital.
+
+\subsection{Market Clearing across Sectors}
+
+Since we are assuming our economy to be closed, input demands must equal supplies,
+\begin{eqnarray}\label{equation:marketclearingHard}
+k^c_t = k^c_{1,t} + k^c_{2,t},
+\end{eqnarray}
+\begin{eqnarray}\label{equation:marketclearingICT}
+k^i_t = k^i_{1,t} + k^i_{2,t}, \ \ \text{and}
+\end{eqnarray}
+\begin{eqnarray}\label{equation:marketclearingLabor}
+l_t = l_{1,t} + l_{2,t}.
+\end{eqnarray}
+Taking as given Equations \ref{equation:production_FINAL}-\ref{equation:marketclearingLabor} and assuming that factor markets are perfective competitive, representative household maximizes intertemporal utility function under the following constraint,
+\begin{eqnarray}\label{equation:resourceHH}
+	c_t + k^c_{t+1} +p_t k^i_{t+1} = \bigg( 1 - \delta^c + r^c_t \bigg) k^c_t + \bigg( 1 - \delta^i + \frac{r^i_t}{p_t} \bigg) p_t k^i_t + w_t l_t	
+\end{eqnarray}
+where $p_t$ represents the price of ICT capital expressed in consumption units.
+Since price of consumption is normalized to be one then $p_t$ also represents the relative price between final output and ICT output.
+
+\subsection{Competitive Equilibrium}
+
+Competitive equilibrium is represented by (i) household's first order conditions with respect to consumption $c_t$, labor $l_t$, hard capital $k^c_t$, ICT capital $k^i_t$, (ii) final-good producers' first order conditions with respect to $k^c_{1,t}$, $k^i_{1,t}$, and $l_{1,t}$, (iii) ICT-good producers' first order conditions with respect to $k^c_{2,t}$, $k^i_{2,t}$, and $l_{2,t}$, (iv) definition of production functions \ref{equation:production_FINAL} and \ref{equation:productionICT}, (v) low of motion of hard and ICT capital \ref{equation:LOM_Hard} and \ref{equation:LOM_ICT}, (vi) sector-specific resource constraints \ref{equation:marketclearingHard} and \ref{equation:marketclearingICT}, and intrasectoral resource constraints \ref{equation:marketclearingHard}, \ref{equation:marketclearingICT}, and \ref{equation:marketclearingLabor}.
 

### 2018-07-10 Latex/Draft_Summer2018/Summer2018.tex
Few more writing

@@
 
-\subsection{Final-Good Sector}
+\subsection{Final-Good Producers}
 
-In each period, the production of final output $y^c_t$ requires the services of labor $l_{t}$, and two types of capital: hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$.
+Instead of working with the aggregate production function, assume that the production side of the final-good sector consist of a set $[0,1]$ of firms.
+In each period, final-good firm $j \in [0,1]$ produces $y^c_t(j)$ using the services of labor $l_{t}$, and two types of capital: hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$.
 In addition, production function is augmented with (i) neutral productivity common across sectors, (ii) sector-specific productivity, and (iii) a positive spillover effect related to the diffusion of ICT capital in the whole economy.
-Production of final output is undertaken in accordance with
+Production of final output of firm $j$ is undertaken in accordance with
 \begin{eqnarray}\label{equation:production_FINAL}
-y^c_t = A^c_t \ (k^c_{1,t})^a \ (k^i_{1,t})^b \ (l_{1,t})^{1-a-b}, \ \ 0 < a,b < 1
+y^c_t(j) = A^c_t \ \big( k^c_{t}(j) \big)^a \ \big( k^i_{t}(j) \big)^b \ \big( l_{t}(j) \big)^{1-a-b}, \ \ 0 < a,b < 1
 \end{eqnarray}
@@
 $\eta_t$ is the neutral technological component, $\theta^c_t$ is the sector-specific technological component, and $\gamma$ represents the parameter that governs the size of the spillover effect of ICT capital in the production function.
-Moreover, $k^c_{1,t}$ is the part of hard capital $k^c_t$ devoted to the final-good sector, i.e.
+Moreover, $k^c_{t}(j)$ is the part of hard capital $k^c_t$ used by firm $j$ in oder to produce final-good output.
+Similarly, $k^i_{t}(j)$ and $l_{t}(j)$ are the parts of ICT capital $k^i_t$ and labor $l_t$ used by firm $j$ in oder to produce final-good output, respectively.
+
+Since all the final-good producers are identical ex ante and ex post, the following conditions hold,
+\begin{eqnarray}\label{equation:aggregation_hard_final}
+\int_0^1 k^c_{t}(j) dj = k^c_{1,t},
+\end{eqnarray}
+\begin{eqnarray}\label{equation:aggregation_ICT_final}
+\int_0^1 k^i_{t}(j) dj = k^i_{1,t}, 
+\end{eqnarray}
+\begin{eqnarray}\label{equation:aggregation_labor_final}
+\int_0^1 l_{t}(j) dj = l_{1,t},
+\end{eqnarray}
+where $k^c_{1,t}$ is the aggregate part of hard capital $k^c_t$ devoted to the final-sector, i.e.
 sector 1.
-Similarly, $k^i_{1,t}$ and $l_{1,t}$ are the parts of ICT capital $k^i_t$ and labor $l_t$ devoted to the final-good sector, respectively.
+Moreover, $k^i_{1,t}$ and $l_{1,t}$ are the aggregate parts of ICT capital $k^i_{t}$ and labor $l_{t}$ devoted to the final-good sector, respectively.
 
-Final output $y^c_t$ can be used for two purposes: consumption, $c_t$ and investment in hard capital, $i^c_t$,
+Aggregate final-good output is defined as
+\begin{eqnarray}\label{equation:production_FINAL_aggregate}
+y^c_t = A^c_t \ ( k^c_{1,t} )^a \ ( k^i_{1,t} )^b \ ( l_{1,t} )^{1-a-b}, \ \ 0 < a,b < 1
+\end{eqnarray}
+and it can be used for two purposes: consumption, $c_t$ and investment in hard capital, $i^c_t$,
 \begin{eqnarray}\label{equation:resourceFINAL}
@@
 
-Similar to final-output production function, the creation of ICT output $y^i_t$ requires the services of labor $l_{t}$, and two types of capital: hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$.
+Instead of working with the aggregate production function, assume that the production side of the ICT-good sector consist of a set $[0,1]$ of firms.
+Similar to final-output production function, ICT-good firm $q \in [0,1]$ produces $y^c_t(q)$ using the services of labor $l_{t}$, and two types of capital: hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$.
 In addition, production function is augmented with (i) neutral productivity common across sectors, (ii) sector-specific productivity, and (iii) a positive spillover effect related to the diffusion of ICT capital in the whole economy.
-Production of ICT output is undertaken in accordance with
+Production of ICT output of firm $q$ is undertaken in accordance with
 \begin{eqnarray}\label{equation:productionICT}
-y^i_t = A^i_t \ (k^c_{2,t})^a \ (k^i_{2,t})^b \ (l_{2,t})^{1-a-b} , \ \ 0 < a,b < 1
+y^c_t(q) = A^c_t \ \big( k^c_{t}(q) \big)^a \ \big( k^i_{t}(q) \big)^b \ \big( l_{t}(q) \big)^{1-a-b}, \ \ 0 < a,b < 1
 \end{eqnarray}
-where total factor productivity is equal to $ A_t^i = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma} $.
-$\eta_t$ is the same neutral technological component, $\theta^i_t$ is the ICT-specific technological component, and $\gamma$ represents the same parameter that governs the size of the spillover effect of ICT capital also in this production function.
-Similarly, $k^c_{2,t}$ is the part of hard capital $k^c_t$ devoted to the ICT-good sector, i.e.
-sector 2 and $k^i_{2,t}$ and $l_{2,t}$ are the parts of ICT capital $k^c_t$ and labor $l_t$ devoted to the ICT-good sector, respectively.
+where total factor productivity is equal to $ A_t^c = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma} $.
+$\eta_t$ is the same neutral technological component, $\theta^i_t$ is the sector-specific technological component, and $\gamma$ represents the same parameter that governs the size of the spillover effect of ICT capital in the production function.
+Moreover, $k^c_{t}(q)$ is the part of hard capital $k^c_t$ used by firm $q$ in oder to produce ICT goods.
+Similarly, $k^i_{t}(q)$ and $l_{t}(q)$ are the parts of ICT capital $k^i_t$ and labor $l_t$ used by firm $q$ in oder to produce ICT goods, respectively.
 
-ICT output $y^i_t$ can be only investment in ICT capital, $i^i_t$,
+Similarly, since all the final-good producers are identical ex ante and ex post, the following conditions hold,
+\begin{eqnarray}\label{equation:aggregation_hard_ICTsec}
+\int_0^1 k^c_{t}(q) dq = k^c_{2,t},
+\end{eqnarray}
+\begin{eqnarray}\label{equation:aggregation_ICT_ICTsec}
+\int_0^1 k^i_{t}(q) dq = k^i_{2,t}, 
+\end{eqnarray}
+\begin{eqnarray}\label{equation:aggregation_labor_ICTsec}
+\int_0^1 l_{t}(q) dq = l_{2,t},
+\end{eqnarray}
+where $k^c_{2,t}$ is the aggregate part of hard capital $k^c_t$ devoted to the ICT-sector, i.e.
+sector 2.
+Moreover, $k^i_{2,t}$ and $l_{2,t}$ are the aggregate parts of ICT capital $k^i_{t}$ and labor $l_{t}$ devoted to the ICT-good sector, respectively.
+
+Aggregate ICT-good output is defined as
+\begin{eqnarray}\label{equation:production_ICT_aggregate}
+	y^i_t = A^c_t \ ( k^c_{2,t} )^a \ ( k^i_{2,t} )^b \ ( l_{2,t} )^{1-a-b}, \ \ 0 < a,b < 1
+\end{eqnarray}
+and it can be only investment in ICT capital, $i^i_t$,
 \begin{eqnarray}\label{equation:resourceICT}
@@
 \begin{eqnarray}\label{equation:marketclearingICT}
-k^i_t = k^i_{1,t} + k^i_{2,t}, \ \ \text{and}
+k^i_t = k^i_{1,t} + k^i_{2,t}, 
 \end{eqnarray}
@@
 
-\subsection{Competitive Equilibrium}
+\subsection{Competitive Equilibrium and Solution Method}
 
-Competitive equilibrium is represented by (i) household's first order conditions with respect to consumption $c_t$, labor $l_t$, hard capital $k^c_t$, ICT capital $k^i_t$, (ii) final-good producers' first order conditions with respect to $k^c_{1,t}$, $k^i_{1,t}$, and $l_{1,t}$, (iii) ICT-good producers' first order conditions with respect to $k^c_{2,t}$, $k^i_{2,t}$, and $l_{2,t}$, (iv) definition of production functions \ref{equation:production_FINAL} and \ref{equation:productionICT}, (v) low of motion of hard and ICT capital \ref{equation:LOM_Hard} and \ref{equation:LOM_ICT}, (vi) sector-specific resource constraints \ref{equation:marketclearingHard} and \ref{equation:marketclearingICT}, and intrasectoral resource constraints \ref{equation:marketclearingHard}, \ref{equation:marketclearingICT}, and \ref{equation:marketclearingLabor}.
+Competitive equilibrium is represented by (i) Equations \ref{equation:utilFunc}-\ref{equation:marketclearingLabor}, (ii) household's first order conditions with respect to consumption $c_t$, labor $l_t$, hard capital $k^c_t$, ICT capital $k^i_t$, (iii) final-good producers' first order conditions with respect to $k^c_{1,t}$, $k^i_{1,t}$, and $l_{1,t}$, and (iv) ICT-good producers' first order conditions with respect to $k^c_{2,t}$, $k^i_{2,t}$, and $l_{2,t}$.
 

### 2018-07-10 Latex/Draft_Summer2018/Summer2018.tex
Found a typo

@@
 
-Competitive equilibrium is represented by (i) Equations \ref{equation:utilFunc}-\ref{equation:marketclearingLabor}, (ii) household's first order conditions with respect to consumption $c_t$, labor $l_t$, hard capital $k^c_t$, ICT capital $k^i_t$, (iii) final-good producers' first order conditions with respect to $k^c_{1,t}$, $k^i_{1,t}$, and $l_{1,t}$, and (iv) ICT-good producers' first order conditions with respect to $k^c_{2,t}$, $k^i_{2,t}$, and $l_{2,t}$.
+Competitive equilibrium is represented by (i) Equations \ref{equation:utilFunc}-\ref{equation:marketclearingLabor}, (ii) household's first order conditions with respect to consumption $c_t$, labor $l_t$, hard capital $k^c_t$, ICT capital $k^i_t$, (iii) final-good producers' first order conditions with respect to $k^c_{t}(j)$, $k^i_{t}(j)$, and $l_{t}(j)$, and (iv) ICT-good producers' first order conditions with respect to $k^c_{t}(q)$, $k^i_{t}(q)$, and $l_{t}(q)$.
 

### 2018-07-11 Latex/Draft_Summer2018/Summer2018.tex
attempt to do a serious calibration

@@
 \begin{eqnarray*}
-U(c_t,l_t) = \log(c_t) - \frac{1}{1+\eta} l_t^{1+\eta}
+U(c_t,l_t) = \log(c_t) - \frac{1}{1+\frac{1}{\chi}} l_t^{1+\frac{1}{\chi}}
 \end{eqnarray*}
@@
 \end{eqnarray}
-where total factor productivity is equal to $ A_t^c = \eta_t \ \theta^c_t \ (k^i_{t})^{\gamma} $.
-$\eta_t$ is the neutral technological component, $\theta^c_t$ is the sector-specific technological component, and $\gamma$ represents the parameter that governs the size of the spillover effect of ICT capital in the production function.
+where total factor productivity is equal to $ A_t^c = \eta_t \ \theta^c_t \ (k^i_{t})^{\gamma} $. $\eta_t$ is the neutral technological component which moves along the following deterministic trend
+\begin{eqnarray}\label{equation:neutral_tech_process}
+\eta_t = (\Gamma^{\eta})^t e^{\varepsilon_t},  
+\end{eqnarray} 
+\begin{eqnarray}\label{equation:neutral_tech_shock}
+ \varepsilon_t = \rho_{\nu} \varepsilon_{t-1} + \nu_t
+\end{eqnarray} 
+where $\rho_{\nu} \in (0,1)$ and $\nu_t \sim N(0,\sigma_{\nu})$ represents a neutral technology shock.
+$\theta^c_t$ is the sector-specific technological component,  which moves along the following deterministic trend
+\begin{eqnarray}
+\theta_t^c = (\Gamma^{c})^t.
+\end{eqnarray} 
+Then, $\gamma$ represents the parameter that governs the size of the spillover effect of ICT capital in the production function.
 Moreover, $k^c_{t}(j)$ is the part of hard capital $k^c_t$ used by firm $j$ in oder to produce final-good output.
@@
 where total factor productivity is equal to $ A_t^c = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma} $.
-$\eta_t$ is the same neutral technological component, $\theta^i_t$ is the sector-specific technological component, and $\gamma$ represents the same parameter that governs the size of the spillover effect of ICT capital in the production function.
+$\eta_t$ is the same neutral technological component which follows \ref{equation:neutral_tech_process} and \ref{equation:neutral_tech_shock}, $\theta^i_t$ is the sector-specific technological component which moves along the following deterministic trend
+\begin{eqnarray}\label{equation:ICT_tech_process}
+\theta^i_t = (\Gamma^{i})^t e^{\zeta_t},  
+\end{eqnarray} 
+\begin{eqnarray}\label{equation:ICT_tech_shock}
+\zeta_t = \rho_{\iota} \zeta_{t-1} + \iota_t
+\end{eqnarray} 
+where $\rho_{\iota} \in (0,1)$ and $\iota_t \sim N(0,\sigma_{\iota})$ represents an ICT technology shock.
+Then, $\gamma$ represents the same parameter that governs the size of the spillover effect of ICT capital in the production function.
 Moreover, $k^c_{t}(q)$ is the part of hard capital $k^c_t$ used by firm $q$ in oder to produce ICT goods.
@@
 
+In order to simulate responses to (i) neutral technology shocks, $\nu_t$ and (ii) ICT shocks, $\iota_t$ we employ a standard first-order approximation of the log-transformation of the system around the detrended (stationarized) steady state.
+In order to stationarized the system we use results firstly presented by \cite{greenwood1997long} where they formally show the balance-growth path of the two sectors under the assumption that one sector is moving faster than the other.
+In our case, results are going to be slightly different since we need to take into account the additional effect provided by the spillover.\footnote{The stationarized version of the steady state is available on request.} Results are derived mostly using the code provide by Stephanie Schmitt-Grohe and Martin Uribe available on their websites.\footnote{Code to replicate our results is available on request.}
+
+\section{Model Assessment}
+
+In this section we describes the parameter values and test the empirical performance of the model.
+Following \cite{christiano2005nominal}, we partition those values into two groups.
+We calibrate parameters of the first group using steady-state relations or results from previous works.
+We estimate the second group of parameters by minimizing the distance between the model-implied impulse responses and the empirical results presented in \ref{section:mainSpec}.
+In particular, the second group focuses on parameters specifically related to the effect of ICT investment on future TFP: (i) the size of the spillover effect of ICT capital on productivity $\gamma$, (ii) the standard deviation $\sigma_{\iota}$ and (iii) persistence $\rho_{\iota}$ of ICT shocks.
+
+\subsection{Parameterization}\label{section:parameterization}
+
+We calibrate the model at a quarterly frequency.
+We set the discount factor $\beta$ to $0.97^{\frac{1}{4}}$ to match the average yield of $3$\% of the 3-month Treasury bill using data from 1989:Q1 to 2017:Q1.
+Moreover, we set ICT share $b$ equal to $0.0310$ following \cite{oulton2012long} and hard capital share $a$ equal to $0.3$.
+Moreover, adapting \cite{oulton2012long} accordingly to our additional assumptions, we derive steady state growth rates of final-sector technology $\Gamma^c$ and ICT-sector technology $\Gamma^i$ solving the system,
+\begin{equation}\label{equation:system_param}
+\begin{cases}
+\E \big( \frac{p_t}{p_{t-1}} \big) = \frac{\Gamma^c}{\Gamma^i} \\
+\E \big( \frac{c_t}{c_{t-1}} \big) = (\Gamma^c)^{\frac{1-b-\gamma}{1-a-b-\gamma}}  (\Gamma^i)^{\frac{b+\gamma}{1-a-b-\gamma}}
+\end{cases}
+\end{equation}
+where $\E[p_t/p_{t-1}]$ and $\E[c_t/c_{t-1}]$ are derived from the simple mean of their empirical related values using quarterly data from 1989:Q1 to 2017:Q1.
+Estimation implies $\Gamma^c = 1.0034$ and $\Gamma^i = 1.0160$.\footnote{Notice that the value of $\gamma$ is unknown at this step since it is going to be evaluated using impulse-response matching.
+This implies that the solution for $\Gamma^c$, $\Gamma^i$, and $\gamma$ should be a fixed point where given $\gamma^*$ we obtain $(\Gamma^i)^*$ and $(\Gamma^c)^*$ solving \ref{equation:system_param}.
+Given $(\Gamma^i)^*$ and $(\Gamma^c)^*$ we obtain $\gamma^*$ by minimizing the impulse-response matching.
+At this step we are simply solving the system for $\gamma$ equal to zero but a more refine solution will be provided in future.} Finally, to avoid an over-identification problem we set the growth rate of sector-neutral technology $\Gamma^{\eta}$ equal to one.
+
+In addition, we set the frisch elasticity of labor supply $\chi$ to be equal to $1$.
+Moreover, following Bureau fo Economic Analysis (BEA) depreciation estimates, we set the quarterly depreciation rates for hard capital $\delta^c$ to be equal to $0.0206$ in order to match an annual depreciation rate of $0.08$.
+Similarly, according to BEA depreciation estimates (i) communication equipments and (ii) computer and electronic products depreciate at an annual rate of $0.15$ and $0.14$ respectively.
+Thus, we set the quarterly depreciation rates for ICT capital $\delta^i$ to be equal to $0.0398$ in order to match the highest of the two values.
+
+\subsection{Impulse-Response Matching}\label{section:IRmatching}
+
+\subsection{Interpretation of the Results}\label{section:Interpretation_theory}
+
 %%%%%%%%%%%%%%%%%%%%               MODEL                 %%%%%%%%%%%%%%%%%% 
@@
 \section{Conclusion}\label{section:conclusions}
-hjklbhjkl
 

### 2018-07-11 Code/oulton2010/evaluate_gamC_gamI.m

@@ -1,0 +1,17 @@
+clear 
+close all
+
+b = 0.05;
+a = 1/3 - b;
+gam = 0; 
+gc_mean = 0.002942;
+gp_mean = - 0.0126;
+w1 = (1-a-gam)/(1-a-b-gam);
+w2 = (b+gam)/(1-a-b-gam);
+
+
+gamC = (gc_mean - w2*gp_mean)/(w1+w2);
+gamI = gamC - gp_mean;
+
+deltyear = 0.15;
+deltquarter= 1 - (1 - deltyear)^(1/4)

### 2018-07-12 Latex/Draft_Summer2018/Summer2018.tex
editing the draft

@@
 As a first-pass test, % cite Barsky Basu Lee and Forni or whatevs
-we check if our results are robust once we remove all the forward looking variables whose fluctuations may be unrelated to sector-specific technological changes: consumption and output.
-Technically speaking, consumption and output may Granger-cause future TFP for reasons which are orthogonal to ICT shocks.
+we check if our results are robust once we remove all the forward-looking variables whose fluctuations may be unrelated to sector-specific technological changes: consumption and output.
+Technically speaking, consumption and output may Granger-cause movements in future TFP for reasons which are orthogonal to ICT shocks.
 For example, the forward-looking nature of consumption may provide the VAR with information regarding future changes in TFP not related to an ICT shock, which our identification strategy is not able to filter out.
+
 Our second test is running a VAR in which we identify both ICT shocks and news shocks.
@@
 
-In this part of the paper, we employ a first-pass test where we attempt to show that our ICT shock is not confounded with future signals of TFP unrelated to the ICT sector.
+In this part of the paper, we employ a first-pass test of whether our ICT shock may be confounded with future signals of TFP unrelated to the ICT sector.
 
 As discussed by \cite{sims2012news}, \cite{forni2014sufficient}, and \cite{barsky2015whither} the presence of forward-looking variables in the VAR is a necessary condition to correctly identify a news shock.
-In particular, since the univariate TFP process cannot predict future TFP,\footnote{It is well-accepted that TFP growth can be approximated as a white noise.} a news shock can be identified if there are variables that granger-cause TFP inside the VAR.
+In particular, since the univariate TFP process cannot predict its own future values,\footnote{It is well-accepted that TFP growth can be approximated as a white noise process, or, equivalently, that the TFP level process is a random walk.} a news shock can only be identified if there are variables that Granger-cause TFP inside the VAR.
 For example, \cite{beaudry2006stock} use current movements in stock prices to predict future productivity, but also contemporary fluctuations in consumption, hours, investment, may implicitly reflect information regarding future technical change.
 
-Thus, as a simple test we propose to redo the exercise described in Section \ref{section:mainSpec} without two forward-looking macroeconomic variables not directly related with the ICT sector: consumption and output.\footnote{Notice that output implicitly reflect the behavior of hours and investment once we control for consumption.} If we are actually confounding news shocks with our ICT shock series then we would expect to see some differences in this second estimate.
-In other words, once our VAR is deprived by a source of information useful to recover a news shock, then the confounded part should either decreases or cancels out.
+Thus, as a simple test we redo the exercise described in Section \ref{section:mainSpec}, omitting the two forward-looking macroeconomic variables not directly related with the ICT sector: consumption and output.\footnote{Notice that output implicitly reflects the behavior of hours and investment once we control for consumption.} If we are actually confounding news shocks with our ICT shock series then we would expect to see some differences in this second estimate, because absent the two forward-looking variables, our VAR is deprived of a source of information useful to recover a news shock and should thus no longer be able to capture it appropriately.
 
-As hinted above, in this section we estimate the following 3-dimensional system
+Without consumption and output, we thus estimate the following three-dimensional system
 \begin{equation}\label{eq:noForVariables}
@@
 \end{equation}
-where  $TFP_t$, $ICTI_{t}$, and $RP_t$ have the same meaning and transformation as in System \ref{eq:mainSpecification}.
-As before, dataset is quarterly and covers the U.S.
+where  $TFP_t$, $ICTI_{t}$, and $RP_t$ are defined and treated as in System \ref{eq:mainSpecification}.
+As before, the dataset is quarterly and covers the U.S.
 economy from 1989:Q1 to 2017:Q1.
-Finally, according to the Bayesian Information Criterion (BIC), we choose one lag.\footnote{The Hannan-Quinn Criterion (HQ) suggests to use two lags.
-Results remains consistent following this second criterion.} Using the same identification strategy presented in \ref{section:empiricalstrategy_simple}, we recover a series of ICT shocks which is correlated at $95$\% with the one estimated in 5-dimensional system.
-In particular, in Appendix \ref{section:removing_FL_Var}, Figure \ref{fig:shockSeries_removing} shows ICT shock series for both the 3-dimensional system and 5-dimensional one.
-In line with the correlation coefficient, the two series almost overlap each others suggesting that our initial result is not driven by the forward-looking power of consumption and output on TFP.
+Finally, analogously to before, we follow the Bayesian Information Criterion (BIC) to choose one lag.
+Using the same identification strategy presented in \ref{section:empiricalstrategy_simple}, we recover a series of ICT shocks.
+The newly recovered series is correlated at $95$\% with the one estimated in five-dimensional system, indicating that our main specification is not contaminated by news.
+Figure \ref{fig:shockSeries_removing} in Appendix \ref{section:removing_FL_Var} shows the ICT shock series for both the three-dimensional system and the five-dimensional one.
+In line with the very high correlation coefficient, the two series overlap perfectly, suggesting that both procedures recover the same structural shock series.
+Thus, our first-pass test indicates that our initial result is not driven by the forward-looking power of consumption and output on TFP.
 
-However, although this result is encouraging, this first-pass test has obviously a weak power because the jump of ICTI on impact may be triggered by future exogenous signal of TFP.
-In this case, ICTI would be itself the source to granger-cause TFP and our ICT shock would be upward biased by news.
-To amend this deeper concern, we then need to employ a more complicated strategy presented in the next section.
+However, although this result is encouraging, the first-pass test has weak power because the jump of ICTI on impact may itself be triggered by exogenous signals on future TFP.
+In this case, ICTI would be itself the source to Granger-cause TFP and our ICT shock would be upward biased by news.
+To address this deeper concern, we proceed to employ a more complicated strategy aimed at directly capturing, and filtering out news.
 

### 2018-07-12 Latex/Draft_Summer2018/Summer2018.tex
more editing

@@
 
-In this part, we present an alternative procedure to rule out the presence of news from our empirical result.
+In this part, we present an alternative procedure to rule out the presence of news from our recovered ICT shock.
 In this second test we run a VAR where we identify both ICT shocks and news shocks.
-We apply a sequential identification where we first identify a news shocks in the spirit of \cite{barsky2011news}, and subsequently we identify ICT shocks using our original identification strategy.
-Here we are seriously attempting to filter out future signals unrelated to current ICT shocks.
+In contrast to our first-pass test, this test aims to directly identify and filter out future signals unrelated to current ICT shocks.
+
+We apply a sequential identification which involves first identifying a news shock in the spirit of \cite{barsky2011news}, and subsequently identifying the ICT shock using our original strategy.
 Specifically, in the first step the news shock is identified as the shock orthogonal to current TFP that best explains its future movements.
@@
 
-However, we need to clarify that in order to correctly employ this procedure, we need to take care of a second issue.
-As correctly mentioned by \cite{barsky2011news}, \textit{``A general objection to our emprical approach would be that a number of structural shocks, which are not really news in the sense defined in the literature, might affect a measure of TFP in the future without impacting it immediately.
+However, in order to correctly employ this procedure, we need to take care of a second issue. As \cite{barsky2011news} warns,
+
+\begin{quote} A general objection to our emprical approach would be that a number of structural shocks, which are not really news in the sense defined in the literature, might affect a measure of TFP in the future without impacting it immediately.
 Among these shocks might be research and development shocks, investment specific shocks, and reallocative shocks.
-Our identification (and any other existing VAR identifications) would obviously confound any true news shock with these shocks.''} In other words, by naively employing the procedure presented above, any ICT shocks would be fully captured as a news shock since it is orthogonal to current TFP and explains its future movements.
+Our identification (and any other existing VAR identifications) would obviously confound any true news shock with these shocks.
+%add p.
+number
+\end{quote}
 
-Thus, in order to avoid the opposite mistake, namely confounding ICT shocks into news shocks, we need to augment the first step with a sort of control ad hoc for our case.
-To formally discipline this additional identification assumption we need to design a two-sector model in the spirit of \cite{greenwood1997long}.\footnote{In particular, the model presented in Section \ref{section:theory} is closely related to \cite{oulton2007investment}.} In particular, we will mostly rely on the effect of an sector-neutral technology shock on relative prices to constraint the first step in order to avoid to capture an ICT shock into a news shock.
+In other words, by naively employing the procedure presented above, any ICT shock would be interpreted as a news shock since it is orthogonal to current TFP and explains its future movements.
+Put plainly, to get the identification of the two shocks right, we need to add a restriction that is able to distinguish between them.
+
+Thus, to avoid confounding ICT shocks with news shocks, we need to augment the first step with an extra restriction.
+The restriction we will use here is derived from a two-sector structural model in the tradition of \cite{greenwood1997long}.\footnote{While our model belongs to the class of models along the lines of \cite{greenwood1997long}, our exposition is closer to that of \cite{oulton2007investment}.
+We discuss this choice in detail in Section \ref{section:theory}.} Here, we refrain from presenting the model in its entirety; the reader is referred to Section \ref{section:theory}.
+Instead, Proposition \ref{prop:priceRestriction} presents the key property of the model that gives rise to our identification assumption.
 
 \begin{prop}\label{prop:priceRestriction}
-In a two-sector economy, if both production functions are identical then any economy-wide productivity shocks do not affect relative prices between the two sectors.
+In a two-sector economy, if both production functions are identical, then any economy-wide productivity shocks do not affect relative prices between the two sectors.
 \end{prop}
@@
 
-Proposition \ref{prop:priceRestriction} implies that a future sector-neutral technological change (the so-called news shock) never affects relative prices between sectors.
-Obviously, this statement is correct under the extreme assumptions that (i) the shock is expected to have the same impact on the two sectors and (ii) production functions are identical to each others.
-If those assumptions hold in the data, then the correct additional restriction would be to shut down to zero the impulse response of relative prices to a news shock.
+Proposition \ref{prop:priceRestriction} implies that an anticipated future sector-neutral technological change (the so-called news shock) never affects relative prices between sectors.
+Obviously, this statement is correct under the extreme assumptions that (i) the shock is expected to have the same impact on the two sectors and (ii) production functions are identical.
+If those assumptions hold in the data, then the correct additional restriction would be to  restrict the impulse response of relative prices to a news shock to hard zero at all horizons.
 However, this restriction would obviously penalize the identification of news shocks since it is unlikely that assumptions (i) and (ii) perfectly hold in the data.
-We then opt for a more moderate strategy where we basically impose that the response of relative prices to a news shock should be relatively much smaller than the response observed by an ICT shock.
-Practically speaking, we arbitrarily set the impulse response of relative prices to be zero on some specific horizon rather than always.
-In particular, although results are robust to different horizon restrictions, our favorite specification is the one which set relative prices to have zero effect in the first three periods.
+We therefore opt for a more moderate strategy where we impose that the response of relative prices to a news shock should be smaller than the response following an ICT shock.
+Practically speaking, we arbitrarily set the impulse response of relative prices to news to be zero on some specific horizons rather than at all horizons.
+While results are robust to different horizon restrictions, our favorite specification is the one which sets relative prices to have zero response in the first three periods.
 
@@
 
-In this case, our specification is the following 6-variable VAR,
+Motivated by Proposition \ref{prop:priceRestriction}, we augment our initial VAR system with stock prices, SP.
+As discussed above, SP is added in order to provide an additional forward-looking variable to the system.\footnote{The presence of forward-looking variables in the VAR is a necessary condition to correctly identify a news shock.
+For more details on this discussion, see \cite{sims2012news}, \cite{forni2014sufficient}, and \cite{barsky2015whither}.} Thus, our current specification is the following six-variable VAR,
 \begin{equation}\label{eq:newsSpecification}
@@
 \end{equation}
-where $TFP_t$, $ICTI_t$, $GDP_t$, $C_t$, and $RP_t$ have the same meaning and transformation as in System \ref{eq:mainSpecification}.
-Moreover, $SP_t$ represents the log-transformation of Standard \& Poor's 500 stock prices added to provide an additional forward-looking variable to the system.\footnote{As mentioned before, following \cite{sims2012news}, \cite{forni2014sufficient}, and \cite{barsky2015whither} the presence of forward-looking variables in the VAR is a necessary condition to correctly identify a news shock.} As before, dataset is quarterly and covers the U.S.
+where $TFP_t$, $ICTI_t$, $GDP_t$, $C_t$, and $RP_t$ are defined and treated identically to System \ref{eq:mainSpecification}.
+$SP_t$ represents the log-transformation of Standard \& Poor's 500 stock price index.
+As before, dataset is quarterly and covers the U.S.
 economy from 1989:Q1 to 2017:Q1 and following the BIC and HQ criteria we opt for one lag.
@@
 
-Using a similar notation in Section \ref{section:empiricalstrategy_simple}, assume for notation simplicity that $B(L) = B$ allows only of one lag.
+Using the notation of Section \ref{section:empiricalstrategy_simple}, assume for simplicity that $B(L) = B$ allows only for one lag.
 Define the impulse response of variable $i$ to the identified shock $j$ at time $t$ as,\footnote{We also suppress the constant to simplify the notation.
-Identification strategy can obviously be applied for $B(L)$ allowing for more than one lag and with the constant.}
+Of course, our identification strategy can be applied for $B(L)$ allowing for more than one lag and with the constant.}
 $$
@@
 $$
-and its variance decomposition up to time $h$
+and its variance decomposition up to time $h$ as
 $$
@@
 $$
-Given the following notation and let notice that TFP is ordered first and ICTI second, the identification strategy can be summarized as follows,
+Given this and recalling that TFP is ordered first, ICTI second and RP sixth, the identification strategy can be summarized as follows,
 
@@
 where the first constraint represents the zero-impact restriction of news on TFP.
-Moreover, the second constraint represents the arbitrary restriction to have a response of relative prices to news relatively small.\footnote{Our identification strategy is robust over different restrictions to relative prices.
+The second constraint is the restriction derived from Proposition \ref{prop:priceRestriction} to have the response of relative prices to news relatively small.\footnote{Our identification strategy is robust over different restrictions to relative prices.
 Results hold even if we set the zero restriction on other horizons.} Finally, the last constraint imposes that $\gamma_{news}$ should be a column derived from the orthogonal matrix $D$.
@@
 $$
-where the first constraint represents the zero-impact restriction of news on TFP and the last constraint imposes that both $\gamma_{news}$ and $\gamma_{ICT}$ should be two different columns derived from the orthogonal matrix $D$.
+where the first constraint represents the zero-impact restriction of ICT on TFP and the last constraint imposes that both $\gamma_{news}$ and $\gamma_{ICT}$ should be two different columns derived from the orthogonal matrix $D$.
 
@@
 
-Figures \ref{fig:2stepIRF_first} and \ref{fig:2stepIRF_second} in Appendix \ref{section:IRF_2step} shows estimated impulse responses to both news and ICT shocks.
-In particular, Figure \ref{fig:2stepIRF_first} shows dynamic responses of TFP, stock prices, and ICT investment to both shocks and Figure \ref{fig:2stepIRF_second} shows dynamic responses of GDP, consumption and relative prices to both shocks as well.
-The shaded gray areas are the $90$\% and $95$\% confidence bands from a bias-corrected bootstrap procedure of \cite{kilian1998small} using 2000 simulations.
+Figures \ref{fig:2stepIRF_first} and \ref{fig:2stepIRF_second} in Appendix \ref{section:IRF_2step} show estimated impulse responses to both news and ICT shocks.
+Figure \ref{fig:2stepIRF_first} focuses on the responses of TFP, stock prices, and ICT investment , while Figure \ref{fig:2stepIRF_second} shows the responses of GDP, consumption and relative prices.
+The shaded gray areas are the $90$\% and $95$\% confidence bands from the bias-corrected bootstrap procedure of \cite{kilian1998small} using 2000 simulations.
 
-Dynamic responses to an ICT shock are almost identical to the ones presented in the main identification in Section \ref{section:mainSpec}.
-After few lags, TFP displays a positive and significant effect and reaches its peak of $1.2$\% after $6$ years.
-Interestingly, stock prices jump on impact and the effect remain significant over the medium run.
-Real ICT investment has a large and positive impact response and it slowly starts to decay remaining significant for a long period of time.
-Both real GDP and real consumption have a significant impact response and reaches its peak approximately after $6$ years.
-Thus, the response of relative prices is negative and persistent as we have previously discussed.
-Finally, even if to formally shown, ICT shocks explains $27$\% of TFP fluctuations over $10$-year horizon.
-Also this result, is completely in line with previous results presented in Table \ref{table:vardec} in Appendix \ref{section:vardec}.
+A first comforting indication is that the responses to an ICT shock are almost identical to the ones from our main identification of Section \ref{section:mainSpec}.
+After few lags, TFP displays a positive and significant response and reaches its peak of $1.2$\% after $6$ years.
+Interestingly, stock prices jump on impact and the effect remains significant over the medium run.
+Real ICT investment has a large and positive impact response and slowly starts to decay, remaining significant for a long period of time.
+Both real GDP and real consumption have a significant impact response and reach their peak approximately after $6$ years.
+The response of relative prices is negative and persistent as we have previously discussed.
+Finally, the ICT shocks explains $27$\% of TFP fluctuations over a $10$-year horizon.
+Also this result is completely in line with the previous results presented in Table \ref{table:vardec} in Appendix \ref{section:vardec}.
 
-In addition, we show dynamic responses to a news shock to confirm the reliability of our identification strategy.
-Constraining fluctuations of relative prices to news does not qualitatively affect what has been already found in the literature.
-In line with \cite{barsky2011news}, it takes more that 2 years for TFP to display a positive, significant and strongly persistent effect.
+In addition, we show the impulse responses to a news shock to confirm that our identification strategy is picking up news shocks correctly.
+As the responses show, constraining the response of relative prices to news does not qualitatively affect the behavior of news shocks.
+Our identified news shock generates responses broadly in line with those found by the news shock literature.
+In particular, in line with \cite{barsky2011news}, it takes more that 2 years after the news shock for TFP to display a positive, significant and strongly persistent effect.
 Stock prices have a strong forecasting power and show a $4$\% impact effect which is persistent and significant in the long run.
 Real ICT investment does not show a positive impact response but it slowly starts to increase getting significant after almost $2$ years.
-As found by \cite{barsky2011news} in their main specification, real GDP has a non-significant impact effect and it fast rises with all the variables of the system.
-Moreover, as expected by its forward looking nature, real consumption have a significant impact response and reaches its peak once TFP displays a significant effect.
-Finally, relative prices are initially constrained to have a zero response and then shows a small, negative and persistent deviation for at least five years which eventually dies out.
+As found by \cite{barsky2011news} in their main specification, real GDP has a non-significant impact effect, but it rises fast with all the variables of the system.
+Moreover, as was expected, considering the forward-looking nature of consumption, real consumption has a significant impact response and reaches its peak once the TFP response becomes significant.
+Finally, relative prices are initially constrained to have a zero response, and then show a small, negative and persistent deviation for at least five years which eventually dies out.
 
-Finally, we recover a series of ICT shocks which is correlated at $94$\% with the one estimated in System \ref{eq:mainSpecification} using the simple identification strategy presented in Section \ref{section:empiricalstrategy_simple}.
-In particular, in Appendix \ref{section:ICTshockseries_2step}, Figure \ref{fig:shockSeries_2steps} shows ICT shock series for both the 5-dimensional system and 6-dimensional presented in this section.
-In line with the correlation coefficient, the two series almost overlap each others suggesting that our initial result is not confounding any signal regarding future TFP with our estimated ICT shock.
+Thus, not only are the responses to the ICT shock in line with those of our main specification, but the identified news shock also seems to be capturing the right thing: anticipated future technology changes.
+Having thus correctly filtered out news components from our ICT shock, we now check how this newly recovered ICT shock series compares to the series backed out by our main specification of Section \ref{section:empiricalstrategy_simple}.
+It turns out that the correlation between the two shock series is 94\%!
+Figure \ref{fig:shockSeries_2steps} in Appendix \ref{section:ICTshockseries_2step} portrays the two ICT shock series.
+Again, the two recovered shocks are nearly identical, visually reinforcing the very high correlation between them.
+Thus we can confidently state that our initial result is not confounding any signal regarding future TFP with our estimated ICT shock.
 

### 2018-07-12 Latex/Draft_Summer2018/Summer2018.tex
more editing

@@
 In the previous section, we have documented results regarding the relation of current ICT investment and future productivity.
-Clearly, to rationalize empirical dynamic responses of aggregate macroeconomic variables to ICT shocks, we need a two-sector approach that distinguishes ICT goods from other output.
+Clearly, to rationalize the empirical responses of aggregate macroeconomic variables to ICT shocks, we need a two-sector approach that distinguishes ICT goods from other output.
 In this section, we present a simple two-sector model that rationalizes our structural VAR estimates.
-The model presented has several common features with \cite{greenwood1997long} that design a two-sector economy where one sector displays a faster technology than the other.
+
+% Need to add something here that says that we investigate whether a spillover can explain things.
+
+The model presented has several common features with the two-sector environment of \cite{greenwood1997long} that design a two-sector economy where one sector displays a faster technology than the other.
 One different is that we focus specifically on ICT capital sector, rather than equipment, as the sector with faster technological improvements.

### 2018-07-12 Latex/Draft_Summer2018/Summer2018.tex
more editing

@@
 
-The model presented has several common features with the two-sector environment of \cite{greenwood1997long} that design a two-sector economy where one sector displays a faster technology than the other.
-One different is that we focus specifically on ICT capital sector, rather than equipment, as the sector with faster technological improvements.
-This assumption will be necessary if we want to fit the fact that relative prices between the ICT investment and overall economy display a downward sloping trend.\footnote{In addition, we also rely on the results of \cite{whelan2003two} and \cite{oulton2007investment} to correctly define productivity and output share in our setting.}
+The model presented has several common features with the two-sector environment of \cite{greenwood1997long} where one sector displays a faster technology than the other.
+One difference is that we focus specifically on the ICT capital sector, rather than equipment, as the sector with faster technological improvement.
+This assumption will be necessary if we want to fit the fact that relative prices between ICT investment and the overall economy display a downward sloping trend.\footnote{In addition, we also rely on the results of \cite{whelan2003two} and \cite{oulton2007investment} to correctly define productivity and output share in our setting.} A second difference is that  we consider two production functions - one for each sector.
+As \cite{oulton2007investment} shows, the two formulations are isomorphic, so our modeling choice has no implication for the resulting dynamics.
+The reason we choose this approach is because it allows for definitions of GDP and TFP in the model that are consistent with the way these variables are constructed in the national income accounts.
 
@@
 
-Consider an economy inhabited by a representative agent which maximizes the expect values of his lifetime utility as given by
+Consider an economy inhabited by a representative agent who maximizes the expected values of his lifetime utility as given by
 \begin{eqnarray}\label{equation:utilFunc}
@@
 \begin{eqnarray*}
-U(c_t,l_t) = \log(c_t) - \frac{1}{1+\frac{1}{\chi}} l_t^{1+\frac{1}{\chi}}
+U(c_t,l_t) = \log(c_t) - \frac{\chi}{2} l_t^{2}
 \end{eqnarray*}
+%\begin{eqnarray*}
+%U(c_t,l_t) = \log(c_t) - \frac{1}{1+\frac{1}{\chi}} l_t^{1+\frac{1}{\chi}}
+%\end{eqnarray*}
 where $c_t$ and $l_t$ represent consumption and labor at time $t$.
@@
 
-Instead of working with the aggregate production function, assume that the production side of the final-good sector consist of a set $[0,1]$ of firms.
+The production side of the final-good sector consists of a set $[0,1]$ of firms.
 In each period, final-good firm $j \in [0,1]$ produces $y^c_t(j)$ using the services of labor $l_{t}$, and two types of capital: hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$.
-In addition, production function is augmented with (i) neutral productivity common across sectors, (ii) sector-specific productivity, and (iii) a positive spillover effect related to the diffusion of ICT capital in the whole economy.
+In addition, the production function is augmented with (i) neutral productivity common across sectors, (ii) sector-specific productivity, and (iii) a positive spillover effect related to the diffusion of ICT capital in the whole economy.
 Production of final output of firm $j$ is undertaken in accordance with
@@
 
-Since all the final-good producers are identical ex ante and ex post, the following conditions hold,
+Since all the final-good producers are identical, the following conditions hold,
 \begin{eqnarray}\label{equation:aggregation_hard_final}
@@
 
-Instead of working with the aggregate production function, assume that the production side of the ICT-good sector consist of a set $[0,1]$ of firms.
+The production side of the ICT-good sector is symmetric to the first sector.
+It consists of a set $[0,1]$ of firms.
 Similar to final-output production function, ICT-good firm $q \in [0,1]$ produces $y^c_t(q)$ using the services of labor $l_{t}$, and two types of capital: hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$.
-In addition, production function is augmented with (i) neutral productivity common across sectors, (ii) sector-specific productivity, and (iii) a positive spillover effect related to the diffusion of ICT capital in the whole economy.
+In addition, production function is augmented with the same components as the other sector: (i) neutral productivity common across sectors, (ii) sector-specific productivity, and (iii) a positive spillover effect related to the diffusion of ICT capital in the whole economy.
 Production of ICT output of firm $q$ is undertaken in accordance with
 \begin{eqnarray}\label{equation:productionICT}
-y^c_t(q) = A^c_t \ \big( k^c_{t}(q) \big)^a \ \big( k^i_{t}(q) \big)^b \ \big( l_{t}(q) \big)^{1-a-b}, \ \ 0 < a,b < 1
+y^i_t(q) = A^i_t \ \big( k^c_{t}(q) \big)^a \ \big( k^i_{t}(q) \big)^b \ \big( l_{t}(q) \big)^{1-a-b}, \ \ 0 < a,b < 1
 \end{eqnarray}
-where total factor productivity is equal to $ A_t^c = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma} $.
+where total factor productivity is equal to $ A_t^i = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma} $.
 $\eta_t$ is the same neutral technological component which follows \ref{equation:neutral_tech_process} and \ref{equation:neutral_tech_shock}, $\theta^i_t$ is the sector-specific technological component which moves along the following deterministic trend
@@
 
-Similarly, since all the final-good producers are identical ex ante and ex post, the following conditions hold,
+Similarly, since all the final-good producers are identical, the following conditions hold,
 \begin{eqnarray}\label{equation:aggregation_hard_ICTsec}
@@
 \end{eqnarray}
-Notice that elements in the equation above are normalized such that both output and investment are measured in the same units.
-Moreover, ICT goods can be produced from ICT output on a one-to-one basis.
+Also here the elements in the equation above are normalized such that both output and investment are measured in the same units.
+Moreover, ICT output is converted to ICT goods on a one-to-one basis.
 The stock of ICT capital evolves according to
@@
 
-Since we are assuming our economy to be closed, input demands must equal supplies,
+Since the economy is closed, input demands must equal supplies,
 \begin{eqnarray}\label{equation:marketclearingHard}
@@
 \end{eqnarray}
-Taking as given Equations \ref{equation:production_FINAL}-\ref{equation:marketclearingLabor} and assuming that factor markets are perfective competitive, representative household maximizes intertemporal utility function under the following constraint,
+Taking as given Equations \ref{equation:production_FINAL}-\ref{equation:marketclearingLabor} and assuming that factor markets are perfective competitive, the representative household maximizes intertemporal utility under the following constraint,
 \begin{eqnarray}\label{equation:resourceHH}
@@
 where $p_t$ represents the price of ICT capital expressed in consumption units.
-Since price of consumption is normalized to be one then $p_t$ also represents the relative price between final output and ICT output.
+Since the price of consumption is normalized to be 1, $p_t$ also represents the relative price between final output and ICT output.
 

### 2018-07-14 Latex/Draft_Summer2018/Summer2018.tex
not much for now
More writing

@@
 The model presented has several common features with the two-sector environment of \cite{greenwood1997long} where one sector displays a faster technology than the other.
-One difference is that we focus specifically on the ICT capital sector, rather than equipment, as the sector with faster technological improvement.
+Three main assumptions distinguish our model from the one by \cite{greenwood1997long}.
+Firs of all, we focus specifically on the ICT capital sector, rather than equipment, as the sector with faster technological improvement.
 This assumption will be necessary if we want to fit the fact that relative prices between ICT investment and the overall economy display a downward sloping trend.\footnote{In addition, we also rely on the results of \cite{whelan2003two} and \cite{oulton2007investment} to correctly define productivity and output share in our setting.} A second difference is that we consider two production functions - one for each sector.
@@
 The reason we choose this approach is because it allows for definitions of GDP and TFP in the model that are consistent with the way these variables are constructed in the national income accounts.
+Finally, we assume that the total ICT capital stock has a positive spillover effect on the production function of both sectors.
+The general-purpose nature of ICT capital works through its own diffusion because information sharing improves only when new communication technologies are widely spread over the population.
 
@@
 with 
+%\begin{eqnarray*}
+%U(c_t,l_t) = \log(c_t) - \frac{\chi}{2} l_t^{2}
+%\end{eqnarray*}
 \begin{eqnarray*}
-U(c_t,l_t) = \log(c_t) - \frac{\chi}{2} l_t^{2}
+U(c_t,l_t) = \log(c_t) - \frac{1}{1+\frac{1}{\chi}} l_t^{1+\frac{1}{\chi}}
 \end{eqnarray*}
-%\begin{eqnarray*}
-%U(c_t,l_t) = \log(c_t) - \frac{1}{1+\frac{1}{\chi}} l_t^{1+\frac{1}{\chi}}
-%\end{eqnarray*}
 where $c_t$ and $l_t$ represent consumption and labor at time $t$.
@@
 \end{eqnarray}
-where total factor productivity is equal to $ A_t^c = \eta_t \ \theta^c_t \ (k^i_{t})^{\gamma} $. $\eta_t$ is the neutral technological component which moves along the following deterministic trend
+where productivity is equal to $ A_t^c = \eta_t \ \theta^c_t \ (k^i_{t})^{\gamma} $. $\eta_t$ is the neutral technological component which moves along the following deterministic trend
 \begin{eqnarray}\label{equation:neutral_tech_process}
@@
 
-The production side of the ICT-good sector is symmetric to the first sector.
-It consists of a set $[0,1]$ of firms.
-Similar to final-output production function, ICT-good firm $q \in [0,1]$ produces $y^c_t(q)$ using the services of labor $l_{t}$, and two types of capital: hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$.
-In addition, production function is augmented with the same components as the other sector: (i) neutral productivity common across sectors, (ii) sector-specific productivity, and (iii) a positive spillover effect related to the diffusion of ICT capital in the whole economy.
-Production of ICT output of firm $q$ is undertaken in accordance with
+Production of ICT capital goods turns out ot be symmetric to final-output production.
+It is populated by a set $[0,1]$ of firms.
+Similarly, ICT-good firm $q \in [0,1]$ produces $y^i_t(q)$ with labor $l_{t}$, hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$.
+Analogously to the first sector, production function is augmented by neutral productivity $\eta_t$, sector-specific productivity $\theta^i_t$, and the spillover effect $(k^i_{t})^{\gamma}$.
+Firm $q$ produces in accordance with
 \begin{eqnarray}\label{equation:productionICT}
-y^i_t(q) = A^i_t \ \big( k^c_{t}(q) \big)^a \ \big( k^i_{t}(q) \big)^b \ \big( l_{t}(q) \big)^{1-a-b}, \ \ 0 < a,b < 1
+y^i_t(q) = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma} \ \ \big( k^c_{t}(q) \big)^a \ \big( k^i_{t}(q) \big)^b \ \big( l_{t}(q) \big)^{1-a-b}, \ \ 0 < a,b < 1
 \end{eqnarray}
-where total factor productivity is equal to $ A_t^i = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma} $.
-$\eta_t$ is the same neutral technological component which follows \ref{equation:neutral_tech_process} and \ref{equation:neutral_tech_shock}, $\theta^i_t$ is the sector-specific technological component which moves along the following deterministic trend
+where $\theta^i_t$ is the sector-specific technological component which moves along the following deterministic trend
 \begin{eqnarray}\label{equation:ICT_tech_process}
@@
 where $\rho_{\iota} \in (0,1)$ and $\iota_t \sim N(0,\sigma_{\iota})$ represents an ICT technology shock.
-Then, $\gamma$ represents the same parameter that governs the size of the spillover effect of ICT capital in the production function.
-Moreover, $k^c_{t}(q)$ is the part of hard capital $k^c_t$ used by firm $q$ in oder to produce ICT goods.
+In line with the first sector, $k^c_{t}(q)$ is the part of hard capital $k^c_t$ used by firm $q$ in oder to produce ICT goods.
 Similarly, $k^i_{t}(q)$ and $l_{t}(q)$ are the parts of ICT capital $k^i_t$ and labor $l_t$ used by firm $q$ in oder to produce ICT goods, respectively.
 
-Similarly, since all the final-good producers are identical, the following conditions hold,
+Since we assume homogeneity across ICT producers, following conditions hold
 \begin{eqnarray}\label{equation:aggregation_hard_ICTsec}
@@
 \end{eqnarray}
-where $k^c_{2,t}$ is the aggregate part of hard capital $k^c_t$ devoted to the ICT-sector, i.e.
-sector 2.
-Moreover, $k^i_{2,t}$ and $l_{2,t}$ are the aggregate parts of ICT capital $k^i_{t}$ and labor $l_{t}$ devoted to the ICT-good sector, respectively.
+where $k^c_{2,t}$ is the aggregate part of hard capital $k^c_t$ devoted to the second sector.
+Similarly, $k^i_{2,t}$ and $l_{2,t}$ are the aggregate parts of ICT capital $k^i_{t}$ and labor $l_{t}$ devoted to the ICT-good sector, respectively.
 
@@
 \begin{eqnarray}\label{equation:production_ICT_aggregate}
-	y^i_t = A^c_t \ ( k^c_{2,t} )^a \ ( k^i_{2,t} )^b \ ( l_{2,t} )^{1-a-b}, \ \ 0 < a,b < 1
+	y^i_t = A^i_t \ ( k^c_{2,t} )^a \ ( k^i_{2,t} )^b \ ( l_{2,t} )^{1-a-b}, \ \ 0 < a,b < 1
 \end{eqnarray}
-and it can be only investment in ICT capital, $i^i_t$,
+where $A^i_t = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma}$ and $y^i_t$ can be only investment in ICT capital, $i^i_t$,
 \begin{eqnarray}\label{equation:resourceICT}
@@
 Moreover, ICT output is converted to ICT goods on a one-to-one basis.
-The stock of ICT capital evolves according to
+The law of motion of ICT capital is described as follows,
 \begin{eqnarray}\label{equation:LOM_ICT}

### 2018-07-23 Latex/Draft_Summer2018/Summer2018.tex
back to work: edited some of the draft
I wonder if you have forgotten to commit some work, since the draft is
basically unchanged since I last saw it?

@@
 
-Production of ICT capital goods turns out ot be symmetric to final-output production.
+Production of ICT capital goods is symmetric to final-output production.
 It is populated by a set $[0,1]$ of firms.
@@
 
-Competitive equilibrium is represented by (i) Equations \ref{equation:utilFunc}-\ref{equation:marketclearingLabor}, (ii) household's first order conditions with respect to consumption $c_t$, labor $l_t$, hard capital $k^c_t$, ICT capital $k^i_t$, (iii) final-good producers' first order conditions with respect to $k^c_{t}(j)$, $k^i_{t}(j)$, and $l_{t}(j)$, and (iv) ICT-good producers' first order conditions with respect to $k^c_{t}(q)$, $k^i_{t}(q)$, and $l_{t}(q)$.
+Competitive equilibrium is represented by (i) Equations \ref{equation:utilFunc}-\ref{equation:marketclearingLabor}, (ii) the household's first order conditions with respect to consumption $c_t$, labor $l_t$, hard capital $k^c_t$, ICT capital $k^i_t$, (iii) final-good producers' first order conditions with respect to $k^c_{t}(j)$, $k^i_{t}(j)$, and $l_{t}(j)$, and (iv) ICT-good producers' first order conditions with respect to $k^c_{t}(q)$, $k^i_{t}(q)$, and $l_{t}(q)$.
+In order to simulate responses to (i) neutral technology shocks, $\nu_t$ and (ii) ICT shocks, $\iota_t$ we employ a standard first-order approximation of the log-transformation of the system around the detrended (stationarized) steady state.\footnote{The stationarized system as well as code to replicate our results are available on request.}
 
-In order to simulate responses to (i) neutral technology shocks, $\nu_t$ and (ii) ICT shocks, $\iota_t$ we employ a standard first-order approximation of the log-transformation of the system around the detrended (stationarized) steady state.
-In order to stationarized the system we use results firstly presented by \cite{greenwood1997long} where they formally show the balance-growth path of the two sectors under the assumption that one sector is moving faster than the other.
+%In order to stationarized the system we use results firstly presented by \cite{greenwood1997long} where they formally show the balance-growth path of the two sectors under the assumption that one sector is moving faster than the other.
 In our case, results are going to be slightly different since we need to take into account the additional effect provided by the spillover.\footnote{The stationarized version of the steady state is available on request.} Results are derived mostly using the code provide by Stephanie Schmitt-Grohe and Martin Uribe available on their websites.\footnote{Code to replicate our results is available on request.}
@@
 
-In this section we describes the parameter values and test the empirical performance of the model.
-Following \cite{christiano2005nominal}, we partition those values into two groups.
+We now turn to describing the parameter values and testing the empirical performance of the model.
+Following \cite{christiano2005nominal}, we partition the model parameters into two groups.
 We calibrate parameters of the first group using steady-state relations or results from previous works.
-We estimate the second group of parameters by minimizing the distance between the model-implied impulse responses and the empirical results presented in \ref{section:mainSpec}.
+We estimate the second group by minimizing the distance between the model-implied impulse responses and the empirical results presented in Section \ref{section:mainSpec}.
 In particular, the second group focuses on parameters specifically related to the effect of ICT investment on future TFP: (i) the size of the spillover effect of ICT capital on productivity $\gamma$, (ii) the standard deviation $\sigma_{\iota}$ and (iii) persistence $\rho_{\iota}$ of ICT shocks.
@@
 We set the discount factor $\beta$ to $0.97^{\frac{1}{4}}$ to match the average yield of $3$\% of the 3-month Treasury bill using data from 1989:Q1 to 2017:Q1.
-Moreover, we set ICT share $b$ equal to $0.0310$ following \cite{oulton2012long} and hard capital share $a$ equal to $0.3$.
-Moreover, adapting \cite{oulton2012long} accordingly to our additional assumptions, we derive steady state growth rates of final-sector technology $\Gamma^c$ and ICT-sector technology $\Gamma^i$ solving the system,
+We set the ICT share $b$ equal to $0.0310$ following \cite{oulton2012long} and hard capital share $a$ equal to $0.3$.
+Moreover, adapting \cite{oulton2012long} accordingly to our additional assumptions, we derive steady state growth rates of final-sector technology $\Gamma^c$ and ICT-sector technology $\Gamma^i$ from solving the system,
 \begin{equation}\label{equation:system_param}
@@
 where $\E[p_t/p_{t-1}]$ and $\E[c_t/c_{t-1}]$ are derived from the simple mean of their empirical related values using quarterly data from 1989:Q1 to 2017:Q1.
-Estimation implies $\Gamma^c = 1.0034$ and $\Gamma^i = 1.0160$.\footnote{Notice that the value of $\gamma$ is unknown at this step since it is going to be evaluated using impulse-response matching.
+This implies $\Gamma^c = 1.0034$ and $\Gamma^i = 1.0160$.\footnote{Notice that the value of $\gamma$ is unknown at this step since it is going to be evaluated using impulse-response matching.
 This implies that the solution for $\Gamma^c$, $\Gamma^i$, and $\gamma$ should be a fixed point where given $\gamma^*$ we obtain $(\Gamma^i)^*$ and $(\Gamma^c)^*$ solving \ref{equation:system_param}.
@@
 
-In addition, we set the frisch elasticity of labor supply $\chi$ to be equal to $1$.
+In addition, we set the Frisch elasticity of labor supply $\chi$ to be equal to $1$.
 Moreover, following Bureau fo Economic Analysis (BEA) depreciation estimates, we set the quarterly depreciation rates for hard capital $\delta^c$ to be equal to $0.0206$ in order to match an annual depreciation rate of $0.08$.

### 2018-07-25 Latex/Draft_Summer2018/Summer2018.tex
Progress with writing
We miss (i) interpretation of the results and (ii) conclusions. I personally will wait after the green line for experiments.

@@
 \begin{prop}\label{prop:priceRestriction}
-In a two-sector economy, if both production functions are identical, then any economy-wide productivity shocks do not affect relative prices between the two sectors.
+In a two-sector economy, if both production functions display identical input shares, then any economy-wide productivity shocks do not affect relative prices between the two sectors.
 \end{prop}
@@
 
-\subsubsection{Household}
+\subsection{Household}
 
@@
 \end{eqnarray} 
-where $\rho_{\nu} \in (0,1)$ and $\nu_t \sim N(0,\sigma_{\nu})$ represents a neutral technology shock.
+where $\rho_{\nu} \in (0,1)$ and $\nu_t \sim N(0,\sigma_{\nu}^2)$ represents a neutral technology shock.
 $\theta^c_t$ is the sector-specific technological component,  which moves along the following deterministic trend
@@
 \end{eqnarray} 
-where $\rho_{\iota} \in (0,1)$ and $\iota_t \sim N(0,\sigma_{\iota})$ represents an ICT technology shock.
+where $\rho_{\iota} \in (0,1)$ and $\iota_t \sim N(0,\sigma_{\iota}^2)$ represents an ICT technology shock.
 In line with the first sector, $k^c_{t}(q)$ is the part of hard capital $k^c_t$ used by firm $q$ in oder to produce ICT goods.
@@
 We estimate the second group by minimizing the distance between the model-implied impulse responses and the empirical results presented in Section \ref{section:mainSpec}.
-In particular, the second group focuses on parameters specifically related to the effect of ICT investment on future TFP: (i) the size of the spillover effect of ICT capital on productivity $\gamma$, (ii) the standard deviation $\sigma_{\iota}$ and (iii) persistence $\rho_{\iota}$ of ICT shocks.
+In particular, the second group focuses on parameters specifically related to the effect of ICT investment on future TFP: (i) the standard deviation $\sigma_{\iota}$ of ICT shock $\zeta_t$, (ii) persistence $\rho_{\iota}$ of ICT shock $\zeta_t$ and (iii) the size of the spillover effect of ICT capital on productivity $\gamma$.
 
@@
 \begin{cases}
-\E \big( \frac{p_t}{p_{t-1}} \big) = \frac{\Gamma^c}{\Gamma^i} \\
-\E \big( \frac{c_t}{c_{t-1}} \big) = (\Gamma^c)^{\frac{1-b-\gamma}{1-a-b-\gamma}}  (\Gamma^i)^{\frac{b+\gamma}{1-a-b-\gamma}}
+ \frac{p_t}{p_{t-1}}  = \frac{\Gamma^c}{\Gamma^i} \\
+ \frac{c_t}{c_{t-1}}  = (\Gamma^c)^{\frac{1-b-\gamma}{1-a-b-\gamma}}  (\Gamma^i)^{\frac{b+\gamma}{1-a-b-\gamma}}
 \end{cases}
 \end{equation}
-where $\E[p_t/p_{t-1}]$ and $\E[c_t/c_{t-1}]$ are derived from the simple mean of their empirical related values using quarterly data from 1989:Q1 to 2017:Q1.
+where $p_t/p_{t-1}$ and $c_t/c_{t-1}$ are derived from the simple mean of their empirical related values using quarterly data from 1989:Q1 to 2017:Q1.
 This implies $\Gamma^c = 1.0034$ and $\Gamma^i = 1.0160$.\footnote{Notice that the value of $\gamma$ is unknown at this step since it is going to be evaluated using impulse-response matching.
@@
 \subsection{Impulse-Response Matching}\label{section:IRmatching}
+
+In this section, we estimate model’s key parameters governing the effect of ICT investment on future TFP by imposing theoretical impulse responses of an ICT shock to be as close as possible to the empirical ones.
+To enhance movement in ICT investment, we use a shock to the ICT-specific technological component $\zeta_t$.
+Using empirical impulse responses of TFP, ICT investment, consumption, and relative prices, we estimate four parameters: the variance of an ICT technology shock, $\sigma_{\iota}^2$, the persistence of the same shock, $\rho_{\iota}$, and the size of the spillover effect of ICT capital on TFP, $\gamma$.
+We estimate $\Omega = (\gamma, \ \sigma_{\iota}^2, \ \rho_{\iota})$ by minimizing,
+\begin{eqnarray}\label{equation:min_prob_IRmatching}
+\min_{\Omega} \big[  \hat{\Psi} - \Psi(\Omega)  \big]' \Lambda \big[  \hat{\Psi} - \Psi(\Omega)  \big]
+\end{eqnarray}
+where $\Psi(\Omega)$ denotes the mapping from $\Omega$ to the theoretical impulse responses, and $\hat{Psi}$ denotes the empirical impulse responses of an ICT shock to TFP, ICTI, consumption, and relative prices shown in Appendix \ref{section:mainSetResults}.
+Moreover, $\Lambda$ is a diagonal matrix which embodies variances of the empirical impulse responses.
+These elements serve as weights to impose relatively more precision on some estimates on the optimization problem.
+Finally, accordingly to what presented above, we use a horizon of $40$ periods for each response which sum up to a total of $160$ elements for three theoretical parameters only.
+
+Table \ref{table:estimated_parameters} shows results of Problem \ref{equation:min_prob_IRmatching}.
+The estimate of the spillover effect of ICT capital on TFP, $\gamma$, is $0.58$ indicating that empirical responses favor a causality relation from an ICT capital deepening to total factor productivity.
+Moreover, estimates of variance and persistence of an ICT-specific technological shock $\sigma^2_{\iota}$ and $\rho_{\iota}$ are $0.01^2$ and $0.9$, respectively.
+Results imply both a remarkable size and persistence of an ICT sector-specific technological shock $\zeta_t$ in the economy.
+% does it make sense? I dont know what to say for sigmaiota and rhoiota...
+
+Using the estimated parameter values in Table \ref{table:estimated_parameters}, Figure \ref{fig:IR_matching} displays empirical impulse responses along with theoretical ones.
+Our simple model is able to mimic empirical movements in TFP, ICT investment, consumption, and relative prices.
+In both the model and the data, a sector-specific technological shock $\zeta_t$ has a delayed positive effect on TFP which tend to last over the medium and long run.
+Moreover, in both cases, ICT investment has a large initial peak and then tends to remain persistently positive over the $40$-quarter horizon.
+In the model and the data, consumption responds positively on impact, reaches its peak after $4$ years and persistently remains positive.
+Finally, model-generated and empirical impulse responses of relative prices have a large and negative impact response which dies out in about $6$ years.
 
@@
 
-Prova
+Notice that in this proof we use the same assumptions and the same notation in the 2-sector model presented in Section \ref{section:theory}.
+
+\
+
+First order condition with respect to labor input for firm $j$ is
+\begin{eqnarray}\label{equation:FOC_j_l}
+w_t =  (1 - a - b) p_t \eta_t \theta^c (k^i_t)^{\gamma} \bigg( \frac{k_t^c(j)}{l_t(j)} \bigg)^a \bigg( \frac{k_t^i(j)}{l_t(j)} \bigg)^b,
+\end{eqnarray}
+and first order condition with respect to labor input for firm $q$ is
+\begin{eqnarray}\label{equation:FOC_q_l}
+w_t = (1 - a - b) \eta_t \theta^c (k^i_t)^{\gamma} \bigg( \frac{k_t^c(q)}{l_t(q)} \bigg)^a \bigg( \frac{k_t^i(q)}{l_t(q)} \bigg)^b,
+\end{eqnarray}
+Since both production functions display identical input shares then in equilibrium input ratios must be the same over the two sectors, which is,
+\begin{eqnarray}\label{eq:shares_result1}
+\frac{k_t^c(j)}{l_t(j)} = \frac{k_t^c(q)}{l_t(q)},
+\end{eqnarray}
+\begin{eqnarray}\label{eq:shares_result2}
+\frac{k_t^i(j)}{l_t(j)} = \frac{k_t^i(q)}{l_t(q)},
+\end{eqnarray}
+\begin{eqnarray*}\label{eq:shares_result3}
+\frac{k_t^i(j)}{k^c_t(j)} = \frac{k_t^i(q)}{k^c_t(q)}.
+\end{eqnarray*}
+Now, dividing \ref{equation:FOC_j_l} over \ref{equation:FOC_q_l}, we can use \ref{eq:shares_result1} and \ref{eq:shares_result2} to obtain
+\begin{eqnarray}\label{eq:result_proof}
+1 = \frac{1}{p_t} \frac{\theta^c_t}{\theta^i_t} \ \ \Rightarrow \ \ p_t = \frac{\theta^c_t}{\theta^i_t}.
+\end{eqnarray}
+From Equation \ref{eq:result_proof}, it is clear that the equilibrium path of $p_t$ is fully independent on the past, current, and future values of neutral technology, $\eta_t$. 
+\qed
 
@@
 
+\newpage
+
+\section{Estimated Parameters via IR Matching}
+
+ 	\begin{table}[h!]
+	\begin{center}
+		\begin{tabular}{clc}
+			\hline
+			Symbol & Economic Interpretation & Estimated Value \\
+			\hline
+            $\sigma^2_{\iota}$ & Variance of ICT technological shock &   $0.01^2$  \\
+            $\rho_{\iota}$     & Persistence of ICT technological shock & $0.9$   \\
+            $\gamma$           & Size of spillover of ICT capital on TFP &  $0.5881$ \\
+			\hline
+		\end{tabular}
+		\caption{Estimation of key parameters by imposing model's impulse responses of an ICT shock to be as close as possible to the empirical ones.
+Theoretical estimates are impulse responses to an ICT-specific technological shock, $\zeta_t$ which are functions of key parameters: $\sigma_{\iota}^2$, $\rho_{\iota}$, and $\gamma$.
+Empirical impulse responses of an ICT shock to TFP, ICTI, consumption, and relative prices are derived from Specification \ref{eq:mainSpecification} using the empirical strategy presented in Section \ref{section:empiricalstrategy_simple}.
+According to what presented in Appendix \ref{section:mainSetResults}, we use a horizon of $40$ periods for each response.}
+		\label{table:estimated_parameters}
+	\end{center}
+\end{table}
+
+\newpage
+
+\section{Impulse-Response Matching}\label{section:appendix_IR_matching}
+
+\begin{figure}[h!]
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{MainFigures/fig_ICT_Shock_on_TFP_IRmatching_together}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{MainFigures/fig_ICT_Shock_on_ICTI_IRmatching_together}
+	\end{subfigure}
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{MainFigures/fig_ICT_Shock_on_C_IRmatching_together}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=1\linewidth]{MainFigures/fig_ICT_Shock_on_RP_IRmatching_together}
+	\end{subfigure}
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+	\caption{Empirical VAR versus model responses to an ICT shock.
+The black solid lines show the empirical responses to an identified ICT shock in Specification \ref{eq:mainSpecification}.
+The dotted red lines show the model’s responses to a shock to the ICT-specific technological component $\zeta_t$.
+The horizontal axes refer to forecast horizon and the units of the vertical axes are percentage deviations.}
+	\label{fig:IR_matching}
+\end{figure}
+
 \end{document}

### 2018-07-25 Code/oulton2010/main_file_IRmatching.m

@@ -263,8 +263,9 @@ else
     addpath([base_path '/Code/just_IT_vecm']) %for Mac
 end
 
-print_figs ='no'; 
-plot_matchedIRFs(IRF_IT,ir_matched,T_VAR,1,shocknames, {'TFP','IT inv', 'C', 'RP'}, print_figs, base_path, 'IRmatching_together')
+print_figs = 'yes'; 
+shocknames = {'ICT Shock'};
+plot_matchedIRFs(IRF_IT,ir_matched,T_VAR,1,shocknames, {'TFP','ICTI', 'C', 'RP'}, print_figs, base_path, 'IRmatching_together')
 
 param_names = {'gam', 'sigitlev', 'rhoitlev'};
 % param_names = {'a', 'b', 'gam', 'sigitlev', 'rhoitlev'};

### 2018-07-25 Code/oulton2010/paramsset.m

@@ -10,8 +10,8 @@ set.di         = 0.0398; %0.124; % depreciation rate of IT capital (Some work su
 set.dc         = 0.0206; %0.056 depreciation rate of standard capital
 set.chi        = 1; % preference parameter of preference for leisure. (From Ryan)
 param.gam      = 0.2; %0.2 spillover elasticity (only used in model_spillover.m and model_spillover_ss.m)
-set.siggami  = 1; % variance of BIGGAMI
-set.rhogami  = 0.8;
+set.siggami    = 1; % variance of BIGGAMI
+set.rhogami    = 0.8;
 set.sige       = 1; %2 variance of signal on BIGGAMI
 param.sigitlev = 1; % variance of the IT prod. shock (level)
 param.rhoitlev = 0.8; % persistence of the IT prod shock

### 2018-07-25 plot_matchedIRFs.m

@@ -31,9 +31,11 @@ for i_shock=1:nshocks
         name = shocknames{which_shock(i_shock)};
         hold on
         plot(periods,IRFs_VAR(i_var,1:h,which_shock(i_shock)),'linewidth',2,'Color','k')
-        plot(periods,IRFs_theory(i_var,1:h,which_shock(i_shock)),'linewidth',2,'Color','r')
+        plot(periods,IRFs_theory(i_var,1:h,which_shock(i_shock)),'--','linewidth',2,'Color','r')
         plot(zeros(1,h), 'Color','b')
-        legend('Empirical', 'Model')
+        LEG = legend('Empirical', 'Model');
+        LEG.FontSize = 24;
+        legend boxoff
         xt = get(gca, 'XTick');
         set(gca, 'FontSize', 22)
         title([name, ' on ' , varname],'fontsize',72)

### 2018-07-26 Latex/Draft_Summer2018/Summer2018.tex
WRITE WRITE WRITE

@@
 Encouragingly, controlling for signals regarding future movements in TFP does not affect our results.
-We view this as strengthening our statement relating movements in current ICT technology to future TFP.
+We view this as strengthening the causality relation from current ICT investment to future TFP.
 
@@
 Three main assumptions distinguish our model from the one by \cite{greenwood1997long}.
-Firs of all, we focus specifically on the ICT capital sector, rather than equipment, as the sector with faster technological improvement.
+First of all, we focus specifically on the ICT capital sector, rather than equipment, as the sector with faster technological improvement.
 This assumption will be necessary if we want to fit the fact that relative prices between ICT investment and the overall economy display a downward sloping trend.\footnote{In addition, we also rely on the results of \cite{whelan2003two} and \cite{oulton2007investment} to correctly define productivity and output share in our setting.} A second difference is that we consider two production functions - one for each sector.
@@
 
-%%%%%%%%%%%%%%%%%%%%               MODEL                 %%%%%%%%%%%%%%%%%% 
-\section{Experiments}\label{section:experiments}
+Although both the model and impulse-response matching exercise should be considered as preliminary, we strongly believe they are already able to rationalize empirical results obtained in Section \ref{section:empirics} and convey the main message of this project.
+Formally, the question we tried to answer is why a contemporaneous technological shock specific to the ICT sector is able to trigger increases in future total factor productivity.
+In other words, why an ICT-investment shock is able to increase productivity of ICT goods users with some lags.
+
+We interpret ICT capital as being the general-purpose technology of the U.S.
+economy over the last $3$ decades.
+Specifically, when an ICT technology shock hits the economy, both sectors invest more on ICT capital goods since they are now cheaper to purchase and easier to produce.
+Now, in order to link current higher investment on ICT durable goods to future TFP, we assume that both production functions are augmented by a spillover effect related to the overall stock of ICT capital which is not internalized by the agents.\footnote{This externality is governed by the parameter $\gamma$ which has been estimated via impulse-response matching to be robustly larger than zero.
+Using different empirical results, changing the initial calibration, or the methodology do not qualitative change the estimated value of $\gamma$ close to $0.6$.} These assumptions are mechanically suitable for two main reasons.
+First of all, this spillover enters into the estimated Solow residual since it takes the form of an externality which implies that industries are not paying for this additional benefit.
+Moreover, since this spillover arises from a state variable, it leads to a dynamics where the accumulation of ICT durable goods is a slow process and the benefits of an ICT technology shock show up in the productivity of ICT-capital users with some lags and this effect tends to be persistent.
+
+Although this assumption is mathematically suitable to track empirical impulse responses, we consider important to highlight that this positive externality is sustained by an intuitive and reliable economic intuition which distinguishes the general-purpose nature of ICT capital.
+Since the purpose of ICT goods is to enhance communication, the quality and speed of information sharing is also determined by the overall diffusion of these goods.
+As a simple example, assume that in 1995 a scholar decides to purchase a computer with an Internet subscription in order to speed up the acquisition of information.
+She is very satisfied of this investment and does not regret the paid amount.
+However, at the same time, a former colleague who is now working in a different university decides to buy a computer with an Internet subscription as well.
+Once she learns of this development, she also decides to exploit her computer to exchange research material with her former colleague.
+They eventually decide to start a new project together since being in two different universities is not anymore a constraint for the quality of their joint research.
+Both scholars did not pay for this additional benefit since they did not expect to have simultaneously a computer with an Internet subscription.
+However, what is actually happening is that their research production has been boosted by the positive externality that also the other colleague is endowed with the same technology.
+
+As a result, we expect that the nature of ICT capital should display two main features.
+First of all, the effectiveness of an ICT good must be related to its own diffusion as pointed out by the spillover effect.
+Moreover, the cost of ICT items should not initially reflect an unexpected increase in their diffusion as pointed out by the assumption that the first feature is not internalized.
+
+%%%%%%%%%%%%%%%%%%%%            EXPERIMENTS             %%%%%%%%%%%%%%%%%% 
+%\section{Experiments}\label{section:experiments}
+
+%TBD. %I personally would wait after some comments/conferences
 
@@
 \section{Conclusion}\label{section:conclusions}
+
+In the first part of the paper, we investigate the effect of technological shocks specific to the ICT sector on future TFP.
+Using Structural VAR techniques on quarterly aggregate U.S.
+data from 1989, we impose two identifying restrictions to correctly identify ICT shocks: (i) they must be orthogonal to current productivity and (ii) maximize the impact response of ICT investment.
+In response to an ICT shock, ICT investment increases on impact and stays significant for more than 10 years; relative prices persistently decline as an additional support to the reliability of our identification strategy; and TFP rises after three quarters and remains significant for more than 10-years.
+In addition, variance decomposition analysis suggests that the quantitative impact of ICT shocks on TFP is economically remarkable since they explain about one third of the overall TFP fluctuations over a 10-year horizon.
+
+In order to check whether our identification assumptions may confound our shock with a news shock which contemporaneously boosts ICT investment, we provide a series of different identification strategies which deliver analogous results.
+Our main robustness check is a sequential identification of news shocks first and then ICT shocks which encouragingly does not affect estimates.
+We view this as confirmation of the causality relation which goes from current ICT investment to future TFP.
+
+In the second part of the paper, we rationalize our empirical results by analyze a two-sector DSGE model \`a la \cite{greenwood1997long} augmented by three main assumptions.
+Firstly, the sector with the faster technological improvement produces specifically ICT capital.
+Moreover, we consider two production functions in order to have a consistent definition of GDP and TFP between the model and the data.
+Finally, we augment both production functions with a spillover effect related to the overall level of ICT capital which is not internalized by the agents.
+In particular, this last assumption points out our interpretation of the general-purpose nature of ICT capital: the effectiveness of ICT capital is enhanced by its diffusion and its cost does not reflect this indirect benefit.
+We use both empirical and theoretical results to estimate main parameters of the model via impulse-response matching to an ICT technology shock.
+Results point out that the parameter which governs the size of the spillover effect is positive, suggesting that our interpretation of the general-purpose nature of ICT capital is confirmed by the data.
 

### 2018-07-27 Latex/Draft_Summer2018/Summer2018.tex
More writing

@@
 Our main result is that TFP, restricted not to respond on impact, rises after few quarters and remains significant and stable for at least 5 years, despite the tiny size of the ICT sector relative to the economy.
+Finally, variance decomposition analysis suggests that ICT shocks explains a remarkable size of economic fluctuations over the medium and long run.
+These shocks drive about $40$\% and $33$\% of the overall GDP and TFP fluctuations over a 10-year horizon, respectively.
 
@@
 
-Although both the model and impulse-response matching exercise should be considered as preliminary, we strongly believe they are already able to rationalize empirical results obtained in Section \ref{section:empirics} and convey the main message of this project.
+Although both the model and impulse-response matching exercise should be considered as preliminary, we strongly believe they are already able to rationalize empirical results obtained in Section \ref{section:empirics} and convey the main message of this paper.
 Formally, the question we tried to answer is why a contemporaneous technological shock specific to the ICT sector is able to trigger increases in future total factor productivity.
-In other words, why an ICT-investment shock is able to increase productivity of ICT goods users with some lags.
+In other words, why an ICT-investment shock is able to increase productivity of ICT-good users with some lags.
 
@@
 
-In the second part of the paper, we rationalize our empirical results by analyze a two-sector DSGE model \`a la \cite{greenwood1997long} augmented by three main assumptions.
-Firstly, the sector with the faster technological improvement produces specifically ICT capital.
-Moreover, we consider two production functions in order to have a consistent definition of GDP and TFP between the model and the data.
-Finally, we augment both production functions with a spillover effect related to the overall level of ICT capital which is not internalized by the agents.
+In the second part of the paper, we rationalize our empirical results by analyze a two-sector DSGE model \`a la \cite{greenwood1997long} augmented by two main assumptions: (i) the sector with the faster technological improvement produces specifically ICT capital, and (ii) both production functions are augmented with a spillover related to the overall level of ICT capital which is not internalized by the agents.
 In particular, this last assumption points out our interpretation of the general-purpose nature of ICT capital: the effectiveness of ICT capital is enhanced by its diffusion and its cost does not reflect this indirect benefit.
 We use both empirical and theoretical results to estimate main parameters of the model via impulse-response matching to an ICT technology shock.
-Results point out that the parameter which governs the size of the spillover effect is positive, suggesting that our interpretation of the general-purpose nature of ICT capital is confirmed by the data.
+Results point out that the parameter which governs the size of the spillover effect is positive and large, suggesting that our interpretation of the general-purpose nature of ICT capital is confirmed by the data.
 

### 2018-07-28 Latex/Draft_Summer2018/Summer2018.tex
Some few details on the draft

@@
 We then present and analyze the two-sector DSGE model in Section \ref{section:theory}.
-We estimate via impulse-response matching key parameters of the model and run a series of related experiments in Section \ref{section:experiments}.
-Concluding remarks, caveats and prospective future research are discussed in Section \ref{section:conclusions}.
+We estimate via impulse-response matching key parameters of the model and assess its empirical reliability in Section \ref{section:model_assessment}.
+Concluding remarks are discussed in Section \ref{section:conclusions}.
 
@@
 
-\section{Model Assessment}
+\section{Model Assessment}\label{section:model_assessment}
 

### 2018-07-29 Latex/Draft_Summer2018/Summer2018.tex
read the last part of the paper
will read the whole again with fresh eyes tomorrow

@@
 We estimate the second group by minimizing the distance between the model-implied impulse responses and the empirical results presented in Section \ref{section:mainSpec}.
-In particular, the second group focuses on parameters specifically related to the effect of ICT investment on future TFP: (i) the standard deviation $\sigma_{\iota}$ of ICT shock $\zeta_t$, (ii) persistence $\rho_{\iota}$ of ICT shock $\zeta_t$ and (iii) the size of the spillover effect of ICT capital on productivity $\gamma$.
+In particular, the second group focuses on parameters specifically related to the effect of ICT investment on future TFP: (i) the standard deviation $\sigma_{\iota}$ of the ICT shock $\zeta_t$, (ii) the persistence $\rho_{\iota}$ of the ICT shock $\zeta_t$ and (iii) the size of the spillover effect of ICT capital on productivity $\gamma$.
 
@@
 Given $(\Gamma^i)^*$ and $(\Gamma^c)^*$ we obtain $\gamma^*$ by minimizing the impulse-response matching.
-At this step we are simply solving the system for $\gamma$ equal to zero but a more refine solution will be provided in future.} Finally, to avoid an over-identification problem we set the growth rate of sector-neutral technology $\Gamma^{\eta}$ equal to one.
+At this step, however, we are simply solving the system assuming $\gamma$ equal to zero, but a more refined solution will be provided in future.} Finally, to avoid an over-identification problem we set the growth rate of sector-neutral technology $\Gamma^{\eta}$ equal to one.
 
@@
 
-In this section, we estimate model’s key parameters governing the effect of ICT investment on future TFP by imposing theoretical impulse responses of an ICT shock to be as close as possible to the empirical ones.
+In this section, we estimate the model's key parameters governing the effect of ICT investment on future TFP by imposing theoretical impulse responses of an ICT shock to be as close as possible to the empirical ones.
 To enhance movement in ICT investment, we use a shock to the ICT-specific technological component $\zeta_t$.
-Using empirical impulse responses of TFP, ICT investment, consumption, and relative prices, we estimate four parameters: the variance of an ICT technology shock, $\sigma_{\iota}^2$, the persistence of the same shock, $\rho_{\iota}$, and the size of the spillover effect of ICT capital on TFP, $\gamma$.
+Using empirical impulse responses of TFP, ICT investment, consumption, and relative prices, we estimate three parameters: the variance of an ICT technology shock, $\sigma_{\iota}^2$, the persistence of the same shock, $\rho_{\iota}$, and the size of the spillover effect of ICT capital on TFP, $\gamma$.
 We estimate $\Omega = (\gamma, \ \sigma_{\iota}^2, \ \rho_{\iota})$ by minimizing,
@@
 \end{eqnarray}
-where $\Psi(\Omega)$ denotes the mapping from $\Omega$ to the theoretical impulse responses, and $\hat{Psi}$ denotes the empirical impulse responses of an ICT shock to TFP, ICTI, consumption, and relative prices shown in Appendix \ref{section:mainSetResults}.
-Moreover, $\Lambda$ is a diagonal matrix which embodies variances of the empirical impulse responses.
-These elements serve as weights to impose relatively more precision on some estimates on the optimization problem.
-Finally, accordingly to what presented above, we use a horizon of $40$ periods for each response which sum up to a total of $160$ elements for three theoretical parameters only.
+where $\Psi(\Omega)$ denotes the mapping from $\Omega$ to the theoretical impulse responses, and $\hat{\Psi}$ denotes the empirical impulse responses of an ICT shock to TFP, ICTI, consumption, and relative prices shown in Appendix \ref{section:mainSetResults}.
+$\Lambda$ is a diagonal weighting matrix, which is the inverse of the variance matrix of the empirical impulse responses.
+These elements serve as weights to impose more precision on some estimates of the optimization problem.
+Finally, consistent with our choice of horizons presented above, we use a horizon of $40$ periods for each response.
+% which sum up to a total of $160$ elements for three theoretical parameters only.
 
 Table \ref{table:estimated_parameters} shows results of Problem \ref{equation:min_prob_IRmatching}.
-The estimate of the spillover effect of ICT capital on TFP, $\gamma$, is $0.58$ indicating that empirical responses favor a causality relation from an ICT capital deepening to total factor productivity.
-Moreover, estimates of variance and persistence of an ICT-specific technological shock $\sigma^2_{\iota}$ and $\rho_{\iota}$ are $0.01^2$ and $0.9$, respectively.
-Results imply both a remarkable size and persistence of an ICT sector-specific technological shock $\zeta_t$ in the economy.
+The estimate of the spillover effect of ICT capital on TFP, $\gamma$, is $0.58$, while estimates of variance and persistence of an ICT-specific technological shock $\sigma^2_{\iota}$ and $\rho_{\iota}$ are $0.01$ and $0.9$ respectively.\footnote{Estimated parameter values are strongly robust to various alternative specifications.
+Using different empirical results, changing the initial calibration, the number of parameters matched or the methodology do not qualitative change the estimated value of $\gamma$ close to $0.6$.} These results convey a number of interesting messages regarding the fit of our two-sector model.
+Most importantly, the key question of our model was whether the presence of ICT shocks alone can account for the empirical responses we observe in data, or whether ICT diffusion plays a crucial role in this dynamics.
+This amounts to asking whether $\gamma = 0$ is supported by the data.
+Clearly, our estimate of $0.58$ rejects this hypothesis strongly.
+Thus, the data favor an interpretation of our model in which there are considerable spillovers to ICT capital.
+Accordingly, ICT shocks do not need to be large in magnitude to have sizable effects on TFP, GDP and consumption.
+This is indicated by the relatively small number we obtain for $\sigma^2_{\iota}$ of $0.01$.
+Confronted with data, the model is clearly telling a story in which there are small, but persistent ($\rho_{\iota} = 0.9$) ICT shocks that lead considerable medium-run TFP growth because of large spillovers from ICT capital accumulation.
 % does it make sense? I dont know what to say for sigmaiota and rhoiota...
@@
 Our simple model is able to mimic empirical movements in TFP, ICT investment, consumption, and relative prices.
-In both the model and the data, a sector-specific technological shock $\zeta_t$ has a delayed positive effect on TFP which tend to last over the medium and long run.
+In both the model and the data, a sector-specific technological shock $\zeta_t$ has a delayed positive effect on TFP which tends to last over the medium and long run.
 Moreover, in both cases, ICT investment has a large initial peak and then tends to remain persistently positive over the $40$-quarter horizon.
@@
 
-Although both the model and impulse-response matching exercise should be considered as preliminary, we strongly believe they are already able to rationalize empirical results obtained in Section \ref{section:empirics} and convey the main message of this paper.
-Formally, the question we tried to answer is why a contemporaneous technological shock specific to the ICT sector is able to trigger increases in future total factor productivity.
-In other words, why an ICT-investment shock is able to increase productivity of ICT-good users with some lags.
+Although both the model and impulse-response matching exercise should be considered as preliminary, we believe that they are already able to rationalize the empirical results obtained in Section \ref{section:empirics} and thus convey the main message of this paper.
+Formally, the question we tried to answer is why a contemporaneous technological shock specific to the ICT sector is able to trigger increases in future total factor productivity even when it is too small to affect TFP today.
+In other words, why is an ICT-investment shock able to increase the productivity of ICT-good users with lags?
 
 We interpret ICT capital as being the general-purpose technology of the U.S.
-economy over the last $3$ decades.
+economy over the last three decades.
 Specifically, when an ICT technology shock hits the economy, both sectors invest more on ICT capital goods since they are now cheaper to purchase and easier to produce.
-Now, in order to link current higher investment on ICT durable goods to future TFP, we assume that both production functions are augmented by a spillover effect related to the overall stock of ICT capital which is not internalized by the agents.\footnote{This externality is governed by the parameter $\gamma$ which has been estimated via impulse-response matching to be robustly larger than zero.
-Using different empirical results, changing the initial calibration, or the methodology do not qualitative change the estimated value of $\gamma$ close to $0.6$.} These assumptions are mechanically suitable for two main reasons.
-First of all, this spillover enters into the estimated Solow residual since it takes the form of an externality which implies that industries are not paying for this additional benefit.
-Moreover, since this spillover arises from a state variable, it leads to a dynamics where the accumulation of ICT durable goods is a slow process and the benefits of an ICT technology shock show up in the productivity of ICT-capital users with some lags and this effect tends to be persistent.
-
-Although this assumption is mathematically suitable to track empirical impulse responses, we consider important to highlight that this positive externality is sustained by an intuitive and reliable economic intuition which distinguishes the general-purpose nature of ICT capital.
-Since the purpose of ICT goods is to enhance communication, the quality and speed of information sharing is also determined by the overall diffusion of these goods.
+Now, in order to link current higher investment in ICT goods to future TFP, we assume that the general-purpose nature of ICT goods manifests itself in the form of a spillover on both production functions which is not internalized by the agents.\footnote{This externality is governed by the parameter $\gamma$ which has been estimated via impulse-response matching to be robustly larger than zero.} Since the spillover comes from the overall stock of ICT capital, we interpret it as the diffusion of ICT capital.
+
+This assumption is legitimate from a mathematical standpoint for two main reasons.
+First of all, the spillover enters the estimated Solow residual since, being an externality, it is a non-renumerated input.
+Additionally, since the spillover arises from a state variable, it leads to a dynamics where the benefits of an ICT technology shock show up in the productivity of ICT-capital users with some lags because the accumulation of ICT goods is a slow process.
+Thus, the spillover effect only comes into play only gradually once enough ICT capital is being accumulated.
+The slow-moving nature of the state variable capital also means that this effect tends to be persistent, which also helps us match the empirical responses we see in the data.\footnote{We could slow down the dynamics of ICT capital further, for example by assuming investment adjustment costs.
+Obviously, this would improve the fit of the model since it would allow the externality effect to play out even slower.
+Our key point here, however, is to show how the spillover is necessary to match the main features of the empirical responses.
+Without it, the model has no chance to capture the lagged effect of ICT shocks on TFP.}
+
+More importantly, there is important economic intuition underlying our assumption of the spillover.
+Since the purpose of ICT goods is to enhance communication, the quality and speed of information acquisition and sharing is also determined by the overall diffusion of ICT goods.
 As a simple example, assume that in 1995 a scholar decides to purchase a computer with an Internet subscription in order to speed up the acquisition of information.
-She is very satisfied of this investment and does not regret the paid amount.
+She is very satisfied by this investment and does not regret the amount paid.
 However, at the same time, a former colleague who is now working in a different university decides to buy a computer with an Internet subscription as well.
-Once she learns of this development, she also decides to exploit her computer to exchange research material with her former colleague.
-They eventually decide to start a new project together since being in two different universities is not anymore a constraint for the quality of their joint research.
-Both scholars did not pay for this additional benefit since they did not expect to have simultaneously a computer with an Internet subscription.
-However, what is actually happening is that their research production has been boosted by the positive externality that also the other colleague is endowed with the same technology.
-
-As a result, we expect that the nature of ICT capital should display two main features.
-First of all, the effectiveness of an ICT good must be related to its own diffusion as pointed out by the spillover effect.
+Once she learns of this development, the initial researcher decides to henceforth use her computer to exchange research material with her former colleague as well.
+They eventually decide to start a new project together, since being in two different universities is no longer a constraint for their joint research.
+None of the two scholars paid for this additional benefit when they purchased a computer, since they bought it for their personal use and did not expect the other to simultaneously acquire one also.
+What is actually happening here is that the research production of both researchers has been boosted by the positive externality that also the other colleague is endowed with the same technology.
+This externality is what we understand under the general-purpose nature of ICT goods and what our model captures with the assumption of the spillover.
+
+The impulse response matching exercise of Section \ref{section:IRmatching} shows that a two-sector model featuring ICT capital and hard capital can only successfully match the empirical responses to an ICT shock if indeed the spillover effect is in action.
+Thus the main takeaway of this paper is that the interpretation of ICT as a general-purpose technology of the US between 1989-2017 is a good explanation of medium-run TFP growth dynamics.
+This relies on understanding the general-purpose nature of ICT goods as the extent to which their diffusion in the economy matters.
+
+%As a result, we expect that ICT capital should display two main features.
+First of all, the effectiveness of an ICT good must be related to its own diffusion as captured by the spillover effect.
 Moreover, the cost of ICT items should not initially reflect an unexpected increase in their diffusion as pointed out by the assumption that the first feature is not internalized.
@@
 
+In this paper, we look at the effect of ICT shocks on medium-run TFP from both an empirical and a theoretical perspective.
 In the first part of the paper, we investigate the effect of technological shocks specific to the ICT sector on future TFP.
@@
 data from 1989, we impose two identifying restrictions to correctly identify ICT shocks: (i) they must be orthogonal to current productivity and (ii) maximize the impact response of ICT investment.
-In response to an ICT shock, ICT investment increases on impact and stays significant for more than 10 years; relative prices persistently decline as an additional support to the reliability of our identification strategy; and TFP rises after three quarters and remains significant for more than 10-years.
-In addition, variance decomposition analysis suggests that the quantitative impact of ICT shocks on TFP is economically remarkable since they explain about one third of the overall TFP fluctuations over a 10-year horizon.
-
-In order to check whether our identification assumptions may confound our shock with a news shock which contemporaneously boosts ICT investment, we provide a series of different identification strategies which deliver analogous results.
-Our main robustness check is a sequential identification of news shocks first and then ICT shocks which encouragingly does not affect estimates.
-We view this as confirmation of the causality relation which goes from current ICT investment to future TFP.
-
-In the second part of the paper, we rationalize our empirical results by analyze a two-sector DSGE model \`a la \cite{greenwood1997long} augmented by two main assumptions: (i) the sector with the faster technological improvement produces specifically ICT capital, and (ii) both production functions are augmented with a spillover related to the overall level of ICT capital which is not internalized by the agents.
-In particular, this last assumption points out our interpretation of the general-purpose nature of ICT capital: the effectiveness of ICT capital is enhanced by its diffusion and its cost does not reflect this indirect benefit.
+In response to an ICT shock, ICT investment increases on impact and stays significant for more than 10 years; relative prices persistently decline as an additional support for the reliability of our identification strategy; and TFP rises after three quarters and remains significant for more than 10-years.
+In addition, variance decomposition analysis suggests that the quantitative impact of ICT shocks on TFP is economically significant since they explain about one third of the overall TFP fluctuations over a 10-year horizon.
+
+In order to check whether our identification assumptions may confound our shock with a news shock which contemporaneously boosts ICT investment, we provide a series of different identification strategies and show that they deliver analogous results.
+Our main robustness check is a sequential identification of news shocks first and then ICT shocks.
+Encouragingly, neither this, nor any other robustness check affects our initial estimates.
+We view this as a confirmation of the causality relation which goes from current ICT investment to future TFP.
+
+In the second part of the paper, we dig deeper into the nature of the link between current ICT investment and future TFP.
+We rationalize our empirical results by analyzing a two-sector DSGE model \`a la \cite{greenwood1997long} augmented by two main assumptions: (i) the sector with the faster technological improvement produces specifically ICT capital, and (ii) both production functions are augmented with a spillover related to the overall level of ICT capital which is not internalized by the agents.
+In particular, this last assumption points out our interpretation of the general-purpose nature of ICT capital: the effectiveness of ICT capital is enhanced by its diffusion, and the cost of ICT goods does not reflect this indirect benefit.
 We use both empirical and theoretical results to estimate main parameters of the model via impulse-response matching to an ICT technology shock.
-Results point out that the parameter which governs the size of the spillover effect is positive and large, suggesting that our interpretation of the general-purpose nature of ICT capital is confirmed by the data.
+Results show that the parameter which governs the size of the spillover effect is positive and large, suggesting that our interpretation of the general-purpose nature of ICT capital is confirmed by the data.
+Thus, our investigation suggests not only that ICT is an important driver of medium-run TFP, but specifically that what matters for the evolution of TFP is whether ICT can act as a general-purpose technology.
+In particular, large externalities from using ICT goods can explain why a sector comprising a tiny fraction of both output and investment can play an important role for future productivity developments.
 

### 2018-07-30 Latex/Draft_Summer2018/Summer2018.tex
reading the whole paper

@@
 Although there is large consensus on the importance of productivity as a driver of economic performance, there is less agreement on the underlying sources of productivity growth.
-For several years most of the business-cycle literature purposely decided to avoid such a question by proxying movements in productivity as exogenous shocks.\footnote{\cite{kydland1982time} and \cite{long1983real} are among the first papers which consider productivity shocks on general equilibrium models.} However, the robust empirical evidence of the slowdown in productivity right before the Great Recession has led recent literature to take a step back and devote more attention to the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
+For several years, much of the business-cycle literature decided to avoid such questions by proxying movements in productivity by exogenous shocks.\footnote{\cite{kydland1982time} and \cite{long1983real} are among the first papers which consider productivity shocks in general equilibrium models.} However, the robust empirical evidence of the slowdown in productivity right before the Great Recession has led recent literature to take a step back and devote more attention to the drivers of medium-term productivity growth.\footnote{See \cite{cette2016pre} and \cite{byrne2016does} among others.}
 
@@
 Following \cite{romer1990endogenous}, most of these papers augment final-good production functions with an expanding composite of intermediate goods invented by the Research \& Development (R\&D) sector in order to allow for an endogenous rate of adoption of new technologies.\footnote{\cite{bianchi2014growth}, \cite{anzoategui2016endogenous}, and \cite{moran2017innovation} use similar techniques to endogenize growth.
-In particular, \cite{bianchi2014growth} augment a DSGE  model using a quality ladders model in the vein of \cite{grossman1991quality}.
-Moreover, \cite{anzoategui2016endogenous} and \cite{moran2017innovation}, similarly to \cite{comin2006medium}, use a model of expanding variety in the vein of \cite{romer1990endogenous}.} Guided by the prediction of such theoretical work that R\&D developments matter for growth, other papers attempt to provide empirical evidence of a slowdown in the productivity of the R\&D sector.
-Specifically, they show that although research effort keeps rising, the rate of new ideas and discoveries is slowing down.\footnote{\cite{jones2009burden} and \cite{bloom2017ideas} are two important contributions that highlight these facts.}
+\cite{bianchi2014growth} augment a DSGE  model using a quality ladders model in the vein of \cite{grossman1991quality}.
+\cite{anzoategui2016endogenous} and \cite{moran2017innovation}, similarly to \cite{comin2006medium}, use a model of expanding variety \`a la \cite{romer1990endogenous}.} Guided by the prediction of such theoretical work that R\&D developments matter for growth, other papers attempt to provide empirical evidence of a slowdown in the productivity of the R\&D sector.
+Specifically, they show that although research effort keeps rising, the rate of new ideas and discoveries is slowing down.\footnote{\cite{jones2009burden} and \cite{bloom2017ideas} are two contributions that highlight these facts.}
 
@@
 First, we provide robust empirical evidence to show that current rises in ICT investment explain significant and persistent increases in future Total Factor Productivity (hereafter TFP).
-Second, we analyze a standard theoretical framework in order to both rationalize and draw conclusions from our empirical results.
+Second, we analyze a standard theoretical framework in order to both rationalize our empirical results and to draw conclusions concerning the nature of the ICT contribution to future productivity.
 
@@
 The authors identify ICT shocks as a potential driver of the Iranian business cycle using a completely different identification strategy and obtaining qualitatively different results.} Our multivariate system includes three key variables: TFP, ICT investment (hereafter ICTI), and relative prices (hereafter RP).
-ICTI is defined as the total expenditure in equipment and computer software meant to be used in production for more than an year.
+ICTI is defined as the total expenditure in equipment and computer software meant to be used in production for more than a year.
 Thus, an increase in ICTI is ICT capital deepening.
@@
 First, we expect it to be orthogonal to the current productivity of all the other sectors.
-Since the share of the ICT sector accounts for a negligible part in the whole economy, ICT shocks should have an approximately zero effect on TFP on impact.
+Since the share of the ICT sector accounts for a negligible part of the whole economy, ICT shocks should have an approximately zero effect on TFP on impact.
 Thus, our first restriction will be a zero-impact restriction on TFP after an ICT shock.
-Moreover, following \cite{greenwood1997long} and \cite{fisher2006dynamic}, we rely on RP and ICTI because we expect that a sectoral technology shock should decrease its relative prices and enhance expenditure in the underlying sector.
-For theoretical reasons discussed in more detail below, we do not impose any restriction on RP; instead, we let the ICT shock maximize the impact response of ICTI.\footnote{However, as suggested by both \cite{greenwood2000role} and \cite{basu2010sector}, we are aware that conditioning our identifying restrictions only on the direction of RP does not properly measure for technological changes between sectors.
-This is the main reason why we never impose the direction of RP as an direct identifying condition.} In response to this shock, ICTI rises on impact and remains significant for several quarters.
+Moreover, following \cite{greenwood1997long} and \cite{fisher2006dynamic}, we rely on RP and ICTI because we expect that a sectoral technology shock should decrease the relative prices of the sector while enhancing expenditure in the underlying sector.
+For theoretical reasons discussed in more detail below, we do not impose any restriction on RP; instead, we let the ICT shock maximize the impact response of ICTI.\footnote{As pointed out by both \cite{greenwood2000role} and \cite{basu2010sector}, letting the the direction of RP be the sole identifying restriction does not properly capture technological changes between sectors.
+This is the main reason why we do not impose the direction of RP as a direct identifying condition.
+While our main robustness check uses RP, also there we refrain from considering the direction of the RP response.
+See Section \ref{section:twosteps}.} In response to this shock, ICTI rises on impact and remains significant for several quarters.
 RP persistently and significantly declines for more than two years, suggesting that we are indeed identifying the correct sectoral shock.
 Our main result is that TFP, restricted not to respond on impact, rises after few quarters and remains significant and stable for at least 5 years, despite the tiny size of the ICT sector relative to the economy.
-Finally, variance decomposition analysis suggests that ICT shocks explains a remarkable size of economic fluctuations over the medium and long run.
+Finally, variance decomposition analysis suggests that ICT shocks explain a remarkable size of economic fluctuations over the medium and long run.
 These shocks drive about $40$\% and $33$\% of the overall GDP and TFP fluctuations over a 10-year horizon, respectively.
 
-Although our results are robust over different specifications, an important critique to our empirical strategy is reverse causality coming from news on future TFP.
+Although our results are robust over different specifications, a critique to our empirical strategy is reverse causality coming from news on future TFP.
 As suggested by the news-shock literature, the positive reaction of ICTI on impact may be triggered by signals related future increases in TFP and not to contemporaneous ICT technological improvements.
@@
 We address this issue by providing a series of alternative identification strategies which we show deliver the same time series of ICT innovations as our initial specification.
-The heart of these robustness checks is sequential identification of news and ICT shocks: we firstly identify a news shock in the spirit of \cite{barsky2011news}, and subsequently we identify our sectoral ICT shock using the previous identification strategy.
+The heart of these robustness checks is sequential identification of news and ICT shocks: we first identify a news shock in the spirit of \cite{barsky2011news}, and subsequently we identify our sectoral ICT shock using the previous identification strategy.
 Encouragingly, controlling for signals regarding future movements in TFP does not affect our results.
@@
 
-In order to understand the economics behind our empirical results, we then analyze a two-sector DSGE model which allows ICT to be the general purpose technology (hereafter GPT) of the whole economy.
+In order to understand the economics behind our empirical results, we then analyze a two-sector DSGE model which allows ICT to be the general-purpose technology (hereafter GPT) of the whole economy.
 There are two main justifications for interpreting ICT as a GPT.
-On the one hand, there is a vast literature that makes a case for the general-purpose nature of ICT capital.\footnote{See for example \cite{oliner2000resurgence} and \cite{stiroh2002information} amongst others.} On the other hand, the small size of the share of the ICT sector both in overall investment and overall output makes our results of a strong and persistent TFP increase after an ICT shock hard to interpret in absence of an additional force such as an externality coming from the general-purpose property of ICT capital.
+On the one hand, there is a vast literature that makes a case for the general-purpose nature of ICT capital.\footnote{See for example \cite{oliner2000resurgence} and \cite{stiroh2002information} amongst others.} On the other hand, the tiny share of the ICT sector both in overall investment and overall output makes our results of a strong and persistent TFP increase after an ICT shock hard to interpret in absence of an additional force such as an externality coming from the general-purpose property of ICT capital.
 
@@
 
-Since the purpose of ICT capital is to improve information sharing, the quality and speed of communication mainly depends on the diffusion of these technologies among agents.
+What is the intuition behind our assumption of ICT as a GPT showing up in the economy as a spillover?
+To better understand this externality assumption, consider the special nature of ICT capital.
+Since the purpose of ICT capital is to improve information acquisition and sharing, the quality and speed of communication fundamentally depends on the diffusion of these technologies among agents.
 As a simple example, owning a mobile phone enables one to contact another person instantaneously only if the other person is also endowed with the same technology.
@@
 
-As a last step, we use both our empirical and theoretical results to estimate the key parameters of the model via impulse-response function matching to an ICT technology shock.
-The key parameters within this set are (i) the elasticity of productivity to ICT capital diffusion, namely the parameter which governs the spillover effect, and (ii) the standard deviation and (iii) persistence of ICT technology shocks.
-Results consistently point out a positive spillover effect of ICT capital deepening on TFP, confirming that within this class of theoretical models, data supports the existence of spillovers from ICT capital.
+As a last step, we use both our empirical and theoretical results to estimate the key parameters of the model via impulse-response matching to an ICT technology shock.
+The key parameters are (i) the elasticity of productivity to ICT capital diffusion, namely the parameter which governs the spillover effect, and (ii) the standard deviation and (iii) persistence of ICT technology shocks.
+Results consistently obtain a positive spillover effect of ICT capital deepening on TFP, confirming that within this class of theoretical models, data supports the existence of spillovers from ICT capital.
 Thus, our theoretical model suggests to interpret the responses obtained in the empirical section in light of ICT as a general-purpose technology which enhances productivity of ICT capital users through a spillover effect related to its own diffusion.
@@
 We estimate via impulse-response matching key parameters of the model and assess its empirical reliability in Section \ref{section:model_assessment}.
-Concluding remarks are discussed in Section \ref{section:conclusions}.
+Section \ref{section:conclusions} concludes.
 
@@
 In this section we present our main empirical results.
-Our attempt is to properly identify technological shocks which are specific to the ICT sector in a Structural VAR context and analyze their impact on key macroeconomic variables.
+Our attempt is to properly identify technological shocks which are specific to the ICT sector in a Structural VAR context and to analyze their impact on key macroeconomic variables.
 
@@
 
-We start by illustrating our main specification where we impose minimal discipline on the identification strategy.
-In subsequent sections, we try vastly different alternative empirical strategies.
+We start by illustrating our main specification where we impose minimal discipline on the model.
+In subsequent sections, we try vastly different empirical strategies.
 It turns out that the set of results presented here are consistent with the different robustness checks.
@@
 
-Our first-step specification is the following 5-variable VAR 
+Our first-step specification is the following five-variable VAR 
 \begin{equation}\label{eq:mainSpecification}
@@
 \end{equation}
-where $TFP_t$ is the log-level of Fernald total factor productivity at time $t$, $ICTI_{t}$ is the log-level of real information and communication technology investment at time $t$,\footnote{$ICTI_t$ is defined as the total expenditure at time $t$ in equipment and computer software meant to be used in production for more than an year.} $GDP_t$ is the log-level of real gross domestic product at time $t$, $C_t$ is the log-level of real consumption at time $t$, and $RP_t$ is the log-deviation of the ratio between prices of ICT goods and services and the consumer price index (CPI).\footnote{Except for $RP_t$ that is not cointegrated with the remaining variables, we opt for estimating the VAR in levels since it produces consistent estimates of the impulse responses and is robust to cointegration of unknown forms.
-In particular, as suggested by \cite{hamilton1994time} when there is uncertainty regarding the nature of common trends, estimating the system in levels is considered the conservative approach.
-The alternative approach is to estimate the system as a vector error correction model (VECM); our results remain very similar also in this case.} Our dataset is quarterly and covers the U.S.
+where $TFP_t$ is the log-level of Fernald total factor productivity at time $t$, $ICTI_{t}$ is the log-level of real information and communication technology investment at time $t$,\footnote{$ICTI_t$ is defined as the total expenditure at time $t$ in equipment and computer software meant to be used in production for more than a year.} $GDP_t$ is the log-level of real gross domestic product at time $t$, $C_t$ is the log-level of real consumption at time $t$, and $RP_t$ is the log-deviation of the ratio between prices of ICT goods and services and the consumer price index (CPI).\footnote{Except for $RP_t$, which is not cointegrated with the remaining variables, we opt for estimating the VAR in levels since this produces consistent estimates of the impulse responses and is robust to cointegration of unknown forms.
+In particular, as suggested by \cite{hamilton1994time}, when there is uncertainty regarding the nature of common trends, estimating the system in levels is considered the conservative approach.
+The alternative approach is to estimate the system as a vector error correction model (VECM); our results remain very similar also in this case.} \footnote{Using the PCE deflator instead of the CPI yields similar results.} Our dataset is quarterly and covers the U.S.
 economy from 1989:Q1 to 2017:Q1.\footnote{All data are from the BEA except for TFP, which is the series constructed by John Fernald, available on his website.} $B(L)$ is a ($5\times 5$) matrix of lag-operator functions of the same order.
@@
 
-Our simplest identification strategy assumes that an ICT-investment technological shock (hereafter ICT shock) has no impact effect on TFP and maximal impact effect on ICTI.
+Our simplest identification strategy assumes that an ICT technological shock (hereafter ICT shock) has no impact effect on TFP and maximal impact effect on ICTI.
 We justify these assumptions with both empirical and theoretical arguments.

### 2018-07-30 Latex/Draft_Summer2018/Summer2018.tex
more reading

@@
 We justify these assumptions with both empirical and theoretical arguments.
-First of all, using data released in April, 2018 by the Bureau of Economic Analysis (BEA) the real value added of the information sector on real GDP is slightly below $5$\% for the underlying quarter.\footnote{There are many ways to quantify the size of the ICT sector, both in terms of what share one considers and how one defines the ICT sector.
-The number presented in the text refers to the value added share of the ICT sector, defined as in Section \ref{eq:mainSpecification}.
+First of all, as data released in April, 2018 by the Bureau of Economic Analysis (BEA) shows, the real value added of the information sector on real GDP is slightly below $5$\% for the underlying quarter.\footnote{There are many ways to quantify the size of the ICT sector, both in terms of what share one considers and how one defines the ICT sector.
+The number in the text refers to the value added share of the ICT sector, defined as in Section \ref{eq:mainSpecification}.
 The statement that the ICT sector is tiny is however not sensitive to the definition of the sector or to the choice of share.
-Even with broader definitions, one obtains numbers in the range of 5\%.} Thus, since the share of this sector accounts for a negligible part in the whole economy, we think it safe to assume that an ICT shock is orthogonal to current TFP.
-In addition, the theory of multi-sector models, firstly presented by \cite{greenwood1997long}, predicts that a productivity increase in one sector should lead to sectoral output becoming cheaper.
-Thus, we expect that an ICT shock should enhance sector-specific investment since ICT goods are now easier to produce and cheaper to buy.
+Even with broader definitions, one obtains numbers in the range of 5\%.} Thus, since the ICT sector accounts for a negligible part of the whole economy, we think it safe to assume that an ICT shock is orthogonal to current TFP.
+
+In addition, the theory of multi-sector models, as presented by \cite{greenwood1997long}, predicts that a productivity increase in one sector should lead to sectoral output becoming cheaper.
+Thus, we expect that an ICT shock should enhance sector-specific investment since ICT goods are less costly to produce and to buy.
 As a result, we expect an ICT shock to have a maximal impact effect on ICTI.
@@
 Appendix \ref{section:mainSetResults} shows the estimated impulse responses of System \ref{eq:mainSpecification} to the identified ICT shock.
-The shaded gray areas are the $90$\% and $95$\% confidence bands from a bias-corrected bootstrap procedure of \cite{kilian1998small} using 2000 simulations.
+The shaded gray areas are the $90$\% and $95$\% confidence bands from the bias-corrected bootstrap procedure of \cite{kilian1998small} using 2000 simulations.
 Our main interest, Figure \ref{fig:TFP_main}, shows the impulse response of TFP to an ICT shock.
@@
 In Figure \ref{fig:ICT_main}, real ICT investment has a large and positive impact response of almost $2$\% that gets even larger after a quarter.
-Then, it slowly starts to decay remaining significant for more than $40$ quarters.
+Then, it slowly starts to decay, remaining significant for more than $40$ quarters.
 In Figures \ref{fig:GDP_main} and \ref{fig:C_main}, we present responses of real GDP and real consumption, respectively.
@@
 These results are very interesting in their own right, as they hint that the ICT sector may have a particular role for the overall productivity of the economy.
-
 In line with the impulse responses, ICT shocks, which are orthogonal to current productivity, explain nothing of current TFP fluctuations.
@@
 Interestingly, both output and consumption have a remarkable reaction on impact: $26$\% and $19$\%, respectively.
-Moreover, this effect tends to increase reaching $40$\% in both cases at the maximal horizon.
+Moreover, this effect tends to increase, reaching $40$\% in both cases at the maximal horizon.
 Finally, ICT shocks only account for a small fraction of movements in relative prices.
 The fraction of fluctuations explained on impact is only $6$\% with a peak of $14$\% between four and six years.
-Overall, these variance decompositions all seem to suggest that the ICT shock leads to complex forms of reallocation and accumulation that take place over the medium run in the economy.
+Overall, these variance decompositions all seem to suggest that the ICT shock leads to complex forms of reallocation and accumulation that take place over the medium run in the economy and that seem to result in productivity growth.
 Our structural model of Section \ref{section:theory} provides a theoretical framework to think about these dynamics and to give them an economic interpretation.
@@
 
-Our second test is running a VAR in which we identify both ICT shocks and news shocks.
+Our second and main robustness test is running a VAR in which we identify both ICT shocks and news shocks.
 In particular, we apply a sequential identification where we first identify a news shock in the spirit of \cite{barsky2011news}, and subsequently we identify our sectoral ICT shock using our original identification strategy.
-This second strategy has the specific purpose of filtering out all the current movements in forward-looking variables related to future fluctuations of TFP which are not related to current ICT shocks, as such fluctuations are all captured by the identified news shock.
+This second strategy has the specific purpose of directly filtering out all the current movements in forward-looking variables related to future fluctuations of TFP which are not related to current ICT shocks, as such fluctuations are all captured by the identified news shock.
 
@@
 
-In this part of the paper, we employ a first-pass test of whether our ICT shock may be confounded with future signals of TFP unrelated to the ICT sector.
-
-As discussed by \cite{sims2012news}, \cite{forni2014sufficient}, and \cite{barsky2015whither} the presence of forward-looking variables in the VAR is a necessary condition to correctly identify a news shock.
-In particular, since the univariate TFP process cannot predict its own future values,\footnote{It is well-accepted that TFP growth can be approximated as a white noise process, or, equivalently, that the TFP level process is a random walk.} a news shock can only be identified if there are variables that Granger-cause TFP inside the VAR.
+We now show our first-pass test in detail.
+As discussed by \cite{sims2012news}, \cite{forni2014sufficient} and \cite{barsky2015whither}, the presence of forward-looking variables in the VAR is a necessary condition to correctly identify a news shock.
+In particular, since the univariate TFP process cannot predict its own future values,\footnote{It is well-accepted that TFP growth can be approximated as a white noise process.} a news shock can only be identified if there are variables that Granger-cause TFP inside the VAR.
 For example, \cite{beaudry2006stock} use current movements in stock prices to predict future productivity, but also contemporary fluctuations in consumption, hours, investment, may implicitly reflect information regarding future technical change.
 
-Thus, as a simple test we redo the exercise described in Section \ref{section:mainSpec}, omitting the two forward-looking macroeconomic variables not directly related with the ICT sector: consumption and output.\footnote{Notice that output implicitly reflects the behavior of hours and investment once we control for consumption.} If we are actually confounding news shocks with our ICT shock series then we would expect to see some differences in this second estimate, because absent the two forward-looking variables, our VAR is deprived of a source of information useful to recover a news shock and should thus no longer be able to capture it appropriately.
+Thus, as a simple test, we redo the exercise described in Section \ref{section:mainSpec}, omitting the two forward-looking macroeconomic variables not directly related with the ICT sector: consumption and output.\footnote{Note that output implicitly reflects the behavior of hours and investment once we control for consumption.} If we are actually confounding news shocks with our ICT shock series then we would expect to see some differences in this second estimate, because absent the two forward-looking variables, our VAR is deprived of a source of information useful to recover a news shock and should thus no longer be able to capture it appropriately.
 
@@
 Using the same identification strategy presented in \ref{section:empiricalstrategy_simple}, we recover a series of ICT shocks.
-The newly recovered series is correlated at $95$\% with the one estimated in five-dimensional system, indicating that our main specification is not contaminated by news.
+The newly recovered series is correlated at $95$\% with the one estimated in the five-dimensional system, indicating that our main specification is not contaminated by news.
 Figure \ref{fig:shockSeries_removing} in Appendix \ref{section:removing_FL_Var} shows the ICT shock series for both the three-dimensional system and the five-dimensional one.
@@
 In this case, ICTI would be itself the source to Granger-cause TFP and our ICT shock would be upward biased by news.
-To address this deeper concern, we proceed to employ a more complicated strategy aimed at directly capturing, and filtering out news.
+To address this deeper concern, we proceed to employ a more complicated strategy aimed at directly capturing and filtering out news.
 
@@
 
-In this part, we present an alternative procedure to rule out the presence of news from our recovered ICT shock.
+We now turn to an alternative procedure to rule out the presence of news from our recovered ICT shock.
 In this second test we run a VAR where we identify both ICT shocks and news shocks.
-In contrast to our first-pass test, this test aims to directly identify and filter out future signals unrelated to current ICT shocks.
+In contrast to our first-pass test, this approach aims to directly identify and filter out future signals unrelated to current ICT shocks.
 
@@
 
+\hspace{9cm} \cite{barsky2011news}, p. 278.
+
+\vspace{0.5cm}
+
 In other words, by naively employing the procedure presented above, any ICT shock would be interpreted as a news shock since it is orthogonal to current TFP and explains its future movements.
@@
 However, this restriction would obviously penalize the identification of news shocks since it is unlikely that assumptions (i) and (ii) perfectly hold in the data.
-We therefore opt for a more moderate strategy where we impose that the response of relative prices to a news shock should be smaller than the response following an ICT shock.
-Practically speaking, we arbitrarily set the impulse response of relative prices to news to be zero on some specific horizons rather than at all horizons.
+We therefore opt for a more moderate strategy where we impose that the impulse response of relative prices to news should be zero on some specific horizons rather than at all horizons.
 While results are robust to different horizon restrictions, our favorite specification is the one which sets relative prices to have zero response in the first three periods.
@@
 Motivated by Proposition \ref{prop:priceRestriction}, we augment our initial VAR system with stock prices, SP.
-As discussed above, SP is added in order to provide an additional forward-looking variable to the system.\footnote{The presence of forward-looking variables in the VAR is a necessary condition to correctly identify a news shock.
-For more details on this discussion, see \cite{sims2012news}, \cite{forni2014sufficient}, and \cite{barsky2015whither}.} Thus, our current specification is the following six-variable VAR,
+As discussed above, SP is added in order to provide an additional forward-looking variable to the system.
+Thus, our current specification is the following six-variable VAR,
 \begin{equation}\label{eq:newsSpecification}
@@
 $SP_t$ represents the log-transformation of Standard \& Poor's 500 stock price index.
-As before, dataset is quarterly and covers the U.S.
-economy from 1989:Q1 to 2017:Q1 and following the BIC and HQ criteria we opt for one lag.
+As before, the dataset is quarterly and covers the U.S.
+economy from 1989:Q1 to 2017:Q1 and following the BIC and HQ criteria we choose one lag.
 
@@
 
-Using the notation of Section \ref{section:empiricalstrategy_simple}, assume for simplicity that $B(L) = B$ allows only for one lag.
+Using the notation of Section \ref{section:empiricalstrategy_simple}, assume for simplicity that $B(L) = B$ allows for only one lag.
 Define the impulse response of variable $i$ to the identified shock $j$ at time $t$ as,\footnote{We also suppress the constant to simplify the notation.
@@
 where the first constraint represents the zero-impact restriction of news on TFP.
-The second constraint is the restriction derived from Proposition \ref{prop:priceRestriction} to have the response of relative prices to news relatively small.\footnote{Our identification strategy is robust over different restrictions to relative prices.
-Results hold even if we set the zero restriction on other horizons.} Finally, the last constraint imposes that $\gamma_{news}$ should be a column derived from the orthogonal matrix $D$.
+The second constraint is the restriction derived from Proposition \ref{prop:priceRestriction} to have the response of relative prices to news relatively small.\footnote{Our identification strategy is robust to different restrictions to relative prices.
+Results hold if we set the zero restriction on other horizons.} Finally, the last constraint imposes that $\gamma_{news}$ should be a column derived from the orthogonal matrix $D$.
 
@@
 Figures \ref{fig:2stepIRF_first} and \ref{fig:2stepIRF_second} in Appendix \ref{section:IRF_2step} show estimated impulse responses to both news and ICT shocks.
-Figure \ref{fig:2stepIRF_first} focuses on the responses of TFP, stock prices, and ICT investment , while Figure \ref{fig:2stepIRF_second} shows the responses of GDP, consumption and relative prices.
+Figure \ref{fig:2stepIRF_first} focuses on the responses of TFP, stock prices, and ICT investment, while Figure \ref{fig:2stepIRF_second} shows the responses of GDP, consumption and relative prices.
 The shaded gray areas are the $90$\% and $95$\% confidence bands from the bias-corrected bootstrap procedure of \cite{kilian1998small} using 2000 simulations.
@@
 
-In addition, we show the impulse responses to a news shock to confirm that our identification strategy is picking up news shocks correctly.
-As the responses show, constraining the response of relative prices to news does not qualitatively affect the behavior of news shocks.
-Our identified news shock generates responses broadly in line with those found by the news shock literature.
+In addition, we show the impulse responses to a news shock to confirm that our identification strategy is picking up news shocks correctly (left panel of the same figures).
+As the figures depict, constraining the response of relative prices to news does not qualitatively affect the behavior of news shocks; our identified news shock generates responses broadly in line with those found by the news shock literature.
 In particular, in line with \cite{barsky2011news}, it takes more that 2 years after the news shock for TFP to display a positive, significant and strongly persistent effect.
 Stock prices have a strong forecasting power and show a $4$\% impact effect which is persistent and significant in the long run.
-Real ICT investment does not show a positive impact response but it slowly starts to increase getting significant after almost $2$ years.
-As found by \cite{barsky2011news} in their main specification, real GDP has a non-significant impact effect, but it rises fast with all the variables of the system.
+Real ICT investment does not show a positive impact response but it slowly starts to increase, getting significant after almost $2$ years.
+As found by \cite{barsky2011news} in their main specification, real GDP has an insignificant impact effect, but it rises fast with all the variables of the system.
 Moreover, as was expected, considering the forward-looking nature of consumption, real consumption has a significant impact response and reaches its peak once the TFP response becomes significant.

### 2018-07-30 Latex/Draft_Summer2018/Summer2018.tex
more reading

@@
 In this section, we present a simple two-sector model that rationalizes our structural VAR estimates.
-
-% Need to add something here that says that we investigate whether a spillover can explain things.
+We also attempt to give an economic explanation for why a sector that accounts for a minuscule fraction of the entire economy can give rise to medium-run responses of the magnitude we documented in the previous section.
+As discussed below in more detail, we therefore entertain the possibility that there are spillover effects coming from the stock of ICT capital, and we confront the model with data to see if this explanation can be supported empirically.
 
@@
 First of all, we focus specifically on the ICT capital sector, rather than equipment, as the sector with faster technological improvement.
-This assumption will be necessary if we want to fit the fact that relative prices between ICT investment and the overall economy display a downward sloping trend.\footnote{In addition, we also rely on the results of \cite{whelan2003two} and \cite{oulton2007investment} to correctly define productivity and output share in our setting.} A second difference is that we consider two production functions - one for each sector.
+This assumption will be necessary if we want to fit the fact that relative prices between ICT investment and the overall economy display a downward sloping trend.
+A second difference is that we consider two production functions - one for each sector.
 As \cite{oulton2007investment} shows, the two formulations are isomorphic, so our modeling choice has no implication for the resulting dynamics.
-The reason we choose this approach is because it allows for definitions of GDP and TFP in the model that are consistent with the way these variables are constructed in the national income accounts.
-Finally, we assume that the total ICT capital stock has a positive spillover effect on the production function of both sectors.
+The reason we choose this approach is because it allows for definitions of GDP and TFP in the model that are consistent with the way these variables are constructed in the national income accounts.\footnote{See also \cite{whelan2003two}.} Finally, and crucially, we assume that the total ICT capital stock has a positive spillover effect on the production function of both sectors.
+
+What considerations lead us to augment both production functions with a spillover from ICT capital?
+First of all, the large, significant and persistent impulse responses of aggregates like TFP, GDP and consumption to an ICT shock are hard to square with the fact that the ICT sectoral share is less than 5\%.
+This seems to suggest that there is an additional, indirect effect coming from the ICT sector.
+A spillover is a natural way of capturing such an indirect effect.
+
+Secondly, a long line of literature going back to the early 1990s postulates that ICT may be a general-purpose technology.\footnote{\cite{basu2003case}, \cite{basu2007information}, \cite{fernald2017disappointing} and \cite{oliner2000resurgence} and are some examples.} Following the classical definition of \cite{bresnahan1992general}, GPTs are technologies that alter the process of economy-wide production, and thus affect the productivity of the entire economy.
+
 The general-purpose nature of ICT capital works through its own diffusion because information sharing improves only when new communication technologies are widely spread over the population.

### 2018-07-30 Latex/Draft_Summer2018/Summer2018.tex
read through the whole paper
ready to discuss some stuff

@@
 
-Secondly, a long line of literature going back to the early 1990s postulates that ICT may be a general-purpose technology.\footnote{\cite{basu2003case}, \cite{basu2007information}, \cite{fernald2017disappointing} and \cite{oliner2000resurgence} and are some examples.} Following the classical definition of \cite{bresnahan1992general}, GPTs are technologies that alter the process of economy-wide production, and thus affect the productivity of the entire economy.
-
-The general-purpose nature of ICT capital works through its own diffusion because information sharing improves only when new communication technologies are widely spread over the population.
+Secondly, a long line of literature going back to the early 1990s postulates that ICT may be a general-purpose technology.\footnote{\cite{basu2003case}, \cite{basu2007information} and \cite{oliner2000resurgence} and are some examples.} % need to include Brynjolfsson's work here, the all-star paper and the Gordon-Mokyr debate.
+Following the classical definition of BT,
+% Bresnahan Trajtenberg -- need to get citation right
+ GPTs are technologies that alter the process of economy-wide production, and thus affect the productivity of the entire economy.
+This effect can come about  through several channels.
+For example, investment in ICT goods may trigger accumulation of unobserved complementary capital, as suggested by both \cite{basu2003case} and \cite{basu2007information}.
+Conversely, as advocated by Brynjolffson, new ICT goods may change managerial practices, thus affecting the production process.
+We take a broader view in which we simply consider the diffusion of ICT goods to be the crucial element of ICT's general-purpose nature.
+
+To understand what we mean by ICT diffusion, consider again the example of purchasing a mobile phone from the Introduction.
+Clearly, an individual's productivity improves when acquiring a mobile phone, since she gains access to many functionalities she couldn't enjoy previously.
+However, the full productivity boost can only materialize when others also use mobile phones.
+In fact, the more mobile phones there are in the economy, the more productivity gain the individual experiences.
+Thus, the higher the diffusion of ICT, the higher is its effect on productivity.
+This is the effect our spillover assumption means to capture.
+The key exercise, then, of our theoretical model will be to verify via impulse-response matching whether data support the existence of a spillover and thus the hypothesis of ICT as a GPT in the three decades following 1989 in the US economy.
 
@@
 
-Consider an economy inhabited by a representative agent who maximizes the expected values of his lifetime utility as given by
+The household in our economy is completely standard. The economy is inhabited by a representative agent who maximizes the expected value of his lifetime utility as given by
 \begin{eqnarray}\label{equation:utilFunc}
@@
 
-In this section, we estimate the model's key parameters governing the effect of ICT investment on future TFP by imposing theoretical impulse responses of an ICT shock to be as close as possible to the empirical ones.
-To enhance movement in ICT investment, we use a shock to the ICT-specific technological component $\zeta_t$.
+Now we estimate the model's key parameters governing the effect of ICT investment on future TFP by imposing theoretical impulse responses of an ICT shock ($\zeta_t$) to be as close as possible to the empirical ones.
 Using empirical impulse responses of TFP, ICT investment, consumption, and relative prices, we estimate three parameters: the variance of an ICT technology shock, $\sigma_{\iota}^2$, the persistence of the same shock, $\rho_{\iota}$, and the size of the spillover effect of ICT capital on TFP, $\gamma$.
@@
 
-Although both the model and impulse-response matching exercise should be considered as preliminary, we believe that they are already able to rationalize the empirical results obtained in Section \ref{section:empirics} and thus convey the main message of this paper.
+Although both the model and impulse-response matching exercise are simple and preliminary, we believe that they are already able to rationalize the empirical results obtained in Section \ref{section:empirics} and thus convey the main message of this paper.
 Formally, the question we tried to answer is why a contemporaneous technological shock specific to the ICT sector is able to trigger increases in future total factor productivity even when it is too small to affect TFP today.
@@
 Our key point here, however, is to show how the spillover is necessary to match the main features of the empirical responses.
-Without it, the model has no chance to capture the lagged effect of ICT shocks on TFP.}
-
-More importantly, there is important economic intuition underlying our assumption of the spillover.
+Without it, the model has no chance to capture the large lagged effect of ICT shocks on TFP.}
+
+More importantly, there is clear economic intuition underlying our assumption of the spillover.
 Since the purpose of ICT goods is to enhance communication, the quality and speed of information acquisition and sharing is also determined by the overall diffusion of ICT goods.
-As a simple example, assume that in 1995 a scholar decides to purchase a computer with an Internet subscription in order to speed up the acquisition of information.
-She is very satisfied by this investment and does not regret the amount paid.
+As a simple example different from the one in the Introduction, assume that in 1995 a scholar decides to purchase a computer with an Internet subscription in order to speed up the acquisition of information.
+She is very satisfied with this investment and does not regret the amount paid.
 However, at the same time, a former colleague who is now working in a different university decides to buy a computer with an Internet subscription as well.
-Once she learns of this development, the initial researcher decides to henceforth use her computer to exchange research material with her former colleague as well.
+Once she learns of this development, the initial researcher decides to henceforth use her computer to exchange research material with her former colleague.
 They eventually decide to start a new project together, since being in two different universities is no longer a constraint for their joint research.
@@
 In particular, this last assumption points out our interpretation of the general-purpose nature of ICT capital: the effectiveness of ICT capital is enhanced by its diffusion, and the cost of ICT goods does not reflect this indirect benefit.
+
 We use both empirical and theoretical results to estimate main parameters of the model via impulse-response matching to an ICT technology shock.

### 2018-07-30 Latex/Draft_Summer2018/Summer2018.tex
Minor Change
There is a part in the introduction we need to improve. We discuss tomorrow

@@
 Thus, an increase in ICTI is ICT capital deepening.
-RP is the ratio between the price of the ICT good and the price level in the overall economy.
+RP is the ratio between the price level of ICT durable goods and the price level in the overall economy.
 
@@
 Although our results are robust over different specifications, a critique to our empirical strategy is reverse causality coming from news on future TFP.
-As suggested by the news-shock literature, the positive reaction of ICTI on impact may be triggered by signals related future increases in TFP and not to contemporaneous ICT technological improvements.
+As suggested by the news-shock literature, the positive reaction of ICTI on impact may be triggered by signals related to future increases in TFP and not to contemporaneous ICT technological improvements.
 In other words, our identification strategy may confound our shock of interest with a news shock which contemporaneously enhances investment in ICT capital goods.
@@
 economy assuming that exogenous technological changes in the ICT sector are able to affect economy-wide productivity above the direct effect coming from the technology increase itself.\footnote{A clarification is in place here.
-In a two-sector model, the overall residual productivity is a convolution of the two exogenous productivities.
-Thus sectoral productivity changes trivially show up in overall productivity.
-Our assumption of ICT capital being a GPT means that overall productivity responds more to an ICT-sector-specific technology shock than warranted by this shock directly.
+In a two-sector model, total factor productivity is a convolution of the two exogenous productivities.
+Thus sectoral productivity changes trivially show up in TFP as a direct effect.
+Our assumption of ICT capital being a GPT means that overall productivity responds much more to an ICT-sector-specific technology shock than warranted by this shock directly.
 We address this question in detail in the main text in Section \ref{section:empirics}.} In particular, when an ICT technology shock arrives, both sectors accumulate ICT capital since it is easier to produce and cheaper to buy.
@@
 
-Our simplest identification strategy assumes that an ICT technological shock (hereafter ICT shock) has no impact effect on TFP and maximal impact effect on ICTI.
-We justify these assumptions with both empirical and theoretical arguments.
+Our simplest identification strategy assumes that an ICT technological shock (hereafter ICT shock) has (i) no impact effect on TFP and (ii) maximal impact effect on ICTI.
+We justify these two assumptions with both empirical and theoretical arguments.
 First of all, as data released in April, 2018 by the Bureau of Economic Analysis (BEA) shows, the real value added of the information sector on real GDP is slightly below $5$\% for the underlying quarter.\footnote{There are many ways to quantify the size of the ICT sector, both in terms of what share one considers and how one defines the ICT sector.
@@
 The statement that the ICT sector is tiny is however not sensitive to the definition of the sector or to the choice of share.
-Even with broader definitions, one obtains numbers in the range of 5\%.} Thus, since the ICT sector accounts for a negligible part of the whole economy, we think it safe to assume that an ICT shock is orthogonal to current TFP.
+Even with broader definitions, one obtains numbers in the range of 5\%.} Thus, since the ICT sector accounts for a negligible part of the whole economy, we think it is safe to assume that an ICT shock is orthogonal to current TFP.
 
@@
 
-\subsubsection{Removing Forward-Looking Variables}
+\subsubsection{Removing Forward-Looking Variables}\label{sec:removing}
 
@@
 Proposition \ref{prop:priceRestriction} implies that an anticipated future sector-neutral technological change (the so-called news shock) never affects relative prices between sectors.
-Obviously, this statement is correct under the extreme assumptions that (i) the shock is expected to have the same impact on the two sectors and (ii) production functions are identical.
+Obviously, this statement is correct under the extreme assumptions that (i) the shock is expected to have the same impact on the two sectors and (ii) production functions have identical input shares.
 If those assumptions hold in the data, then the correct additional restriction would be to  restrict the impulse response of relative prices to a news shock to hard zero at all horizons.
@@
 
-Motivated by Proposition \ref{prop:priceRestriction}, we augment our initial VAR system with stock prices, SP.
-As discussed above, SP is added in order to provide an additional forward-looking variable to the system.
+Motivated by Section \ref{sec:removing}, we augment our initial VAR system with stock prices in order to provide an additional forward-looking variable to the system.
 Thus, our current specification is the following six-variable VAR,

### 2018-07-31 Latex/Draft_Summer2018/Summer2018.tex
minor changes

@@
 
-Table \ref{table:estimated_parameters} shows results of Problem \ref{equation:min_prob_IRmatching}.
+Table \ref{table:estimated_parameters} in Appendix \ref{sec:appendix_table_IRmatching} shows results of Problem \ref{equation:min_prob_IRmatching}.
 The estimate of the spillover effect of ICT capital on TFP, $\gamma$, is $0.58$, while estimates of variance and persistence of an ICT-specific technological shock $\sigma^2_{\iota}$ and $\rho_{\iota}$ are $0.01$ and $0.9$ respectively.\footnote{Estimated parameter values are strongly robust to various alternative specifications.
@@
 
-Using the estimated parameter values in Table \ref{table:estimated_parameters}, Figure \ref{fig:IR_matching} displays empirical impulse responses along with theoretical ones.
+Using the estimated parameter values in Table \ref{table:estimated_parameters}, Figure \ref{fig:IR_matching} in Appendix \ref{section:appendix_IR_matching} displays empirical impulse responses along with theoretical ones.
 Our simple model is able to mimic empirical movements in TFP, ICT investment, consumption, and relative prices.
@@
 
-\section{Estimated Parameters via IR Matching}
+\section{Estimated Parameters via IR Matching}\label{sec:appendix_table_IRmatching}
 

### 2018-07-31 Latex/Draft_Summer2018/Summer2018.tex
final changes agreed together

@@
 \small{
-\abstract{We employ Structural VARs to investigate the effects of ICT supply shocks on Total Factor Productivity (TFP) and other macroeconomic variables.
-In response to this sector-specific supply shock, relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a significant delayed and persistent increase.
+\abstract{We employ Structural VARs to investigate the effects of technological shocks specific to the ICT sector on Total Factor Productivity (TFP) and other macroeconomic variables.
+In response to this sector-specific technological change, relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a significant delayed and persistent increase.
+Moreover, current ICT supply shocks explain almost one third of overall TFP fluctuations over a 10-year horizon.
 Taking up the view of theories of ICT as a general-purpose technology, we analyze a two-sector general equilibrium model in order to rationalize previous results and estimate spillovers from the stock of ICT via impulse-response matching.
@@
 Along with \cite{comin2006medium}, theoretical contributions rationalize endogenous productivity dynamics by incorporating features of endogenous growth models in standard models of business cycles.
-Following \cite{romer1990endogenous}, most of these papers augment final-good production functions with an expanding composite of intermediate goods invented by the Research \& Development (R\&D) sector in order to allow for an endogenous rate of adoption of new technologies.\footnote{\cite{bianchi2014growth}, \cite{anzoategui2016endogenous}, and \cite{moran2017innovation} use similar techniques to endogenize growth.
+Following \cite{romer1990endogenous}, most of these papers augment final-good production functions with an expanding composite of intermediate goods invented by the Research \& Development (R\&D) sector in order to allow for an endogenous rate of adoption of new technologies.\footnote{\cite{bianchi2014growth}, \cite{anzoategui2016endogenous}, \cite{moran2017innovation} and \cite{guerron2015financial} use similar techniques to endogenize growth.
 \cite{bianchi2014growth} augment a DSGE  model using a quality ladders model in the vein of \cite{grossman1991quality}.
-\cite{anzoategui2016endogenous} and \cite{moran2017innovation}, similarly to \cite{comin2006medium}, use a model of expanding variety \`a la \cite{romer1990endogenous}.} Guided by the prediction of such theoretical work that R\&D developments matter for growth, other papers attempt to provide empirical evidence of a slowdown in the productivity of the R\&D sector.
+\cite{anzoategui2016endogenous}, \cite{moran2017innovation} and \cite{guerron2015financial}, similarly to \cite{comin2006medium}, use a model of expanding variety \`a la \cite{romer1990endogenous}.} Guided by the prediction of such theoretical work that R\&D developments matter for growth, other papers attempt to provide empirical evidence of a slowdown in the productivity of the R\&D sector.
 Specifically, they show that although research effort keeps rising, the rate of new ideas and discoveries is slowing down.\footnote{\cite{jones2009burden} and \cite{bloom2017ideas} are two contributions that highlight these facts.}
@@
 
-We use two identifying restrictions in order to back out an ICT technology shock.
-First, we expect it to be orthogonal to the current productivity of all the other sectors.
-Since the share of the ICT sector accounts for a negligible part of the whole economy, ICT shocks should have an approximately zero effect on TFP on impact.
-Thus, our first restriction will be a zero-impact restriction on TFP after an ICT shock.
-Moreover, following \cite{greenwood1997long} and \cite{fisher2006dynamic}, we rely on RP and ICTI because we expect that a sectoral technology shock should decrease the relative prices of the sector while enhancing expenditure in the underlying sector.
-For theoretical reasons discussed in more detail below, we do not impose any restriction on RP; instead, we let the ICT shock maximize the impact response of ICTI.\footnote{As pointed out by both \cite{greenwood2000role} and \cite{basu2010sector}, letting the the direction of RP be the sole identifying restriction does not properly capture technological changes between sectors.
-This is the main reason why we do not impose the direction of RP as a direct identifying condition.
-While our main robustness check uses RP, also there we refrain from considering the direction of the RP response.
-See Section \ref{section:twosteps}.} In response to this shock, ICTI rises on impact and remains significant for several quarters.
+We use two main identifying restrictions in order to back out an ICT technology shock: (i) it must be orthogonal to current total factor productivity and (ii) maximize the impact effect on ICT investment.
+First of all, Restriction (i) is justified because the share of the ICT sector accounts for a negligible part of the whole economy implying that ICT shocks should have approximately zero impact effect on TFP.
+In other words, although TFP embodies ICT technical changes by construction, we argue that the direct impact effect of an ICT technological shock on TFP is so tiny to be approximately neglected in our identifying restriction.
+Moreover, we follow results by \cite{greenwood1997long} and \cite{fisher2006dynamic} (among others) to support Restriction (ii).
+In particular, a vast body of literature on sector-specific technological changes argues that a sectoral technology shock should boost quantities in the underlying sector implying a current large impact effect on ICT investment.\footnote{For theoretical reasons discussed in more detail in Section \ref{section:empirics}, we do not impose any restriction on RP in our main specification; instead, we let the ICT shock maximize the impact response of ICTI.
+As pointed out by both \cite{greenwood2000role} and \cite{basu2010sector}, letting the the direction of RP be the sole identifying restriction does not properly capture technological changes between sectors.
+This is the main reason why we do not impose the direction of RP as a direct identifying condition.}
+
+In response to this shock, ICTI rises on impact and remains significant for several quarters.
 RP persistently and significantly declines for more than two years, suggesting that we are indeed identifying the correct sectoral shock.
@@
 The impact matrix $A_0$ must be such that $\Sigma = A_0 A_0'$.
-Notice that $A_0$ is not unique since for any $D$ such that $DD' = I$, $\tilde{A}_0 = A_0 D$ satisfies $\Sigma = \tilde{A}_0 \tilde{A}_0'$.
-
-The matrix of impact responses to all shocks is: % TYPO HERE? either Atilde or A0 D. Checked Barsky, this seems correct but I'm confused. 
+Notice that for any arbitrary orthogonalization $\tilde{A}_0$ such that $\Sigma = \tilde{A}_0 \tilde{A}_0'$, impact matrix $A_0$ can be back out by the appropriate orthonormal matrix $D$ ($DD' = I$) where $A_0 = \tilde{A}_0 D$.
+
+Thus, the matrix of impact responses to all shocks is: % TYPO HERE? either Atilde or A0 D. Checked Barsky, this seems correct but I'm confused. 
 $$
@@
 
-Secondly, a long line of literature going back to the early 1990s postulates that ICT may be a general-purpose technology.\footnote{\cite{basu2003case}, \cite{basu2007information} and \cite{oliner2000resurgence} and are some examples.} % need to include Brynjolfsson's work here, the all-star paper and the Gordon-Mokyr debate.
-Following the classical definition of BT,
-% Bresnahan Trajtenberg -- need to get citation right
+Secondly, a long line of literature going back to the early 1990s postulates that ICT may be a general-purpose technology.\footnote{\cite{oliner2000resurgence}, \cite{basu2003case}, and \cite{basu2007information} are some examples.
+In addition, we are somehow related to the so-called Gordon-Mokyr debate where the two authors present opposing views of future innovation.
+Among the series of published papers we highlight the followings two: \cite{gordon2012us} and \cite{mokyr2014secular}.}
+
+Following the classical definition of \cite{bresnahan1992general},
  GPTs are technologies that alter the process of economy-wide production, and thus affect the productivity of the entire economy.
@@
 For example, investment in ICT goods may trigger accumulation of unobserved complementary capital, as suggested by both \cite{basu2003case} and \cite{basu2007information}.
-Conversely, as advocated by Brynjolffson, new ICT goods may change managerial practices, thus affecting the production process.
+Conversely, as advocated by \cite{bresnahan2002information}, new ICT goods may change managerial practices, thus affecting the production process.
 We take a broader view in which we simply consider the diffusion of ICT goods to be the crucial element of ICT's general-purpose nature.
@@
 \end{eqnarray} 
-where $\rho_{\nu} \in (0,1)$ and $\nu_t \sim N(0,\sigma_{\nu}^2)$ represents a neutral technology shock.
-$\theta^c_t$ is the sector-specific technological component,  which moves along the following deterministic trend
+where $\rho_{\nu} \in (0,1)$ and $\nu_t \sim N(0,\sigma_{\nu}^2)$ represents a neutral technology shock.\footnote{In this case, a news shock would be a current signal regarding innovations to the future values of $\eta_t$.} $\theta^c_t$ is the sector-specific technological component,  which moves along the following deterministic trend
 \begin{eqnarray}
@@
 Similarly, ICT-good firm $q \in [0,1]$ produces $y^i_t(q)$ with labor $l_{t}$, hard capital, $k^c_{t}$ and ICT capital, $k^i_{t}$.
-Analogously to the first sector, production function is augmented by neutral productivity $\eta_t$, sector-specific productivity $\theta^i_t$, and the spillover effect $(k^i_{t})^{\gamma}$.
 Firm $q$ produces in accordance with
 \begin{eqnarray}\label{equation:productionICT}
-y^i_t(q) = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma} \ \ \big( k^c_{t}(q) \big)^a \ \big( k^i_{t}(q) \big)^b \ \big( l_{t}(q) \big)^{1-a-b}, \ \ 0 < a,b < 1
-\end{eqnarray}
-where $\theta^i_t$ is the sector-specific technological component which moves along the following deterministic trend
+y^i_t(q) = A_t^i \ \big( k^c_{t}(q) \big)^a \ \big( k^i_{t}(q) \big)^b \ \big( l_{t}(q) \big)^{1-a-b}, \ \ 0 < a,b < 1
+\end{eqnarray}
+where  $A_t^i = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma}$.
+Analogously to the first sector, production function is augmented by neutral productivity $\eta_t$, sector-specific productivity $\theta^i_t$, and the spillover effect $(k^i_{t})^{\gamma}$.
+In particular, $\theta^i_t$ is the sector-specific technological component which moves along the following deterministic trend
 \begin{eqnarray}\label{equation:ICT_tech_process}
@@
 Given $(\Gamma^i)^*$ and $(\Gamma^c)^*$ we obtain $\gamma^*$ by minimizing the impulse-response matching.
-At this step, however, we are simply solving the system assuming $\gamma$ equal to zero, but a more refined solution will be provided in future.} Finally, to avoid an over-identification problem we set the growth rate of sector-neutral technology $\Gamma^{\eta}$ equal to one.
+At this step, however, we are simply solving the system assuming $\gamma$ equal to zero, but a more refined solution will be provided in future.}\footnote{Other different systems might be use in order to pin down the steady state growth rates of both sectors.
+At this first stage, we opt for System \ref{equation:system_param} because both relative prices and aggregate consumption are well observable variables in the data.} Finally, to avoid an over-identification problem we set the growth rate of sector-neutral technology $\Gamma^{\eta}$ equal to one.
 
@@
 Thus, the data favor an interpretation of our model in which there are considerable spillovers to ICT capital.
-Accordingly, ICT shocks do not need to be large in magnitude to have sizable effects on TFP, GDP and consumption.
-This is indicated by the relatively small number we obtain for $\sigma^2_{\iota}$ of $0.01$.
-Confronted with data, the model is clearly telling a story in which there are small, but persistent ($\rho_{\iota} = 0.9$) ICT shocks that lead considerable medium-run TFP growth because of large spillovers from ICT capital accumulation.
-% does it make sense? I dont know what to say for sigmaiota and rhoiota...
+Accordingly, ICT shocks do not need to be extremely large in magnitude to have sizable effects on TFP, GDP and consumption.
+This is indicated by the value we obtain for $\sigma^2_{\iota}$ of $0.01$.
+Confronted with data, the model is clearly telling a story in which there are small (relative to the overall economy) but persistent ($\rho_{\iota} = 0.9$) ICT shocks that lead considerable medium-run effect on TFP and consumption because of large spillovers from ICT capital accumulation.
 

### 2018-09-05 Latex/Poster_Session/poster_session.tex
Template Latex for the poster session

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% a0poster Landscape Poster
% LaTeX Template
% Version 1.0 (22/06/13)
%
% The a0poster class was created by:
% Gerlinde Kettl and Matthias Weiser (tex@kettl.de)
% 
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[a0,landscape]{a0poster}

\usepackage{multicol} % This is so we can have multiple columns of text side-by-side
\columnsep=100pt % This is the amount of white space between the columns in the poster
\columnseprule=3pt % This is the thickness of the black line between the columns in the poster

\usepackage[svgnames]{xcolor} % Specify colors by their 'svgnames', for a full list of all colors available see here: http://www.latextemplates.com/svgnames-colors

\usepackage{times} % Use the times font
%\usepackage{palatino} % Uncomment to use the Palatino font

\usepackage{graphicx} % Required for including images
\graphicspath{{figures/}} % Location of the graphics files
\usepackage{booktabs} % Top and bottom rules for table
\usepackage[font=small,labelfont=bf]{caption} % Required for specifying captions to tables and figures
\usepackage{amsfonts, amsmath, amsthm, amssymb} % For math fonts, symbols and environments
\usepackage{wrapfig} % Allows wrapping text around tables and figures

\begin{document}

%----------------------------------------------------------------------------------------
%	POSTER HEADER 
%----------------------------------------------------------------------------------------

% The header is divided into three boxes:
% The first is 55% wide and houses the title, subtitle, names and university/organization
% The second is 25% wide and houses contact information
% The third is 19% wide and houses a logo for your university/organization or a photo of you
% The widths of these boxes can be easily edited to accommodate your content as you see fit

\begin{minipage}[b]{0.55\linewidth}
\veryHuge \color{NavyBlue} \textbf{ICT and Future Productivity} \color{Black}\\ % Title
\Huge\textit{Evidence and Theory of a GPT}\\[1cm] % Subtitle
\huge \textbf{Marco Brianti \& Laura Gati}\\ % Author(s)
\huge Boston College\\ % University/organization
\end{minipage}
%
\begin{minipage}[b]{0.25\linewidth}
\color{DarkSlateGray}\Large \textbf{Contact Information:}\\
Department of Economics\\ % Address
Boston College\\
140 Commonwealth Avenue, Chestnut Hill, MA \\\\
Phone: +1 (617) 552 3670\\ % Phone number
Email: \texttt{brianti@bc.edu, gati@bc.edu}\\ % Email address
\end{minipage}
%
\begin{minipage}[b]{0.19\linewidth}
\includegraphics[width=25cm]{logo.jpg} % Logo or a photo of you, adjust its dimensions here
\end{minipage}

\vspace{1cm} % A bit of extra whitespace between the header and poster content

%----------------------------------------------------------------------------------------

\begin{multicols}{4} % This is how many columns your poster will be broken into, a poster with many figures may benefit from less columns whereas a text-heavy poster benefits from more

%----------------------------------------------------------------------------------------
%	ABSTRACT
%----------------------------------------------------------------------------------------

\color{Navy} % Navy color for the abstract

\begin{abstract}

We employ Structural VARs to investigate the effects of technological shocks specific to the ICT sector on Total Factor Productivity (TFP) and other macroeconomic variables. In response to this sector-specific technological change, relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a significant delayed and persistent increase. Moreover, current ICT supply shocks explain almost one third of overall TFP fluctuations over a 10-year horizon. Taking up the view of theories of ICT as a general-purpose technology, we analyze a two-sector general equilibrium model in order to rationalize previous results and estimate spillovers from the stock of ICT via impulse-response matching. We conclude that ICT accumulation is able to enhance productivity through a positive spillover effect which takes into account the overall level of diffusion of ICT capital in the economy.

\end{abstract}

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\color{SaddleBrown} % SaddleBrown color for the introduction

\section*{Introduction}

Aliquam non lacus dolor, \textit{a aliquam quam} \cite{Smith:2012qr}. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Nulla in nibh mauris. Donec vel ligula nisi, a lacinia arcu. Sed mi dui, malesuada vel consectetur et, egestas porta nisi. Sed eleifend pharetra dolor, et dapibus est vulputate eu. \textbf{Integer faucibus elementum felis vitae fringilla.} In hac habitasse platea dictumst. Duis tristique rutrum nisl, nec vulputate elit porta ut. Donec sodales sollicitudin turpis sed convallis. Etiam mauris ligula, blandit adipiscing condimentum eu, dapibus pellentesque risus.

\textit{Aliquam auctor}, metus id ultrices porta, risus enim cursus sapien, quis iaculis sapien tortor sed odio. Mauris ante orci, euismod vitae tincidunt eu, porta ut neque. Aenean sapien est, viverra vel lacinia nec, venenatis eu nulla. Maecenas ut nunc nibh, et tempus libero. Aenean vitae risus ante. Pellentesque condimentum dui. Etiam sagittis purus non tellus tempor volutpat. Donec et dui non massa tristique adipiscing.

Phasellus imperdiet, tortor vitae congue bibendum, felis enim sagittis lorem, et volutpat ante orci sagittis mi. Morbi rutrum laoreet semper. Morbi accumsan enim nec tortor consectetur non commodo nisi sollicitudin. Proin sollicitudin. Pellentesque eget orci eros. Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique \textbf{purus urna nec nibh}.

%----------------------------------------------------------------------------------------
%	OBJECTIVES
%----------------------------------------------------------------------------------------

\color{DarkSlateGray} % DarkSlateGray color for the rest of the content

\section*{Main Objectives}

\begin{enumerate}
\item Lorem ipsum dolor sit amet, consectetur.
\item Nullam at mi nisl. Vestibulum est purus, ultricies cursus volutpat sit amet, vestibulum eu.
\item Praesent tortor libero, vulputate quis elementum a, iaculis.
\item Phasellus a quam mauris, non varius mauris. Fusce tristique, enim tempor varius porta, elit purus commodo velit, pretium mattis ligula nisl nec ante.
\item Ut adipiscing accumsan sapien, sit amet pretium.
\item Estibulum est purus, ultricies cursus volutpat
\item Nullam at mi nisl. Vestibulum est purus, ultricies cursus volutpat sit amet, vestibulum eu.
\item Praesent tortor libero, vulputate quis elementum a, iaculis.
\end{enumerate}

%----------------------------------------------------------------------------------------
%	MATERIALS AND METHODS
%----------------------------------------------------------------------------------------

\section*{Materials and Methods}

Fusce magna risus, molestie ut porttitor in, consectetur sed mi. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Pellentesque consectetur blandit pellentesque. Sed odio justo, viverra nec porttitor vel, lacinia a nunc. Suspendisse pulvinar euismod arcu, sit amet accumsan enim fermentum quis. In id mauris ut dui feugiat egestas. Vestibulum ac turpis lacinia nisl commodo sagittis eget sit amet sapien. Phasellus imperdiet, tortor vitae congue bibendum, felis enim sagittis lorem, et volutpat ante orci sagittis mi. Morbi rutrum laoreet semper. Morbi accumsan enim nec tortor consectetur non commodo nisi sollicitudin. Proin sollicitudin. Pellentesque eget orci eros. Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique purus urna nec nibh. Proin sollicitudin. Pellentesque eget orci eros. Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique purus urna nec nibh.

%------------------------------------------------

\subsection*{Mathematical Section}

Nulla vel nisl sed mauris auctor mollis non sed.

\begin{equation}
E = mc^{2}
\label{eqn:Einstein}
\end{equation}

Curabitur mi sem, pulvinar quis aliquam rutrum. (1) edf (2)
, $\Omega=[-1,1]^3$, maecenas leo est, ornare at. $z=-1$ edf $z=1$ sed interdum felis dapibus sem. $x$ set $y$ ytruem. 
Turpis $j$ amet accumsan enim $y$-lacina; 
ref $k$-viverra nec porttitor $x$-lacina.

Vestibulum ac diam a odio tempus congue. Vivamus id enim nisi:

\begin{eqnarray}
\cos\bar{\phi}_k Q_{j,k+1,t} + Q_{j,k+1,x}+\frac{\sin^2\bar{\phi}_k}{T\cos\bar{\phi}_k} Q_{j,k+1} &=&\nonumber\\ 
-\cos\phi_k Q_{j,k,t} + Q_{j,k,x}-\frac{\sin^2\phi_k}{T\cos\phi_k} Q_{j,k}\label{edgek}
\end{eqnarray}
and
\begin{eqnarray}
\cos\bar{\phi}_j Q_{j+1,k,t} + Q_{j+1,k,y}+\frac{\sin^2\bar{\phi}_j}{T\cos\bar{\phi}_j} Q_{j+1,k}&=&\nonumber \\
-\cos\phi_j Q_{j,k,t} + Q_{j,k,y}-\frac{\sin^2\phi_j}{T\cos\phi_j} Q_{j,k}.\label{edgej}
\end{eqnarray}

Nulla sed arcu arcu. Duis et ante gravida orci venenatis tincidunt. Fusce vitae lacinia metus. Pellentesque habitant morbi. $\mathbf{A}\underline{\xi}=\underline{\beta}$ Vim $\underline{\xi}$ enum nidi $3(P+2)^{2}$ lacina. Id feugain $\mathbf{A}$ nun quis; magno. Fusce convallis rutrum turpis, quis aliquet enim accumsan id. Vestibulum ullamcorper porttitor convallis. Integer sagittis interdum malesuada. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos. Sed adipiscing tristique orci at ullamcorper. Morbi accumsan, urna et porttitor pulvinar, lacus risus dignissim massa. Proin sollicitudin. Pellentesque eget orci eros. Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique purus urna nec nibh.

%----------------------------------------------------------------------------------------
%	RESULTS 
%----------------------------------------------------------------------------------------

\section*{Results}

Donec faucibus purus at tortor egestas eu fermentum dolor facilisis. Maecenas tempor dui eu neque fringilla rutrum. Mauris \emph{lobortis} nisl accumsan. Aenean vitae risus ante. Pellentesque condimentum dui. Etiam sagittis purus non tellus tempor volutpat. Donec et dui non massa tristique adipiscing.
%
\begin{wraptable}{l}{12cm} % Left or right alignment is specified in the first bracket, the width of the table is in the second
\begin{tabular}{l l l}
\toprule
\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
\midrule
Treatment 1 & 0.0003262 & 0.562 \\
Treatment 2 & 0.0015681 & 0.910 \\
Treatment 3 & 0.0009271 & 0.296 \\
\bottomrule
\end{tabular}
\captionof{table}{\color{Green} Table caption}
\end{wraptable}
%
Phasellus imperdiet, tortor vitae congue bibendum, felis enim sagittis lorem, et volutpat ante orci sagittis mi. Morbi rutrum laoreet semper. Morbi accumsan enim nec tortor consectetur non commodo nisi sollicitudin. Proin sollicitudin. Pellentesque eget orci eros. Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique purus urna nec nibh.

Nulla ut porttitor enim. Suspendisse venenatis dui eget eros gravida tempor. Mauris feugiat elit et augue placerat ultrices. Morbi accumsan enim nec tortor consectetur non commodo. Pellentesque condimentum dui. Etiam sagittis purus non tellus tempor volutpat. Donec et dui non massa tristique adipiscing. Quisque vestibulum eros eu. Phasellus imperdiet, tortor vitae congue bibendum, felis enim sagittis lorem, et volutpat ante orci sagittis mi. Morbi rutrum laoreet semper. Morbi accumsan enim nec tortor consectetur non commodo nisi sollicitudin.

\begin{center}\vspace{1cm}
\includegraphics[width=0.8\linewidth]{placeholder}
\captionof{figure}{\color{Green} Figure caption}
\end{center}\vspace{1cm}

In hac habitasse platea dictumst. Etiam placerat, risus ac.

Adipiscing lectus in magna blandit:

\begin{center}\vspace{1cm}
\begin{tabular}{l l l l}
\toprule
\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2} \\
\midrule
Treatment 1 & 0.0003262 & 0.562 \\
Treatment 2 & 0.0015681 & 0.910 \\
Treatment 3 & 0.0009271 & 0.296 \\
\bottomrule
\end{tabular}
\captionof{table}{\color{Green} Table caption}
\end{center}\vspace{1cm}

Vivamus sed nibh ac metus tristique tristique a vitae ante. Sed lobortis mi ut arcu fringilla et adipiscing ligula rutrum. Aenean turpis velit, placerat eget tincidunt nec, ornare in nisl. In placerat.

\begin{center}\vspace{1cm}
\includegraphics[width=0.8\linewidth]{placeholder}
\captionof{figure}{\color{Green} Figure caption}
\end{center}\vspace{1cm}

%----------------------------------------------------------------------------------------
%	CONCLUSIONS
%----------------------------------------------------------------------------------------

\color{SaddleBrown} % SaddleBrown color for the conclusions to make them stand out

\section*{Conclusions}

\begin{itemize}
\item Pellentesque eget orci eros. Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique purus urna nec nibh. Phasellus fermentum rutrum elementum. Nam quis justo lectus.
\item Vestibulum sem ante, hendrerit a gravida ac, blandit quis magna.
\item Donec sem metus, facilisis at condimentum eget, vehicula ut massa. Morbi consequat, diam sed convallis tincidunt, arcu nunc.
\item Nunc at convallis urna. isus ante. Pellentesque condimentum dui. Etiam sagittis purus non tellus tempor volutpat. Donec et dui non massa tristique adipiscing.
\end{itemize}

\color{DarkSlateGray} % Set the color back to DarkSlateGray for the rest of the content

%----------------------------------------------------------------------------------------
%	FORTHCOMING RESEARCH
%----------------------------------------------------------------------------------------

\section*{Forthcoming Research}

Vivamus molestie, risus tempor vehicula mattis, libero arcu volutpat purus, sed blandit sem nibh eget turpis. Maecenas rutrum dui blandit lorem vulputate gravida. Praesent venenatis mi vel lorem tempor at varius diam sagittis. Nam eu leo id turpis interdum luctus a sed augue. Nam tellus.

 %----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\nocite{*} % Print all references regardless of whether they were cited in the poster or not
\bibliographystyle{plain} % Plain referencing style
\bibliography{sample} % Use the example bibliography file sample.bib

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\section*{Acknowledgements}

Etiam fermentum, arcu ut gravida fringilla, dolor arcu laoreet justo, ut imperdiet urna arcu a arcu. Donec nec ante a dui tempus consectetur. Cras nisi turpis, dapibus sit amet mattis sed, laoreet.

%----------------------------------------------------------------------------------------

\end{multicols}
\end{document}

### 2018-09-10 Latex/Poster_Session/template_Pablo/main.tex
added template from Pablo + mail sent to Graziella

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Landscape Poster
% LaTeX Template
% Version 1.0 (29/03/13)
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
% 
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[final]{beamer}

\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster

\usetheme{confposter} % Use the confposter theme supplied with this template

\setbeamercolor{block title}{fg=ngreen,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in} % A0 width: 46.8in
\setlength{\paperheight}{36in} % A0 height: 33.1in
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
\setlength{\onecolwid}{0.22\paperwidth} % Width of one column
\setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

\usepackage{graphicx}  % Required for including images

\usepackage{booktabs} % Top and bottom rules for tables

%----------------------------------------------------------------------------------------
%	TITLE SECTION 
%----------------------------------------------------------------------------------------

\title{Unnecessarily Complicated Research Title} % Poster title

\author{John Smith, James Smith and Jane Smith} % Author(s)

\institute{Department and University Name} % Institution(s)

%----------------------------------------------------------------------------------------

\begin{document}

\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

\setlength{\belowcaptionskip}{2ex} % White space under figures
\setlength\belowdisplayshortskip{2ex} % White space under equations

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

\begin{columns}[t] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The first column

%----------------------------------------------------------------------------------------
%	OBJECTIVES
%----------------------------------------------------------------------------------------

\begin{alertblock}{Objectives}

Lorem ipsum dolor sit amet, consectetur, nunc tellus pulvinar tortor, commodo eleifend risus arcu sed odio:
\begin{itemize}
\item Mollis dignissim, magna augue tincidunt dolor, interdum vestibulum urna
\item Sed aliquet luctus lectus, eget aliquet leo ullamcorper consequat. Vivamus eros sem, iaculis ut euismod non, sollicitudin vel orci.
\item Nascetur ridiculus mus.  
\item Euismod non erat. Nam ultricies pellentesque nunc, ultrices volutpat nisl ultrices a.
\end{itemize}

\end{alertblock}

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\begin{block}{Introduction}

Lorem ipsum dolor \textbf{sit amet}, consectetur adipiscing elit. Sed commodo molestie porta. Sed ultrices scelerisque sapien ac commodo. Donec ut volutpat elit. Sed laoreet accumsan mattis. Integer sapien tellus, auctor ac blandit eget, sollicitudin vitae lorem. Praesent dictum tempor pulvinar. Suspendisse potenti. Sed tincidunt varius ipsum, et porta nulla suscipit et. Etiam congue bibendum felis, ac dictum augue cursus a. \textbf{Donec} magna eros, iaculis sit amet placerat quis, laoreet id est. In ut orci purus, interdum ornare nibh. Pellentesque pulvinar, nibh ac malesuada accumsan, urna nunc convallis tortor, ac vehicula nulla tellus eget nulla. Nullam lectus tortor, \textit{consequat tempor hendrerit} quis, vestibulum in diam. Maecenas sed diam augue.

This statement requires citation \cite{Smith:2012qr}.

\end{block}

%------------------------------------------------

\begin{figure}
\includegraphics[width=0.8\linewidth]{placeholder.jpg}
\caption{Figure caption}
\end{figure}

%----------------------------------------------------------------------------------------

\end{column} % End of the first column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\twocolwid} % Begin a column which is two columns wide (column 2)

\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column

\begin{column}{\onecolwid}\vspace{-.6in} % The first column within column 2 (column 2.1)

%----------------------------------------------------------------------------------------
%	MATERIALS
%----------------------------------------------------------------------------------------

\begin{block}{Materials}

The following materials were required to complete the research:

\begin{itemize}
\item Curabitur pellentesque dignissim
\item Eu facilisis est tempus quis
\item Duis porta consequat lorem
\item Eu facilisis est tempus quis
\end{itemize}

The materials were prepared according to the steps outlined below:

\begin{enumerate}
\item Curabitur pellentesque dignissim
\item Eu facilisis est tempus quis
\item Duis porta consequat lorem
\item Curabitur pellentesque dignissim
\end{enumerate}

\end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of column 2.1

\begin{column}{\onecolwid}\vspace{-.6in} % The second column within column 2 (column 2.2)

%----------------------------------------------------------------------------------------
%	METHODS
%----------------------------------------------------------------------------------------

\begin{block}{Methods}

Lorem ipsum dolor \textbf{sit amet}, consectetur adipiscing elit. Sed laoreet accumsan mattis. Integer sapien tellus, auctor ac blandit eget, sollicitudin vitae lorem. Praesent dictum tempor pulvinar. Suspendisse potenti. Sed tincidunt varius ipsum, et porta nulla suscipit et. Etiam congue bibendum felis, ac dictum augue cursus a. \textbf{Donec} magna eros, iaculis sit amet placerat quis, laoreet id est. In ut orci purus, interdum ornare nibh. Pellentesque pulvinar, nibh ac malesuada accumsan, urna nunc convallis tortor, ac vehicula nulla tellus eget nulla. Nullam lectus tortor, \textit{consequat tempor hendrerit} quis, vestibulum in diam. Maecenas sed diam augue.

\end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of column 2.2

\end{columns} % End of the split of column 2 - any content after this will now take up 2 columns width

%----------------------------------------------------------------------------------------
%	IMPORTANT RESULT
%----------------------------------------------------------------------------------------

\begin{alertblock}{Important Result}

Lorem ipsum dolor \textbf{sit amet}, consectetur adipiscing elit. Sed commodo molestie porta. Sed ultrices scelerisque sapien ac commodo. Donec ut volutpat elit.

\end{alertblock}

%----------------------------------------------------------------------------------------

\begin{columns}[t,totalwidth=\twocolwid] % Split up the two columns wide column again

\begin{column}{\onecolwid} % The first column within column 2 (column 2.1)

%----------------------------------------------------------------------------------------
%	MATHEMATICAL SECTION
%----------------------------------------------------------------------------------------

\begin{block}{Mathematical Section}

Nam quis odio enim, in molestie libero. Vivamus cursus mi at nulla elementum sollicitudin. Nam quis odio enim, in molestie libero. Vivamus cursus mi at nulla elementum sollicitudin.

\begin{equation}
E = mc^{2}
\label{eqn:Einstein}
\end{equation}

Nam quis odio enim, in molestie libero. Vivamus cursus mi at nulla elementum sollicitudin. Nam quis odio enim, in molestie libero. Vivamus cursus mi at nulla elementum sollicitudin.

\begin{equation}
\cos^3 \theta =\frac{1}{4}\cos\theta+\frac{3}{4}\cos 3\theta
\label{eq:refname}
\end{equation}

Nam quis odio enim, in molestie libero. Vivamus cursus mi at nulla elementum sollicitudin. Nam quis odio enim, in molestie libero. Vivamus cursus mi at nulla elementum sollicitudin.

\begin{equation}
\kappa =\frac{\xi}{E_{\mathrm{max}}} %\mathbb{ZNR}
\end{equation}

\end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of column 2.1

\begin{column}{\onecolwid} % The second column within column 2 (column 2.2)

%----------------------------------------------------------------------------------------
%	RESULTS
%----------------------------------------------------------------------------------------

\begin{block}{Results}

\begin{figure}
\includegraphics[width=0.8\linewidth]{placeholder.jpg}
\caption{Figure caption}
\end{figure}

Nunc tempus venenatis facilisis. Curabitur suscipit consequat eros non porttitor. Sed a massa dolor, id ornare enim:

\begin{table}
\vspace{2ex}
\begin{tabular}{l l l}
\toprule
\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
\midrule
Treatment 1 & 0.0003262 & 0.562 \\
Treatment 2 & 0.0015681 & 0.910 \\
Treatment 3 & 0.0009271 & 0.296 \\
\bottomrule
\end{tabular}
\caption{Table caption}
\end{table}

\end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of column 2.2

\end{columns} % End of the split of column 2

\end{column} % End of the second column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The third column

%----------------------------------------------------------------------------------------
%	CONCLUSION
%----------------------------------------------------------------------------------------

\begin{block}{Conclusion}

Nunc tempus venenatis facilisis. \textbf{Curabitur suscipit} consequat eros non porttitor. Sed a massa dolor, id ornare enim. Fusce quis massa dictum tortor \textbf{tincidunt mattis}. Donec quam est, lobortis quis pretium at, laoreet scelerisque lacus. Nam quis odio enim, in molestie libero. Vivamus cursus mi at \textit{nulla elementum sollicitudin}.

\end{block}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{block}{Additional Information}

Maecenas ultricies feugiat velit non mattis. Fusce tempus arcu id ligula varius dictum. 
\begin{itemize}
\item Curabitur pellentesque dignissim
\item Eu facilisis est tempus quis
\item Duis porta consequat lorem
\end{itemize}

\end{block}

%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\begin{block}{References}

\nocite{*} % Insert publications even if they are not cited in the poster
\small{\bibliographystyle{unsrt}
\bibliography{sample}\vspace{0.75in}}

\end{block}

%----------------------------------------------------------------------------------------
%	ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\setbeamercolor{block title}{fg=red,bg=white} % Change the block title color

\begin{block}{Acknowledgements}

\small{\rmfamily{Nam mollis tristique neque eu luctus. Suspendisse rutrum congue nisi sed convallis. Aenean id neque dolor. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.}} \\

\end{block}

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\setbeamercolor{block alerted title}{fg=black,bg=norange} % Change the alert block title colors
\setbeamercolor{block alerted body}{fg=black,bg=white} % Change the alert block body colors

\begin{alertblock}{Contact Information}

\begin{itemize}
\item Web: \href{http://www.university.edu/smithlab}{http://www.university.edu/smithlab}
\item Email: \href{mailto:john@smith.com}{john@smith.com}
\item Phone: +1 (000) 111 1111
\end{itemize}

\end{alertblock}

\begin{center}
\begin{tabular}{ccc}
\includegraphics[width=0.4\linewidth]{logo.png} & \hfill & \includegraphics[width=0.4\linewidth]{logo.png}
\end{tabular}
\end{center}

%----------------------------------------------------------------------------------------

\end{column} % End of the third column

\end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}

### 2018-09-10 Latex/Poster_Session/poster_session.tex
Poster. Step 1

@@
 
-\color{Navy} % Navy color for the abstract
+\color{Black} % Navy color for the abstract
+%\color{Navy} % Navy color for the abstract
 
-\begin{abstract}
+%\begin{abstract}
 
-We employ Structural VARs to investigate the effects of technological shocks specific to the ICT sector on Total Factor Productivity (TFP) and other macroeconomic variables.
+%We employ Structural VARs to investigate the effects of technological shocks specific to the ICT sector on Total Factor Productivity (TFP) and other macroeconomic variables.
 In response to this sector-specific technological change, relative prices of ICT goods and services immediately fall, ICT investment rises on impact, and TFP displays a significant delayed and persistent increase.
@@
 
-\end{abstract}
+%\end{abstract}
 
@@
 
-\color{SaddleBrown} % SaddleBrown color for the introduction
+%\color{SaddleBrown} % SaddleBrown color for the introduction
 
@@
 
-Aliquam non lacus dolor, \textit{a aliquam quam} \cite{Smith:2012qr}.
-Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus.
-Nulla in nibh mauris.
-Donec vel ligula nisi, a lacinia arcu.
-Sed mi dui, malesuada vel consectetur et, egestas porta nisi.
-Sed eleifend pharetra dolor, et dapibus est vulputate eu.
-\textbf{Integer faucibus elementum felis vitae fringilla.} In hac habitasse platea dictumst.
-Duis tristique rutrum nisl, nec vulputate elit porta ut.
-Donec sodales sollicitudin turpis sed convallis.
-Etiam mauris ligula, blandit adipiscing condimentum eu, dapibus pellentesque risus.
-
-\textit{Aliquam auctor}, metus id ultrices porta, risus enim cursus sapien, quis iaculis sapien tortor sed odio.
-Mauris ante orci, euismod vitae tincidunt eu, porta ut neque.
-Aenean sapien est, viverra vel lacinia nec, venenatis eu nulla.
-Maecenas ut nunc nibh, et tempus libero.
-Aenean vitae risus ante.
-Pellentesque condimentum dui.
-Etiam sagittis purus non tellus tempor volutpat.
-Donec et dui non massa tristique adipiscing.
-
-Phasellus imperdiet, tortor vitae congue bibendum, felis enim sagittis lorem, et volutpat ante orci sagittis mi.
-Morbi rutrum laoreet semper.
-Morbi accumsan enim nec tortor consectetur non commodo nisi sollicitudin.
-Proin sollicitudin.
-Pellentesque eget orci eros.
-Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique \textbf{purus urna nec nibh}.
+Although there is large consensus on the importance of productivity as a driver of economic performance, there is less agreement on the underlying sources of productivity growth.
+Along with \cite{comin2006medium}, theoretical contributions rationalize endogenous productivity dynamics by incorporating features of endogenous growth models in standard models of business cycles.
+Following \cite{romer1990endogenous}, most of these papers augment final-good production functions with an expanding composite of intermediate goods invented by the Research \& Development (R\&D) sector in order to allow for an endogenous rate of adoption of new technologies.
+Motivated by this wave of research, this paper follows a different path and argues that Information and Communication Technology (hereafter ICT) plays an important role in driving medium-term productivity in sectors that are ICT users.
 
@@
 
-\color{DarkSlateGray} % DarkSlateGray color for the rest of the content
+%\color{DarkSlateGray} % DarkSlateGray color for the rest of the content
 
@@
 \begin{enumerate}
-\item Lorem ipsum dolor sit amet, consectetur.
-\item Nullam at mi nisl. Vestibulum est purus, ultricies cursus volutpat sit amet, vestibulum eu.
-\item Praesent tortor libero, vulputate quis elementum a, iaculis.
-\item Phasellus a quam mauris, non varius mauris. Fusce tristique, enim tempor varius porta, elit purus commodo velit, pretium mattis ligula nisl nec ante.
-\item Ut adipiscing accumsan sapien, sit amet pretium.
-\item Estibulum est purus, ultricies cursus volutpat
-\item Nullam at mi nisl. Vestibulum est purus, ultricies cursus volutpat sit amet, vestibulum eu.
-\item Praesent tortor libero, vulputate quis elementum a, iaculis.
+\item Provide robust empirical evidence to show that current rises in ICT investment explain significant and persistent increases in future Total Factor Productivity (hereafter TFP)
+\item Analyze a standard theoretical framework in order to both rationalize our empirical results and to draw conclusions concerning the nature of the ICT contribution to future productivity
 \end{enumerate}
@@
 
-\section*{Materials and Methods}
+\section*{Empirics}
 
-Fusce magna risus, molestie ut porttitor in, consectetur sed mi.
-Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Pellentesque consectetur blandit pellentesque.
-Sed odio justo, viverra nec porttitor vel, lacinia a nunc.
-Suspendisse pulvinar euismod arcu, sit amet accumsan enim fermentum quis.
-In id mauris ut dui feugiat egestas.
-Vestibulum ac turpis lacinia nisl commodo sagittis eget sit amet sapien.
-Phasellus imperdiet, tortor vitae congue bibendum, felis enim sagittis lorem, et volutpat ante orci sagittis mi.
-Morbi rutrum laoreet semper.
-Morbi accumsan enim nec tortor consectetur non commodo nisi sollicitudin.
-Proin sollicitudin.
-Pellentesque eget orci eros.
-Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique purus urna nec nibh.
-Proin sollicitudin.
-Pellentesque eget orci eros.
-Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique purus urna nec nibh.
+We identify technological shocks specific to the ICT sector in a Structural VAR context.
+Our multivariate system includes three key variables: TFP, ICT investment (hereafter ICTI), and relative prices (hereafter RP).\footnote{ICTI is defined as the total expenditure in equipment and computer software meant to be used in production for more than a year.
+Thus, an increase in ICTI is ICT capital deepening.
+RP is the ratio between the price level of ICT durable goods and the price level in the overall economy.} We use two main identifying restrictions in order to back out an ICT technology shock: (i) it must be orthogonal to current total factor productivity and (ii) maximize the impact effect on ICT investment.
+Although our results are robust over different specifications, a critique to our empirical strategy is reverse causality coming from news on future TFP.
+The heart of these robustness checks is sequential identification of news and ICT shocks: we first identify a news shock in the spirit of \cite{barsky2011news}, and subsequently we identify our sectoral ICT shock using the previous identification strategy.
 
@@
 
-\subsection*{Mathematical Section}
+\subsection*{Identification Strategy}
+\subsubsection*{Step 1 - Identification of $\gamma_{news}$}
+$$
+\max_{\gamma_{news}} \Omega_{1,news}(h) = \frac{ \sum_{t=0}^h e_1' B^t \tilde{A}_0 \gamma_{news} \gamma_{news}' \tilde{A}_0' B'^t e_1 } {e_1' ( \sum_{\tau = 0}^H B^t \Sigma B'^t )e_1}
+$$
+subject to
+$$
+\Pi_{1,news}(0) = 0,
+$$
+$$
+\Pi_{6,news}(0) = \Pi_{6,news}(1) = \Pi_{6,news}(2) = 0, \ \ \text{and}
+$$
+$$
+\gamma_{news} \gamma_{news}' = 1.
+$$
+where the first constraint represents the zero-impact restriction of news on TFP.
+The second constraint dictates that the response of relative prices to news should be relatively small.\footnote{Our identification strategy is robust to different restrictions to relative prices.
+Results hold if we set the zero restriction on other horizons.} Finally, the last constraint imposes that $\gamma_{news}$ should be a column derived from an orthogonal matrix.
 
-Nulla vel nisl sed mauris auctor mollis non sed.
-
-\begin{equation}
-E = mc^{2}
-\label{eqn:Einstein}
-\end{equation}
-
-Curabitur mi sem, pulvinar quis aliquam rutrum. (1) edf (2)
-, $\Omega=[-1,1]^3$, maecenas leo est, ornare at. $z=-1$ edf $z=1$ sed interdum felis dapibus sem. $x$ set $y$ ytruem. 
-Turpis $j$ amet accumsan enim $y$-lacina; 
-ref $k$-viverra nec porttitor $x$-lacina.
-
-Vestibulum ac diam a odio tempus congue. Vivamus id enim nisi:
-
-\begin{eqnarray}
-\cos\bar{\phi}_k Q_{j,k+1,t} + Q_{j,k+1,x}+\frac{\sin^2\bar{\phi}_k}{T\cos\bar{\phi}_k} Q_{j,k+1} &=&\nonumber\\ 
--\cos\phi_k Q_{j,k,t} + Q_{j,k,x}-\frac{\sin^2\phi_k}{T\cos\phi_k} Q_{j,k}\label{edgek}
-\end{eqnarray}
-and
-\begin{eqnarray}
-\cos\bar{\phi}_j Q_{j+1,k,t} + Q_{j+1,k,y}+\frac{\sin^2\bar{\phi}_j}{T\cos\bar{\phi}_j} Q_{j+1,k}&=&\nonumber \\
--\cos\phi_j Q_{j,k,t} + Q_{j,k,y}-\frac{\sin^2\phi_j}{T\cos\phi_j} Q_{j,k}.\label{edgej}
-\end{eqnarray}
-
-Nulla sed arcu arcu.
-Duis et ante gravida orci venenatis tincidunt.
-Fusce vitae lacinia metus.
-Pellentesque habitant morbi.
-$\mathbf{A}\underline{\xi}=\underline{\beta}$ Vim $\underline{\xi}$ enum nidi $3(P+2)^{2}$ lacina.
-Id feugain $\mathbf{A}$ nun quis; magno.
-Fusce convallis rutrum turpis, quis aliquet enim accumsan id.
-Vestibulum ullamcorper porttitor convallis.
-Integer sagittis interdum malesuada.
-Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos himenaeos.
-Sed adipiscing tristique orci at ullamcorper.
-Morbi accumsan, urna et porttitor pulvinar, lacus risus dignissim massa.
-Proin sollicitudin.
-Pellentesque eget orci eros.
-Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique purus urna nec nibh.
+\subsubsection*{Step 2 - Identification of $\gamma_{ICT}$}
+$$
+\max_{\gamma_{ICT}} \Pi_{2,ICT}(0) =  e_2' \tilde{A}_0 \gamma_{ICT} 
+$$
+subject to
+$$
+\Pi_{1,ICT}(0) = 0,
+$$
+$$
+\gamma_{news} \gamma_{ICT}' = 0, \ \ \text{and} \ \ \gamma_{ICT} \gamma_{ICT}' = 1.
+$$
+where the first constraint represents the zero-impact restriction of ICT on TFP and the last constraint imposes that both $\gamma_{news}$ and $\gamma_{ICT}$ should be two different columns derived from an orthogonal matrix.
 
@@
 
-\section*{Results}
+\begin{center}\vspace{1cm}
+	\includegraphics[width=1\linewidth]{alltogether}
+	\captionof{figure}{The red solid lines are the estimated impulse responses to our ICT shock.
+The shaded dark gray area and the shaded light gray area are the $90$\% and $95$\% confidence intervals, respectively, from 2000 bias-corrected bootstrap replications of the reduced-form VAR.
+The horizontal axes refer to forecast horizon and the units of the vertical axes are percentage deviations.}
+\end{center}\vspace{1cm}
 
-Donec faucibus purus at tortor egestas eu fermentum dolor facilisis.
-Maecenas tempor dui eu neque fringilla rutrum.
-Mauris \emph{lobortis} nisl accumsan.
-Aenean vitae risus ante.
-Pellentesque condimentum dui.
-Etiam sagittis purus non tellus tempor volutpat.
-Donec et dui non massa tristique adipiscing.
-%
-\begin{wraptable}{l}{12cm} % Left or right alignment is specified in the first bracket, the width of the table is in the second
-\begin{tabular}{l l l}
-\toprule
-\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2}\\
-\midrule
-Treatment 1 & 0.0003262 & 0.562 \\
-Treatment 2 & 0.0015681 & 0.910 \\
-Treatment 3 & 0.0009271 & 0.296 \\
-\bottomrule
-\end{tabular}
-\captionof{table}{\color{Green} Table caption}
-\end{wraptable}
-%
-Phasellus imperdiet, tortor vitae congue bibendum, felis enim sagittis lorem, et volutpat ante orci sagittis mi.
-Morbi rutrum laoreet semper.
-Morbi accumsan enim nec tortor consectetur non commodo nisi sollicitudin.
-Proin sollicitudin.
-Pellentesque eget orci eros.
-Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique purus urna nec nibh.
+\section*{Empirical Results}
 
-Nulla ut porttitor enim.
-Suspendisse venenatis dui eget eros gravida tempor.
-Mauris feugiat elit et augue placerat ultrices.
-Morbi accumsan enim nec tortor consectetur non commodo.
-Pellentesque condimentum dui.
-Etiam sagittis purus non tellus tempor volutpat.
-Donec et dui non massa tristique adipiscing.
-Quisque vestibulum eros eu.
-Phasellus imperdiet, tortor vitae congue bibendum, felis enim sagittis lorem, et volutpat ante orci sagittis mi.
-Morbi rutrum laoreet semper.
-Morbi accumsan enim nec tortor consectetur non commodo nisi sollicitudin.
+In response to this shock, ICTI rises on impact and remains significant for several quarters.
+RP persistently and significantly declines for more than two years, suggesting that we are indeed identifying the correct sectoral shock.
+Our main result is that TFP, restricted not to respond on impact, rises after few quarters and remains significant and stable for at least 5 years, despite the tiny size of the ICT sector relative to the economy.
+Finally, variance decomposition analysis suggests that ICT shocks explain a remarkable size of economic fluctuations over the medium and long run.
+These shocks drive about $40$\% and $33$\% of the overall GDP and TFP fluctuations over a 10-year horizon, respectively.
+
+\section*{Theory}
+
+In order to understand the economics behind our empirical results, we then analyze a two-sector DSGE model which allows ICT to be the general-purpose technology (hereafter GPT) of the whole economy.
+In our model, both sectoral production functions are fed with three inputs: (i) labor, supplied by households, (ii) hard capital, produced by the final sector, and (iii) ICT capital, produced by the ICT sector.
+We then interpret ICT as the GPT of the last 30 years of the U.S.
+economy assuming that exogenous technological changes in the ICT sector are able to affect economy-wide productivity well above the direct effect coming from the technology increase itself.
+
+\section*{Main Assumption}
+
+Production functions are described as follows
+\begin{eqnarray*}
+\begin{aligned}
+y^c_t(j) &= A^c_t \ \big( k^c_{t}(j) \big)^a \ \big( k^i_{t}(j) \big)^b \ \big( l_{t}(j) \big)^{1-a-b}, \ \ 0 < a,b < 1 \\
+y^i_t(q) &= A_t^i \ \big( k^c_{t}(q) \big)^a \ \big( k^i_{t}(q) \big)^b \ \big( l_{t}(q) \big)^{1-a-b}, \ \ 0 < a,b < 1
+\end{aligned}
+\end{eqnarray*}
+where $A_t^c = \eta_t \ \theta^c_t \ (k^i_{t})^{\gamma}$ and $A_t^i = \eta_t \ \theta^i_t \ (k^i_{t})^{\gamma}$.
 
 \begin{center}\vspace{1cm}
-\includegraphics[width=0.8\linewidth]{placeholder}
-\captionof{figure}{\color{Green} Figure caption}
+	\includegraphics[width=1\linewidth]{IRmatchingall}
+	\captionof{figure}{Empirical VAR versus model responses to an ICT shock.
+The black solid lines show the empirical responses to an identified ICT shock.
+The dotted red lines show the model’s responses to a shock to the ICT-specific technological component.
+The horizontal axes refer to forecast horizon and the units of the vertical axes are percentage deviations.}
 \end{center}\vspace{1cm}
 
-In hac habitasse platea dictumst. Etiam placerat, risus ac.
+\section*{Theoretical Results}
 
-Adipiscing lectus in magna blandit:
+The question we tried to answer is why a contemporaneous technological shock specific to the ICT sector is able to trigger increases in future total factor productivity even when it is too small to affect TFP today.
+When an ICT technology shock hits the economy, both sectors invest more on ICT capital goods since they are now cheaper to purchase and easier to produce.
+Now, in order to link current higher investment in ICT goods to future TFP, we assume that the general-purpose nature of ICT goods manifests itself in the form of a spillover on both production functions which is not internalized by the agents.\footnote{This externality is governed by the parameter $\gamma$ which has been estimated via impulse-response matching to be robustly larger than zero.} Since the spillover comes from the overall stock of ICT capital, we interpret it as the diffusion of ICT capital.
 
-\begin{center}\vspace{1cm}
-\begin{tabular}{l l l l}
-\toprule
-\textbf{Treatments} & \textbf{Response 1} & \textbf{Response 2} \\
-\midrule
-Treatment 1 & 0.0003262 & 0.562 \\
-Treatment 2 & 0.0015681 & 0.910 \\
-Treatment 3 & 0.0009271 & 0.296 \\
-\bottomrule
-\end{tabular}
-\captionof{table}{\color{Green} Table caption}
-\end{center}\vspace{1cm}
-
-Vivamus sed nibh ac metus tristique tristique a vitae ante.
-Sed lobortis mi ut arcu fringilla et adipiscing ligula rutrum.
-Aenean turpis velit, placerat eget tincidunt nec, ornare in nisl.
-In placerat.
-
-\begin{center}\vspace{1cm}
-\includegraphics[width=0.8\linewidth]{placeholder}
-\captionof{figure}{\color{Green} Figure caption}
-\end{center}\vspace{1cm}
+There is clear economic intuition underlying our assumption of the spillover.
+Since the purpose of ICT goods is to enhance communication, the quality and speed of information acquisition and sharing is also determined by the overall diffusion of ICT goods.
+As a simple example, owning a mobile phone enables one to contact another person instantaneously only if the other person is also endowed with the same technology.
+As a result, the effectiveness of ICT capital is intrinsically related to its own diffusion.
+The impulse response matching exercise shows that a two-sector model featuring ICT capital and hard capital can successfully match the empirical responses to an ICT shock if the spillover effect is in action.
 
@@
 
-\color{SaddleBrown} % SaddleBrown color for the conclusions to make them stand out
+%\color{SaddleBrown} % SaddleBrown color for the conclusions to make them stand out
 
@@
 
-\begin{itemize}
-\item Pellentesque eget orci eros.
-Fusce ultricies, tellus et pellentesque fringilla, ante massa luctus libero, quis tristique purus urna nec nibh.
-Phasellus fermentum rutrum elementum.
-Nam quis justo lectus.
-\item Vestibulum sem ante, hendrerit a gravida ac, blandit quis magna.
-\item Donec sem metus, facilisis at condimentum eget, vehicula ut massa. Morbi consequat, diam sed convallis tincidunt, arcu nunc.
-\item Nunc at convallis urna. isus ante. Pellentesque condimentum dui. Etiam sagittis purus non tellus tempor volutpat. Donec et dui non massa tristique adipiscing.
-\end{itemize}
+In this project, we look at the effect of ICT shocks on medium-run TFP from both an empirical and a theoretical perspective.
+In response to an ICT shock TFP rises after three quarters and remains significant for more than 10-years.
+We rationalize our empirical results by analyzing a two-sector DSGE model \`a la \cite{greenwood1997long}.
+We use both empirical and theoretical results to estimate main parameters of the model via impulse-response matching to an ICT technology shock.
+Results show that the parameter which governs the size of the spillover effect is positive and large, suggesting that our interpretation of the general-purpose nature of ICT capital is confirmed by the data.
 
-\color{DarkSlateGray} % Set the color back to DarkSlateGray for the rest of the content
+Thus the main takeaway of this paper is that the interpretation of ICT as a general-purpose technology of the US between 1989-2017 is a good explanation of medium-run TFP growth dynamics.
+This relies on understanding the general-purpose nature of ICT goods as the extent to which their diffusion in the economy matters.
 
@@
 
-Vivamus molestie, risus tempor vehicula mattis, libero arcu volutpat purus, sed blandit sem nibh eget turpis.
-Maecenas rutrum dui blandit lorem vulputate gravida.
-Praesent venenatis mi vel lorem tempor at varius diam sagittis.
-Nam eu leo id turpis interdum luctus a sed augue.
-Nam tellus.
+Augment the model with capital adjustment costs in order to match the slow response displayed by productivity after a ICT shock.
 
@@
 
-\nocite{*} % Print all references regardless of whether they were cited in the poster or not
-\bibliographystyle{plain} % Plain referencing style
-\bibliography{sample} % Use the example bibliography file sample.bib
+%\nocite{*} % Print all references regardless of whether they were cited in the poster or not
+\bibliographystyle{Plain} % Plain referencing style
+\bibliography{literature} % Use the example bibliography file sample.bib
 
@@
 
-Etiam fermentum, arcu ut gravida fringilla, dolor arcu laoreet justo, ut imperdiet urna arcu a arcu. Donec nec ante a dui tempus consectetur. Cras nisi turpis, dapibus sit amet mattis sed, laoreet.
+We thank Professors of Boston College, Department of Economics for the support during the realization of this project.
 

### 2018-09-12 Latex/Poster_Session/poster_session.tex
tiny change in poster
poster update

@@
 \begin{minipage}[b]{0.55\linewidth}
-\veryHuge \color{NavyBlue} \textbf{ICT and Future Productivity} \color{Black}\\ % Title
-\Huge\textit{Evidence and Theory of a GPT}\\[1cm] % Subtitle
-\huge \textbf{Marco Brianti \& Laura Gati}\\ % Author(s)
+\veryHuge \color{NavyBlue} \textbf{ICT-Specific Investment Shocks and Economic  \\ Fluctuations} \color{Black}\\ % Title
+\Huge\textit{Evidence and Theory of a General-Purpose Technology}\\[1cm] % Subtitle
+\huge \textbf{Marco Brianti \& Laura G\'ati}\\ % Author(s)
 \huge Boston College\\ % University/organization
@@
 
-In response to this shock, ICTI rises on impact and remains significant for several quarters.
+In response to the ICT shock, ICTI rises on impact and remains significant for several quarters.
 RP persistently and significantly declines for more than two years, suggesting that we are indeed identifying the correct sectoral shock.

### 2018-11-09 Latex/MacroLunch_Nov2018/Slides_Nov2018.tex
some work on prezzy, almost done

\documentclass{beamer}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{float}
%\usepackage{natbib}
\usepackage{csquotes}
\usepackage{sansmathaccent}
\usepackage{subfigure}
\usepackage{multicol}
\pdfmapfile{+sansmathaccent.map}
\usepackage{mathtools}
\def \ourFigPath {../../} 
\def \MainFigures{../Draft_Summer2018/MainFigures}
\def \ourTablePath {../../Tables/} 
\def\myFigWidth{2.0in}

\setbeamersize{text margin left=5mm,text margin right=12mm} 
%
\font\reali=msbm10 at 12pt
% subsets of real numbers
\newcommand{\numberset}{\mathbb}
\newcommand{\real}{\hbox{\reali R}}
\newcommand{\N}{\numberset{N}}
\newcommand{\realp}{\hbox{\reali R}_{\scriptscriptstyle +}}
\newcommand{\realpp}{\hbox{\reali R}_{\scriptscriptstyle ++}}
\newcommand{\virgolette}[1]{``#1''}
%

\author[Brianti, G\'ati]{Marco Brianti and Laura G\'ati}

\institute[Boston College]{Boston College}

\title[ICT]{ICT and Future Productivity: Evidence and Theory of a GPT}

\date{June 2018}

\usetheme{Warsaw}

\begin{document}

\begin{frame}

\maketitle

\end{frame}

% Structure:
% 1. Motivation: the triumvirate of medium-run BC, ICT and SVAR literature on things that affect future stuff
% 2. This paper: 1. run a VAR with ICT identified properly, get surprising results  2. Try to interpret those along the ICT literature: is ICT a GPT?
% 3. Show VAR
% 4. Show model

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Motivation}

	\begin{itemize}

		\item Point of departure: medium-run business cycle models \`a la Comin \& Gertler (2006).

		\

		\item Key prediction: BC fluctuations of a particular kind of investment (research \& development (R\&D) $\rightarrow$ adoption) lead total factor productivity (TFP)

		\

	\item The Great Recession 2008 casts doubt on whether this is all of the story (Fernald et al. (2017)).

	\

	\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Wrong timing}

		\vspace{-1cm}
	\noindent
	\begin{figure}
		\centering
		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_RD_level_macrolunch_30-Nov-2017_11_31_04}
	\end{figure}

	Fernald et al. (2017): ``R\&D and adoption cannot be the whole story''.

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{}

		\noindent
	\begin{figure}
		\centering
		\includegraphics[scale=0.29]{\ourFigPath Figures/fig_IT_level_macrolunch_30-Nov-2017_11_37_26}
	\end{figure}

	\begin{itemize}

		\item [$\rightarrow$] A variable with at least the right timing is investment in information and communication technologies (ICT)

	\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{This paper}

	\begin{enumerate}
	\item Stick ICT investment (ICT-I) in a VAR and explore how an identified shock to this affects TFP.
	\item [] ICT shock = a shock to the productivity of the ICT sector today

	\

	\begin{itemize}
	\item [$\rightarrow$] A shock to ICT leads to substantial TFP increases over the medium-run.
	\end{itemize}

\

    \item Draw on the conclusions of the ICT literature (references!) to build a structural model to interpret the results.

    \

    	\begin{itemize}
	\item [$\rightarrow$] ICT literature: ICT is a general-purpose technology (GPT).

	\

	\item[$\Rightarrow$] Estimate a two-sector endogenous growth model to ask whether aggregate data supports this interpretation. 
	\end{itemize}

	\end{enumerate}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% HERE HERE HERE
% - complete ICT literature references 
% - implement roadmap
% - edit title

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Related literature}

	\begin{enumerate}
	\item Medium-run business cycles 
		\begin{itemize}
		\item Comin \& Gertler (2006), Bianchi et al. (2014), Moran \& Queralto (2017), Guerron \& Jinnai (2015)
		\end{itemize}

	\

	\item ICT and productivity 
		\begin{itemize}
		\item Oliner \& Stichel (2000), Stiroh(2002), 
		\end{itemize}

	\

	\item Identification of news shocks in SVARs
		\begin{itemize}
		\item Beaudry \& Portier (2006), Barsky \& Sims (2011)
		\end{itemize}

	\

	\item Multi-sector growth models
		\begin{itemize}
		\item Greenwood, Hercowitz \& Krusell (1997), Oulton (2007), Fisher (2006), Whelan (2003)
		\end{itemize}
	\end{enumerate}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{Roadmap}

EDIT THIS LATER
\begin{enumerate} 
	\item SVAR analysis: identifying an ICT shock

	\

	\

	\item A two-sector endogenous growth model

	\

\end{enumerate}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{1. SVAR analysis}

	We run a SVAR using aggregate, quarterly US data. The data vector is:

	\begin{equation}
	\mathbf{X_t} = 
	\begin{bmatrix}
    TFP_t      \\

   ICTI_t   \\

   GDP_t \\

   C_t \\

   RP_t
\end{bmatrix}
	\end{equation}

\

\

\begin{itemize}
\item $RP = \pi^{IT}/\pi^{CPI}$. 
\item All variables are real (except price indexes) and in log levels (except for RP, which is in growth rates). 
\item The dataset ranges from 1989:q1 - 2017:q2.
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Baseline identification}
	\label{baseline_spec}

\begin{equation}\label{eq:mainObjective}
\max_{\gamma_j} \Pi_{2,j}(0) = e_2' \tilde{A}_0 \gamma_j
\end{equation}
subject to
\begin{equation}\label{eq:mainZeroTFP}
\Pi_{1,j}(0) = e_1' \tilde{A}_0 \gamma_j = 0, \ \ \text{and}
\end{equation}
\begin{equation}\label{eq:mainOrtho}
\gamma_j' \gamma_j = 1
\end{equation}
where $j$ represents the arbitrary position of the ICT shock.

	\begin{itemize}
	 \item[(2)] maximal impact effect on ICTI. 
	 \item[(3)] no impact effect on TFP. 
	 \item[(4)]$\gamma_j$ comes from an orthogonal matrix.

	\end{itemize}

\hyperlink{VAR_notation}{\beamerbutton{VAR}}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Why this identification?}

	\begin{itemize}
	\item ICT value added is less than 5\% of GDP (BEA, April 2018)

	$\rightarrow$ ICT-I increases shouldn't affect TFP on impact.

	\

	\

	\item Prediction of multisector models (GHK): sectoral productivity increase leads to sectoral output becoming cheaper

	$\rightarrow$ ICT-I should rise after ICT productivity shock.
	\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%
%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Our favorite specification}

	\begin{itemize}
	\item Recall: dataset is quarterly and covers 1989:q1-2017-q2.

	\

	\item One lag (as suggested by BIC and HQ).

	\

	\item Horizon of FEV-maximization: 60 quarters.

	\

	%\item Restriction on relative prices after a news shock is imposed at 8 quarters.

	\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Results}

\begin{figure}[h!]
\begin{center}
\includegraphics[scale=0.25]{\MainFigures/fig_ICT_Shock_on_TFP_empirical_noH}
\label{fig:TFP_main}
\end{center}
\end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Results II}

\begin{figure}[h!]
%\caption{Best Responses of $\sigma_1^2$} 
%\centering
\subfigure{\includegraphics[width=   \myFigWidth]{\MainFigures/fig_ICT_Shock_on_Real_ICT_Investment_empirical_noH}} \hspace{.2in%
} 
\subfigure{\includegraphics[width=  \myFigWidth]{\MainFigures/fig_ICT_Shock_on_Real_GDP_empirical_noH}} \hspace{.2in%
} 
\subfigure{\includegraphics[width=   \myFigWidth]{\MainFigures/fig_ICT_Shock_on_Real_Consumption_empirical_noH}} \hspace{.2in%
} 
\subfigure{\includegraphics[width=   \myFigWidth]{\MainFigures/fig_ICT_Shock_on_Relative_Price_empirical_noH}} 
\end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Results III}

\begin{table}[h!]
 		\begin{center}
 \begin{tabular}{lcccccccccc}
\hline
 	& $h = 1$ & $h = 4$ & $h = 8$ & $h = 16$ & $h = 24$ & $h = 40$ \\
 	\hline
TFP &  0       &  0.0023  &  0.0194 &   0.1088 &   0.2273  &  0.3382 \\
ICT-I &  0.9997  &  0.9038  &  0.7964 &   0.6320 &   0.5310  &  0.4371 \\
Real GDP &  0.2620  &  0.3061  &  0.3486 &   0.3936 &   0.4046  &  0.3881 \\
Real C &  0.1952  &  0.2638  &  0.3219 &   0.3931 &   0.4188  &  0.4064 \\
Relative Prices &  0.0618  &  0.0967  &  0.1276 &   0.1511 &   0.1516  &  0.1467 \\	
\hline
 	\end{tabular}
  		%\caption{The letter $h$ denotes the forecast horizon. The numbers refer to the fraction of the forecast error variance of each variable at various forecast horizons to the identified ICT shock}
  \label{table:vardec}
  \end{center}
 \end{table}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Robustness checks}
	\label{robustness_checks}

\begin{itemize}
\item Main critique: reverse causality from news about future TFP.

\

\

\item[$\rightarrow$] Alternative specification filters out news to recover an alternative ICT shock series

\hyperlink{controlling_news}{\beamerbutton{Alternative specification}}	
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{The two recovered ICT shock series}

\begin{figure}[h!]
\includegraphics[width=   4.55in]{\MainFigures/Removing_FLVariables}
\end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Interpretation of results}

	\begin{itemize}
	\item ICT-I leads to significant and persistent TFP increases in the medium run.

	\

	\

	\item ICT literature: it's a general purpose technology (GPT)!

	\

	\

	\item[$\rightarrow$] embed in a structural model and estimate whether data favors the GPT-interpretation.
	\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
\frametitle{Roadmap}

EDIT THIS LATER
\begin{enumerate} 
	\item SVAR analysis: identifying an ICT shock

	\

	\

	\item A two-sector endogenous growth model

	\

\end{enumerate}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{2. Model - in a nutshell}

	\begin{itemize}
	\item Belongs to the class of (GHK) models

	(we use isomorphic formulation of Oulton)

	\

	\item Key: two sectors with identical production functions
	\item[$\rightarrow$] with an externality capturing the GPT-nature of ICT-capital.

	\

	\

	\item	Rest of model perfectly standard.
	\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Two sectors}

Consumption-good sector
\begin{eqnarray}\label{equation:production_FINAL}
y^c_t(j) = A^c_t \ \big( k^c_{t}(j) \big)^a \ \big( k^i_{t}(j) \big)^b \ \big( l_{t}(j) \big)^{1-a-b}, \ \ 0 < a,b < 1
\end{eqnarray}

\

ICT-good sector
\begin{eqnarray}\label{equation:productionICT}
y^i_t(q) = A_t^i \ \big( k^c_{t}(q) \big)^a \ \big( k^i_{t}(q) \big)^b \ \big( l_{t}(q) \big)^{1-a-b}, \ \ 0 < a,b < 1
\end{eqnarray}

\

with

\

\centering
$ A_t^c = \eta_t \ \theta^c_t \ \textcolor{red}{(k^i_{t})^{\gamma}}  $

\

$A_t^i = \eta_t \ \theta^i_t \ \textcolor{red}{(k^i_{t})^{\gamma}} $

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Uses of outputs and GDP}

Consumption-good sector

$$
y^c_t = c_t + i^c_t
$$

ICT-good sector

$$
y^i_t = i^i_t
$$

\

GDP is 
$$
GDP_t = (1 - w) y^c_t+ w y^i_t \ \ \ \text{where} \ \ \ w = \frac{p_t y^i_t }{y^c_t + p_t y^i_t }
$$

with

$$
p_t = \frac{p_t^i}{p_t^c} \quad \text{where we normalize} \quad p_t^c = 1
$$

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{TFP in the model}

Can be computed 2 ways:

\begin{align*}
&1) \;\; TFP_t = (1 - w) TFP_t^c + w TFP_t^i \\
\\
& 2) \;\; g_{TFP} = g_{GDP} - a g_{k^c} -b g_{l} - (1-a-b)g_{k^i}
\end{align*}

\

where for a variable $X$, $g_x \coloneqq \text{ln}\left(\frac{X_t}{X_{t-1}}\right)$.

\

In the model, the latter is equivalent to

\begin{equation}
g_{TFP} = g_{\eta} + wg_{\theta^c} + (1-w)g_{\theta^i} +\textcolor{red}{\gamma}  g_{k^i}
\end{equation}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Impulse-response matching - does data support $\gamma>0$?}

Estimate three parameters: $\Omega = (\gamma, \ \sigma_{\iota}^2, \ \rho_{\iota})$ with

\begin{itemize}
\item $\sigma_{\iota}^2 =$ the variance of an ICT technology shock
\item $\rho_{\iota}=$ the persistence of the same shock
\item $\gamma=$  the size of the spillover effect of ICT capital on TFP
\end{itemize}

\

We estimate $\Omega$ as
\begin{eqnarray}\label{equation:min_prob_IRmatching}
\min_{\Omega} \big[  \hat{\Psi} - \Psi(\Omega)  \big]' \Lambda \big[  \hat{\Psi} - \Psi(\Omega)  \big]
\end{eqnarray}

\begin{itemize}
\item $\Psi(\Omega) =$ mapping from $\Omega$ to the theoretical impulse responses
\item $\hat{\Psi} =$ the empirical impulse responses of an ICT shock to TFP, ICTI, C and RP
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{IR-matching results I}

	\begin{table}[h!]
	\begin{center}
		\begin{tabular}{clc}
			\hline
			Symbol & Economic Interpretation & Estimated Value \\
			\hline
            $\sigma^2_{\iota}$ & Variance of ICT technological shock &   $0.01$  \\
            $\rho_{\iota}$     & Persistence of ICT technological shock & $0.9$   \\
            $\gamma$           & Size of spillover of ICT capital on TFP &  $0.5881$ \\
			\hline
		\end{tabular}
		%\caption{Estimation of key parameters by imposing model's impulse responses of an ICT shock to be as close as possible to the empirical ones. Theoretical estimates are impulse responses to an ICT-specific technological shock, $\zeta_t$ which are functions of key parameters: $\sigma_{\iota}^2$, $\rho_{\iota}$, and $\gamma$. Empirical impulse responses of an ICT shock to TFP, ICTI, consumption, and relative prices are derived from Specification \ref{eq:mainSpecification} using the empirical strategy presented in Section \ref{section:empiricalstrategy_simple}. According to what presented in Appendix \ref{section:mainSetResults}, we use a horizon of $40$ periods for each response.}
		\label{table:estimated_parameters}
	\end{center}
\end{table}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{IR-matching results II}

\begin{figure}[h!]
%\caption{Best Responses of $\sigma_1^2$} 
%\centering
\subfigure{\includegraphics[width=   \myFigWidth]{\MainFigures/fig_ICT_Shock_on_TFP_IRmatching_together}} \hspace{.2in%
} 
\subfigure{\includegraphics[width=  \myFigWidth]{\MainFigures/fig_ICT_Shock_on_ICTI_IRmatching_together}} \hspace{.2in%
} 
\subfigure{\includegraphics[width=   \myFigWidth]{\MainFigures/fig_ICT_Shock_on_C_IRmatching_together}} \hspace{.2in%
} 
\subfigure{\includegraphics[width=   \myFigWidth]{\MainFigures/fig_ICT_Shock_on_RP_IRmatching_together}} 
\end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{The spillover drives the TFP-response}
\begin{figure}[h!]
\begin{center}
\includegraphics[scale=0.13]{\MainFigures/fig_ICT_Shock_on_TFP_IRmatching_together_gam_set_to0point1}
\caption{Setting $\gamma =0.1$}
\label{fig:TFP_main}
\end{center}
\end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Conclusion}

\begin{itemize}
\item SVAR analysis uncovered interesting pattern between ICT productivity and TFP.

\

	\begin{itemize}
	\item[$\rightarrow$] An ICT shock leads to delayed but persistent TFP increases.
	\end{itemize}

\

\

\item Two-sector structural model with a spillover from ICT-capital can rationalize results.

\

	\begin{itemize}
	\item[$\rightarrow$] Estimation of the model suggests that data supports the GPT-interpretation of ICT.
	\end{itemize}
\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
\centering
	THANK YOU!

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%                     APPENDIX  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Notation in detail}
	\label{VAR_notation}
The reduced-form VAR is
$$
y_t = B(L)y_{t-1} + i_t 
$$

\

Mapping between innovations $i_t$ to structural shocks $s_t$
$$
A_0 s_t = i_t
$$
\

$\rightarrow$ structural-form VAR is
$$
A_0^{-1}y_t = C(L) y_{t-1} + s_t
$$

\

where $C(L) = A_0^{-1} B(L)$ and $s_t = A_0^{-1} i_t$, and the impact matrix $A_0$ satisfies $\Sigma = A_0 A_0'$.

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{}

For any arbitrary orthogonalization $\tilde{A}_0 \; : \; \Sigma = \tilde{A}_0 \tilde{A}_0'$, a rotation using an orthogonal matrix $D$ ($DD' = I$) allows us to back out impact matrix as $A_0 = \tilde{A}_0 D$.

\

$\rightarrow$ The matrix of impact responses to all shocks is: 
$$
\Pi(0) = \tilde{A}_0 D
$$

\

Specifically, denoting the responses of variable $i$ to shock $j$, it is
$$
\Pi_{i,j}(0) = e_i' \tilde{A}_0 D e_j
$$
where $e_k$ is a selector column vector.

Denote $\gamma_j \coloneqq De_j$, a specific column of $D$.

\

$\rightarrow \tilde{A}_0\gamma_j =$the vector of impact responses of all variables to shock $j$.

\

\hyperlink{baseline_spec}{\beamerreturnbutton{Return}}	
\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Controlling for news}
	\label{controlling_news}
\textbf{Step 1 - Identification of $\gamma_{news}$}

\

\

$$
\max_{\gamma_{news}} \Omega_{1,news}(h) = \frac{ \sum_{t=0}^h e_1' B^t \tilde{A}_0 \gamma_{news} \gamma_{news}' \tilde{A}_0' B'^t e_1 } {e_1' ( \sum_{\tau = 0}^H B^t \Sigma B'^t )e_1}
$$

\

subject to

\

$$
\Pi_{1,news}(0) = 0,
$$
$$
\Pi_{6,news}(0) = \Pi_{6,news}(1) = \Pi_{6,news}(2) = 0, \ \ \text{and}
$$
$$
\gamma_{news} \gamma_{news}' = 1.
$$

\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Controlling for news}
\textbf{Step 2 - Identification of $\gamma_{ICT}$}

\

$$
\max_{\gamma_{ICT}} \Pi_{2,ICT}(0) =  e_2' \tilde{A}_0 \gamma_{ICT} 
$$

\

subject to

\

$$
\Pi_{1,ICT}(0) = 0,
$$
$$
\gamma_{news} \gamma_{ICT}' = 0, \ \ \text{and} \ \ \gamma_{ICT} \gamma_{ICT}' = 1.
$$

\

\

\hyperlink{robustness_checks}{\beamerreturnbutton{Return}}	
\end{frame}
%%%%%%%%%%%%%%%%%

%%%%%%% Slide %%%%%%
\begin{frame}
	\frametitle{Robustness checks for the news specification}

\begin{itemize}
\item Different variables
	\begin{itemize}
	\item Add the Michigan index of consumer confidence (expected business conditions 5 years ahead)

	\

	\item Replace IT prices with capital prices (following Comin \& Gertler)

	\

	\item Replace CPI inflation with PCE inflation
	\end{itemize}

	\

\item Different horizons at which we impose the restriction on relative prices for the news shock
\item[] $\rightarrow$ ran  6, 8, 10, 12 and 16 quarters.

\

\item Increase the number of lags (2)

\

\item Check whether VAR is information-sufficient to identify the news shock (Forni-Gambetti test) (p-val of 12\%)
\end{itemize}

\

\hyperlink{robustness_checks}{\beamerreturnbutton{Return}}

\end{frame}
%%%%%%%%%%%%%%%%%

\end{document}

### 2018-11-10 Latex/MacroLunch_Nov2018/Slides_Nov2018.tex
presentation is finished
maybe you can have a look to it and then we can discuss sometime early
next week?

@@
 \def\myFigWidth{2.0in}
+\def\myFigWidthAlt{1.5in}
 
@@
 
-\title[ICT]{ICT and Future Productivity: Evidence and Theory of a GPT}
+\title[ICT \& medium-run TFP]{ICT and Future Productivity: Evidence and Theory of a GPT}
 
@@
 \usetheme{Warsaw}
+
+\AtBeginSection[]
+{
+  \begin{frame}<beamer>
+    \frametitle{Roadmap}
+    \tableofcontents[currentsection]
+  \end{frame}
+}
 
@@
 
-		\item Key prediction: BC fluctuations of a particular kind of investment (research \& development (R\&D) $\rightarrow$ adoption) lead total factor productivity (TFP)
+		\item Key prediction: BC fluctuations of a particular kind of investment (research \& development (R\&D) $\rightarrow$ adoption) lead total factor productivity (TFP).
 
@@
 
-	Fernald et al. (2017): ``R\&D and adoption cannot be the whole story''.
+	Fernald et al. (2017): ``R\&D and adoption can't be the whole story''.
 
@@
 
-		\item [$\rightarrow$] A variable with at least the right timing is investment in information and communication technologies (ICT)
+		\item [$\rightarrow$] A suspect is investment in information and communication technologies (ICT).
 
@@
 
-    \item Draw on the conclusions of the ICT literature (references!) to build a structural model to interpret the results.
+    \item Draw on the conclusions of the ICT literature to build a structural model to interpret the results.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% HERE HERE HERE
-% - complete ICT literature references 
-% - implement roadmap
-% - edit title
-
 %%%%%%% Slide %%%%%%
@@
 		\begin{itemize}
-		\item Oliner \& Stichel (2000), Stiroh(2002), 
+		\item Jorgenson \& Stiroh (1999), Oliner \& Stichel (2000),  Brynjolffson \& Lorin (2000), Stiroh (2002) %Brynjolffson \& Yang (1999) %use stock market valuations of firms to identify the value of IT assets
 		\end{itemize}
@@
 
-%%%%%%% Slide %%%%%%
-\begin{frame}
-\frametitle{Roadmap}
-
-EDIT THIS LATER
-\begin{enumerate} 
-	\item SVAR analysis: identifying an ICT shock
-
-	\
-
-	\
-
-	\item A two-sector endogenous growth model
-
-	\
-
-\end{enumerate}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{SVAR Analysis}
+%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 	\begin{itemize}
-	\item ICT value added is less than 5\% of GDP (BEA, April 2018)
+	\item ICT value added is less than 5\% of GDP (BEA, April 2018).
 
@@
 
-	\item Prediction of multisector models (GHK): sectoral productivity increase leads to sectoral output becoming cheaper
+	\item Prediction of multisector models (GHK): sectoral productivity increase leads to sectoral output becoming cheaper.
 
@@
 	\frametitle{Results II}
+	\label{results2}
 
@@
 
+\hyperlink{largeVAR}{\beamerbutton{Results for a larger-scale VAR}}	
 \end{frame}
@@
 
-\item[$\rightarrow$] Alternative specification filters out news to recover an alternative ICT shock series
+\item[$\rightarrow$] Alternative specification filters out news to recover an alternative ICT shock series.
 
@@
 
-%%%%%%% Slide %%%%%%
-\begin{frame}
-\frametitle{Roadmap}
-
-EDIT THIS LATER
-\begin{enumerate} 
-	\item SVAR analysis: identifying an ICT shock
-
-	\
-
-	\
-
-	\item A two-sector endogenous growth model
-
-	\
-
-\end{enumerate}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Structural Model}
+%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 	\begin{itemize}
-	\item Belongs to the class of (GHK) models
+	\item Belongs to the class of Greenwood, Hercowitz \& Krusell (GHK) models.
 
-	(we use isomorphic formulation of Oulton)
+	(We use isomorphic formulation of Oulton (2007).)
 
@@
 \begin{frame}
+	\frametitle{IRFs for a larger-scale VAR I (2 lags)}
+	\label{largeVAR}
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[scale=0.25]{\ourFigPath Figures/fig_ICT_Shock_on_TFPUtil_empirical_fullEconomy}
+%\caption{Setting $\gamma =0.1$}
+\end{center}
+\end{figure}
+
+\
+
+\hyperlink{results2}{\beamerreturnbutton{Return}}	
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{IRFs for a larger-scale VAR II (2 lags)}
+
+\begin{figure}[h!]
+%\caption{Best Responses of $\sigma_1^2$} 
+%\centering
+
+\subfigure{\includegraphics[width=  \myFigWidthAlt]{\ourFigPath Figures/fig_ICT_Shock_on_Consumption_empirical_fullEconomy}} \hspace{.2in%
+} 
+\subfigure{\includegraphics[width=   \myFigWidthAlt]{\ourFigPath Figures/fig_ICT_Shock_on_GDP_empirical_fullEconomy}} \hspace{.2in%
+} 
+\subfigure{\includegraphics[width=   \myFigWidthAlt]{\ourFigPath Figures/fig_ICT_Shock_on_Hours_empirical_fullEconomy}} \hspace{.2in%
+} 
+\subfigure{\includegraphics[width=   \myFigWidthAlt]{\ourFigPath Figures/fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}} \hspace{.2in%
+} 
+\subfigure{\includegraphics[width=   \myFigWidthAlt]{\ourFigPath Figures/fig_ICT_Shock_on_Investment_empirical_fullEconomy}} \hspace{.2in%
+} 
+\subfigure{\includegraphics[width=   \myFigWidthAlt]{\ourFigPath Figures/fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}} 
+\end{figure}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
 	\frametitle{Controlling for news}

### 2018-11-13 Latex/MacroLunch_Nov2018/Slides_Nov2018.tex
edited presentation based on yesterday's run-thru
didn’t change variables though, to stay consistent with IR-matching

@@
 
-\title[ICT \& medium-run TFP]{ICT and Future Productivity: Evidence and Theory of a GPT}
+\title[ICT \& medium-run TFP]{ICT and Future Productivity \\
+Evidence and Theory of a GPT}
 
@@
 	\frametitle{Motivation}
+	\label{motivation}
 
@@
 
-	\item The Great Recession 2008 casts doubt on whether this is all of the story (Fernald et al. (2017)).
+	\item Fernald et al. (2017): the Great Recession 2008 casts doubt on whether this is all of the story.
 
@@
 
-\end{frame}
-%%%%%%%%%%%%%%%%%
+		\
 
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Wrong timing}
-
-		\vspace{-1cm}
-	\noindent
-	\begin{figure}
-		\centering
-		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_RD_level_macrolunch_30-Nov-2017_11_31_04}
-	\end{figure}
-
-	Fernald et al. (2017): ``R\&D and adoption can't be the whole story''.
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{}
-
-		\noindent
-	\begin{figure}
-		\centering
-		\includegraphics[scale=0.29]{\ourFigPath Figures/fig_IT_level_macrolunch_30-Nov-2017_11_37_26}
-	\end{figure}
-
-	\begin{itemize}
-
-		\item [$\rightarrow$] A suspect is investment in information and communication technologies (ICT).
-
-	\end{itemize}
+\hyperlink{wrong_timing}{\beamerbutton{Argument}}
 
@@
 	\begin{enumerate}
-	\item Stick ICT investment (ICT-I) in a VAR and explore how an identified shock to this affects TFP.
+	\item Stick aggregate ICT investment (ICT-I) in a VAR and explore how an identified shock to this affects TFP.
 	\item [] ICT shock = a shock to the productivity of the ICT sector today
@@
 \begin{frame}
-	\frametitle{Baseline identification}
+	\frametitle{Baseline identification: Cholesky}
 	\label{baseline_spec}
 
-\begin{equation}\label{eq:mainObjective}
-\max_{\gamma_j} \Pi_{2,j}(0) = e_2' \tilde{A}_0 \gamma_j
-\end{equation}
-subject to
-\begin{equation}\label{eq:mainZeroTFP}
-\Pi_{1,j}(0) = e_1' \tilde{A}_0 \gamma_j = 0, \ \ \text{and}
-\end{equation}
-\begin{equation}\label{eq:mainOrtho}
-\gamma_j' \gamma_j = 1
-\end{equation}
-where $j$ represents the arbitrary position of the ICT shock.
+	The ICT shock is assumed to have
+
+	\
 
 	\begin{itemize}
-	 \item[(2)] maximal impact effect on ICTI. 
-	 \item[(3)] no impact effect on TFP. 
-	 \item[(4)]$\gamma_j$ comes from an orthogonal matrix.
+	\item no impact effect on TFP;
 
+	\
+
+	\item maximal impact effect on ICT-I.
 	\end{itemize}
 
-\hyperlink{VAR_notation}{\beamerbutton{VAR}}
+%\hyperlink{VAR_notation}{\beamerbutton{VAR}}
 
@@
 	$\rightarrow$ ICT-I should rise after ICT productivity shock.
-	\end{itemize}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{Our favorite specification}
-
-	\begin{itemize}
-	\item Recall: dataset is quarterly and covers 1989:q1-2017-q2.
-
-	\
-
-	\item One lag (as suggested by BIC and HQ).
-
-	\
-
-	\item Horizon of FEV-maximization: 60 quarters.
-
-	\
-
-	%\item Restriction on relative prices after a news shock is imposed at 8 quarters.
-
 	\end{itemize}
@@
 \begin{frame}
-	\frametitle{Uses of outputs and GDP}
+	\frametitle{Uses of outputs}
+	\label{uses}
 
@@
 
-GDP is 
-$$
-GDP_t = (1 - w) y^c_t+ w y^i_t \ \ \ \text{where} \ \ \ w = \frac{p_t y^i_t }{y^c_t + p_t y^i_t }
-$$
-
-with
-
-$$
-p_t = \frac{p_t^i}{p_t^c} \quad \text{where we normalize} \quad p_t^c = 1
-$$
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
-	\frametitle{TFP in the model}
-
-Can be computed 2 ways:
-
-\begin{align*}
-&1) \;\; TFP_t = (1 - w) TFP_t^c + w TFP_t^i \\
-\\
-& 2) \;\; g_{TFP} = g_{GDP} - a g_{k^c} -b g_{l} - (1-a-b)g_{k^i}
-\end{align*}
-
 \
 
-where for a variable $X$, $g_x \coloneqq \text{ln}\left(\frac{X_t}{X_{t-1}}\right)$.
-
-\
-
-In the model, the latter is equivalent to
-
-\begin{equation}
-g_{TFP} = g_{\eta} + wg_{\theta^c} + (1-w)g_{\theta^i} +\textcolor{red}{\gamma}  g_{k^i}
-\end{equation}
+\hyperlink{tfp_in_model}{\beamerbutton{TFP in the model}}
 
@@
 	\frametitle{Impulse-response matching - does data support $\gamma>0$?}
+	\label{IRmatching}
 
@@
 \end{itemize}
+
+\
+
+and calibrate the rest.  \hyperlink{calibration}{\beamerbutton{Calibration}}
 
@@
 \begin{frame}
-	\frametitle{The spillover drives the TFP-response}
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[scale=0.13]{\MainFigures/fig_ICT_Shock_on_TFP_IRmatching_together_gam_set_to0point1}
-\caption{Setting $\gamma =0.1$}
-\label{fig:TFP_main}
-\end{center}
-\end{figure}
-
-\end{frame}
-%%%%%%%%%%%%%%%%%
-
-%%%%%%% Slide %%%%%%
-\begin{frame}
 	\frametitle{Conclusion}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Wrong timing}
+	\label{wrong_timing}
+
+		\vspace{-1cm}
+	\noindent
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.28]{\ourFigPath Figures/fig_RD_level_macrolunch_30-Nov-2017_11_31_04}
+	\end{figure}
+
+	Fernald et al. (2017): ``R\&D and adoption can't be the whole story''.
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{}
+
+		\noindent
+	\begin{figure}
+		\centering
+		\includegraphics[scale=0.29]{\ourFigPath Figures/fig_IT_level_macrolunch_30-Nov-2017_11_37_26}
+	\end{figure}
+
+\
+
+\hyperlink{motivation}{\beamerreturnbutton{Return}}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
 
@@
 
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{TFP in the model}
+	\label{tfp_in_model}
+
+Can be computed 2 ways:
+
+\begin{align*}
+&1) \;\; TFP_t = (1 - w) TFP_t^c + w TFP_t^i \\
+\\
+& 2) \;\; g_{TFP} = g_{GDP} - a g_{k^c} -b g_{l} - (1-a-b)g_{k^i}
+\end{align*}
+
+\
+
+where for a variable $X$, $g_x \coloneqq \text{ln}\left(\frac{X_t}{X_{t-1}}\right)$.
+
+\
+
+In the model, the latter is equivalent to
+
+\begin{equation}
+g_{TFP} = g_{\eta} + wg_{\theta^c} + (1-w)g_{\theta^i} +\textcolor{red}{\gamma}  g_{k^i}
+\end{equation}
+
+\
+
+\hyperlink{uses}{\beamerreturnbutton{Return}}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{GDP and relative prices in the model}
+	\label{tfp_in_model}
+
+\
+
+GDP is 
+$$
+GDP_t = (1 - w) y^c_t+ w y^i_t \ \ \ \text{where} \ \ \ w = \frac{p_t y^i_t }{y^c_t + p_t y^i_t }
+$$
+
+with
+
+$$
+p_t = \frac{p_t^i}{p_t^c} \quad \text{where we normalize} \quad p_t^c = 1
+$$
+
+\
+
+\hyperlink{uses}{\beamerreturnbutton{Return}}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
+%%%%%%% Slide %%%%%%
+\begin{frame}
+	\frametitle{Calibration}
+	\label{calibration}
+
+\begin{table}[h!]
+\footnotesize
+	\begin{center}
+		\begin{tabular}{clcl}
+			\hline
+			 & Economic Interpretation &  Value & Reference\\
+			\hline
+            $\beta$ & Discount factor of households &   $0.97^{\frac{1}{4}}$ & Match 3M-T-bill return \\
+            $\delta^c$     & Depreciation of hard capital & $0.0206$  & BEA\\
+            $\delta^i$           & Depreciation of ICT capital &  $0.0398$ & BEA \\
+            $a$           & Hard capital share & $0.3$  & Standard value\ \\
+            $b$           & ICT capital share &  $0.031$ & Oulton (2012) \\
+            $\Gamma^c$           & Steady state growth rate of hard capital &  $1.0034$ & See below   \\
+            $\Gamma^i$           & Steady state growth rate of ICT capital &  $1.0160$ & See below\\
+            $\chi$           & Frisch elasticity &  $1$ & Standard value \\ 
+			\hline
+		\end{tabular}
+		%\caption{$\beta$: Match average yield of 3month T-bill 1989:Q1-2017:Q1. $delta^i: match the higher of two BEA annual depreciation items that both correspond to ICT }
+		\label{table:estimated_parameters}
+	\end{center}
+\end{table}
+
+Get $(\Gamma^c, \Gamma^i)$ by solving the following model-implied steady state system
+
+\begin{equation}\label{equation:system_param}
+\begin{cases}
+ \frac{p_t}{p_{t-1}}  = \frac{\Gamma^c}{\Gamma^i} \\
+ \frac{c_t}{c_{t-1}}  = (\Gamma^c)^{\frac{1-b-\gamma}{1-a-b-\gamma}}  (\Gamma^i)^{\frac{b+\gamma}{1-a-b-\gamma}}
+\end{cases}
+\end{equation}
+
+\hyperlink{IRmatching}{\beamerreturnbutton{Return}}
+
+\end{frame}
+%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2018-11-14 Latex/Conference_Zurich_Dec2018/Slides_Dec2018.tex
edited one bit of presentation for december

--- 2018-11-13 Latex/MacroLunch_Nov2018/Slides_Nov2018.tex
@@
 		\begin{itemize}
-		\item Jorgenson \& Stiroh (1999), Oliner \& Stichel (2000),  Brynjolffson \& Lorin (2000), Stiroh (2002) %Brynjolffson \& Yang (1999) %use stock market valuations of firms to identify the value of IT assets
+		\item Jorgenson \& Stiroh (1999), Oliner \& Sichel (2000),  Brynjolffson \& Lorin (2000), Stiroh (2002) %Brynjolffson \& Yang (1999) %use stock market valuations of firms to identify the value of IT assets
 		\end{itemize}
@@
 	\begin{itemize}
+
+	\item ICT shocks fluctuations are small (recovered shocks in VAR and model are small)
+
+	\
+
 	\item ICT value added is less than 5\% of GDP (BEA, April 2018).
@@
 	\begin{itemize}
-	\item ICT-I leads to significant and persistent TFP increases in the medium run.
+	\item ICT-shock leads to significant and persistent TFP increases in the medium run.
 

### 2019-03-06 Latex/Conference_Modena_March2019/Brianti Gati March 2019.tex
slides for Modena presentation

\documentclass[hyperref={pdfpagelabels=false}]{beamer}
\setbeamercolor{background canvas}{bg=white}
\usepackage{graphicx,lmodern,subfigure,ulem,color,graphicx,tikz,booktabs,natbib}
\usepackage{mathrsfs}
\usetheme{Warsaw}
%\definecolor{beamer@blendedblue}{rgb}{0.1,0.5,0.1}
%\definecolor{ForestGreen}{RGB}{60, 140, 60}
%\setbeamercolor{structure}{fg=beamer@blendedblue}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[frame number]
\bibliographystyle{chicago}
\newcommand{\spitem}{\vspace{.3cm}\item}
\newcommand{\elas}{$E_{labor}$}
%\def \FigPath {Users\th3\Documents\Job_Market_Paper\Code\Figures} 
\DeclareMathOperator{\E}{\mathbb{E}}
\usepackage{makecell}

\title{ICT-Specific Investment Shocks and Economic Fluctuations}
%\\ \bigskip \\ \normalsize{Evidence and Theory of a General-Purpose Technology}
\author{Marco Brianti, Boston College\\Laura G\'ati, Boston College}
\institute{Convegno RECent\\Modena}
\date{March 2019}

\usetheme[
outer/progressbar=foot,
outer/numbering=none
]{metropolis}

\begin{document}

	\frame{\titlepage}

		\frame{\frametitle{Motivation}

	Why did U.S. output grow so slowly since the recession trough in 2009?

	\

	Fernald, Hall, Stock and Watson (2017) empirically show that two components explain nearly all this growth gap
	\begin{enumerate}
		\item Slow growth in total factor productivity (TFP)
		\item Falling labor force participation
	\end{enumerate}

\

In this paper we focus on the slowdown in TFP,
\begin{itemize}
	\item[$\Rightarrow$] Which variable(s) actually boost productivity? Why? 
\end{itemize}

	}

	\frame{\frametitle{An alternative to R\&D Investment}

		Following Romer (1990) and Coming and Gertler (2006), several papers endogenize TFP through \textbf{R\&D investment}
		\begin{itemize}
			\item Financial crisis $\Rightarrow$ $\downarrow$ $Y^D$ $\Rightarrow$ $\downarrow$ R\&D $\Rightarrow$ $\downarrow$ TFP $\Rightarrow$ $\downarrow$ $Y^S$
		\end{itemize}

		\

		Unfortunately, as showed by Oliner et al. (2007) and Jorgerson et al. (2008), TFP have started slowing down \textbf{before} the crisis.
		%\begin{itemize}
		%	\item[$\Rightarrow$] Medium-run business cycle models cannot be the full story
		%\end{itemize}

	\

	We follow an alternative avenue and focus on the relation between \textbf{information and communication technology investment} (ICTI) and future total factor productivity
	\begin{itemize}
			\item \textit{Expenditure in equipment and computer software meant to be used in production (as an input) for more than a year.}
			\end{itemize}

}

\frame{\frametitle{Our Contribution}

	\begin{enumerate}
		\item \textbf{Empirical evidence} that contemporaneous jumps in ICTI explain significant and persistent increases in future TFP
		\begin{itemize}
			\item SVAR techniques on U.S. aggregates to identify supply shocks specific to the ICT sector
		\end{itemize}

	\

	\

		\item We analyze a \textbf{GE model} to rationalize our empirical findings and draw conclusions concerning the nature of ICT 
		\begin{itemize}
		\item We extend the two-sector model of Greenwood et al. (1997) to accommodate for the role of ICT capital in production
		\end{itemize}
	\end{enumerate}

}

	\frame{\frametitle{Information and Communication Technology}

		ICT Investment is defined as \textit{total expenditure in equipment and computer software meant to be used in production (as an input) for more than a year.}
		\begin{itemize}
			\item $\uparrow$ ICT Investment  $\Rightarrow$ $\uparrow$ ICT capital stock in the economy
		\end{itemize}

\

\

	}

	\frame{\frametitle{Motivation: Empirical Challenge in Structural VAR}

	Empirically distinguishing between financial and uncertainty shocks is difficult
	\begin{itemize}
		\item[$\Rightarrow$] financial distress is empirically associated with larger volatility 
	\end{itemize}

\

Within a SVAR framework, this correlation significantly complicates identification of both shocks
\begin{enumerate}
	\item Implausible \textbf{zero-contemporaneous restrictions}
	\begin{itemize}
		\item[$\Rightarrow$] Both $F_t$ and $U_t$ are fast moving
	\end{itemize}	
	\item Unavailable instruments for \textbf{sign restrictions}	
	\begin{itemize}
		\item[$\Rightarrow$] Current theoretical models predict same qualitative effects on both prices and quantities
	\end{itemize}
\end{enumerate}

}

\frame{\frametitle{My contribution}

	I want to take a step back and show evidence and theory that financial and uncertainty shocks are \textbf{qualitative different}.

	\

	In particular,

	\begin{enumerate}
		\item \textbf{Corporate cash holdings} respond differently to financial and uncertainty shocks. 
		\begin{itemize}
			\item[$\Rightarrow$] Identification assumption
			\end{itemize}

		\

		\item I provide a \textbf{new econometric tool} to simultaneously identify two structural shocks when an internal instrument is available.\begin{itemize}
			\item[$\Rightarrow$] Generalized Penalty Function Approach  
		\end{itemize}

	\end{enumerate}
}

\frame{\frametitle{Roadmap}
	\Large{
		$ \ \ \ \ \ $ 1. \textbf{Cash Holdings}

		$ \ \ \ \ \ $ 2. Model

		$ \ \ \ \ \ $ 3. Empirical Strategy

		$ \ \ \ \ \ $ 4. Results

		$ \ \ \ \ \ $ 5. Conclusions
	}
}

\frame{\frametitle{Corporate Cash Holdings}

	\

\textbf{Cash and Cash Equivalents} refer to assets a business holds as ready cash
\begin{itemize}
	\item Coffer as petty cash
	\item Bank accounts
	\item Certificates of deposits
\end{itemize}

\

U.S. large firms have cash equal to about 15\% of total assets.

\

It is a \textbf{stock variable}, 
$$
Cash_t = Cash_{t-1} + NY_t + \delta K_t - I_t + B_t - D_t.
$$

}

\frame{\frametitle{Cross-Sectional Evidence}

	\textbf{Cash} and \textbf{Financial Frictions}
	\begin{itemize}
		\item[$\Rightarrow$] Cash is a substitute for external finance 
		\item[] \textit{Kaplan and Zingales (1997); Almeida, et al. (2004); Campello at al. (2010); Campello et al. (2011).}
	\end{itemize}

\

\textbf{Cash} and \textbf{Uncertainty}
	\begin{itemize}
	\item[$\Rightarrow$] Cash is positively associated with uncertainty shocks 
	\item[] \textit{Han and Qiu (2007); Baum et al. (2008); Bloom et al. (2018); Alfaro et al. (2018).}
\end{itemize}

}

\frame{\frametitle{Aggregate Evidence}

Aggregate quarterly cash (CHEQ) and assets (ATQ) using \textbf{Compustat} from 1961 to 2018.

\

Remove seasonality using 7-term Henderson filter on aggregate cash and aggregate assets and obtain \textbf{Cash2Assets}.

\

	\begin{table}[h!]
	\centering
	\begin{tabular}{llcc} \hline \hline
		                         & $\Delta$GDP         & U                &                   F    \\ 
		\hline
		\textit{Correlations}    &                     &                  &                                            \\ 
		U                        &      $-0.48^{***}$                &                  &                    \\
		F                        &  $-0.36^{***}$   &     $0.22^{***}$       &                             \\ 
		C2A                      &     $-0.06  $               &       $0.43^{***}$      &            $-0.37^{***}$           \\ 
		\hline \hline
	\end{tabular}
\end{table}

}

\frame{\frametitle{Roadmap}
	\Large{
		$ \ \ \ \ \ $ 1. Cash Holdings

		$ \ \ \ \ \ $ 2. \textbf{Model}

		$ \ \ \ \ \ $ 3. Empirical Strategy

		$ \ \ \ \ \ $ 4. Results

		$ \ \ \ \ \ $ 5. Conclusions
	}
}

%\frame{\frametitle{Economic Intuition I}

%To provide an economic intuition of the differential response of \textbf{cash holdings} to uncertainty and financial shocks, I present a properly augmented model in the spirit of 
%\begin{itemize}
	%\item Almeida, Campello, and Weisbach (2004)
	%\item Han and Qiu (2007)
%\end{itemize}

%\

%It is a simple representation of a dynamic setting where a credit-constrained profit-maximizing firm has a trade-off between present and future investment opportunities

%}

\frame{\frametitle{Model - General Setup}

\begin{itemize}

\item \textbf{Three-period partial equilibrium} model

\

\item Firm \textbf{maximizes} sum of \textbf{dividends} 
\begin{itemize}
\item Discount factor $\beta$ is one
\end{itemize}

\

\item \textbf{Choice variables} are
\begin{itemize}
	\item \textbf{Investments} $i_0$ and $i_1$ in period 0 and 1
	\item Amount to \textbf{borrow} $b_0$ and $b_1$ in period 0 and 1
	\item \textbf{Cash} $c$ in period 0 to be carried in period 1
\end{itemize}

\

\item Feature \textbf{financial frictions} in the form of risk premium

\

\item \textbf{Gross returns} $g(\cdot)$ happen in the last period for both investments
\begin{itemize}
	\item where $g'(\cdot) > 0$ and $g''(\cdot) < 0$.
\end{itemize}

	\end{itemize}

}

\frame{\frametitle{Model - Analytical Setup}

\begin{itemize}
	\item[]
\begin{itemize}
     \item[Period 0] $ \ \ \ d_0 = y_0 + b_0 - i_0 - c$

	\

	\item[Period 1] $ \ \ \ d_1 = y_1 + b_1 - i_1 + c, \ \ \ $ where $ \ y_1 \sim F(y_0,\sigma^2)$

	\

	\item[Period 2] $ \ \ \ d_2 = g(i_0) - b_0(1 + r_0) + g(i_1) - b_1(1 + r_1)$
\end{itemize}
\end{itemize}

\begin{eqnarray*}
	\begin{aligned}
\max_{\{ b_t,i_t,c \}_{t=0,1}} \ \ &\E \Big[  d_0 + d_1 + d_2     \Big| F  \Big] \\
\text{subject to} \ \ &r_0 = \frac{1}{2}\alpha_0 b_0 \ \ \text{and} \ \ r_1 = \frac{1}{2}\alpha_1 b_1 \\
&d_t \geq 0, \ \ \ t = 0,1,2 \\
\end{aligned}
\end{eqnarray*}

\

\begin{center}
Financial shock: $\uparrow \alpha_0$ $ \ \ \ \ $ vs $ \ \ \ \ $ Uncertainty shock: $\uparrow \sigma^2$
\end{center}

}

\frame{\frametitle{Solution}

	Assuming that firm needs external finance in equilibrium, model implies: 
\begin{itemize}
	\item $i_0 = y_0 + b_0 - c$,
	\item $i_1 = y_1 + b_1 + c$,
\end{itemize}
and first order conditions are
\begin{itemize}
	\item[$b_0:$] $g'(y_0 + b_0^* - c^*) = \underbrace{1 + \alpha_0 b_0^*}_{\text{Marginal Cost of $i_0$}}$

	\

	\item[$b_1:$] $\E \Big[ g'(y_1 + b_1^* + c^*) \Big] = \underbrace{1 + \alpha_1 b_1^*}_{\text{Marginal Cost of $i_1$}}$

	\

	\item[$c:$] $\underbrace{\E \Big[ g'(y_1 + b_1^* + c^*) \Big]}_{\text{Expected Marginal Return of $i_1$}} = \underbrace{g'(y_0 + b_0^* - c^*)}_{\text{Marginal Return of $i_0$}}$
\end{itemize}

}

%$\E_0 \Big[ g(y_t) \Big] > 1$ for $t=0,1$
%\begin{itemize}
	%\item[$\Rightarrow$] $d_t = 0 \ \ $ for $ \ t=0,1$
%\end{itemize}

%Objective function is,
%\begin{eqnarray*}
	%\begin{aligned}
	%	\max_{b_0,b_1,c} \ \ &g \big( i_0 \big) - b_0 - \frac{1}{2} \alpha_0 b_0^2 - y_0 + \E \bigg[  g \big( i_1 \big) - b_1 - \frac{1}{2} \alpha_1 b_1^2 - y_1   \bigg| F     \bigg]
	%\end{aligned}
%\end{eqnarray*}

\frame{\frametitle{Comparative Statics}

\begin{itemize}
	\item[$b_0:$] $g'(y_0 + b_0^* - c^*) = \underbrace{1 + \alpha_0 b_0^*}_{\text{Marginal Cost of $i_0$}}$

	\

	\item[$b_1:$] $\E \Big[ g'(y_1 + b_1^* + c^*) \Big] = \underbrace{1 + \alpha_1 b_1^*}_{\text{Marginal Cost of $i_1$}}$

	\

	\item[$c:$] $\underbrace{\E \Big[ g'(y_1 + b_1^* + c^*) \Big]}_{\text{Expected Marginal Return of $i_1$}} = \underbrace{g'(y_0 + b_0^* - c^*)}_{\text{Marginal Return of $i_0$}}$
\end{itemize}

\

\textbf{Uncertainty shock}: $y_1 \sim Q$ which is mean-preserving spread in $F$
	\begin{enumerate}
	\item[$\Rightarrow$] $c^*(\alpha_0,Q) > c^*(\alpha_0,F)$ as long as $g'''(\cdot) > 0$
\end{enumerate}

\

\textbf{Financial shock}: $\alpha_0^f > \alpha_0$ which is an exogenous increase in $r_0$
	\begin{enumerate}
	\item[$\Rightarrow$] $c^*(\alpha_0^f,F) < c^*(\alpha_0,F)$ 
\end{enumerate}

}

\frame{\frametitle{Roadmap}
	\Large{
		$ \ \ \ \ \ $ 1. Cash Reserves

		$ \ \ \ \ \ $ 2. Model

		$ \ \ \ \ \ $ 3. \textbf{Empirical Strategy}

		$ \ \ \ \ \ $ 4. Results

		$ \ \ \ \ \ $ 5. Conclusions
	}
}

\frame{\frametitle{Empirical Analysis}

Given the reduced-form system $X_t = B(L) X_{t-1} + \iota_t$ where

$$
X_t = \begin{bmatrix}
U_t \\
F_t \\
GDP_t \\
C_t \\
I_t \\
H_t \\
C2A_t \\
GDPDef_t \\
\end{bmatrix}
$$

\

Dataset ranges from 1978q1 to 2015q3.

}

\frame{\frametitle{Objective of the Empirical Strategy}

Given the reduced-form system $X_t = B(L) X_{t-1} + \iota_t$,

$\Rightarrow$ find a rotation of $\Sigma_{\iota} = \iota_t' \iota_t$ such that

\begin{enumerate}
	\item it allows $F_t$ and $U_t$ to respond to both shocks on \textbf{impact}
	\item it respects \textbf{sign-restriction} assumptions on cash
	\item it is \textbf{unique}
	\item it delivers shocks \textbf{orthogonal} to each other
	\item it is unaffected by the \textbf{order} of the estimation
\end{enumerate}

}

\frame{\frametitle{Sequential Penalty Function Approach ($\delta \geq 0$)}

	\

	\textbf{1. Uncertainty Shock}
	\begin{eqnarray*}
		\begin{aligned}
		\max_{\gamma_{U}} \ \ \ \ \ &  \ \underbrace{e_U A_0 \gamma_U}_{\text{Impact on U}} \ \ \  + \ \ \ \textcolor{red}{\delta} \underbrace{e_{C} A_0 \gamma_U}_{\text{Impact on Cash}} \\
		\end{aligned}
	\end{eqnarray*}

\textbf{Intuition}. $\gamma_{U}$ increases both uncertainty and cash on impact.

\

	\textbf{2. Financial Shock}
	\begin{eqnarray*}
		\begin{aligned}
		\max_{\gamma_{F}} \ \ \ \ \ & \  \underbrace{e_F A_0 \gamma_F}_{\text{Impact on F}} \ \ \  - \ \ \  \textcolor{red}{\delta} \underbrace{e_{C} A_0 \gamma_F}_{\text{Impact on Cash}} \ \ s.t. \ \ \underbrace{\textcolor{red}{\gamma_U \gamma_F' = 0}}_{\text{Orthogonality with U shock}} \\
		\end{aligned}
	\end{eqnarray*}

\textbf{Intuition}. $\gamma_{F}$ increases uncertainty and decreases cash on impact.

}

\frame{\frametitle{Sequential Penalty Function Approach ($\delta \geq 0$)}

		\

	\textbf{1. Financial Shock}
	\begin{eqnarray*}
		\begin{aligned}
			\max_{\gamma_{F}} \ \ \ \ \ & \  \underbrace{e_F A_0 \gamma_F}_{\text{Impact on F}} \ \ \  - \ \ \  \textcolor{red}{\delta} \underbrace{e_{C} A_0 \gamma_F}_{\text{Impact on Cash}}  \\
		\end{aligned}
	\end{eqnarray*}

	\textbf{Intuition}. $\gamma_{F}$ increases uncertainty and decreases cash on impact.

	\

	\textbf{2. Uncertainty Shock}
	\begin{eqnarray*}
		\begin{aligned}
			\max_{\gamma_{U}} \ \ \ \ \ &  \ \underbrace{e_U A_0 \gamma_U}_{\text{Impact on U}} \ \ \  + \ \ \ \textcolor{red}{\delta} \underbrace{e_{C} A_0 \gamma_U}_{\text{Impact on Cash}} \ \ s.t. \ \ \underbrace{\textcolor{red}{\gamma_U \gamma_F' = 0}}_{\text{Orthogonality with F shock}} \\
		\end{aligned}
	\end{eqnarray*}

	\textbf{Intuition}. $\gamma_{U}$ increases both uncertainty and cash on impact.

}

\frame{\frametitle{Generalized Penalty Function Approach}

	\

	\textbf{1. Financial Shock}
	\begin{eqnarray*}
		\begin{aligned}
			\max_{\gamma_{F}} \ \ \ \ \ & \  \underbrace{e_F A_0 \gamma_F}_{\text{Impact on F}} \ \ \  - \ \ \  \textcolor{red}{\delta^*} \underbrace{e_{C} A_0 \gamma_F}_{\text{Impact on Cash}}  \\
		\end{aligned}
	\end{eqnarray*}

	\textbf{2. Uncertainty Shock}
	\begin{eqnarray*}
		\begin{aligned}
			\max_{\gamma_{U}} \ \ \ \ \ &  \ \underbrace{e_U A_0 \gamma_U}_{\text{Impact on U}} \ \ \  + \ \ \ \textcolor{red}{\delta^*} \underbrace{e_{C} A_0 \gamma_U}_{\text{Impact on Cash}}  \\
		\end{aligned}
	\end{eqnarray*}

where $\textcolor{red}{\delta^*}$ is chosen such that $\textcolor{red}{\gamma_U \gamma_F' = 0}$.

\

\textbf{Economic Intuition.} Weight of sign restrictions should be large enough such that the two shocks are separated without any external constraint.

}

%	\text{subject to} \ \ \ \ \  & \ \delta \geq 0 \ \ \ \ \ \ \text{and} \ \ \ \ \ \  \underbrace{\gamma_U \gamma_U' = 1}_{\text{Normalization}}

%		\text{subject to} \ \ \ \ \ \ & \ \delta \geq 0, \ \ \ \ \ \ \ \underbrace{\gamma_F \gamma_F' = 1}_{\text{Normalization}}, \ \ \ \ \ \ \text{and}

\frame{\frametitle{Roadmap}
	\Large{
		$ \ \ \ \ \ $ 1. Cash Reserves

		$ \ \ \ \ \ $ 2. Model

		$ \ \ \ \ \ $ 3. Empirical Strategy

		$ \ \ \ \ \ $ 4. \textbf{Results}

		$ \ \ \ \ \ $ 5. Conclusions
	}
}

\frame{\frametitle{Uncertainty Shock}

}

\frame{\frametitle{Financial Shock}

}

\frame{\frametitle{Variance Explained}

}

\frame{\frametitle{Roadmap}
	\Large{
		$ \ \ \ \ \ $ 1. Cash Reserves

		$ \ \ \ \ \ $ 2. Model

		$ \ \ \ \ \ $ 3. Empirical Strategy

		$ \ \ \ \ \ $ 4. Results

		$ \ \ \ \ \ $ 5. \textbf{Conclusions}
	}
}

\frame{\frametitle{Conclusions}

\begin{itemize}

\item \textbf{Cash reserves} as an internal instrument to simultaneously identify financial and uncertainty shocks.

\

\item An \textbf{econometric tool} to overcome known SVAR shortcomings
\begin{itemize}
	\item[$\Rightarrow$] Tests using simulated data confirm the reliability of the procedure. See \textbf{Appendix A}.
\end{itemize}

\

\item Empirical results confirm the \textbf{relevance} and \textbf{exogeneity} of both shocks.
\begin{itemize}
	\item[$\Rightarrow$] Correlations with external shocks is available in \textbf{Appendix B}.
\end{itemize}

\

\item \textbf{Financial shocks} have larger effects in the \textbf{short run} while \textbf{uncertainty shocks} have a more \textbf{persistent} effect.

\end{itemize}

}

\frame{\frametitle{Next Steps}

	\begin{enumerate}

\item Empirical evidence in favor of my identification assumption

\begin{itemize}
	\item Using \textbf{Quarterly Financial Report} data to show that my results are mostly driven by small firms 
	\item Merging \textbf{Compustat} and \textbf{TRACE} to show firm-level evidence of the differential response of cash
	$$
	\frac{Cash_{it}}{Assets_{it}} = \underbrace{\beta^U}_{(+)} U_{it} + \underbrace{\beta^F}_{(-)} F_{it} + \beta^X X_{it} + \delta_i + \lambda_t + \varepsilon_{it}
	$$
\end{itemize}

\

\item Design and analyze a \textbf{dynamic GE model} 
\begin{itemize}

	\item to show my identification assumption survives to GE effects

	\item to test whether GPFA can recover both shocks

\end{itemize}

\end{enumerate}

}

\frame{\frametitle{Appendix A - Simulated Data and Generalized PFA}

	Consider the following structural model,

	\begin{itemize}
		\item $U_t = B_{UU} U_{t-1} + B_{UF} F_{t-1}  + B_{UC} C_{t-1}  +  A_{UU}s_t^U  +  A_{UF}s_t^F$
		\item $F_t = B_{FU} U_{t-1} + B_{FF} F_{t-1}  + B_{FC} C_{t-1}  +  A_{FU}s_t^U  +  A_{FF}s_t^F$
		\item $C_t = B_{CU} U_{t-1} - B_{CF} F_{t-1}  + B_{CC} C_{t-1}  +  A_{CU}s_t^U  -  A_{CF}s_t^F$
		\end{itemize}
where $s_t^U \sim N(0, \sigma^2_U)$, $s_t^F \sim N(0, \sigma^2_F)$ and $s_t^U \perp s_t^F$.

\

	Objective is to estimate structural parameters 
	\begin{itemize}
		\item using only $X_t = [U_t, \ F_t, \ C_t]$, and
		\item only knowing that $A_{ji} \geq 0$ for $j,i = \{U, \ F, \ C \}$.
	\end{itemize} 
	$\Rightarrow$ apply GPFA to test reliability of the econometric tool
}

\frame{\frametitle{Appendix A - Small Sample Performance (T = 100)}

}

\frame{\frametitle{Appendix A - Large Sample Performance (T = 100000)}

}

\frame{\frametitle{Appendix B - Correlations with Other External Shocks}

	\begin{table}[h!]
		\centering
		\begin{tabular}{lrr} \hline \hline
			                & \textbf{Uncertainty Shocks} & \textbf{Financial Shocks} \\ 
			                \hline
			\textit{External Shocks} &                    &                      \\ 
			BZP Military News        & $-0.10$  $(0.24)$  &   $0.08$  $(0.31)$   \\ 
			Ramey Military news      &  $0.07$  $(0.44)$  &   $0.02$  $(0.82)$   \\ 
			LWY Exp. Tax             &  $0.03$  $(0.74)$  &   $0.15$  $(0.11)$   \\ 
			RRMR Unexp. Tax          & $-0.13$  $(0.16)$  &   $0.05$  $(0.59)$   \\ 
		    RRMR Exp. Tax            & $-0.08$  $(0.36)$  &   $0.03$  $(0.76)$   \\ 
		    AdjTFP AR(1)             &  $0.08$  $(0.31)$  &  $-0.14$  $(0.11)$   \\ 
		    RR Mon. Policy           & $-0.13$  $(0.18)$  &  $-0.04$  $(0.70)$   \\ 
		    \hline \hline
		\end{tabular}
	\end{table}

}

\end{document}

### 2019-03-06 Latex/Conference_Modena_March2019/Brianti Gati March 2019.tex
presentation

@@
 \usepackage{graphicx,lmodern,subfigure,ulem,color,graphicx,tikz,booktabs,natbib}
+\usepackage{subfig}
 \usepackage{mathrsfs}
+\usepackage{subfigure}
 \usetheme{Warsaw}
@@
 
-	Why did U.S. output grow so slowly since the recession trough in 2009?
+	\textbf{Empirical Fact.} U.S. output has expanded only slowly in the aftermath of the financial crisis
 
@@
 
-In this paper we focus on the slowdown in TFP,
+In this paper we focus on the \textbf{slowdown in TFP},
 \begin{itemize}
-	\item[$\Rightarrow$] Which variable(s) actually boost productivity? Why? 
+	\item[$\Rightarrow$] Which variable actually boost productivity? Why? 
+	\item[$\Rightarrow$] Can this variable explain the recent slowdown in TFP?
 \end{itemize}
@@
 
-		Following Romer (1990) and Coming and Gertler (2006), several papers endogenize TFP through \textbf{R\&D investment}
+		Several papers endogenize TFP through \textbf{R\&D investment}
 		\begin{itemize}
-			\item Financial crisis $\Rightarrow$ $\downarrow$ $Y^D$ $\Rightarrow$ $\downarrow$ R\&D $\Rightarrow$ $\downarrow$ TFP $\Rightarrow$ $\downarrow$ $Y^S$
+			\item Financial crisis $\Rightarrow$ $\downarrow$ $Y$ $\Rightarrow$ $\downarrow$ R\&D $\Rightarrow$ $\downarrow$ TFP 
 		\end{itemize}
@@
 
-		Unfortunately, as showed by Oliner et al. (2007) and Jorgerson et al. (2008), TFP have started slowing down \textbf{before} the crisis.
-		%\begin{itemize}
-		%	\item[$\Rightarrow$] Medium-run business cycle models cannot be the full story
-		%\end{itemize}
+		However, as showed by Oliner et al. (2007) and Jorgerson et al. (2008), TFP have started slowing down \textbf{before} the crisis.
+		\begin{itemize}
+			\item[$\Rightarrow$] R\&D cannot be the full story
+		\end{itemize}
 
@@
 
-	We follow an alternative avenue and focus on the relation between \textbf{information and communication technology investment} (ICTI) and future total factor productivity
+	We follow an alternative avenue and focus on the relation between \textbf{Information and Communication Technology Investment} (ICTI) and total factor productivity
 	\begin{itemize}
@@
 
-		\item We analyze a \textbf{GE model} to rationalize our empirical findings and draw conclusions concerning the nature of ICT 
+		\item We analyze a \textbf{theoretical model} to rationalize our empirical findings and draw conclusions concerning the nature of ICT 
 		\begin{itemize}
-		\item We extend the two-sector model of Greenwood et al. (1997) to accommodate for the role of ICT capital in production
+		\item We extend the 2-sector GE model of Greenwood et al. (1997) to accommodate for the role of ICT capital in production
 		\end{itemize}
@@
 
-	\frame{\frametitle{Information and Communication Technology}
+	\frame{\frametitle{Empirical Analysis}
 
-		ICT Investment is defined as \textit{total expenditure in equipment and computer software meant to be used in production (as an input) for more than a year.}
+	We estimate a structural VAR using aggregate, quarterly US data from 1989Q1 to 2017Q2.
+
+\begin{equation}
+X_t = B(L)X_{t-1} + \underbrace{A \varepsilon_t}_{u_t}
+\end{equation}
+
 \begin{itemize}
-			\item $\uparrow$ ICT Investment  $\Rightarrow$ $\uparrow$ ICT capital stock in the economy
+	\item $X_t = [ TFP_t   \ \ ICTI_t   \ \ 	RP_t \ \ Y_t ]$ where $RP_t = \pi^{IT}_t/\pi^{CPI}_t$
+	\item $Y_t$ represents the log transformations of endogenous variables
+	\item A is Cholesky decomposition of $\Sigma_u = u_t' u_t$
 \end{itemize}
@@
 
-\
+Focus is on the second structural shock $\varepsilon_{2,t}$ 
+\begin{itemize}
+	\item[$\Rightarrow$] $\varepsilon_{2,t}$ maximizes the impact effect on $ICTI_t$ and is orthogonal to contemporaneous innovations in TFP
+\end{itemize}
 
@@
 
-	\frame{\frametitle{Motivation: Empirical Challenge in Structural VAR}
+	\frame{
+\frametitle{Impulse Response of TFP to $\varepsilon_{2,t}$}
 
-	Empirically distinguishing between financial and uncertainty shocks is difficult
+\begin{figure}[h!]
+	\begin{center}
+		\includegraphics[scale=0.25]{fig_ICT_Shock_on_TFPUtil_empirical_fullEconomy}
+		\label{fig:TFP_main}
+	\end{center}
+\end{figure}
+}
+
+\frame{
+	\frametitle{Impulse Responses of $X_t$ to $\varepsilon_{2,t}$}
+
+%\begin{figure}[h!]
+%	\subfigure{\includegraphics[width=  0.2]{fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}} \hspace{.2in} 
+%	\subfigure{\includegraphics[width=  0.2]{fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}} \hspace{.2in} 
+%	\subfigure{\includegraphics[width=   0.2]{fig_ICT_Shock_on_GDP_empirical_fullEconomy}} \hspace{.2in} 
+%	\subfigure{\includegraphics[width=   0.2]{fig_ICT_Shock_on_Investment_empirical_fullEconomy}} 
+%\end{figure}
+
+\begin{figure}
+	\centering
+	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}}\qquad
+	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}}\qquad
+	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_GDP_empirical_fullEconomy}}\qquad
+
+		\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Investment_empirical_fullEconomy}}\qquad
+	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Consumption_empirical_fullEconomy}}\qquad
+	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Hours_empirical_fullEconomy}}\qquad
+\end{figure}
+
+}
+
+\frame{\frametitle{Robustness Checks and Related Exercises}
+
 	\begin{itemize}
-		\item[$\Rightarrow$] financial distress is empirically associated with larger volatility 
+		\item ICT shocks are \textbf{important driver} of business cycle fluctuations
+	\begin{itemize}
+		\item[-] Almost $100$\% of ICT investment on impact
+		\item[-] Around $30$\% of TFP fluctuations over 10-year horizon 
+		\item[-] Almost $40$\% of GDP fluctuations over BC frequencies
 	\end{itemize}
@@
 
-Within a SVAR framework, this correlation significantly complicates identification of both shocks
-\begin{enumerate}
-	\item Implausible \textbf{zero-contemporaneous restrictions}
+\item \textbf{Results are robust} to
 \begin{itemize}
-		\item[$\Rightarrow$] Both $F_t$ and $U_t$ are fast moving
+	\item[-] Changing the available information in the system
+	\begin{itemize}
+	\item[$\rightarrow$] Estimated ICT shocks pass Forni-Gambetti test
 	\end{itemize}
-	\item Unavailable instruments for \textbf{sign restrictions}	
+	\item[-] Not controlling for contemporaneous TFP
+	\item[-] Controlling for news shocks \`a la Barsky and Sims
+	\item[-] Controlling for other shocks
 	\begin{itemize}
-		\item[$\Rightarrow$] Current theoretical models predict same qualitative effects on both prices and quantities
+		\item[$\rightarrow$] Ramey Military News 
+		\item[$\rightarrow$]  Romer-Romer Monetary Policy 
+		\item[$\rightarrow$]  \dots
 	\end{itemize}
-\end{enumerate}
-
-}
-
-\frame{\frametitle{My contribution}
-
-	I want to take a step back and show evidence and theory that financial and uncertainty shocks are \textbf{qualitative different}.
-
-	\
-
-	In particular,
-
-	\begin{enumerate}
-		\item \textbf{Corporate cash holdings} respond differently to financial and uncertainty shocks. 
-		\begin{itemize}
-			\item[$\Rightarrow$] Identification assumption
 \end{itemize}
-
-		\
-
-		\item I provide a \textbf{new econometric tool} to simultaneously identify two structural shocks when an internal instrument is available.\begin{itemize}
-			\item[$\Rightarrow$] Generalized Penalty Function Approach  
-		\end{itemize}
-
-	\end{enumerate}
-}
-
-\frame{\frametitle{Roadmap}
-	\Large{
-		$ \ \ \ \ \ $ 1. \textbf{Cash Holdings}
-
-		$ \ \ \ \ \ $ 2. Model
-
-		$ \ \ \ \ \ $ 3. Empirical Strategy
-
-		$ \ \ \ \ \ $ 4. Results
-
-		$ \ \ \ \ \ $ 5. Conclusions
-	}
-}
-
-\frame{\frametitle{Corporate Cash Holdings}
-
-	\
-
-\textbf{Cash and Cash Equivalents} refer to assets a business holds as ready cash
-\begin{itemize}
-	\item Coffer as petty cash
-	\item Bank accounts
-	\item Certificates of deposits
-\end{itemize}
-
-\
-
-U.S. large firms have cash equal to about 15\% of total assets.
-
-\
-
-It is a \textbf{stock variable}, 
-$$
-Cash_t = Cash_{t-1} + NY_t + \delta K_t - I_t + B_t - D_t.
-$$
-
-}
-
-\frame{\frametitle{Cross-Sectional Evidence}
-
-	\textbf{Cash} and \textbf{Financial Frictions}
-	\begin{itemize}
-		\item[$\Rightarrow$] Cash is a substitute for external finance 
-		\item[] \textit{Kaplan and Zingales (1997); Almeida, et al. (2004); Campello at al. (2010); Campello et al. (2011).}
-	\end{itemize}
-
-\
-
-\textbf{Cash} and \textbf{Uncertainty}
-	\begin{itemize}
-	\item[$\Rightarrow$] Cash is positively associated with uncertainty shocks 
-	\item[] \textit{Han and Qiu (2007); Baum et al. (2008); Bloom et al. (2018); Alfaro et al. (2018).}
 \end{itemize}
@@
 
-\frame{\frametitle{Aggregate Evidence}
+\frame{\frametitle{Takeaway}
 
-Aggregate quarterly cash (CHEQ) and assets (ATQ) using \textbf{Compustat} from 1961 to 2018.
+	We identify a shock specific to the ICT sector where prices and quantities move in different directions
 
@@
 
-Remove seasonality using 7-term Henderson filter on aggregate cash and aggregate assets and obtain \textbf{Cash2Assets}.
-
-\
-
-	\begin{table}[h!]
-	\centering
-	\begin{tabular}{llcc} \hline \hline
-		                         & $\Delta$GDP         & U                &                   F    \\ 
-		\hline
-		\textit{Correlations}    &                     &                  &                                            \\ 
-		U                        &      $-0.48^{***}$                &                  &                    \\
-		F                        &  $-0.36^{***}$   &     $0.22^{***}$       &                             \\ 
-		C2A                      &     $-0.06  $               &       $0.43^{***}$      &            $-0.37^{***}$           \\ 
-		\hline \hline
-	\end{tabular}
-\end{table}
-
-}
-
-\frame{\frametitle{Roadmap}
-	\Large{
-		$ \ \ \ \ \ $ 1. Cash Holdings
-
-		$ \ \ \ \ \ $ 2. \textbf{Model}
-
-		$ \ \ \ \ \ $ 3. Empirical Strategy
-
-		$ \ \ \ \ \ $ 4. Results
-
-		$ \ \ \ \ \ $ 5. Conclusions
-	}
-}
-
-%\frame{\frametitle{Economic Intuition I}
-
-%To provide an economic intuition of the differential response of \textbf{cash holdings} to uncertainty and financial shocks, I present a properly augmented model in the spirit of 
-%\begin{itemize}
-	%\item Almeida, Campello, and Weisbach (2004)
-	%\item Han and Qiu (2007)
-%\end{itemize}
-
-%\
-
-%It is a simple representation of a dynamic setting where a credit-constrained profit-maximizing firm has a trade-off between present and future investment opportunities
-
-%}
-
-\frame{\frametitle{Model - General Setup}
+	Altough TFP does not move on impact, it start rising significantly after a couple of years
+	\begin{itemize}
+		\item this effect is significant and economically meaningful
+	\end{itemize}
 
 \begin{itemize}
-
-\item \textbf{Three-period partial equilibrium} model
-
-\
-
-\item Firm \textbf{maximizes} sum of \textbf{dividends} 
+	\item Supply shocks specific to the ICT sector explain a large part of medium-run TFP fluctuations
 	\begin{itemize}
-\item Discount factor $\beta$ is one
+		\item[-] ICT prices fall relatively to CPI
 	\end{itemize}
-
-\
-
-\item \textbf{Choice variables} are
-\begin{itemize}
-	\item \textbf{Investments} $i_0$ and $i_1$ in period 0 and 1
-	\item Amount to \textbf{borrow} $b_0$ and $b_1$ in period 0 and 1
-	\item \textbf{Cash} $c$ in period 0 to be carried in period 1
-\end{itemize}
-
-\
-
-\item Feature \textbf{financial frictions} in the form of risk premium
-
-\
-
-\item \textbf{Gross returns} $g(\cdot)$ happen in the last period for both investments
-\begin{itemize}
-	\item where $g'(\cdot) > 0$ and $g''(\cdot) < 0$.
-\end{itemize}
-
+	\item Shocks which explains large part of TFP fluctuations
 \end{itemize}
@@
 
-\frame{\frametitle{Model - Analytical Setup}
-
-\begin{itemize}
-	\item[]
-\begin{itemize}
-     \item[Period 0] $ \ \ \ d_0 = y_0 + b_0 - i_0 - c$
-
-	\
-
-	\item[Period 1] $ \ \ \ d_1 = y_1 + b_1 - i_1 + c, \ \ \ $ where $ \ y_1 \sim F(y_0,\sigma^2)$
-
-	\
-
-	\item[Period 2] $ \ \ \ d_2 = g(i_0) - b_0(1 + r_0) + g(i_1) - b_1(1 + r_1)$
-\end{itemize}
-\end{itemize}
-
-\begin{eqnarray*}
-	\begin{aligned}
-\max_{\{ b_t,i_t,c \}_{t=0,1}} \ \ &\E \Big[  d_0 + d_1 + d_2     \Big| F  \Big] \\
-\text{subject to} \ \ &r_0 = \frac{1}{2}\alpha_0 b_0 \ \ \text{and} \ \ r_1 = \frac{1}{2}\alpha_1 b_1 \\
-&d_t \geq 0, \ \ \ t = 0,1,2 \\
-\end{aligned}
-\end{eqnarray*}
-
-\
-
-\begin{center}
-Financial shock: $\uparrow \alpha_0$ $ \ \ \ \ $ vs $ \ \ \ \ $ Uncertainty shock: $\uparrow \sigma^2$
-\end{center}
-
-}
-
-\frame{\frametitle{Solution}
-
-	Assuming that firm needs external finance in equilibrium, model implies: 
-\begin{itemize}
-	\item $i_0 = y_0 + b_0 - c$,
-	\item $i_1 = y_1 + b_1 + c$,
-\end{itemize}
-and first order conditions are
-\begin{itemize}
-	\item[$b_0:$] $g'(y_0 + b_0^* - c^*) = \underbrace{1 + \alpha_0 b_0^*}_{\text{Marginal Cost of $i_0$}}$
-
-	\
-
-	\item[$b_1:$] $\E \Big[ g'(y_1 + b_1^* + c^*) \Big] = \underbrace{1 + \alpha_1 b_1^*}_{\text{Marginal Cost of $i_1$}}$
-
-	\
-
-	\item[$c:$] $\underbrace{\E \Big[ g'(y_1 + b_1^* + c^*) \Big]}_{\text{Expected Marginal Return of $i_1$}} = \underbrace{g'(y_0 + b_0^* - c^*)}_{\text{Marginal Return of $i_0$}}$
-\end{itemize}
-
-}
-
-%$\E_0 \Big[ g(y_t) \Big] > 1$ for $t=0,1$
-%\begin{itemize}
-	%\item[$\Rightarrow$] $d_t = 0 \ \ $ for $ \ t=0,1$
-%\end{itemize}
-
-%Objective function is,
-%\begin{eqnarray*}
-	%\begin{aligned}
-	%	\max_{b_0,b_1,c} \ \ &g \big( i_0 \big) - b_0 - \frac{1}{2} \alpha_0 b_0^2 - y_0 + \E \bigg[  g \big( i_1 \big) - b_1 - \frac{1}{2} \alpha_1 b_1^2 - y_1   \bigg| F     \bigg]
-	%\end{aligned}
-%\end{eqnarray*}
-
-\frame{\frametitle{Comparative Statics}
-
-\begin{itemize}
-	\item[$b_0:$] $g'(y_0 + b_0^* - c^*) = \underbrace{1 + \alpha_0 b_0^*}_{\text{Marginal Cost of $i_0$}}$
-
-	\
-
-	\item[$b_1:$] $\E \Big[ g'(y_1 + b_1^* + c^*) \Big] = \underbrace{1 + \alpha_1 b_1^*}_{\text{Marginal Cost of $i_1$}}$
-
-	\
-
-	\item[$c:$] $\underbrace{\E \Big[ g'(y_1 + b_1^* + c^*) \Big]}_{\text{Expected Marginal Return of $i_1$}} = \underbrace{g'(y_0 + b_0^* - c^*)}_{\text{Marginal Return of $i_0$}}$
-\end{itemize}
-
-\
-
-\textbf{Uncertainty shock}: $y_1 \sim Q$ which is mean-preserving spread in $F$
-	\begin{enumerate}
-	\item[$\Rightarrow$] $c^*(\alpha_0,Q) > c^*(\alpha_0,F)$ as long as $g'''(\cdot) > 0$
-\end{enumerate}
-
-\
-
-\textbf{Financial shock}: $\alpha_0^f > \alpha_0$ which is an exogenous increase in $r_0$
-	\begin{enumerate}
-	\item[$\Rightarrow$] $c^*(\alpha_0^f,F) < c^*(\alpha_0,F)$ 
-\end{enumerate}
-
-}
-
-\frame{\frametitle{Roadmap}
-	\Large{
-		$ \ \ \ \ \ $ 1. Cash Reserves
-
-		$ \ \ \ \ \ $ 2. Model
-
-		$ \ \ \ \ \ $ 3. \textbf{Empirical Strategy}
-
-		$ \ \ \ \ \ $ 4. Results
-
-		$ \ \ \ \ \ $ 5. Conclusions
-	}
-}
-
-\frame{\frametitle{Empirical Analysis}
-
-Given the reduced-form system $X_t = B(L) X_{t-1} + \iota_t$ where
-
-$$
-X_t = \begin{bmatrix}
-U_t \\
-F_t \\
-GDP_t \\
-C_t \\
-I_t \\
-H_t \\
-C2A_t \\
-GDPDef_t \\
-\end{bmatrix}
-$$
-
-\
-
-Dataset ranges from 1978q1 to 2015q3.
-
-}
-
-\frame{\frametitle{Objective of the Empirical Strategy}
-
-Given the reduced-form system $X_t = B(L) X_{t-1} + \iota_t$,
-
-$\Rightarrow$ find a rotation of $\Sigma_{\iota} = \iota_t' \iota_t$ such that
-
-\begin{enumerate}
-	\item it allows $F_t$ and $U_t$ to respond to both shocks on \textbf{impact}
-	\item it respects \textbf{sign-restriction} assumptions on cash
-	\item it is \textbf{unique}
-	\item it delivers shocks \textbf{orthogonal} to each other
-	\item it is unaffected by the \textbf{order} of the estimation
-\end{enumerate}
-
-}
-
-\frame{\frametitle{Sequential Penalty Function Approach ($\delta \geq 0$)}
-
-	\
-
-	\textbf{1. Uncertainty Shock}
-	\begin{eqnarray*}
-		\begin{aligned}
-		\max_{\gamma_{U}} \ \ \ \ \ &  \ \underbrace{e_U A_0 \gamma_U}_{\text{Impact on U}} \ \ \  + \ \ \ \textcolor{red}{\delta} \underbrace{e_{C} A_0 \gamma_U}_{\text{Impact on Cash}} \\
-		\end{aligned}
-	\end{eqnarray*}
-
-\textbf{Intuition}. $\gamma_{U}$ increases both uncertainty and cash on impact.
-
-\
-
-	\textbf{2. Financial Shock}
-	\begin{eqnarray*}
-		\begin{aligned}
-		\max_{\gamma_{F}} \ \ \ \ \ & \  \underbrace{e_F A_0 \gamma_F}_{\text{Impact on F}} \ \ \  - \ \ \  \textcolor{red}{\delta} \underbrace{e_{C} A_0 \gamma_F}_{\text{Impact on Cash}} \ \ s.t.
-\ \ \underbrace{\textcolor{red}{\gamma_U \gamma_F' = 0}}_{\text{Orthogonality with U shock}} \\
-		\end{aligned}
-	\end{eqnarray*}
-
-\textbf{Intuition}. $\gamma_{F}$ increases uncertainty and decreases cash on impact.
-
-}
-
-\frame{\frametitle{Sequential Penalty Function Approach ($\delta \geq 0$)}
-
-		\
-
-	\textbf{1. Financial Shock}
-	\begin{eqnarray*}
-		\begin{aligned}
-			\max_{\gamma_{F}} \ \ \ \ \ & \  \underbrace{e_F A_0 \gamma_F}_{\text{Impact on F}} \ \ \  - \ \ \  \textcolor{red}{\delta} \underbrace{e_{C} A_0 \gamma_F}_{\text{Impact on Cash}}  \\
-		\end{aligned}
-	\end{eqnarray*}
-
-	\textbf{Intuition}. $\gamma_{F}$ increases uncertainty and decreases cash on impact.
-
-	\
-
-	\textbf{2. Uncertainty Shock}
-	\begin{eqnarray*}
-		\begin{aligned}
-			\max_{\gamma_{U}} \ \ \ \ \ &  \ \underbrace{e_U A_0 \gamma_U}_{\text{Impact on U}} \ \ \  + \ \ \ \textcolor{red}{\delta} \underbrace{e_{C} A_0 \gamma_U}_{\text{Impact on Cash}} \ \ s.t.
-\ \ \underbrace{\textcolor{red}{\gamma_U \gamma_F' = 0}}_{\text{Orthogonality with F shock}} \\
-		\end{aligned}
-	\end{eqnarray*}
-
-	\textbf{Intuition}. $\gamma_{U}$ increases both uncertainty and cash on impact.
-
-}
-
-\frame{\frametitle{Generalized Penalty Function Approach}
-
-	\
-
-	\textbf{1. Financial Shock}
-	\begin{eqnarray*}
-		\begin{aligned}
-			\max_{\gamma_{F}} \ \ \ \ \ & \  \underbrace{e_F A_0 \gamma_F}_{\text{Impact on F}} \ \ \  - \ \ \  \textcolor{red}{\delta^*} \underbrace{e_{C} A_0 \gamma_F}_{\text{Impact on Cash}}  \\
-		\end{aligned}
-	\end{eqnarray*}
-
-	\textbf{2. Uncertainty Shock}
-	\begin{eqnarray*}
-		\begin{aligned}
-			\max_{\gamma_{U}} \ \ \ \ \ &  \ \underbrace{e_U A_0 \gamma_U}_{\text{Impact on U}} \ \ \  + \ \ \ \textcolor{red}{\delta^*} \underbrace{e_{C} A_0 \gamma_U}_{\text{Impact on Cash}}  \\
-		\end{aligned}
-	\end{eqnarray*}
-
-where $\textcolor{red}{\delta^*}$ is chosen such that $\textcolor{red}{\gamma_U \gamma_F' = 0}$.
-
-\
-
-\textbf{Economic Intuition.} Weight of sign restrictions should be large enough such that the two shocks are separated without any external constraint.
-
-}
-
-%	\text{subject to} \ \ \ \ \  & \ \delta \geq 0 \ \ \ \ \ \ \text{and} \ \ \ \ \ \  \underbrace{\gamma_U \gamma_U' = 1}_{\text{Normalization}}
-
-%		\text{subject to} \ \ \ \ \ \ & \ \delta \geq 0, \ \ \ \ \ \ \ \underbrace{\gamma_F \gamma_F' = 1}_{\text{Normalization}}, \ \ \ \ \ \ \text{and}
-
-\frame{\frametitle{Roadmap}
-	\Large{
-		$ \ \ \ \ \ $ 1. Cash Reserves
-
-		$ \ \ \ \ \ $ 2. Model
-
-		$ \ \ \ \ \ $ 3. Empirical Strategy
-
-		$ \ \ \ \ \ $ 4. \textbf{Results}
-
-		$ \ \ \ \ \ $ 5. Conclusions
-	}
-}
-
-\frame{\frametitle{Uncertainty Shock}
-
-}
-
-\frame{\frametitle{Financial Shock}
-
-}
-
-\frame{\frametitle{Variance Explained}
-
-}
-
-\frame{\frametitle{Roadmap}
-	\Large{
-		$ \ \ \ \ \ $ 1. Cash Reserves
-
-		$ \ \ \ \ \ $ 2. Model
-
-		$ \ \ \ \ \ $ 3. Empirical Strategy
-
-		$ \ \ \ \ \ $ 4. Results
-
-		$ \ \ \ \ \ $ 5. \textbf{Conclusions}
-	}
-}
-
-\frame{\frametitle{Conclusions}
-
-\begin{itemize}
-
-\item \textbf{Cash reserves} as an internal instrument to simultaneously identify financial and uncertainty shocks.
-
-\
-
-\item An \textbf{econometric tool} to overcome known SVAR shortcomings
-\begin{itemize}
-	\item[$\Rightarrow$] Tests using simulated data confirm the reliability of the procedure. See \textbf{Appendix A}.
-\end{itemize}
-
-\
-
-\item Empirical results confirm the \textbf{relevance} and \textbf{exogeneity} of both shocks.
-\begin{itemize}
-	\item[$\Rightarrow$] Correlations with external shocks is available in \textbf{Appendix B}.
-\end{itemize}
-
-\
-
-\item \textbf{Financial shocks} have larger effects in the \textbf{short run} while \textbf{uncertainty shocks} have a more \textbf{persistent} effect.
-
-\end{itemize}
-
-}
-
-\frame{\frametitle{Next Steps}
-
-	\begin{enumerate}
-
-\item Empirical evidence in favor of my identification assumption
-
-\begin{itemize}
-	\item Using \textbf{Quarterly Financial Report} data to show that my results are mostly driven by small firms 
-	\item Merging \textbf{Compustat} and \textbf{TRACE} to show firm-level evidence of the differential response of cash
-	$$
-	\frac{Cash_{it}}{Assets_{it}} = \underbrace{\beta^U}_{(+)} U_{it} + \underbrace{\beta^F}_{(-)} F_{it} + \beta^X X_{it} + \delta_i + \lambda_t + \varepsilon_{it}
-	$$
-\end{itemize}
-
-\
-
-\item Design and analyze a \textbf{dynamic GE model} 
-\begin{itemize}
-
-	\item to show my identification assumption survives to GE effects
-
-	\item to test whether GPFA can recover both shocks
-
-\end{itemize}
-
-\end{enumerate}
-
-}
-
-\frame{\frametitle{Appendix A - Simulated Data and Generalized PFA}
-
-	Consider the following structural model,
-
-	\begin{itemize}
-		\item $U_t = B_{UU} U_{t-1} + B_{UF} F_{t-1}  + B_{UC} C_{t-1}  +  A_{UU}s_t^U  +  A_{UF}s_t^F$
-		\item $F_t = B_{FU} U_{t-1} + B_{FF} F_{t-1}  + B_{FC} C_{t-1}  +  A_{FU}s_t^U  +  A_{FF}s_t^F$
-		\item $C_t = B_{CU} U_{t-1} - B_{CF} F_{t-1}  + B_{CC} C_{t-1}  +  A_{CU}s_t^U  -  A_{CF}s_t^F$
-		\end{itemize}
-where $s_t^U \sim N(0, \sigma^2_U)$, $s_t^F \sim N(0, \sigma^2_F)$ and $s_t^U \perp s_t^F$.
-
-\
-
-	Objective is to estimate structural parameters 
-	\begin{itemize}
-		\item using only $X_t = [U_t, \ F_t, \ C_t]$, and
-		\item only knowing that $A_{ji} \geq 0$ for $j,i = \{U, \ F, \ C \}$.
-	\end{itemize} 
-	$\Rightarrow$ apply GPFA to test reliability of the econometric tool
-}
-
-\frame{\frametitle{Appendix A - Small Sample Performance (T = 100)}
-
-}
-
-\frame{\frametitle{Appendix A - Large Sample Performance (T = 100000)}
-
-}
-
-\frame{\frametitle{Appendix B - Correlations with Other External Shocks}
-
-	\begin{table}[h!]
-		\centering
-		\begin{tabular}{lrr} \hline \hline
-			                & \textbf{Uncertainty Shocks} & \textbf{Financial Shocks} \\ 
-			                \hline
-			\textit{External Shocks} &                    &                      \\ 
-			BZP Military News        & $-0.10$  $(0.24)$  &   $0.08$  $(0.31)$   \\ 
-			Ramey Military news      &  $0.07$  $(0.44)$  &   $0.02$  $(0.82)$   \\ 
-			LWY Exp. Tax             &  $0.03$  $(0.74)$  &   $0.15$  $(0.11)$   \\ 
-			RRMR Unexp. Tax          & $-0.13$  $(0.16)$  &   $0.05$  $(0.59)$   \\ 
-		    RRMR Exp. Tax            & $-0.08$  $(0.36)$  &   $0.03$  $(0.76)$   \\ 
-		    AdjTFP AR(1)             &  $0.08$  $(0.31)$  &  $-0.14$  $(0.11)$   \\ 
-		    RR Mon. Policy           & $-0.13$  $(0.18)$  &  $-0.04$  $(0.70)$   \\ 
-		    \hline \hline
-		\end{tabular}
-	\end{table}
-
-}
-
 \end{document}

### 2019-03-06 Latex/Conference_Modena_March2019/Brianti Gati March 2019.tex
more on presentation

@@
 \usepackage{graphicx,lmodern,subfigure,ulem,color,graphicx,tikz,booktabs,natbib}
-\usepackage{subfig}
+%\usepackage{subfig}
 \usepackage{mathrsfs}
@@
 \begin{itemize}
-	\item[$\Rightarrow$] Which variable actually boost productivity? Why? 
-	\item[$\Rightarrow$] Can this variable explain the recent slowdown in TFP?
+	\item[$\Rightarrow$] Which variable actually boosted productivity in the last three decades? Why? 
 \end{itemize}
@@
 	\begin{itemize}
-			\item \textit{Expenditure in equipment and computer software meant to be used in production (as an input) for more than a year.}
+			\item \textit{Acquisition of equipment and computer software meant to be used in production for more than a year.}
 			\end{itemize}
@@
 	\begin{enumerate}
-		\item \textbf{Empirical evidence} that contemporaneous jumps in ICTI explain significant and persistent increases in future TFP
+		\item \textbf{Empirical Contribution} that contemporaneous jumps in ICTI explain significant and persistent increases in future TFP
 		\begin{itemize}
-			\item SVAR techniques on U.S. aggregates to identify supply shocks specific to the ICT sector
+			\item Structural VAR techniques on U.S. aggregates to identify ICT investment shocks
 		\end{itemize}
@@
 
-	We estimate a structural VAR using aggregate, quarterly US data from 1989Q1 to 2017Q2.
+	We estimate a structural VAR using aggregate quarterly US data from 1989Q1 to 2017Q2.
 
@@
 
-\begin{figure}
-	\centering
-	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}}\qquad
-	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}}\qquad
-	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_GDP_empirical_fullEconomy}}\qquad
+%\begin{figure}
+%	\centering
+%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}}\qquad
+%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}}\qquad
+%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_GDP_empirical_fullEconomy}}\qquad
 
-		\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Investment_empirical_fullEconomy}}\qquad
-	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Consumption_empirical_fullEconomy}}\qquad
-	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Hours_empirical_fullEconomy}}\qquad
-\end{figure}
+%		\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Investment_empirical_fullEconomy}}\qquad
+%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Consumption_empirical_fullEconomy}}\qquad
+%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Hours_empirical_fullEconomy}}\qquad
+%\end{figure}
 
@@
 
-\frame{\frametitle{Robustness Checks and Related Exercises}
+\frame{\frametitle{Variance Decomposition Analysis and Robustness Checks}
 
 	\begin{itemize}
-		\item ICT shocks are \textbf{important driver} of business cycle fluctuations
+		\item ICT shocks are an \textbf{important driver} of economic fluctuations
 	\begin{itemize}
-		\item[-] Almost $100$\% of ICT investment on impact
 		\item[-] Around $30$\% of TFP fluctuations over 10-year horizon 
@@
 
-\item \textbf{Results are robust} to
+\
+
+\item \textbf{Results are robust} after
 \begin{itemize}
-	\item[-] Changing the available information in the system
-	\begin{itemize}
-	\item[$\rightarrow$] Estimated ICT shocks pass Forni-Gambetti test
+	\item[-] controlling for news shocks \`a la Barsky and Sims
+	\item[-] controlling for other shocks estimated via narrative approach
+     \item[-] ordering TFP after ICT investment
 \end{itemize}
-	\item[-] Not controlling for contemporaneous TFP
-	\item[-] Controlling for news shocks \`a la Barsky and Sims
-	\item[-] Controlling for other shocks
-	\begin{itemize}
-		\item[$\rightarrow$] Ramey Military News 
-		\item[$\rightarrow$]  Romer-Romer Monetary Policy 
-		\item[$\rightarrow$]  \dots
-	\end{itemize}
-\end{itemize}
+
 \end{itemize}

### 2019-03-07 Latex/Conference_Modena_March2019/Brianti Gati March 2019.tex
presentation almost done

@@
 
-\title{ICT-Specific Investment Shocks and Economic Fluctuations}
-%\\ \bigskip \\ \normalsize{Evidence and Theory of a General-Purpose Technology}
+\title{ICT-Specific Investment Shocks and Economic Fluctuations \bigskip \\ \normalsize{Evidence and Theory of a General-Purpose Technology}}
 \author{Marco Brianti, Boston College\\Laura G\'ati, Boston College}
 \institute{Convegno RECent\\Modena}
-\date{March 2019}
+\date{\textit{March 2019}}
 
@@
 		\frame{\frametitle{Motivation}
+
+\bigskip
 
@@
 
-\frame{\frametitle{Our Contribution}
+\frame{\frametitle{This Paper}
+
+\bigskip
 
 	\begin{enumerate}
-		\item \textbf{Empirical Contribution} that contemporaneous jumps in ICTI explain significant and persistent increases in future TFP
+		\item We identify ICT investment shocks using \textbf{SVAR} techniques
 		\begin{itemize}
-			\item Structural VAR techniques on U.S. aggregates to identify ICT investment shocks
+			\item A contemporaneous increase in ICT investment leads to delayed, persistent, and large rise in productivity
+             \item Historical decomposition confirms that the doc-com crash explains most of the slowdown in TFP since 2006 
 		\end{itemize}
@@
 
-		\item We analyze a \textbf{theoretical model} to rationalize our empirical findings and draw conclusions concerning the nature of ICT 
+		\item We analyze a \textbf{general equilibrium model} to rationalize our empirical findings 
 		\begin{itemize}
-		\item We extend the 2-sector GE model of Greenwood et al. (1997) to accommodate for the role of ICT capital in production
+		\item Our identified shocks can be interpreted as supply shocks specific to the ICT sector
+         \item ICT capital goods boosts productivity of ICT users thorugh a positive externality
+\begin{itemize}
+\item[$\Rightarrow$] The effectiveness of ICT depends on its own level of diffusion
+\end{itemize}
 		\end{itemize}
@@
 
-%\begin{figure}[h!]
-%	\subfigure{\includegraphics[width=  0.2]{fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}} \hspace{.2in} 
-%	\subfigure{\includegraphics[width=  0.2]{fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}} \hspace{.2in} 
-%	\subfigure{\includegraphics[width=   0.2]{fig_ICT_Shock_on_GDP_empirical_fullEconomy}} \hspace{.2in} 
-%	\subfigure{\includegraphics[width=   0.2]{fig_ICT_Shock_on_Investment_empirical_fullEconomy}} 
-%\end{figure}
+\bigskip
 
-%\begin{figure}
-%	\centering
-%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}}\qquad
-%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}}\qquad
-%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_GDP_empirical_fullEconomy}}\qquad
-
-%		\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Investment_empirical_fullEconomy}}\qquad
-%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Consumption_empirical_fullEconomy}}\qquad
-%	\subfloat{\includegraphics[height=3cm,width=3cm]{fig_ICT_Shock_on_Hours_empirical_fullEconomy}}\qquad
-%\end{figure}
+\begin{columns}[t]
+\column{.3\textwidth}
+\centering
+\includegraphics[width=3.5cm,height=3.5cm]{fig_ICT_Shock_on_ICTInvestment_empirical_fullEconomy}\\
+\bigskip
+\includegraphics[width=3.5cm,height=3.5cm]{fig_ICT_Shock_on_Investment_empirical_fullEconomy} 
+\column{.3\textwidth}
+\centering
+\includegraphics[width=3.5cm,height=3.5cm]{fig_ICT_Shock_on_RelativePriceICT_empirical_fullEconomy}\\
+\bigskip
+\includegraphics[width=3.5cm,height=3.5cm]{fig_ICT_Shock_on_Consumption_empirical_fullEconomy}
+\column{.3\textwidth}
+\centering
+\includegraphics[width=3.5cm,height=3.5cm]{fig_ICT_Shock_on_GDP_empirical_fullEconomy}\\
+\bigskip
+\includegraphics[width=3.5cm,height=3.5cm]{fig_ICT_Shock_on_Hours_empirical_fullEconomy}
+\end{columns}
 
@@
 
-\frame{\frametitle{Variance Decomposition Analysis and Robustness Checks}
+\frame{\frametitle{Related Exercises and Robustness Checks}
+
+\bigskip
 
 	\begin{itemize}
-		\item ICT shocks are an \textbf{important driver} of economic fluctuations
+		\item \textbf{Variance Decomposition Analysis}
 	\begin{itemize}
@@
 	\end{itemize}
+\item[$\Rightarrow$]  ICT shocks are an \textbf{important driver} of economic fluctuations
 
@@
 
+\item \textbf{Historical Decomposition Analysis}
+\begin{itemize}
+\item[-] Large negative shocks in 2000-2001 (dot-com crash) explain the slowdown in TFP since 2006
+\end{itemize}
+\item[$\Rightarrow$] ICT shocks \textbf{rationalize} the facts by Fernald et al. (2017)
+
 \
 
-\item \textbf{Results are robust} after
+\item \textbf{Resulness Checks} 
 \begin{itemize}
-	\item[-] controlling for news shocks \`a la Barsky and Sims
-	\item[-] controlling for other shocks estimated via narrative approach
-     \item[-] ordering TFP after ICT investment
+	\item[-] Controlling for news shocks \`a la Barsky and Sims
+	\item[-] Controlling for other shocks estimated via narrative approach
 \end{itemize}
-
+\item[$\Rightarrow$]  ICT shocks are \textbf{not confounded} with other shocks
 \end{itemize}
@@
 
-\frame{\frametitle{Takeaway}
+\frame{\frametitle{Model}
 
-	We identify a shock specific to the ICT sector where prices and quantities move in different directions
+Main objectives of theoretical analysis
+\begin{itemize}
+\item[1.] Providing structural interpretation to the identified shocks
+\begin{itemize}
+\item[$\Rightarrow$] ICT shocks move price and quantities in different directions
+\end{itemize}
+\item[2.] Rationalize the relation between current ICT investment and future TFP
+\begin{itemize}
+\item[$\Rightarrow$] Why current ICT investment drives future TFP?
+\end{itemize}
+\end{itemize}
 
@@
 
-	Altough TFP does not move on impact, it start rising significantly after a couple of years
+We extend and analyze a 2-sector GE model in the spirit of Greenwood et al. (2007). Two main assumptions are in place,
 \begin{itemize}
-		\item this effect is significant and economically meaningful
-	\end{itemize}
-
-\begin{itemize}
-	\item Supply shocks specific to the ICT sector explain a large part of medium-run TFP fluctuations
-	\begin{itemize}
-		\item[-] ICT prices fall relatively to CPI
-	\end{itemize}
-	\item Shocks which explains large part of TFP fluctuations
+\item[1.] Second sector specifically produce ICT durable goods to be used as inputs in both sectors' production function
+\item[2.] Agents fail to internalize that productivity of both sectors positively depends of the overall ICT diffusion in the economy
 \end{itemize}
@@
 
+\frame{\frametitle{Main Equations}
+
+Consumption-good sector
+\begin{eqnarray}\label{equation:production_FINAL}
+y^c_t(j) = A^c_t \ \big( k^c_{t}(j) \big)^a \ \big( k^i_{t}(j) \big)^b \ \big( l_{t}(j) \big)^{1-a-b}
+\end{eqnarray}
+
+\
+
+ICT-good sector
+\begin{eqnarray}\label{equation:productionICT}
+y^i_t(q) = A_t^i \ \big( k^c_{t}(q) \big)^a \ \big( k^i_{t}(q) \big)^b \ \big( l_{t}(q) \big)^{1-a-b}
+\end{eqnarray}
+
+\
+
+where
+
+\centering
+$ A_t^c = \eta_t \ \theta^c_t \ \textcolor{red}{(k^i_{t})^{\gamma}} \ \ \ \text{and} \ \ \ A_t^i = \eta_t \ \theta^i_t \ \textcolor{red}{(k^i_{t})^{\gamma}} $
+
+}
+
+\frame{\frametitle{Conclusions}
+
+\begin{itemize}
+\item Structural VAR analysis unfolds a novel relation between current ICT investment and future TFP
+\begin{itemize}
+\item[-] Unexpected jumps of ICT investment leads to delayed and persistent rise in productivity
+\end{itemize}
+
+\
+
+\item Theoretical analysis suggests to interpret ICT capital as the general purpose technology of the last three decades
+\begin{itemize}
+\item[-] ICT diffusions increases the productivity of both ICT users and producers
+\end{itemize}
+
+\
+
+\item The fall in ICT investment during the doc-com crash has the right timing to rationalize the structural break in TFP
+\end{itemize}
+
+}
+
+\frame{\frametitle{Estimated Shocks}
+
+\begin{figure}[h!]
+	\begin{center}
+		\includegraphics[scale=0.25]{Removing_FLVariables}
+		\label{fig:TFP_main}
+	\end{center}
+\end{figure}
+
+}
+
 \end{document}

### 2019-03-07 Latex/Conference_Modena_March2019/Brianti Gati March 2019.tex
presentation with Laura comments

@@
 \begin{itemize}
-	\item[$\Rightarrow$] Which variable actually boosted productivity in the last three decades? Why? 
+	\item[$\Rightarrow$] Which variable boosted productivity in the last three decades? 
+\item[$\Rightarrow$] Can this variable explain its recent slowdown?
 \end{itemize}
@@
 
-		However, as showed by Oliner et al. (2007) and Jorgerson et al. (2008), TFP have started slowing down \textbf{before} the crisis.
+		However, as showed by Oliner et al. (2007) and Jorgenson et al. (2008), TFP have started slowing down \textbf{before} the crisis.
 		\begin{itemize}
@@
 		\begin{itemize}
-			\item A contemporaneous increase in ICT investment leads to delayed, persistent, and large rise in productivity
-             \item Historical decomposition confirms that the doc-com crash explains most of the slowdown in TFP since 2006 
+			\item A contemporaneous increase in ICT investment leads to a delayed, persistent, and large rise in productivity
+             \item Historical decomposition confirms that the dot-com crash explains most of the slowdown in TFP since 2006 
 		\end{itemize}
@@
 		\item Our identified shocks can be interpreted as supply shocks specific to the ICT sector
-         \item ICT capital goods boosts productivity of ICT users thorugh a positive externality
+         \item ICT capital boosts productivity of ICT users through a positive externality
 \begin{itemize}
@@
 
-\item \textbf{Resulness Checks} 
+\item \textbf{Rebustness Checks} 
 \begin{itemize}
@@
 
-We extend and analyze a 2-sector GE model in the spirit of Greenwood et al. (2007). Two main assumptions are in place,
+We extend and analyze a 2-sector GE model in the spirit of Greenwood et al. (2000). Two main assumptions are in place,
 \begin{itemize}
-\item[1.] Second sector specifically produce ICT durable goods to be used as inputs in both sectors' production function
+\item[1.] Second sector specifically produces ICT durable goods to be used as inputs in both sectors' production function
 \item[2.] Agents fail to internalize that productivity of both sectors positively depends of the overall ICT diffusion in the economy
@@
 
-\item The fall in ICT investment during the doc-com crash has the right timing to rationalize the structural break in TFP
+\item The fall in ICT investment during the dot-com crash has the right timing to rationalize the structural break in TFP
 \end{itemize}
@@
 
+\frame{\frametitle{IRF Matching}
+
+\
+
+\begin{columns}[t]
+\column{.3\textwidth}
+\centering
+\includegraphics[width=4cm,height=3.5cm]{fig_ICT_Shock_on_TFP_IRmatching_together}\\
+\bigskip
+\includegraphics[width=4cm,height=3.5cm]{fig_ICT_Shock_on_C_IRmatching_together} 
+\column{.3\textwidth}
+\centering
+\includegraphics[width=4cm,height=3.5cm]{fig_ICT_Shock_on_ICTI_IRmatching_together}\\
+\bigskip
+\includegraphics[width=4cm,height=3.5cm]{fig_ICT_Shock_on_RP_IRmatching_together}
+\end{columns}
+
+}
+
 \end{document}
